### 2020-05-18 documents/paper.tex
E. coli transfer

\documentclass[11pt]{article}
%Gummi|065|=)
\title{\textbf{On the application of microwave-acoustic resonant viral inactivation}}
\author{Daniel Correia}
\date{}
\begin{document}

\maketitle

\begin{abstract}
We extend this work rather trivially by:
\begin{itemize}
  \item Demonstrating a prototype emitter in an "electromagnetic mask" form-factor, costing about \$5 in prototype quantities, which can be produced in 10 million-of quantities using existing PCB infrastructure  
  \item Using a coarse-grained molecular-dynamics simulation 
  \item Discussing the biological basis for the safety of the device
  \item We show that some of the variance can be described by variance in the 
\end{itemize}
\end{abstract}

\end{document}

### 2020-05-23 documents/paper.tex
paper progress

@@
-\documentclass[11pt]{article}
-%Gummi|065|=)
-\title{\textbf{On the application of microwave-acoustic resonant viral inactivation}}
-\author{Daniel Correia}
-\date{}
+\documentclass[fleqn,10pt]{article}
+
+\usepackage[left=2cm,right=2cm,
+			top=2.25cm,
+			bottom=2.25cm,%
+			headheight=11pt,%
+			letterpaper]{geometry}
+
+\usepackage{multicol}
+\usepackage{fancyhdr}
+\usepackage{blindtext,graphicx}
+\usepackage[absolute]{textpos}
+\setlength{\TPHorizModule}{1cm}
+\setlength{\TPVertModule}{1cm}
+
+\title{The Triangulation of Titling Data in Non-Linear Gaussian Fashion via $\rho$ Series\thanks{No procrastination}}
+\date{2017\\ December}
+\author{John Doe\\ Magic Department\thanks{I am no longer a member of this department}, Richard Miles University 
+\and Richard Row, \LaTeX\ Academy}
+
 \begin{document}
 
+\flushbottom 
 \maketitle
+\thispagestyle{empty}
+
+This work was prepared by an undergraduate and has not been peer-reviewed. 
+Please consider all claims with the appropriate skepticism.
+
+\begin{textblock}{5}(14,1)
+\noindent University of Nowhere
+\end{textblock}
+\begin{textblock}{5}(1,27)
+\end{textblock}
+
+\null\hfill\begin{tabular}[t]{l@{}}
+  \textbf{My e} \\
+  \textit{My University}
+\end{tabular}
 
 \begin{abstract}
-We extend this work rather trivially by:
+We extend this landmark work rather trivially by:
 \begin{itemize}
+  \item Testing the time dependence of inactivation
   \item Demonstrating a prototype emitter in an "electromagnetic mask" form-factor, costing about \$5 in prototype quantities, which can be produced in 10 million-of quantities using existing PCB infrastructure
-  \item Using a coarse-grained molecular-dynamics simulation 
+  \item Testing power thresholds in various conditions; biological fluids of various conductivities and pHs
+  \item Using a coarse-grained molecular-dynamics simulation to optimize the impulse
+  \item Using a virus-in-the-loop optimization with a centrifugal microfluidic system
   \item Discussing the biological basis for the safety of the device
-  \item We show that some of the variance can be described by variance in the 
+  \item Showing that the deviation from the expected theshold could be explained by variance in the 
 \end{itemize}
@@
 
+With typical 2.4 GHz microwave exposure, sterilization occurs by heating of the fluid and tissue.
+
+Of course, the temperature of the atoms of the virus undoubtedly increase; but the
+
+\clearpage
+
+\begin{multicols}{1}
+
+The following properties: P1dB
+
+For ease of design and simulation, a device with Touchstone S-parameters and SPICE files is greatly preferable.
+
+\paragraph{} Feedback-loop-oscillator
+
+\paragraph{}
+The buffer amplifiers
+
+In our simulations, the varactor-tuned feedback circuit appeared to be particularly sensitive to the introduction of bias-tees.
+
+ gate must be weakly biased to ground, otherwise stray charge destroys the oscillation.
+
+\fancyhead[C]{style 1 with thin line}
+
+With 0.79 mm FR4 substrate and 0.2 mm (8 mil) wide traces, the maximum impedance achievable was about 115 ohms.
+
+If suitably high-impedance traces are not available, a common technique is to use a quarter-wavelength line (approximately 6 mm at these frequencies) terminated with a stub to produce a virtual short or open circuit [Seo 2007].
+
+However, reflections from these structures still appeared to distort signals beyond repair, even with wideband half-moon stubs [Syrett 1980].
+
+\noindent\fbox{\parbox{\linewidth}{
+	Rebuke: despite this blather, many other papers have had success with VCOs at these frequencies.
+
+}}
+
+In production, these could be accomodated by graphite-polymer resistors.
+
+Timeline
+
+\end{multicols}
+
 \end{document}

### 2020-05-23 documents/paper_2.tex
paper progress

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Stylish Article
% LaTeX Template
% Version 2.1 (1/10/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Mathias Legrand (legrand.mathias@gmail.com) 
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[fleqn,10pt]{SelfArx} % Document font size and equations flushed left

\usepackage[english]{babel}

%----------------------------------------------------------------------------------------
%	COLUMNS
%----------------------------------------------------------------------------------------

\setlength{\columnsep}{0.55cm} % Distance between the two columns of text
\setlength{\fboxrule}{0.75pt} % Width of the border around the abstract

%----------------------------------------------------------------------------------------
%	COLORS
%----------------------------------------------------------------------------------------

\definecolor{color1}{RGB}{0,0,90} % Color of the article title and sections
\definecolor{color2}{RGB}{0,20,20} % Color of the boxes behind the abstract and headings

%----------------------------------------------------------------------------------------
%	HYPERLINKS
%----------------------------------------------------------------------------------------

\usepackage{hyperref} % Required for hyperlinks
\hypersetup{hidelinks,colorlinks,breaklinks=true,urlcolor=color2,citecolor=color1,linkcolor=color1,bookmarksopen=false,pdftitle={Title},pdfauthor={Author}}

%----------------------------------------------------------------------------------------
%	ARTICLE INFORMATION
%----------------------------------------------------------------------------------------

\JournalInfo{Journal, Vol. XXI, No. 1, 1-5, 2013} % Journal information
\Archive{Additional note} % Additional notes (e.g. copyright, DOI, review/research article)

\PaperTitle{Article Title} % Article title

\Authors{John Smith\textsuperscript{1}*, James Smith\textsuperscript{2}} % Authors
\affiliation{\textsuperscript{1}\textit{Department of Biology, University of Examples, London, United Kingdom}} % Author affiliation
\affiliation{\textsuperscript{2}\textit{Department of Chemistry, University of Examples, London, United Kingdom}} % Author affiliation
\affiliation{*\textbf{Corresponding author}: john@smith.com} % Corresponding author

\Keywords{Keyword1 --- Keyword2 --- Keyword3} % Keywords - if you don't want any simply remove all the text between the curly brackets
\newcommand{\keywordname}{Keywords} % Defines the keywords heading name

%----------------------------------------------------------------------------------------
%	ABSTRACT
%----------------------------------------------------------------------------------------

\Abstract{

We extend this landmark work rather trivially by:
\begin{itemize}
  \item Testing the time dependence of inactivation
  \item Demonstrating a prototype emitter in an "electromagnetic mask" form-factor, costing about \$5 in prototype quantities, which can be produced in 10 million-of quantities using existing PCB infrastructure  
  \item Testing power thresholds in various conditions; biological fluids of various conductivities and pHs
  \item Using a coarse-grained molecular-dynamics simulation to optimize the impulse
  \item Using a virus-in-the-loop optimization with a centrifugal microfluidic system
  \item Discussing the biological basis for the safety of the device
  \item Showing that the deviation from the expected theshold could be explained by variance in the 
\end{itemize}

}

%----------------------------------------------------------------------------------------

\begin{document}

\flushbottom % Makes all text pages the same height

\maketitle % Print the title and abstract box

\tableofcontents % Print the contents section

\thispagestyle{empty} % Removes page numbering from the first page

%----------------------------------------------------------------------------------------
%	ARTICLE CONTENTS
%----------------------------------------------------------------------------------------

\section*{Introduction} % The \section*{} command stops section numbering

\addcontentsline{toc}{section}{Introduction} % Adds this section to the table of contents

 and some mathematics $\cos\pi=-1$ and $\alpha$ in the text\footnote{And some mathematics $\cos\pi=-1$ and $\alpha$ in the text.}.

%------------------------------------------------

\section{Methods}

\begin{figure*}[ht]\centering % Using \begin{figure*} makes the figure take up the entire width of the page
%\includegraphics[width=\linewidth]{view}
\caption{Wide Picture}
\label{fig:view}
\end{figure*}

\begin{equation}
\cos^3 \theta =\frac{1}{4}\cos\theta+\frac{3}{4}\cos 3\theta
\label{eq:refname2}
\end{equation}

\begin{enumerate}[noitemsep] % [noitemsep] removes whitespace between the items for a compact look
\item First item in a list
\item Second item in a list
\item Third item in a list
\end{enumerate}

\subsection{Subsection}

\paragraph{Paragraph} 
\paragraph{Paragraph}

\subsection{Subsection}

\begin{figure}[ht]\centering
%\includegraphics[width=\linewidth]{results}
\caption{In-text Picture}
\label{fig:results}
\end{figure}

Reference to Figure \ref{fig:results}.

%------------------------------------------------

\section{Results and Discussion}

\subsection{Subsection}

\begin{table}[hbt]
\caption{Table of Grades}
\centering
\begin{tabular}{llr}
\toprule
\multicolumn{2}{c}{Name} \\
\cmidrule(r){1-2}
First name & Last Name & Grade \\
\midrule
John & Doe & $7.5$ \\
Richard & Miles & $2$ \\
\bottomrule
\end{tabular}
\label{tab:label}
\end{table}

\subsubsection{Subsubsection}

\begin{description}
\item[Word] Definition
\item[Concept] Explanation
\item[Idea] Text
\end{description}

\subsubsection{Subsubsection}

\begin{itemize}[noitemsep] % [noitemsep] removes whitespace between the items for a compact look
\item First item in a list
\item Second item in a list
\item Third item in a list
\end{itemize}

\subsubsection{Subsubsection}

\subsection{Subsection}

%------------------------------------------------
\phantomsection
\section*{Acknowledgments} % The \section*{} command stops section numbering

\addcontentsline{toc}{section}{Acknowledgments} % Adds this section to the table of contents

So long and thanks for all the fish \cite{Figueredo:2009dg}.

%----------------------------------------------------------------------------------------
%	REFERENCE LIST
%----------------------------------------------------------------------------------------
\phantomsection
\bibliographystyle{unsrt}
\bibliography{sample}

%----------------------------------------------------------------------------------------

\end{document}

### 2020-05-25 documents/paper.tex
LO test something more

@@
 \usepackage[left=2cm,right=2cm,
-			top=2.25cm,
+			top=1.25cm,
 			bottom=2.25cm,%
@@
 			letterpaper]{geometry}
+
+\frenchspacing
 
@@
 \usepackage[absolute]{textpos}
+\usepackage[parfill]{parskip}
+\usepackage[colorlinks]{hyperref}
+
+\usepackage{tcolorbox}
+\newtcolorbox{autem}{colback=red!5!white,colframe=red!75!black}
+\newtcolorbox{toolchain}{colback=blue!5!white,colframe=blue!40!black!40}
+%https://tex.stackexchange.com/questions/66154/how-to-construct-a-coloured-box-with-rounded-corners
+
+%\usepackage[sfdefault,light]{roboto}
+
 \setlength{\TPHorizModule}{1cm}
@@
 
-\title{The Triangulation of Titling Data in Non-Linear Gaussian Fashion via $\rho$ Series\thanks{No procrastination}}
-\date{2017\\ December}
-\author{John Doe\\ Magic Department\thanks{I am no longer a member of this department}, Richard Miles University 
-\and Richard Row, \LaTeX\ Academy}
+\title{On the application of microwave-acoustic resonant viral inactivation
+\thanks{I would be delighted to include any criticisms or comments anyone may have; preferably leave them on the GitHub issues page, or email therobotist@gmail.com, @0xDBFB7 on Twitter, or irc.0xDBFB7.com:6667 \#covid.}}
+\date{May 2020}
+\author{Based primarily on exceptional work by }
 
@@
 This work was prepared by an undergraduate and has not been peer-reviewed.
-Please consider all claims with the appropriate skepticism.
 
-\begin{textblock}{5}(14,1)
-\noindent University of Nowhere
+Additionally, the author has no prior experience with either biology or microwave design.
+
+Testing was only performed with a surrogate bacteriophage. All experiments must be repeated with Inf. A and then SARS-NCoV-2.
+
+Please consider all claims with appropriate skepticism.
+
+\begin{textblock}{5}(1,1)
+\noindent Please view the latest version at github.com/0xDBFB7/covidinator
 \end{textblock}
-\begin{textblock}{5}(1,27)
-\end{textblock}
+%\begin{textblock}{5}(1,27)
+%\end{textblock}
 
-\null\hfill\begin{tabular}[t]{l@{}}
-  \textbf{My e} \\
-  \textit{My University}
+\null\begin{tabular}[t]{l@{}}
+  {Daniel Correia} \\
+  \textit{York University}
 \end{tabular}
@@
 \begin{abstract}
+
+Brief:
+
+Aims:
 We extend this landmark work rather trivially by:
 \begin{itemize}
-  \item Testing the time dependence of inactivation
-  \item Demonstrating a prototype emitter in an "electromagnetic mask" form-factor, costing about \$5 in prototype quantities, which can be produced in 10 million-of quantities using existing PCB infrastructure
+  \item Establishing the time dependence of inactivation
+  \item Demonstrating a modulation scheme that decreases the inactivation threshold to below current safety levels in surrogate bacteriophage
+  \item Demonstrating a prototype emitter in an "electromagnetic mask" form-factor, costing about \$5 in prototype quantities, which can reasonably be produced in 10 million-of quantities
   \item Testing power thresholds in various conditions; biological fluids of various conductivities and pHs
@@
 
+\begin{multicols}{1}
+
 With typical 2.4 GHz microwave exposure, sterilization occurs by heating of the fluid and tissue.
@@
 Of course, the temperature of the atoms of the virus undoubtedly increase; but the
+
+\begin{toolchain}
+	{\it \bf [Yang 2015]'s toolchain}
+	\begin{itemize}
+	\item Envelope/liposome breaking strength and stiffness from AFM nanoindentation data
+	\item Analytical expression assuming homogenous sphere for microwave absorption cross-section
+	\item Experimental data from microwave cuvette to 
+	\item COMSOL finite-element for illustration
+	\end{itemize}
+\end{toolchain}
+
+\paragraph{\textbf{Time dependence}}\
+
+Both Yang and [] used an apparently arbitrary 15-minute exposure in their tests - a very reasonable decision given the focus of their paper.
+
+To determine the effectiveness against airborne particles, and to minimize the power required in a dwelling phased-array beam, we must first establish the required duration of exposure.
+
+{\color{red} speculative hypothesizing \{ }
+
+In contrast to chemical inactivation, where the time dependence appears to be dominated by viscous fluid dynamic effects [Hirose 2017], or UV inactivation, where a certain dose of photons must be absorbed, one might expect RF
+
+As a damped, driven oscillator, the ring-up time of the virus depends on the Q factor.
+Yang et al.
+state the Q of Inf.
+A as between 2 and 10, so at 8 GHz the steady-state amplitude should be reached in well under 1 us.
+
+[] found a significant mechanical fatigue effect in phage capsids, where a small strain applied repetitively eventually causes a fracture.
+Such a mechanism could perhaps extend the exposure required to break the capsid or membrane.
+Other mechanisms could include some sort of lipid denaturation, requiring an absolute amount of energy absorption to break or twist bonds before the lipid fractures,
+
+{\color{red}  \} }
+
+\end{multicols}
 
@@
 
+\noindent\fbox{\parbox{\linewidth}{
+	Toolchain:
+	\begin{itemize}
+	\item QUCS 0.0.20 for AC simulation, with python-qucs and scipy's 'basinhopper' for optimization
+	\item gprMax for FDTD EM simulation
+	\item KiCAD, wcalc, scikit-rf
+	\end{itemize}
+}}
+%
 The following properties: P1dB
@@
 For ease of design and simulation, a device with Touchstone S-parameters and SPICE files is greatly preferable.
+%
+\paragraph{\textbf{The feedback loop oscillator}}\
 
-\paragraph{} Feedback-loop-oscillator
+Oscillators must meet the Barkhausen criterion:
+
+\begin{itemize}
+
+\item A 360 degree phase shift around the feedback loop (including the phase shift contribution from the amplifier, which itself varies greatly with frequency)
+\item A loop gain $>1.$
+
+\end{itemize}\
+%
+Generally a third element is also used:
+%
+\begin{itemize}
+\item A frequency-selective element that restricts oscillation modes and decreases phase noise.
+\end{itemize}
+%
+We encountered proximity effects from reflections and near-field coupling off nearby flesh; if this instablity, mode-hopping and de-tuning becomes an issue, it could be mitigated by way of shielding (adding a manufacturing step), or a tight filter around the desired mode.
+
+ design of a triple-tuned oscillator.
 
@@
 
+\paragraph{Biasing}\
+
 In our simulations, the varactor-tuned feedback circuit appeared to be particularly sensitive to the introduction of bias-tees.
 
- gate must be weakly biased to ground, otherwise stray charge destroys the oscillation.
+The gate must be weakly pulled to ground, otherwise stray charge destroys the oscillation.
 
@@
 
-If suitably high-impedance traces are not available, a common technique is to use a quarter-wavelength line (approximately 6 mm at these frequencies) terminated with a stub to produce a virtual short or open circuit [Seo 2007].
+If suitably high-impedance traces are not available, a common technique is to use a quarter-wavelength line (approximately 6 mm with the above parameters) terminated with a stub to produce a virtual short or open circuit [Seo 2007].
 
-However, reflections from these structures still appeared to distort signals beyond repair, even with wideband half-moon stubs [Syrett 1980].
+However, reflections from these structures still appeared to distort the frequency/phase response beyond repair, even with ostensibly wideband stubs [Syrett 1980].
 
 \noindent\fbox{\parbox{\linewidth}{
-	Rebuke: despite this blather, many other papers have had success with VCOs at these frequencies.
-
+	Rebuke: despite this blather, many other papers have had success with bias-tees at these frequencies.
 }}
 
-In production, these could be accomodated by graphite-polymer resistors.
+In production, these could be accomodated by graphite-polymer printed resistors.
 
-Timeline
+Odd-pole varactor-loaded combline filters appeared to have excellent phase and frequency response; however, the geometry necessitates low-inductance via stitching to the ground plane.
+
+%\noindent\fbox{\parbox{\linewidth}{
+\begin{autem}
+	{\it autem} Others have had great success with varactor-tuned comblines, especially non-grounded lines.
+\end{autem}
+
+[Tsuru 2008 fig. 10] is an excellent review of various oscillator designs.
+
+The parasitic inductance of common varactors appears to become problematic at these frequencies (but not for non-wideband use).
+
+\clearpage
+
+{\Large Mass production}
+
+\clearpage
+
+{\Large Captain's Log, Supplemental}
+
+\paragraph{Timeline}
+
+\paragraph{Comments by others}
+
+\paragraph{Lessons Learned}
+
+When iteratively testing with simulations, it may be helpful to automatically save a package with images of all the components (schematics, graphs) of each distinct test.
+Including a picture with a webcam of the assembled board is also helpful.
+
+Version control alone isn't quite enough.
+Just having a simulation setup file somewhere in the commit history isn't "discoverable" - that is, you should be able to see what the input and output was without re-running the simulation; and manually taking notes tended to disrupt the flow of testing.
+
+Write a paper to be understood; to be as clear and helpful as possible to the reader.
 

### 2020-05-25 documents/paper.tex
4-pole LO

@@
 
-\title{On the application of microwave-acoustic resonant viral inactivation
+\title{On the application of microwave acoustic resonant viral inactivation
 \thanks{I would be delighted to include any criticisms or comments anyone may have; preferably leave them on the GitHub issues page, or email therobotist@gmail.com, @0xDBFB7 on Twitter, or irc.0xDBFB7.com:6667 \#covid.}}
@@
 
-Brief:
+We extend this landmark work rather trivially by:
 
 Aims:
-We extend this landmark work rather trivially by:
+
 \begin{itemize}
@@
 Such a mechanism could perhaps extend the exposure required to break the capsid or membrane.
-Other mechanisms could include some sort of lipid denaturation, requiring an absolute amount of energy absorption to break or twist bonds before the lipid fractures,
+Other mechanisms could include some sort of lipid denaturation, requiring an absolute amount of energy absorption to break or twist bonds before the envelope fractures.
 
@@
 %
-Generally a third element is also used:
+However, a third element is also required:
 %
@@
 %
-We encountered proximity effects from reflections and near-field coupling off nearby flesh; if this instablity, mode-hopping and de-tuning becomes an issue, it could be mitigated by way of shielding (adding a manufacturing step), or a tight filter around the desired mode.
+Without this element, proximity effects from nearby flesh, startup instablity, mode-hopping, and de-tuning were all encountered.
 
@@
 
-With 0.79 mm FR4 substrate and 0.2 mm (8 mil) wide traces, the maximum impedance achievable was about 115 ohms.
+With 0.79 mm FR4 substrate and 0.2 mm (8 mil) wide traces, the maximum impedance achievable was about 115 ohms, which did not appear to be sufficient as an RF choke.
 
-If suitably high-impedance traces are not available, a common technique is to use a quarter-wavelength line (approximately 6 mm with the above parameters) terminated with a stub to produce a virtual short or open circuit [Seo 2007].
+If suitably high-impedance traces are not available, a common technique is to use a quarter-wavelength line (approximately 6 mm long with the above parameters) terminated with a stub to produce a virtual short or open circuit [Seo 2007].
 
@@
 
+\paragraph{Acknowledgements}\
+
+This paper is not novel enough to deserve this chapter, but those to be acknowledged are.
+
+Professor Shahramian's excellent video blog {\it The Signal Path} inspired this work.
+
+Hopfstader be damned; despite the name below the abstract, this paper is of course entirely the result of circumstance and luck.
+Any comparable dimwit to the author would have accomplished the same under the same conditions.
+
+It is infinitely to be regretted that such equally capable people were stuck in warehouses doing menial 15-hour shifts or assembling smartphones.
+
+Chiefly among the enablers are of course my parents, without which the author would not have existed[] - but who also supported this work financially.
+
+One Very Important Thought
+
 {\Large Captain's Log, Supplemental}
@@
 \paragraph{Lessons Learned}
+
+It may be helpful to treat simulations very similarly to IRL experiments.
 

### 2020-05-28 documents/paper.tex
SPICE

@@
 \usepackage[colorlinks]{hyperref}
+\usepackage{hyperref}
 
@@
 \thispagestyle{empty}
-
-This work was prepared by an undergraduate and has not been peer-reviewed.
-
-Additionally, the author has no prior experience with either biology or microwave design.
-
-Testing was only performed with a surrogate bacteriophage. All experiments must be repeated with Inf. A and then SARS-NCoV-2.
-
-Please consider all claims with appropriate skepticism.
 
@@
 \end{abstract}
+
+\footnote{footnotes working fine}
+
+This work was prepared by an undergraduate and has not been peer-reviewed.
+
+Additionally, the author has no prior experience with either biology or microwave design.
+
+Testing was only performed with a surrogate bacteriophage. All experiments must be repeated with Inf. A and then SARS-NCoV-2.
+
+Please consider all claims with appropriate skepticism.
+
+{\it "You cannot create a VCO that way. It is not easy."}
+{ - An anonymous admirer.}
 
@@
 
-Chiefly among the enablers are of course my parents, without which the author would not have existed[] - but who also supported this work financially.
+Chiefly among the enablers are of course my parents, Doris and Brian, without which this work would have been done by someone else[] - but who also supported this work financially.
 
@@
 
-{\Large Captain's Log, Supplemental}
+\clearpage
+
+{\Large Captain's Log, Supplemental}\\
+
+[Steenput 1999] has an interesting analytic method to synthesize a SPICE model suitable for a transient simulations from S-parameter measurements using negative resistances.
+
+However, it seems to neglect the I/V characteristic, so we synthesized the SPICE model using an optimization method [Polyfet 1998].
+
+OpenEMS is excellent, with Python bindings, lumped . However, embarassingly, we were not able to resolve all the dependency issues in order to install it.
+
+\label{para}
+\ref{para}
 
@@
 
-\paragraph{Lessons Learned}
+\paragraph{Lessons Learned} \
+
+\rule{\linewidth}{0.2pt}
 
@@
 
-When iteratively testing with simulations, it may be helpful to automatically save a package with images of all the components (schematics, graphs) of each distinct test.
+This is obvious to all compentent, but when rapidly iteratively testing with simulations, it may be helpful to automatically save a package with images of all the components (schematics, graphs) of each distinct test.
 Including a picture with a webcam of the assembled board is also helpful.
@@
 
+\rule{\linewidth}{0.2pt}
+
+A great deal of time was spent trying to resolve version conflicts and dependency hells with the numerous libraries used by all the simulation programs.
+This also wastes developer time - some fraction of issues raised are due to library version conflicts.
+OpenFOAM's Docker installation is excellent.
+
+Running chroot with the original developer's Linux distribution is also of some utility, but clunky.
+
+Packaged binaries help this slightly, but of course don't help if modifications are required, and managing shared libraries is still a tricky matter.
+
+In some situations (especially where the library has a permissive licence) it could be useful to consider packaging a complete, batteries-included 'known good' repository, either with the source of all the correct library versions included, or with a script to clone and compile the specific version used, and integrating all the libraries with the build system.
+
+For instance, this was done with the PDB reader.
+
+\rule{\linewidth}{0.2pt}
+
 Write a paper to be understood; to be as clear and helpful as possible to the reader.
@@
 
+\Acrobatmenu{GoBack}{Back}
 \end{document}

### 2020-05-30 documents/paper.tex
More spice
Progress

@@
 \usepackage{hyperref}
+\usepackage{gensymb}
+\usepackage{csquotes}
 
@@
 Please consider all claims with appropriate skepticism.
-
-{\it "You cannot create a VCO that way. It is not easy."}
-{ - An anonymous admirer.}
 
@@
 
-OpenEMS is excellent, with Python bindings, lumped . However, embarassingly, we were not able to resolve all the dependency issues in order to install it.
+\rule{\linewidth}{0.2pt}
+
+OpenEMS is excellent, with Python bindings, some lumped components, and mesh refinement. However, embarassingly, we were not able to resolve all the dependency issues in order to install it.
+
+\rule{\linewidth}{0.2pt}
 
@@
 
-In some situations (especially where the library has a permissive licence) it could be useful to consider packaging a complete, batteries-included 'known good' repository, either with the source of all the correct library versions included, or with a script to clone and compile the specific version used, and integrating all the libraries with the build system.
+In some situations (especially where the library has a permissive licence) perhaps it could be useful to consider packaging a complete, batteries-included 'known good' repository, either with the source of all the correct library versions included, or with a script to clone and compile the specific version used, and integrating all the libraries with the build system.
 
@@
 
+\paragraph{Hall of Hubris} \
+
+Lest our hats stop fitting
+
+\rule{\linewidth}{0.2pt}
+
+An inane remark:
+
+\begin{displayquote}
+We believe once we have the P. Syringae host, we from environmental samples
+\end{displayquote}
+
+Truly the depths of Dunning-Kruger.
+
+\rule{\linewidth}{0.2pt}
+
+An expert and distinguished gentleman that we contacted regarding assistance resolving transients in our microstrip VCO stated the following:
+
+This was a perfectly sensible remark; it is almost always the case that (at X-band, no less!) a custom IC would have been needed to build a VCO.
+
+Also, if taken in the context of a tired, overworked PI getting an unsolicited email from an excessively verbose undergraduate at a different university, I hardly think I would have replied differently.
+
+However, I think this person may have missed out. Learning
+
+So perhaps it is wise to ponder the ideas of fools for skeet; one always learns target practice, if only an example what not to do, and occasionally one learns positively.
+I have often found that I learn greatly from working on the projects of others.
+
+We present this only as a cautionary tale in the hopes that someday I will listen, rather than talk.
+
+\rule{\linewidth}{0.2pt}
+
 \end{multicols}

### 2020-05-30 documents/paper.tex
Upgraded Atom

@@
 
+Alternate methods evaluated, failures:
+
 In production, these could be accomodated by graphite-polymer printed resistors.
@@
 
-However, it seems to neglect the I/V characteristic, so we synthesized the SPICE model using an optimization method [Polyfet 1998].
+NDY However, it seems to neglect the I/V characteristic, so we synthesized the SPICE model using an optimization method [Polyfet 1998].
 
@@
 OpenEMS is excellent, with Python bindings, some lumped components, and mesh refinement. However, embarassingly, we were not able to resolve all the dependency issues in order to install it.
+
+\rule{\linewidth}{0.2pt}
+
+Simulating the oscillator with an AC sim using the manufacturer's S-parameters and QUCS' microstrip approximations [qucs/optimize\_filter\_1] appeared to yield good agreement with experiment.
+The peaks in the feedback voltage simulation corresponded approximately with peaks in the observed spectrum.
+[figures from LO prototype N].
+
+Dips and peaks in varactor tuning were unexpected; and the tuning range was far smaller than expected.
+
+However, it was thought that a transient simulation - to determine how the spectrum actually evolved as the oscillator run - would improve the situation.
+
+QUCS' microstrip models were not yet compatible with transient simulations; and some improved filter designs required simulating coupling between more than two microstrips, which QUCS did not yet support.
+
+\rule{\linewidth}{0.2pt}
+
+Again, inductive biasing in the feedback loop was practically impossible.
+Biasing PiN diodes with a 10kohm resistor, (with 330 ohm safety resistor) one to 48V bias and another through an N-channel mosfet worked fine.
+The oscillator ran fine with a PiN bias of 2.34 mA.
+[LO prototype N].
+Such a high bias voltage was required to get sufficient current through the PiN while remaining delicate with the vfb.
 
@@
 Version control alone isn't quite enough.
-Just having a simulation setup file somewhere in the commit history isn't "discoverable" - that is, you should be able to see what the input and output was without re-running the simulation; and manually taking notes tended to disrupt the flow of testing.
+Just having a simulation setup file somewhere in the commit history isn't "discoverable" - that is, you should be able to see what the input and output was without re-running the simulation.
+
+Manually taking notes tended to disrupt the flow of testing; and in any case, just noting "SIR filter has appropriate phase response" is almost useless. What {\it was} the phase response? Plot it!
 

### 2020-05-30 electronics/simple_fdtd/PCB_extensions.py

@@ -5,26 +5,42 @@ import lxml.etree as etree
 from PIL import Image
 import io
 import math
+from pyevtk.hl import gridToVTK
+from math import pi, ceil
+from scipy.constants import epsilon_0
 
 X = 0
 Y = 1
 Z = 2
 
 class PCB:
-    def __init__(self, name, age):
-        self.name = name
-        self.age = age
+    def __init__(self, cell_size, z_height=10e-3, xy_margin=15, z_margin=15, pml_cells=10):
 
-    def initialize_grid(N_x, N_y, N_z, cell_size, pml_cells):
+        self.grid = None
+        self.cell_size = cell_size
+
+        self.z_height = z_height
+        self.xy_margin = xy_margin
+        self.z_margin = z_margin
+
+        self.pml_cells = pml_cells
+
+        self.ground_plane_z_top = None
+        self.component_plane_z = None
+
+
+    def initialize_grid(self, N_x, N_y, N_z):
         grid = fdtd.Grid(
             (N_x,N_y,N_z),
-            grid_spacing=cell_size,
+            grid_spacing=self.cell_size,
             permittivity=1.0,
             permeability=1.0
         )
 
         fdtd.PML(1e-8, # stability factor
             None)
+
+        pml_cells = self.pml_cells
 
         grid[0:pml_cells, :, :] = fdtd.PML(name="pml_xlow")
         grid[-pml_cells:, :, :] = fdtd.PML(name="pml_xhigh")
@@ -33,24 +49,38 @@ class PCB:
         grid[:, : ,0:pml_cells] = fdtd.PML(name="pml_zlow")
         grid[:, : ,-pml_cells:] = fdtd.PML(name="pml_zhigh")
 
-        return grid
+        self.grid = grid
 
 
-    def create_ground_and_substrate(ground_plane_thickness, permittivity, xy_margin=15, z_margin=15):
+
+    def create_planes(self, ground_plane_thickness, conductor_conductivity):
         '''
         Using thick copper planes only seems to affect the impedance by about 3%.
-        This should be okay as long as
-
+        This should be okay, but might affect interdigital filters etc.
         '''
 
-        N_ground_plane = ceil(ground_plane_thickness / cell_size)
-        grid[xy_margin:-xy_margin, xy_margin:-xy_margin, z_margin:(z_margin+N_ground_plane)]
-                                                            = fdtd.AbsorbingObject(permittivity=1.7**2, conductivity, name="ground_plane")
[…]

### 2020-05-30 electronics/simple_fdtd/test/test_PCB_extensions.py

@@ -4,6 +4,18 @@ from PCB_extensions import *
 
 fdtd.set_backend("torch.cuda.float32")
 
-def test_answer():
-    import_svg_pcb('test/test.svg',0.0002)
+def test_grid_creation():
+    pcb = PCB(0.0002)
+    pcb.initialize_grid_with_svg('test/test.svg')
+    pcb.create_planes(0.032e-3, 6e7)
+    pcb.create_substrate(0.8e-3, 4.4, 0.02, 9e9)
+
+
     # assert
+
+def test_copper_creation():
+    pcb = PCB(0.0002)
+    pcb.initialize_grid_with_svg('test/test.svg')
+    pcb.create_planes(0.032e-3, 6e7)
+    pcb.create_substrate(0.8e-3, 4.4, 0.02, 9e9)
+    pcb.construct_copper_geometry_from_svg('test/test.svg')

### 2020-06-02 electronics/simple_fdtd/PCB_extensions.py
yay

@@ -88,8 +88,7 @@ class PCB:
 
         N_ground_plane = ceil(ground_plane_thickness / self.cell_size)
 
-        # self.grid[self.xy_margin:-self.xy_margin, self.xy_margin:-self.xy_margin, self.z_margin:(self.z_margin+N_ground_plane)] \
-        #                     = fdtd.PECObject(name="ground_plane")
+        #using a copper mask is much faster than an fdtd.object
         self.copper_mask[self.xy_margin:-self.xy_margin, self.xy_margin:-self.xy_margin, self.z_margin:(self.z_margin+N_ground_plane)] = 1
 
         self.ground_plane_z_top = self.z_margin+N_ground_plane
@@ -182,11 +181,12 @@ class PCB:
 
     def compute_all_voltages(self):
         for port in self.component_ports:
-            # port.voltage = e_field_integrate(G, port, self.reference_port)
+            # port.voltage = self.e_field_integrate(port, self.reference_port)
+
+            #since all conductors have zero electric field, this is a reasonable approximation -
+            #
             port.voltage = sum(self.grid.E[port.N_x,port.N_y,self.ground_plane_z_top:self.component_plane_z,Z])*self.cell_size
-            # port.voltage = self.grid.E[port.N_x,port.N_y,self.component_plane_z-1,Z]*self.cell_size
-            # self.grid.E[port.N_x,port.N_y,self.ground_plane_z_top:self.component_plane_z-1] = 0
-            # port.voltage_history.append(port.voltage)
+            port.voltage_history.append(port.voltage)
 
 #permittivity might have to be cubed
 #is there a bug in fdtd/grid/permittivity? Seems like it's not updated unless it's an array
@@ -204,8 +204,6 @@ class PCB:
 
 
     def zero_conductor_fields(self):
-        self.grid.E[self.copper_mask] = 0
-        self.grid.E[self.copper_mask] = 0
         self.grid.E[self.copper_mask] = 0
 
 

### 2020-06-02 electronics/simple_fdtd/simple_FDTD.py

@@ -10,21 +10,14 @@ pcb.create_planes(0.032e-3, 6e7)
 pcb.create_substrate(0.8e-3, 4.4, 0.02, 9e9)
 pcb.construct_copper_geometry_from_svg(0.032e-3, 6e7, 'test/basic_test.svg')
 
+pcb.reference_port = Port(pcb, 0, 0, 0)
+
+
 pcb.component_ports.append(Port(pcb, 0, 11e-3, 11.3e-3))
 pcb.component_ports.append(Port(pcb, 1, 9e-3, 11.3e-3))
 
 dump_step = 20
 for i in range(0,10000):
-
-    # pcb.grid.E[:,:,:,pcb.component_plane_z:pcb.component_plane_z+1] = 0
-
-    # pcb.grid.E[40:60,40:60,pcb.component_plane_z,X] = 0
-    # pcb.grid.E[40:60,40:60,pcb.component_plane_z,Y] = 0
-    # pcb.grid.E[40:60,40:60,pcb.component_plane_z,Z] = 0
-    # pcb.grid.E[40:60,40:60,pcb.ground_plane_z_top-1,X] = 0
-    # pcb.grid.E[40:60,40:60,pcb.ground_plane_z_top-1,Y] = 0
-    # pcb.grid.E[40:60,40:60,pcb.ground_plane_z_top-1,Z] = 0
-    # pcb.grid.E[55,55,pcb.ground_plane_z_top:pcb.component_plane_z,Z] = 100.0 / (4.0*pcb.cell_size)
 
     pcb.grid.update_E()
 
@@ -40,5 +33,3 @@ for i in range(0,10000):
     print(pcb.grid.time_passed)
     print(pcb.component_ports[0].voltage)
     print(pcb.component_ports[1].voltage)
-    # print(sum(pcb.grid.E[50,50,pcb.ground_plane_z_top:pcb.component_plane_z,Z])*pcb.cell_size)
-    # print(sum(pcb.grid.E[55,55,pcb.ground_plane_z_top:pcb.component_plane_z,Z])*pcb.cell_size)

### 2020-06-04 documents/paper.tex
yay
Yay! oscillation!

@@
 \usepackage{csquotes}
+
+\usepackage{graphicx}
+\graphicspath{ {../media/} }
 
@@
 	\item gprMax for FDTD EM simulation
-	\item KiCAD, wcalc, scikit-rf
+	\item KiCAD, wcalc, scikit-rf, ngspice
 	\end{itemize}
@@
 
+The authors of the original paper on
+
 Professor Shahramian's excellent video blog {\it The Signal Path} inspired this work.
@@
 
+CEL did not supply a SPICE model for the GaAs FET device used in early prototypes. A FET was chosen because the a gate is ostensibly easier to bias than a base.
+
 [Steenput 1999] has an interesting analytic method to synthesize a SPICE model suitable for a transient simulations from S-parameter measurements using negative resistances.
+However, this neglects the I/V characteristic.
 
-NDY However, it seems to neglect the I/V characteristic, so we synthesized the SPICE model using an optimization method [Polyfet 1998].
+[Polyfet 1998] describes a simple optimization method to synthesize a SPICE model; it would be useful.
+
+However, since a Si-process device would be required for mass production anyhow, we decided to accept the difficulty in biasing and use a bipolar transistor.
 
@@
 
-Dips and peaks in varactor tuning were unexpected; and the tuning range was far smaller than expected.
+However, unexpected dips and peaks were found with varactor tuning; and the tuning range was far smaller than expected.
 
-However, it was thought that a transient simulation - to determine how the spectrum actually evolved as the oscillator run - would improve the situation.
+A filter design with apparently ideal phase and frequency properties was designed using this process, but again poor agreement was found with experiment.
 
-QUCS' microstrip models were not yet compatible with transient simulations; and some improved filter designs required simulating coupling between more than two microstrips, which QUCS did not yet support.
+\hspace*{-0.7cm}   \includegraphics[scale=0.6]{LO_2_pole_test.png}
+
+Because we lacked a spectrum analyzer that could monitor the higher poles of the filter until the bootstrap LO was designed.
+
+It was thought that a transient simulation - to determine how the spectrum actually evolved - would improve the situation.
+
+QUCS' microstrip models are not yet compatible with transient simulations; and some improved filter designs required simulating coupling between more than two microstrips, which QUCS did not yet support natively.
+Coupling can be emulated by introducing discrete coupling capacitors; but
 
@@
 
-Again, inductive biasing in the feedback loop was practically impossible.
+Again, inductive choke biasing in the feedback loop was practically impossible.
 Biasing PiN diodes with a 10kohm resistor, (with 330 ohm safety resistor) one to 48V bias and another through an N-channel mosfet worked fine.
@@
 \rule{\linewidth}{0.2pt}
+
+Conductors are represented by zeroing all components of the electric field in those regions.
+
+There are many different possible source geometries, each introducing their own distortions.
+
+It's possible to link SPICE and FDTD in two main ways
+
+\rule{\linewidth}{0.2pt}
+
+Bandpass filters can be designed by first designing a low-pass filter prototype (usually Chebychev) (or, in our case, using reference filter component tables), and then transforming this low-pass into a band-pass.
+[Hunter 2001] is an excellent overview of this process, with many design examples for different filter topologies.
+
+The coupling coefficient between two low-pass filters determines the band-pass bandwidth.[Hui 2012]
+
+[Hunter 2001] also describes an analytical method to create a filter with the precise group delay - phase shift versus frequency - required for stable oscillation.
+However, simultaneously compensating for the group delay introduced by the amplifier itself (nearly 180 degrees over the frequency range for the CEL part) seemed complex.
 

### 2020-06-05 documents/paper.tex
Varactor checks out

@@
 
+\end{multicols}
+
+\clearpage
+
 \paragraph{\textbf{Time dependence}}\
@@
 
-To determine the effectiveness against airborne particles, and to minimize the power required in a dwelling phased-array beam, we must first establish the required duration of exposure.
+The effectiveness against airborne particles, and to minimize the power required in a dwelling phased-array beam, we must first establish the required duration of exposure.
 
@@
 Such a mechanism could perhaps extend the exposure required to break the capsid or membrane.
-Other mechanisms could include some sort of lipid denaturation, requiring an absolute amount of energy absorption to break or twist bonds before the envelope fractures.
+Other mechanisms could include some sort of lipid denaturation, requiring an absolute amount of energy absorption to break or twist bonds and modify the properties before the envelope fractures.
 
 {\color{red}  \} }
+
+\clearpage
+\begin{multicols}{1}
+{\Large Biology}\\
+
+\paragraph{\textbf{Centrifugal microfluidics}}\
+
+The field of centrifugal microfluidics is accelerating.
+
+Many CD microfluidics systems use standard CD molding techniques for the channels and machining techniques, using either acrylic or silicone.
+The turbidity sensor is most sensitive if the plastic is clear.
+Sterilization does not seem to be discussed.
+
+Polypropylene is the ideal material, being almost indefinitely autoclavable. It is quite difficult to machine.
 

### 2020-06-06 documents/paper.tex
Review of safety

@@
 \usepackage{csquotes}
+\usepackage{amsmath}
+\usepackage{fontawesome}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \clearpage
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \paragraph{\textbf{Time dependence}}\
@@
 \clearpage
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{multicols}{1}
+{\Large Safety}\\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Because this is an ostensibly novel and niche mechanism, it may behoove us to breifly review the biological basis for the safety limits set by standards organizations.
+
+For instance, we could question why we might not see such resonances in bodily tissues.
+After all, approximately similar nanoscopic structures exist in humans; for instance, nuclear pores (120 nm) and the famous microtubules (10x50 nm).
+
+While from which epidemiological data could be derived. \footnote{The cloud service [scite.ai] was irreplaceable during this. It's like a mirror to an alternate universe where literature made sense.}
+
+[ICNIRP 2020], [ICNIRP 2019], [Adair]
+
+The existence of resonance modes in DNA has been a matter of some contention; but the best data demonstrates 
+quite conclusively
+
+\begin{center}
+\begin{tabular}{|l|l|l|}
+\hline
+ [Manikowska 1979] & 9.4 GHz pulsed &  \\ \hline
+\end{tabular}
+\end{center}
+
+\begin{autem}
+	{\it Evidence against safety}\
+
+	\begin{itemize}
+	  \item {[Manikowska 1979] / 9.4 GHz pulsed / 2 weeks\
+
+	   this is a particularly concerning paper. [Servantie 1989] discusses the (somewhat }
+
+	  \item {[Sagripanti 1986] find DNA damage at $8.5 mW/g$ at 2.55 GHz, without undue heating of the solvent.
+	  	}
+
+	\end{itemize}\
+
+\end{autem}
+
+\begin{toolchain}
+	{\it Evidence for safety:}\
+	\begin{itemize}
+	  \item
+ 	\end{itemize}\
+\end{toolchain}
+
+{\it Please contact the author if you are aware of other salient research, or have a different interpretation.}
+
+Adair, 2002:
+
+The conclusion that there can be no microwave resonances in DNA in water is in accord with the results of measurements in three different laboratories ([Gabriel et al., 1987] [Foster et al., 1987] using techniques designed to detect resonances with amplitudes less than 1/20th of that reported by [Edwards et al.
+(1984)].
+
+ Evidence of such microwave absorption resonances has been reported ([Edwards et al., 1984] [Grundler and Keilman, 1983], but these results have not been replicated ([Gabriel et al., 1987] [Foster et al., 1987]
+
+> We extend analyses that suggest that the damping of the vibratory motion by biological fluids severely restrict such possibilities[].
+
+It is interesting that this analysis would seem to disagree with the viral resonance seen by Yang.
+
+[Foster (1987)] find that the DNA resonance found by [Edwards (1987)] was well below the experimental error, given the latter's setup. The Foster paper is of excellent quality.
+
+ What is that in $mw/cm^2$?
+
+Via the :
+
+> This is typically described as a function of a relevant dosimetric quantity.
+For example, below about 6 GHz, where EMFs penetrate deep into tissue (and thus require depth to be considered), it is useful to describe this in terms of “specific energy absorption rate” (SAR), which is the power absorbed per unit mass (W kg−1).
+Conversely, above 6 GHz, where EMFs are absorbed more superficially (making depth less relevant), it is useful to describe exposure in terms of the density of absorbed power over area(W m−2), which we refer to as “absorbed power density”.
+> 
+> Similarly, as there is no evidence that continuous (e.g., sinusoidal) and discontinuous (e.g., pulsed) EMFs result in different biological effects (Kowalczuk et al.
+2010; Juutilainen et al.
+2011), no theoretical distinction has been made between these types of exposure (all exposures have been considered empirically in terms of whether they adversely affect health)
+
+Juutilainen references a wealth of empirical data. Vijayalaxmi (2006) is particularly helpful:
+
+Chemeris discusses 8.8 GHz  pulses, and finds no effect:
+
+> We found no data on genotoxic effects of HPPP EMF at peak SAR exceeding hundreds of megawatts per kilogram and at average SAR, which does not induce dramatic overheating of the exposed objects.
+At such powerful EMF, peak electric field intensity in the exposed biological objects is close to maximally achievable, i.e.
+near breakdown electric field intensity.
+It would be reasonable to expect specific genotoxic effects of RF EMF under such extreme conditions.
+
+\footnote{``{\it{For example, below about 6 GHz, where EMFs penetrate deep into tissue (and thus require depth to be considered), it is useful to describe this in terms of “specific energy absorption rate” (SAR), which is the power absorbed per unit mass $(W/kg)$.
+Conversely, above 6 GHz, where EMFs are absorbed more superficially (making depth less relevant), it is useful to describe exposure in terms of the density of absorbed power over area $W/m^2$, which we refer to as “absorbed power density”}}'' [ICNIRP 2020 \faExternalLink]}
+
+\end{multicols}
+
+\clearpage
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{multicols}{1}
 {\Large Biology}\\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \clearpage
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{multicols}{1}
+{\Large Modes of application}\\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
+\paragraph{\textbf{Personal 'electromagnetic mask'}}\
+
+We demonstrate this form factor because, superficially, there are fewer people than there are places.
+Even with judicious use of phased-arrays, power-combining, etc, each transistor can only reasonably sterilize approx.
+$ 1 \text{ m}^3 $.
+
+On the other hand, a personal device may present issues with compliance\footnote{that sounds evil, but it really isn't} and production volume.
+
+\paragraph{\textbf{Direct treatments}}\
+
+[Hand 1982] $E_{mag}=1/e$ (13.5\% power density) skin\footnote{electromagnetic skin, not tissue skin}\footnote{well, both, I suppose.} depth of 10 GHz microwave is approximately:
+
+\begin{center}
+\begin{tabular}{|l|l|l|}
+\hline
+F=10 GHz          & Dry tissue & Wet tissue \\ \hline
+Penetration depth & 30 mm      & $\sim$5 mm \\ \hline
+\end{tabular}
+\end{center}
+
+SARS is found widely distributed throughout the most desirable organs [Ding 2004], shielded by an average of 4 cm of chest wall [Schroeder 2013]; so safe external treatment of the body is unlikely.
+
+However, destruction of lung tissue appears to be the 	[Yuan 2019]
+
+\paragraph{\textbf{More fanciful concepts}}\
+
+Many weather radar systems operate in these X-band frequency ranges.
+
+It is relatively easy to produce megawatts of power at these frequency ranges using Klystrons.
+
+\end{multicols}
+
+\clearpage
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{multicols}{1}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \clearpage
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+{\Large Mass production}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-{\Large Mass production}
+If this 'electromagnetic mask' form is the ideal (not nearly ), a minimum of 5 GaAs or SiGe:C transistors will be required.
+
+There are, for instance, 1 million hospital beds in the U.S. [AHA 2018].
+
+It is difficult to determine the supply capacity for these modern semiconductor processes. A few fermi est
+
+GaAs MMIC market of \$2.2 Bn USD / random sample of MMIC prices =
+
+3e9 wifi connected devices produced each year.
+
+The largest RFID plants can produce
+
+The techniques and equipment required to produce these are non-trivial. SiGe:C, for instance, requires,
 
 \clearpage
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \paragraph{Acknowledgements}\
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 This paper is not novel enough to deserve this chapter, but those to be acknowledged are.
@@
 
+\rule{\linewidth}{0.2pt}
+
+NGSPICE's KSPICE coupled transmission lines require the capacitance and inductance per unit length in Maxwell matrix form, rather than the physical $C_{even}$/$L_{even}$ (each line's capacitance and inductance to ground) and $_{odd}$ (between elements) form provided by tools like wcalc.
+"matrix not positive definite".
+[Schutt-Aine] discusses this; we reproduce here for convienience.
+
+\[ L_{11} = L_{22} = L_{even}  \]
+\[ L_{12} = L_{21} = L_{odd}  \]
+\[ C_{11} = C_{22} = C_{even}+C_{odd}  \]
+\[ C_{12} = C_{21} {\it{(unused)}} = -C_{odd}  \]
+
+\rule{\linewidth}{0.2pt}
+
 \label{para}
@@
 Manually taking notes tended to disrupt the flow of testing; and in any case, just noting "SIR filter has appropriate phase response" is almost useless. What {\it was} the phase response? Plot it!
+
+Sacred, recipy, Sumatra
 

### 2020-06-07 documents/paper.tex
More lit review

@@
 
-\footnote{footnotes working fine}
-
 This work was prepared by an undergraduate and has not been peer-reviewed.
@@
 
-Testing was only performed with a surrogate bacteriophage. All experiments must be repeated with Inf. A and then SARS-NCoV-2.
+Testing was only performed with a surrogate bacteriophage. All experiments must be repeated with SARS-NCoV-2.
 
@@
 	\item Analytical expression assuming homogenous sphere for microwave absorption cross-section
-	\item Experimental data from microwave cuvette to 
+	\item Experimental absorption data from microwave cuvette -> 
 	\item COMSOL finite-element for illustration
@@
 
-In contrast to chemical inactivation, where the time dependence appears to be dominated by viscous fluid dynamic effects [Hirose 2017], or UV inactivation, where a certain dose of photons must be absorbed, one might expect RF
+In contrast to chemical inactivation, where the time dependence appears to be dominated by viscous fluid dynamic effects [Hirose 2017], or UV inactivation, where a certain quantized dose of photons must be absorbed, we expected RF to act instantaneously.
 
@@
 
+Contrary to Far UV, where ozone production.
+
 {\color{red}  \} }
+
+The medium (not specified in the paper, but ATCC recommends that MDCK cells are grown in Eagle's MEM + 10\% fetal bovine serum).
+
+[IEEE C95.1-2019]
+
+[IEEE C95.1-2005]
+
+\footnote{All values have been converted to $W/m^2$ to avoid confusion.}
 
@@
 Because this is an ostensibly novel and niche mechanism, it may behoove us to breifly review the biological basis for the safety limits set by standards organizations.
+\footnote{The idea of biological microwave resonances appears to have originated in [Frohlich 1980].}
 
-For instance, we could question why we might not see such resonances in bodily tissues.
-After all, approximately similar nanoscopic structures exist in humans; for instance, nuclear pores (120 nm) and the famous microtubules (10x50 nm).
+Contrary to some [Hardell 2017] reports, we do not find the FCC and ICNIRP to be significantly affected by special interest groups; their rationales appear to be transparent. 
+\footnote{[FCC-19-126A1] an FCC memorandum wherein the FCC tells groups to respectfully screw themselves no fewer than three times: ''Similarly, IEEE-ICES urges the Commission to
+adopt a higher SAR exposure limit of 2 W/kg averaged over 10 g.
+[snip] We are not persuaded that the IEC standard should be adopted at this time.", "Medtronic and the AAMI-CRMD recommend a more relaxed threshold of 20 mW.
+We decline to increase the 1-mW threshold.".
+Things heating up at the Microwave Safety fandom.}
 
-While from which epidemiological data could be derived. \footnote{The cloud service [scite.ai] was irreplaceable during this. It's like a mirror to an alternate universe where literature made sense.}
+There are some 20,000 papers on the topic of microwave safety, with solid in vitro, in vivo and epidemiological evidence of safety in the 2.4 GHz and 5.8 GHz bands.
 
-[ICNIRP 2020], [ICNIRP 2019], [Adair]
+However, "There are limited experimental human data upon which to set limits on exposures above 6 GHz" [Chan 2019].
+The frequency ranges above 6 GHz appear to be set primarily by assuming purely thermal mechanisms and introducing a substantial safety factor of 20 or 50x.
 
-The existence of resonance modes in DNA has been a matter of some contention; but the best data demonstrates 
-quite conclusively
+The IEEE standard which the flagship paper [Yang 2015] references [IEEE C95.1–2005] was recently overhauled [IEEE C95.1-2019] with new metrics. The
 
-\begin{center}
-\begin{tabular}{|l|l|l|}
-\hline
- [Manikowska 1979] & 9.4 GHz pulsed &  \\ \hline
-\end{tabular}
-\end{center}
+For instance, we wondered why we might not see such resonances in bodily tissues.
+Approximately similar nanoscopic structures exist in humans; for instance, nuclear pores (120 nm) and the famous microtubules (10x50 nm).
 
-\begin{autem}
-	{\it Evidence against safety}\
+While from which epidemiological data could be derived.\footnote{The cloud service [scite.ai] was irreplaceable during this. It's like a mirror to an alternate universe where literature made sense.}
 
-	\begin{itemize}
-	  \item {[Manikowska 1979] / 9.4 GHz pulsed / 2 weeks\
+What we find is a messy affair. Biology is hard.
 
-	   this is a particularly concerning paper. [Servantie 1989] discusses the (somewhat }
+\rule{\linewidth}{0.2pt}
 
-	  \item {[Sagripanti 1986] find DNA damage at $8.5 mW/g$ at 2.55 GHz, without undue heating of the solvent.
-	  	}
+[Adair 2002] demonstrate theoretically that acoustic resonances are not possible in biological solvents.
+All resonance modes are strongly overdamped by the surrounding solvent, and no amplitude amplification can take place.
 
-	\end{itemize}\
+This analysis would seem to disagree with the viral resonance apparently conclusively demonstrated by [Yang 2015]; the PCR result seems especially inarguable. We cannot explain this discrepancy.
 
-\end{autem}
+[Liu 2009] cite [Edwards, Swicord 1984], saying: "It was proposed that a hydration layer surrounding DNA molecules could lower the viscoelastic transition
+frequency, raise the quality factor of confined acoustic vibrations, and result in a microwave resonant absorption".
+But [Adair 2002]'s [Foster 1987] seem to quite conclusively put the kibosh on that idea, demonstrating no resonances and showing previous results to be an artifact of the measurement equipment.
 
-\begin{toolchain}
-	{\it Evidence for safety:}\
-	\begin{itemize}
-	  \item
- 	\end{itemize}\
-\end{toolchain}
+However, [Sagripanti 1986] find DNA damage at $8.5 mW/g$ at 2.55 GHz, with only 0.8C heating of the solvent.
+
+\paragraph{[Manikowska 1979]} \
+
+9.4 GHz pulsed / in vivo, mouse, $0.1-10 \text{mW}/\text{m}^2$ over the whole body for 2 weeks.
+
+This is a particularly concerning result, especially given their $p<0.001$. [Servantie 1989] discusses the (admittedly circuituious) route by which birth defects could occur.
+
+Work by [Manikowska 1985] in the 2.4 GHz range has been contradicted [Beechey 1986], but the 9 GHz range does not appear to have been repeated.
+
+\rule{\linewidth}{0.2pt}
+
+More modern research does not tend to agree with these concerns.
+As cited by [ICNIRP 2020]'s excellent literature review, [Vijayalaxmi 2006] expose lymphocyte blood cells to pulsed 8.2 GHz radiation for 2 hours at an average power of $10 \text{mW/cm}^2$.
+They find no change in any of the parameters measured, including various chromosomal parameters.
+They further discuss previous results.
+
+We must defer to health experts for interpretation of these data, and will not attempt to draw a conclusion.
+
+It would be ideal to have an expert review our claims before publication. However, we tenatively make the following claims:
 
 {\it Please contact the author if you are aware of other salient research, or have a different interpretation.}
-
-Adair, 2002:
-
-The conclusion that there can be no microwave resonances in DNA in water is in accord with the results of measurements in three different laboratories ([Gabriel et al., 1987] [Foster et al., 1987] using techniques designed to detect resonances with amplitudes less than 1/20th of that reported by [Edwards et al.
-(1984)].
 
@@
 > We extend analyses that suggest that the damping of the vibratory motion by biological fluids severely restrict such possibilities[].
-
-It is interesting that this analysis would seem to disagree with the viral resonance seen by Yang.
 
@@
 
-> This is typically described as a function of a relevant dosimetric quantity.
-For example, below about 6 GHz, where EMFs penetrate deep into tissue (and thus require depth to be considered), it is useful to describe this in terms of “specific energy absorption rate” (SAR), which is the power absorbed per unit mass (W kg−1).
-Conversely, above 6 GHz, where EMFs are absorbed more superficially (making depth less relevant), it is useful to describe exposure in terms of the density of absorbed power over area(W m−2), which we refer to as “absorbed power density”.
 > 
@@
 
+\rule{\linewidth}{0.2pt}
+
+There seems to be a discrepancy between [Yang 2015] and our reading of C95.1-2005. This is very likely a misreading on our part, and so calls into question our understanding of the standard.
+
+They say: "Based on the IEEE Microwave Safety Standard, the spatial averaged value of the power density in air in open public space shall not exceed the equivalent power density of $100(f/3)^{1/5} \text{ W/m}^2$ at frequencies between 3 and 96GHz ($f$ is in GHz).
+This corresponds to $115 \text{ W}/\text{m}^2$ at 6 GHz".
+The 115 W @ 6 GHz value corresponds to this equation with a coefficient of 100.
+
+The only reference to a 3 - 96 GHz limit we can find is that of Section 4.6, {\it Relaxation of the power density MPEs for localized exposures}, where the equation is $200 (f/3)^{1/5} \text{ W/m}^2$ [IEEE C95.1-2005]; but this is for controlled, occupational exposures only, referring to Table 8.
+For Table 9, general public, the equation is $18.56 (f)^{0.699} \text{ W/m}^2$, or $64.93 \text{ W}/\text{m}^2$ @ 6 GHz.
+
+We don't think this changes the substance of [Yang 2015]'s paper, if it is an error; it just means the mechanism is more useful for healthcare workers who acknowledge the risks.
+
+Different versions of the IEEE standard have used equations of equivalent form but with different coefficients [Wu 2015]; it is possible that we have retrieved the wrong standard.
+
+\rule{\linewidth}{0.2pt}
+
 CEL did not supply a SPICE model for the GaAs FET device used in early prototypes. A FET was chosen because the a gate is ostensibly easier to bias than a base.

### 2020-06-10 documents/paper.tex
Some more documentation

@@
 \title{On the application of microwave acoustic resonant viral inactivation
-\thanks{I would be delighted to include any criticisms or comments anyone may have; preferably leave them on the GitHub issues page, or email therobotist@gmail.com, @0xDBFB7 on Twitter, or irc.0xDBFB7.com:6667 \#covid.}}
+\thanks{I would be delighted to include any criticisms or comments anyone may have, both on substance and comprehensibility; preferably leave them on the GitHub issues page, or email therobotist@gmail.com, @0xDBFB7 on Twitter, or irc.0xDBFB7.com:6667 \#covid.}}
 \date{May 2020}
@@
 
-Testing was only performed with a surrogate bacteriophage. All experiments must be repeated with SARS-NCoV-2.
+Though the original research used Inf. A, our testing was only performed with a surrogate bacteriophage. All experiments must be repeated with SARS-NCoV-2.
+
+Additionally, other mechanisms may produce superior results and should be evaluated in the same context. Recent data on far UVC [Buonanno 2017] indicate safety.
 
@@
 
-Contrary to Far UV, where ozone production.
-
 {\color{red}  \} }
@@
 Because this is an ostensibly novel and niche mechanism, it may behoove us to breifly review the biological basis for the safety limits set by standards organizations.
-\footnote{The idea of biological microwave resonances appears to have originated in [Frohlich 1980].}
+\footnote{The idea of biological microwave resonances appears to have originated in [Frohlich 1968, 1980].}
 
@@
 
-There are some 20,000 papers on the topic of microwave safety, with solid in vitro, in vivo and epidemiological evidence of safety in the 2.4 GHz and 5.8 GHz bands.
-
-However, "There are limited experimental human data upon which to set limits on exposures above 6 GHz" [Chan 2019].
-The frequency ranges above 6 GHz appear to be set primarily by assuming purely thermal mechanisms and introducing a substantial safety factor of 20 or 50x.
-
-The IEEE standard which the flagship paper [Yang 2015] references [IEEE C95.1–2005] was recently overhauled [IEEE C95.1-2019] with new metrics. The
+The IEEE standard which the flagship paper [Yang 2015] references [IEEE C95.1-2005] was recently overhauled [IEEE C95.1-2019] with new metrics.
 
@@
 
-[Adair 2002] demonstrate theoretically that acoustic resonances are not possible in biological solvents.
+There are some 20,000 papers on the topic of RF safety, with solid in vitro, in vivo and epidemiological evidence of safety in the 2.4 GHz and 5.8 GHz bands.
+
+However, "There are limited experimental human data upon which to set limits on exposures above 6 GHz" [Chan 2019]. Only 2\% of the above papers are on frequencies $>6$ GHz [Vijayalaxmi 2018].
+
+In addition, what data remains in this category is of varying quality.
+
+As has been starkly demonstrated in the recent hydroxychloroquine contradictions [Gautret 2020] [Geleris 2020], biological research must be essentially perfect to have any meaning at all.
+
+[Vijayalaxmi 2018] is a remarkable meta-analysis of in vitro data.
+They synthesize a quality score, rating bindedness, sham controls, dosimetry, and sample size.
+Quality was inversely, monotonically related to the effect size.
+An example of the subtle effects that can call into question superfically reasonable results are [
+
+They additionally find a publication bias of incredible magnitude in the positive (harm) direction in this field, further degrading the usefulness of statistical analyeses.
+
+An example of a relevant study that they grade as "quality 1" [Karaca 2011].
+This study's conclusion is that However, in figure 5, one can see that only 1 out of 11 genes tested had a statistically significant difference in expression.
+Given the N=6 cultures,
+
+\rule{\linewidth}{0.2pt}
+
+[Adair 2002] demonstrate theoretically that acoustic resonances are, in general, highly unlikely in biological solvents, primarily focusing on DNA.
 All resonance modes are strongly overdamped by the surrounding solvent, and no amplitude amplification can take place.
 
-This analysis would seem to disagree with the viral resonance apparently conclusively demonstrated by [Yang 2015]; the PCR result seems especially inarguable. We cannot explain this discrepancy.
+This analysis would seem to disagree with the viral resonance apparently conclusively demonstrated by [Yang 2015] - the PCR result seems especially inarguable.
+This could be explained by the large charge on the virus compared to the molecules analyzed in Adair.
+[Yang 2015] find a charge of order $10^7 e$, whereas Adair analyzes a very different regime, "assume coupling to the field through single charges q = e at each end".
 
@@
 frequency, raise the quality factor of confined acoustic vibrations, and result in a microwave resonant absorption".
-But [Adair 2002]'s [Foster 1987] seem to quite conclusively put the kibosh on that idea, demonstrating no resonances and showing previous results to be an artifact of the measurement equipment.
+But [Adair 2002]'s [Foster 1987] seem to quite conclusively put the kibosh on that idea, demonstrating no resonances in DNA with 20x higher precision and showing previous results to be an artifact of the measurement equipment.
 
-However, [Sagripanti 1986] find DNA damage at $8.5 mW/g$ at 2.55 GHz, with only 0.8C heating of the solvent.
+The supplemental material to [Vijayalaxmi 2018] has a table of studies on this topic. High-quality research in-vitro concurs with.
 
@@
 
-9.4 GHz pulsed / in vivo, mouse, $0.1-10 \text{mW}/\text{m}^2$ over the whole body for 2 weeks.
+9.4 GHz pulsed / in vivo, mouse, $0.1-10 \text{mW}/\text{m}^2$ over the whole body for 2 weeks. N=16.
 
@@
 
-More modern research does not tend to agree with these concerns.
-As cited by [ICNIRP 2020]'s excellent literature review, [Vijayalaxmi 2006] expose lymphocyte blood cells to pulsed 8.2 GHz radiation for 2 hours at an average power of $10 \text{mW/cm}^2$.
+More modern research [Juutilainen 2011], [Chemeris], [Vijayalaxmi 2006],  does not tend to agree with these concerns.
+As cited by [ICNIRP 2020]'s excellent literature review, expose lymphocyte blood cells to 8 ns pulsed 8.2 GHz radiation for 2 hours at an average power of $10 \text{mW/cm}^2$.
 They find no change in any of the parameters measured, including various chromosomal parameters.
@@
 
-We must defer to health experts for interpretation of these data, and will not attempt to draw a conclusion.
+\rule{\linewidth}{0.2pt}
 
-It would be ideal to have an expert review our claims before publication. However, we tenatively make the following claims:
+In the frequency range of interest, there seems to be good-quality in-vitro evidence using lymphocytes of lack of harm.
+We are not aware of any high-quality in vivo or epidemeological data from which useful conclusions can be drawn.
+
+We must defer to health experts for interpretation of these data.
+
+\rule{\linewidth}{0.2pt}
 
 {\it Please contact the author if you are aware of other salient research, or have a different interpretation.}
-
-Evidence of such microwave absorption resonances has been reported ([Edwards et al., 1984] [Grundler and Keilman, 1983], but these results have not been replicated ([Gabriel et al., 1987] [Foster et al., 1987]
-
-> We extend analyses that suggest that the damping of the vibratory motion by biological fluids severely restrict such possibilities[].
-
-[Foster (1987)] find that the DNA resonance found by [Edwards (1987)] was well below the experimental error, given the latter's setup. The Foster paper is of excellent quality.
-
- What is that in $mw/cm^2$?
-
-Via the :
-
-> 
-> Similarly, as there is no evidence that continuous (e.g., sinusoidal) and discontinuous (e.g., pulsed) EMFs result in different biological effects (Kowalczuk et al.
-2010; Juutilainen et al.
-2011), no theoretical distinction has been made between these types of exposure (all exposures have been considered empirically in terms of whether they adversely affect health)
-
-Juutilainen references a wealth of empirical data. Vijayalaxmi (2006) is particularly helpful:
-
-Chemeris discusses 8.8 GHz  pulses, and finds no effect:
-
-> We found no data on genotoxic effects of HPPP EMF at peak SAR exceeding hundreds of megawatts per kilogram and at average SAR, which does not induce dramatic overheating of the exposed objects.
-At such powerful EMF, peak electric field intensity in the exposed biological objects is close to maximally achievable, i.e.
-near breakdown electric field intensity.
-It would be reasonable to expect specific genotoxic effects of RF EMF under such extreme conditions.
 
@@
 
-[Hand 1982] $E_{mag}=1/e$ (13.5\% power density) skin\footnote{electromagnetic skin, not tissue skin}\footnote{well, both, I suppose.} depth of 10 GHz microwave is approximately:
+[Hand 1982] $E_{mag}=1/e$ (13.5\% power density) skin\footnote{electromagnetic skin, not tissue skin}\footnote{well, both, I suppose.} depth is approximately:
 
@@
 F=10 GHz          & Dry tissue & Wet tissue \\ \hline
-Penetration depth & 30 mm      & $\sim$5 mm \\ \hline
+Penetration depth & 30 mm      & 5 mm \\ \hline
 \end{tabular}
@@
 
-However, destruction of lung tissue appears to be the 	[Yuan 2019]
+However, destruction of lung tissue appears to be the primary cause of death via SARS [Nicholls 2006].
+
+A minimally-invasive bronchoscopic technique may be effective when mounted on a modified brochoscope and periodically inserted into the main bronchus, a la [Yuan 2019].
+
+The bronchi are less than 2 mm thick [Theriault 2018] and the lungs themselves are only on the order of 
+7 mm thick [Chekan 2016].
+
+Further study is required to validate this method.
 
@@
 For ease of design and simulation, a device with Touchstone S-parameters and SPICE files is greatly preferable.
+
+As a result of our gross incompetence, the oscillator was designed via an inane, roundabout, and fiendishly tedious manner, and our description of this technique only contributes to the field by being suitable for a dartboard; our analysis can only hold water when combined with paper mache; and a lesser invertebrate in posession of a copy of Microwave Oscillator Design would have accomplished the task faster.
+
+Designing an oscillator of this type in one step with a few kindergarten equations appears to be well within the reach of modern network analytical techniques.
+Genetic algorithms are quite well matched to this problem, and many commercial software packages are  [computer microwave design book].
+
+In addition, the design of wideband feedback-loop VCOs is a relatively well-explored field, and many reference designs exist.
+
+The key sticking point - which we missed - seems to be that at these scales, using microstrip design techniques, the parasitics of any possible filter structure are so large that the small change in inductance that varactors can provide cannot tune the circuit by any meaningful amount.
+
+"Using the lead inductances of the bipolar transistor and varactors provides the required value of the base inductance".
+
+Indeed, [Tsuru 2008]'s "tuned circuit" in Fig 8 is, in fact, just the varactors, plus an almost invisible high-impedance line.
+
+We began experimentally by building a scaled version of [Mueller 2008]'s active antenna in microstrip, using a CEL mosfet.
+
+This immediately oscillated perfectly.
+
+Several analytical filter design methods were
+
 %
@@
 With 0.79 mm FR4 substrate and 0.2 mm (8 mil) wide traces, the maximum impedance achievable was about 115 ohms, which did not appear to be sufficient as an RF choke.
+Use of defected grounds can increase inductance, but this was not evaluated.
 
-If suitably high-impedance traces are not available, a common technique is to use a quarter-wavelength line (approximately 6 mm long with the above parameters) terminated with a stub to produce a virtual short or open circuit [Seo 2007].
+If suitably high-impedance traces are not available, a common technique is to use a quarter-wavelength line (approximately 6 mm long with the above parameters at 8 GHz) terminated with a stub to produce a virtual short or open circuit [Seo 2007].
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+{\Large Molecular dynamics simulation}\\
+\begin{multicols}{1}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+aa
+
+\end{multicols}
+
+\clearpage
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+{\Large Optical centrifuge polarization chirp}\\
+\begin{multicols}{1}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+aa
+
+\end{multicols}
+
+\clearpage
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \paragraph{Acknowledgements}\
@@
 
-Professor Shahramian's excellent video blog {\it The Signal Path} inspired this work.
+Professor Shahramian's excellent video blog {\it The Signal Path} inspired this work. Alex Dainis' videos on sterile technique were also useful.
 
@@
 This corresponds to $115 \text{ W}/\text{m}^2$ at 6 GHz".
-The 115 W @ 6 GHz value corresponds to this equation with a coefficient of 100.
+The 115 W @ 6 GHz value correctly corresponds to this equation with a coefficient of 100.
 
@@
 
-We don't think this changes the substance of [Yang 2015]'s paper, if it is an error; it just means the mechanism is more useful for healthcare workers who acknowledge the risks.
+We don't think this changes the substance of [Yang 2015]'s paper, if it is an error; the relaxed localized exposure is probably the correct threshold to use, and it just means the mechanism is more useful for healthcare workers who acknowledge the risks.
 
@@
 
-Simulating the oscillator with an AC sim using the manufacturer's S-parameters and QUCS' microstrip approximations [qucs/optimize\_filter\_1] appeared to yield good agreement with experiment.
-The peaks in the feedback voltage simulation corresponded approximately with peaks in the observed spectrum.
+Simulating the oscillator with an AC sim using the manufacturer's S-parameters and QUCS' microstrip approximations [qucs/optimize\_filter\_1] intially appeared to yield good agreement with experiment.
+Peaks in the feedback voltage simulation corresponded approximately with peaks in the observed spectrum.
 [figures from LO prototype N].
@@
 
-A filter design with apparently ideal phase and frequency properties was designed using this process, but again poor agreement was found with experiment.
+A feedback loop filter design with apparently ideal phase and frequency properties was designed using this process; but the behavior of this oscillator did not correspond to reality.
 
@@
 
-Because we lacked a spectrum analyzer that could monitor the higher poles of the filter until the bootstrap LO was designed.
+Because we lacked a spectrum analyzer that could monitor the higher poles of the filter until the bootstrap LO was designed, we had to rely on in-silico analyeses.
 
@@
 
-QUCS' microstrip models are not yet compatible with transient simulations; and some improved filter designs required simulating coupling between more than two microstrips, which QUCS did not yet support natively.
-Coupling can be emulated by introducing discrete coupling capacitors; but
+As of 0.0.20, QUCS' microstrip models are not yet compatible with transient simulations; and some improved filter designs required simulating coupling between more than two microstrips, which QUCS did not yet support natively.
+Coupling can be emulated by introducing discrete coupling capacitors
+
+Transient simulations with ngspice matched experiment far more closely.
 
@@
 
-It's possible to link SPICE and FDTD in two main ways
+There are many ways of linking SPICE and FDTD.
 
@@
 However, simultaneously compensating for the group delay introduced by the amplifier itself (nearly 180 degrees over the frequency range for the CEL part) seemed complex.
+
+Phase shift can be introduced either via a length of microstrip, or a high-pass/low-pass filter [Microwave101].
+Adding a fixed microstrip line restricts the tuning range, however, and the filter inevitably affects the frequency response.
 
@@
 
-It may be helpful to treat simulations very similarly to IRL experiments.
+It may be helpful to think of simulations very similarly to IRL experiments.
 
-This is obvious to all compentent, but when rapidly iteratively testing with simulations, it may be helpful to automatically save a package with images of all the components (schematics, graphs) of each distinct test.
-Including a picture with a webcam of the assembled board is also helpful.
+A simulation is just a universe in a bottle that you can examine more closely; as with real-world, you can learn much from observation, but
+
+But this need for documentation conflicts with the rapid, iterative cycle necessary for productivity.
+
+This is obvious to all compentent, but when rapidly iteratively testing with simulations, it may be helpful to automatically save a package with images of all the components (schematics, graphs, input files) of each distinct test.
+
+For comparison to experiment, having a webcam take an image of the assembled board is also helpful.
 
 Version control alone isn't quite enough.
-Just having a simulation setup file somewhere in the commit history isn't "discoverable" - that is, you should be able to see what the input and output was without re-running the simulation.
+Just having a simulation setup file somewhere in the commit history isn't "discoverable" - that is, you must be able to see what the input and output was without re-running the simulation.
 
@@
 
-Sacred, recipy, Sumatra
+Software such as Sumatra, Sacred, recipy, and others. In our case, we used eLabFTW's elabapy bindings.
 
@@
 
-For instance, this was done with the PDB reader.
+For instance, this was done with the PDB reader in the OpenMM wrapper and JAMES.
+
+\rule{\linewidth}{0.2pt}
+
+There's also a very neat thing that seems to be common in computational biology, but which doesn't seem popular in other fields.
+After an algorithm or software tool is written (and the source published seperately), a simple CGI frontend is written around it and hosted on the university's servers.
+eLNemo and the CHARMMing web interface are advanced examples of this.
+This way, anyone with an input file can get results without futzing around with installation.
+
+The computational biologists have beat us at our own game.
 
@@
 Write a paper to be understood; to be as clear and helpful as possible to the reader.
+
+\rule{\linewidth}{0.2pt}
+
+We have always encountered wasting extreme amounts of time on subtle assembly mistakes in hardware prototypes.
+
+In one example, many hours were spent because the enamel insulation on a bodge wire had not burned off completely in the solder joint, leading to a high-impedance connection.
+
+The same has occurred in previous projects; in one example, many days were spent debugging software to fix an apparently slow hardware interrupt, which ended up being the result of a poor solder paste stencil leading to a hidden high-impedance connection to a leadless package.
+
+Many failures are perhaps the result of carelessness in modification and a lack of inspection; but others would only have been found by a 100\% electrical test.
+
+If flying-probe or bed-of-nails tests can be made sufficiently rapid and closely coupled with the existing toolchain,
+
+In {\it 2001: A space odyssey}, an automated system is shown guiding the troubleshooting of an assembly, apparently generating a fault tree of all the
+
+\rule{\linewidth}{0.2pt}
 
@@
 
-We present this only as a cautionary tale in the hopes that someday I will listen, rather than talk.
+We present this only as a cautionary tale in the hopes that someday I will listen.
 

### 2020-06-10 electronics/simple_fdtd/PCB_extensions.py

@@ -21,6 +21,14 @@ import ngspyce
 from fdtd.backend import NumpyBackend
 from fdtd.backend import backend as bd
 
+
+from numpy import array
+
+# from pykicad.pcb import *
+# from pykicad.module import * unfortunately, got an error immediately with this. probably for a different version of kicad.
+
+
+
 X = 0
 Y = 1
 Z = 2
@@ -72,13 +80,13 @@ class PCB:
         self.times = []
 
 
-    def initialize_grid(self, N_x, N_y, N_z):
+    def initialize_grid(self, N_x, N_y, N_z, courant_number=None):
         grid = fdtd.Grid(
             (N_x,N_y,N_z),
             grid_spacing=self.cell_size,
             permittivity=1.0,
-            permeability=1.0)
-            # courant_number = 0.2        )
+            permeability=1.0,
+            courant_number = courant_number)
 
         fdtd.PML(1e-8, # stability factor
             None)
@@ -169,31 +177,6 @@ class PCB:
                     #                     = fdtd.PECObject(name=None)
 
 
-    # class LumpedComponent(object):
-    # """
-    #
-    # See "The use of SPICE lumped circuits as sub-grid models for FDTD analysis", doi:10.1109/75.289516
-    # which deals with lumped elements of a single-cell size, and
-
-    # "Incorporating non-linear lumped elements in FDTD: the equivalent source method", Jason Mix
-    # http://ecee.colorado.edu/microwave/docs/publications/1999/IJNM_JMjdMPM_99.pdf
-    # which deals with objects of arbitrary size.
-    #
-    # You can use this 'equivalent source method' either by line-integrating the currents around a conductor
-    # and setting the electric field, or by line-integrating the voltage and setting the magnetic field.
-    #
-    # I chose the latter because it seems to make more sense to set a voltage initial-condition in SPICE than a current.
-    #
-    # 1. Normal electric field update.
-    # 2. Obtain terminal voltages by an electric field line integration from one port to another.
-    # 3. Normal magnetic field update.
-    # 4. Obtain the lumped currents from the voltages - either via SPICE or via analytic expressions for each component
-    # 5. Set H along a contour enclosing the conductor to net_current / Lc
-    # 6. ...
-    # 7. Profit!
-    #
-    #
-    # """
 
     def compute_all_voltages(self):
         for port in self.component_ports:
@@ -356,5 +339,12 @@ class PCB:
     def save_voltages(self):
[…]

### 2020-06-12 documents/paper.tex
Adaptive timestep apparently working

@@
 
-For instance, we wondered why we might not see such resonances in bodily tissues.
-Approximately similar nanoscopic structures exist in humans; for instance, nuclear pores (120 nm) and the famous microtubules (10x50 nm).
+For instance, it is reasonable to wonder why we might not see such resonances in bodily tissues.
+Approximately similar nanoscopic structures exist in humans, such as nuclear pores (120 nm) and the famous microtubules (10x50 nm).
 
@@
 frequency, raise the quality factor of confined acoustic vibrations, and result in a microwave resonant absorption".
-But [Adair 2002]'s [Foster 1987] seem to quite conclusively put the kibosh on that idea, demonstrating no resonances in DNA with 20x higher precision and showing previous results to be an artifact of the measurement equipment.
+
+But [Adair 2002]'s [Foster 1987] seem to quite conclusively put the kibosh on that idea, demonstrating no resonances in DNA with 20x higher precision than previous work, showing previous results to be an artifact of the measurement equipment.
 
@@
 
-We demonstrate this form factor because, superficially, there are fewer people than there are places.
-Even with judicious use of phased-arrays, power-combining, etc, each transistor can only reasonably sterilize approx.
-$ 1 \text{ m}^3 $.
+Even with judicious use of phased-arrays, power-combining, etc, each transistor can only reasonably sterilize approx. $ 1 \text{ m}^3 $.
+
+We therefore demonstrate this form factor because, superficially, there are fewer people than there are places.
 
@@
 
-It is relatively easy to produce megawatts of power at these frequency ranges using Klystrons.
+It is relatively easy to produce megawatts of power at these frequency ranges using Klystrons. Airborne phased-arrays.
 
@@
 
+It is commonly claimed that FR4 is a 'slow' substrate, and that the high loss tangent of ~0.02 makes it unsuitable for microwave systems.
+
+However, with this PCB substrate, a loss of only 0.026 dB/mm on signals of minimum 0 dBm.
+We are also only minimally concerned with $S_{11}$ reflections, noise, or spurs (viruses do not have a discriminating palate), so precise impedance control is not required; the wideband VCO sweep accomodates for any variations in resonant frequency due to wide manufacturing tolerances.
+
 As a result of our gross incompetence, the oscillator was designed via an inane, roundabout, and fiendishly tedious manner, and our description of this technique only contributes to the field by being suitable for a dartboard; our analysis can only hold water when combined with paper mache; and a lesser invertebrate in posession of a copy of Microwave Oscillator Design would have accomplished the task faster.
@@
 Genetic algorithms are quite well matched to this problem, and many commercial software packages are  [computer microwave design book].
+
+Initially,
+
+Not having a good analytical understanding, we resorted to using a purely computational method.
 
@@
 
-We began experimentally by building a scaled version of [Mueller 2008]'s active antenna in microstrip, using a CEL mosfet.
+We began experimentally by building a scaled version of [Mueller 2008]'s active antenna on FR4, using a CEL mosfet.
 
@@
 
+Figures are not forthcoming,
+
+Given the supply difficulties of comparatively simple materials such as Tyvek at pandemic scales, it is difficult to imagine that RF semiconductor production can be immediately re-tasked and scaled to this degree.
+
+\paragraph{\textbf{Vacuum RF triode}}\
+
+One concern is the large filament heater power, which prevents the use of low-cost button cells for power.
+Use of cold-cathode field-emitter arrays would alleviate this issue, but at the cost of complexity.
+
+Small tungsten incandescent lights are available down to 0.05 watts. With a suitable high-efficiency cathode coating, a pulsed heater power of less than 0.02
+
 \clearpage
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 This paper is not novel enough to deserve this chapter, but those to be acknowledged are.
 
-The authors of the original paper on
+The authors of the original papers deserve the credit for this entire work; it is rare that such a is served on a silver platter.
 
-Professor Shahramian's excellent video blog {\it The Signal Path} inspired this work. Alex Dainis' videos on sterile technique were also useful.
+Professor Shahramian's excellent video blog {\it The Signal Path} inspired this work.
+
+Dr. Dainis' videos on microbiological technique were also useful.
 
@@
 
-Chiefly among the enablers are of course my parents, Doris and Brian, without which this work would have been done by someone else[] - but who also supported this work financially.
+Chiefly among the enablers are of course my parents, Doris and Brian, without which this work would have been done by someone else[] - but who also supported this work financially. Brian
 

### 2020-06-17 documents/paper.tex
Teensy

@@
 
-Additionally, other mechanisms may produce superior results and should be evaluated in the same context. Recent data on far UVC [Buonanno 2017] indicate safety.
+Additionally, other sterilization techniques may produce superior results and should be evaluated in the same context. Data on far UVC [Buonanno 2017] indicate safety.
 
@@
 {\color{red}  \} }
-
-The medium (not specified in the paper, but ATCC recommends that MDCK cells are grown in Eagle's MEM + 10\% fetal bovine serum).
-
-[IEEE C95.1-2019]
-
-[IEEE C95.1-2005]
 
@@
 
-On the other hand, a personal device may present issues with compliance\footnote{that sounds evil, but it really isn't} and production volume.
+On the other hand, a personal device may present issues with participation and production volume.
 
@@
 	\begin{itemize}
-	\item QUCS 0.0.20 for AC simulation, with python-qucs and scipy's 'basinhopper' for optimization
+	\item Failed oscillator feedback-loop optimization toolchain: QUCS 0.0.20 + python-qucs + scipy's 'basinhopper'
+	\item Successful A slightly modified ngspice + ngspyce + pyEVTK
 	\item gprMax for FDTD EM simulation
@@
 %
+
+The oscillator is a 'wideband double-tuned varactor VCO', based almost verbatim on [Tsuru 2008] and the reference design in Figure 8.36, p378 of [Grebennikov 2007].
+
+The rest of the papers in the bibliography were highly enlightening regarding the principles of microwave oscillator design.
+
+This topology of oscillator worked marvellously on essentially the first try.
+
+The process by which we failed miserably to design our own oscillator topology is detailed in the supplemental.
+
 The following properties: P1dB
@@
 
-However, with this PCB substrate, a loss of only 0.026 dB/mm on signals of minimum 0 dBm.
-We are also only minimally concerned with $S_{11}$ reflections, noise, or spurs (viruses do not have a discriminating palate), so precise impedance control is not required; the wideband VCO sweep accomodates for any variations in resonant frequency due to wide manufacturing tolerances.
+However, with this PCB substrate, the expected loss of only 0.026 dB/mm on signals of minimum 0 dBm is patently acceptable.
+As viruses do not have a discriminating palate, we are also only minimally concerned with $S_{11}$ reflections, noise, or spurs, so precise impedance control is not required; the wideband VCO sweep accomodates for any variations in resonant frequency due to wide manufacturing tolerances.
 
@@
 
-The key sticking point - which we missed - seems to be that at these scales, using microstrip design techniques, the parasitics of any possible filter structure are so large that the small change in inductance that varactors can provide cannot tune the circuit by any meaningful amount.
+The key sticking point - which we missed - seems to be that at these scales, using microstrip design techniques, the parasitics of any possible filter structure are so large that the small change in impedance that varactors can provide cannot tune the circuit by any meaningful amount.
 
@@
 
+Optimizing S-parameter simulations of the feedback loop and negative-resistance device did not produce an accurate picture of the oscillator.
+While the phase and frequency response appeared to be excellent, the transient response painted a different picture:
+
+[gnuplot transient sim here]
+
+The complete transient simulation matched reality very closely.
+
 This immediately oscillated perfectly.
@@
 Several analytical filter design methods were
+
+This is apparently known as a "double-tuned" wideband.
 
@@
 %
-Without this element, proximity effects from nearby flesh, startup instablity, mode-hopping, and de-tuning were all encountered.
+
+With large feedback-loop structures, such as PiN switched lines, proximity effects from nearby flesh would detune the oscillator to a s
 
@@
 The parasitic inductance of common varactors appears to become problematic at these frequencies (but not for non-wideband use).
+
+\paragraph{\textbf{Spacing}}\
+
+FDTD results still yielded some coupling at 2 mm isolation.
+
+\paragraph{\textbf{Via stitching}}\
+
+Rather than the almost universal technique of via stitching components immediately to the ground plane (a tedious process with our prototyping setup), a large ground pour on the component layer was used, similar to [Hunter?
+combline].
+Since we use microstrip rather than coplanar waveguide,
+
+Since the ground plane does not participate in the DC bias at all, no vias are required in the final device.
+This means that the comparatively slow drilling, electroless strike and electroplating steps are unneccesary for this device.
 
@@
 
-aa
-
 \end{multicols}
@@
 
+Special thanks to all the people - most equally capable of writing this paper if provided the opportunity - who work menial shifts at the component suppliers that remained open that were so critical.
 Hopfstader be damned; despite the name below the abstract, this paper is of course entirely the result of circumstance and luck.
-Any comparable dimwit to the author would have accomplished the same under the same conditions.
 
-It is infinitely to be regretted that such equally capable people were stuck in warehouses doing menial 15-hour shifts or assembling smartphones.
-
-Chiefly among the enablers are of course my parents, Doris and Brian, without which this work would have been done by someone else[] - but who also supported this work financially. Brian
+Chiefly among the enablers are of course my parents, Doris and Brian, without whom this work would have been done by someone else, and who also supported this work financially.
 
@@
 
-The only reference to a 3 - 96 GHz limit we can find is that of Section 4.6, {\it Relaxation of the power density MPEs for localized exposures}, where the equation is $200 (f/3)^{1/5} \text{ W/m}^2$ [IEEE C95.1-2005]; but this is for controlled, occupational exposures only, referring to Table 8.
+The only reference to a 3 - 96 GHz limit we can find is that of Section 4.6, {\it Relaxation of the power density MPEs for localized exposures}, where the equation is $200 (f/3)^{1/5} \text{ W/m}^2$ [IEEE C95.1-2005], for controlled occupational exposures, referring to Table 8.
 For Table 9, general public, the equation is $18.56 (f)^{0.699} \text{ W/m}^2$, or $64.93 \text{ W}/\text{m}^2$ @ 6 GHz.
 
-We don't think this changes the substance of [Yang 2015]'s paper, if it is an error; the relaxed localized exposure is probably the correct threshold to use, and it just means the mechanism is more useful for healthcare workers who acknowledge the risks.
+Different versions of the IEEE standard have used equations of equivalent form but with different coefficients [Wu 2015]; it is possible that we have retrieved the wrong standard.
 
-Different versions of the IEEE standard have used equations of equivalent form but with different coefficients [Wu 2015]; it is possible that we have retrieved the wrong standard.
+In any case, this doesn't change the substance of [Yang 2015]'s paper; the relaxed localized exposure is probably the correct threshold to use, and it just means the mechanism is more useful for healthcare workers who acknowledge the risks.
 
@@
 Again, inductive choke biasing in the feedback loop was practically impossible.
-Biasing PiN diodes with a 10kohm resistor, (with 330 ohm safety resistor) one to 48V bias and another through an N-channel mosfet worked fine.
+Biasing PiN diodes with a 10kohm resistor, (with 330 ohm safety resistor) one to 48V bias and another through an 2N7002P N-channel mosfet worked fine.
+
 The oscillator ran fine with a PiN bias of 2.34 mA.
 [LO prototype N].
-Such a high bias voltage was required to get sufficient current through the PiN while remaining delicate with the vfb.
+A high bias voltage of 48V was required to get sufficient current through the two 10K resistors and the PiN diode to obtain a low impedance while remaining delicate with the vfb.
+
+The PiN diode used has a resting resistance of 500 ohms, 5 ohms at 2 mA and 2 ohms at ??.
+
+48V is a little tight on the 50V rated voltage of our DC blocking capacitors.
+
+Each activated PiN diode should be biased separately, since putting 2x 2 mA through 20K would take an impractical 80V.
 
@@
 Software such as Sumatra, Sacred, recipy, and others. In our case, we used eLabFTW's elabapy bindings.
+
+\rule{\linewidth}{0.2pt}
+
+It is far easier to use existing, well-characterized reference designs verbatim than to modify
 

### 2020-06-17 documents/paper.tex
More teensy
Re-organized yet again, company too

@@
 
-We began experimentally by building a scaled version of [Mueller 2008]'s active antenna on FR4, using a CEL mosfet.
-
-Optimizing S-parameter simulations of the feedback loop and negative-resistance device did not produce an accurate picture of the oscillator.
-While the phase and frequency response appeared to be excellent, the transient response painted a different picture:
-
-[gnuplot transient sim here]
-
-The complete transient simulation matched reality very closely.
-
-This immediately oscillated perfectly.
-
 Several analytical filter design methods were
@@
 
+\end{multicols}
+
 \clearpage
@@
 \clearpage
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 {\Large Captain's Log, Supplemental}\\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-CEL did not supply a SPICE model for the GaAs FET device used in early prototypes. A FET was chosen because the a gate is ostensibly easier to bias than a base.
+CEL did not supply a SPICE model for the GaAs FET device used in early prototypes. A FET was originally because a gate is ostensibly easier to bias than a base; but this turned out to be unfounded.
 
@@
 
-[Polyfet 1998] describes a simple optimization method to synthesize a SPICE model; it would be useful.
-
-However, since a Si-process device would be required for mass production anyhow, we decided to accept the difficulty in biasing and use a bipolar transistor.
+[Polyfet 1998] describes a simple optimization method to synthesize a SPICE model for an active device, and CEL appnote provides some details for GaAs devices.
 
@@
 
-Simulating the oscillator with an AC sim using the manufacturer's S-parameters and QUCS' microstrip approximations [qucs/optimize\_filter\_1] intially appeared to yield good agreement with experiment.
+We began experimentally by building a scaled version of [Mueller 2008]'s active antenna crudely with copper tape, using a CEL [] FET.
+
+We then manually tried a number of filter designs, using the manufacturer's S-parameters and QUCS' microstrip approximations.
+This intially appeared to yield good agreement with experiment.
 Peaks in the feedback voltage simulation corresponded approximately with peaks in the observed spectrum.
@@
 
-However, unexpected dips and peaks were found with varactor tuning; and the tuning range was far smaller than expected.
+A crude, inane, and extremely disorganized trial-and-error procedure was performed for many weeks.
+A wide variety of analytical methods for filter design were attempted, but simultaneously obtaining the correct phase shift and frequency response was somewhat difficult.
+The parasitic inductance of the varactors always seemed to destroy our most perfect creations.
 
-A feedback loop filter design with apparently ideal phase and frequency properties was designed using this process; but the behavior of this oscillator did not correspond to reality.
+An SIR filter has the added advantage of confusing epidemiologists greatly.
 
-\hspace*{-0.7cm}   \includegraphics[scale=0.6]{LO_2_pole_test.png}
+Eventually, QUCS, zonca/python-qucs, and scipy's basinhopper was used with the cost function somewhat similar to that described in [Kaplevich]:
 
-Because we lacked a spectrum analyzer that could monitor the higher poles of the filter until the bootstrap LO was designed, we had to rely on in-silico analyeses.
+\begin{verbatim}
+    freq_coeff = 1
+    phase_coeff = 1.5
+    ratio_coeff = 0.5
+    insertion_loss_coeff = 0.2
+
+    frequency_cost = freq_coeff * (abs(desired_center_frequency-fb_peak_frequencies[0])/1e9)
+    phase_cost = phase_coeff * abs(1.0 - phase_at_peak)
+    ratio_cost = ratio_coeff * fb_peak_ratio
+    insertion_loss_cost = insertion_loss_coeff*(1.0 - fb_peak_values[0])
+    cost = frequency_cost + phase_cost + fb_peak_ratio + insertion_loss_cost
+\end{verbatim}
+
+Optimizing first for the high frequency, fixing the inductor and microstrip values, and then optimizing for the varactor values at the low frequency.
+
+This produced a seemingly acceptable feedback loop:
+
+\includegraphics[scale=1]{LO_2_pole_test.png}
+
+However, when this was built, varactor tuning performance was abysmal, with hops and peaks; and the tuning range was far smaller than expected.
 
@@
 As of 0.0.20, QUCS' microstrip models are not yet compatible with transient simulations; and some improved filter designs required simulating coupling between more than two microstrips, which QUCS did not yet support natively.
-Coupling can be emulated by introducing discrete coupling capacitors
+
+\includegraphics[scale=0.5]{3d_spectrum_2.png}
+
+The complete transient simulation matched reality very closely.
+
+Because we lacked a spectrum analyzer that could monitor the higher poles of the filter until the bootstrap LO was designed, we had to rely on in-silico analyeses.
 
@@
 
-In some situations (especially where the library has a permissive licence) perhaps it could be useful to consider packaging a complete, batteries-included 'known good' repository, either with the source of all the correct library versions included, or with a script to clone and compile the specific version used, and integrating all the libraries with the build system.
+In some situations (especially where the library has a permissive licence) perhaps it could be useful to consider packaging a complete, batteries-included 'known good' repository, either with the source of all the correct library versions included, or with a script to clone and compile the specific version used, integrating all the libraries with the build system.
 
@@
 
-In one example, many hours were spent because the enamel insulation on a bodge wire had not burned off completely in the solder joint, leading to a high-impedance connection.
+In one example in this project, many hours were wasted because the enamel insulation on a bodge wire had not burned off completely in the solder joint, leading to a high-impedance connection.
 
@@
 In {\it 2001: A space odyssey}, an automated system is shown guiding the troubleshooting of an assembly, apparently generating a fault tree of all the
+
+Boundary-scan features might really help
+
+\rule{\linewidth}{0.2pt}
+
+The ability to almost immediately compare simulation to experiment was quite important.
 
@@
 
-\end{multicols}
+%\end{multicols}
 

### 2020-06-17 firmware/eppendoofus/test/main.cpp

@@ -1,0 +1,17 @@
+// #pragma GCC diagnostic push
+// #pragma GCC diagnostic ignored "-Wall"
+//#include "WProgram.h"
+// #pragma GCC diagnostic pop
+
+
+
+int main(void)
+{
+	// pinMode(13, OUTPUT);
+	// while (1) {
+	// 	digitalWriteFast(13, HIGH);
+	// 	delay(100);
+	// 	digitalWriteFast(13, LOW);
+	// 	delay(100);
+	// }
+}

### 2020-06-18 firmware/eppendoofus/test_hw/main.cpp
Mocking

@@ -3,8 +3,8 @@
 
 
 
-int main(void)
-{
+int main(void){
+    
     Serial.begin(115200);
 
     run_all();

### 2020-06-19 firmware/eppendoofus/src/VCO_driver.hpp
Disorganized

@@ -1,13 +1,12 @@
 #include "defines.hpp"
 
-
-#ifndef MOCK_INCLUDES
+#ifdef MOCK_INCLUDES
 
 #include "mocks.hpp"
 
 #else
 
-
+#include "WProgram.h"
 
 #endif
 
@@ -15,7 +14,6 @@
 
 /*-------------------------------------------*/
 
-#define
 
 
 /*-------------------------------------------*/

### 2020-06-19 firmware/eppendoofus/src/defines.hpp

@@ -1,3 +1,10 @@
 
 
 #define CORE_CLOCK_FREQ 120e6
+
+#define DAC_write analogWrite
+
+#define CORE_SUPPLY_VOLTAGE 3.3
+
+#define ANALOG_WRITE_RESOLUTION 12
+//mandated by DAC

### 2020-06-19 firmware/eppendoofus/test_hw/main.cpp

@@ -7,8 +7,16 @@ int main(void){
 
     Serial.begin(115200);
 
-    run_all();
 
-    
+
+    while(true){
+        for(int i = 1000; i < 3000; i++){
+
+        }
+        yield();
+    }
+    // run_all();
+
+
 
 }

### 2020-06-19 firmware/eppendoofus/test_hw/quick_checks.cpp

@@ -1,7 +1,10 @@
-void run_all(){
-    analog_write_res_access();
-}
 
-void analog_write_res_access(){
-    Serial.print(analog_write_res);
-}
+
+// 
+// void run_all(){
+//     analog_write_res_access();
+// }
+//
+// void analog_write_res_access(){
+//     Serial.print(analog_write_res);
+// }

### 2020-06-19 electronics/simple_fdtd/U_patch_antenna_designer.py
Antenna design

@@ -1,0 +1,63 @@
+from PCB_extensions import *
+
+import time
+import os
+
+import copy
+# fdtd.set_backend("torch.cuda.HalfTensor")
+fdtd.set_backend("torch.cuda.float32")
+# fdtd.set_backend("numpy")
+
+import matplotlib.pyplot as plt
+
+#Polycarb. permittivity @ 10 GHz: 2.9 [10.6028/jres.071C.014] - conductivity is very low, no need for absorb.
+#Water permittivity @ 10 GHz: 65 - use AbsorbingObject
+
+#A good reference design on 1.6 mm FR4 is 10.1109/ATSIP.2016.7523197 [Werfelli 2016]
+
+pcb = PCB(0.0001)
+pcb.initialize_grid(0.001/pcb.grid_spacing, 0.001/pcb.grid_spacing, 0.001/pcb.grid_spacing)
+pcb.create_planes(0.032e-3, 6e7)
+pcb.create_substrate(0.8e-3, 4.4, 0.02, 9e9)
+
+
+
+def create_patch_antenna(patch_width, patch_length):
+
+
+def create_U_patch_antenna(patch_width, patch_length, slot_length, slot_width, feed_x_position):
+    # U-patch antenna from 10.1109/LAWP.2007.914122.
+    MICROSTRIP_FEED_WIDTH = 1.5e-3
+
+
+def compute_patch_dimensions():
+
+print_step = 50
+
+dump_step = 1000
+i = 0
+clock_time_before = 0
+sim_time_before = 0
+
+end_time = 500e-12
+
+while(pcb.time < end_time):
+
+    pcb.FDTD_step()
+    pcb.compute_all_voltages()
+
+
+
+    pcb.apply_all_currents()
+
+
+    for port in pcb.component_ports:
+        print(port.SPICE_net, port.voltage, port.current)
+
+    if(i % dump_step == 0):
+        pcb.dump_to_vtk('dumps/test',i)
+
+
+
+for port in pcb.component_ports:
+    np.savetxt("data/"+port.SPICE_net+".csv", np.array(port.voltage_history).reshape(-1, 1), delimiter=",",fmt='%10.5f')

### 2020-06-22 documents/paper.tex
Mocking
Paper fixes
Disorganized
Antenna design
faster sim

@@
 \usepackage{fontawesome}
+\usepackage{orcidlink}
 
@@
 \null\begin{tabular}[t]{l@{}}
-  {Daniel Correia} \\
+  {Daniel Correia}\ \orcidlink{0000-0002-9353-0216}  \\
   \textit{York University}
@@
 
-We extend this landmark work rather trivially by:
+We extend this landmark work rather trivially by:\\
 
@@
   \item Showing that the deviation from the expected theshold could be explained by variance in the
+
 \end{itemize}
+
+{Perhaps notable that a completely free and open-source toolchain was used for the entire project, including FDTD microwave antenna optimization. This work can be replicated with \$500 in equipment.}
+
 \end{abstract}
 
-This work was prepared by an undergraduate and has not been peer-reviewed.
+\begin{autem}
+	{\large  \it autem} \\
 
-Additionally, the author has no prior experience with either biology or microwave design.
+	This work was prepared by an undergraduate and has not been peer-reviewed. Additionally, the author has no prior experience with either biology or microwave design. \\
 
-Though the original research used Inf. A, our testing was only performed with a surrogate bacteriophage. All experiments must be repeated with SARS-NCoV-2.
+	While our study is very simple, biology is of such complexity that a tremendous amount of care must be taken before any conclusion can be drawn at all.
+It is not likely that we have taken sufficient care.\\
 
-Additionally, other sterilization techniques may produce superior results and should be evaluated in the same context. Data on far UVC [Buonanno 2017] indicate safety.
+	Though the original research used Inf. A, our testing was only performed with a surrogate bacteriophage. All experiments must be repeated with SARS-NCoV-2. \\
+
+	Additionally, other sterilization techniques may produce superior results and should be evaluated in the same context. Data on far UV [Buonanno 2017] indicate safety.\\
 
 	Please consider all claims with appropriate skepticism.
+
+\end{autem}
 
@@
 
+\includegraphics[scale=0.5]{cells.png}
+
 Contrary to some [Hardell 2017] reports, we do not find the FCC and ICNIRP to be significantly affected by special interest groups; their rationales appear to be transparent. 
@@
 Things heating up at the Microwave Safety fandom.}
-
-The IEEE standard which the flagship paper [Yang 2015] references [IEEE C95.1-2005] was recently overhauled [IEEE C95.1-2019] with new metrics.
 
@@
 As has been starkly demonstrated in the recent hydroxychloroquine contradictions [Gautret 2020] [Geleris 2020], biological research must be essentially perfect to have any meaning at all.
+
+The IEEE standard which the flagship paper [Yang 2015] references [IEEE C95.1-2005] was recently overhauled [IEEE C95.1-2019] with new metrics.
 
@@
 
+Thanks to L.H. for wisdom regarding this project.
+
 Special thanks to all the people - most equally capable of writing this paper if provided the opportunity - who work menial shifts at the component suppliers that remained open that were so critical.
@@
 
+In practice, the timestep required to obtain convergence in particularly tight corners of the SPICE simulation can drop to 1e-20, which is far below the Courant limit of the FDTD simulation.
+To eek out a bit more performance, a simple adaptive-timestep technique from [ a ] is used; we simply set the timestep so that the maximum voltage deviation from the non-FDTD portion is less than some threshold.
+
+\rule{\linewidth}{0.2pt}
+
+A similar mismatch exists for FFT methods, but in the other direction.
+The courant limit often demands fine timesteps, but since each FFT bin is $ f_bin = n_bin * (1 / (N_simulation * dt)) $ , the majority of the frequency points exist into the hundreds or thousands of GHz, leaving no resolution in the low-frequency domain of interest unless $N_simulation$ is extremely large.
+
+\rule{\linewidth}{0.2pt}
+
+\rule{\linewidth}{0.2pt}
+
 \label{para}

### 2020-06-22 documents/paper.tex
Oh yeah, antenna impedance

@@
 In practice, the timestep required to obtain convergence in particularly tight corners of the SPICE simulation can drop to 1e-20, which is far below the Courant limit of the FDTD simulation.
-To eek out a bit more performance, a simple adaptive-timestep technique from [ a ] is used; we simply set the timestep so that the maximum voltage deviation from the non-FDTD portion is less than some threshold.
+To eek out a bit more performance, a simple adaptive-timestep technique from [ a ] is used; we simply set the timestep so that the maximum change in voltage per timestep from the non-FDTD portion is less than some threshold.
 
@@
 
-A similar mismatch exists for FFT methods, but in the other direction.
-The courant limit often demands fine timesteps, but since each FFT bin is $ f_bin = n_bin * (1 / (N_simulation * dt)) $ , the majority of the frequency points exist into the hundreds or thousands of GHz, leaving no resolution in the low-frequency domain of interest unless $N_simulation$ is extremely large.
+The frequency impedance of an antenna can be determined by applying a gaussian pulse to a hard voltage source on the feedline, running the simulation until the transients have all died out while logging the voltage and current at each timestep, and then taking the fourier transform of the voltage and current.
+This is much faster and
+
+However, a similar mismatch to the SPICE exists for FFT methods, but in the other direction.
+The courant limit often demands fine timesteps, but since each FFT bin is $ f_bin = n_bin * (1 / (N_simulation * dt)) $ , the majority of the FFT bins exist into the hundreds or thousands of GHz, leaving no resolution in the low-frequency domain of interest unless $N_simulation$ is extremely large - even if all the transients in the simulation have died down, you still have to keep the sim running to make the FFT happy!
+
+There's more than enough 'information entropy' in 2000 FDTD points for most antennas. But you need some 30,000 points to get 10 bins below 20 GHz!
+
+There are a few methods of changing the FFT bin size artificially, which [Bi 1992] reviews. You can "use a manual fourier integration over the frequency region of interest".
+
+But, in a personally staggering turn of events which will presumably be familiar to statisticans and preposterous to everyone else, a far simpler method is to {\it discard} 95\% of the data!
+Re-sampling some fraction of the current
+
+An equally simple method that seemed to produce better results in our case is to {\it pad }
+
+It is important to remember to normalize the gaussian pulse, or else numerical noise will be introduced.
+
+Though uneven dt FFTs exist, the time step can be constant here .
 
@@
 It is far easier to use existing, well-characterized reference designs verbatim than to modify
+
+\rule{\linewidth}{0.2pt}
+
+When rapidly testing data analyses which aren't really conducive to unit testing, I previously used to run the whole simulation, look at the analysis, re-run the sim, etc.
+
+This is slow. I often don't change the input parameters for the sim, but just the analysis. However, there's often a large amount of state to persist to disk.
+
+Saving the entire session with 'dill' is very helpful.
+
+\rule{\linewidth}{0.2pt}
+
+Software opacity is evil.
 

### 2020-06-22 documents/paper.tex
???

@@
 
-It is important to remember to normalize the gaussian pulse, or else numerical noise will be introduced.
+It is important to remember to normalize the gaussian pulse, or else numerical noise will be introduced. The precise magnitude is not important - [Luebbers 1992/1991] use 100v, others use 1v, etc.
 
@@
 
+A step impulse (1 first timestep, 0 otherwise) can also be used, though the performance is almost unusable worse.
+
 \rule{\linewidth}{0.2pt}
+
+The impedance of a microstrip antenna varies with position on its plane. Probe feeds that couple a microstrip to a specific point are often used.
 

### 2020-06-24 documents/paper.tex
YAAAAAAAAAY

@@
 
-Even with judicious use of phased-arrays, power-combining, etc, each transistor can only reasonably sterilize approx. $ 1 \text{ m}^3 $.
+Even with judicious use of phased-arrays, spatial power-combining, etc, each transistor can only reasonably sterilize approx. $ 1 \text{ m}^3 $.
 
@@
 
-A minimally-invasive bronchoscopic technique may be effective when mounted on a modified brochoscope and periodically inserted into the main bronchus, a la [Yuan 2019].
+A minimally-invasive bronchoscopic technique may be effective when mounted on a modified brochoscope and periodically inserted into the main bronchus, as demonstrated by [Yuan 2019].
 
@@
 
-Many weather radar systems operate in these X-band frequency ranges.
+Many systems operate in these X-band frequency ranges; and precision
 
-It is relatively easy to produce megawatts of power at these frequency ranges using Klystrons. Airborne phased-arrays.
+It is relatively easy to produce megawatts of power at these frequency ranges using Klystrons.
+
+Existing marine, weather, and aviation radar systems often use the X-band; depending on the focusing power
 
@@
 
-With large feedback-loop structures, such as PiN switched lines, proximity effects from nearby flesh would detune the oscillator to a s
+With large feedback-loop structures, such as long PiN-switched phasing lines, proximity effects from nearby flesh would detune the oscillator significantly.
 
@@
 Thanks to L.H. for wisdom regarding this project.
+
+Thanks to P.B and H.P. for tolerating ramblings and M. for the hug.
 
@@
 
-The frequency impedance of an antenna can be determined by applying a gaussian pulse to a hard voltage source on the feedline, running the simulation until the transients have all died out while logging the voltage and current at each timestep, and then taking the fourier transform of the voltage and current.
-This is much faster and
+Originally tried
 
-However, a similar mismatch to the SPICE exists for FFT methods, but in the other direction.
-The courant limit often demands fine timesteps, but since each FFT bin is $ f_bin = n_bin * (1 / (N_simulation * dt)) $ , the majority of the FFT bins exist into the hundreds or thousands of GHz, leaving no resolution in the low-frequency domain of interest unless $N_simulation$ is extremely large - even if all the transients in the simulation have died down, you still have to keep the sim running to make the FFT happy!
+The frequency impedance of an antenna can be determined by:
+
+\begin{itemize}
+  \item Applying a gaussian pulse to a hard voltage source on the feedline
+  \item Running the simulation until the transients have all died out below some threshold, while logging the source voltage and current at each timestep
+
+  \item Taking the fourier transform of the (real) excitation voltage and current (producing a complex result, mind you)
+  \item Taking the ratio of the two complex spectra.
+\end{itemize}
+
+However, a similar mismatch to the SPICE exists for fourier methods, but in the other direction.
+The courant limit often demands fine timesteps, but since each FFT bin is $ f_{bin} = n_{bin} / (N_{simulation} \ dt) $ , the majority of the FFT bins exist into the hundreds or thousands of GHz, leaving no resolution in the low-frequency domain of interest unless $N_{simulation}$ is extremely large - even if all the transients in the simulation have died down, you still have to keep the sim running to make the FFT happy!
 
@@
 
-But, in a personally staggering turn of events which will presumably be familiar to statisticans and preposterous to everyone else, a far simpler method is to {\it discard} 95\% of the data!
-Re-sampling some fraction of the current
+But, in a personally staggering turn of events which will presumably be familiar to statisticans and preposterous to everyone else, a far simpler method is to {\it discard} 95\% of the data, by down-sampling to 1/10th.
 
-An equally simple method that seemed to produce better results in our case is to {\it pad }
+An equally simple method that seemed to produce better results in our case is to pad the voltage and current samples to the correct length.
+
+It's so thumpingly unintuitive to me that adding 50,000 zeros to a 5000 value dataset can improve the resolution of a measurement by 300-fold.
 
@@
 
-Though uneven dt FFTs exist, the time step can be constant here .
+Though uneven dt FFTs exist, the time step can be made constant at the courant limit.
 
-A step impulse (1 first timestep, 0 otherwise) can also be used, though the performance is almost unusable worse.
+A step impulse (1 first timestep, 0 otherwise) has been used in some works, though in our case the performance was horrid.
+
+A method of moments solver like NEC-2 may have provided faster results; but handling of multiple dielectrics does not seem to be simple.
+
+This technique is equivalent to that used in electrochemistry for fourier impedance - except they seem to usually use a known impedance source rather than a hard source.
+
+The duration of the simulation is very important. When they say
+
+\rule{\linewidth}{0.2pt}
+
+Many equations in papers on the FDTD method are supplied without explicit scaling factors.
+For instance, for use with flaport/fdtd the H-field to current line integral in [] requires scaling by $\mu_0  (dx/dt)$, where $\mu_0$ is the vacuum magnetic permittivity, dx the cell size, and dt the timestep - despite the equation already possessing a deceptive set of $dx$-es.
+
+Naturally, if one is competent, this discrepancy will be immediately obvious.
+Those not dimensionally-intuitive, such as myself, find it useful to run a test using a unit-aware calculator such as {\it sharkdp/insect}.
 

### 2020-06-24 electronics/simple_fdtd/run/U_patch_antenna_designer.py

@@ -2,6 +2,7 @@ import fdtd_PCB_extensions as fd
 from fdtd_PCB_extensions import fdtd
 from fdtd_PCB_extensions import X,Y,Z
 from scipy.constants import mu_0
+import scipy.constants
 import numpy as np
 from math import sin, pi, pow, exp
 import time
@@ -26,11 +27,11 @@ import store
 #Water permittivity @ 10 GHz: 65 - use AbsorbingObject
 
 #analytic 8 GHz patch antenna - ~240 ohms at the edge
-patch_width = 11.4e-3
-patch_length = 8.7e-3
-feed_length = 5e-3
-substrate_thickness = 0.8e-3
-dielectric_constant = 4.4
+# patch_width = 11.4e-3
+# patch_length = 8.7e-3
+# feed_length = 5e-3
+# substrate_thickness = 0.8e-3
+# dielectric_constant = 4.4
 
 #
 # patch_width =  22.26e-3
@@ -43,11 +44,11 @@ dielectric_constant = 4.4
 
 
 # [Samaras 2004]
-# patch_width =  59.4e-3
-# patch_length = 40.4e-3
-# feed_length = 0e-3
-# substrate_thickness = 1.2e-3
-# dielectric_constant = 2.42
+patch_width =  59.4e-3
+patch_length = 40.4e-3
+feed_length = 0e-3
+substrate_thickness = 1.2e-3
+dielectric_constant = 2.42
 
 pcb = fd.PCB(0.0004)
 fd.initialize_grid(pcb,int((patch_width+20.0e-3)/pcb.cell_size),int((patch_length+20.0e-3+feed_length)/pcb.cell_size),
@@ -275,7 +276,9 @@ plt.legend()
 
 plt.figure()
 
-impedance_spectrum = abs(2.0*voltage_spectrum/(current_spectrum+current_spectrum_2))
+Z0 = scipy.constants.physical_constants['characteristic impedance of vacuum'][0]
+
+impedance_spectrum = (abs(2.0*voltage_spectrum/(current_spectrum+current_spectrum_2)) - Z0) / 2.0
 
 plt.plot(spectrum_freqs[begin_freq:end_freq],impedance_spectrum[begin_freq:end_freq])
 # plt.plot(spectrum_freqs[begin_freq:end_freq],impedance_spectrum[begin_freq:end_freq])
@@ -291,6 +294,8 @@ plt.pause(0.001)
 
[…]

### 2020-06-24 documents/paper.tex
Reworked threshold slightly

@@
 
+The oscillator design is a testament  This highlights that a computation is not a substitute for understanding.
+
 We began experimentally by building a scaled version of [Mueller 2008]'s active antenna crudely with copper tape, using a CEL [] FET.
@@
 
-The frequency impedance of an antenna can be determined by:
+The impedance of an antenna over frequency can be determined by:
 
 \begin{itemize}
-  \item Applying a gaussian pulse to a hard voltage source on the feedline
+  \item Applying a gaussian pulse to a hard voltage source - in our case, applied to a via connecting the path (or probe)
   \item Running the simulation until the transients have all died out below some threshold, while logging the source voltage and current at each timestep
-
   \item Taking the fourier transform of the (real) excitation voltage and current (producing a complex result, mind you)
@@
 
-However, a similar mismatch to the SPICE exists for fourier methods, but in the other direction.
+This is the computational equivalent of dropping a piano off a balcony to see which key is stuck.
+
+See [Penney 1994], [Luebbers 1992], [Luebbers 1991], [Luk 1997].
+
+Our implementation is in electronics/simple\_fdtd/runs/U.py.
+
+A similar mismatch to the SPICE exists for fourier methods - but in the other direction.
 The courant limit often demands fine timesteps, but since each FFT bin is $ f_{bin} = n_{bin} / (N_{simulation} \ dt) $ , the majority of the FFT bins exist into the hundreds or thousands of GHz, leaving no resolution in the low-frequency domain of interest unless $N_{simulation}$ is extremely large - even if all the transients in the simulation have died down, you still have to keep the sim running to make the FFT happy!
@@
 
-But, in a personally staggering turn of events which will presumably be familiar to statisticans and preposterous to everyone else, a far simpler method is to {\it discard} 95\% of the data, by down-sampling to 1/10th.
+But, in a staggering turn of events which will presumably be familiar to statisticans and preposterous to everyone else, a far simpler method is to {\it discard} 95\% of the data, by down-sampling to 1/10th or so.
 
 An equally simple method that seemed to produce better results in our case is to pad the voltage and current samples to the correct length.
+The jump discontinuity introduced by padding with zeros has a negligible effect.
 
@@
 
-It is important to remember to normalize the gaussian pulse, or else numerical noise will be introduced. The precise magnitude is not important - [Luebbers 1992/1991] use 100v, others use 1v, etc.
+It is important to remember to normalize the gaussian pulse, or else numerical noise will be introduced. The magnitude is not important - [Luebbers 1992] use 100v, others use 1v, etc.
 
-Though uneven dt FFTs exist, the time step can be made constant at the courant limit.
+Though uneven dt FFTs exist, the time step can be constant at the courant limit for this simulation.
 
-A step impulse (1 first timestep, 0 otherwise) has been used in some works, though in our case the performance was horrid.
+A step impulse (1 first timestep, 0 otherwise) has been used in some works, though in our case performance was quite horrid.
+
+A correction factor due to the staggered magnetic field of the Yee lattice should be introduced;  Their $Z_2$ equation (correcting for spatial inaccuracies, but not temporal) was sufficient.
 
@@
 
-This technique is equivalent to that used in electrochemistry for fourier impedance - except they seem to usually use a known impedance source rather than a hard source.
+This technique is equivalent to that used in electrochemistry, known as fourier impedance spectroscopy - except they seem to usually use a known impedance source rather than a hard source, presumably because ideal hard sources don't exist in reality.
 
-The duration of the simulation is very important. When they say
+Allowing the simulation to run for long enough that all transients dissipate is important for accuracy - deceptive dips in the current can cause early termination.
+A surprising amount of detail is contributed by even the smallest current levels.
+Our threshold is 1e-7 amps for 700 iterations.
+
+[Samaras 2004] has a very useful set of experimental and FDTD data for calibration and comparison.
+Comparing a probe via source in the different positions, we obtained agreement of $\sim 7\%$ in impedance and $\sim 5\%$ in frequency.
 

### 2020-06-24 documents/paper.tex
RSI

@@
 
-A correction factor due to the staggered magnetic field of the Yee lattice should be introduced;  Their $Z_2$ equation (correcting for spatial inaccuracies, but not temporal) was sufficient.
+A correction factor due to the staggered magnetic field of the Yee lattice should be introduced; [Fang 1994].
+Their $Z_2$ equation (correcting for spatial inaccuracies, but not temporal) was sufficient.
 
@@
 Comparing a probe via source in the different positions, we obtained agreement of $\sim 7\%$ in impedance and $\sim 5\%$ in frequency.
+
+The type of feed-port may affect the convergence rate by introducing unphysical transients.
+
+Simply monitoring the source current during the simulation is deceptive. Periodically monitoring the fourier transform
 

### 2020-06-28 documents/paper.tex
Paper split into sections

--- 2020-06-24 documents/paper.tex
@@
 
-\usepackage[left=2cm,right=2cm,
-			top=1.25cm,
-			bottom=2.25cm,%
-			headheight=11pt,%
-			letterpaper]{geometry}
-
-\frenchspacing
-
-\usepackage{multicol}
-\usepackage{fancyhdr}
-\usepackage{blindtext,graphicx}
-\usepackage[absolute]{textpos}
-\usepackage[parfill]{parskip}
-\usepackage[colorlinks]{hyperref}
-\usepackage{hyperref}
-\usepackage{gensymb}
-\usepackage{csquotes}
-\usepackage{amsmath}
-\usepackage{fontawesome}
-\usepackage{orcidlink}
-
-\usepackage{graphicx}
-\graphicspath{ {../media/} }
-
-\usepackage{tcolorbox}
-\newtcolorbox{autem}{colback=red!5!white,colframe=red!75!black}
-\newtcolorbox{toolchain}{colback=blue!5!white,colframe=blue!40!black!40}
-%https://tex.stackexchange.com/questions/66154/how-to-construct-a-coloured-box-with-rounded-corners
-
-%\usepackage[sfdefault,light]{roboto}
-
-\setlength{\TPHorizModule}{1cm}
-\setlength{\TPVertModule}{1cm}
+\include{preamble}
 
@@
 
+This is especially true with RF biophysics. The literature is littered with otherwise impeccably perormed research which was later demonstrated to be an artifact. \\
+
 	Though the original research used Inf. A, our testing was only performed with a surrogate bacteriophage. All experiments must be repeated with SARS-NCoV-2. \\
@@
 	Additionally, other sterilization techniques may produce superior results and should be evaluated in the same context. Data on far UV [Buonanno 2017] indicate safety.\\
+
+It has occurred before that otherwise striking resonances were detected and replication found them to be artifacts of the measurement equipment. [Foster 1987] even offers this disclaimer:
+
+"To detect the DNA resonances with the probe
+technique requires correction for system errors that are
+potentially much larger than the effect to be studied and
+lead to resonance-like artifacts. This is true even with the
+more precise instrumentation used in this study. Such data
+are easily misinterpreted, and we suggest this might have
+happened in the former study."
+
+The direct inactivation plaque and PCR data from [Yang], replicated by [Sun], is a somewhat convincing corroboration that this effect is not an artifact, but hundreds of convincing and  wrong papers exist in the literature.
+Our data is crude and imprecise, our equipment hastily constructed, and should not be considered validation of this effect even existing.
+\\
 
@@
 
-With typical 2.4 GHz microwave exposure, sterilization occurs by heating of the fluid and tissue.
+With typical 2.4 GHz microwave exposure, sterilization can only occur by heating of the fluid and tissue.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The chain of literature Fruluch -> ([Sun ] | [Yang 2015]) establishes that spherical virions possess a weak dipole resonance mode which happens to fall within the microwave spectrum, at approximately the X-band (6-10 GHz).
+
+This is a non-ionizing, non-thermal technique;
+
+This resonance mode
+
+The myth that 2.4 GHz was chosen because it "couples strongly with water" is largely false; but this is
+
+This is quite surprising, and should perhaps be considered with some trepidation, since
+
 \paragraph{\textbf{Time dependence}}\
@@
 state the Q of Inf.
-A as between 2 and 10, so at 8 GHz the steady-state amplitude should be reached in well under 1 us.
+A as between 2 and 10, so at 8 GHz the steady-state amplitude should be reached in well under 100 nanoseconds.???????????FIXME
 
@@
 
-\clearpage
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{multicols}{1}
-{\Large Safety}\\
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Because this is an ostensibly novel and niche mechanism, it may behoove us to breifly review the biological basis for the safety limits set by standards organizations.
-\footnote{The idea of biological microwave resonances appears to have originated in [Frohlich 1968, 1980].}
-
-\includegraphics[scale=0.5]{cells.png}
-
-Contrary to some [Hardell 2017] reports, we do not find the FCC and ICNIRP to be significantly affected by special interest groups; their rationales appear to be transparent. 
-\footnote{[FCC-19-126A1] an FCC memorandum wherein the FCC tells groups to respectfully screw themselves no fewer than three times: ''Similarly, IEEE-ICES urges the Commission to
-adopt a higher SAR exposure limit of 2 W/kg averaged over 10 g.
-[snip] We are not persuaded that the IEC standard should be adopted at this time.", "Medtronic and the AAMI-CRMD recommend a more relaxed threshold of 20 mW.
-We decline to increase the 1-mW threshold.".
-Things heating up at the Microwave Safety fandom.}
-
-For instance, it is reasonable to wonder why we might not see such resonances in bodily tissues.
-Approximately similar nanoscopic structures exist in humans, such as nuclear pores (120 nm) and the famous microtubules (10x50 nm).
-
-While from which epidemiological data could be derived.\footnote{The cloud service [scite.ai] was irreplaceable during this. It's like a mirror to an alternate universe where literature made sense.}
-
-What we find is a messy affair. Biology is hard.
-
-\rule{\linewidth}{0.2pt}
-
-There are some 20,000 papers on the topic of RF safety, with solid in vitro, in vivo and epidemiological evidence of safety in the 2.4 GHz and 5.8 GHz bands.
-
-However, "There are limited experimental human data upon which to set limits on exposures above 6 GHz" [Chan 2019]. Only 2\% of the above papers are on frequencies $>6$ GHz [Vijayalaxmi 2018].
-
-In addition, what data remains in this category is of varying quality.
-
-As has been starkly demonstrated in the recent hydroxychloroquine contradictions [Gautret 2020] [Geleris 2020], biological research must be essentially perfect to have any meaning at all.
-
-The IEEE standard which the flagship paper [Yang 2015] references [IEEE C95.1-2005] was recently overhauled [IEEE C95.1-2019] with new metrics.
-
-[Vijayalaxmi 2018] is a remarkable meta-analysis of in vitro data.
-They synthesize a quality score, rating bindedness, sham controls, dosimetry, and sample size.
-Quality was inversely, monotonically related to the effect size.
-An example of the subtle effects that can call into question superfically reasonable results are [
-
-They additionally find a publication bias of incredible magnitude in the positive (harm) direction in this field, further degrading the usefulness of statistical analyeses.
-
-An example of a relevant study that they grade as "quality 1" [Karaca 2011].
-This study's conclusion is that However, in figure 5, one can see that only 1 out of 11 genes tested had a statistically significant difference in expression.
-Given the N=6 cultures,
-
-\rule{\linewidth}{0.2pt}
-
-[Adair 2002] demonstrate theoretically that acoustic resonances are, in general, highly unlikely in biological solvents, primarily focusing on DNA.
-All resonance modes are strongly overdamped by the surrounding solvent, and no amplitude amplification can take place.
-
-This analysis would seem to disagree with the viral resonance apparently conclusively demonstrated by [Yang 2015] - the PCR result seems especially inarguable.
-This could be explained by the large charge on the virus compared to the molecules analyzed in Adair.
-[Yang 2015] find a charge of order $10^7 e$, whereas Adair analyzes a very different regime, "assume coupling to the field through single charges q = e at each end".
-
-[Liu 2009] cite [Edwards, Swicord 1984], saying: "It was proposed that a hydration layer surrounding DNA molecules could lower the viscoelastic transition
-frequency, raise the quality factor of confined acoustic vibrations, and result in a microwave resonant absorption".
-
-But [Adair 2002]'s [Foster 1987] seem to quite conclusively put the kibosh on that idea, demonstrating no resonances in DNA with 20x higher precision than previous work, showing previous results to be an artifact of the measurement equipment.
-
-The supplemental material to [Vijayalaxmi 2018] has a table of studies on this topic. High-quality research in-vitro concurs with.
-
-\paragraph{[Manikowska 1979]} \
-
-9.4 GHz pulsed / in vivo, mouse, $0.1-10 \text{mW}/\text{m}^2$ over the whole body for 2 weeks. N=16.
-
-This is a particularly concerning result, especially given their $p<0.001$. [Servantie 1989] discusses the (admittedly circuituious) route by which birth defects could occur.
-
-Work by [Manikowska 1985] in the 2.4 GHz range has been contradicted [Beechey 1986], but the 9 GHz range does not appear to have been repeated.
-
-\rule{\linewidth}{0.2pt}
-
-More modern research [Juutilainen 2011], [Chemeris], [Vijayalaxmi 2006],  does not tend to agree with these concerns.
-As cited by [ICNIRP 2020]'s excellent literature review, expose lymphocyte blood cells to 8 ns pulsed 8.2 GHz radiation for 2 hours at an average power of $10 \text{mW/cm}^2$.
-They find no change in any of the parameters measured, including various chromosomal parameters.
-They further discuss previous results.
-
-\rule{\linewidth}{0.2pt}
-
-In the frequency range of interest, there seems to be good-quality in-vitro evidence using lymphocytes of lack of harm.
-We are not aware of any high-quality in vivo or epidemeological data from which useful conclusions can be drawn.
-
-We must defer to health experts for interpretation of these data.
-
-\rule{\linewidth}{0.2pt}
-
-{\it Please contact the author if you are aware of other salient research, or have a different interpretation.}
-
-\footnote{``{\it{For example, below about 6 GHz, where EMFs penetrate deep into tissue (and thus require depth to be considered), it is useful to describe this in terms of “specific energy absorption rate” (SAR), which is the power absorbed per unit mass $(W/kg)$.
-Conversely, above 6 GHz, where EMFs are absorbed more superficially (making depth less relevant), it is useful to describe exposure in terms of the density of absorbed power over area $W/m^2$, which we refer to as “absorbed power density”}}'' [ICNIRP 2020 \faExternalLink]}
-
-\end{multicols}
+\subfile{safety}
 
@@
 
-SARS is found widely distributed throughout the most desirable organs [Ding 2004], shielded by an average of 4 cm of chest wall [Schroeder 2013]; so safe external treatment of the body is unlikely.
+SARS is found widely distributed throughout the most favorable organs [Ding 2004], shielded by an average of 4 cm of chest wall [Schroeder 2013]; so safe external treatment of the body is unlikely.
 
@@
 
-A minimally-invasive bronchoscopic technique may be effective when mounted on a modified brochoscope and periodically inserted into the main bronchus, as demonstrated by [Yuan 2019].
+A bronchoscopic technique may therefore be effective, very similarly to that demonstrated by [Yuan 2019]: the bronchi are less than 2 mm thick [Theriault 2018] and the lungs themselves are only on the order of 7 mm thick [Chekan 2016].
 
-The bronchi are less than 2 mm thick [Theriault 2018] and the lungs themselves are only on the order of 
-7 mm thick [Chekan 2016].
+There is considerable tolerance in the
 
@@
 Existing marine, weather, and aviation radar systems often use the X-band; depending on the focusing power
+
+\paragraph{}
+
+Finally, there is one concern.
+Use of this technique will provide a selection bias towards immunity to electromagnetic fields, which could perhaps be effected by preferring extreme-sized mutants (shifting the resonance away from the applied field).
+We do not have the biological knowledge to know if this is plausible; it is simply worth mentioning.
 
@@
 
-Rather than the almost universal technique of via stitching components immediately to the ground plane (a tedious process with our prototyping setup), a large ground pour on the component layer was used, similar to [Hunter?
+Rather than the almost universal technique of via stitching components immediately to the ground plane (a tedious process with our prototyping setup), a large ground pour on the component layer was used wherever ground was needed, as mentioned in [Hunter?
 combline].
@@
 Since the ground plane does not participate in the DC bias at all, no vias are required in the final device.
-This means that the comparatively slow drilling, electroless strike and electroplating steps are unneccesary for this device.
+This means that the drilling, electroless strike and electroplating steps are unnecessary for production.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-{\Large Molecular dynamics simulation}\\
-\begin{multicols}{1}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-aa
-
-\end{multicols}
-
-\clearpage
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-{\Large Optical centrifuge polarization chirp}\\
-\begin{multicols}{1}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\end{multicols}
-
-\clearpage
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \paragraph{Acknowledgements}\
@@
 
-The authors of the original papers deserve the credit for this entire work; it is rare that such a is served on a silver platter.
+The authors of the original papers deserve the credit for this entire work;  it is rare that such a monumental finding is served on a silver platter.
 
@@
 Dr. Dainis' videos on microbiological technique were also useful.
+
+Thanks to the professors at York and beyond for returning my emails.
 
@@
 
-\clearpage
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-{\Large Captain's Log, Supplemental}\\
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subfile{supplemental}
 
-\rule{\linewidth}{0.2pt}
-
-There seems to be a discrepancy between [Yang 2015] and our reading of C95.1-2005. This is very likely a misreading on our part, and so calls into question our understanding of the standard.
-
-They say: "Based on the IEEE Microwave Safety Standard, the spatial averaged value of the power density in air in open public space shall not exceed the equivalent power density of $100(f/3)^{1/5} \text{ W/m}^2$ at frequencies between 3 and 96GHz ($f$ is in GHz).
-This corresponds to $115 \text{ W}/\text{m}^2$ at 6 GHz".
-The 115 W @ 6 GHz value correctly corresponds to this equation with a coefficient of 100.
-
-The only reference to a 3 - 96 GHz limit we can find is that of Section 4.6, {\it Relaxation of the power density MPEs for localized exposures}, where the equation is $200 (f/3)^{1/5} \text{ W/m}^2$ [IEEE C95.1-2005], for controlled occupational exposures, referring to Table 8.
-For Table 9, general public, the equation is $18.56 (f)^{0.699} \text{ W/m}^2$, or $64.93 \text{ W}/\text{m}^2$ @ 6 GHz.
-
-Different versions of the IEEE standard have used equations of equivalent form but with different coefficients [Wu 2015]; it is possible that we have retrieved the wrong standard.
-
-In any case, this doesn't change the substance of [Yang 2015]'s paper; the relaxed localized exposure is probably the correct threshold to use, and it just means the mechanism is more useful for healthcare workers who acknowledge the risks.
-
-\rule{\linewidth}{0.2pt}
-
-CEL did not supply a SPICE model for the GaAs FET device used in early prototypes. A FET was originally because a gate is ostensibly easier to bias than a base; but this turned out to be unfounded.
-
-[Steenput 1999] has an interesting analytic method to synthesize a SPICE model suitable for a transient simulations from S-parameter measurements using negative resistances.
-However, this neglects the I/V characteristic.
-
-[Polyfet 1998] describes a simple optimization method to synthesize a SPICE model for an active device, and CEL appnote provides some details for GaAs devices.
-
-\rule{\linewidth}{0.2pt}
-
-OpenEMS is excellent, with Python bindings, some lumped components, and mesh refinement. However, embarassingly, we were not able to resolve all the dependency issues in order to install it.
-
-\rule{\linewidth}{0.2pt}
-
-We began experimentally by building a scaled version of [Mueller 2008]'s active antenna crudely with copper tape, using a CEL [] FET.
-
-We then manually tried a number of filter designs, using the manufacturer's S-parameters and QUCS' microstrip approximations.
-This intially appeared to yield good agreement with experiment.
-Peaks in the feedback voltage simulation corresponded approximately with peaks in the observed spectrum.
-[figures from LO prototype N].
-
-A crude, inane, and extremely disorganized trial-and-error procedure was performed for many weeks.
-A wide variety of analytical methods for filter design were attempted, but simultaneously obtaining the correct phase shift and frequency response was somewhat difficult.
-The parasitic inductance of the varactors always seemed to destroy our most perfect creations.
-
-An SIR filter has the added advantage of confusing epidemiologists greatly.
-
-Eventually, QUCS, zonca/python-qucs, and scipy's basinhopper was used with the cost function somewhat similar to that described in [Kaplevich]:
-
-\begin{verbatim}
-    freq_coeff = 1
-    phase_coeff = 1.5
-    ratio_coeff = 0.5
-    insertion_loss_coeff = 0.2
-
-    frequency_cost = freq_coeff * (abs(desired_center_frequency-fb_peak_frequencies[0])/1e9)
-    phase_cost = phase_coeff * abs(1.0 - phase_at_peak)
-    ratio_cost = ratio_coeff * fb_peak_ratio
-    insertion_loss_cost = insertion_loss_coeff*(1.0 - fb_peak_values[0])
-    cost = frequency_cost + phase_cost + fb_peak_ratio + insertion_loss_cost
-\end{verbatim}
-
-Optimizing first for the high frequency, fixing the inductor and microstrip values, and then optimizing for the varactor values at the low frequency.
-
-This produced a seemingly acceptable feedback loop:
-
-\includegraphics[scale=1]{LO_2_pole_test.png}
-
-However, when this was built, varactor tuning performance was abysmal, with hops and peaks; and the tuning range was far smaller than expected.
-
-It was thought that a transient simulation - to determine how the spectrum actually evolved - would improve the situation.
-
-As of 0.0.20, QUCS' microstrip models are not yet compatible with transient simulations; and some improved filter designs required simulating coupling between more than two microstrips, which QUCS did not yet support natively.
-
-\includegraphics[scale=0.5]{3d_spectrum_2.png}
-
-The complete transient simulation matched reality very closely.
-
-Because we lacked a spectrum analyzer that could monitor the higher poles of the filter until the bootstrap LO was designed, we had to rely on in-silico analyeses.
-
-Transient simulations with ngspice matched experiment far more closely.
-
-\rule{\linewidth}{0.2pt}
-
-Again, inductive choke biasing in the feedback loop was practically impossible.
-Biasing PiN diodes with a 10kohm resistor, (with 330 ohm safety resistor) one to 48V bias and another through an 2N7002P N-channel mosfet worked fine.
-
-The oscillator ran fine with a PiN bias of 2.34 mA.
-[LO prototype N].
-A high bias voltage of 48V was required to get sufficient current through the two 10K resistors and the PiN diode to obtain a low impedance while remaining delicate with the vfb.
-
-The PiN diode used has a resting resistance of 500 ohms, 5 ohms at 2 mA and 2 ohms at ??.
-
-48V is a little tight on the 50V rated voltage of our DC blocking capacitors.
-
-Each activated PiN diode should be biased separately, since putting 2x 2 mA through 20K would take an impractical 80V.
-
-\rule{\linewidth}{0.2pt}
-
-Conductors are represented by zeroing all components of the electric field in those regions.
-
-There are many different possible source geometries, each introducing their own distortions.
-
-There are many ways of linking SPICE and FDTD.
-
-\rule{\linewidth}{0.2pt}
-
-Bandpass filters can be designed by first designing a low-pass filter prototype (usually Chebychev) (or, in our case, using reference filter component tables), and then transforming this low-pass into a band-pass.
-[Hunter 2001] is an excellent overview of this process, with many design examples for different filter topologies.
-
-The coupling coefficient between two low-pass filters determines the band-pass bandwidth.[Hui 2012]
-
-[Hunter 2001] also describes an analytical method to create a filter with the precise group delay - phase shift versus frequency - required for stable oscillation.
-However, simultaneously compensating for the group delay introduced by the amplifier itself (nearly 180 degrees over the frequency range for the CEL part) seemed complex.
-
-Phase shift can be introduced either via a length of microstrip, or a high-pass/low-pass filter [Microwave101].
-Adding a fixed microstrip line restricts the tuning range, however, and the filter inevitably affects the frequency response.
-
-\rule{\linewidth}{0.2pt}
-
-NGSPICE's KSPICE coupled transmission lines require the capacitance and inductance per unit length in Maxwell matrix form, rather than the physical $C_{even}$/$L_{even}$ (each line's capacitance and inductance to ground) and $_{odd}$ (between elements) form provided by tools like wcalc.
-"matrix not positive definite".
-[Schutt-Aine] discusses this; we reproduce here for convienience.
-
-\[ L_{11} = L_{22} = L_{even}  \]
-\[ L_{12} = L_{21} = L_{odd}  \]
-\[ C_{11} = C_{22} = C_{even}+C_{odd}  \]
-\[ C_{12} = C_{21} {\it{(unused)}} = -C_{odd}  \]
-
-\rule{\linewidth}{0.2pt}
-
-In practice, the timestep required to obtain convergence in particularly tight corners of the SPICE simulation can drop to 1e-20, which is far below the Courant limit of the FDTD simulation.
-To eek out a bit more performance, a simple adaptive-timestep technique from [ a ] is used; we simply set the timestep so that the maximum change in voltage per timestep from the non-FDTD portion is less than some threshold.
-
-\rule{\linewidth}{0.2pt}
-
-Originally tried
-
-The frequency impedance of an antenna can be determined by:
-
-\begin{itemize}
-  \item Applying a gaussian pulse to a hard voltage source on the feedline
-  \item Running the simulation until the transients have all died out below some threshold, while logging the source voltage and current at each timestep
-
-  \item Taking the fourier transform of the (real) excitation voltage and current (producing a complex result, mind you)
-  \item Taking the ratio of the two complex spectra.
-\end{itemize}
-
-However, a similar mismatch to the SPICE exists for fourier methods, but in the other direction.
-The courant limit often demands fine timesteps, but since each FFT bin is $ f_{bin} = n_{bin} / (N_{simulation} \ dt) $ , the majority of the FFT bins exist into the hundreds or thousands of GHz, leaving no resolution in the low-frequency domain of interest unless $N_{simulation}$ is extremely large - even if all the transients in the simulation have died down, you still have to keep the sim running to make the FFT happy!
-
-There's more than enough 'information entropy' in 2000 FDTD points for most antennas. But you need some 30,000 points to get 10 bins below 20 GHz!
-
-There are a few methods of changing the FFT bin size artificially, which [Bi 1992] reviews. You can "use a manual fourier integration over the frequency region of interest".
-
-But, in a personally staggering turn of events which will presumably be familiar to statisticans and preposterous to everyone else, a far simpler method is to {\it discard} 95\% of the data, by down-sampling to 1/10th.
-
-An equally simple method that seemed to produce better results in our case is to pad the voltage and current samples to the correct length.
-
-It's so thumpingly unintuitive to me that adding 50,000 zeros to a 5000 value dataset can improve the resolution of a measurement by 300-fold.
-
-It is important to remember to normalize the gaussian pulse, or else numerical noise will be introduced. The precise magnitude is not important - [Luebbers 1992/1991] use 100v, others use 1v, etc.
-
-Though uneven dt FFTs exist, the time step can be made constant at the courant limit.
-
-A step impulse (1 first timestep, 0 otherwise) has been used in some works, though in our case the performance was horrid.
-
-A method of moments solver like NEC-2 may have provided faster results; but handling of multiple dielectrics does not seem to be simple.
-
-This technique is equivalent to that used in electrochemistry for fourier impedance - except they seem to usually use a known impedance source rather than a hard source.
-
-The duration of the simulation is very important. When they say
-
-\rule{\linewidth}{0.2pt}
-
-Many equations in papers on the FDTD method are supplied without explicit scaling factors.
-For instance, for use with flaport/fdtd the H-field to current line integral in [] requires scaling by $\mu_0  (dx/dt)$, where $\mu_0$ is the vacuum magnetic permittivity, dx the cell size, and dt the timestep - despite the equation already possessing a deceptive set of $dx$-es.
-
-Naturally, if one is competent, this discrepancy will be immediately obvious.
-Those not dimensionally-intuitive, such as myself, find it useful to run a test using a unit-aware calculator such as {\it sharkdp/insect}.
-
-\rule{\linewidth}{0.2pt}
-
-The impedance of a microstrip antenna varies with position on its plane. Probe feeds that couple a microstrip to a specific point are often used.
-
-\rule{\linewidth}{0.2pt}
-
-\label{para}
-\ref{para}
-
-\paragraph{Timeline}
-
-\paragraph{Comments by others}
-
-\paragraph{Lessons Learned} \
-
-\rule{\linewidth}{0.2pt}
-
-It may be helpful to think of simulations very similarly to IRL experiments.
-
-A simulation is just a universe in a bottle that you can examine more closely; as with real-world, you can learn much from observation, but
-
-But this need for documentation conflicts with the rapid, iterative cycle necessary for productivity.
-
-This is obvious to all compentent, but when rapidly iteratively testing with simulations, it may be helpful to automatically save a package with images of all the components (schematics, graphs, input files) of each distinct test.
-
-For comparison to experiment, having a webcam take an image of the assembled board is also helpful.
-
-Version control alone isn't quite enough.
-Just having a simulation setup file somewhere in the commit history isn't "discoverable" - that is, you must be able to see what the input and output was without re-running the simulation.
-
-Manually taking notes tended to disrupt the flow of testing; and in any case, just noting "SIR filter has appropriate phase response" is almost useless. What {\it was} the phase response? Plot it!
-
-Software such as Sumatra, Sacred, recipy, and others. In our case, we used eLabFTW's elabapy bindings.
-
-\rule{\linewidth}{0.2pt}
-
-It is far easier to use existing, well-characterized reference designs verbatim than to modify
-
-\rule{\linewidth}{0.2pt}
-
-When rapidly testing data analyses which aren't really conducive to unit testing, I previously used to run the whole simulation, look at the analysis, re-run the sim, etc.
-
-This is slow. I often don't change the input parameters for the sim, but just the analysis. However, there's often a large amount of state to persist to disk.
-
-Saving the entire session with 'dill' is very helpful.
-
-\rule{\linewidth}{0.2pt}
-
-Software opacity is evil.
-
-\rule{\linewidth}{0.2pt}
-
-A great deal of time was spent trying to resolve version conflicts and dependency hells with the numerous libraries used by all the simulation programs.
-This also wastes developer time - some fraction of issues raised are due to library version conflicts.
-OpenFOAM's Docker installation is excellent.
-
-Running chroot with the original developer's Linux distribution is also of some utility, but clunky.
-
-Packaged binaries help this slightly, but of course don't help if modifications are required, and managing shared libraries is still a tricky matter.
-
-In some situations (especially where the library has a permissive licence) perhaps it could be useful to consider packaging a complete, batteries-included 'known good' repository, either with the source of all the correct library versions included, or with a script to clone and compile the specific version used, integrating all the libraries with the build system.
-
-For instance, this was done with the PDB reader in the OpenMM wrapper and JAMES.
-
-\rule{\linewidth}{0.2pt}
-
-There's also a very neat thing that seems to be common in computational biology, but which doesn't seem popular in other fields.
-After an algorithm or software tool is written (and the source published seperately), a simple CGI frontend is written around it and hosted on the university's servers.
-eLNemo and the CHARMMing web interface are advanced examples of this.
-This way, anyone with an input file can get results without futzing around with installation.
-
-The computational biologists have beat us at our own game.
-
-\rule{\linewidth}{0.2pt}
-
-Write a paper to be understood; to be as clear and helpful as possible to the reader.
-
-\rule{\linewidth}{0.2pt}
-
-We have always encountered wasting extreme amounts of time on subtle assembly mistakes in hardware prototypes.
-
-In one example in this project, many hours were wasted because the enamel insulation on a bodge wire had not burned off completely in the solder joint, leading to a high-impedance connection.
-
-The same has occurred in previous projects; in one example, many days were spent debugging software to fix an apparently slow hardware interrupt, which ended up being the result of a poor solder paste stencil leading to a hidden high-impedance connection to a leadless package.
-
-Many failures are perhaps the result of carelessness in modification and a lack of inspection; but others would only have been found by a 100\% electrical test.
-
-If flying-probe or bed-of-nails tests can be made sufficiently rapid and closely coupled with the existing toolchain,
-
-In {\it 2001: A space odyssey}, an automated system is shown guiding the troubleshooting of an assembly, apparently generating a fault tree of all the
-
-Boundary-scan features might really help
-
-\rule{\linewidth}{0.2pt}
-
-The ability to almost immediately compare simulation to experiment was quite important.
-
-\rule{\linewidth}{0.2pt}
-
-\paragraph{Hall of Hubris} \
-
-Lest our hats stop fitting
-
-\rule{\linewidth}{0.2pt}
-
-An inane remark:
-
-\begin{displayquote}
-We believe once we have the P. Syringae host, we from environmental samples
-\end{displayquote}
-
-Truly the depths of Dunning-Kruger.
-
-\rule{\linewidth}{0.2pt}
-
-An expert and distinguished gentleman that we contacted regarding assistance resolving transients in our microstrip VCO stated the following:
-
-This was a perfectly sensible remark; it is almost always the case that (at X-band, no less!) a custom IC would have been needed to build a VCO.
-
-Also, if taken in the context of a tired, overworked PI getting an unsolicited email from an excessively verbose undergraduate at a different university, I hardly think I would have replied differently.
-
-However, I think this person may have missed out. Learning
-
-So perhaps it is wise to ponder the ideas of fools for skeet; one always learns target practice, if only an example what not to do, and occasionally one learns positively.
-I have often found that I learn greatly from working on the projects of others.
-
-We present this only as a cautionary tale in the hopes that someday I will listen.
-
-\rule{\linewidth}{0.2pt}
-
-%\end{multicols}
-
-\Acrobatmenu{GoBack}{Back}
 \end{document}

### 2020-06-28 documents/supplemental.tex
Paper split into sections

\documentclass[paper.tex]{subfiles}
\begin{document}

\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\Large Captain's Log, Supplemental}\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Molecular dynamics simulation}
\
%\begin{multicols}{1}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

It was originally expected that a large part of this work would be done in-silico, as we did not anticipate having access to suitable RF test equipment.

Some time was spent attempting to set up a molecular dynamics toolchain capable of simulating an entire virus.

Having an approximate simulation of the this technique would be useful for a number of reasons:

We would have a better idea of the transferability to SARS, without wasting the time of experts with BSL-3/4 labs.

The impulse could be subjected to the same optimization as the RF feedback loop. A number of parameters (such as phase, polarization)

Coarse-graining also greatly increases the allowable timestep.

%\end{multicols}

\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\Large Optical centrifuge polarization chirp}\\
\begin{multicols}{1}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\includepdf[
    %% Include all pages of the PDF
    pages=-,
    %% make this page have the usual page style
    %% (you can change it to plain etc). By default pdfpages
    %% sets the pagecommand to \pagestyle{empty}
    pagecommand={\pagestyle{headings}},  
    %% Add a "section" entry to the ToC with the heading
    %% "Quilling Shapes" and the label "sec:shapes"
    addtotoc={1,section,1,Quilling Shapes,sec:shapes}]
%% The pdf file itself
{optical_centrifuge.pdf}

\end{multicols}

\clearpage
\rule{\linewidth}{0.2pt}

There seems to be a discrepancy between [Yang 2015] and our reading of [C95.1-2005].

They use a threshold in open public space of $100(f/3)^{1/5} \text{ W/m}^2$. The 115 W @ 6 GHz they provide correctly corresponds to this equation with a coefficient of 100.

For Table 9, general public, the equation is $18.56 (f)^{0.699} \text{ W/m}^2$, or $64.93 \text{ W}/\text{m}^2$ @ 6 GHz.

Different versions of the IEEE standard have used equations of equivalent form but with different coefficients [Wu 2015]; it is very possible that we have retrieved the wrong standard.

\rule{\linewidth}{0.2pt}

CEL did not supply a SPICE model for the GaAs FET device used in early prototypes. A FET was originally because a gate is ostensibly easier to bias than a base; but this turned out to be unfounded.

[Steenput 1999] has an interesting analytic method to synthesize a SPICE model suitable for a transient simulations from S-parameter measurements using negative resistances. However, this neglects the I/V characteristic.

[Polyfet 1998] describes a simple optimization method to synthesize a SPICE model for an active device, and CEL appnote provides some details for GaAs devices.

\rule{\linewidth}{0.2pt}

OpenEMS is excellent, with Python bindings, some lumped components, and mesh refinement. However, embarassingly, we were not able to resolve all the dependency issues in order to install it.

\rule{\linewidth}{0.2pt}

The oscillator design is a testament  This highlights that a computation is not a substitute for understanding.

We began experimentally by building a scaled version of [Mueller 2008]'s active antenna crudely with copper tape, using a CEL [] FET.

We then manually tried a number of filter designs, using the manufacturer's S-parameters and QUCS' microstrip approximations. This intially appeared to yield good agreement with experiment. Peaks in the feedback voltage simulation corresponded approximately with peaks in the observed spectrum. [figures from LO prototype N].

A crude, inane, and extremely disorganized trial-and-error procedure was performed for many weeks. A wide variety of analytical methods for filter design were attempted, but simultaneously obtaining the correct phase shift and frequency response was somewhat difficult. The parasitic inductance of the varactors always seemed to destroy our most perfect creations.

An SIR filter has the added advantage of confusing epidemiologists greatly.

Eventually, QUCS, zonca/python-qucs, and scipy's basinhopper was used with the cost function somewhat similar to that described in [Kaplevich]:

\begin{verbatim}
    freq_coeff = 1
    phase_coeff = 1.5
    ratio_coeff = 0.5
    insertion_loss_coeff = 0.2

    frequency_cost = freq_coeff * (abs(desired_center_frequency-fb_peak_frequencies[0])/1e9)
    phase_cost = phase_coeff * abs(1.0 - phase_at_peak)
    ratio_cost = ratio_coeff * fb_peak_ratio
    insertion_loss_cost = insertion_loss_coeff*(1.0 - fb_peak_values[0])
    cost = frequency_cost + phase_cost + fb_peak_ratio + insertion_loss_cost
\end{verbatim}

Optimizing first for the high frequency, fixing the inductor and microstrip values, and then optimizing for the varactor values at the low frequency.

This produced a seemingly acceptable feedback loop:

\includegraphics[scale=1]{LO_2_pole_test.png}

However, when this was built, varactor tuning performance was abysmal, with hops and peaks; and the tuning range was far smaller than expected.

It was thought that a transient simulation - to determine how the spectrum actually evolved - would improve the situation.

As of 0.0.20, QUCS' microstrip models are not yet compatible with transient simulations; and some improved filter designs required simulating coupling between more than two microstrips, which QUCS did not yet support natively.

\includegraphics[scale=0.5]{3d_spectrum_2.png}

The complete transient simulation matched reality very closely.

Because we lacked a spectrum analyzer that could monitor the higher poles of the filter until the bootstrap LO was designed, we had to rely on in-silico analyeses.

Transient simulations with ngspice matched experiment far more closely.

\rule{\linewidth}{0.2pt}

Again, inductive choke biasing in the feedback loop was practically impossible. Biasing PiN diodes with a 10kohm resistor, (with 330 ohm safety resistor) one to 48V bias and another through an 2N7002P N-channel mosfet worked fine.

The oscillator ran fine with a PiN bias of 2.34 mA. [LO prototype N]. A high bias voltage of 48V was required to get sufficient current through the two 10K resistors and the PiN diode to obtain a low impedance while remaining delicate with the vfb.

The PiN diode used has a resting resistance of 500 ohms, 5 ohms at 2 mA and 2 ohms at ??.

48V is a little tight on the 50V rated voltage of our DC blocking capacitors.

Each activated PiN diode should be biased separately, since putting 2x 2 mA through 20K would take an impractical 80V.

\rule{\linewidth}{0.2pt}

Conductors are represented by zeroing all components of the electric field in those regions.

There are many different possible source geometries, each introducing their own distortions.

There are many ways of linking SPICE and FDTD.

\rule{\linewidth}{0.2pt}

Bandpass filters can be designed by first designing a low-pass filter prototype (usually Chebychev) (or, in our case, using reference filter component tables), and then transforming this low-pass into a band-pass. [Hunter 2001] is an excellent overview of this process, with many design examples for different filter topologies.

The coupling coefficient between two low-pass filters determines the band-pass bandwidth.[Hui 2012]

[Hunter 2001] also describes an analytical method to create a filter with the precise group delay - phase shift versus frequency - required for stable oscillation. However, simultaneously compensating for the group delay introduced by the amplifier itself (nearly 180 degrees over the frequency range for the CEL part) seemed complex.

Phase shift can be introduced either via a length of microstrip, or a high-pass/low-pass filter [Microwave101]. Adding a fixed microstrip line restricts the tuning range, however, and the filter inevitably affects the frequency response.

\rule{\linewidth}{0.2pt}

NGSPICE's KSPICE coupled transmission lines require the capacitance and inductance per unit length in Maxwell matrix form, rather than the physical $C_{even}$/$L_{even}$ (each line's capacitance and inductance to ground) and $_{odd}$ (between elements) form provided by tools like wcalc. "matrix not positive definite". [Schutt-Aine] discusses this; we reproduce here for convienience.

\[ L_{11} = L_{22} = L_{even}  \]
\[ L_{12} = L_{21} = L_{odd}  \]
\[ C_{11} = C_{22} = C_{even}+C_{odd}  \]
\[ C_{12} = C_{21} {\it{(unused)}} = -C_{odd}  \]

\rule{\linewidth}{0.2pt}

In practice, the timestep required to obtain convergence in particularly tight corners of the SPICE simulation can drop to 1e-20, which is far below the Courant limit of the FDTD simulation. To eek out a bit more performance, a simple adaptive-timestep technique from [ a ] is used; we simply set the timestep so that the maximum change in voltage per timestep from the non-FDTD portion is less than some threshold.

\rule{\linewidth}{0.2pt}

Originally tried

The impedance of an antenna over frequency can be determined by:

\begin{itemize}
  \item Applying a gaussian pulse to a voltage source - in our case, applied to a via connecting the path (or probe)
  \item Running the simulation until the transients have all died out below some threshold, while logging the source voltage and current at each timestep
  \item Taking the fourier transform of the (real) excitation voltage and current (producing a complex result, mind you)
  \item Taking the ratio of the two complex spectra.
\end{itemize}

This is the computational equivalent of dropping a piano off a balcony to see which key is stuck.

See [Penney 1994], [Luebbers 1992], [Luebbers 1991], [Luk 1997].

Our implementation is in electronics/simple\_fdtd/runs/U.py.

A similar mismatch to the SPICE exists for fourier methods - but in the other direction.  The courant limit often demands fine timesteps, but since each FFT bin is $ f_{bin} = n_{bin} / (N_{simulation} \ dt) $ , the majority of the FFT bins exist into the hundreds or thousands of GHz, leaving no resolution in the low-frequency domain of interest unless $N_{simulation}$ is extremely large - even if all the transients in the simulation have died down, you still have to keep the sim running to make the FFT happy!

There's more than enough 'information entropy' in 2000 FDTD points for most antennas. But you need some 30,000 points to get 10 bins below 20 GHz!

There are a few methods of changing the FFT bin size artificially, which [Bi 1992] reviews. You can "use a manual fourier integration over the frequency region of interest".

But, in a staggering turn of events which will presumably be familiar to statisticans and preposterous to everyone else, a far simpler method is to {\it discard} 95\% of the data, by down-sampling to 1/10th or so.

An equally simple method that seemed to produce better results in our case is to pad the voltage and current samples to the correct length. The jump discontinuity introduced by padding with zeros has a negligible effect.

It's so thumpingly unintuitive to me that adding 50,000 zeros to a 5000 value dataset can improve the resolution of a measurement by 300-fold.

It is important to remember to normalize the gaussian pulse, or else numerical noise will be introduced. The magnitude is not important - [Luebbers 1992] use 100v, others use 1v, etc.

Though uneven dt FFTs exist, the time step can be constant at the courant limit for this simulation.

A step impulse (1 first timestep, 0 otherwise) has been used in some works, though in our case performance was quite horrid.

A correction factor due to the staggered magnetic field of the Yee lattice must be introduced; [Fang 1994]. Their $Z_2$ equation (correcting for spatial inaccuracies, but not temporal) was sufficient.

A method of moments solver like NEC-2 may have provided faster results; but handling of multiple dielectrics does not seem to be simple.

This technique is equivalent to that used in electrochemistry, known as fourier impedance spectroscopy - except they seem to usually use a known impedance source rather than a hard source, presumably because ideal hard sources don't exist in reality.

Allowing the simulation to run for long enough that all transients dissipate is important for accuracy - deceptive dips in the current can cause early termination. A surprising amount of detail is contributed by even the smallest current levels. Our threshold is 1e-7 amps for 700 iterations.

[Samaras 2004] has a very useful set of experimental and FDTD data for calibration and comparison. Comparing a probe via source in the different positions, we obtained agreement of $\sim 7\%$ in impedance and $\sim 5\%$ in frequency.

The use of a hard source feed-port affects the number of timesteps required by introducing unphysical transients. Using a port with a virtual 50-ohm resistance reduces the computational requirements by a large factor; see [Luebbers 1996].

Simply monitoring the source current during the simulation is somewhat deceptive. Periodically monitoring the change in the fourier transform seems to be a better convergence metric.

The units of the FFT (unlike those of the continuous FT) remain in volts

\rule{\linewidth}{0.2pt}

Many equations in papers on the FDTD method are supplied without explicit scaling factors. For instance, for use with flaport/fdtd the H-field to current line integral in [] requires scaling by $\mu_0  (dx/dt)$, where $\mu_0$ is the vacuum magnetic permittivity, dx the cell size, and dt the timestep - despite the equation already possessing a deceptive set of $dx$-es.

Naturally, if one is competent, this discrepancy will be immediately obvious. Those not dimensionally-intuitive, such as myself, find it useful to run a test using a unit-aware calculator such as {\it sharkdp/insect}.

\rule{\linewidth}{0.2pt}

The impedance of a microstrip antenna varies with position on its plane. Probe feeds that couple a microstrip to a specific point are often used.

\rule{\linewidth}{0.2pt}

\label{para}
\ref{para}

\paragraph{Timeline}

\paragraph{Comments by others}

\paragraph{Lessons Learned} \

\rule{\linewidth}{0.2pt}

It may be helpful to think of simulations very similarly to IRL experiments.

A simulation is just a universe in a bottle that you can examine more closely; as with real-world, you can learn much from observation, but

But this need for documentation conflicts with the rapid, iterative cycle necessary for productivity.

This is obvious to all compentent, but when rapidly iteratively testing with simulations, it may be helpful to automatically save a package with images of all the components (schematics, graphs, input files) of each distinct test.

For comparison to experiment, having a webcam take an image of the assembled board is also helpful.

Version control alone isn't quite enough. Just having a simulation setup file somewhere in the commit history isn't "discoverable" - that is, you must be able to see what the input and output was without re-running the simulation.

Manually taking notes tended to disrupt the flow of testing; and in any case, just noting "SIR filter has appropriate phase response" is almost useless. What {\it was} the phase response? Plot it!

Software such as Sumatra, Sacred, recipy, and others. In our case, we used eLabFTW's elabapy bindings.

\rule{\linewidth}{0.2pt}

It is far easier to use existing, well-characterized reference designs verbatim than to modify

\rule{\linewidth}{0.2pt}

When rapidly testing data analyses which aren't really conducive to unit testing, I previously used to run the whole simulation, look at the analysis, re-run the sim, etc.

This is slow. I often don't change the input parameters for the sim, but just the analysis. However, there's often a large amount of state to persist to disk.

Saving the entire session with 'dill' is very helpful.

\rule{\linewidth}{0.2pt}

Software opacity is evil.

\rule{\linewidth}{0.2pt}

A great deal of time was spent trying to resolve version conflicts and dependency hells with the numerous libraries used by all the simulation programs. Over a week was spent trying to recursively track down all the This also wastes developer time - some fraction of issues raised are due to library version conflicts.

Packaged binaries help this slightly, but of course don't help if modifications are required, and managing shared libraries is still a tricky matter.

Good solutions include OpenFOAM's Docker installation. In some cases, using chroot with the original developer's Linux distribution is also of some utility.

But this all seems like quite a lot of overhead and opacity for what ultimately doesn't seem a super-complex problem: deterministically obtain a known-good version of a library, build locally, and set paths appropriately.

A good example might be gTest's cmake integration.

In the extreme, systems exist to extract every

In some situations (especially where the library has a permissive licence) perhaps it could be useful to consider packaging a complete, batteries-included 'known good' repository, either with the source of all the correct library versions included, or with a script to clone and compile the specific version used, integrating all the libraries with the build system.

For instance, this was done with the PDB reader in the OpenMM wrapper and JAMES.

\rule{\linewidth}{0.2pt}

There's also a very neat thing that seems to be common in computational biology, but which doesn't seem popular in other fields. After an algorithm or software tool is written (and the source published seperately), a simple CGI frontend is written around it and hosted on the university's servers. eLNemo and the CHARMMing web interface are advanced examples of this. This way, anyone with an input file can get results without futzing around with installation.

The computational biologists have beat us at our own game.

\rule{\linewidth}{0.2pt}

Write a paper to be understood; to be as clear and helpful as possible to the reader.

\rule{\linewidth}{0.2pt}

We have always encountered wasting extreme amounts of time on subtle assembly mistakes in hardware prototypes.

In one example in this project, many hours were wasted because the enamel insulation on a bodge wire had not burned off completely in the solder joint, leading to a high-impedance connection.

The same has occurred in previous projects; in one example, many days were spent debugging software to fix an apparently slow hardware interrupt, which ended up being the result of a poor solder paste stencil leading to a hidden high-impedance connection to a leadless package.

Many failures are perhaps the result of carelessness in modification and a lack of inspection; but others would only have been found by a 100\% electrical test.

If flying-probe or bed-of-nails tests can be made sufficiently rapid and closely coupled with the existing toolchain,

In {\it 2001: A space odyssey}, an automated system is shown guiding the troubleshooting of an assembly, apparently generating a fault tree of all the

Boundary-scan features might really help

\rule{\linewidth}{0.2pt}

The ability to almost immediately compare simulation to experiment was quite important.

\rule{\linewidth}{0.2pt}

\paragraph{Hall of Hubris} \

Lest our hats stop fitting

\rule{\linewidth}{0.2pt}

An inane remark:

\begin{displayquote}
We believe once we have the P. Syringae host, we from environmental samples
\end{displayquote}

Truly the depths of Dunning-Kruger.

\rule{\linewidth}{0.2pt}

An expert and distinguished gentleman that we contacted regarding assistance resolving transients in our microstrip VCO stated the following:

This was a perfectly sensible remark; it is almost always the case that (at X-band, no less!) a custom IC would have been needed to build a VCO.

Also, if taken in the context of a tired, overworked PI getting an unsolicited email from an excessively verbose undergraduate at a different university, I hardly think I would have replied differently.

However, I think this person may have missed out. Learning

So perhaps it is wise to ponder the ideas of fools for skeet; one always learns target practice, if only an example what not to do, and occasionally one learns positively. I have often found that I learn greatly from working on the projects of others.

We present this only as a cautionary tale in the hopes that someday I will listen.

\rule{\linewidth}{0.2pt}

%\end{multicols}

\Acrobatmenu{GoBack}{Back}

\end{document}

### 2020-06-28 electronics/ngspice/oscillator_designer_2.py

@@ -41,7 +41,8 @@ def run_sim(varactor_voltage):
     timesteps = ngspyce.vector('time')
     v_collector = ngspyce.vector('v(E1)')
     v_base = ngspyce.vector('v(Base)')
-    varactor_bias = ngspyce.vector('v(Base_)')
+    varactor_bias = ngspyce.vector('v(Vvaractor)')
+    output = ngspyce.vector('v(output)')
 
     stable_running_point = -1*len(v_collector)//3
     v_collector_trimmed = v_collector[stable_running_point:] # lots of noise on startup. we want to trim that out of the FFT.
@@ -60,13 +61,17 @@ def run_sim(varactor_voltage):
 
     fft_cleaned = fft_cleaned[:int(600)] # trim all spectra to the same length 2ps,800, 5ps, 600
     spectrum_freqs = spectrum_freqs[:int(600)]
-    return [np.array(np.abs(fft_cleaned)), np.array(spectrum_freqs), timesteps, v_collector, v_base, varactor_bias]
+    return [np.array(np.abs(fft_cleaned)), np.array(spectrum_freqs), timesteps, v_collector, v_base, varactor_bias, output]
 
 spectra = []
 values = []
 
 # values = []
-for i,v in enumerate(np.linspace(0, 20, 30)):
+
+# NUM_SPECTRA = 30
+NUM_SPECTRA = 5
+
+for i,v in enumerate(np.linspace(0, 20, NUM_SPECTRA)):
     values.append(run_sim(v))
     spectrum = values[i][0]
     if(not len(spectra)):
@@ -125,7 +130,10 @@ for i in values[0], values[-1]:
     plt.ylabel("V")
     plt.xlabel("T (nanoseconds)")
     plt.plot(i[2][-300:],i[3][-300:])
-
+    print(np.max(i[6][-300:]))
+    print(np.min(i[6][-300:]))
+    print(np.max(i[3][-300:]))
+    print(np.min(i[3][-300:]))
     plt.draw()
     plt.pause(0.001)
 

### 2020-06-29 documents/acknowledgement.tex
Lots of words.

--- 2020-06-28 documents/paper.tex
@@
-\documentclass[fleqn,10pt]{article}
-
-\include{preamble}
-
-\title{On the application of microwave acoustic resonant viral inactivation
-\thanks{I would be delighted to include any criticisms or comments anyone may have, both on substance and comprehensibility; preferably leave them on the GitHub issues page, or email therobotist@gmail.com, @0xDBFB7 on Twitter, or irc.0xDBFB7.com:6667 \#covid.}}
-\date{May 2020}
-\author{Based primarily on exceptional work by }
-
-\begin{document}
-
-\flushbottom 
-\maketitle
-\thispagestyle{empty}
-
-\begin{textblock}{5}(1,1)
-\noindent Please view the latest version at github.com/0xDBFB7/covidinator
-\end{textblock}
-%\begin{textblock}{5}(1,27)
-%\end{textblock}
-
-\null\begin{tabular}[t]{l@{}}
-  {Daniel Correia}\ \orcidlink{0000-0002-9353-0216}  \\
-  \textit{York University}
-\end{tabular}
-
-\begin{abstract}
-
-We extend this landmark work rather trivially by:\\
-
-Aims:
-
-\begin{itemize}
-  \item Establishing the time dependence of inactivation
-  \item Demonstrating a modulation scheme that decreases the inactivation threshold to below current safety levels in surrogate bacteriophage
-  \item Demonstrating a prototype emitter in an "electromagnetic mask" form-factor, costing about \$5 in prototype quantities, which can reasonably be produced in 10 million-of quantities
-  \item Testing power thresholds in various conditions; biological fluids of various conductivities and pHs
-  \item Using a coarse-grained molecular-dynamics simulation to optimize the impulse
-  \item Using a virus-in-the-loop optimization with a centrifugal microfluidic system
-  \item Discussing the biological basis for the safety of the device
-  \item Showing that the deviation from the expected theshold could be explained by variance in the
-
-\end{itemize}
-
-{Perhaps notable that a completely free and open-source toolchain was used for the entire project, including FDTD microwave antenna optimization. This work can be replicated with \$500 in equipment.}
-
-\end{abstract}
-
-\begin{autem}
-	{\large  \it autem} \\
-
-	This work was prepared by an undergraduate and has not been peer-reviewed. Additionally, the author has no prior experience with either biology or microwave design. \\
-
-	While our study is very simple, biology is of such complexity that a tremendous amount of care must be taken before any conclusion can be drawn at all.
-It is not likely that we have taken sufficient care.\\
-
-This is especially true with RF biophysics. The literature is littered with otherwise impeccably perormed research which was later demonstrated to be an artifact. \\
-
-	Though the original research used Inf. A, our testing was only performed with a surrogate bacteriophage. All experiments must be repeated with SARS-NCoV-2. \\
-
-	Additionally, other sterilization techniques may produce superior results and should be evaluated in the same context. Data on far UV [Buonanno 2017] indicate safety.\\
-
-It has occurred before that otherwise striking resonances were detected and replication found them to be artifacts of the measurement equipment. [Foster 1987] even offers this disclaimer:
-
-"To detect the DNA resonances with the probe
-technique requires correction for system errors that are
-potentially much larger than the effect to be studied and
-lead to resonance-like artifacts. This is true even with the
-more precise instrumentation used in this study. Such data
-are easily misinterpreted, and we suggest this might have
-happened in the former study."
-
-The direct inactivation plaque and PCR data from [Yang], replicated by [Sun], is a somewhat convincing corroboration that this effect is not an artifact, but hundreds of convincing and  wrong papers exist in the literature.
-Our data is crude and imprecise, our equipment hastily constructed, and should not be considered validation of this effect even existing.
-\\
-
-	Please consider all claims with appropriate skepticism.
-
-\end{autem}
-
-\begin{multicols}{1}
-
-With typical 2.4 GHz microwave exposure, sterilization can only occur by heating of the fluid and tissue.
-
-Of course, the temperature of the atoms of the virus undoubtedly increase; but the
-
-\begin{toolchain}
-	{\it \bf [Yang 2015]'s toolchain}
-	\begin{itemize}
-	\item Envelope/liposome breaking strength and stiffness from AFM nanoindentation data
-	\item Analytical expression assuming homogenous sphere for microwave absorption cross-section
-	\item Experimental absorption data from microwave cuvette -> 
-	\item COMSOL finite-element for illustration
-	\end{itemize}
-\end{toolchain}
-
-\end{multicols}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\clearpage
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The chain of literature Fruluch -> ([Sun ] | [Yang 2015]) establishes that spherical virions possess a weak dipole resonance mode which happens to fall within the microwave spectrum, at approximately the X-band (6-10 GHz).
-
-This is a non-ionizing, non-thermal technique;
-
-This resonance mode
-
-The myth that 2.4 GHz was chosen because it "couples strongly with water" is largely false; but this is
-
-This is quite surprising, and should perhaps be considered with some trepidation, since
-
-\paragraph{\textbf{Time dependence}}\
-
-Both Yang and [] used an apparently arbitrary 15-minute exposure in their tests - a very reasonable decision given the focus of their paper.
-
-The effectiveness against airborne particles, and to minimize the power required in a dwelling phased-array beam, we must first establish the required duration of exposure.
-
-{\color{red} speculative hypothesizing \{ }
-
-In contrast to chemical inactivation, where the time dependence appears to be dominated by viscous fluid dynamic effects [Hirose 2017], or UV inactivation, where a certain quantized dose of photons must be absorbed, we expected RF to act instantaneously.
-
-As a damped, driven oscillator, the ring-up time of the virus depends on the Q factor.
-Yang et al.
-state the Q of Inf.
-A as between 2 and 10, so at 8 GHz the steady-state amplitude should be reached in well under 100 nanoseconds.???????????FIXME
-
-[] found a significant mechanical fatigue effect in phage capsids, where a small strain applied repetitively eventually causes a fracture.
-Such a mechanism could perhaps extend the exposure required to break the capsid or membrane.
-Other mechanisms could include some sort of lipid denaturation, requiring an absolute amount of energy absorption to break or twist bonds and modify the properties before the envelope fractures.
-
-{\color{red}  \} }
-
-\footnote{All values have been converted to $W/m^2$ to avoid confusion.}
-
-\subfile{safety}
-
-\clearpage
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{multicols}{1}
-{\Large Biology}\\
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\paragraph{\textbf{Centrifugal microfluidics}}\
-
-The field of centrifugal microfluidics is accelerating.
-
-Many CD microfluidics systems use standard CD molding techniques for the channels and machining techniques, using either acrylic or silicone.
-The turbidity sensor is most sensitive if the plastic is clear.
-Sterilization does not seem to be discussed.
-
-Polypropylene is the ideal material, being almost indefinitely autoclavable. It is quite difficult to machine.
-
-\end{multicols}
-
-\clearpage
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{multicols}{1}
-{\Large Modes of application}\\
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\paragraph{\textbf{Personal 'electromagnetic mask'}}\
-
-Even with judicious use of phased-arrays, spatial power-combining, etc, each transistor can only reasonably sterilize approx. $ 1 \text{ m}^3 $.
-
-We therefore demonstrate this form factor because, superficially, there are fewer people than there are places.
-
-On the other hand, a personal device may present issues with participation and production volume.
-
-\paragraph{\textbf{Direct treatments}}\
-
-[Hand 1982] $E_{mag}=1/e$ (13.5\% power density) skin\footnote{electromagnetic skin, not tissue skin}\footnote{well, both, I suppose.} depth is approximately:
-
-\begin{center}
-\begin{tabular}{|l|l|l|}
-\hline
-F=10 GHz          & Dry tissue & Wet tissue \\ \hline
-Penetration depth & 30 mm      & 5 mm \\ \hline
-\end{tabular}
-\end{center}
-
-SARS is found widely distributed throughout the most favorable organs [Ding 2004], shielded by an average of 4 cm of chest wall [Schroeder 2013]; so safe external treatment of the body is unlikely.
-
-However, destruction of lung tissue appears to be the primary cause of death via SARS [Nicholls 2006].
-
-A bronchoscopic technique may therefore be effective, very similarly to that demonstrated by [Yuan 2019]: the bronchi are less than 2 mm thick [Theriault 2018] and the lungs themselves are only on the order of 7 mm thick [Chekan 2016].
-
-There is considerable tolerance in the
-
-Further study is required to validate this method.
-
-\paragraph{\textbf{More fanciful concepts}}\
-
-Many systems operate in these X-band frequency ranges; and precision
-
-It is relatively easy to produce megawatts of power at these frequency ranges using Klystrons.
-
-Existing marine, weather, and aviation radar systems often use the X-band; depending on the focusing power
-
-\paragraph{}
-
-Finally, there is one concern.
-Use of this technique will provide a selection bias towards immunity to electromagnetic fields, which could perhaps be effected by preferring extreme-sized mutants (shifting the resonance away from the applied field).
-We do not have the biological knowledge to know if this is plausible; it is simply worth mentioning.
-
-\end{multicols}
-
-\clearpage
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{multicols}{1}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\noindent\fbox{\parbox{\linewidth}{
-	Toolchain:
-	\begin{itemize}
-	\item Failed oscillator feedback-loop optimization toolchain: QUCS 0.0.20 + python-qucs + scipy's 'basinhopper'
-	\item Successful A slightly modified ngspice + ngspyce + pyEVTK
-	\item gprMax for FDTD EM simulation
-	\item KiCAD, wcalc, scikit-rf, ngspice
-	\end{itemize}
-}}
-%
-
-The oscillator is a 'wideband double-tuned varactor VCO', based almost verbatim on [Tsuru 2008] and the reference design in Figure 8.36, p378 of [Grebennikov 2007].
-
-The rest of the papers in the bibliography were highly enlightening regarding the principles of microwave oscillator design.
-
-This topology of oscillator worked marvellously on essentially the first try.
-
-The process by which we failed miserably to design our own oscillator topology is detailed in the supplemental.
-
-The following properties: P1dB
-
-For ease of design and simulation, a device with Touchstone S-parameters and SPICE files is greatly preferable.
-
-It is commonly claimed that FR4 is a 'slow' substrate, and that the high loss tangent of ~0.02 makes it unsuitable for microwave systems.
-
-However, with this PCB substrate, the expected loss of only 0.026 dB/mm on signals of minimum 0 dBm is patently acceptable.
-As viruses do not have a discriminating palate, we are also only minimally concerned with $S_{11}$ reflections, noise, or spurs, so precise impedance control is not required; the wideband VCO sweep accomodates for any variations in resonant frequency due to wide manufacturing tolerances.
-
-As a result of our gross incompetence, the oscillator was designed via an inane, roundabout, and fiendishly tedious manner, and our description of this technique only contributes to the field by being suitable for a dartboard; our analysis can only hold water when combined with paper mache; and a lesser invertebrate in posession of a copy of Microwave Oscillator Design would have accomplished the task faster.
-
-Designing an oscillator of this type in one step with a few kindergarten equations appears to be well within the reach of modern network analytical techniques.
-Genetic algorithms are quite well matched to this problem, and many commercial software packages are  [computer microwave design book].
-
-Initially,
-
-Not having a good analytical understanding, we resorted to using a purely computational method.
-
-In addition, the design of wideband feedback-loop VCOs is a relatively well-explored field, and many reference designs exist.
-
-The key sticking point - which we missed - seems to be that at these scales, using microstrip design techniques, the parasitics of any possible filter structure are so large that the small change in impedance that varactors can provide cannot tune the circuit by any meaningful amount.
-
-"Using the lead inductances of the bipolar transistor and varactors provides the required value of the base inductance".
-
-Indeed, [Tsuru 2008]'s "tuned circuit" in Fig 8 is, in fact, just the varactors, plus an almost invisible high-impedance line.
-
-Several analytical filter design methods were
-
-This is apparently known as a "double-tuned" wideband.
-
-%
-\paragraph{\textbf{The feedback loop oscillator}}\
-
-Oscillators must meet the Barkhausen criterion:
-
-\begin{itemize}
-
-\item A 360 degree phase shift around the feedback loop (including the phase shift contribution from the amplifier, which itself varies greatly with frequency)
-\item A loop gain $>1.$
-
-\end{itemize}\
-%
-However, a third element is also required:
-%
-\begin{itemize}
-\item A frequency-selective element that restricts oscillation modes and decreases phase noise.
-\end{itemize}
-%
-
-With large feedback-loop structures, such as long PiN-switched phasing lines, proximity effects from nearby flesh would detune the oscillator significantly.
-
- design of a triple-tuned oscillator.
-
-\paragraph{}
-The buffer amplifiers
-
-\paragraph{Biasing}\
-
-In our simulations, the varactor-tuned feedback circuit appeared to be particularly sensitive to the introduction of bias-tees.
-
-The gate must be weakly pulled to ground, otherwise stray charge destroys the oscillation.
-
-\fancyhead[C]{style 1 with thin line}
-
-With 0.79 mm FR4 substrate and 0.2 mm (8 mil) wide traces, the maximum impedance achievable was about 115 ohms, which did not appear to be sufficient as an RF choke.
-Use of defected grounds can increase inductance, but this was not evaluated.
-
-If suitably high-impedance traces are not available, a common technique is to use a quarter-wavelength line (approximately 6 mm long with the above parameters at 8 GHz) terminated with a stub to produce a virtual short or open circuit [Seo 2007].
-
-However, reflections from these structures still appeared to distort the frequency/phase response beyond repair, even with ostensibly wideband stubs [Syrett 1980].
-
-\noindent\fbox{\parbox{\linewidth}{
-	Rebuke: despite this blather, many other papers have had success with bias-tees at these frequencies.
-}}
-
-Alternate methods evaluated, failures:
-
-In production, these could be accomodated by graphite-polymer printed resistors.
-
-Odd-pole varactor-loaded combline filters appeared to have excellent phase and frequency response; however, the geometry necessitates low-inductance via stitching to the ground plane.
-
-%\noindent\fbox{\parbox{\linewidth}{
-\begin{autem}
-	{\it autem} Others have had great success with varactor-tuned comblines, especially non-grounded lines.
-\end{autem}
-
-[Tsuru 2008 fig. 10] is an excellent review of various oscillator designs.
-
-The parasitic inductance of common varactors appears to become problematic at these frequencies (but not for non-wideband use).
-
-\paragraph{\textbf{Spacing}}\
-
-FDTD results still yielded some coupling at 2 mm isolation.
-
-\paragraph{\textbf{Via stitching}}\
-
-Rather than the almost universal technique of via stitching components immediately to the ground plane (a tedious process with our prototyping setup), a large ground pour on the component layer was used wherever ground was needed, as mentioned in [Hunter?
-combline].
-Since we use microstrip rather than coplanar waveguide,
-
-Since the ground plane does not participate in the DC bias at all, no vias are required in the final device.
-This means that the drilling, electroless strike and electroplating steps are unnecessary for production.
-
-\clearpage
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-{\Large Mass production}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-If this 'electromagnetic mask' form is the ideal (not nearly ), a minimum of 5 GaAs or SiGe:C transistors will be required.
-
-There are, for instance, 1 million hospital beds in the U.S. [AHA 2018].
-
-It is difficult to determine the supply capacity for these modern semiconductor processes. A few fermi est
-
-GaAs MMIC market of \$2.2 Bn USD / random sample of MMIC prices =
-
-3e9 wifi connected devices produced each year.
-
-The largest RFID plants can produce
-
-The techniques and equipment required to produce these are non-trivial. SiGe:C, for instance, requires,
-
-Figures are not forthcoming,
-
-Given the supply difficulties of comparatively simple materials such as Tyvek at pandemic scales, it is difficult to imagine that RF semiconductor production can be immediately re-tasked and scaled to this degree.
-
-\paragraph{\textbf{Vacuum RF triode}}\
-
-One concern is the large filament heater power, which prevents the use of low-cost button cells for power.
-Use of cold-cathode field-emitter arrays would alleviate this issue, but at the cost of complexity.
-
-Small tungsten incandescent lights are available down to 0.05 watts. With a suitable high-efficiency cathode coating, a pulsed heater power of less than 0.02
-
-\end{multicols}
-
 \clearpage
@@
 One Very Important Thought
-
-\subfile{supplemental}
-
-\end{document}

### 2020-06-29 documents/safety.tex
Lots of words.

\documentclass[paper.tex]{subfiles}
\begin{document}

\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{multicols}{1}
{\Large Safety}\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Because this is an ostensibly novel and niche mechanism, it may behoove us to breifly review the biological basis for the safety limits set by standards organizations. \footnote{The idea of biological microwave resonances appears to have originated in [Frohlich 1968, 1980].} a loophole in the guidelines

\includegraphics[scale=0.5]{cells.png}

\footnote{Contrary to some [Hardell 2017] reports, we do not find the FCC and ICNIRP to be significantly affected by special interest groups; their rationales appear to be transparent.  [FCC-19-126A1] an FCC memorandum wherein the FCC tells groups to respectfully screw themselves no fewer than three times: ''Similarly, IEEE-ICES urges the Commission to
adopt a higher SAR exposure limit of 2 W/kg averaged over 10 g. [snip] We are not persuaded that the IEC standard should be adopted at this time.", "Medtronic and the AAMI-CRMD recommend a more relaxed threshold of 20 mW. We decline to increase the 1-mW threshold.". Things heating up at the Microwave Safety fandom.}

There are also things.

For instance, it is reasonable to wonder why we might not see such resonances in bodily tissues. Approximately similar nanoscopic structures exist in humans, such as nuclear pores (120 nm) and the famous microtubules (10x50 nm).

While from which epidemiological data could be derived.\footnote{The cloud service [scite.ai] was irreplaceable during this. It's like a mirror to an alternate universe where literature made sense.}

What we find is a messy affair. Biology is hard.

\rule{\linewidth}{0.2pt}

There are some 20,000 papers on the topic of RF safety, with solid in vitro, in vivo and epidemiological evidence of safety in the 2.4 GHz and 5.8 GHz bands.

However, "There are limited experimental human data upon which to set limits on exposures above 6 GHz" [Chan 2019]. Only 2\% of the above papers are on frequencies $>6$ GHz [Vijayalaxmi 2018].

In addition, what data remains in this category is of varying quality.

As has been starkly demonstrated in the recent hydroxychloroquine contradictions [Gautret 2020] [Geleris 2020], biological research must be essentially perfect to have any meaning at all.

The IEEE standard which the flagship paper [Yang 2015] references [IEEE C95.1-2005] was recently overhauled [IEEE C95.1-2019] with new metrics.

[Vijayalaxmi 2018] is a remarkable meta-analysis of in vitro data. They synthesize a quality score, rating bindedness, sham controls, dosimetry, and sample size. Quality was inversely, monotonically related to the effect size. An example of the subtle effects that can call into question superfically reasonable results are [

They additionally find a publication bias of incredible magnitude in the positive (harm) direction in this field, further degrading the usefulness of statistical analyeses.

An example of a relevant study that they grade as "quality 1" [Karaca 2011]. This study's conclusion is that However, in figure 5, one can see that only 1 out of 11 genes tested had a statistically significant difference in expression. Given the N=6 cultures,

\rule{\linewidth}{0.2pt}

[Adair 2002] demonstrate theoretically that acoustic resonances are, in general, highly unlikely in biological solvents, primarily focusing on DNA. All resonance modes are strongly overdamped by the surrounding solvent, and no amplitude amplification can take place.

This analysis would seem to disagree with the viral resonance apparently conclusively demonstrated by [Yang 2015] - the PCR result seems especially inarguable. This could be explained by the large charge on the virus compared to the molecules analyzed in Adair. [Yang 2015] find a charge of order $10^7 e$, whereas Adair analyzes a very different regime, "assume coupling to the field through single charges q = e at each end".

[Liu 2009] cite [Edwards, Swicord 1984], saying: "It was proposed that a hydration layer surrounding DNA molecules could lower the viscoelastic transition
frequency, raise the quality factor of confined acoustic vibrations, and result in a microwave resonant absorption".

But [Adair 2002]'s [Foster 1987] seem to quite conclusively put the kibosh on that idea, demonstrating no resonances in DNA with 20x higher precision than previous work, showing previous results to be an artifact of the measurement equipment.

The supplemental material to [Vijayalaxmi 2018] has a table of studies on this topic. High-quality research in-vitro concurs with.

\paragraph{[Manikowska 1979]} \

9.4 GHz pulsed / in vivo, mouse, $0.1-10 \text{mW}/\text{m}^2$ over the whole body for 2 weeks. N=16.

This is a particularly concerning result, especially given their $p<0.001$. [Servantie 1989] discusses the (admittedly circuituious) route by which birth defects could occur.

Work by [Manikowska 1985] in the 2.4 GHz range has been contradicted [Beechey 1986], but the 9 GHz range does not appear to have been repeated.

\rule{\linewidth}{0.2pt}

More modern research [Juutilainen 2011], [Chemeris], [Vijayalaxmi 2006],  does not tend to agree with these concerns. As cited by [ICNIRP 2020]'s excellent literature review, expose lymphocyte blood cells to 8 ns pulsed 8.2 GHz radiation for 2 hours at an average power of $10 \text{mW/cm}^2$. They find no change in any of the parameters measured, including various chromosomal parameters. They further discuss previous results.

\rule{\linewidth}{0.2pt}

In the frequency range of interest, there seems to be good-quality in-vitro evidence using lymphocytes of lack of harm. We are not aware of any high-quality in vivo or epidemeological data from which useful conclusions can be drawn.

We must defer to health experts for interpretation of these data.

\rule{\linewidth}{0.2pt}

{\it Please contact the author if you are aware of other salient research, or have a different interpretation.}

\end{multicols}

\end{document}

### 2020-06-29 documents/supplemental.tex
Lots of words.

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-{\Large Captain's Log, Supplemental}\\
+{\Huge Captain's Log, Supplemental}\\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Coarse-graining also greatly increases the allowable timestep.
+
+We also did not understand the *confined* part in the *confined* acoustic resonance.
+
+Simulating the aggregate bose condensate wavefunction is well beyond us.
 
@@
 
+\PRLsep{{\itshape Wherein an oscillator is designed }}
+
+\paragraph{Biasing}\
+
+In our simulations, the varactor-tuned feedback circuit appeared to be particularly sensitive to the introduction of bias-tees.
+
+The gate must be weakly pulled to ground, otherwise stray charge destroys the oscillation.
+
+\fancyhead[C]{style 1 with thin line}
+
+With 0.79 mm FR4 substrate and 0.2 mm (8 mil) wide traces, the maximum impedance achievable was about 115 ohms, which did not appear to be sufficient as an RF choke.
+Use of defected grounds can increase inductance, but this was not evaluated.
+
+If suitably high-impedance traces are not available, a common technique is to use a quarter-wavelength line (approximately 6 mm long with the above parameters at 8 GHz) terminated with a stub to produce a virtual short or open circuit [Seo 2007].
+
+However, reflections from these structures still appeared to distort the frequency/phase response beyond repair, even with ostensibly wideband stubs [Syrett 1980].
+
+\noindent\fbox{\parbox{\linewidth}{
+	Rebuke: despite this blather, many other papers have had success with bias-tees at these frequencies.
+}}
+
+Alternate methods evaluated, failures:
+
+In production, these could be accomodated by graphite-polymer printed resistors.
+
+Odd-pole varactor-loaded combline filters appeared to have excellent phase and frequency response; however, the geometry necessitates low-inductance via stitching to the ground plane.
+
+%\noindent\fbox{\parbox{\linewidth}{
+\begin{autem}
+	{\it autem} Others have had great success with varactor-tuned comblines, especially non-grounded lines.
+\end{autem}
+
+[Tsuru 2008 fig. 10] is an excellent review of various oscillator designs.
+
+The parasitic inductance of common varactors appears to become problematic at these frequencies (but not for non-wideband use).
+
+\paragraph{\textbf{Spacing}}\
+
+FDTD results still yielded some coupling at 2 mm isolation.
+
+\paragraph{\textbf{Via stitching}}\
+
+Rather than the almost universal technique of via stitching components immediately to the ground plane (a tedious process with our prototyping setup), a large ground pour on the component layer was used wherever ground was needed, as mentioned in [Hunter?
+combline].
+Since we use microstrip rather than coplanar waveguide,
+
+Since the ground plane does not participate in the DC bias at all, no vias are required in the final device.
+This means that the drilling, electroless strike and electroplating steps are unnecessary for production.
+
+\paragraph{A}
 \rule{\linewidth}{0.2pt}
+
+Microwave design has a reputation for being the purview of wizards. The software [Microwave Office], Agilent ADS, or Mathworks
+
+It seems there's a subset of these, where wide tolerances and poor performance are acceptable, that does not require a goatee or the sale of firstborn.
+
+Before about 2005, however, it seems to have been somewhat the norm to write a simple numerical code to solve the problem at hand based on underlying principles.
+
+We are also aided by the fact that what took a \$150,000 computing cluster a decade ago can be done in a few minutes by a single budget GPU.
+
+With judicious application of reference designs, it seems to be possible to design
 
@@
 
-\includegraphics[scale=0.5]{3d_spectrum_2.png}
+\begin{figure}[H]
+\includegraphics[width=\textwidth]{3d_spectrum_2.png}
+\end{figure}
 
 The complete transient simulation matched reality very closely.
+
+"Wideband", p. 378, Figure 8.36, dnw
+
+\begin{figure}[H]
+	\includesvg[width=\textwidth]{wideband_LO_2_simulated_tuning}
+ 	\caption{"Wideband VCO 2": BFP620  \\
+ 	 Oscillator tuning simulated with electronics/ngspice/oscillator\_designer\_2.py commit <>, eLabID 20200613-d28a8004c...}
+\end{figure}
+
+The pad size
 
@@
 
-\rule{\linewidth}{0.2pt}
+\PRLsep{{\itshape Wherein an oscillator is designed }}
 
-Originally tried
+\clearpage
+\PRLsep{ Wherein antennas are characterized}
 

### 2020-06-30 documents/paper.tex
Modelling distribution

@@
   {Daniel Correia}\ \orcidlink{0000-0002-9353-0216}  \\
-  \textit{York University}
+  \textit{????????? York??????}
 \end{tabular}
@@
 
-	Additionally, other sterilization techniques may produce superior results and should be evaluated in the same context. Data on far UV [Buonanno 2017] indicate safety.\\
+	Additionally, other sterilization techniques may produce superior results with less faffing about and should be evaluated in the same context. Data on far UV [Buonanno 2017] indicates safety.\\
 
@@
 
+\clearpage
 \begin{multicols}{1}
+
+\paragraph{{\Large the gist}}\
+
+Any claims of
+
+The chain of literature 
+%
+[Fr\"{o}hlich 1968] \textrightarrow \ [Fr\"{o}hlich 1980] \textrightarrow \ [Liu 2009] \textrightarrow \ ([Hung 2014] $\parallel$ [Yang 2015] $\parallel$ [Sun 2017])\footnote{We have probably missed several steps in this chain out of haste.} apparently culminates in the flagship work we focus on in this paper,
+
+{\it Efficient Structure Resonance Energy Transfer from Microwaves to Confined Acoustic Vibrations in Viruses} [Yang 2015].
+%
+
+estabilishes that - unique to certain viruses, and apparently unlike human cell structures, as we shall see - coincidentally have just the right size, shape, stiffness, and net charge distribution to form a weak (Q=2) spherical dipole resonance mode which couples well to the microwave spectrum at approximately the X-band (6-10 GHz).
+
+More critically, [Yang 2015] (in parallel with [Hung 2014]) theoretically model and then experimentally demonstrate that the electric field strength required to produce an amplitude of vibration sufficient to tear the lipid envelope of the order of magnitude of 100 V/m.
+
+They demonstrate this with both a plaque and PCR assay, with fantastic agreement to the theoretical model.
+
+This is a non-ionizing, non-thermal technique.
+
+Microwave resonant absorption of viruses through dipolar coupling with confined acoustic vibrations
+
+This resonance mode
+
+The myth that 2.4 GHz was chosen because it "couples strongly with water" is largely false; but this is
+
+This is quite surprising, and should perhaps be considered with some trepidation, since
+
+\footnote{This {\it confined} acoustic resonance is apparently distinct from common-and-garden pipe-organ acoustic resonance.
+Rather than simple covalent or Lennard-Jones interaction between particles, if [Fr\"{o}hlich 1968] is to be believed at these nanoscopic scales a sort of coherent wavefunction is set up among the particles of the virus which produces coupling modes not otherwise expected.
+We confess to not yet understanding this phenomenon; fortunately, while helpful, the details of how this mode appears is not critical to implementing this technique.}
+
+\footnote{``{For example, below about 6 GHz, where EMFs penetrate deep into tissue (and thus require depth to be considered), it is useful to describe this in terms of “specific energy absorption rate” (SAR), which is the power absorbed per unit mass $(W/kg)$.
+Conversely, above 6 GHz, where EMFs are absorbed more superficially (making depth less relevant), it is useful to describe exposure in terms of the density of absorbed power over area $W/m^2$, which we refer to as “absorbed power density”}'' [ICNIRP 2020 \faExternalLink] }
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \clearpage
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The chain of literature Fruluch -> ([Sun ] | [Yang 2015]) establishes that spherical virions possess a weak dipole resonance mode which happens to fall within the microwave spectrum, at approximately the X-band (6-10 GHz).
-
-This is a non-ionizing, non-thermal technique;
-
-This resonance mode
-
-The myth that 2.4 GHz was chosen because it "couples strongly with water" is largely false; but this is
-
-This is quite surprising, and should perhaps be considered with some trepidation, since
-
 \paragraph{\textbf{Time dependence}}\
@@
 
-\footnote{All values have been converted to $W/m^2$ to avoid confusion.}
+\footnote{All values have been converted to $\text{W/m}^2$ to avoid confusion. 100 $\text{W/m}^2 = 50 \text{mW/cm}^2$}
 
@@
 
-A bronchoscopic technique may therefore be effective, very similarly to that demonstrated by [Yuan 2019]: the bronchi are less than 2 mm thick [Theriault 2018] and the lungs themselves are only on the order of 7 mm thick [Chekan 2016].
+A bronchoscopic technique may therefore be effective, very similarly to that demonstrated by [Yuan 2019]: in adults, the bronchi are less than 2 mm thick [Theriault 2018] and the lungs themselves are only on the order of 7 mm thick [Chekan 2016].
 
-There is considerable tolerance in the
-
-Further study is required to validate this method.
+The main bronchus is about 8 mm in diameter, which is smaller than the patch antenna used here; a monopole (or multiple, phased monopoles) like is probably more suitable.
 
@@
 
-\paragraph{Biasing}\
-
-In our simulations, the varactor-tuned feedback circuit appeared to be particularly sensitive to the introduction of bias-tees.
-
-The gate must be weakly pulled to ground, otherwise stray charge destroys the oscillation.
-
-\fancyhead[C]{style 1 with thin line}
-
-With 0.79 mm FR4 substrate and 0.2 mm (8 mil) wide traces, the maximum impedance achievable was about 115 ohms, which did not appear to be sufficient as an RF choke.
-Use of defected grounds can increase inductance, but this was not evaluated.
-
-If suitably high-impedance traces are not available, a common technique is to use a quarter-wavelength line (approximately 6 mm long with the above parameters at 8 GHz) terminated with a stub to produce a virtual short or open circuit [Seo 2007].
-
-However, reflections from these structures still appeared to distort the frequency/phase response beyond repair, even with ostensibly wideband stubs [Syrett 1980].
-
-\noindent\fbox{\parbox{\linewidth}{
-	Rebuke: despite this blather, many other papers have had success with bias-tees at these frequencies.
-}}
-
-Alternate methods evaluated, failures:
-
-In production, these could be accomodated by graphite-polymer printed resistors.
-
-Odd-pole varactor-loaded combline filters appeared to have excellent phase and frequency response; however, the geometry necessitates low-inductance via stitching to the ground plane.
-
-%\noindent\fbox{\parbox{\linewidth}{
-\begin{autem}
-	{\it autem} Others have had great success with varactor-tuned comblines, especially non-grounded lines.
-\end{autem}
-
-[Tsuru 2008 fig. 10] is an excellent review of various oscillator designs.
-
-The parasitic inductance of common varactors appears to become problematic at these frequencies (but not for non-wideband use).
-
-\paragraph{\textbf{Spacing}}\
-
-FDTD results still yielded some coupling at 2 mm isolation.
-
-\paragraph{\textbf{Via stitching}}\
-
-Rather than the almost universal technique of via stitching components immediately to the ground plane (a tedious process with our prototyping setup), a large ground pour on the component layer was used wherever ground was needed, as mentioned in [Hunter?
-combline].
-Since we use microstrip rather than coplanar waveguide,
-
-Since the ground plane does not participate in the DC bias at all, no vias are required in the final device.
-This means that the drilling, electroless strike and electroplating steps are unnecessary for production.
-
 \clearpage
@@
 
-\clearpage
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph{Acknowledgements}\
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-This paper is not novel enough to deserve this chapter, but those to be acknowledged are.
-
-The authors of the original papers deserve the credit for this entire work;  it is rare that such a monumental finding is served on a silver platter.
-
-Professor Shahramian's excellent video blog {\it The Signal Path} inspired this work.
-
-Dr. Dainis' videos on microbiological technique were also useful.
-
-Thanks to the professors at York and beyond for returning my emails.
-
-Thanks to L.H. for wisdom regarding this project.
-
-Thanks to P.B and H.P. for tolerating ramblings and M. for the hug.
-
-Special thanks to all the people - most equally capable of writing this paper if provided the opportunity - who work menial shifts at the component suppliers that remained open that were so critical.
-Hopfstader be damned; despite the name below the abstract, this paper is of course entirely the result of circumstance and luck.
-
-Chiefly among the enablers are of course my parents, Doris and Brian, without whom this work would have been done by someone else, and who also supported this work financially.
-
-One Very Important Thought
+\subfile{acknowledgement}
 

### 2020-07-01 documents/introduction.tex
Added spring-constant variation

--- 2020-06-30 documents/paper.tex
@@
-\documentclass[fleqn,10pt]{article}
-
-\include{preamble}
-
 \title{On the application of microwave acoustic resonant viral inactivation
@@
 \end{autem}
-
-\clearpage
-\begin{multicols}{1}
-
-\paragraph{{\Large the gist}}\
-
-Any claims of
-
-The chain of literature 
-%
-[Fr\"{o}hlich 1968] \textrightarrow \ [Fr\"{o}hlich 1980] \textrightarrow \ [Liu 2009] \textrightarrow \ ([Hung 2014] $\parallel$ [Yang 2015] $\parallel$ [Sun 2017])\footnote{We have probably missed several steps in this chain out of haste.} apparently culminates in the flagship work we focus on in this paper,
-
-{\it Efficient Structure Resonance Energy Transfer from Microwaves to Confined Acoustic Vibrations in Viruses} [Yang 2015].
-%
-
-estabilishes that - unique to certain viruses, and apparently unlike human cell structures, as we shall see - coincidentally have just the right size, shape, stiffness, and net charge distribution to form a weak (Q=2) spherical dipole resonance mode which couples well to the microwave spectrum at approximately the X-band (6-10 GHz).
-
-More critically, [Yang 2015] (in parallel with [Hung 2014]) theoretically model and then experimentally demonstrate that the electric field strength required to produce an amplitude of vibration sufficient to tear the lipid envelope of the order of magnitude of 100 V/m.
-
-They demonstrate this with both a plaque and PCR assay, with fantastic agreement to the theoretical model.
-
-This is a non-ionizing, non-thermal technique.
-
-Microwave resonant absorption of viruses through dipolar coupling with confined acoustic vibrations
-
-This resonance mode
-
-The myth that 2.4 GHz was chosen because it "couples strongly with water" is largely false; but this is
-
-This is quite surprising, and should perhaps be considered with some trepidation, since
-
-\footnote{This {\it confined} acoustic resonance is apparently distinct from common-and-garden pipe-organ acoustic resonance.
-Rather than simple covalent or Lennard-Jones interaction between particles, if [Fr\"{o}hlich 1968] is to be believed at these nanoscopic scales a sort of coherent wavefunction is set up among the particles of the virus which produces coupling modes not otherwise expected.
-We confess to not yet understanding this phenomenon; fortunately, while helpful, the details of how this mode appears is not critical to implementing this technique.}
-
-\footnote{``{For example, below about 6 GHz, where EMFs penetrate deep into tissue (and thus require depth to be considered), it is useful to describe this in terms of “specific energy absorption rate” (SAR), which is the power absorbed per unit mass $(W/kg)$.
-Conversely, above 6 GHz, where EMFs are absorbed more superficially (making depth less relevant), it is useful to describe exposure in terms of the density of absorbed power over area $W/m^2$, which we refer to as “absorbed power density”}'' [ICNIRP 2020 \faExternalLink] }
-
-With typical 2.4 GHz microwave exposure, sterilization can only occur by heating of the fluid and tissue.
-
-Of course, the temperature of the atoms of the virus undoubtedly increase; but the
-
-\begin{toolchain}
-	{\it \bf [Yang 2015]'s toolchain}
-	\begin{itemize}
-	\item Envelope/liposome breaking strength and stiffness from AFM nanoindentation data
-	\item Analytical expression assuming homogenous sphere for microwave absorption cross-section
-	\item Experimental absorption data from microwave cuvette -> 
-	\item COMSOL finite-element for illustration
-	\end{itemize}
-\end{toolchain}
-
-\end{multicols}
-
-\clearpage
-\paragraph{\textbf{Time dependence}}\
-
-Both Yang and [] used an apparently arbitrary 15-minute exposure in their tests - a very reasonable decision given the focus of their paper.
-
-The effectiveness against airborne particles, and to minimize the power required in a dwelling phased-array beam, we must first establish the required duration of exposure.
-
-{\color{red} speculative hypothesizing \{ }
-
-In contrast to chemical inactivation, where the time dependence appears to be dominated by viscous fluid dynamic effects [Hirose 2017], or UV inactivation, where a certain quantized dose of photons must be absorbed, we expected RF to act instantaneously.
-
-As a damped, driven oscillator, the ring-up time of the virus depends on the Q factor.
-Yang et al.
-state the Q of Inf.
-A as between 2 and 10, so at 8 GHz the steady-state amplitude should be reached in well under 100 nanoseconds.???????????FIXME
-
-[] found a significant mechanical fatigue effect in phage capsids, where a small strain applied repetitively eventually causes a fracture.
-Such a mechanism could perhaps extend the exposure required to break the capsid or membrane.
-Other mechanisms could include some sort of lipid denaturation, requiring an absolute amount of energy absorption to break or twist bonds and modify the properties before the envelope fractures.
-
-{\color{red}  \} }
-
-\footnote{All values have been converted to $\text{W/m}^2$ to avoid confusion. 100 $\text{W/m}^2 = 50 \text{mW/cm}^2$}
-
-\subfile{safety}
-
-\clearpage
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{multicols}{1}
-{\Large Biology}\\
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\paragraph{\textbf{Centrifugal microfluidics}}\
-
-The field of centrifugal microfluidics is accelerating.
-
-Many CD microfluidics systems use standard CD molding techniques for the channels and machining techniques, using either acrylic or silicone.
-The turbidity sensor is most sensitive if the plastic is clear.
-Sterilization does not seem to be discussed.
-
-Polypropylene is the ideal material, being almost indefinitely autoclavable. It is quite difficult to machine.
-
-\end{multicols}
-
-\clearpage
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{multicols}{1}
-{\Large Modes of application}\\
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\paragraph{\textbf{Personal 'electromagnetic mask'}}\
-
-Even with judicious use of phased-arrays, spatial power-combining, etc, each transistor can only reasonably sterilize approx. $ 1 \text{ m}^3 $.
-
-We therefore demonstrate this form factor because, superficially, there are fewer people than there are places.
-
-On the other hand, a personal device may present issues with participation and production volume.
-
-\paragraph{\textbf{Direct treatments}}\
-
-[Hand 1982] $E_{mag}=1/e$ (13.5\% power density) skin\footnote{electromagnetic skin, not tissue skin}\footnote{well, both, I suppose.} depth is approximately:
-
-\begin{center}
-\begin{tabular}{|l|l|l|}
-\hline
-F=10 GHz          & Dry tissue & Wet tissue \\ \hline
-Penetration depth & 30 mm      & 5 mm \\ \hline
-\end{tabular}
-\end{center}
-
-SARS is found widely distributed throughout the most favorable organs [Ding 2004], shielded by an average of 4 cm of chest wall [Schroeder 2013]; so safe external treatment of the body is unlikely.
-
-However, destruction of lung tissue appears to be the primary cause of death via SARS [Nicholls 2006].
-
-A bronchoscopic technique may therefore be effective, very similarly to that demonstrated by [Yuan 2019]: in adults, the bronchi are less than 2 mm thick [Theriault 2018] and the lungs themselves are only on the order of 7 mm thick [Chekan 2016].
-
-The main bronchus is about 8 mm in diameter, which is smaller than the patch antenna used here; a monopole (or multiple, phased monopoles) like is probably more suitable.
-
-\paragraph{\textbf{More fanciful concepts}}\
-
-Many systems operate in these X-band frequency ranges; and precision
-
-It is relatively easy to produce megawatts of power at these frequency ranges using Klystrons.
-
-Existing marine, weather, and aviation radar systems often use the X-band; depending on the focusing power
-
-\paragraph{}
-
-Finally, there is one concern.
-Use of this technique will provide a selection bias towards immunity to electromagnetic fields, which could perhaps be effected by preferring extreme-sized mutants (shifting the resonance away from the applied field).
-We do not have the biological knowledge to know if this is plausible; it is simply worth mentioning.
-
-\end{multicols}
-
-\clearpage
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{multicols}{1}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\noindent\fbox{\parbox{\linewidth}{
-	Toolchain:
-	\begin{itemize}
-	\item Failed oscillator feedback-loop optimization toolchain: QUCS 0.0.20 + python-qucs + scipy's 'basinhopper'
-	\item Successful A slightly modified ngspice + ngspyce + pyEVTK
-	\item gprMax for FDTD EM simulation
-	\item KiCAD, wcalc, scikit-rf, ngspice
-	\end{itemize}
-}}
-%
-
-The oscillator is a 'wideband double-tuned varactor VCO', based almost verbatim on [Tsuru 2008] and the reference design in Figure 8.36, p378 of [Grebennikov 2007].
-
-The rest of the papers in the bibliography were highly enlightening regarding the principles of microwave oscillator design.
-
-This topology of oscillator worked marvellously on essentially the first try.
-
-The process by which we failed miserably to design our own oscillator topology is detailed in the supplemental.
-
-The following properties: P1dB
-
-For ease of design and simulation, a device with Touchstone S-parameters and SPICE files is greatly preferable.
-
-It is commonly claimed that FR4 is a 'slow' substrate, and that the high loss tangent of ~0.02 makes it unsuitable for microwave systems.
-
-However, with this PCB substrate, the expected loss of only 0.026 dB/mm on signals of minimum 0 dBm is patently acceptable.
-As viruses do not have a discriminating palate, we are also only minimally concerned with $S_{11}$ reflections, noise, or spurs, so precise impedance control is not required; the wideband VCO sweep accomodates for any variations in resonant frequency due to wide manufacturing tolerances.
-
-As a result of our gross incompetence, the oscillator was designed via an inane, roundabout, and fiendishly tedious manner, and our description of this technique only contributes to the field by being suitable for a dartboard; our analysis can only hold water when combined with paper mache; and a lesser invertebrate in posession of a copy of Microwave Oscillator Design would have accomplished the task faster.
-
-Designing an oscillator of this type in one step with a few kindergarten equations appears to be well within the reach of modern network analytical techniques.
-Genetic algorithms are quite well matched to this problem, and many commercial software packages are  [computer microwave design book].
-
-Initially,
-
-Not having a good analytical understanding, we resorted to using a purely computational method.
-
-In addition, the design of wideband feedback-loop VCOs is a relatively well-explored field, and many reference designs exist.
-
-The key sticking point - which we missed - seems to be that at these scales, using microstrip design techniques, the parasitics of any possible filter structure are so large that the small change in impedance that varactors can provide cannot tune the circuit by any meaningful amount.
-
-"Using the lead inductances of the bipolar transistor and varactors provides the required value of the base inductance".
-
-Indeed, [Tsuru 2008]'s "tuned circuit" in Fig 8 is, in fact, just the varactors, plus an almost invisible high-impedance line.
-
-Several analytical filter design methods were
-
-This is apparently known as a "double-tuned" wideband.
-
-%
-\paragraph{\textbf{The feedback loop oscillator}}\
-
-Oscillators must meet the Barkhausen criterion:
-
-\begin{itemize}
-
-\item A 360 degree phase shift around the feedback loop (including the phase shift contribution from the amplifier, which itself varies greatly with frequency)
-\item A loop gain $>1.$
-
-\end{itemize}\
-%
-However, a third element is also required:
-%
-\begin{itemize}
-\item A frequency-selective element that restricts oscillation modes and decreases phase noise.
-\end{itemize}
-%
-
-With large feedback-loop structures, such as long PiN-switched phasing lines, proximity effects from nearby flesh would detune the oscillator significantly.
-
- design of a triple-tuned oscillator.
-
-\paragraph{}
-The buffer amplifiers
-
-\clearpage
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-{\Large Mass production}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-If this 'electromagnetic mask' form is the ideal (not nearly ), a minimum of 5 GaAs or SiGe:C transistors will be required.
-
-There are, for instance, 1 million hospital beds in the U.S. [AHA 2018].
-
-It is difficult to determine the supply capacity for these modern semiconductor processes. A few fermi est
-
-GaAs MMIC market of \$2.2 Bn USD / random sample of MMIC prices =
-
-3e9 wifi connected devices produced each year.
-
-The largest RFID plants can produce
-
-The techniques and equipment required to produce these are non-trivial. SiGe:C, for instance, requires,
-
-Figures are not forthcoming,
-
-Given the supply difficulties of comparatively simple materials such as Tyvek at pandemic scales, it is difficult to imagine that RF semiconductor production can be immediately re-tasked and scaled to this degree.
-
-\paragraph{\textbf{Vacuum RF triode}}\
-
-One concern is the large filament heater power, which prevents the use of low-cost button cells for power.
-Use of cold-cathode field-emitter arrays would alleviate this issue, but at the cost of complexity.
-
-Small tungsten incandescent lights are available down to 0.05 watts. With a suitable high-efficiency cathode coating, a pulsed heater power of less than 0.02
-
-\end{multicols}
-
-\subfile{acknowledgement}
-
-\subfile{supplemental}
-
-\end{document}

### 2020-07-02 documents/paper.tex
Fixed distribution; somewhat similar values
Working on low-impedance cascode

@@
 
-\title{On the application of microwave acoustic resonant viral inactivation
-\thanks{I would be delighted to include any criticisms or comments anyone may have, both on substance and comprehensibility; preferably leave them on the GitHub issues page, or email therobotist@gmail.com, @0xDBFB7 on Twitter, or irc.0xDBFB7.com:6667 \#covid.}}
-\date{May 2020}
-\author{Based primarily on exceptional work by }
+\include{title}
 
-\begin{document}
+\clearpage
 
-\flushbottom 
-\maketitle
-\thispagestyle{empty}
+\paragraph{To-do list}
 
-\begin{textblock}{5}(1,1)
-\noindent Please view the latest version at github.com/0xDBFB7/covidinator
-\end{textblock}
-%\begin{textblock}{5}(1,27)
-%\end{textblock}
-
-\null\begin{tabular}[t]{l@{}}
-  {Daniel Correia}\ \orcidlink{0000-0002-9353-0216}  \\
-  \textit{????????? York??????}
-\end{tabular}
-
-\begin{abstract}
-
-We extend this landmark work rather trivially by:\\
-
-Aims:
+The following have to be done before production can be started:
 
 \begin{itemize}
-  \item Establishing the time dependence of inactivation
-  \item Demonstrating a modulation scheme that decreases the inactivation threshold to below current safety levels in surrogate bacteriophage
-  \item Demonstrating a prototype emitter in an "electromagnetic mask" form-factor, costing about \$5 in prototype quantities, which can reasonably be produced in 10 million-of quantities
-  \item Testing power thresholds in various conditions; biological fluids of various conductivities and pHs
-  \item Using a coarse-grained molecular-dynamics simulation to optimize the impulse
-  \item Using a virus-in-the-loop optimization with a centrifugal microfluidic system
-  \item Discussing the biological basis for the safety of the device
-  \item Showing that the deviation from the expected theshold could be explained by variance in the
+  \item Re-run the experiment with 
+  \item
+
+  \item
 
 \end{itemize}
-
-{Perhaps notable that a completely free and open-source toolchain was used for the entire project, including FDTD microwave antenna optimization. This work can be replicated with \$500 in equipment.}
-
-\end{abstract}
-
-\begin{autem}
-	{\large  \it autem} \\
-
-	This work was prepared by an undergraduate and has not been peer-reviewed. Additionally, the author has no prior experience with either biology or microwave design. \\
-
-	While our study is very simple, biology is of such complexity that a tremendous amount of care must be taken before any conclusion can be drawn at all.
-It is not likely that we have taken sufficient care.\\
-
-This is especially true with RF biophysics. The literature is littered with otherwise impeccably perormed research which was later demonstrated to be an artifact. \\
-
-	Though the original research used Inf. A, our testing was only performed with a surrogate bacteriophage. All experiments must be repeated with SARS-NCoV-2. \\
-
-	Additionally, other sterilization techniques may produce superior results with less faffing about and should be evaluated in the same context. Data on far UV [Buonanno 2017] indicates safety.\\
-
-It has occurred before that otherwise striking resonances were detected and replication found them to be artifacts of the measurement equipment. [Foster 1987] even offers this disclaimer:
-
-"To detect the DNA resonances with the probe
-technique requires correction for system errors that are
-potentially much larger than the effect to be studied and
-lead to resonance-like artifacts. This is true even with the
-more precise instrumentation used in this study. Such data
-are easily misinterpreted, and we suggest this might have
-happened in the former study."
-
-The direct inactivation plaque and PCR data from [Yang], replicated by [Sun], is a somewhat convincing corroboration that this effect is not an artifact, but hundreds of convincing and  wrong papers exist in the literature.
-Our data is crude and imprecise, our equipment hastily constructed, and should not be considered validation of this effect even existing.
-\\
-
-	Please consider all claims with appropriate skepticism.
-
-\end{autem}
 
@@
 
-Any claims of
-
 The chain of literature 
 %
-[Fr\"{o}hlich 1968] \textrightarrow \ [Fr\"{o}hlich 1980] \textrightarrow \ [Liu 2009] \textrightarrow \ ([Hung 2014] $\parallel$ [Yang 2015] $\parallel$ [Sun 2017])\footnote{We have probably missed several steps in this chain out of haste.} apparently culminates in the flagship work we focus on in this paper,
+[Fr\"{o}hlich 1968] \textrightarrow \ [Fr\"{o}hlich 1980] \textrightarrow \ [Liu 2009] \textrightarrow \ ([Hung 2014] $\parallel$ [Yang 2015] $\parallel$ [Sun 2017])\footnote{We have not conducted a thorough review; many more papers are probably involved.} apparently culminates in the flagship work we focus on in this paper,
 
@@
 
-estabilishes that - unique to certain viruses, and apparently unlike human cell structures, as we shall see - coincidentally have just the right size, shape, stiffness, and net charge distribution to form a weak (Q=2) spherical dipole resonance mode which couples well to the microwave spectrum at approximately the X-band (6-10 GHz).
+estabilishes that - unique to certain viruses, and apparently unlike human cellular structures, as we shall see - coincidentally have just the right size, shape, stiffness, and net charge distribution to form a weak (Q=2) spherical dipole resonance mode which couples well to the microwave spectrum at approximately the X-Band (6-10 GHz).
 
-More critically, [Yang 2015] (in parallel with [Hung 2014]) theoretically model and then experimentally demonstrate that the electric field strength required to produce an amplitude of vibration sufficient to tear the lipid envelope of the order of magnitude of 100 V/m.
+More critically, [Yang 2015] (and, in parallel, [Hung 2014]) theoretically model and then experimentally demonstrate in various strains of Influenza A that the electric field strength required to produce an amplitude of vibration sufficient to tear the envelope is approximately 100 V/m, below safety limits even for continous point-blank exposure.\footnote{See supplemental.}
 
-They demonstrate this with both a plaque and PCR assay, with fantastic agreement to the theoretical model.
+They demonstrate this with both a plaque and PCR assay, with fantastic agreement with the theoretical model.\footnote{As we will discuss, there are a few issues with the experimental technique.; sham, blinding, and dosimetry demanded by [Vjl.] are not mentioned.}
 
-This is a non-ionizing, non-thermal technique.
+Like pumping a tire swing, this effect allows an otherwise inconsequential field magnitude to store energy over a small number of cycles until the virus is destroyed.
 
-Microwave resonant absorption of viruses through dipolar coupling with confined acoustic vibrations
+\lettrine{It} cannot be overstated how unexpected and dubious this finding appears to be -at least, based on our limited research and experience to date.
 
-This resonance mode
+For the RF safety limits set by standards organizations are themselves based on the assumption that no resonances exist in biological tissues, and (as we shall see), this claim is grounded in solid {\it in vitro} (albeit limited {\it in vivo}) evidence.
 
-The myth that 2.4 GHz was chosen because it "couples strongly with water" is largely false; but this is
+It is difficult to reconcile this discrepancy. A failure tree is included below.
 
-This is quite surprising, and should perhaps be considered with some trepidation, since
+If this mechanism exists, it would seem to provide the following advantages over other methods such as UV or cold-plasma sterilization:
 
-\footnote{This {\it confined} acoustic resonance is apparently distinct from common-and-garden pipe-organ acoustic resonance.
-Rather than simple covalent or Lennard-Jones interaction between particles, if [Fr\"{o}hlich 1968] is to be believed at these nanoscopic scales a sort of coherent wavefunction is set up among the particles of the virus which produces coupling modes not otherwise expected.
-We confess to not yet understanding this phenomenon; fortunately, while helpful, the details of how this mode appears is not critical to implementing this technique.}
+\begin{itemize}
+  \item This is a non-ionizing, non-thermal, non-chemical technique.
+  \item Far-field and moderately penetrating inactivation.
+
+  \item
+
+\end{itemize}
+
+\footnote{It should be noted that this {\it confined} acoustic resonance is subtly distinct from common-and-garden pipe-organ acoustic resonance; this is apparently not a strictly classical phenomenon.
+Besides standard Coulomb-like and Lennard-Jones-like interactions between constituent particles, if Fr\"{o}hlich is to be believed at these nanoscopic scales there are also wave-function interactions among the particles of the virus which can shift storage to modes not otherwise expected.
+
+We confess to not yet understanding this phenomenon; fortunately, while helpful, the details of how this mode appears are not critical to implementing this technique.}
 
@@
 Conversely, above 6 GHz, where EMFs are absorbed more superficially (making depth less relevant), it is useful to describe exposure in terms of the density of absorbed power over area $W/m^2$, which we refer to as “absorbed power density”}'' [ICNIRP 2020 \faExternalLink] }
+
+\footnote{All values have been converted to $\text{W/m}^2$ to avoid confusion. 100 $\text{ W/m}^2 = 10 \text{ mW/cm}^2 = 10 \text{ dBm/cm}^2$.}
 
@@
 \clearpage
+{\Large \it Talkin' 'bout the Variation}\\
+
+[Yang 2015] theoretically model the virus to determine the minimum electric field required to destroy it.
+
+They assume that the virus is a simple damped harmonic oscillator, where the 'core' and 'shell' oscillate in opposition.
+
+They determine the net charge experimentally from microwave absorption measurements.
+
+\begin{center}
+ \begin{tabular}{||c c c c||} 
+ \hline
+ Col1 & Col2 & Col2 & Col3 \\ [0.5ex] 
+ \hline\hline
+ 1 & 6 & 87837 & 787 \\ 
+ \hline
+ 2 & 7 & 78 & 5415 \\
+ \hline
+ 3 & 545 & 778 & 7507 \\
+ \hline
+ 4 & 545 & 18744 & 7560 \\
+ \hline
+ 5 & 88 & 788 & 6344 \\ [1ex] 
+ \hline
+\end{tabular}
+\end{center}
+
+\clearpage
 \paragraph{\textbf{Time dependence}}\
 
-Both Yang and [] used an apparently arbitrary 15-minute exposure in their tests - a very reasonable decision given the focus of their paper.
+Both [Yang 2015] and [Hung 2014] use an apparently arbitrary 15-minute exposure in their tests - a very reasonable decision, given the focus of their paper.
 
-The effectiveness against airborne particles, and to minimize the power required in a dwelling phased-array beam, we must first establish the required duration of exposure.
+The effectiveness against airborne particles, and to minimize the power required in a dwelling phased-array beam, we must establish the required duration of exposure.
 
@@
 
-\footnote{All values have been converted to $\text{W/m}^2$ to avoid confusion. 100 $\text{W/m}^2 = 50 \text{mW/cm}^2$}
-
 \subfile{safety}
@@
 \begin{multicols}{1}
-{\Large Biology}\\
+{\Large The Experiment}\\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+{\Large Microwave Musings}\\
 \begin{multicols}{1}
@@
 
+While it is possible to use conventional Si devices at these frequencies, especially with second-harmonic techniques [Winch 1982], obtaining the required output power is not trivial.
+
 The techniques and equipment required to produce these are non-trivial. SiGe:C, for instance, requires,

### 2020-07-07 documents/safety.tex
Spectrum analyzer progress

@@
 \includegraphics[scale=0.5]{cells.png}
-
-\footnote{Contrary to some [Hardell 2017] reports, we do not find the FCC and ICNIRP to be significantly affected by special interest groups; their rationales appear to be transparent.
-[FCC-19-126A1] an FCC memorandum wherein the FCC tells groups to respectfully screw themselves no fewer than three times: ''Similarly, IEEE-ICES urges the Commission to
-adopt a higher SAR exposure limit of 2 W/kg averaged over 10 g.
-[snip] We are not persuaded that the IEC standard should be adopted at this time.", "Medtronic and the AAMI-CRMD recommend a more relaxed threshold of 20 mW.
-We decline to increase the 1-mW threshold.".
-Things heating up at the Microwave Safety fandom.}
 

### 2020-07-08 firmware/eppendoofus/deps.sh
Protobuf

@@ -1,0 +1,3 @@
+
+git clone --branch v3.12.3 https://github.com/protocolbuffers/protobuf libraries/protobuf
+cd libraries/protobuf

### 2020-07-08 firmware/eppendoofus/src/native/comms.cpp

@@ -14,6 +14,6 @@ void println(std::string input){
 
 
 
-void host_comms_available(){
+int host_comms_available(){
     return HOST_SERIAL.available();
 }

### 2020-07-11 documents/paper.tex
Trying to fix units

@@
 
+\include{introduction}
+
 \clearpage
@@
 
-The following have to be done before production can be started:
+We see the following steps that must be undertaken before production can be started:
 
@@
   \item Re-run the experiment with 
-  \item
-
-  \item
-
+  \item Verify 
+  \item Failure-tree to ensure that power levels can never go above specified values.
+  \item Obtain special permission from the FCC?
 \end{itemize}
@@
 
-estabilishes that - unique to certain viruses, and apparently unlike human cellular structures, as we shall see - coincidentally have just the right size, shape, stiffness, and net charge distribution to form a weak (Q=2) spherical dipole resonance mode which couples well to the microwave spectrum at approximately the X-Band (6-10 GHz).
+estabilishes that - unique to certain viruses, and apparently unlike human cellular structures, as we shall see - coincidentally have just the right size, shape, stiffness, and net charge distribution to form a weak (Q=2) spherical dipole resonance mode which couples well to the microwave spectrum at approximately the X-Band, around 7-10 GHz.
 
-More critically, [Yang 2015] (and, in parallel, [Hung 2014]) theoretically model and then experimentally demonstrate in various strains of Influenza A that the electric field strength required to produce an amplitude of vibration sufficient to tear the envelope is approximately 100 V/m, below safety limits even for continous point-blank exposure.\footnote{See supplemental.}
+More critically, [Yang 2015] (and, in parallel, [Hung 2014]) theoretically model and then experimentally validate in various strains of Influenza A that - due to this acoustic-resonance effect - the power levels required to crack the lipid envelope are on the order of magnitude of the safety limits even for continous point-blank exposure.\footnote{See supplemental.}
 
-They demonstrate this with both a plaque and PCR assay, with fantastic agreement with the theoretical model.\footnote{As we will discuss, there are a few issues with the experimental technique.; sham, blinding, and dosimetry demanded by [Vjl.] are not mentioned.}
+They demonstrate this with both a plaque and PCR assay, finding good agreement with the theoretical model.\footnote{As we will discuss, there are a few issues with the experimental technique.; sham, blinding, and dosimetry demanded by [Vjl.] are not mentioned.}
 
-Like pumping a tire swing, this effect allows an otherwise inconsequential field magnitude to store energy over a small number of cycles until the virus is destroyed.
+Like pumping a swing, this effect allows an otherwise inconsequential field magnitude to store energy over a small number of cycles until the virus is destroyed.
 
@@
 
-For the RF safety limits set by standards organizations are themselves based on the assumption that no resonances exist in biological tissues, and (as we shall see), this claim is grounded in solid {\it in vitro} (albeit limited {\it in vivo}) evidence.
+For even the RF power limits set by standards organizations appear to be based on the observation that few significant resonance modes exist in biological tissues, and (as we shall see), this is grounded in solid {\it in vitro} (albeit limited {\it in vivo}) evidence.
+
+This may account for why this paper has been ignored.
 
@@
 \begin{itemize}
-  \item This is a non-ionizing, non-thermal, non-chemical technique.
-  \item Far-field and moderately penetrating inactivation.
+  \item This is a non-ionizing, non-thermal
+%
+\footnote{It may be useful to define 'non-thermal'; it caused us some confusion.
+Certainly the proteins of the virion locally absorb energy and increase in temperature.
+The key is that, when excited in this manner, the energies in the envelope are poorly modelled by a Maxwell-Boltzmann distribution; they are not given sufficient time to 'thermalize'.
+In contrast, with typical 2.4 GHz microwave exposure, sterilization can only occur by aggregate heating of the fluid and tissue.}
+%
+, non-chemical technique, harmless for continuous exposure to tissue, which produces no ozone, can be effective inside bodily tissues, and can readily be produced with \$1 - scale devices.
 
+  \item Potentially far-field and moderately penetrating inactivation. 
   \item
@@
 
-\footnote{``{For example, below about 6 GHz, where EMFs penetrate deep into tissue (and thus require depth to be considered), it is useful to describe this in terms of “specific energy absorption rate” (SAR), which is the power absorbed per unit mass $(W/kg)$.
+\footnote{``{[B]elow about 6 GHz, where EMFs penetrate deep into tissue (and thus require depth to be considered), it is useful to describe this in terms of “specific energy absorption rate” (SAR), which is the power absorbed per unit mass $(W/kg)$.
 Conversely, above 6 GHz, where EMFs are absorbed more superficially (making depth less relevant), it is useful to describe exposure in terms of the density of absorbed power over area $W/m^2$, which we refer to as “absorbed power density”}'' [ICNIRP 2020 \faExternalLink] }
@@
 \footnote{All values have been converted to $\text{W/m}^2$ to avoid confusion. 100 $\text{ W/m}^2 = 10 \text{ mW/cm}^2 = 10 \text{ dBm/cm}^2$.}
-
-With typical 2.4 GHz microwave exposure, sterilization can only occur by heating of the fluid and tissue.
-
-Of course, the temperature of the atoms of the virus undoubtedly increase; but the
 
@@
 \clearpage
+
+[IEEE C95.1-2005], Annex B, "Identification of levels of RF exposure responsible for adverse
+effects: summary of the literature",
+
+\begin{quote}
+Further examination of the RF literature reveals no reproducible low level (non-thermal) effect that would
+occur even under extreme environmental exposures. The scientific consensus is that there are no accepted
+theoretical mechanisms that would suggest the existence of such effects. This consensus further supports the
+analysis presented in this section, i.e., that harmful effects are and will be due to excessive absorption of
+energy, resulting in heating that can result in a detrimentally elevated temperature. The accepted mechanism
+is RF energy absorbed by the biological system through interaction with polar molecules (dielectric relaxation) or interactions with ions (ohmic loss) is rapidly dispersed to all modes of the system leading to an
+average energy rise or temperature elevation. Since publication of ANSI C95.1-1982 [B6], significant
+advances have been made in our knowledge of the biological effects of exposure to RF energy. This
+increased knowledge strengthens the basis for and confidence in the statement that the MPEs and BRs in this
+standard are protective against established adverse health effects with a large margin of safety.
+
+\end{quote}
+
+The human body contains proteins with all sorts of net charges.
+
+Other physiological effects include changes in the permeability of membranes, direct nerve stimulation, and others.
+These are all accounted for in the time-domain equation and the 6-minute averaging period.
+
+This would seem to open an obvious route of optimization.
+If the virus is destroyed in tens of nanoseconds - essentially governed by instantaneous power.
+But tissue damage requires *energy deposition*.
+
+Obviously, the solution is thus to turn the CW microwave signal into an effectively instantaneous pulse.
+
+\clearpage
 {\Large \it Talkin' 'bout the Variation}\\
 
-[Yang 2015] theoretically model the virus to determine the minimum electric field required to destroy it.
+To re-cap, [Yang 2015] theoretically model the virus to determine the minimum electric field required to destroy it.
 
@@
 They determine the net charge experimentally from microwave absorption measurements.
+
+Since [Yang] try to compute the {\it threshold}, they use a value of 400 pN for the breaking strength of the envelope, obtained from [Li 2011]. However,
+
+"95%.".
 
@@
 
+[Vj] mention the importance of precise dosimetry. Even simple structures can produce hot-spots 
+Yang et al use both a plastic cuvette, and a single drop of solution on a glass slide; in either case, a sharp change dielectric constant is present.
+
+To the extreme, some papers have used
+
 \clearpage
 \paragraph{\textbf{Time dependence}}\
+
+The fact that the viral inactivation is non-thermal
 
@@
 
-Even with judicious use of phased-arrays, spatial power-combining, etc, each transistor can only reasonably sterilize approx. $ 1 \text{ m}^3 $.
+Even with judicious use of phased-arrays, spatial power-combining, etc, each transistor can only reasonably maintain sterility in approx. $ 0.1 \text{ m}^3 $.
 
@@
 
-It is relatively easy to produce megawatts of power at these frequency ranges using Klystrons.
+It is easy to produce megawatts of power at these frequency ranges using Klystrons.
+Assuming an appropriate antenna, a single 50MW SLAC XL-class klystron with a PRF of 180 Hz can sanitize almost a square kilometer every second.
+\footnote{A new meaning of 'asceptic field'.}
+
+On the other hand, if this is conducted in outdoor free-space, sunlight
 
@@
 
+\paragraph{Sensing}
+
+Surprisingly, there is little discussion on microwave virus detection, with the notable exception of [Mehrotra 2019].
+Such scholarly silence is usually an indicator that a technique is impossible for reasons so obvious they scarcely bear repeating.
+
+However, [Oberoi 2012] find that they can detect a single E. Coli bacterium in 50 uL of broth via a microwave cavity. This is so unbelievable that we are inclined to look for methodological issues.
+
+Frequency-domain measurements can be made with incredible precision; and there are many parameters by which virions could be discriminated; ring-up time of the resonance, excitation non-linearity, precise microwave spectroscopy, etc.
+
 \paragraph{}
 
-Finally, there is one concern.
+Finally, there is one concern. It has been shown that virions can effect large-scale changes in the electric charges of their [].
+
 Use of this technique will provide a selection bias towards immunity to electromagnetic fields, which could perhaps be effected by preferring extreme-sized mutants (shifting the resonance away from the applied field).
@@
 
-The oscillator is a 'wideband double-tuned varactor VCO', based almost verbatim on [Tsuru 2008] and the reference design in Figure 8.36, p378 of [Grebennikov 2007].
+Microwave design has a reputation for being the purview of wizards. Modern RF software packages like HFSS, Microwave Office, Agilent's ADS, and Mathworks' RF toolbox, for which; component models
 
-The rest of the papers in the bibliography were highly enlightening regarding the principles of microwave oscillator design.
+Luckily, this project falls perfectly within the subset of microwave technologies that do not require a goatee.
+The vast majority of the behavior of most circuits can be modelled with the very same SPICE tools as one would use at low frequencies.
+With judicious application of reference designs, it seems to be possible to design
 
-This topology of oscillator worked marvellously on essentially the first try.
+Before about 2005, however, it seems to have been somewhat the norm to write a simple numerical code to solve the problem at hand based on underlying principles.
 
-The process by which we failed miserably to design our own oscillator topology is detailed in the supplemental.
+We are also aided by the fact that what took a \$150,000 computing cluster a single decade ago can now be done in a few minutes by a single budget GPU.
 
-The following properties: P1dB
-
-For ease of design and simulation, a device with Touchstone S-parameters and SPICE files is greatly preferable.
-
-It is commonly claimed that FR4 is a 'slow' substrate, and that the high loss tangent of ~0.02 makes it unsuitable for microwave systems.
-
-However, with this PCB substrate, the expected loss of only 0.026 dB/mm on signals of minimum 0 dBm is patently acceptable.
-As viruses do not have a discriminating palate, we are also only minimally concerned with $S_{11}$ reflections, noise, or spurs, so precise impedance control is not required; the wideband VCO sweep accomodates for any variations in resonant frequency due to wide manufacturing tolerances.
-
-As a result of our gross incompetence, the oscillator was designed via an inane, roundabout, and fiendishly tedious manner, and our description of this technique only contributes to the field by being suitable for a dartboard; our analysis can only hold water when combined with paper mache; and a lesser invertebrate in posession of a copy of Microwave Oscillator Design would have accomplished the task faster.
-
-Designing an oscillator of this type in one step with a few kindergarten equations appears to be well within the reach of modern network analytical techniques.
-Genetic algorithms are quite well matched to this problem, and many commercial software packages are  [computer microwave design book].
-
-Initially,
-
-Not having a good analytical understanding, we resorted to using a purely computational method.
-
-In addition, the design of wideband feedback-loop VCOs is a relatively well-explored field, and many reference designs exist.
-
-The key sticking point - which we missed - seems to be that at these scales, using microstrip design techniques, the parasitics of any possible filter structure are so large that the small change in impedance that varactors can provide cannot tune the circuit by any meaningful amount.
-
-"Using the lead inductances of the bipolar transistor and varactors provides the required value of the base inductance".
-
-Indeed, [Tsuru 2008]'s "tuned circuit" in Fig 8 is, in fact, just the varactors, plus an almost invisible high-impedance line.
-
-Several analytical filter design methods were
-
-This is apparently known as a "double-tuned" wideband.
-
-%
-\paragraph{\textbf{The feedback loop oscillator}}\
-
-Oscillators must meet the Barkhausen criterion:
-
-\begin{itemize}
-
-\item A 360 degree phase shift around the feedback loop (including the phase shift contribution from the amplifier, which itself varies greatly with frequency)
-\item A loop gain $>1.$
-
-\end{itemize}\
-%
-However, a third element is also required:
-%
-\begin{itemize}
-\item A frequency-selective element that restricts oscillation modes and decreases phase noise.
-\end{itemize}
-%
-
-With large feedback-loop structures, such as long PiN-switched phasing lines, proximity effects from nearby flesh would detune the oscillator significantly.
-
- design of a triple-tuned oscillator.
-
-\paragraph{}
-The buffer amplifiers
+\end{multicols}
 
 \clearpage
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+{\Large Interference}\\
+\begin{multicols}{1}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-If this 'electromagnetic mask' form is the ideal (not nearly ), a minimum of 5 GaAs or SiGe:C transistors will be required.
+We've got a thing 
+that's called 
+Radar Love
+We've got a wave
+in the air
+Radar Love
 
-There are, for instance, 1 million hospital beds in the U.S. [AHA 2018].
+Almost all components on the device can be replicated with fully vertically-integrated first-principles. Capacitors can be
 
-It is difficult to determine the supply capacity for these modern semiconductor processes. A few fermi est
-
-GaAs MMIC market of \$2.2 Bn USD / random sample of MMIC prices =
-
-3e9 wifi connected devices produced each year.
+If this 'electromagnetic mask' form is the ideal (not nearly),
 
@@
 
-While it is possible to use conventional Si devices at these frequencies, especially with second-harmonic techniques [Winch 1982], obtaining the required output power is not trivial.
+a minimum of 5 GaAs or SiGe:C transistors will be required. Without SOI or, it does not appear that
 
-The techniques and equipment required to produce these are non-trivial. SiGe:C, for instance, requires,
+As a lower bound, there are 1 million hospital beds in the U.S. [AHA 2018]; and as an upper bound obtaining global herd immunity would take 1.75 billion units.
+
+It is difficult to determine the supply capacity for these semiconductor processes; information is not forthcoming from the manufacturers.
+Fermi estimates \footnote{GaAs MMIC market of \$2.2 Bn USD / random sample of MMIC prices = about 2 Bil devices / yr, 3e9 wifi connected devices produced each year,}
+
+It is possible to use common Si-based devices at these frequencies, especially with second-harmonic techniques [Winch 1982].
+However, obtaining the required gain and output power is not a trivial matter.
+
+The techniques and equipment required to produce these devices are extremely complex; load-lock UHV,
 
@@
 \paragraph{\textbf{Vacuum RF triode}}\
+
+Especially combined with an integral titanium sorption pump,
 

### 2020-07-11 documents/supplemental.tex
Trying to fix units

@@
 \end{multicols}
+
+Contrary to some [Hardell 2017] reports, we do not find the FCC and ICNIRP to be significantly affected by special interest groups; their rationales appear to be transparent.
+[FCC-19-126A1] an FCC memorandum wherein the FCC tells groups to respectfully screw themselves no fewer than three times: ''Similarly, IEEE-ICES urges the Commission to
+adopt a higher SAR exposure limit of 2 W/kg averaged over 10 g.
+[snip] We are not persuaded that the IEC standard should be adopted at this time.", "Medtronic and the AAMI-CRMD recommend a more relaxed threshold of 20 mW.
+We decline to increase the 1-mW threshold.".
+
+Things heating up at the Microwave Safety fandom.
 
@@
 
-\paragraph{A}
-\rule{\linewidth}{0.2pt}
+\PRLsep{{\itshape The wideband oscillator }}
 
-Microwave design has a reputation for being the purview of wizards. The software [Microwave Office], Agilent ADS, or Mathworks
+Not having access to any RF equipment, we needed an oscillator tunable over the X-band.
 
-It seems there's a subset of these, where wide tolerances and poor performance are acceptable, that does not require a goatee or the sale of firstborn.
+There are many oscillators. The HB100 uses a dielectric resonator, for instance; cavity-based methods with mechanical tuning; active antennas using.
 
-Before about 2005, however, it seems to have been somewhat the norm to write a simple numerical code to solve the problem at hand based on underlying principles.
+The literature is quite mature, partly due to the FCC's recent ultrawideband communications guides.
 
-We are also aided by the fact that what took a \$150,000 computing cluster a decade ago can be done in a few minutes by a single budget GPU.
+As a result of our gross incompetence, the oscillator was designed via an inane, roundabout, and fiendishly tedious manner, and our description of this technique only contributes to the field by being suitable for a dartboard; our analysis can only hold water when combined with paper mache; and a lesser invertebrate in posession of a copy of Grebennikov's excellent Microwave Oscillator Design would have accomplished the task faster.
 
-With judicious application of reference designs, it seems to be possible to design
+Designing an oscillator of this type in one step with a few kindergarten equations appears to be well within the reach of modern network analytical techniques.
+Genetic algorithms are quite well matched to this problem, and many commercial software packages are  [computer microwave design book].
 
-The oscillator design is a testament  This highlights that a computation is not a substitute for understanding.
-
-We began experimentally by building a scaled version of [Mueller 2008]'s active antenna crudely with copper tape, using a CEL [] FET.
+We began experimentally by building a scaled version of [Mueller 2008]'s active antenna crudely with copper tape, using a CEL [] GaAs FET.
 
@@
 A crude, inane, and extremely disorganized trial-and-error procedure was performed for many weeks.
-A wide variety of analytical methods for filter design were attempted, but simultaneously obtaining the correct phase shift and frequency response was somewhat difficult.
-The parasitic inductance of the varactors always seemed to destroy our most perfect creations.
+A wide variety of analytical methods for filter design were attempted [documents/global.ipynb], but simultaneously obtaining the correct phase shift and frequency response was somewhat difficult.
+Adding the parasitic inductance of the varactors always seemed to destroy our most perfect creations.
 
-An SIR filter has the added advantage of confusing epidemiologists greatly.
+Using an SIR filter has the added advantage of confusing epidemiologists.
 
-Eventually, QUCS, zonca/python-qucs, and scipy's basinhopper was used with the cost function somewhat similar to that described in [Kaplevich]:
+Eventually, QUCS, zonca/python-qucs, and scipy's basinhopper were used with a cost function somewhat similar to that described in [Kaplevich]:
 
@@
 
-This produced a seemingly acceptable feedback loop:
+This produced a seemingly acceptable feedback loop (note the group delay / phase progression):
 
@@
 
-"Wideband", p. 378, Figure 8.36, dnw
-
 \begin{figure}[H]
@@
 
-The pad size
+The oscillator design is a testament  This highlights that a computation is not a substitute for understanding.
 
-Because we lacked a spectrum analyzer that could monitor the higher poles of the filter until the bootstrap LO was designed, we had to rely on in-silico analyeses.
+The key sticking point seems to be that as frequency increases, using microstrip design techniques, the parasitics of any filter structure are so large that the small change in impedance that the varactors can provide does not tune the circuit by any meaningful amount.
 
-Transient simulations with ngspice matched experiment far more closely.
+The two varactors on each tuning circuit each contribute 0.7 nH and between 0.35 to 2.4 pF; each blocking capacitor contributes about 0.2 nH.
+The frequency range of the oscillator can be selected by adding between 0.5 nH to 1.5 nH symmetrically to both tuning circuits.
+
+"Using the lead inductances of the bipolar transistor and varactors provides the required value of the base inductance".
+
+Indeed, [Tsuru 2008]'s "tuned circuit" in Fig 8 is, in fact, just the varactors, plus an almost invisible high-impedance line.
+
+The final oscillator is a 'wideband double-tuned varactor VCO', based almost verbatim on [Tsuru 2008] and the reference design in Figure 8.36, p378 of [Grebennikov 2007].
+
+The rest of the papers in the bibliography were highly enlightening regarding the principles of microwave oscillator design.
+
+For ease of design and simulation, selecting a device with both Touchstone S-parameters and SPICE models is greatly preferable.
+
+It is commonly claimed that FR4 is a 'slow' substrate, and that the high loss tangent of ~0.02 makes it unsuitable for microwave systems.
+
+However, with this PCB substrate, the expected loss of only 0.026 dB/mm on signals of minimum 0 dBm is patently acceptable.
+As viruses do not have a discriminating palate, we are also only minimally concerned with $S_{11}$ reflections, noise, or spurs, so precise impedance control is not required; the wideband VCO sweep accomodates for any variations in resonant frequency due to wide manufacturing tolerances.
+
+This topology of oscillator worked marvellously on essentially the first try.
+
+Not having a good analytical understanding, we resorted to using a purely computational method.
+
+In addition, the design of wideband feedback-loop VCOs is a relatively well-explored field, and many reference designs exist.
+
+Merely scaling designs like [] was not effective.
+
+Several analytical filter design methods were
+
+This is apparently known as a "double-tuned" wideband.
+
+Oscillators must meet the Barkhausen criterion:
+
+\begin{itemize}
+
+\item A 360 degree phase shift around the feedback loop (including the phase shift contribution from the amplifier, which itself varies greatly with frequency)
+\item A loop gain $>1.$
+
+\end{itemize}\
+%
+However, a third element is also required:
+%
+\begin{itemize}
+\item A frequency-selective element that restricts oscillation modes and decreases phase noise.
+\end{itemize}
+%
+
+With large feedback-loop structures, such as long PiN-switched phasing lines, proximity effects from nearby flesh would detune the oscillator significantly.
+
+ design of a triple-tuned oscillator.
+
+\paragraph{}
+The buffer amplifiers
 
@@
 In practice, the timestep required to obtain convergence in particularly tight corners of the SPICE simulation can drop to 1e-20, which is far below the Courant limit of the FDTD simulation.
-To eek out a bit more performance, a simple adaptive-timestep technique from [ a ] is used; we simply set the timestep so that the maximum change in voltage per timestep from the non-FDTD portion is less than some threshold.
+To eek out a bit more performance, a simple adaptive-timestep technique from [ a ] is used; we simply set the timestep so that the maximum change in voltage per timestep from the SPICE portion is less than some threshold.
 
-\PRLsep{{\itshape Wherein an oscillator is designed }}
+\PRLsep{{\itshape Power amplifier }}
+
+The amplifier and oscillator are separate for ease of design; this way the phase response of the amplifier is of no consequence.
+
+Our target power for the test is about 0.01 W, mandating a $2 \sqrt(2)$ V peak to peak RF swing on the Z=50 output.
+
+The $V_{CEO}$ breakdown of the bipolar transistor in question is only 2.3V.
+Above this value, current begins to flow from the emitter to the base, turning on the transistor and causing thermal runaway.
+If the base bias can source current,
+
+One solution would be to match the output to a lower impedance [Leuschner 2010]:
+
+\begin{quote}
+Generating high RF power from low supply voltages poses also another problem: the optimum load impedance of the PA output stage transistors becomes very small.
+A matching network with a high transformation ratio is needed to transform the antenna impedance of 50 to the optimum load impedance.
+High transformation ratios usually result in small bandwidth and higher losses.
+Possible solutions are the use of either non-standard high power RF devices or special circuit topologies using only the available standard devices.
+\end{quote}
+
+Use of so-called stacked, HiVP, or collector-feedback cascode designs can also allow the RF voltage to be distributed over many devices.
+
+\PRLsep{{\itshape Power sensing }}
 
@@
 
-The impedance of an antenna over frequency can be determined by:
+Method-of-moments solvers like NEC-2 are typical for simulating antennas.
+However, most commonly-available packages don't seem to handle multiple dielectric constants, such as the air and substrate for a patch antenna.
+
+The impedance of an antenna over frequency can be determined in FDTD by:
 
@@
 
-There's more than enough 'information entropy' in 2000 FDTD points for most antennas. But you need some 30,000 points to get 10 bins below 20 GHz!
+There's more than enough 'information entropy' in 4000 FDTD points for most antennas. But you need some 30,000 points to get 10 bins below 20 GHz!
 
@@
 
-A method of moments solver like NEC-2 may have provided faster results; but handling of multiple dielectrics does not seem to be simple.
-
 This technique is equivalent to that used in electrochemistry, known as fourier impedance spectroscopy - except they seem to usually use a known impedance source rather than a hard source, presumably because ideal hard sources don't exist in reality.
@@
 
-The units of the FFT (unlike those of the continuous FT) remain in volts
+The units of the FFT (unlike those of the continuous FT) remain in volts.
 
@@
 
-Many equations in papers on the FDTD method are supplied without explicit scaling factors.
-For instance, for use with flaport/fdtd the H-field to current line integral in [] requires scaling by $\mu_0  (dx/dt)$, where $\mu_0$ is the vacuum magnetic permittivity, dx the cell size, and dt the timestep - despite the equation already possessing a deceptive set of $dx$-es.
+Most equations in papers on the FDTD method are supplied without making the scaling factors explicit; some need multiplying by the Courant number, For use with flaport/fdtd the H-field to current line integral in [] requires scaling by $\mu_0 * (dx/dt)$, where $\mu_0$ is the vacuum magnetic permittivity, dx the cell size, and dt the timestep - despite the equation already possessing a deceptive set of $dx$-es.
 
 Naturally, if one is competent, this discrepancy will be immediately obvious.
-Those not dimensionally-intuitive, such as myself, find it useful to run a test using a unit-aware calculator such as {\it sharkdp/insect}.
+Those not dimensionally-intuitive, such as myself, find it useful to run dimensional analysis using a unit-aware calculator such as {\it sharkdp/insect}.
 
-\rule{\linewidth}{0.2pt}
+\PRLsep{{\itshape The antenna itself }}
 
-The impedance of a microstrip antenna varies with position on its plane. Probe feeds that couple a microstrip to a specific point are often used.
+The impedance of a patch antenna varies with position on its surface. Probe feeds to a specific point on the patch
+
+Unfortunately, patch antennas have a relatively narrow bandwidth.
 
@@
 
+Automatic, no-effort documentation of simulation and experiment runs is critical.
+
 It may be helpful to think of simulations very similarly to IRL experiments.
@@
 For comparison to experiment, having a webcam take an image of the assembled board is also helpful.
+
+Many months of testing have vanished into the ether due to
 
@@
 
-Write a paper to be understood; to be as clear and helpful as possible to the reader.
-
-\rule{\linewidth}{0.2pt}
-
 We have always encountered wasting extreme amounts of time on subtle assembly mistakes in hardware prototypes.
@@
 
-Many failures are perhaps the result of carelessness in modification and a lack of inspection; but others would only have been found by a 100\% electrical test.
+Many failures are the result of carelessness in modification and lack of inspection. Others would only have been found by a 100\% electrical test.
 
@@
 
-The ability to almost immediately compare simulation to experiment was quite important.
+The ability to almost immediately compare simulation to experiment was essential.
+
+\rule{\linewidth}{0.2pt}
+
+This project started at the tail end of a project to produce ceramics. Many weeks were wasted; I had convinced myself that ceramics were required over FR4.
+
+\rule{\linewidth}{0.2pt}
+
+I originally rationalized not contacting others about . There are some 10,000 labs working on a cure; it's not helpful to have random amateurs tying up expert time with ignorant flights of fancy.
+
+Later, as the project became more mature and seemed likely, this morphed into a sort of arrogance.
+
+An expert in microwave engineering could probably have completed this entire project in a few days, rather than the months it took us.
 

### 2020-07-11 electronics/phased_array/phased_array.cpp

@@ -1,4 +1,12 @@
 
 
+
+test(){
+    assert();
+}
 // Optimal phase relation from L. Azar et al. / NDT&E International 33 (2000) 1
 //
+
+int main(){
+
+}

### 2020-07-11 documents/paper.tex
Paper

@@
 
+Of course, this application is hardly much better than an N95 mask, except that it is non-disposable and provides protection for eyes and skin.
+
+Vomit
+
 [Vj] mention the importance of precise dosimetry. Even simple structures can produce hot-spots 
@@
 It is easy to produce megawatts of power at these frequency ranges using Klystrons.
-Assuming an appropriate antenna, a single 50MW SLAC XL-class klystron with a PRF of 180 Hz can sanitize almost a square kilometer every second.
-\footnote{A new meaning of 'asceptic field'.}
+Assuming an appropriate antenna, a single 50MW SLAC XL-class klystron with a PRF of 180 Hz could sanitize almost a square kilometer every second.
+\footnote{Giving 'asceptic field' new meaning.}
 
@@
 
-Especially combined with an integral titanium sorption pump,
+Especially combined with an integrated titanium sorption pump,
 

### 2020-07-11 electronics/simple_fdtd/run/microstrip.py

@@ -59,7 +59,7 @@ fluid_width = 1e-3
 
 pcb = fd.PCB(0.00005, xy_margin=15, z_margin=15)
 fd.initialize_grid(pcb,int((5e-3)/pcb.cell_size),int((microstrip_length)/pcb.cell_size),
-                                int(0.0025/pcb.cell_size), courant_number = None)
+                                int(0.0025/pcb.cell_size), courant_number = 0.4)
 
 fd.create_planes(pcb, 0.032e-3, 6e7)
 fd.create_substrate(pcb, substrate_thickness, substrate_dielectric_constant, 0.02, 9e9)

### 2020-07-13 documents/supplemental.tex
Analytic phased-array antenna test

@@
 
-Different versions of the IEEE standard have used equations of equivalent form but with different coefficients [Wu 2015]; it is very possible that we have retrieved the wrong standard.
+Different versions of the IEEE standard have used equations of equivalent form but with different coefficients [Wu 2015]; it is entirely possible that we have retrieved the wrong standard.
 
@@
 Above this value, current begins to flow from the emitter to the base, turning on the transistor and causing thermal runaway.
-If the base bias can source current,
+If the base bias has a low enough impedance and can source current, this $V_{CEO}$ can be violated safely.
+[Toshiba, Bipolar Transistors, some other paper on the strong base bias]
 
@@
 Use of so-called stacked, HiVP, or collector-feedback cascode designs can also allow the RF voltage to be distributed over many devices.
+
+It should also be noted that when stressed, these devices can fail with a slow power-output degradation over weeks, an effect not usually found in lower-frequency designs.
 
@@
 \rule{\linewidth}{0.2pt}
+
+\PRLsep{{\itshape Fluidics }}
+
+We had anticipated having to perform a large number of tests for optimization of the impulse.
+Automating tests also has the advantage of removing operator bias, and (in our case) minimizing artifacts from the sample holder.
+Since all the components were already computer-controlled, it seemed little extra effort.
+
+We originally planned on using techniques from the rapidly accelerating field of centrifugal microfluidics, using a broadband patch antenna smaller than the cuvette, and measuring transmission absorption.
+
+However, aligning seemed liable to produce artifacts; runout in the spindle could be
+
+Sterilization is often effected by cytotoxic gas []; not having such a setup, autoclaving was our only resort.
+
+In a crude version of transmission welding.
+Tx welding usually relies on one material being transparent, and the other opaque - clear and black plastics, for instance.
+We obtained nearly useable results by scuffing one surface and rubbing in fine graphite powder.
 
@@
 
+Numerology doesn't pay
+
+\rule{\linewidth}{0.2pt}
+
 The ability to almost immediately compare simulation to experiment was essential.

### 2020-07-13 electronics/phased_array/phased_array.py

@@ -1,0 +1,4 @@
+import numpy as np
+
+def dipole_E_field(point, ):
+    R = np.linalg.norm(point)

### 2020-07-13 documents/paper.tex
Austinman request

@@
 
+We've got a thing 
+that's called 
+Radar Love
+We've got a wave
+in the air
+
+The phased-array techdemo.
+
 \paragraph{{\Large the gist}}\
@@
 
-estabilishes that - unique to certain viruses, and apparently unlike human cellular structures, as we shall see - coincidentally have just the right size, shape, stiffness, and net charge distribution to form a weak (Q=2) spherical dipole resonance mode which couples well to the microwave spectrum at approximately the X-Band, around 7-10 GHz.
+estabilishes that - unique to certain viruses, and apparently unlike human cellular structures, as we shall see - coincidentally have just the right size, shape, stiffness, and net charge distribution to form a weak (Q=2) spherical dipole resonance mode which couples well to the microwave spectrum at approximately the X-Band, at around 8 GHz.
 
@@
 
-\lettrine{It} cannot be overstated how unexpected and dubious this finding appears to be -at least, based on our limited research and experience to date.
+If this mechanism exists, it would seem to provide significant advantages over existing UV or cold-plasma sterilization.
+
+If the extensions made in our paper are valid, this is a non-ionizing, non-thermal
+%
+\footnote{It may be useful to define 'non-thermal'; it caused us some confusion.
+Certainly the proteins of the virion locally absorb energy and increase in temperature.
+The key is that, when excited in this manner, the energies in the envelope are poorly modelled by a Maxwell-Boltzmann distribution; they are not given sufficient time to 'thermalize'.
+In contrast, with typical 2.4 GHz microwave exposure, sterilization can only occur by aggregate heating of the fluid and tissue.}
+%
+, non-chemical technique, harmless for continuous exposure to tissue, produces no ozone, can readily be produced with \$1 - scale devices.
+
+Moreover, it would act instantaneously, and - perhaps most critically - could be made to act {\bf within infected tissues}; and is minimally absorbed by air, allowing action in the far-field, scaling to square-kilometer areas with single installations.
+
+\begin{autem}
+
+{\it autem}\\
+
+That paragraph may cut an impressive figure; but recall that the rest of this paper
+
+\end{autem}
+
+\lettrine{It} cannot be overstated how unexpected and positively dubious this finding appears to be -at least, based on our limited research and experience to date.
 
@@
 It is difficult to reconcile this discrepancy. A failure tree is included below.
-
-If this mechanism exists, it would seem to provide the following advantages over other methods such as UV or cold-plasma sterilization:
-
-\begin{itemize}
-  \item This is a non-ionizing, non-thermal
-%
-\footnote{It may be useful to define 'non-thermal'; it caused us some confusion.
-Certainly the proteins of the virion locally absorb energy and increase in temperature.
-The key is that, when excited in this manner, the energies in the envelope are poorly modelled by a Maxwell-Boltzmann distribution; they are not given sufficient time to 'thermalize'.
-In contrast, with typical 2.4 GHz microwave exposure, sterilization can only occur by aggregate heating of the fluid and tissue.}
-%
-, non-chemical technique, harmless for continuous exposure to tissue, which produces no ozone, can be effective inside bodily tissues, and can readily be produced with \$1 - scale devices.
-
-  \item Potentially far-field and moderately penetrating inactivation. 
-  \item
-
-\end{itemize}
 
@@
 \footnote{All values have been converted to $\text{W/m}^2$ to avoid confusion. 100 $\text{ W/m}^2 = 10 \text{ mW/cm}^2 = 10 \text{ dBm/cm}^2$.}
-
-\begin{toolchain}
-	{\it \bf [Yang 2015]'s toolchain}
-	\begin{itemize}
-	\item Envelope/liposome breaking strength and stiffness from AFM nanoindentation data
-	\item Analytical expression assuming homogenous sphere for microwave absorption cross-section
-	\item Experimental absorption data from microwave cuvette -> 
-	\item COMSOL finite-element for illustration
-	\end{itemize}
-\end{toolchain}
 
@@
 
-Other physiological effects include changes in the permeability of membranes, direct nerve stimulation, and others.
-These are all accounted for in the time-domain equation and the 6-minute averaging period.
+Other physiological effects include changes in the permeability of membranes, direct nerve stimulation; these are all accounted for in the time-domain equation and the 6-minute averaging period.
 
-This would seem to open an obvious route of optimization.
+To drive home this point, apparently the best-quality evidence available fulfills sham requirements [Vijayalaxmi 2006] provide in-vitro.
+They expose blood lymphocytes to pulse power  in precisely the regime required in this work; 8.2 GHz, 8 ns duration and 50 khz repetition rate, pulse power densities of 250,000 $W/m^2$\footnote{computed from average power / duty cycle}, for 2 hours, and find no genotoxicity.
+[Chemeris 2004] use 8.8 GHz, 180 ns pulse width, peak power 65,000 W , repetition rate 50 Hz, exposure duration 40 min, on frog etheyrocytes?
+
+So it appears that this is not merely rules-lawyering to exploit a loophole in the regulations; it is a physically-informed effect.
+
+\begin{autem}
+
+These papers (the best quality we are aware of) were extensively cherry-picked from the literature based on the results of a meta-analysis [Vj.
+2019], listing the requirements for reliable in-vitro RF experiments.\\
+
+How sensitive this research is, [Chemeris 2004] mention:\\
+
+"The increase in DNA damage after exposure of cells to HPPP EMF shown in Table 2 was due to the temperature rise in the cell suspension by 3.5±0.1 ◦C.
+This was confirmed in sham-exposure experiments and experiments with incubation of cells for 40 min under the corresponding temperature conditions."\\
+
+There are a substantial number of papers in the literature which show positive effect sizes; these are listed in the bibliography. \\
+
+The literature reviews conducted by standards organizations.\\
+
+We are not aware of any past uses of these microwave en-masse. We do not have the
+
+\end{autem}
+
+This would seem to open an obvious avenue of optimization.
 If the virus is destroyed in tens of nanoseconds - essentially governed by instantaneous power.
@@
 
-\paragraph{\textbf{Direct treatments}}\
+\paragraph{\textbf{Direct treatments at the fundamental}}\
 
-[Hand 1982] $E_{mag}=1/e$ (13.5\% power density) skin\footnote{electromagnetic skin, not tissue skin}\footnote{well, both, I suppose.} depth is approximately:
+Via [Hand 1982], the $E_{mag}=1/e$ penetration depth\footnote{"skin skin depth?"} is approximately 40 mm for 'dry' tissues and 5 mm for 'wet'.
 
-\begin{center}
-\begin{tabular}{|l|l|l|}
-\hline
-F=10 GHz          & Dry tissue & Wet tissue \\ \hline
-Penetration depth & 30 mm      & 5 mm \\ \hline
-\end{tabular}
-\end{center}
+SARS is found widely distributed throughout many of the most favoured organs [Ding 2004], shielded by an average of 4 cm of chest wall [Schroeder 2013]; so safe external treatment of the body is unlikely.
 
-SARS is found widely distributed throughout the most favorable organs [Ding 2004], shielded by an average of 4 cm of chest wall [Schroeder 2013]; so safe external treatment of the body is unlikely.
-
-However, destruction of lung tissue appears to be the primary cause of death via SARS [Nicholls 2006].
+However, destruction of lung tissue appears to be significant in the lethality of SARS [Nicholls 2006].
 
@@
 The main bronchus is about 8 mm in diameter, which is smaller than the patch antenna used here; a monopole (or multiple, phased monopoles) like is probably more suitable.
+
+\paragraph{\textbf{Subharmonics}}\
+
+The 8 GHz wave need not be the fundamental.
+A modulated carrier wave with a more deeply penetrating wavelength which then locally interferes to produce the 8 GHz tone within the tissue could be useful.
+
+The penetration depth shortens as frequency increases, until the so-called 'optical windows' in the absorption spectra of tissues, particularly in the near-IR range.
 
@@
 Luckily, this project falls perfectly within the subset of microwave technologies that do not require a goatee.
-The vast majority of the behavior of most circuits can be modelled with the very same SPICE tools as one would use at low frequencies.
+The vast majority of the behavior of most circuits can be accurately modelled with the very same SPICE tools as one would use at low frequencies.
 With judicious application of reference designs, it seems to be possible to design
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-We've got a thing 
-that's called 
-Radar Love
-We've got a wave
-in the air
-Radar Love
 

### 2020-07-13 documents/supplemental.tex
Austinman request

@@
 
+Th edges are charred; however, we have not found any discussion of toxicity of the laser cut edges, so we assume they're fine.
+
 In a crude version of transmission welding.
@@
 We obtained nearly useable results by scuffing one surface and rubbing in fine graphite powder.
+
+Not all plastics can be laser welded.
+
+One problem with the formal, academic paper format is that one starts to believe what is written, which is a death sentence for accurate reasoning. We try to avoid this by being unprofessional.
 

### 2020-07-15 documents/paper.tex
Layer 0

@@
 
-That paragraph may cut an impressive figure; but recall that the rest of this paper
+That paragraph may cut an impressive figure; but it hinges on all the rest of this paper being correct.
 
@@
 To drive home this point, apparently the best-quality evidence available fulfills sham requirements [Vijayalaxmi 2006] provide in-vitro.
-They expose blood lymphocytes to pulse power  in precisely the regime required in this work; 8.2 GHz, 8 ns duration and 50 khz repetition rate, pulse power densities of 250,000 $W/m^2$\footnote{computed from average power / duty cycle}, for 2 hours, and find no genotoxicity.
-[Chemeris 2004] use 8.8 GHz, 180 ns pulse width, peak power 65,000 W , repetition rate 50 Hz, exposure duration 40 min, on frog etheyrocytes?
+They expose blood lymphocytes to pulse power  in precisely the regime required in this work; 8.2 GHz, 8 ns duration and 50 khz repetition rate, pulse power densities of 250,000 $\text{W/m}^2$\footnote{computed from average power / duty cycle}, average power 100 $\text{W/m}^2$ \footnote{the safety limit}, for 2 hours, finding no change in any of the measured quantities.
+[Chemeris 2004] use 8.8 GHz, 180 ns pulse width, peak power 65,000 W, repetition rate 50 Hz, exposure duration 40 min, on frog etheyrocytes, and find genotoxicity only from the temperature rise.
 
@@
 
-How sensitive this research is, [Chemeris 2004] mention:\\
+How sensitive this research is, [Chemeris 2004] mention:
 
-"The increase in DNA damage after exposure of cells to HPPP EMF shown in Table 2 was due to the temperature rise in the cell suspension by 3.5±0.1 ◦C.
-This was confirmed in sham-exposure experiments and experiments with incubation of cells for 40 min under the corresponding temperature conditions."\\
+\begin{quote}
+
+The increase in DNA damage after exposure of cells to HPPP EMF shown in Table 2 was due to the temperature rise in the cell suspension by $3.5\pm0.1^{\circ}  $C.
+This was confirmed in sham-exposure experiments and experiments with incubation of cells for 40 min under the corresponding temperature conditions."
+
+\end{quote}
 
@@
 This would seem to open an obvious avenue of optimization.
-If the virus is destroyed in tens of nanoseconds - essentially governed by instantaneous power.
-But tissue damage requires *energy deposition*.
+If the virus is destroyed in tens of nanoseconds via an electric field amplitude incidentally caused by an instantaneous power $\text{P}$, but tissue damage requires an energy deposition $\text{P}  \cdot  \text{dt}$, then we should minimize dt.\\
 
-Obviously, the solution is thus to turn the CW microwave signal into an effectively instantaneous pulse.
+We thus turn the CW microwave signal into an effectively instantaneous pulse.
 
@@
 
-However, [Oberoi 2012] find that they can detect a single E. Coli bacterium in 50 uL of broth via a microwave cavity. This is so unbelievable that we are inclined to look for methodological issues.
+However, [Oberoi 2012] find that - in controlled conditions - they can detect a single E. Coli bacterium in 50 uL of broth via a microwave cavity.
 
-Frequency-domain measurements can be made with incredible precision; and there are many parameters by which virions could be discriminated; ring-up time of the resonance, excitation non-linearity, precise microwave spectroscopy, etc.
+Of course, discriminating miniscule returns in free-space is not easy; but with precise knowledge of this resonance mode, it may become somewhat easier.
+Frequency-domain measurements can be made with incredible precision; and there are many parameters by which virions could be discriminated; ring-up time of the resonance, excitation non-linearity, etc.
 
@@
 
-Finally, there is one concern. It has been shown that virions can effect large-scale changes in the electric charges of their [].
+It has been shown that virions can effect large-scale changes in the electric charges of their [].
 
 Use of this technique will provide a selection bias towards immunity to electromagnetic fields, which could perhaps be effected by preferring extreme-sized mutants (shifting the resonance away from the applied field).
-We do not have the biological knowledge to know if this is plausible; it is simply worth mentioning.
+
+We do not have the biological knowledge to know if this is plausible; it simply seemed worth mentioning.
 

### 2020-07-15 biology/data/net_charge.py

@@ -1,0 +1,34 @@
+from localcider.sequenceParameters import SequenceParameters
+import glob
+#
+ 
+# NOTE: Where pH values can be provided, if left blank we assume a neutral pH where only R/K/D/E are charged. If a pH value is provided, then R/K/D/E/C/Y/H are all considered titratable residues using EMBOSS pKa values, listed below: ‘C’: 8.5, ‘Y’: 10.1, ‘H’: 6.5, ‘E’: 4.1, ‘D’: 3.9, ‘K’: 10.0, ‘R’: 12.5
+
+files = glob.glob('protein_sequences/*.*')
+for file in files:
+    print(file)
+    contents = open(file).read().split('>')
+    #can't use SeqParam(seqfile=file)
+    #because all the sequences are appended to each other.
+    output = open("charge" + file)
+    for protein in [x for x in contents if x]:
+
+        header = protein[0:protein.index('\n')]
+        seq = protein[protein.index('\n'):-1] 
+
+        print(header)
+        if('X' in seq):
+            print("Warning: unspecified protein encountered.")
+        seq = seq.replace('X', '')
+
+
+        seq_param = SequenceParameters(seq)
+
+        #mean_net_charge is always positive, whereas
+        # net_charge_per_residue is alternating
+        net_charge = seq_param.get_NCPR(pH=7.0)*seq_param.get_length()
+        print(net_charge)
+    
+        output.write()
+
+    output.close()

### 2020-07-16 documents/introduction.tex
Frame

@@
-\title{On the application of microwave acoustic resonant viral inactivation
-\thanks{I would be delighted to include any criticisms or comments anyone may have, both on substance and comprehensibility; preferably leave them on the GitHub issues page, or email therobotist@gmail.com, @0xDBFB7 on Twitter, or irc.0xDBFB7.com:6667 \#covid.}}
-\date{May 2020}
-\author{Based primarily on exceptional work by }
-
-\begin{document}
-
 \flushbottom 
@@
 \thispagestyle{empty}
-
-\begin{textblock}{5}(1,1)
-\noindent Please view the latest version at github.com/0xDBFB7/covidinator
-\end{textblock}
-%\begin{textblock}{5}(1,27)
-%\end{textblock}
-
-\null\begin{tabular}[t]{l@{}}
-  {Daniel Correia}\ \orcidlink{0000-0002-9353-0216}  \\
-  \textit{????????? York??????}
-\end{tabular}
-
-\begin{abstract}
-
-We extend this landmark work rather trivially by:\\
-
-Aims:
-
-\begin{itemize}
-  \item Establishing the time dependence of inactivation
-  \item Demonstrating a modulation scheme that decreases the inactivation threshold to below current safety levels in surrogate bacteriophage
-  \item Demonstrating a prototype emitter in an "electromagnetic mask" form-factor, costing about \$5 in prototype quantities, which can reasonably be produced in 10 million-of quantities
-  \item Testing power thresholds in various conditions; biological fluids of various conductivities and pHs
-  \item Using a coarse-grained molecular-dynamics simulation to optimize the impulse
-  \item Using a virus-in-the-loop optimization with a centrifugal microfluidic system
-  \item Discussing the biological basis for the safety of the device
-  \item Showing that the deviation from the expected theshold could be explained by variance in the
-
-\end{itemize}
-
-{Perhaps notable that a completely free and open-source toolchain was used for the entire project, including FDTD microwave antenna optimization. This work can be replicated with \$500 in equipment.}
-
-\end{abstract}
 
@@
 
-	While our study is very simple, biology is of such complexity that a tremendous amount of care must be taken before any conclusion can be drawn at all.
+	While our study is very simple, biological research is of such complexity that a tremendous amount of care must be taken before any conclusion can be drawn at all.
 It is not likely that we have taken sufficient care.\\
 
-This is especially true with RF biophysics. The literature is littered with otherwise impeccably perormed research which was later demonstrated to be an artifact. \\
+This is especially true with RF biophysics. The literature is littered with otherwise impeccably perormed research which is both difficult to find fault in, and faulty. \\
+
+This paper does not contribute to the state of the art at all, except perhaps in the obvious avenue of time-domain modulation; [Hung 2014] have already demonstrated a reflectarray, and the rest of our discussion is anything but novel.
 
@@
 
-	Additionally, other sterilization techniques may produce superior results with less faffing about and should be evaluated in the same context. Data on far UV [Buonanno 2017] indicates safety.\\
+	Additionally, other sterilization techniques may produce superior results with less faffing about and should be evaluated in the same context.
+For instance, data on far UV [Buonanno 2017] indicates safety.\\
 
-It has occurred before that otherwise striking resonances were detected and replication found them to be artifacts of the measurement equipment. [Foster 1987] even offers this disclaimer:
+Accurate microwave measurements are rife with parasitics and sensitivities.
+It has occurred before that otherwise striking resonances were detected, and further replication found them to be artifacts of the measurement equipment.
+[Foster 1987] even offers this disclaimer:\\
+
+\begin{quote}
 
@@
 more precise instrumentation used in this study. Such data
-are easily misinterpreted, and we suggest this might have
-happened in the former study."
+are easily misinterpreted".
 
-The direct inactivation plaque and PCR data from [Yang], replicated by [Sun], is a somewhat convincing corroboration that this effect is not an artifact, but hundreds of convincing and  wrong papers exist in the literature.
-Our data is crude and imprecise, our equipment hastily constructed, and should not be considered validation of this effect even existing.
-\\
+\end{quote}
+
+The direct inactivation plaque and PCR data in the referenced papers are somewhat convincing corroboration that this effect is not an artifact; but hundreds of convincing and wrong papers exist in the literature.\\
+
+ Our data is crude and imprecise, our equipment hastily constructed, and should not be considered validation of this effect even existing. \\
+
+Even if this effect exists and is as effective as it appears, it could still be impractical to apply for any number of reasons.\\
 

### 2020-07-16 documents/supplemental.tex
Frame

@@
 
+\PRLsep{{\itshape Power sensing }}
+
+The diode detector power sensor is based on the Infineon appnote [] and [], itself based on a circuit from The Art Of Electronics.
+
+A detailed description of various diode detectors are found in []. Because the steady-state current through the detector is very small, the microstrip can simply be terminated in the standard manner.
+
+The Mini-Circuits ZX47-40-S+ would be an excellent low-cost COTS alternative.
+
 \PRLsep{{\itshape Fluidics }}
@@
 
-However, aligning seemed liable to produce artifacts; runout in the spindle could be
+Centrifugal microfluidics has the advantage of getting a pump for free; mixing can be effected by generating vortexes by accelerating and decelerating quickly; and because everything is circular, it is easier to design equidistant.
 
-Sterilization is often effected by cytotoxic gas []; not having such a setup, autoclaving was our only resort.
+However, aligning seemed liable to produce artifacts; runout in the spindle;
+
+Sterilization is often effected by cytotoxic gas []. UV we resorted to autoclaving, warping.
 
@@
 
+Both the hydrophobicity / wetting angle of the substrate (useful for valves with a certain threshold pressure, among other things), the adhesive surface energy, and sterilization can all be effected by UVC exposure.
+Unfortunately, we were not confident in the homogeneity of the
+
 Not all plastics can be laser welded.
+
+3DuF; this is an excellent program
 

### 2020-07-16 mechanical/microfluidic/generate_slide.py

@@ -6,19 +6,78 @@ import os
 OPENSCAD_BINARY = "~/Programs/OpenSCAD-2019.05-x86_64.AppImage"
 #OpenSCAD 2015 doesn't add units to SVG output.
 
-FRAME_WIDTH = 50
-FRAME_HEIGHT = 1.58
+#Mylar 0.10mm -
+#9495MP 0.14mm - channel
+#Mylar 0.10mm - channel
+#9495MP 0.14mm - channel
+#Mylar 0.10mm
 
-CUVETTE_LENGTH = 5
+thicknesses = [0.10, 0.14]
 
-WINDOW_LENGTH = 10
+FRAME_WIDTH = 50.0
+FRAME_THICKNESS = 3.175
+FRAME_X_MARGIN = 8.0
+FRAME_END_MARGIN = FRAME_WIDTH/2
+CENTERLINE = FRAME_WIDTH / 2.0
+
+WINDOW_LENGTH = 10.0
+
+O_RING_OD = 4.15 # McMaster-Carr 003 size Viton O-ring
+SYRINGE_OD = 1.8
+
+TEXT_SIZE = 3
+
+ID = 0
+
+IR_ENCODER_SLIT_WIDTH = 0.1
+IR_ENCODER_SLIT_LENGTH = 5
+
+NUM_CUVETTES = 10
+CUVETTE_SPACING = 4.0 # between
+CUVETTE_LENGTH = 5.0
+CUVETTE_WIDTH = 0.8
+
+LEADER_HOLE_DIA = 2.0
+
+FRAME_LENGTH = ((CUVETTE_WIDTH/2.0) + CUVETTE_SPACING) * (NUM_CUVETTES) + 3.0*LEADER_HOLE_DIA + FRAME_MARGIN
+
+layer_0 = square([FRAME_WIDTH, FRAME_LENGTH],center=False)
+layer_0 -= translate([1,1])(text("0 M ID 0", TEXT_SIZE))
+layer_0 -= translate([CENTERLINE,FRAME_LENGTH - (LEADER_HOLE_DIA*1.5)])(circle(d=LEADER_HOLE_DIA))
+
+layer_1 = square([FRAME_WIDTH, FRAME_LENGTH],center=False)
+layer_1 -= translate([1,1])(text("1 A", TEXT_SIZE))
[…]

### 2020-07-16 documents/paper.tex
Reworked paper slightly

@@
 
-\include{title}
+\begin{document}
 
-\include{introduction}
+\subfile{title}
+
+\subfile{introduction}
 
@@
 
-estabilishes that - unique to certain viruses, and apparently unlike human cellular structures, as we shall see - coincidentally have just the right size, shape, stiffness, and net charge distribution to form a weak (Q=2) spherical dipole resonance mode which couples well to the microwave spectrum at approximately the X-Band, at around 8 GHz.
+estabilishes that - unique to certain viruses, and apparently unlike human cellular structures, as we shall see - coincidentally have just the right size, shape, stiffness, and net charge distribution to form a weak (Q=2) spherical dipole resonance mode which couples well to the microwave spectrum at approximately 8 GHz.
 
-More critically, [Yang 2015] (and, in parallel, [Hung 2014]) theoretically model and then experimentally validate in various strains of Influenza A that - due to this acoustic-resonance effect - the power levels required to crack the lipid envelope are on the order of magnitude of the safety limits even for continous point-blank exposure.\footnote{See supplemental.}
+More critically, [Yang 2015] (and, in parallel, [Hung 2014]) theoretically model and then experimentally validate in various strains of Influenza A that - due to this acoustic-resonance effect - the power density levels required to crack the lipid envelope are near the safety limits for continuous exposure to humans.\footnote{Sort of.
+See below and supplemental.}
 
@@
 
-Like pumping a swing, this effect allows an otherwise inconsequential field magnitude to store energy over a small number of cycles until the virus is destroyed.
+Like pumping a swing, this effect allows an otherwise inconsequential field magnitude to store energy over a small number of cycles until the virus is destroyed. \\
+\\\\
+
+\paragraph{Ramifications}\
 
@@
 %
-, non-chemical technique, harmless for continuous exposure to tissue, produces no ozone, can readily be produced with \$1 - scale devices.
+, non-chemical technique, harmless for continuous exposure to tissue, which can sterilize air and surfaces alike, including skin, eyes, and within hair; it evolves no ozone, can readily be generated with \$1 USD - scale devices, acts instantaneously, and - perhaps most critically - could be made to act {\bf within infected tissues}.
 
-Moreover, it would act instantaneously, and - perhaps most critically - could be made to act {\bf within infected tissues}; and is minimally absorbed by air, allowing action in the far-field, scaling to square-kilometer areas with single installations.
+The X-band is also minimally absorbed by air, allowing action in the far-field and scaling to square-kilometer areas with single installations.
 
@@
 {\it autem}\\
-
-That paragraph may cut an impressive figure; but it hinges on all the rest of this paper being correct.
+The previous paragraph may cut an impressive figure; but it hinges on all the rest of this paper being correct.
 
@@
 
-For even the RF power limits set by standards organizations appear to be based on the observation that few significant resonance modes exist in biological tissues, and (as we shall see), this is grounded in solid {\it in vitro} (albeit limited {\it in vivo}) evidence.
+For even the RF power limits set by standards organizations appear to be based on the observation that few significant resonance modes exist in biological tissues, and (as we shall see), this is grounded in solid {\it in vitro} (albeit more limited {\it in vivo}) evidence.
 
@@
 
-It is difficult to reconcile this discrepancy. A failure tree is included below.
+The precise structure and charge of the virion appears to be a singular anomaly in this otherwise catagorical non-existence.
 
@@
 \end{multicols}
+\clearpage
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\clearpage
-
-[IEEE C95.1-2005], Annex B, "Identification of levels of RF exposure responsible for adverse
-effects: summary of the literature",
+A poignant summary of the consensus is found in [IEEE C95.1-2005], Annex B, "Identification of levels of RF exposure responsible for adverse effects: summary of the literature".
 
 \begin{quote}
+%%%%%%%%%%%
 Further examination of the RF literature reveals no reproducible low level (non-thermal) effect that would
@@
 
-The human body contains proteins with all sorts of net charges.
+Unfortunately, the buried lede is that the power levels shown by [Yang 2015] are about twice the continuous safety levels.
 
-Other physiological effects include changes in the permeability of membranes, direct nerve stimulation; these are all accounted for in the time-domain equation and the 6-minute averaging period.
+However, there is an obvious avenue of optimization.
+If the virus is destroyed in a few dozen nanoseconds via an electric field amplitude incidentally caused by an instantaneous power $\text{P}$, but tissue damage requires a temperature rise due to an energy deposition $\text{P} \  \text{dt}$, then we should minimize dt.\
+
+We thus turn the CW microwave signal into a series of effectively instantaneous pulses.
+
+The safety standards of [IEEE] and [ICNIRP] account for such time-domain modulation by specifying both an average power limit over a 6 minute period, and a time-integrated energy deposition limit.
+All known non-thermal and thermal physiological effects, including changes in the permeability of membranes, direct nerve stimulation, etc, are accounted for by obeying those two limits.
 
 To drive home this point, apparently the best-quality evidence available fulfills sham requirements [Vijayalaxmi 2006] provide in-vitro.
-They expose blood lymphocytes to pulse power  in precisely the regime required in this work; 8.2 GHz, 8 ns duration and 50 khz repetition rate, pulse power densities of 250,000 $\text{W/m}^2$\footnote{computed from average power / duty cycle}, average power 100 $\text{W/m}^2$ \footnote{the safety limit}, for 2 hours, finding no change in any of the measured quantities.
-[Chemeris 2004] use 8.8 GHz, 180 ns pulse width, peak power 65,000 W, repetition rate 50 Hz, exposure duration 40 min, on frog etheyrocytes, and find genotoxicity only from the temperature rise.
+They expose blood lymphocytes to pulse power in precisely the regime required in this work; 8.2 GHz, 8 ns duration and 50 khz repetition rate, a whopping pulse power density of 250,000 $\text{W/m}^2$\footnote{computed from average power / duty cycle} (2500x the time-averaged power density safety limit), average power density 100 $\text{W/m}^2$ (the safety limit), for 2 hours, finding no change in any of the measured quantities.
+
+Simlarly, [Chemeris 2004] use 8.8 GHz, 180 ns pulse width, peak power 65,000 W, repetition rate 50 Hz, exposure duration 40 min, on frog etheyrocytes, and find genotoxicity only from the temperature rise.
 
@@
 
-How sensitive this research is, [Chemeris 2004] mention:
+To illustrate how sensitive this research is, [Chemeris 2004] mention:
 
@@
 
-This would seem to open an obvious avenue of optimization.
-If the virus is destroyed in tens of nanoseconds via an electric field amplitude incidentally caused by an instantaneous power $\text{P}$, but tissue damage requires an energy deposition $\text{P}  \cdot  \text{dt}$, then we should minimize dt.\\
+\cite{POLAROGRAPHICOXYGENSENSORS}
 
-We thus turn the CW microwave signal into an effectively instantaneous pulse.
+\bibliography{flagship}
 
@@
 Such a mechanism could perhaps extend the exposure required to break the capsid or membrane.
-Other mechanisms could include some sort of lipid denaturation, requiring an absolute amount of energy absorption to break or twist bonds and modify the properties before the envelope fractures.
+Other mechanisms could include some sort of lipid denaturation, requiring an absolute amount of energy absorption to break or twist bonds and modify properties before the envelope fractures.
 
@@
 
+\bibliography{1.bib}{}
+\bibliographystyle{plain}
 \end{document}

### 2020-07-16 documents/cite_processor.py

@@ -15,3 +15,6 @@ items = refs["items"]
 # they can also be standalone notes, with the key "note" present.
 
 print(collections)
+
+
+files = glob.glob('*.tex')

### 2020-07-16 documents/backup/backup_paper.tex
Quick lil citation processor
Cite processor almost done

--- 2020-07-16 documents/paper.tex
@@
 
-We've got a thing 
-that's called 
-Radar Love
-We've got a wave
-in the air
+\supercite{Yang Efficient 2016}[1789 \href{https://doi.org/10.1038/srep18030}{\faExternalLink}]
+\supercite{Yang Efficient 2016}[1789 \href{https://doi.org/10.1038/srep18030}{\faExternalLink}]
 
-The phased-array techdemo.
+\supercite{Yang Efficient 2016}[1789 \href{https://doi.org/10.1038/srep18030}{\faExternalLink}]
 
-\paragraph{{\Large the gist}}\
-
-The chain of literature 
-%
-[Fr\"{o}hlich 1968] \textrightarrow \ [Fr\"{o}hlich 1980] \textrightarrow \ [Liu 2009] \textrightarrow \ ([Hung 2014] $\parallel$ [Yang 2015] $\parallel$ [Sun 2017])\footnote{We have not conducted a thorough review; many more papers are probably involved.} apparently culminates in the flagship work we focus on in this paper,
-
-{\it Efficient Structure Resonance Energy Transfer from Microwaves to Confined Acoustic Vibrations in Viruses} [Yang 2015].
-%
-
-estabilishes that - unique to certain viruses, and apparently unlike human cellular structures, as we shall see - coincidentally have just the right size, shape, stiffness, and net charge distribution to form a weak (Q=2) spherical dipole resonance mode which couples well to the microwave spectrum at approximately 8 GHz.
+[Frolich 1968] [Frolich 1980] \textrightarrow \ ([Hung 2014] $\parallel$ [Yang 2015] $\parallel$ [Sun 2017])\footnote{We have not conduc98 \href{https://doi.org/10.2514/3.29363}{\faExternalLink}ently unlike human cellular structures, as we shall see - coincidentally have just the right size, shape, stiffness, and net charge distribution to form a weak (Q=2) spherical dipole resonance mode which couples well to the microwave spectrum at approximately 8 GHz.
 
@@
 
-\bibliography{flagship}
+\collect{Flagship}
 

### 2020-07-17 documents/backup/backup_paper.tex
screw it, good enough.

@@
 \begin{document}
+
+\nocite{*}
 
@@
 
-\supercite{Yang Efficient 2016}[1789 \href{https://doi.org/10.1038/srep18030}{\faExternalLink}]
-\supercite{Yang Efficient 2016}[1789 \href{https://doi.org/10.1038/srep18030}{\faExternalLink}]
+[Frolich 1968] [Frolich 1980] \textrightarrow \ (\supercite{[Hung reflectarray 2014]}[\cite{hungFocusingReflectarrayIts2014} \href{https://doi.org/10.1002/2014RS005481}{\faExternalLink}] $\parallel$ \supercite{[Yang Efficient 2015]}[\cite{yangEfficientStructureResonance2015} \href{https://doi.org/10.1038/srep18030}{\faExternalLink}] $\parallel$ \supercite{[Sun rod-shaped 2017]}{})\footnote{We have not conducently unlike human cellular structures, as we shall see} - coincidentally have just the right size, shape, stiffness, and net charge distribution to form a weak (Q=2) spherical dipole resonance mode which couples well to the microwave spectrum at approximately 8 GHz.
 
-\supercite{Yang Efficient 2016}[1789 \href{https://doi.org/10.1038/srep18030}{\faExternalLink}]
-
-[Frolich 1968] [Frolich 1980] \textrightarrow \ ([Hung 2014] $\parallel$ [Yang 2015] $\parallel$ [Sun 2017])\footnote{We have not conduc98 \href{https://doi.org/10.2514/3.29363}{\faExternalLink}ently unlike human cellular structures, as we shall see - coincidentally have just the right size, shape, stiffness, and net charge distribution to form a weak (Q=2) spherical dipole resonance mode which couples well to the microwave spectrum at approximately 8 GHz.
-
-More critically, [Yang 2015] (and, in parallel, [Hung 2014]) theoretically model and then experimentally validate in various strains of Influenza A that - due to this acoustic-resonance effect - the power density levels required to crack the lipid envelope are near the safety limits for continuous exposure to humans.\footnote{Sort of.
+More critically, [\cite{dahlPixelRecursiveSuper2017}] (and, in parallel, [Hung 2014]) theoretically model and then experimentally validate in various strains of Influenza A that - due to this acoustic-resonance effect - the power density levels required to crack the lipid envelope are near the safety limits for continuous exposure to humans.\footnote{Sort of.
 See below and supplemental.}
@@
 
-For even the RF power limits set by standards organizations appear to be based on the observation that few significant resonance modes exist in biological tissues, and (as we shall see), this is grounded in solid {\it in vitro} (albeit more limited {\it in vivo}) evidence.
+For even the RF power limits set by standards organizations appear to be based on the observation that no significant resonance modes exist in biological tissues, and (as we shall see), this is grounded in solid {\it in vitro} (albeit more limited {\it in vivo}) evidence.
 
@@
 \cite{POLAROGRAPHICOXYGENSENSORS}
-
-\collect{Flagship}
 
@@
 
-\bibliography{1.bib}{}
-\bibliographystyle{plain}
+\bibliography{references}
+
+\bibliographystyle{}
+
 \end{document}

### 2020-07-17 documents/paper.tex
screw it, good enough.

@@
 
+\nocite{*}
+
 \subfile{title}
@@
 \clearpage
+
+\bibliographystyle{plainnat}
 
@@
 
-We've got a thing 
-that's called 
-Radar Love
-We've got a wave
-in the air
+\cite{frohlichLongrangeCoherenceEnergy1968} \textrightarrow \ \cite{frohlichBiologicalEffectsMicrowaves1980} \textrightarrow \ (\cite{hungFocusingReflectarrayIts2014} $\parallel$ \cite{yangEfficientStructureResonance2015} $\parallel$ \cite{sunResonantDipolarCoupling2017})\footnote{We have not conducently unlike human cellular structures, as we shall see} - coincidentally have just the right size, shape, stiffness, and net charge distribution to form a weak (Q=2) spherical dipole resonance mode which couples well to the microwave spectrum at approximately 8 GHz.
 
-The phased-array techdemo.
-
-\paragraph{{\Large the gist}}\
-
-The chain of literature 
-%
-[Fr\"{o}hlich 1968] \textrightarrow \ [Fr\"{o}hlich 1980] \textrightarrow \ [Liu 2009] \textrightarrow \ ([Hung 2014] $\parallel$ [Yang 2015] $\parallel$ [Sun 2017])\footnote{We have not conducted a thorough review; many more papers are probably involved.} apparently culminates in the flagship work we focus on in this paper,
-
-{\it Efficient Structure Resonance Energy Transfer from Microwaves to Confined Acoustic Vibrations in Viruses} [Yang 2015].
-%
-
-estabilishes that - unique to certain viruses, and apparently unlike human cellular structures, as we shall see - coincidentally have just the right size, shape, stiffness, and net charge distribution to form a weak (Q=2) spherical dipole resonance mode which couples well to the microwave spectrum at approximately 8 GHz.
-
-More critically, [Yang 2015] (and, in parallel, [Hung 2014]) theoretically model and then experimentally validate in various strains of Influenza A that - due to this acoustic-resonance effect - the power density levels required to crack the lipid envelope are near the safety limits for continuous exposure to humans.\footnote{Sort of.
+More critically, [] (and, in parallel, [Hung 2014]) theoretically model and then experimentally validate in various strains of Influenza A that - due to this acoustic-resonance effect - the power density levels required to crack the lipid envelope are near the safety limits for continuous exposure to humans.\footnote{Sort of.
 See below and supplemental.}
@@
 \cite{POLAROGRAPHICOXYGENSENSORS}
-
-\bibliography{flagship}
 
@@
 
-\bibliography{1.bib}{}
-\bibliographystyle{plain}
+\bibliography{references}
+
 \end{document}

### 2020-07-17 documents/paper.tex
Texstudio

@@
+% arara: pdflatex: { shell: yes } 
+% arara: biber
+% arara: pdflatex: { shell: yes }
+% arara: clean: { files: [ test.aux, test.log] }
+
 \documentclass[fleqn,10pt]{article}
@@
 
-\bibliographystyle{plainnat}
+%\bibliographystyle{plainnat}
 
@@
 
-A poignant summary of the consensus is found in [IEEE C95.1-2005], Annex B, "Identification of levels of RF exposure responsible for adverse effects: summary of the literature".
+A poignant summary of the consensus is found in \cite{instituteofelectricalandelectronicsengineersIEEEC95120052006}, Annex B, "Identification of levels of RF exposure responsible for adverse effects: summary of the literature".
 
@@
 
-\cite{POLAROGRAPHICOXYGENSENSORS}
+\clearpage
+\printbibliography[heading=none, title={}, keyword={Flagship}]
+\printbibliography[heading=none, title={}, keyword={standards}]
 
@@
 
-\bibliography{references}
+%\printbibliography[ title={Other references}]
 

### 2020-07-17 documents/paper.tex
Enough bibtex. Let's go back to hardware.

@@
 
-%\bibliographystyle{plainnat}
-
 \paragraph{To-do list}
@@
 
-\cite{frohlichLongrangeCoherenceEnergy1968} \textrightarrow \ \cite{frohlichBiologicalEffectsMicrowaves1980} \textrightarrow \ (\cite{hungFocusingReflectarrayIts2014} $\parallel$ \cite{yangEfficientStructureResonance2015} $\parallel$ \cite{sunResonantDipolarCoupling2017})\footnote{We have not conducently unlike human cellular structures, as we shall see} - coincidentally have just the right size, shape, stiffness, and net charge distribution to form a weak (Q=2) spherical dipole resonance mode which couples well to the microwave spectrum at approximately 8 GHz.
+We've got a thing 
+that's called 
+Radar Love
+We've got a wave
+in the air
+
+The phased-array techdemo.
+
+\paragraph{{\Large the gist}}\
+
+The chain of literature 
+%
+\cite{Longrange1968} \textrightarrow \ \cite{Biological1980} \textrightarrow \ [Liu 2009] \textrightarrow \ ([Hung 2014] $\parallel$ [Yang 2015] $\parallel$ [Sun 2017])\footnote{We have not conducted a thorough review; many more papers are probably involved.} apparently culminates in the flagship work we focus on in this paper,
+
+{\it Efficient Structure Resonance Energy Transfer from Microwaves to Confined Acoustic Vibrations in Viruses} [Yang 2015].
+%
+
+which establishes that - unique to certain viruses, and apparently unlike human cellular structures, as we shall see - coincidentally have just the right size, shape, stiffness, and net charge distribution to form a weak (Q=2) spherical dipole resonance mode which couples well to the microwave spectrum at approximately 8 GHz.
 
@@
 
-A poignant summary of the consensus is found in \cite{instituteofelectricalandelectronicsengineersIEEEC95120052006}, Annex B, "Identification of levels of RF exposure responsible for adverse effects: summary of the literature".
+A poignant summary of the consensus is found in \cite{IEEE2006}, Annex B, "Identification of levels of RF exposure responsible for adverse effects: summary of the literature".
 

### 2020-07-17 mechanical/microfluidic/generate_slide.py
Microfluidic

@@ -3,14 +3,16 @@ from solid.utils import *
 # pip install git+https://github.com/SolidCode/SolidPython.git
 import os
 
+#when-changed generate_slide.py -v -c "python %f"
+
 OPENSCAD_BINARY = "~/Programs/OpenSCAD-2019.05-x86_64.AppImage"
 #OpenSCAD 2015 doesn't add units to SVG output.
 
 #Mylar 0.10mm -
-#9495MP 0.14mm - channel
-#Mylar 0.10mm - channel
-#9495MP 0.14mm - channel
-#Mylar 0.10mm
+#9495MP 0.14mm -
+#Mylar 0.10mm -
+#9495MP 0.14mm -
+#Polycarbonate 3.175 mm
 
 thicknesses = [0.10, 0.14]
 
@@ -31,22 +33,33 @@ TEXT_SIZE = 3
 
 ID = 0
 
-IR_ENCODER_SLIT_WIDTH = 0.1
-IR_ENCODER_SLIT_LENGTH = 5
+IR_ENCODER_SLIT_WIDTH = 5
+IR_ENCODER_SLIT_LENGTH = 0.1
 
 CHANNEL_WIDTH = 0.2
 
-NUM_CUVETTES = 10
-CUVETTE_SPACING = 4.0 # between
-CUVETTE_LENGTH = 5.0
-CUVETTE_WIDTH = 0.8
+NUM_CUVETTES = 15
+CUVETTE_SPACING = 6.0 # between
+CUVETTE_LENGTH = 0.8
+CUVETTE_WIDTH = 10
+CUVETTE_THICKNESS = 0.14 + 0.1 + 0.14
 
 LEADER_HOLE_DIA = 2.0
 
-FRAME_LENGTH = ((CUVETTE_WIDTH/2.0) + CUVETTE_SPACING) * (NUM_CUVETTES) + 3.0*LEADER_HOLE_DIA + FRAME_END_MARGIN
+total_cuvette_volume = NUM_CUVETTES * CUVETTE_LENGTH * CUVETTE_WIDTH * CUVETTE_THICKNESS
+print(total_cuvette_volume * 0.001)
+
+culture_cuvette_y = 0
+CULTURE_CUVETTE_X = 0
+
+FRAME_LENGTH = ((CUVETTE_LENGTH/2.0) + CUVETTE_SPACING) * (NUM_CUVETTES) + 2*FRAME_END_MARGIN
+
[…]

### 2020-07-17 mechanical/microfluidic/keystroke.sh

@@ -1,0 +1,47 @@
+
+# #thanks https://www.linuxjournal.com/content/using-named-pipes-fifos-bash!
+# pipe=/tmp/kbrun
+#
+# trap "rm -f $pipe" EXIT
+#
+# if [[ ! -p $pipe ]]; then
+#     mkfifo $pipe
+# fi
+#
+# bind -x "\"\C-d\": echo \"\n\" > $pipe"
+#
+# while true
+# do
+#     if read line <$pipe; then
+#         if [[ "$line" == 'quit' ]]; then
+#              break
+#         fi
+#         echo "Running"
+#         python generate_slide.py
+#     fi
+# done
+
+pipe=/tmp/kbrun
+if [[ ! -p $pipe ]]; then
+    mkfifo $pipe
+fi
+xinput test-xi2 --root > /tmp/kbrun &
+
+cat /tmp/kbrun | while read line;
+do
+    if [[ "$line" == *'detail: 108'* ]]; then
+        # echo "$line";
+        echo "Running"
+        python generate_slide.py
+    fi
+done
+# while true
+# do
+#     if read </tmp/kbrun; then
+#         # if [[ "$line" == 'quit' ]]; then
+#         #      break
+#         # fi
+#         echo "Running"
+#         # python generate_slide.py
+#     fi
+# done

### 2020-07-19 documents/supplemental.tex
Inserting citations
Microfluidic
Improved FDTD sim

@@
     %% sets the pagecommand to \pagestyle{empty}
-    pagecommand={\pagestyle{headings}},  
+    pagecommand={\thispagestyle{empty}},  
     %% Add a "section" entry to the ToC with the heading
@@
 Things heating up at the Microwave Safety fandom.
+
+\clearpage
+\rule{\linewidth}{0.2pt}
+
+We do not intend to denigrate the work or otherwise cast aspersions on the authors of the mentioned papers; their experiment extremely well-designed and performed.
+
+However, since the result is unexpected, we would like to mention a few means by which the effect described could be achieved without strong non-thermal coupling.
+
+\begin{quote}
+
+ To confirm that our observation is not due to the microwave thermal heating effect, we had monitored the sample temperature change during the microwave illumination experiments with a radiated power density of 486W/m2 at a frequency of 6GHz by using an infrared thermal imaging camera with a temperature accuracy of 0.05°C (CHCT, P384-20).
+The temperature rise after 15 minutes radiation was 7°C, from 27.5°C up to 34.5°C.
+We thus exclude the possible contribution of microwave thermal heating effect to inactivation H3N2 viruses under our experimental condition.
+
+\end{quote}
+
+The frequency-dependent inactivation result in Figure 4b is difficult to explain without invoking non-thermal mechanisms. Only one  It is not mentioned how this applied power level was measured.
+
+The amplifier in question is not available on the supplier's website \cite{Microwaved} has gain flatness of 3.5 dB over 6-12 GHz - just over 1 octave.
+The amplifier used in [Hung] is not mentioned; because the frequency range mentioned (6 GHz to 18 GHz) is the same as that of the amplifier, we assume the same amplifier was used.
+
+If the amplifier happened to be matched better at 8 GHz than 12 GHz.
+
+\cite{EM6969}
+
+QPJ-06183640
+
+Similarly, the gain of the EM-6969 antenna varies from 17 dBi to 21 dBi over the frequency range in Figure 3.
+
+However, that the spectra of all these effects would combine to produce a peak at precisely the resonant frequency determined by the entirely different microwave cuvette is highly implausible; and so Figure 4b really does seem to be good evidence of such an effect.
 
@@
 
+In case you're wondering, like I was, why the voltage coefficient of capacitors
+
+\rule{\linewidth}{0.2pt}
+
 Again, inductive choke biasing in the feedback loop was practically impossible.
@@
 
+The most important feature is the consistent "down" vector; because capillary forces
+
 However, aligning seemed liable to produce artifacts; runout in the spindle;
@@
 \paragraph{Lessons Learned} \
+
+\rule{\linewidth}{0.2pt}
+
+It might be useful to watch file changes and autoreload. Practically every program in this project required the same three keystrokes to recompile; a recipe for RSI.
 

### 2020-07-19 electronics/simple_fdtd/run/microstrip.py

@@ -53,12 +53,14 @@ ribbon_dielectric_constant = 2.9
 ribbon_thickness = 1.6e-3
 ribbon_length = 10e-3
 
+cover_tape_thickness = 0.1e-3
+
 fluid_dielectric_constant = 65
-fluid_thickness = 1e-3
-fluid_width = 1e-3
+fluid_thickness = (0.14+0.1+0.14) * 1e-3
+fluid_width = 0.8e-3
 
 pcb = fd.PCB(0.00005, xy_margin=15, z_margin=15)
-fd.initialize_grid(pcb,int((5e-3)/pcb.cell_size),int((microstrip_length)/pcb.cell_size),
+fd.initialize_grid(pcb,int((10e-3)/pcb.cell_size),int((microstrip_length)/pcb.cell_size),
                                 int(0.0025/pcb.cell_size), courant_number = 0.4)
 
 fd.create_planes(pcb, 0.032e-3, 6e7)
@@ -75,22 +77,36 @@ centerline = int((5e-3 / pcb.cell_size ) / 2.0) + pcb.xy_margin
 pcb.copper_mask[:, :, z_slice] = 0
 pcb.copper_mask[:,:,pcb.ground_plane_z_top:pcb.component_plane_z] = 0 # vias
 
+microstrip_gap = 3e-3 # distance to ground plane
 #microstrip line
 m_w_N = int((microstrip_width/2)/pcb.cell_size)
 pcb.copper_mask[centerline-m_w_N:centerline+m_w_N, \
                     pcb.xy_margin:int(pcb.xy_margin+(int(microstrip_length/pcb.cell_size))), z_slice] = 1
+# pcb.copper_mask[pcb.xy_margin:centerline-m_w_N-int(microstrip_gap/pcb.cell_size), \
+#                     pcb.xy_margin:int(pcb.xy_margin+(int(microstrip_length/pcb.cell_size))), z_slice] = 1
+pcb.copper_mask[centerline+m_w_N+int(microstrip_gap/pcb.cell_size):-pcb.xy_margin, \
+                    pcb.xy_margin:int(pcb.xy_margin+(int(microstrip_length/pcb.cell_size))), z_slice] = 1
+
+
+#cover tape
+pcb.grid[pcb.xy_margin:-pcb.xy_margin, pcb.xy_margin:-pcb.xy_margin, \
[…]

### 2020-07-19 firmware/eppenwolf/host/run.py

@@ -1,15 +1,46 @@
 import device_comms
 import sweep
 
+# Phage+Bacteria / Bacteria-only / phage only?
+# expose (parameters) / sham / thermal positives
+
+# For each of the animal and human published studies, four
+# predetermined and specific quality control measures were used to
+# assess the quality of the publication.
+# 1. Whether or not the researchers have used ‘‘blind’’ evaluations to
+# avoid individual ‘‘bias’’, B or nB;
+# 2. Whether or not there was detailed/adequate description of
+# ‘‘dosimetry’’ in the publication for independent replication/
+# confirmation studies, D or nD.
+# 3. Whether or not ‘‘positive controls’’ were included in the
+# experiment(s) to replicate/confirm the observations, P or nP.
+# 4. Whether or not ‘‘sham-exposed controls’’ (more appropriate to
+# compare with the observations made in RF exposure conditions)
+# were included in the experiments, S or nS. However, it was not our
+# intention to ‘‘rank’’ the publications either to exclude or include
+# the reported data in the meta-analysis.
 
 def initialize():
-
-    Name this run
-    Fluidic plate ID
+    # Name this run
+    # Fluidic plate ID
 
 
     print("Fill phage into all selected cuvettes.")
     Simulataneously and separately
+
+
+def bacteria_alone_control():
+    //repeated twice
+
+    # fill_phage()
+
+
+def bacteria_and_phage_control():
+    //repeated twice
+
+
+def bacteria_and_inactivated_phage_positive_control():
+    //
 
 
 
@@ -29,7 +60,7 @@ RF
 
 Expose phage, mix with log bacteria, monitor.
 
-Bare 
+Bare
 
 Sham
 

### 2020-07-21 documents/paper.tex
Microfluidic
Improved FDTD sim
Yaaaaaaay microfluidics

@@
 \begin{document}
-
-\nocite{*}
 
@@
 %
-\cite{Longrange1968} \textrightarrow \ \cite{Biological1980} \textrightarrow \ [Liu 2009] \textrightarrow \ ([Hung 2014] $\parallel$ [Yang 2015] $\parallel$ [Sun 2017])\footnote{We have not conducted a thorough review; many more papers are probably involved.} apparently culminates in the flagship work we focus on in this paper,
+\cite{Longrange1968} \textrightarrow \ \cite{Biological1980} \textrightarrow \ \cite{Microwave2009} \textrightarrow \ (\cite{focusing2014} $\parallel$ \cite{Efficient2015} $\parallel$ \cite{Resonant2017})\footnote{We have not conducted a thorough review; many more papers are probably involved.} apparently culminates in the flagship work we focus on in this paper,
 
-{\it Efficient Structure Resonance Energy Transfer from Microwaves to Confined Acoustic Vibrations in Viruses} [Yang 2015].
+{\it Efficient Structure Resonance Energy Transfer from Microwaves to Confined Acoustic Vibrations in Viruses} \cite{Efficient2015}.
 %
@@
 
-\lettrine{It} cannot be overstated how unexpected and positively dubious this finding appears to be -at least, based on our limited research and experience to date.
+\lettrine{It} cannot be overstated how unexpected and positively dubious this finding appears to be - that is, based on our limited research and inexperience to date.
 
-For even the RF power limits set by standards organizations appear to be based on the observation that no significant resonance modes exist in biological tissues, and (as we shall see), this is grounded in solid {\it in vitro} (albeit more limited {\it in vivo}) evidence.
+For even the RF power limits set by standards organizations like \cite{ICNIRP2020} \cite{IEEE2006} appear to be based on the observation that no significant resonance modes exist in biological tissues due to damping forces from the surrounding tissue \cite{Vibrational2002}.
+As we shall see, this is grounded in solid {\it in vitro} (albeit more limited {\it in vivo}) evidence.
 
@@
 
-The precise structure and charge of the virion appears to be a singular anomaly in this otherwise catagorical non-existence.
+The precise structure and charge of the virion appears to be a singular anomaly in this otherwise categorical non-existence.
 
@@
 
-\footnote{All values have been converted to $\text{W/m}^2$ to avoid confusion. 100 $\text{ W/m}^2 = 10 \text{ mW/cm}^2 = 10 \text{ dBm/cm}^2$.}
+\footnote{All values have been converted to $\text{W/m}^2$ to avoid confusion. 100 $\text{W/m}^2 = 10 \text{ mW/cm}^2 = 10 \text{ dBm/cm}^2$.}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{table} 
+	\centering
+	\begin{threeparttable}
+		\caption{Safety limits from various standards}
+		\begin{tabular}{lllll}
+			\toprule
+			Stubhead & \( df \) & \( f \) & \( \Wsqm \) & \( p \) \\
+			\midrule
+			&     \multicolumn{4}{c}{Spanning text}     \\
+			Row 1    & 1        & 0.67    & 0.55       & 0.41    \\
+			Row 2    & 2        & 0.02    & 0.01       & 0.39    \\
+			Row 3    & 3        & 0.15    & 0.33       & 0.34    \\
+			Row 4    & 4        & 1.00    & 0.76       & 0.54    \\
+			\bottomrule
+		\end{tabular}
+		\begin{tablenotes}
+			\small
+			\item This is where authors provide additional information about
+			the data, including whatever notes are needed.
+		\end{tablenotes}
+	\end{threeparttable}
+\end{table}
+
+All pertinent restrictions for frequency $<$ 6 GHz, for general public.
+ICNIRP 2020, Table 2, "Basic restrictions for electromagnetic field exposure",
+20 \Wsqm, averaged over a 6 min period, averaged over a square $4 \text{cm}^2$ surface area of the body.
+
+Whole-body average SAR $<$ 0.08 W/kg
+
+And, additionally,
+
+ICNIRP 2020, Table 3, Basic Restrictions
+
+\clearpage
 
@@
 
+Note that contrary to the limits at lower frequencies, neither ICNIRP nor IEEE appear to explicitly specify a maximum electric field; only the maximum power is specified (thereby implicitly restricting the electric field magnitude).
+
 The safety standards of [IEEE] and [ICNIRP] account for such time-domain modulation by specifying both an average power limit over a 6 minute period, and a time-integrated energy deposition limit.
@@
 
-To drive home this point, apparently the best-quality evidence available fulfills sham requirements [Vijayalaxmi 2006] provide in-vitro.
+To drive home this point, apparently the best-quality evidence available fulfills sham requirements provide in-vitro.
 They expose blood lymphocytes to pulse power in precisely the regime required in this work; 8.2 GHz, 8 ns duration and 50 khz repetition rate, a whopping pulse power density of 250,000 $\text{W/m}^2$\footnote{computed from average power / duty cycle} (2500x the time-averaged power density safety limit), average power density 100 $\text{W/m}^2$ (the safety limit), for 2 hours, finding no change in any of the measured quantities.
 
-Simlarly, [Chemeris 2004] use 8.8 GHz, 180 ns pulse width, peak power 65,000 W, repetition rate 50 Hz, exposure duration 40 min, on frog etheyrocytes, and find genotoxicity only from the temperature rise.
+Similarly, [Chemeris 2004] use 8.8 GHz, 180 ns pulse width, peak power 65,000 W, repetition rate 50 Hz, exposure duration 40 min, and find genotoxicity purely due to the temperature rise.
 
@@
 We are not aware of any past uses of these microwave en-masse. We do not have the
+
+Moreover, 
+\begin{quote}
+
+In the absence of publication bias, since the sampling error is random, all studies will be distributed symmetrically around the mean d value.
+
+\end{quote}
 
@@
 \clearpage
+{\Large \it The plausibility of low-cost microwave masks}\\
+
+With the most recent few generations of semiconductor processes, producing significant powers in the X-band has become inexpensive.
+Silicon transistors are limited in their output power and gain; Silicon-on-insulator topologies
+
+This is perhaps most readily illustrated with the HB100 radar module.
+This device implements a complete doppler radar with two RF MOSFETS and a dielectric resonator.
+It operates at 10.6 GHz, yet are produced for under \$3.
+The PCB is stock FR4.
+
+Our crude experimentation has yielded about 10 mW with a single SiGe:C transistor, the Infineon BFP620 (\$ 0.34 apiece \@ 1000-of.).
+For the personal microwave sterilizer, given the threshold levels found by Yang, this corresponds to a cost per sterilized cubic centimeter of approx.
+\cite{BFP620H7764XTSA1}.
+
+\clearpage
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+The mechanism restricts the possible modes of application; it would be useful to
+
 \paragraph{\textbf{Personal 'electromagnetic mask'}}\
@@
 
-SARS is found widely distributed throughout many of the most favoured organs [Ding 2004], shielded by an average of 4 cm of chest wall [Schroeder 2013]; so safe external treatment of the body is unlikely.
+SARS is found widely distributed throughout many of the most favoured organs \cite{Organ2004}, shielded by an average of 4 cm of chest wall [Schroeder 2013]; so safe external treatment of the body is unlikely.
 
@@
 The main bronchus is about 8 mm in diameter, which is smaller than the patch antenna used here; a monopole (or multiple, phased monopoles) like is probably more suitable.
+
+{\color{red} speculation \{ }
 
@@
 
-\paragraph{}
+\end{multicols}
 
-It has been shown that virions can effect large-scale changes in the electric charges of their [].
-
-Use of this technique will provide a selection bias towards immunity to electromagnetic fields, which could perhaps be effected by preferring extreme-sized mutants (shifting the resonance away from the applied field).
-
-We do not have the biological knowledge to know if this is plausible; it simply seemed worth mentioning.
-
-\end{multicols}
+{\color{red} speculation \} }
 
@@
 
+\clearpage
+\paragraph{}
+
+It has been shown that virions can effect large-scale changes in the electric charges of their [].
+
+Use of this technique will provide a selection bias towards immunity to electromagnetic fields, which could perhaps be effected by preferring extreme-sized mutants (shifting the resonance away from the applied field).
+
+We do not have the biological knowledge to know if this is plausible; it simply seemed worth mentioning.
+
 \subfile{acknowledgement}
@@
 
+\nocite{*}
+
 %\printbibliography[ title={Other references}]

### 2020-07-21 documents/supplemental.tex
Yaaaaaaay microfluidics

@@
 
-There seems to be a discrepancy between [Yang 2015] and our reading of [C95.1-2005].
+There seems to be a discrepancy between \cite{Efficient2015} and our reading of [C95.1-2005].
 
-They use a threshold in open public space of $100(f/3)^{1/5} \text{ W/m}^2$. The 115 W @ 6 GHz they provide correctly corresponds to this equation with a coefficient of 100.
+They use a threshold in open public space of $100(f/3)^{1/5} \text{ W/m}^2$. The 115 W @ 6 GHz figure they provide corresponds to this equation with a coefficient of 100.
 
@@
 \PRLsep{{\itshape Wherein an oscillator is designed }}
+
+We did not discover how little of an effect a wideband sweep would have until late in the project; for this reason, much of the below caters towards wideband circuits and could be greatly simplified for single-frequency operation.
 
@@
 
-\PRLsep{{\itshape Power sensing }}
+\printbibliography[heading=none, title={}, keyword={amplifier}]
 
@@
 The Mini-Circuits ZX47-40-S+ would be an excellent low-cost COTS alternative.
+
+\printbibliography[heading=none, title={}, keyword={rectifier}]
 

### 2020-07-21 mechanical/microfluidic/generate_slide.py

@@ -19,7 +19,7 @@ thicknesses = [0.10, 0.14]
 FRAME_WIDTH = 50.0
 FRAME_THICKNESS = 3.175
 FRAME_X_MARGIN = 8.0
-FRAME_END_MARGIN = FRAME_WIDTH / 3
+FRAME_END_MARGIN = FRAME_WIDTH / 2
 CENTERLINE = FRAME_WIDTH / 2.0
 
 WINDOW_WIDTH = 20.0
@@ -39,7 +39,7 @@ IR_ENCODER_SLIT_LENGTH = 0.1
 CHANNEL_WIDTH = 0.3
 
 NUM_CUVETTES = 2**4
-CUVETTE_SPACING = 4.0 # center-to-center
+CUVETTE_SPACING = 5 # center-to-center
 CUVETTE_LENGTH = 0.8
 CUVETTE_WIDTH = 10
 CUVETTE_THICKNESS = 0.14 + 0.1 + 0.14
@@ -56,10 +56,9 @@ culture_cuvette_y = total_cuvette_volume / CUVETTE_THICKNESS / CULTURE_CUVETTE_X
 FRAME_LENGTH = ((CUVETTE_LENGTH/2.0) + CUVETTE_SPACING) * (NUM_CUVETTES) + 2*FRAME_END_MARGIN
 
 print(FRAME_WIDTH, FRAME_LENGTH)
-print(NUM_CUVETTES*CUVETTE_SPACING + culture_cuvette_y)
+print((NUM_CUVETTES-1)*CUVETTE_SPACING + culture_cuvette_y)
 
 window_length = CUVETTE_SPACING / 1.5
-
 
 
 layer_0 = square([FRAME_WIDTH, FRAME_LENGTH],center=False)
@@ -124,15 +123,17 @@ for i in range(0, NUM_CUVETTES):
     # frame -= translate([CENTERLINE+WINDOW_WIDTH/2 + CUVETTE_WIDTH/1.5 + O_RING_OD, cuvette_y_centerline+CUVETTE_LENGTH*3])(\
     #             cylinder(d=O_RING_OD, h=O_RING_THICKNESS, center=False))
 
-    port_1 = translate([CENTERLINE+WINDOW_WIDTH/2 + O_RING_OD*1.5, cuvette_y_centerline])(
+    # port_x = CENTERLINE+WINDOW_WIDTH/2 + 1 + O_RING_OD*1.5+(i%2)
[…]

### 2020-07-22 documents/acknowledgement.tex
Protobuf
paper or whatever

@@
 
+This paper would have been absolutely impossible without the support of hundreds of open-source software packages, ranging from monolithic industry-supported tools like Paraview and Chimera to poorly-compensated but equally invaluable scripts like zonca.
+Thank you to all the dedicated authors that develop and maintain these tools.
+
 Professor Shahramian's excellent video blog {\it The Signal Path} inspired this work.
 
-Dr. Dainis' videos on microbiological technique were also useful.
+Dr. Dainis' videos on microbiological technique were also useful. The Thought Emporium's videos on PCB prototyping and
 
-Thanks to the professors at York and beyond for returning my emails.
+Thanks to all the professors at York and beyond for returning my emails and checking their biofridges.
 
-Thanks to L.H. for wisdom regarding this project.
+Thanks to L.H. for wisdom regarding this project; P.B and H.P. and ice9 for tolerating midnight ramblings and M.Q. for the hug.
 
-Thanks to P.B and H.P. for tolerating ramblings and M. for the hug.
-
-Special thanks to all the people - most equally capable of writing this paper if provided the opportunity - who work menial shifts at the component suppliers that remained open that were so critical.
+Special thanks to all the people - all equally capable of writing this paper if provided the opportunity - who circumstance led to work menial shifts at the component suppliers that remained open that were so critical.
 Hopfstader be damned; despite the name below the abstract, this paper is of course entirely the result of circumstance and luck.
@@
 
+\rule{\linewidth}{0.2pt}
+
+The authors acknowledge the Computational Electromagnetics Group at The University of Texas at Austin for developing and making the AustinMan and AustinWoman human body models available at https://sites.utexas.edu/austinmanaustinwomanmodels/.
+
+\rule{\linewidth}{0.2pt}
+
 One Very Important Thought
+
+{\Large <3}

### 2020-07-22 documents/biology.tex
paper or whatever

% Default to the notebook output style

% Inherit from the specified cell style.

\documentclass[11pt]{article}

    \usepackage[T1]{fontenc}
    % Nicer default font (+ math font) than Computer Modern for most use cases
    \usepackage{mathpazo}

    % Basic figure setup, for now with no caption control since it's done
    % automatically by Pandoc (which extracts ![](path) syntax from Markdown).
    \usepackage{graphicx}
    % We will generate all images so they have a width \maxwidth. This means
    % that they will get their normal width if they fit onto the page, but
    % are scaled down if they would overflow the margins.
    \makeatletter
    \def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth
    \else\Gin@nat@width\fi}
    \makeatother
    \let\Oldincludegraphics\includegraphics
    % Set max figure width to be 80% of text width, for now hardcoded.
    \renewcommand{\includegraphics}[1]{\Oldincludegraphics[width=.8\maxwidth]{#1}}
    % Ensure that by default, figures have no caption (until we provide a
    % proper Figure object with a Caption API and a way to capture that
    % in the conversion process - todo).
    \usepackage{caption}
    \DeclareCaptionLabelFormat{nolabel}{}
    \captionsetup{labelformat=nolabel}

    \usepackage{adjustbox} % Used to constrain images to a maximum size 
    \usepackage{xcolor} % Allow colors to be defined
    \usepackage{enumerate} % Needed for markdown enumerations to work
    \usepackage{geometry} % Used to adjust the document margins
    \usepackage{amsmath} % Equations
    \usepackage{amssymb} % Equations
    \usepackage{textcomp} % defines textquotesingle
    % Hack from http://tex.stackexchange.com/a/47451/13684:
    \AtBeginDocument{%
        \def\PYZsq{\textquotesingle}% Upright quotes in Pygmentized code
    }
    \usepackage{upquote} % Upright quotes for verbatim code
    \usepackage{eurosym} % defines \euro
    \usepackage[mathletters]{ucs} % Extended unicode (utf-8) support
    \usepackage[utf8x]{inputenc} % Allow utf-8 characters in the tex document
    \usepackage{fancyvrb} % verbatim replacement that allows latex
    \usepackage{grffile} % extends the file name processing of package graphics 
                         % to support a larger range 
    % The hyperref package gives us a pdf with properly built
    % internal navigation ('pdf bookmarks' for the table of contents,
    % internal cross-reference links, web links for URLs, etc.)
    \usepackage{hyperref}
    \usepackage{longtable} % longtable support required by pandoc >1.10
    \usepackage{booktabs}  % table support for pandoc > 1.12.2
    \usepackage[inline]{enumitem} % IRkernel/repr support (it uses the enumerate* environment)
    \usepackage[normalem]{ulem} % ulem is needed to support strikethroughs (\sout)
                                % normalem makes italics be italics, not underlines
    \usepackage{mathrsfs}

    % Colors for the hyperref package
    \definecolor{urlcolor}{rgb}{0,.145,.698}
    \definecolor{linkcolor}{rgb}{.71,0.21,0.01}
    \definecolor{citecolor}{rgb}{.12,.54,.11}

    % ANSI colors
    \definecolor{ansi-black}{HTML}{3E424D}
    \definecolor{ansi-black-intense}{HTML}{282C36}
    \definecolor{ansi-red}{HTML}{E75C58}
    \definecolor{ansi-red-intense}{HTML}{B22B31}
    \definecolor{ansi-green}{HTML}{00A250}
    \definecolor{ansi-green-intense}{HTML}{007427}
    \definecolor{ansi-yellow}{HTML}{DDB62B}
    \definecolor{ansi-yellow-intense}{HTML}{B27D12}
    \definecolor{ansi-blue}{HTML}{208FFB}
    \definecolor{ansi-blue-intense}{HTML}{0065CA}
    \definecolor{ansi-magenta}{HTML}{D160C4}
    \definecolor{ansi-magenta-intense}{HTML}{A03196}
    \definecolor{ansi-cyan}{HTML}{60C6C8}
    \definecolor{ansi-cyan-intense}{HTML}{258F8F}
    \definecolor{ansi-white}{HTML}{C5C1B4}
    \definecolor{ansi-white-intense}{HTML}{A1A6B2}
    \definecolor{ansi-default-inverse-fg}{HTML}{FFFFFF}
    \definecolor{ansi-default-inverse-bg}{HTML}{000000}

    % commands and environments needed by pandoc snippets
    % extracted from the output of `pandoc -s`
    \providecommand{\tightlist}{%
      \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
    \DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
    % Add ',fontsize=\small' for more characters per line
    \newenvironment{Shaded}{}{}
    \newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{{#1}}}}
    \newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.56,0.13,0.00}{{#1}}}
    \newcommand{\DecValTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
    \newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
    \newcommand{\FloatTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
    \newcommand{\CharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
    \newcommand{\StringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
    \newcommand{\CommentTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textit{{#1}}}}
    \newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{{#1}}}
    \newcommand{\AlertTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{{#1}}}}
    \newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.02,0.16,0.49}{{#1}}}
    \newcommand{\RegionMarkerTok}[1]{{#1}}
    \newcommand{\ErrorTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{{#1}}}}
    \newcommand{\NormalTok}[1]{{#1}}

    % Additional commands for more recent versions of Pandoc
    \newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.53,0.00,0.00}{{#1}}}
    \newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
    \newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
    \newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.73,0.40,0.53}{{#1}}}
    \newcommand{\ImportTok}[1]{{#1}}
    \newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.73,0.13,0.13}{\textit{{#1}}}}
    \newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{{#1}}}}}
    \newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{{#1}}}}}
    \newcommand{\VariableTok}[1]{\textcolor[rgb]{0.10,0.09,0.49}{{#1}}}
    \newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{{#1}}}}
    \newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.40,0.40,0.40}{{#1}}}
    \newcommand{\BuiltInTok}[1]{{#1}}
    \newcommand{\ExtensionTok}[1]{{#1}}
    \newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.74,0.48,0.00}{{#1}}}
    \newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.49,0.56,0.16}{{#1}}}
    \newcommand{\InformationTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{{#1}}}}}
    \newcommand{\WarningTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{{#1}}}}}

    % Define a nice break command that doesn't care if a line doesn't already
    % exist.
    \def\br{\hspace*{\fill} \\* }
    % Math Jax compatibility definitions
    \def\gt{>}
    \def\lt{<}
    \let\Oldtex\TeX
    \let\Oldlatex\LaTeX
    \renewcommand{\TeX}{\textrm{\Oldtex}}
    \renewcommand{\LaTeX}{\textrm{\Oldlatex}}
    % Document parameters
    % Document title
    \title{biology}

    % Pygments definitions

\makeatletter
\def\PY@reset{\let\PY@it=\relax \let\PY@bf=\relax%
    \let\PY@ul=\relax \let\PY@tc=\relax%
    \let\PY@bc=\relax \let\PY@ff=\relax}
\def\PY@tok#1{\csname PY@tok@#1\endcsname}
\def\PY@toks#1+{\ifx\relax#1\empty\else%
    \PY@tok{#1}\expandafter\PY@toks\fi}
\def\PY@do#1{\PY@bc{\PY@tc{\PY@ul{%
    \PY@it{\PY@bf{\PY@ff{#1}}}}}}}
\def\PY#1#2{\PY@reset\PY@toks#1+\relax+\PY@do{#2}}

\expandafter\def\csname PY@tok@gd\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.63,0.00,0.00}{##1}}}
\expandafter\def\csname PY@tok@gu\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.50,0.00,0.50}{##1}}}
\expandafter\def\csname PY@tok@gt\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.27,0.87}{##1}}}
\expandafter\def\csname PY@tok@gs\endcsname{\let\PY@bf=\textbf}
\expandafter\def\csname PY@tok@gr\endcsname{\def\PY@tc##1{\textcolor[rgb]{1.00,0.00,0.00}{##1}}}
\expandafter\def\csname PY@tok@cm\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@vg\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@vi\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@vm\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@mh\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@cs\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@ge\endcsname{\let\PY@it=\textit}
\expandafter\def\csname PY@tok@vc\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@il\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@go\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.53,0.53,0.53}{##1}}}
\expandafter\def\csname PY@tok@cp\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.74,0.48,0.00}{##1}}}
\expandafter\def\csname PY@tok@gi\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.63,0.00}{##1}}}
\expandafter\def\csname PY@tok@gh\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,0.50}{##1}}}
\expandafter\def\csname PY@tok@ni\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.60,0.60,0.60}{##1}}}
\expandafter\def\csname PY@tok@nl\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.63,0.63,0.00}{##1}}}
\expandafter\def\csname PY@tok@nn\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\expandafter\def\csname PY@tok@no\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.53,0.00,0.00}{##1}}}
\expandafter\def\csname PY@tok@na\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.49,0.56,0.16}{##1}}}
\expandafter\def\csname PY@tok@nb\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@nc\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\expandafter\def\csname PY@tok@nd\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.67,0.13,1.00}{##1}}}
\expandafter\def\csname PY@tok@ne\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.82,0.25,0.23}{##1}}}
\expandafter\def\csname PY@tok@nf\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\expandafter\def\csname PY@tok@si\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.73,0.40,0.53}{##1}}}
\expandafter\def\csname PY@tok@s2\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@nt\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@nv\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@s1\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@dl\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@ch\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@m\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@gp\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,0.50}{##1}}}
\expandafter\def\csname PY@tok@sh\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@ow\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.67,0.13,1.00}{##1}}}
\expandafter\def\csname PY@tok@sx\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@bp\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@c1\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@fm\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\expandafter\def\csname PY@tok@o\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@kc\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@c\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@mf\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@err\endcsname{\def\PY@bc##1{\setlength{\fboxsep}{0pt}\fcolorbox[rgb]{1.00,0.00,0.00}{1,1,1}{\strut ##1}}}
\expandafter\def\csname PY@tok@mb\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@ss\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@sr\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.40,0.53}{##1}}}
\expandafter\def\csname PY@tok@mo\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@kd\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@mi\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@kn\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@cpf\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@kr\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@s\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@kp\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@w\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.73,0.73}{##1}}}
\expandafter\def\csname PY@tok@kt\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.69,0.00,0.25}{##1}}}
\expandafter\def\csname PY@tok@sc\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@sb\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@sa\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@k\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@se\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.73,0.40,0.13}{##1}}}
\expandafter\def\csname PY@tok@sd\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}

\def\PYZbs{\char`\\}
\def\PYZus{\char`\_}
\def\PYZob{\char`\{}
\def\PYZcb{\char`\}}
\def\PYZca{\char`\^}
\def\PYZam{\char`\&}
\def\PYZlt{\char`\<}
\def\PYZgt{\char`\>}
\def\PYZsh{\char`\#}
\def\PYZpc{\char`\%}
\def\PYZdl{\char`\$}
\def\PYZhy{\char`\-}
\def\PYZsq{\char`\'}
\def\PYZdq{\char`\"}
\def\PYZti{\char`\~}
% for compatibility with earlier versions
\def\PYZat{@}
\def\PYZlb{[}
\def\PYZrb{]}
\makeatother

    % Exact colors from NB
    \definecolor{incolor}{rgb}{0.0, 0.0, 0.5}
    \definecolor{outcolor}{rgb}{0.545, 0.0, 0.0}

    % Prevent overflowing lines due to hard-to-break entities
    \sloppy 
    % Setup hyperref package
    \hypersetup{
      breaklinks=true,  % so long urls are correctly broken across lines
      colorlinks=true,
      urlcolor=urlcolor,
      linkcolor=linkcolor,
      citecolor=citecolor,
      }
    % Slightly bigger margins than the latex defaults

    \geometry{verbose,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}

    \begin{document}

    \maketitle

19.84851961247638

    We know the variation in the diameter and therefore that in the volume.
There is, surprisingly, almost no variation in the total spike mass, so
we subtract that first. We would expect \(\sigma = 19.8\) MDa variation
if volume and mass were proportional, and see \(\sigma = 17\) MDa of
variation.

We therefore assume that mass and volume are proportional.

    \hypertarget{fitting-breaking-force-with-gaussian---doesnt-work-particularly-well}{%
\subsubsection{Fitting breaking force with gaussian - doesn't work
particularly
well}\label{fitting-breaking-force-with-gaussian---doesnt-work-particularly-well}}

    \begin{Verbatim}[commandchars=\\\{\}]
Liposome breaking force mean=0.839 sigma=0.733 pN

    \end{Verbatim}

    Now we run into a problem. We don't know the dependence of k, the spring
constant, on any of the parameters in an actual virus. It is determined
by the strength of the intermolecular forces and is a free parameter.

From {[}Li 2011{]}, Figure 3a we see that the empty liposome stiffness
is negatively correlated with size; but the stiffness of the empty
liposome appears to be hundreds of times smaller than that of the full
virion.

From running ensembles with different values of k\_sigma, while the
distribution of the resonant frequencies is very sensitive to this
parameter, the inactivation threshold is not; so we guess a resonable
figure.

Figure 4b in Yang is dependent on k vs f\_res, and the overall
absorption cross-section data in Figure 3b includes the sum of all the
absorption cross-sections of all the variance. It is likely possible to
extract the remaining data from these plots; but, since none of this is
applicable to SARS-NCoV, this exceeds our patience.

    The liposome breaking force is distributed in an obstinately
non-gaussian bimodal manner, so we override the covariance matrix and
introduce a gaussian KDE sampled from the force histogram in {[}Li
2011{]}.

0.9365113296280462

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{biology_files/biology_17_1.png}
    \end{center}
    { \hspace*{\fill} \\}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{biology_files/biology_17_2.png}
    \end{center}
    { \hspace*{\fill} \\}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{biology_files/biology_17_3.png}
    \end{center}
    { \hspace*{\fill} \\}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{biology_files/biology_17_4.png}
    \end{center}
    { \hspace*{\fill} \\}

    \begin{figure}
\centering
\includegraphics{attachment:Screenshot\%20from\%202020-06-29\%2013-11-21.png}
\caption{Screenshot\%20from\%202020-06-29\%2013-11-21.png}
\end{figure}

    We very simply extend {[}Yang 2015{]}'s analysis to include the
distribution of viral particles.

We have to continue using Inf. A rather than the target SARS-NCoV-2
because of an apparent lack of AFM nanoindentation data. While both
virions have a lipid bilayer

\begin{verbatim}
The majority of virions (n = 78) may be described as spherical (axial ratio 1.2), the remainder are oval or   kidney-shaped with axial ratios up to 1.4 (n = 17) or more elongated with axial ratios as high as 7.7 (n = 15). The outer diameters of the spherical virions ranged from 84 to 170 nm (mean, 120 nm).
\end{verbatim}

Note that, per {[}Lauffer 1944{]}, of Inf A and B, ``the infectious
particles have diameters within the range 80 to 135{[}nm{]}''.

{[}Yang 2015{]}'s MDCK plaque assay is already sensitive to infectivity;
the extreme-sized non-infective mutants would already be filtered out.
Their PCR assay might not be; the DNA of all non-infectious mutants
would be considered.

{[}Yang 2015{]} use a minimum force of 400 pN, though their reference,
{[}Li 2011{]}, mention that

\begin{quote}
More than 95\% puncture events occurred above 0.4 nN.
\end{quote}

This probably accounts for the high 100\% threshold.

The distribution of breaking strengths in {[}Li 2011{]} (Figure 5b) is
bimodal, and a naive gaussian fit does not produce the above 95\%
figure. Rather than implement a unimodal+bimodal covariant sampling
function, we tweaked the gaussian parameters to accordingly. We hope
that the deities of statistical best practice are not displeased.

The mass, diameter, and breaking force are presumably not independently
distributed. The correlations between the three variables do not seem to
be documented in the literature.

{[}Li 2011{]}, the AFM data is from {[}H1N1{]} rather than the H3N1 or
H5N1.

We therefore need the CoV for NCoV.

There seems to be little variation in the mass of the spike proteins;
intact H3N1 is 161 MDa +/- 17, with spikes removed, 75 MDa +/- 17.
{[}Ruigrok 1984{]}

Influenza is found in two different morphologies; the one found in the
lab is almost entirely the spherical variant, whereas filamentous
variant is often associated with infections in humans. Because it is
rare in the lab, this is not part of the cause of {[}Yang 2015{]}'s
discrepancy; and NCoV does not seem to exhibit such pleomorphic
tendencies.

The average stiffness of the liposome varies approximately linearly from
0.025 to 0.015 from 80 to 135 nm {[}Li 2011{]}, plus a random
distribution with approx. 0.0025 sigma.

Size and weight are assumed to be uncorrelated with breaking strength.

From {[}Yang 2015{]}, eq. 7,

\[A = \frac{q E_0}{\mu \sqrt{((2 \pi f_{res})^2 - (2 \pi f_{excite})^2)^2 + \left(\frac{(2 \pi f_{res})(2 \pi f_{excite})}{Q}\right)^2}}\]

The resonant frequency varies as \(\sqrt{k/m^*}\).

Assuming (as Yang et al do) that the core and shell have 90\% and 10\%
of the mass,

Text(0, 0.5, 'Count')

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{biology_files/biology_23_1.png}
    \end{center}
    { \hspace*{\fill} \\}

    A surprising source the sadists that drag cracked virions through
acrylamide gel and then irradiate them for sport.

Two dimensional gel electrophoresis resolves both the mass and the
isoelectric point (where the net charge and that of the solution are in
equilibrium) of large structures. {[}Privalsky 1978{]} provides us a
coarse. view of the charges and relative abundances in the virus.

'NP has MW 60000 Da'

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{biology_files/biology_25_1.png}
    \end{center}
    { \hspace*{\fill} \\}

    There's substantial hetrogeneity in the charge of the proteins with the
exception of the nucleocapsid protein NP. The M proteins have run off
the basic end. The followup work {[}Privalsky 1980{]} indeed finds the M
protein to be very basic. {[}Shtykova 2017{]} discusses the charge on
the M1 matrix protein.

confusingly, there are two different M proteins, sometimes called ``M''
and sometimes called ``M1''.

{[}Bosch 1984{]} discusses the charge hetrogenetity a bit, but not quite
relevant.

    \begin{figure}
\centering
\includegraphics{attachment:influenza-virion3.jpg}
\caption{influenza-virion3.jpg}
\end{figure}

From https://www.virology.ws/2009/04/30/structure-of-influenza-virus/,
CC-BY-3.0

    \begin{figure}
\centering
\includegraphics{attachment:512px-Coronavirus_virion_structure.svg.png}
\caption{512px-Coronavirus\_virion\_structure.svg.png}
\end{figure}

https://commons.wikimedia.org/wiki/File:Coronavirus\_virion\_structure.svg

    \begin{Verbatim}[commandchars=\\\{\}]
6th percentile: 107.719688
25th percentile: 183.150245
38th percentile: 225.606554
50th percentile: 272.826748
63th percentile: 329.726187
75th percentile: 394.636478
90th percentile: 528.376490
99.9th percentile: 901.585217

    \end{Verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{biology_files/biology_34_1.png}
    \end{center}
    { \hspace*{\fill} \\}

    \begin{Verbatim}[commandchars=\\\{\}]
7352272865.997211
8742438606.009031
7918698482.136088
8790540253.025091
7569244106.744585
7616236368.820197
7130634958.911914
8643593632.808327
7668512698.503477
7346623231.698657

    \end{Verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{biology_files/biology_35_1.png}
    \end{center}
    { \hspace*{\fill} \\}

    The resonant frequency does not necessarily correspond to the optimal
excitation frequency. The positive critical point of (12) is

\[w = \frac{\sqrt{2 Q^2 - 1} f_{res}}{\sqrt{2} \ Q}\]

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{biology_files/biology_37_0.png}
    \end{center}
    { \hspace*{\fill} \\}

    \begin{Verbatim}[commandchars=\\\{\}]
Given a frequency sweep in which each virion is excited with its frequency of maximum power dissipation,
The following threshold percentiles would be expected:
6th percentile: 105.377077
25th percentile: 175.031733
38th percentile: 215.079976
50th percentile: 260.006088
63th percentile: 310.672577
75th percentile: 370.657720
90th percentile: 478.860319
99.9th percentile: 761.727525
6th percentile: 0.094006
25th percentile: 2.047698
38th percentile: 5.012599
50th percentile: 9.642929
63th percentile: 17.456217
75th percentile: 28.894219
90th percentile: 55.508068
99.9th percentile: 180.533090

    \end{Verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{biology_files/biology_39_1.png}
    \end{center}
    { \hspace*{\fill} \\}

    % Add a bibliography block to the postdoc

    \end{document}

### 2020-07-22 documents/paper.tex
paper or whatever

@@
 \begin{document}
+
+We've got a thing 
+that's called 
+Radar Love
+We've got a wave
+in the air
+
+The phased-array techdemo.
 
@@
 \begin{multicols}{1}
-
-We've got a thing 
-that's called 
-Radar Love
-We've got a wave
-in the air
-
-The phased-array techdemo.
 
@@
 
-This may account for why this paper has been ignored.
+This may account for why this paper has been largely ignored.
 
@@
 \clearpage
+{\Large \it The contenders}\\
+
+Protein net charges extracted from protein sequences compiled by the proteome-pI database \cite{ProteomepI2017} and UniProt using localCIDER \cite{CIDER2017} \ghfile{biology/data/net_charge.py}.
+
+\clearpage
 
@@
 Unfortunately, the buried lede is that the power levels shown by [Yang 2015] are about twice the continuous safety levels.
+
+\paragraph{Time-domain modulation}
 
@@
 \clearpage
+{\Large \it Time-dependence}\\
+
+The fact that the viral inactivation is non-thermal
+
+Both [Yang 2015] and [Hung 2014] use an apparently arbitrary 15-minute exposure in their tests - a very reasonable decision, given the focus of their paper.
+
+The effectiveness against airborne particles, and to minimize the power required in a dwelling phased-array beam, we must establish the required duration of exposure.
+
+{\color{red} speculative hypothesizing \{ }
+
+In contrast to chemical inactivation, where the time dependence appears to be dominated by viscous fluid dynamic effects [Hirose 2017], or UV inactivation, where a certain quantized dose of photons must be absorbed, we expected RF to act instantaneously.
+
+As a damped, driven oscillator, the ring-up time of the virus depends on the Q factor.
+Yang et al.
+state the Q of Inf.
+A as between 2 and 10, so at 8 GHz the steady-state amplitude should be reached in well under 100 nanoseconds.???????????FIXME
+
+[] found a significant mechanical fatigue effect in phage capsids, where a small strain applied repetitively eventually causes a fracture.
+Such a mechanism could perhaps extend the exposure required to break the capsid or membrane.
+Other mechanisms could include some sort of lipid denaturation, requiring an absolute amount of energy absorption to break or twist bonds and modify properties before the envelope fractures.
+
+{\color{red}  \} }
+
+\clearpage
 {\Large \it Talkin' 'bout the Variation}\\
@@
 To the extreme, some papers have used
-
-\clearpage
-\paragraph{\textbf{Time dependence}}\
-
-The fact that the viral inactivation is non-thermal
-
-Both [Yang 2015] and [Hung 2014] use an apparently arbitrary 15-minute exposure in their tests - a very reasonable decision, given the focus of their paper.
-
-The effectiveness against airborne particles, and to minimize the power required in a dwelling phased-array beam, we must establish the required duration of exposure.
-
-{\color{red} speculative hypothesizing \{ }
-
-In contrast to chemical inactivation, where the time dependence appears to be dominated by viscous fluid dynamic effects [Hirose 2017], or UV inactivation, where a certain quantized dose of photons must be absorbed, we expected RF to act instantaneously.
-
-As a damped, driven oscillator, the ring-up time of the virus depends on the Q factor.
-Yang et al.
-state the Q of Inf.
-A as between 2 and 10, so at 8 GHz the steady-state amplitude should be reached in well under 100 nanoseconds.???????????FIXME
-
-[] found a significant mechanical fatigue effect in phage capsids, where a small strain applied repetitively eventually causes a fracture.
-Such a mechanism could perhaps extend the exposure required to break the capsid or membrane.
-Other mechanisms could include some sort of lipid denaturation, requiring an absolute amount of energy absorption to break or twist bonds and modify properties before the envelope fractures.
-
-{\color{red}  \} }
 
@@
 
-%\printbibliography[ title={Other references}]
+\printbibliography[ title={All references}]
 

### 2020-07-22 documents/supplemental.tex
paper or whatever

@@
 {optical_centrifuge.pdf}
+
+\includepdf[
+%% Include all pages of the PDF
+pages=-,
+%% make this page have the usual page style
+%% (you can change it to plain etc). By default pdfpages
+%% sets the pagecommand to \pagestyle{empty}
+pagecommand={\thispagestyle{empty}},  
+%% Add a "section" entry to the ToC with the heading
+%% "Quilling Shapes" and the label "sec:shapes"
+addtotoc={1,section,1,Quilling Shapes,sec:shapes}]
+%% The pdf file itself
+{biology.pdf}
 
@@
 \rule{\linewidth}{0.2pt}
-
-An expert and distinguished gentleman that we contacted regarding assistance resolving transients in our microstrip VCO stated the following:
-
-This was a perfectly sensible remark; it is almost always the case that (at X-band, no less!) a custom IC would have been needed to build a VCO.
-
-Also, if taken in the context of a tired, overworked PI getting an unsolicited email from an excessively verbose undergraduate at a different university, I hardly think I would have replied differently.
-
-However, I think this person may have missed out. Learning
-
-So perhaps it is wise to ponder the ideas of fools for skeet; one always learns target practice, if only an example what not to do, and occasionally one learns positively.
+%
+%An expert and distinguished gentleman that we contacted regarding assistance resolving transients in our microstrip VCO stated the following:
+%
+%
+%
+%This was a perfectly sensible remark; it is almost always the case that (at X-band, no less!) a custom IC would have been needed to build a VCO.
+%
+%Also, if taken in the context of a tired, overworked PI getting an unsolicited email from an excessively verbose undergraduate at a different university, I hardly think I would have replied differently.
+%
+%However, I think this person may have missed out. Learning 
+%
+%So perhaps it is wise to ponder the ideas of fools for skeet; one always learns target practice, if only an example what not to do, and occasionally one learns positively.
 I have often found that I learn greatly from working on the projects of others.
-
-We present this only as a cautionary tale in the hopes that someday I will listen.
+%
+%We present this only as a cautionary tale in the hopes that someday I will listen.
 

### 2020-07-23 documents/introduction.tex
Reworked paper slightly
Slide 1 done!

@@
+\documentclass[paper.tex]{subfiles}
+\begin{document}
+
 \flushbottom 
@@
 
-The direct inactivation plaque and PCR data in the referenced papers are somewhat convincing corroboration that this effect is not an artifact; but hundreds of convincing and wrong papers exist in the literature.\\
+The direct inactivation plaque and PCR data in the referenced papers are a somewhat convincing corroboration that this effect is not a thermal artifact; but hundreds of convincing and wrong papers exist in the literature.\\
+
+We discuss some possible artifacts in the supplemental, but nothing seems plausible.
+It should be noted that all three papers that reference this technique use similar methods to determine the resonance mode.\\
+
+Then again, our incredulity is itself probably unfounded.
+The data these papers provide are excellent; they passed peer-review in Nature Srep, which is a far closer scrutiny than we could possibly provide.
 
@@
 
-	Please consider all claims with appropriate skepticism.
+In essence, please consider all claims with appropriate skepticism.
 
 \end{autem}
+
+\end{document}

### 2020-07-23 documents/pamphlet.tex
Slide 1 done!

\documentclass[fleqn,10pt]{article}

\begin{document}

Brief: Pulsed microwave-acoustic resonant virus inactivation

Note: please doubt

Mechanism

Evidence for effectiveness:

Evidence against effectiveness:

This works because the damage mechanism

Tasks

Implementation guide

Results seem to indicate that any region with an electric field strength greater than 150 V/m between for 10 ns will be sterilized.

### 2020-07-23 documents/supplemental.tex
Slide 1 done!

@@
 Contrary to some [Hardell 2017] reports, we do not find the FCC and ICNIRP to be significantly affected by special interest groups; their rationales appear to be transparent.
-[FCC-19-126A1] an FCC memorandum wherein the FCC tells groups to respectfully screw themselves no fewer than three times: ''Similarly, IEEE-ICES urges the Commission to
-adopt a higher SAR exposure limit of 2 W/kg averaged over 10 g.
+[FCC-19-126A1], for instance, is a particularly entertaining memorandum:
+
+\begin{quote} 
+Similarly, IEEE-ICES urges the Commission to adopt a higher SAR exposure limit of 2 W/kg averaged over 10 g.
 [snip] We are not persuaded that the IEC standard should be adopted at this time.", "Medtronic and the AAMI-CRMD recommend a more relaxed threshold of 20 mW.
 We decline to increase the 1-mW threshold.".
+
+\end{quote}
 
@@
 
-\PRLsep{{\itshape Fluidics }}
+\PRLsep{{\itshape Microfluidics: small channels, big headaches }}
 
@@
 
-We originally planned on using techniques from the rapidly accelerating field of centrifugal microfluidics, using a broadband patch antenna smaller than the cuvette, and measuring transmission absorption.
+We originally planned on using techniques from the rapidly accelerating field of centrifugal microfluidics, using a broadband patch antenna smaller than the cuvette, and measuring transmission through the cuvette.
 
@@
 3DuF; this is an excellent program
+
+The final process was as follows:
+
+Just using a single-sided tape over micromachined channels didn't work for us; the tape remains sticky and stuck to the bottom of the channel, blocking it.
+
+\begin{itemize}
+	\item 1/16" 003 size Viton O-rings McMaster-Carr \#9464K103, 
+	\item 3M 467MP 0.051 mm double-sided adhesive transfer tape with 200MP acrylic adhesive, DigiKey 3M9726-ND.
+	Various other tapes were tried, such as 9495MP; the laser was not powerful enough to cut these.
+	While the intermittent temperature rating is over 121 C, the high-pressure steam environment does seem to degrade any exposed regions of tape.
+
+	A CO2 laser is usually used to cut these otherwise transparent materials.
+We only had a diode laser.
+However, the front and back paper liners absorb sufficient laser power to melt the tape between.
+This produces horrible results, but was sufficient for this purpose.
+With our 2.5 W, ~0.15 mm spot size, 450 mm/min for the tape.
+
+	\item MG Chemicals 416-T Laser Printer Transparency Film, 0.1 mm thick. Presumably a PET/Mylar material.
+
+	\item A vinyl cutter was used to cut the openings in the top mylar cover slip.
+	\item Cover plate machined from polycarbonate with a 1/16" two-flute carbide endmill, 24000 RPM, between 500 and 1000 mm/min, up to 1.5 mm step-down.
+G-code generated with MeshCAM.
+This seems to withstand the autoclave without any damage.
+	\item Note: the tape preferentially sticks to the back liner, rather than the front.
+	Rub the thing hard with a 
+	Aluminum foil
+
+\end{itemize}
+
+Making this device ourselves was a grave mistake that cost many lives. We should have used \cite{Straight}, a COTS version which we discovered halfway through.
+
+I'm sorry.
+
+\printbibliography[title={General fluidics resources}, keyword={microfluidics}]
+
+\printbibliography[title={Centrifugal}, keyword={centrifugal}]
+
+\PRLsep{{\itshape aaaaa }}
 

### 2020-07-23 documents/pamphlet.tex
Pamphlet

@@
-\documentclass[fleqn,10pt]{article}
+\documentclass[fleqn,10pt]{paper}
+
+\usepackage[left=2cm,right=2cm,
+top=0cm,
+bottom=2.25cm,%
+headheight=11pt,%
+letterpaper]{geometry}
+
+\include{preamble}
+
+\title{Maxwell's Silver Hammer, briefly:\\ On the application of pulsed microwave acoustic resonant viral inactivation}
 
@@
 
-Brief: Pulsed microwave-acoustic resonant virus inactivation
+\maketitle
 
-Note: please doubt
+%\footnote{The}
 
-Mechanism
+This is a heavily condensed version of a (hideously unfinished) paper at \href{https://www.github.com/0xDBFB7/covidinator/documents/paper.pdf}{\faGithub/0xDBFB7/covidinator}.
 
-Evidence for effectiveness:
+I think it is important that you doubt and scrutinize everything written. This hinges on minutia and
 
-Evidence against effectiveness:
+{\Large \textbf{The mechanism}}
+
+The literature is littered with irreproducible claims of non-thermal effects; however, this certainly appears to be a singular anomaly.
+
+\cite{Microwave2009} \textrightarrow \ (\cite{focusing2014} $\parallel$ \cite{Efficient2015} $\parallel$ \cite{Resonant2017}) appear to establish that the net charge, mass, and envelope stiffness of a few species of viruses supports a weak resonance mode in the microwave spectrum, with a peak at roughly 8 GHz.
+
+They appear to demonstrate that this allows a comparatively inconsequential electromagnetic field magnitude to produce mechanical stresses sufficient to crack the lipid envelope, destroying the virus.
+
+By extending this work into the time-domain, pulsing the field at nanosecond scales, it appears to reduce the threshold to less than 1/Xth of all safety limits.
+Better yet, by scanning the focal point or beam , a significant area can be treated with a relatively small output power.
+
+\cite{Efficient2015} test with various strains of Influenza A, we test with Coliphage T4; structural similarities with NCoV mean this
+
+These authors above deserve all the credit for this finding; nothing in this work is even remotely novel.
+
+{\Large \textbf{How is this better than the alternatives?}}
+
+It penetrates tissue.
+
+{\Large \textbf{Is it safe?}}
+
+The consensus is that the environment not favorable to create such modes; damping from the surrounding fluids is too strong \cite{Vibrational2002}.
+
+Quality in-vitro data supports this assertion.
+\cite{Cytogenetic2006} expose blood cells (a representative cell) to pulse power in precisely the regime required in this work; 8.2 GHz, 8 ns duration, 50 khz repetition rate, a whopping pulse power density of 250,000\Wsqm\footnote{computed from average power / duty cycle} (2500x the time-averaged power density safety limit), average power density 100\Wsqm (the safety limit), for 2 hours, finding no change in any of the measured quantities.
+
+Similarly, \cite{DNA2004} use 8.8 GHz, 180 ns pulse width, peak power 65,000 W, repetition rate 50 Hz, exposure duration 40 min, and find genotoxicity purely due through the expected thermal mode.
+
+[Foster 1987]
+
+\footnote{These are cherry-picked.}
+
+The literature reviews of \cite{ICNIRP2020} and \cite{C95} that they have conducted are far more exhaustive than ours.
+
+Whether this is due to a specific feature of the virion or simply, we are unsure. The lipid bilayer of the virion differs in composition from that of the host cell.
 
@@
 
-Tasks
+{\Large \textbf{How do we wield this sword?}}
 
-Implementation guide
+Results seem to indicate that any region with a power density in the 7 to 9 GHz band greater than 300\Wsqm \ for 10 ns will be sterilized. This is not a particularly demanding requirement.
 
-Results seem to indicate that any region with an electric field strength greater than 150 V/m between for 10 ns will be sterilized.
+With modern semiconductor processes, it is trivial to produce
+
+It is possible to create these conditions within human tissues; attenuation limits the safe treatment depth to about 3 cm.
+
+\begin{autem}
+	a
+\end{autem}
+
+%\centering {\color{red} \faHeart}
+
+\clearpage
+
+\printbibliography[heading=none, title={}]
+
+\end{document}

### 2020-07-23 documents/supplemental.tex
Pamphlet

@@
 
-Method-of-moments solvers like NEC-2 are typical for simulating antennas.
-However, most commonly-available packages don't seem to handle multiple dielectric constants, such as the air and substrate for a patch antenna.
+Method-of-moments solvers like NEC-2 are the standard for simulating these sorts of antennas.
+However, most commonly-available packages don't seem to handle multiple dielectric constants, such as the air and substrate of a patch antenna.
 
-The impedance of an antenna over frequency can be determined in FDTD by:
+The impedance of a structure over frequency can be determined in FDTD by:
 
@@
   \item Taking the fourier transform of the (real) excitation voltage and current (producing a complex result, mind you)
-  \item Taking the ratio of the two complex spectra.
+  \item Taking the magnitude of the ratio of the two complex spectra.
 \end{itemize}
@@
 
-Our implementation is in electronics/simple\_fdtd/runs/U.py.
+Our implementation is in \ghfile{electronics/simple_fdtd/runs/U.py}.
 
@@
 	\item A vinyl cutter was used to cut the openings in the top mylar cover slip.
-	\item Cover plate machined from polycarbonate with a 1/16" two-flute carbide endmill, 24000 RPM, between 500 and 1000 mm/min, up to 1.5 mm step-down.
+	\item Frame machined from polycarbonate with a 1/16" two-flute carbide endmill, 24000 RPM, between 500 and 1000 mm/min, up to 1.5 mm step-down.
 G-code generated with MeshCAM.
@@
 	\item Note: the tape preferentially sticks to the back liner, rather than the front.
-	Rub the thing hard with a 
-	Aluminum foil
+	With both adhesive liners on, rub the thing hard with a rounded edge and rolling pin.
+	Aluminum foil tape backing on the adhesive layer.
+	Don't de-weed yet.
 
@@
 
-Making this device ourselves was a grave mistake that cost many lives. We should have used \cite{Straight}, a COTS version which we discovered halfway through.
+Note that cutting many of these materials with a laser is a bad idea. The residue will
+
+\begin{itemize}
+	\item Tape mylar to a cardstock backing with masking tape on the sides. Cut mylar on plotter with InkCut. 175 g force. 
+	\item Apply aluminum foil tape to the rear backing (with "3M" text) of the adhesive transfer tape. This supports the cut structures, without being cut itself.
+	\item Stick the adhesive to the laser bed with Kapton, foil-side down. It's not a good idea to use masking tape; it'll catch fire.
+	\item 
+\end{itemize}
+
+Making this device ourselves was a grave mistake that potentially cost many lives. We should have used \cite{Straight}, a COTS version which we discovered halfway through.
 
 I'm sorry.
+
+\paragraph{Lessons learned:}
+
+When trying to characterize the response to some process parameters (say, laser power), iteratively trying different parameters in series can be somewhat useful, as each trial informs the next.
+In this instance, we would try a speed and power, unstick the material from the bed, observe the result, decide on the course of action, and repeat.
+However, if it is possible to try many parameters in parallel just as fast as in series, (that is, in our case, make a coupon using [] that tries all reasonable values simultaneously), it would be very dumb not to do this.
+
+We are very dumb.
 

### 2020-07-23 documents/pamphlet.tex
gosh writing papers is addictive, have to stop

@@
 
-\title{Maxwell's Silver Hammer, briefly:\\ On the application of pulsed microwave acoustic resonant viral inactivation}
+\title{Maxwell's Silver Hammer, summarized:\\ On the application of pulsed microwave acoustic resonant viral inactivation}
 
@@
 
-This is a heavily condensed version of a (hideously unfinished) paper at \href{https://www.github.com/0xDBFB7/covidinator/documents/paper.pdf}{\faGithub/0xDBFB7/covidinator}.
+This is a heavily condensed version of a (hideously unfinished) paper at \href{https://www.github.com/0xDBFB7/covidinator/documents/paper.pdf}{\faGithub/0xDBFB7/covidinator}.\footnote{Assign blame to Daniel Correia [TODO affiliation] \orcidlink{0000-0002-9353-0216}}
 
-I think it is important that you doubt and scrutinize everything written. This hinges on minutia and
+Both the microwave and dosimetric components \footnote{field field?} appear to be unusually sensitive to experimental design and exceptionally prone to artifacts that cause false positive results: \cite{Microwave1982} $\neq$ \cite{Resonances1987}, \cite{Effects1985a} $\neq$ \cite{Cytogenetic1986}, \cite{Comprehensive2018}.
+Though the cited articles have taken care to avoid these effects, is possible that none of what is discussed below actually exists.
 
@@
 
-\cite{Microwave2009} \textrightarrow \ (\cite{focusing2014} $\parallel$ \cite{Efficient2015} $\parallel$ \cite{Resonant2017}) appear to establish that the net charge, mass, and envelope stiffness of a few species of viruses supports a weak resonance mode in the microwave spectrum, with a peak at roughly 8 GHz.
+\cite{Microwave2009} \textrightarrow \ (\cite{focusing2014} $\parallel$ \cite{Efficient2015} $\parallel$ \cite{Resonant2017})\footnote{A great many papers are involved.} appear to establish that the net charge, mass, and envelope stiffness of a few species of viruses supports a weak resonance mode in the microwave spectrum, with a peak at roughly 8 GHz.
 
@@
 
-Results seem to indicate that any region with a power density in the 7 to 9 GHz band greater than 300\Wsqm \ for 10 ns will be sterilized. This is not a particularly demanding requirement.
+Results seem to indicate that any region with a power density in the 7 to 9 GHz band greater than 300\Wsqm \ for 10 ns will be sterilized.
+This is not a particularly demanding requirement.
+We provide a reference design that costs \$3 in prototype quantities.
 

### 2020-07-24 documents/pamphlet.tex
Eppenwolf milled out

@@
 
-\title{Maxwell's Silver Hammer, summarized:\\ On the application of pulsed microwave acoustic resonant viral inactivation}
+\title{On pulsed microwave acoustic resonant viral inactivation: summary}
 
@@
 
-This is a heavily condensed version of a (hideously unfinished) paper at \href{https://www.github.com/0xDBFB7/covidinator/documents/paper.pdf}{\faGithub/0xDBFB7/covidinator}.\footnote{Assign blame to Daniel Correia [TODO affiliation] \orcidlink{0000-0002-9353-0216}}
+This is a heavily condensed version of a (hideously unfinished) paper at \href{https://www.github.com/0xDBFB7/covidinator/documents/paper.pdf}{\faGithub/0xDBFB7/covidinator}.\footnote{Daniel Correia [TODO affiliation] \orcidlink{0000-0002-9353-0216}}
 
@@
 
-The literature is littered with irreproducible claims of non-thermal effects; however, this certainly appears to be a singular anomaly.
+The literature is littered with irreproducible claims of non-thermal effects; however, this appears to be a singular anomaly.
 
-\cite{Microwave2009} \textrightarrow \ (\cite{focusing2014} $\parallel$ \cite{Efficient2015} $\parallel$ \cite{Resonant2017})\footnote{A great many papers are involved.} appear to establish that the net charge, mass, and envelope stiffness of a few species of viruses supports a weak resonance mode in the microwave spectrum, with a peak at roughly 8 GHz.
+\cite{Microwave2009} \textrightarrow \ (\cite{focusing2014} $\parallel$ \cite{Efficient2015} $\parallel$ \cite{Resonant2017})\footnote{A great many papers are involved.} appear to establish that the net charge, mass distribution, and envelope stiffness of a few species of viruses supports a weak resonance mode in the microwave spectrum, with a peak at roughly 8 GHz.
 
@@
 
-By extending this work into the time-domain, pulsing the field at nanosecond scales, it appears to reduce the threshold to less than 1/Xth of all safety limits.
-Better yet, by scanning the focal point or beam , a significant area can be treated with a relatively small output power.
+\cite{Efficient2015} specifically provides a reasonable spherical-cow model for how this could occur that agrees well with experiment.
 
-\cite{Efficient2015} test with various strains of Influenza A, we test with Coliphage T4; structural similarities with NCoV mean this
+This work can be extended with the following assertion: the virus' Q factor is only 2, meaning that the steady-state amplitude should be reached in some nanoseconds.
+
+Barring protein mechanical fatigue [] or other mechanisms that could prolong the inactivation duration, pulsing the field at nanosecond scales, it appears to reduce the threshold to less than 1/Xth of all safety limits.
+Better yet, by scanning the focal point, a significant area can be treated with a relatively small transmit power.
+
+\cite{Efficient2015} test with various strains of Influenza A, we test with Coliphage T4; structural similarities with NCoV mean this is may be transferable.
 
@@
 
-It penetrates tissue.
+It produces no ozone and causes no damage to tissue (unlike near UV) even during continuous exposure, penetrates tissue (unlike far UV and cold-plasma), and
 
@@
 
-Results seem to indicate that any region with a power density in the 7 to 9 GHz band greater than 300\Wsqm \ for 10 ns will be sterilized.
+If this is correct, any region with a power density in the 7 to 9 GHz band greater than 300\Wsqm \ for 10 ns will be sterilized.
+
 This is not a particularly demanding requirement.
+
 We provide a reference design that costs \$3 in prototype quantities.
@@
 
+{\Large \textbf{Tasks}}
+
+We can see the following
+
+\begin{itemize}
+	\item To prevent duplication of work, are any other teams working on this now? It seems a rather obvious technique. A thorough review of arxiv etc should be performed.
+	\item Double-check all figures and assumptions.
+	\item Get permission to use York University as affiliation, post on arxiv.
+	\item Send off spectrometer (or, ideally, a more precise piece of equipment) to a BSL with a sample of NCoV to obtain the spectra and thresholds.
+	\item Determine the ideal application (requires detailed sims), finish the design for the electromagnetic mask, start bronchoscopic trials?
+
+	\item Check with the FCC/Industry Canada if we can get a temporary exemption for these intentional radiators?
+
+\end{itemize}
+
 %\centering {\color{red} \faHeart}

### 2020-07-25 documents/pamphlet.tex
Driver built

@@
 
-If this is correct, any region with a power density in the 7 to 9 GHz band greater than 300\Wsqm \ for 10 ns will be sterilized.
+If this is correct, any region with a power density in the 7 to 9 GHz band greater than 300\Wsqm \ for 100 ns.
 
@@
 
+It is possible to create these conditions within human tissues.
+Depending on the type of tissue, this field strength appears to be safely produced a minimum of 3 cm thickness (suitable for targeted sterilization of lungs etc with a bronchoscopic technique), up to 200 cm (entirely removing the virus from the body).
+\ghfile{documents/pulse.ipynb} We await the reply
+
+On an individual level, the free-space-combined output of, say, a few dozen SiGe:C or GaAs transistors (\$0.3 apiece [BFP620]) should suffice to locally protect the major vulnerabilities like mouth, nose, eyes, hair and any surfaces that the hands contact.
+This arguably wouldn't provide many advantages over simple masks, however.
+\ghfile{documents/global.ipynb}
+
 We provide a reference design that costs \$3 in prototype quantities.
-
-With modern semiconductor processes, it is trivial to produce
-
-It is possible to create these conditions within human tissues; attenuation limits the safe treatment depth to about 3 cm.
 

### 2020-07-28 documents/pamphlet.tex
Eppenwolf coming together

@@
 \usepackage[left=2cm,right=2cm,
-top=0cm,
+top=0.5cm,
 bottom=2.25cm,%
@@
 
-This is a heavily condensed version of a (hideously unfinished) paper at \href{https://www.github.com/0xDBFB7/covidinator/documents/paper.pdf}{\faGithub/0xDBFB7/covidinator}.\footnote{Daniel Correia [TODO affiliation] \orcidlink{0000-0002-9353-0216}}
+This is a heavily condensed version of a (horribly unfinished) paper at \href{https://www.github.com/0xDBFB7/covidinator/documents/paper.pdf}{\faGithub/0xDBFB7/covidinator}.\footnote{Daniel Correia [TODO affiliation] \orcidlink{0000-0002-9353-0216}}
 
 Both the microwave and dosimetric components \footnote{field field?} appear to be unusually sensitive to experimental design and exceptionally prone to artifacts that cause false positive results: \cite{Microwave1982} $\neq$ \cite{Resonances1987}, \cite{Effects1985a} $\neq$ \cite{Cytogenetic1986}, \cite{Comprehensive2018}.
-Though the cited articles have taken care to avoid these effects, is possible that none of what is discussed below actually exists.
+Though the cited articles have taken care to avoid these effects, it is entirely possible that none of what is discussed below actually exists.
+
+This project was rushed, terribly managed, and not nearly as rigorous as the field demands. This may well end up being a waste of time. I'm very sorry.
+
+%The literature is littered with irreproducible claims of non-thermal effects; however, this appears to be a singular anomaly.
 
 {\Large \textbf{The mechanism}}
-
-The literature is littered with irreproducible claims of non-thermal effects; however, this appears to be a singular anomaly.
 
@@
 
-This work can be extended with the following assertion: the virus' Q factor is only 2, meaning that the steady-state amplitude should be reached in some nanoseconds.
+However, this work would seem to be more useful if extended with the following assertion: the virus' Q factor is only about 2, meaning that the steady-state amplitude and stresses should be reached in some nanoseconds.
 
-Barring protein mechanical fatigue [] or other mechanisms that could prolong the inactivation duration, pulsing the field at nanosecond scales, it appears to reduce the threshold to less than 1/Xth of all safety limits.
-Better yet, by scanning the focal point, a significant area can be treated with a relatively small transmit power.
+Barring protein mechanical fatigue \cite{Mechanical2013} or some other mechanism that could prolong the inactivation duration, it appears to be possible to reduce the required power density to a minuscule fraction of all safety limits by pulsing the field at nanosecond scales.
+Better yet, by then scanning the focal point, a significant area can be treated with a relatively small transmit power.
 
@@
 
-{\Large \textbf{How is this better than the alternatives?}}
-
-It produces no ozone and causes no damage to tissue (unlike near UV) even during continuous exposure, penetrates tissue (unlike far UV and cold-plasma), and
-
 {\Large \textbf{Is it safe?}}
 
-The consensus is that the environment not favorable to create such modes; damping from the surrounding fluids is too strong \cite{Vibrational2002}.
+The consensus is that conditions in human tissues are highly unfavorable for any such resonance modes; damping from biological solvents is too strong \cite{Vibrational2002}.
+Harm occurs only through thermal mechanisms; therefore an almost arbitrarily powerful pulse can be safely applied for infinitesimal periods.
 
@@
 \cite{Cytogenetic2006} expose blood cells (a representative cell) to pulse power in precisely the regime required in this work; 8.2 GHz, 8 ns duration, 50 khz repetition rate, a whopping pulse power density of 250,000\Wsqm\footnote{computed from average power / duty cycle} (2500x the time-averaged power density safety limit), average power density 100\Wsqm (the safety limit), for 2 hours, finding no change in any of the measured quantities.
+\cite{DNA2004} replicate this finding, finding genotoxicity purely through the expected thermal mode.
+\footnote{These papers were cherry-picked from a sea of positive results.
+See the full paper for the rationale.}
 
-Similarly, \cite{DNA2004} use 8.8 GHz, 180 ns pulse width, peak power 65,000 W, repetition rate 50 Hz, exposure duration 40 min, and find genotoxicity purely due through the expected thermal mode.
+The literature reviews of \cite{ICNIRP2020} and \cite{C95} are exhaustive; however, there is not a great deal of in-vivo evidence in this frequency range\cite{New2019}\cite{Comprehensive2018}.
 
-[Foster 1987]
+We are unsure what specific feature of the virion accounts for this discrepancy. The lipid bilayer of the virion differs in composition from that of the host cell, imparting a different net charge.
 
-\footnote{These are cherry-picked.}
-
-The literature reviews of \cite{ICNIRP2020} and \cite{C95} that they have conducted are far more exhaustive than ours.
-
-Whether this is due to a specific feature of the virion or simply, we are unsure. The lipid bilayer of the virion differs in composition from that of the host cell.
-
-This works because the damage mechanism
-
+\clearpage 
 {\Large \textbf{How do we wield this sword?}}
 
-If this is correct, any region with a power density in the 7 to 9 GHz band greater than 300\Wsqm \ for 100 ns.
+If the above is correct, any region with a power density in the 7 to 9 GHz band greater than 300\Wsqm \ for 100 ns will be sterilized.
 
-This is not a particularly demanding requirement.
+This is not a particularly demanding requirement, and lends itself to a wide variety of applications, many of which could be implemented almost immediately.
 
-It is possible to create these conditions within human tissues.
-Depending on the type of tissue, this field strength appears to be safely produced a minimum of 3 cm thickness (suitable for targeted sterilization of lungs etc with a bronchoscopic technique), up to 200 cm (entirely removing the virus from the body).
-\ghfile{documents/pulse.ipynb} We await the reply
+First, depending on the type of tissue, this field strength can apparently be safely produced a minimum of 3 cm deep (suitable for targeted sterilization of lungs or other organs with bronchoscopic techniques), up to 200 cm (eradicating the virus from the body).
+\ghfile{documents/pulse.ipynb}.
+We are working to narrow these bounds now.
 
@@
 
-We provide a reference design that costs \$3 in prototype quantities.
+On the other extreme, installations with Klystrons could sterilize square-kilometer areas.
 
@@
 	\item Double-check all figures and assumptions.
-	\item Get permission to use York University as affiliation, post on arxiv.
 	\item Send off spectrometer (or, ideally, a more precise piece of equipment) to a BSL with a sample of NCoV to obtain the spectra and thresholds.
-	\item Determine the ideal application (requires detailed sims), finish the design for the electromagnetic mask, start bronchoscopic trials?
-
+	\item get the gosh-darned AustinMan voxel team to reply to my gosh-darned emails
+	\item Determine the ideal application to focus effort on
+	\item ???????
 	\item Check with the FCC/Industry Canada if we can get a temporary exemption for these intentional radiators?

### 2020-07-28 firmware/eppenwolf/protocols/pulse_1.cpp

@@ -1,0 +1,87 @@
+import device_comms
+import sweep
+
+# Phage+Bacteria / Bacteria-only / phage only?
+# expose (parameters) / sham / thermal positives
+
+# For each of the animal and human published studies, four
+# predetermined and specific quality control measures were used to
+# assess the quality of the publication.
+# 1. Whether or not the researchers have used ‘‘blind’’ evaluations to
+# avoid individual ‘‘bias’’, B or nB;
+# 2. Whether or not there was detailed/adequate description of
+# ‘‘dosimetry’’ in the publication for independent replication/
+# confirmation studies, D or nD.
+# 3. Whether or not ‘‘positive controls’’ were included in the
+# experiment(s) to replicate/confirm the observations, P or nP.
+# 4. Whether or not ‘‘sham-exposed controls’’ (more appropriate to
+# compare with the observations made in RF exposure conditions)
+# were included in the experiments, S or nS. However, it was not our
+# intention to ‘‘rank’’ the publications either to exclude or include
+# the reported data in the meta-analysis.
+
+def initialize():
+    # Name this run
+    # Fluidic plate ID
+
+
+    print("Fill phage into all selected cuvettes.")
+    Simulataneously and separately
+
+#centrifuge down bacteria lightly to concentrate
+#Mix with fresh broth
+#Vortex for X seconds?
+#
+# Rajnovic 2019
+# Overnight cultures of E. coli were centrifuged and the pellets resuspended in 0.1 mM PB to
+# achieve a concentration of 10^10 cfu/mL.
+# The resulting suspensions were subject to serial dilution
+#
+# For each assay, 160 μL of LB were mixed with
+# 20 μL phage solution, 20 μL of bacteria solution and 20μL of PB in
+
+
+def bacteria_alone_control():
+    //repeated twice
+
+    # fill_phage()
+
+
+def bacteria_and_phage_control():
+    //repeated twice
+
+
+def bacteria_and_inactivated_phage_positive_control():
+    //
+
+
+
+
+Add a small amount of growing e.coli to a new nutrient broth,
+aerate vigorously, then add to culture chamber.
+
+Expose phage.
+Fill culture.
+Monitor culture for log stage.
+Mix culture and phage.
+Monitor mixture.
+
+Types of exposure:
+
+RF
+
+Expose phage, mix with log bacteria, monitor.
+
+Bare
+
+Sham
+
+?
+
+Positive control
+
+Bring phage cuvette temperature to 120c with trace.
+
+
+
+Autoclaved

### 2020-07-30 documents/pamphlet.tex
More progress

@@
 
-\title{On pulsed microwave acoustic resonant viral inactivation: summary}
+\title{{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation}
 
@@
 
-Both the microwave and dosimetric components \footnote{field field?} appear to be unusually sensitive to experimental design and exceptionally prone to artifacts that cause false positive results: \cite{Microwave1982} $\neq$ \cite{Resonances1987}, \cite{Effects1985a} $\neq$ \cite{Cytogenetic1986}, \cite{Comprehensive2018}.
+Both the microwave and microbiological components of this field\footnote{field field?} appear to be unusually sensitive to experimental design and exceptionally prone to artifacts that cause false positive results: \cite{Microwave1982} $\neq$ \cite{Resonances1987}, \cite{Effects1985a} $\neq$ \cite{Cytogenetic1986}, \cite{Comprehensive2018}.
 Though the cited articles have taken care to avoid these effects, it is entirely possible that none of what is discussed below actually exists.
 
-This project was rushed, terribly managed, and not nearly as rigorous as the field demands. This may well end up being a waste of time. I'm very sorry.
+This project was rushed and slow, terribly managed, and not nearly as rigorous as the field demands. This may well end up being a waste of time. I'm very sorry.
 
@@
 
-\cite{Efficient2015} specifically provides a reasonable spherical-cow model for how this could occur that agrees well with experiment.
+\cite{Efficient2015} specifically provides a reasonable spherical-cow model for how this could occur that agrees well with experiment. \footnote{See also \ghfile{documents/biology.ipynb}}
 
@@
 Barring protein mechanical fatigue \cite{Mechanical2013} or some other mechanism that could prolong the inactivation duration, it appears to be possible to reduce the required power density to a minuscule fraction of all safety limits by pulsing the field at nanosecond scales.
-Better yet, by then scanning the focal point, a significant area can be treated with a relatively small transmit power.
+This incidentally allows scanning of a focal point, a significant area can be treated with a relatively small transmit power.
 
@@
 
-The consensus is that conditions in human tissues are highly unfavorable for any such resonance modes; damping from biological solvents is too strong \cite{Vibrational2002}.
+The consensus is that conditions in our cells are highly unfavorable for any such resonance modes; damping from biological solvents is too strong \cite{Vibrational2002}.
 Harm occurs only through thermal mechanisms; therefore an almost arbitrarily powerful pulse can be safely applied for infinitesimal periods.
@@
 
-First, depending on the type of tissue, this field strength can apparently be safely produced a minimum of 3 cm deep (suitable for targeted sterilization of lungs or other organs with bronchoscopic techniques), up to 200 cm (eradicating the virus from the body).
-\ghfile{documents/pulse.ipynb}.
+First, depending on the type of tissue, this field strength can apparently be safely produced a minimum of 3 cm deep (suitable for targeted sterilization of lungs or other organs with bronchoscopic techniques), up to 200 cm (eradicating the virus from the body) \cite{Physical1982}.
 We are working to narrow these bounds now.
 
-On an individual level, the free-space-combined output of, say, a few dozen SiGe:C or GaAs transistors (\$0.3 apiece [BFP620]) should suffice to locally protect the major vulnerabilities like mouth, nose, eyes, hair and any surfaces that the hands contact.
+On an individual level, the free-space-combined output of, say, a few dozen SiGe:C or GaAs transistors (\$0.3 apiece [BFP620]), very similarly to our reference design, should suffice to locally protect the major vulnerabilities like mouth, nose, eyes, hair and any surfaces that the hands contact.
 This arguably wouldn't provide many advantages over simple masks, however.
-\ghfile{documents/global.ipynb}
 
-On the other extreme, installations with Klystrons could sterilize square-kilometer areas.
+Unlike UV, the X-band is minimally attenuated by air. Common areas could be illuminated by magnetron systems.
+
+On the other extreme, installations with megawatt-scale klystrons could sterilize square-kilometer areas at a time.
 

### 2020-07-30 firmware/eppenwolf/src/test_host_comms.cpp

@@ -2,7 +2,8 @@
 
 
 void test_host_comms_init(){
-    host_serial.begin(HOST_BAUD_RATE);
+
+
 }
 
 void run_host_comms_tests(){

### 2020-07-30 documents/pamphlet.tex
Argon

@@
 top=0.5cm,
-bottom=2.25cm,%
+bottom=1.5cm,%
 headheight=11pt,%
@@
 
-This is a heavily condensed version of a (horribly unfinished) paper at \href{https://www.github.com/0xDBFB7/covidinator/documents/paper.pdf}{\faGithub/0xDBFB7/covidinator}.\footnote{Daniel Correia [TODO affiliation] \orcidlink{0000-0002-9353-0216}}
+This is a condensed version of a (horribly unfinished) paper at \href{https://www.github.com/0xDBFB7/covidinator/documents/paper.pdf}{\faGithub/0xDBFB7/covidinator}.\footnote{Daniel Correia [TODO affiliation] \orcidlink{0000-0002-9353-0216}}
 
-Both the microwave and microbiological components of this field\footnote{field field?} appear to be unusually sensitive to experimental design and exceptionally prone to artifacts that cause false positive results: \cite{Microwave1982} $\neq$ \cite{Resonances1987}, \cite{Effects1985a} $\neq$ \cite{Cytogenetic1986}, \cite{Comprehensive2018}.
+Both the microwave and microbiology components of this field\footnote{field field?} appear to be unusually sensitive to experimental design and exceptionally prone to artifacts that cause false positive results: \cite{Microwave1982} $\neq$ \cite{Resonances1987}, \cite{Effects1985a} $\neq$ \cite{Cytogenetic1986}, \cite{Comprehensive2018}.
 Though the cited articles have taken care to avoid these effects, it is entirely possible that none of what is discussed below actually exists.
 
-This project was rushed and slow, terribly managed, and not nearly as rigorous as the field demands. This may well end up being a waste of time. I'm very sorry.
+This project was rushed and slow, terribly managed, and not nearly as rigorous as the field demands. This may well end up being a waste of time.
 
@@
 
-\cite{Microwave2009} \textrightarrow \ (\cite{focusing2014} $\parallel$ \cite{Efficient2015} $\parallel$ \cite{Resonant2017})\footnote{A great many papers are involved.} appear to establish that the net charge, mass distribution, and envelope stiffness of a few species of viruses supports a weak resonance mode in the microwave spectrum, with a peak at roughly 8 GHz.
+\cite{Microwave2009} \textrightarrow \ (\cite{focusing2014} $\parallel$ \cite{Efficient2015} $\parallel$ \cite{Resonant2017})\footnote{A great many papers are involved.} appear to establish that the net charge, mass distribution, and envelope stiffness of a few species of viruses support a weak resonance mode in the microwave spectrum, with a peak at roughly 8 GHz for Inf.
+A.
 
@@
 
-\cite{Efficient2015} specifically provides a reasonable spherical-cow model for how this could occur that agrees well with experiment. \footnote{See also \ghfile{documents/biology.ipynb}}
+\cite{Efficient2015} specifically provides a reasonable spherical-cow model for how this could occur that agrees well with experiment.\footnote{See also \ghfile{documents/biology.ipynb}}
 
@@
 
-\cite{Efficient2015} test with various strains of Influenza A, we test with Coliphage T4; structural similarities with NCoV mean this is may be transferable.
+\cite{Efficient2015} test with various strains of Influenza A, we are testing with Coliphage T4; structural similarities with NCoV mean this is may be transferable.
 
@@
 Quality in-vitro data supports this assertion.
-\cite{Cytogenetic2006} expose blood cells (a representative cell) to pulse power in precisely the regime required in this work; 8.2 GHz, 8 ns duration, 50 khz repetition rate, a whopping pulse power density of 250,000\Wsqm\footnote{computed from average power / duty cycle} (2500x the time-averaged power density safety limit), average power density 100\Wsqm (the safety limit), for 2 hours, finding no change in any of the measured quantities.
+\cite{Cytogenetic2006} expose cells to pulse power in precisely the regime required in this work; 8.2 GHz, 8 ns duration, 50 khz repetition rate, a whopping pulse power density of 250,000\Wsqm\footnote{computed from average power / duty cycle} (2500x the time-averaged power density safety limit), average power density 100\Wsqm (the safety limit), for 2 hours, finding no change in any of the measured quantities.
 \cite{DNA2004} replicate this finding, finding genotoxicity purely through the expected thermal mode.
@@
 
-If the above is correct, any region with a power density in the 7 to 9 GHz band greater than 300\Wsqm \ for 100 ns will be sterilized.
+If the above is correct, any region with a power density in the 7 to 9 GHz band greater than 300\Wsqm \ for 100 ns will be sterilized. (TODO field strength)
 
@@
 On the other extreme, installations with megawatt-scale klystrons could sterilize square-kilometer areas at a time.
-
-\begin{autem}
-	a
-\end{autem}
 

### 2020-07-30 firmware/eppenwolf/host/test/test_.py

@@ -2,15 +2,15 @@ import sys
 sys.path.append('/home/arthurdent/covidinator/firmware/eppendoofus/host/')
 
 import device_comms
-
+from device_comms import *
+import pytest
 link = device_comms.connect()
 
 
 def test_loopback():
     send_size = 0
     float_ = 563.5
-    float_size = link.tx_obj(float_, send_size) - send_size
-    send_size += float_size
+    send_size += add_float(link, send_size, float_)
     link.send(send_size, packet_id=10)
 
     while not link.available():
@@ -24,7 +24,11 @@ def test_loopback():
             else:
                 print('ERROR: {}'.format(link.status))
 
-    rec_float_ = link.rx_obj(obj_type=type(float_),
-                                     obj_byte_size=float_size,
-                                     start_pos=(list_size + str_size))
+    rec_float_ = link.rx_obj(obj_type=type(float()),
+                                     obj_byte_size=4,
+                                     start_pos=(0))
+
+    clear_buffers(link)
+
+    assert rec_float_ == pytest.approx(float_)
     assert link.idByte == 10

### 2020-07-30 firmware/eppenwolf/src/VCO_driver.hpp

@@ -18,7 +18,7 @@
 
 
 void init_VCO();
-
+void set_VCO(float base_bias_voltage, float varactor_voltage, float supply_voltage, bool power_state);
 // struct transistor_driver{
 //     String name = "";
 //

### 2020-07-30 firmware/eppenwolf/src/host_comms.cpp

@@ -6,17 +6,12 @@ SerialTransfer host_transfer;
 
 void dispatch(){
     if(host_transfer.available()){
-        debug_serial.println("Packet " + String(host_transfer.currentPacketID()));
         switch(host_transfer.currentPacketID()) {
+            case 0: set_VCO_handler(); break;
             case 10: loopback(); break;
         }
         //screw function pointers!
     }
-    int t = 0;
-    uint16_t sendSize = 0;
-    sendSize = host_transfer.txObj(t, sendSize);
-
-    host_transfer.sendData(sendSize, 10);
 }
 
 
@@ -27,5 +22,8 @@ void loopback(){
     recSize = host_transfer.rxObj(t, recSize);
     debug_serial.print(t);
 
+    uint16_t sendSize = 0;
+    sendSize = host_transfer.txObj(t, sendSize);
 
+    host_transfer.sendData(sendSize, 10);
 }

### 2020-08-01 firmware/eppenwolf/protocols/microwave_spectrum.py_nw_.tex
Noweb

\documentclass{article}\usepackage{noweb}\pagestyle{noweb}\noweboptions{}\begin{document}\nwfilename{microwave_spectrum.py}\nwbegindocs{0}\nwdocspar% ===> this file was generated automatically by noweave --- better not edit it
\nwenddocs{}\nwbegindocs{1}\nwdocspar
Our aims with this

\nwenddocs{}\nwbegindocs{2}\nwdocspar
Inspired by \cite{Biocoder2010}, we write the microbiology protocol directly into the Eppenwolf firmware.

    log_serial.println(String(__FILE__));

}

\nwenddocs{}\nwbegincode{3}\sublabel{NW3GNx30-3GNx30-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW3GNx30-3GNx30-1}}}\moddef{microwave_spectrum.py~{\nwtagstyle{}\subpageref{NW3GNx30-3GNx30-1}}}\endmoddef\nwstartdeflinemarkup\nwenddeflinemarkup
alalsdjkf

BASE_BIAS_GAINaa
aa
\nwnotused{microwave_spectrum.py}\nwendcode{}

\nwixlogsorted{c}{{microwave_spectrum.py}{NW3GNx30-3GNx30-1}{\nwixd{NW3GNx30-3GNx30-1}}}%
\end{document}

### 2020-08-01 firmware/eppenwolf/protocols/microwave_spectrum.cpp

@@ -1,11 +1,0 @@
-
-
-
-void run_protocol(){
-
-    // Inspired by \cite{Biocoder2010}, we write the
-    // microbiology protocol directly into the Eppenwolf firmware.
-
-    log_serial.println(String(__FILE__));
-
-}

### 2020-08-01 firmware/eppenwolf/protocols/microwave_spectrum.py_nw_.py

@@ -1,0 +1,5 @@
+alalsdjkf
+
+
+BASE_BIAS_GAINaa
+aa

### 2020-08-01 firmware/eppenwolf/src/VCO_driver.cpp

@@ -1,5 +1,10 @@
 #include "VCO_driver.hpp"
 
+
+#define LO_POWER_PIN 2
+#define LO_VARACTOR_PWM_PIN 3
+
+
 #define BASE_BIAS_PWM_PIN 9 //PWM
 #define VARACTOR_PWM_PIN 10 //PWM
 
@@ -28,6 +33,10 @@ void init_VCO(){
 
     //p-channel inverts!
     digitalWriteFast(PULSE_PIN, 1);
+
+
+    pinMode(LO_POWER_PIN, OUTPUT);
+    pinMode(LO_VARACTOR_PWM_PIN, OUTPUT);
 }
 
 
@@ -70,6 +79,20 @@ void set_VCO(float base_bias_voltage, float varactor_voltage, float supply_volta
     //now that's what I call convenience.
 
 }
+
+
+void LO_power(bool power){
+  digitalWrite(2, power);
+}
+
+void LO_tune(int target_voltage){
+
+    const int mosfet_threshold = 0.7;
+    const int supply = 15.0;
+    analogWrite(LO_VARACTOR_PWM_PIN, (ANALOG_WRITE_MAX_VAL - target_voltage) + ((mosfet_threshold / 3.3)*ANALOG_WRITE_MAX_VALUE));
+}
+
+
 
 // void get_current()
 

### 2020-08-01 firmware/eppenwolf/src/VCO_driver.hpp

@@ -19,6 +19,10 @@
 
 void init_VCO();
 void set_VCO(float base_bias_voltage, float varactor_voltage, float supply_voltage, bool power_state);
+
+void LO_power(bool power);
+void LO_tune(int target_voltage);
+
 // struct transistor_driver{
 //     String name = "";
 //

### 2020-08-01 firmware/eppenwolf/protocols/pulse_1.nw.tex
More noweb

\documentclass[paper.tex]{subfiles}% ===> this file was generated automatically by noweave --- better not edit it
\begin{document}

import device_comms
import sweep

\nwfilename{pulse_1.nw}\nwbegindocs{1}\nwdocspar
Our aims with this experiment are to perform the following:

Avoid any ambiguity regarding the temperature rise seen in the

\nwenddocs{}\nwbegindocs{2}\nwdocspar
Inspired by \cite{Biocoder2010}, we write the microbiology protocol directly into the Eppenwolf firmware using literate programming.

}

\nwenddocs{}\nwbegincode{3}\moddef{microwave_spectrum.py}\endmoddef\nwstartdeflinemarkup\nwenddeflinemarkup
alalsdjkf

test()
BASE_BIAS_GAINaa
aa

\nwendcode{}\nwbegindocs{4}aaaaaaaaaaaa

aaaaaaaaaaaaa

# T - 5 hours

# Phage+Bacteria / Bacteria-only / phage only?
# expose (parameters) / sham / thermal positives

# For each of the animal and human published studies, four
# predetermined and specific quality control measures were used to
# assess the quality of the publication.
# 1. Whether or not the researchers have used ‘‘blind’’ evaluations to
# avoid individual ‘‘bias’’, B or nB;
# 2. Whether or not there was detailed/adequate description of
# ‘‘dosimetry’’ in the publication for independent replication/
# confirmation studies, D or nD.
# 3. Whether or not ‘‘positive controls’’ were included in the
# experiment(s) to replicate/confirm the observations, P or nP.
# 4. Whether or not ‘‘sham-exposed controls’’ (more appropriate to
# compare with the observations made in RF exposure conditions)
# were included in the experiments, S or nS. However, it was not our
# intention to ‘‘rank’’ the publications either to exclude or include
# the reported data in the meta-analysis.

def initialize():
    # Name this run
    # Fluidic plate ID

    print("Fill phage into all selected cuvettes.")
    Simulataneously and separately

#centrifuge down bacteria lightly to concentrate
#Mix with fresh broth
#Vortex for X seconds?
#
# Rajnovic 2019
# Overnight cultures of E. coli were centrifuged and the pellets resuspended in 0.1 mM PB to
# achieve a concentration of 10^10 cfu/mL.
# The resulting suspensions were subject to serial dilution
#
# For each assay, 160 μL of LB were mixed with
# 20 μL phage solution, 20 μL of bacteria solution and 20μL of PB in

def bacteria_alone_control():
    //repeated twice

    # fill_phage()

def bacteria_and_phage_control():
    //repeated twice

def bacteria_and_inactivated_phage_positive_control():
    //

"Blank" repeatablity test with just water in all cuvettes

Add a small amount of growing e.coli to a new nutrient broth,
aerate vigorously, then add to culture chamber.

Expose phage.
Fill culture.
Monitor culture for log stage.
Mix culture and phage.
Monitor mixture.

Types of exposure:

RF

Expose phage, mix with log bacteria, monitor.

Bare

Sham

?

Positive control

Bring phage cuvette temperature to 120c with trace.

Autoclaved

\end{document}
\nwenddocs{}

### 2020-08-01 firmware/eppenwolf/protocols/microwave_spectrum.py

@@ -1,18 +1,1 @@
 
-@
-Our aims with this
-
-@
-Inspired by \cite{Biocoder2010}, we write the microbiology protocol directly into the Eppenwolf firmware.
-
-    log_serial.println(String(__FILE__));
-
-}
-
-
-<<microwave_spectrum.py>>=
-alalsdjkf
-
-
-BASE_BIAS_GAINaa
-aa

### 2020-08-01 firmware/eppenwolf/protocols/microwave_spectrum.py_nw_.py

@@ -1,5 +1,6 @@
 alalsdjkf
 
-
+test()
 BASE_BIAS_GAINaa
 aa
+

### 2020-08-01 firmware/eppenwolf/protocols/pulse_1.nw.tex
Noweb -> pweave

@@
 
-import device_comms
-import sweep
+\clearpage
+{\Large \it Experiment 2:}\\
 
@@
 
-Avoid any ambiguity regarding the temperature rise seen in the
+\begin{itemize}
+\item Crudely test the pulse hypothesis. \cite{Efficient2015}'s use of a 15 minute exposure caused us some consternation.
+    While T4 is quite unlike enveloped viruses, it at least provides a first approximation.
+\item Avoid any ambiguity regarding the temperature rise seen in the previous paper.
+\end{itemize}
+
+In the end, performing this was a mistake; but by the time we realized this we had already put in the bulk of the time.
+
+Inspired by \cite{Biocoder2010}, we write the microbiology protocol directly into the {\it Eppenwolf} firmware using \cite{Noweb}.
+
+<<pulse_1.py>>
+import device_comms
+import sweep
 
 \nwenddocs{}\nwbegindocs{2}\nwdocspar
-Inspired by \cite{Biocoder2010}, we write the microbiology protocol directly into the Eppenwolf firmware using literate programming.
-
-}
-
-\nwenddocs{}\nwbegincode{3}\moddef{microwave_spectrum.py}\endmoddef\nwstartdeflinemarkup\nwenddeflinemarkup
-alalsdjkf
-
-test()
-BASE_BIAS_GAINaa
-aa
-
-\nwendcode{}\nwbegindocs{4}aaaaaaaaaaaa
-
-aaaaaaaaaaaaa
 
@@
 
-# For each of the animal and human published studies, four
-# predetermined and specific quality control measures were used to
-# assess the quality of the publication.
-# 1. Whether or not the researchers have used ‘‘blind’’ evaluations to
-# avoid individual ‘‘bias’’, B or nB;
-# 2. Whether or not there was detailed/adequate description of
-# ‘‘dosimetry’’ in the publication for independent replication/
-# confirmation studies, D or nD.
-# 3. Whether or not ‘‘positive controls’’ were included in the
-# experiment(s) to replicate/confirm the observations, P or nP.
-# 4. Whether or not ‘‘sham-exposed controls’’ (more appropriate to
-# compare with the observations made in RF exposure conditions)
-# were included in the experiments, S or nS. However, it was not our
-# intention to ‘‘rank’’ the publications either to exclude or include
-# the reported data in the meta-analysis.
+For each of the animal and human published studies, four
+predetermined and specific quality control measures were used to
+assess the quality of the publication.
+1. Whether or not the researchers have used ‘‘blind’’ evaluations to
+avoid individual ‘‘bias’’, B or nB;
+2. Whether or not there was detailed/adequate description of
+‘‘dosimetry’’ in the publication for independent replication/
+confirmation studies, D or nD.
+3. Whether or not ‘‘positive controls’’ were included in the
+experiment(s) to replicate/confirm the observations, P or nP.
+4. Whether or not ‘‘sham-exposed controls’’ (more appropriate to
+compare with the observations made in RF exposure conditions)
+were included in the experiments, S or nS. However, it was not our
+intention to ‘‘rank’’ the publications either to exclude or include
+the reported data in the meta-analysis.
 

### 2020-08-01 documents/pulse_1.tex
Minted garbage

--- 2020-08-01 firmware/eppenwolf/protocols/pulse_1.nw.tex
@@
-\documentclass[paper.tex]{subfiles}% ===> this file was generated automatically by noweave --- better not edit it
+\documentclass[paper.tex]{subfiles}
 \begin{document}
@@
 
-\nwfilename{pulse_1.nw}\nwbegindocs{1}\nwdocspar
 Our aims with this experiment are to perform the following:
@@
 
-<<pulse_1.py>>
+\begin{minted}[mathescape, fontsize=\small, xleftmargin=0.5em]{python}
 import device_comms
 import sweep
-
-\nwenddocs{}\nwbegindocs{2}\nwdocspar
+\end{minted}
+\begin{minted}[fontsize=\small, xleftmargin=0.5em, mathescape, frame = leftline]{text}
+---------------------------------------------------------------------------ModuleNotFoundError
+Traceback (most recent call last)<ipython-input-1-821b060eb2e8> in
+<module>
+----> 1 import device_comms
+      2 import sweep
+ModuleNotFoundError: No module named 'device_comms'
+\end{minted}
 
@@
 # Phage+Bacteria / Bacteria-only / phage only?
+
 # expose (parameters) / sham / thermal positives
@@
 \end{document}
-\nwenddocs{}

### 2020-08-01 documents/microwave_spectrum.tex
SA test

\documentclass[paper.tex]{subfiles}% ===> this file was generated automatically by noweave --- better not edit it
\begin{document}

\clearpage
{\Large Experiment 1:}\\

\nwfilename{microwave_spectrum.pnw}\nwbegincode{1}\moddef{microwave_spectrum.py}\endmoddef\nwstartdeflinemarkup\nwenddeflinemarkup
import device_comms
import sweep
\nwendcode{}\nwbegindocs{2}\nwdocspar

\nwenddocs{}\nwbegincode{3}\moddef{}\endmoddef\nwstartdeflinemarkup\nwenddeflinemarkup

\nwendcode{}\nwbegindocs{4}\nwdocspar

\end{document}
\nwenddocs{}

### 2020-08-01 documents/pulse_1.tex
SA test

--- 2020-08-01 firmware/eppenwolf/protocols/pulse_1.nw.tex
@@
 
-<<pulse_1.py>>
+\nwfilename{pulse_1.pnw}\nwbegincode{1}\moddef{pulse_1.py}\endmoddef\nwstartdeflinemarkup\nwenddeflinemarkup
 import device_comms
@@
 
-\nwenddocs{}\nwbegindocs{2}\nwdocspar
-
-# T - 5 hours
-
-# Phage+Bacteria / Bacteria-only / phage only?
-# expose (parameters) / sham / thermal positives
+\nwendcode{}\nwbegindocs{2}\nwdocspar
 
@@
 the reported data in the meta-analysis.
+
+# T - 5 hours
+
+# Phage+Bacteria / Bacteria-only / phage only?
+
+# expose (parameters) / sham / thermal positives
 

### 2020-08-01 firmware/eppenwolf/protocols/compile.sh

@@ -10,10 +10,11 @@ filename="${filename%.*}"
 # git clone https://bitbucket.org/romildo/pygnoweb/
 # -filter $PWD/pygnoweb/pygnoweb.py
 
-# noweave  -latex -delay $1 > $1.tex
-# notangle -R$filename.py $1 > $1.py
+noweave  -latex -delay $1 > ../../../documents/$filename.tex
+notangle -R$filename.py $1 > $filename.py
+# cp pygnoweb/pygnoweb.sty ../../../documents/
+# cp pygnoweb/pygstyle.sty ../../../documents/
 #
-# cp $1.tex ../../../documents/
 
 # pweave $1 -o ../../../documents/$filename.tex -f texminted
 # pweave runs the file. This is highly unwanted.

### 2020-08-03 documents/pamphlet.tex
Noweb -> pweave
Minted garbage
SA test
Yay LO working, except we don't need it anymore

@@
 
-This is a condensed version of a (horribly unfinished) paper at \href{https://www.github.com/0xDBFB7/covidinator/documents/paper.pdf}{\faGithub/0xDBFB7/covidinator}.\footnote{Daniel Correia [TODO affiliation] \orcidlink{0000-0002-9353-0216}}
+This is a condensed version of a (horribly unfinished) paper at \href{https://www.github.com/0xDBFB7/covidinator/documents/paper.pdf}{\faGithub/0xDBFB7/covidinator}.\footnote{Daniel Correia [TODO: affiliation] \orcidlink{0000-0002-9353-0216}}
 
-Both the microwave and microbiology components of this field\footnote{field field?} appear to be unusually sensitive to experimental design and exceptionally prone to artifacts that cause false positive results: \cite{Microwave1982} $\neq$ \cite{Resonances1987}, \cite{Effects1985a} $\neq$ \cite{Cytogenetic1986}, \cite{Comprehensive2018}.
+%\subfile{pulse_1.tex}
+
+Both the microwave and microbiology components of this field appear to be unusually sensitive to experimental design and exceptionally prone to artifacts that cause false positive results: \cite{Microwave1982} $\neq$ \cite{Resonances1987}, \cite{Effects1985a} $\neq$ \cite{Cytogenetic1986}, \cite{Comprehensive2018}.
 Though the cited articles have taken care to avoid these effects, it is entirely possible that none of what is discussed below actually exists.
 
-This project was rushed and slow, terribly managed, and not nearly as rigorous as the field demands. This may well end up being a waste of time.
+Please distrust our analysis.
 
@@
 
+\begin{autem}
+	It should be noted that all of the claims we make hinge on this nanosecond inactivation.
+\cite{Efficient2015} and \cite{focusing2014} use a 15-minute exposure, which is apparently the norm for this field.
+\end{autem}
+
+{\Large \textbf{Advantages over existing techniques}}
+
+From crude attenuation data, this pulsed field can be safely produced at least 3 cm deep in tissue.
+This would seem to be unlike any other mechanisms like near or far\cite{Germicidal2017}UV.
+suitable for targeted sterilization of with bronchoscopic techniques), opening up a particularly interesting direct treatment modality.
+We are trying to verify this now with FDTD sims.
+
+Also unlike UV, the X-band is minimally attenuated by air; in the extreme, installations with megawatt-scale klystrons could potentially prevent airborne transmission in square-kilometer areas.
+
 {\Large \textbf{Is it safe?}}
@@
 
-If the above is correct, any region with a power density in the 7 to 9 GHz band greater than 300\Wsqm \ for 100 ns will be sterilized. (TODO field strength)
-
 This is not a particularly demanding requirement, and lends itself to a wide variety of applications, many of which could be implemented almost immediately.
-
-First, depending on the type of tissue, this field strength can apparently be safely produced a minimum of 3 cm deep (suitable for targeted sterilization of lungs or other organs with bronchoscopic techniques), up to 200 cm (eradicating the virus from the body) \cite{Physical1982}.
-We are working to narrow these bounds now.
 
@@
 This arguably wouldn't provide many advantages over simple masks, however.
-
-Unlike UV, the X-band is minimally attenuated by air. Common areas could be illuminated by magnetron systems.
-
-On the other extreme, installations with megawatt-scale klystrons could sterilize square-kilometer areas at a time.
-
-{\Large \textbf{Tasks}}
-
-We can see the following
-
-\begin{itemize}
-	\item To prevent duplication of work, are any other teams working on this now? It seems a rather obvious technique. A thorough review of arxiv etc should be performed.
-	\item Double-check all figures and assumptions.
-	\item Send off spectrometer (or, ideally, a more precise piece of equipment) to a BSL with a sample of NCoV to obtain the spectra and thresholds.
-	\item get the gosh-darned AustinMan voxel team to reply to my gosh-darned emails
-	\item Determine the ideal application to focus effort on
-	\item ???????
-	\item Check with the FCC/Industry Canada if we can get a temporary exemption for these intentional radiators?
-
-\end{itemize}
 

### 2020-08-03 firmware/eppenwolf/src/VCO_driver.cpp

@@ -59,7 +59,7 @@ void set_VCO(float base_bias_voltage, float varactor_voltage, float supply_volta
     //
     // base_bias_voltage = constrain(base_bias_voltage, 0, ANALOG_WRITE_MAX_VAL);
     // varactor_voltage = constrain(varactor_voltage, 0, ANALOG_WRITE_MAX_VAL);
-    supply_voltage = constrain(supply_voltage, 1.5, 6);
+    supply_voltage = constrain(supply_voltage, 1.5, 12);
 
     const float lm317_offset_voltage = 1.5;
     uint16_t base_bias_value = ((base_bias_voltage/BASE_BIAS_GAIN)/CORE_SUPPLY_VOLTAGE) * ANALOG_WRITE_MAX_VAL;
@@ -82,13 +82,17 @@ void set_VCO(float base_bias_voltage, float varactor_voltage, float supply_volta
 
 
 void LO_power(bool power){
-  digitalWrite(2, power);
+    // analogWriteFrequency(LO_VARACTOR_PWM_PIN, 50000.0);
+    debug_serial.printf("LO power set to %i\n", power);
+    digitalWrite(2, power);
 }
 
 void LO_tune(float value){
 
     const int mosfet_threshold = 0.7;
-    analogWrite(LO_VARACTOR_PWM_PIN, (ANALOG_WRITE_MAX_VAL - (value*ANALOG_WRITE_MAX_VAL)) + ((mosfet_threshold / 3.3)*ANALOG_WRITE_MAX_VAL));
+    int lo_val = (ANALOG_WRITE_MAX_VAL - (value*ANALOG_WRITE_MAX_VAL)) + ((mosfet_threshold / 3.3)*ANALOG_WRITE_MAX_VAL);
+    debug_serial.printf("LO tune set to %i\n", lo_val);
+    analogWrite(LO_VARACTOR_PWM_PIN, lo_val);
 }
 
 

### 2020-08-06 documents/paper.tex
Slide 1 done!
gosh writing papers is addictive, have to stop
Noweb -> pweave
VCO

@@
-% arara: pdflatex: { shell: yes } 
-% arara: biber
-% arara: pdflatex: { shell: yes }
-% arara: clean: { files: [ test.aux, test.log] }
-
 \documentclass[fleqn,10pt]{article}
@@
 
-We therefore demonstrate this form factor because, superficially, there are fewer people than there are places.
+We therere demonstrate this form factor because, superficially, there are fewer people than there are places.
 
@@
 
-It has been shown that virions can effect large-scale changes in the electric charges of their [].
+It has been shown that virions can effect large-scale changes in the electric charges of their \cite{Dynamics2010}.
 

### 2020-08-06 documents/supplemental.tex
Eppenwolf milled out
VCO

@@
 %\end{multicols}
+
+\PRLsep{{\itshape Virus structural data }}
+
+One extreme can be seen in
+
+Because CryoEM is sensitive to the
 
@@
 
-The frequency-dependent inactivation result in Figure 4b is difficult to explain without invoking non-thermal mechanisms. Only one  It is not mentioned how this applied power level was measured.
+The frequency-dependent inactivation result in Figure 4b of \cite{Efficient2015} is difficult to explain without invoking non-thermal mechanisms.
+Only one  It is not mentioned how this applied power level was measured.
 
@@
 
-\cite{EM6969}
-
 QPJ-06183640
 
-Similarly, the gain of the EM-6969 antenna varies from 17 dBi to 21 dBi over the frequency range in Figure 3.
+Similarly, the gain of the EM-6969 antenna\cite{EM6969} varies from 17 dBi to 21 dBi over the frequency range in Figure 3.
 
@@
 
+\PRLsep{{\itshape Wherein an oscillator is designed }}
+
+Three incorrect pieces of information conspired to lead us to try to develop an inexpensive ultrawideband oscillator.
+
+\begin{itemize}
+	\item The assumption that a broadband frequency sweep would drastically improve the inactivation threshold, and moreover that 
+	\item The ideal 
+	\item The assumption that the only YIG-tuned 
+\end{itemize}
+
+There are really two different conflicting criteria:
+
+A low-cost, wide-band
+
+Unfortunately, designing wideband microwave circuits is significantly more difficult than for a particular frequency. Quarter-wavelength
+
+Varactor diodes are a GaAs hyper-abrupt junction diode.
+
+We were warned that this would be difficult:
+
 CEL did not supply a SPICE model for the GaAs FET device used in early prototypes. A FET was originally because a gate is ostensibly easier to bias than a base; but this turned out to be unfounded.
@@
 
-OpenEMS is excellent, with Python bindings, some lumped components, and mesh refinement. However, embarassingly, we were not able to resolve all the dependency issues in order to install it.
-
-\PRLsep{{\itshape Wherein an oscillator is designed }}
-
-We did not discover how little of an effect a wideband sweep would have until late in the project; for this reason, much of the below caters towards wideband circuits and could be greatly simplified for single-frequency operation.
+OpenEMS is excellent, with Python bindings, some lumped components, and mesh refinement. However, embarrassingly, we were not able to resolve all the dependency issues in order to install it.
 

### 2020-08-06 firmware/eppenwolf/host/sweep.py

@@ -21,6 +21,11 @@ def create_freq_bins(start_freq, end_freq, bin_width):
 
 #pickle and save background?
 
+# class spectrum():
+#     def __init__(freqs):
+
+
+
 def run_sweep(freqs, bin_width, start_freq, end_freq, lna_gain, vga_gain, samples_per_freq):
     '''
     start_freq, end_freq: freq in MHz.
@@ -47,7 +52,7 @@ def run_sweep(freqs, bin_width, start_freq, end_freq, lna_gain, vga_gain, sample
     data = np.zeros_like(freqs)
     hits = np.zeros_like(freqs)
 
-    N_sweeps = 2
+    N_sweeps = 1
 
     # lna_gain = 0 + int(float(gain_db)/8.0)*8
     # vga_gain = 0 + int(float((gain_db/40.0)*62.0)/2.0)*2
@@ -63,11 +68,11 @@ def run_sweep(freqs, bin_width, start_freq, end_freq, lna_gain, vga_gain, sample
                 freq = (new_input[0] + ((new_input[1] - new_input[0]) / (len(new_input)-4))*i)
                 indice = np.abs(freqs - freq).argmin()
                 val = new_input[i+4]
-                if(not np.isnan(val) and np.isfinite(val)):
+                # if(not np.isnan(val) and np.isfinite(val)):
                     # hackrf_sweep does not seem to be totally deterministic.
                     # so we sort into bins.
-                    data[indice] = val
-                    hits[indice] = 1
+                data[indice] = val
+                hits[indice] = 1
                 # else:
                 #     data[indice] = 0
                 #     hits[indice] = 0
@@ -99,14 +104,18 @@ def peak_detect(data, freqs):
     # peak_indices = data.argsort()[-3:][::-1]
     # peak_freqs = freqs[peak_indices]
     # peak_values = data[peak_indices]
-    naughty = np.logical_or(np.isnan(data), np.isinf(data))
+    # naughty = np.logical_or(np.isnan(data), np.isinf(data))
+    data[data > 1000] = 0 # for some reason, isinf() checks don't work.
 
-    peak_indices = find_peaks(data[np.logical_not(naughty)])[0]
+    peak_indices = find_peaks(data)[0]
     peak_indices = (peak_indices[np.argsort(data[peak_indices])])[::-1]
+
+
+
     peak_freqs = freqs[peak_indices]
     peak_values = data[peak_indices]
 
-    return peak_freqs, peak_values
[…]

### 2020-08-12 documents/biology/biology.tex
Coplanar amp

\documentclass[11pt]{article}

    \usepackage[breakable]{tcolorbox}
    \usepackage{parskip} % Stop auto-indenting (to mimic markdown behaviour)

    \usepackage{iftex}
    \ifPDFTeX
    	\usepackage[T1]{fontenc}
    	\usepackage{mathpazo}
    \else
    	\usepackage{fontspec}
    \fi

    % Basic figure setup, for now with no caption control since it's done
    % automatically by Pandoc (which extracts ![](path) syntax from Markdown).
    \usepackage{graphicx}
    % Maintain compatibility with old templates. Remove in nbconvert 6.0
    \let\Oldincludegraphics\includegraphics
    % Ensure that by default, figures have no caption (until we provide a
    % proper Figure object with a Caption API and a way to capture that
    % in the conversion process - todo).
    \usepackage{caption}
    \DeclareCaptionFormat{nocaption}{}
    \captionsetup{format=nocaption,aboveskip=0pt,belowskip=0pt}

    \usepackage[Export]{adjustbox} % Used to constrain images to a maximum size
    \adjustboxset{max size={0.9\linewidth}{0.9\paperheight}}
    \usepackage{float}
    \floatplacement{figure}{H} % forces figures to be placed at the correct location
    \usepackage{xcolor} % Allow colors to be defined
    \usepackage{enumerate} % Needed for markdown enumerations to work
    \usepackage{geometry} % Used to adjust the document margins
    \usepackage{amsmath} % Equations
    \usepackage{amssymb} % Equations
    \usepackage{textcomp} % defines textquotesingle
    % Hack from http://tex.stackexchange.com/a/47451/13684:
    \AtBeginDocument{%
        \def\PYZsq{\textquotesingle}% Upright quotes in Pygmentized code
    }
    \usepackage{upquote} % Upright quotes for verbatim code
    \usepackage{eurosym} % defines \euro
    \usepackage[mathletters]{ucs} % Extended unicode (utf-8) support
    \usepackage{fancyvrb} % verbatim replacement that allows latex
    \usepackage{grffile} % extends the file name processing of package graphics 
                         % to support a larger range
    \makeatletter % fix for grffile with XeLaTeX
    \def\Gread@@xetex#1{%
      \IfFileExists{"\Gin@base".bb}%
      {\Gread@eps{\Gin@base.bb}}%
      {\Gread@@xetex@aux#1}%
    }
    \makeatother

    % The hyperref package gives us a pdf with properly built
    % internal navigation ('pdf bookmarks' for the table of contents,
    % internal cross-reference links, web links for URLs, etc.)
    \usepackage{hyperref}
    % The default LaTeX title has an obnoxious amount of whitespace. By default,
    % titling removes some of it. It also provides customization options.
    \usepackage{titling}
    \usepackage{longtable} % longtable support required by pandoc >1.10
    \usepackage{booktabs}  % table support for pandoc > 1.12.2
    \usepackage[inline]{enumitem} % IRkernel/repr support (it uses the enumerate* environment)
    \usepackage[normalem]{ulem} % ulem is needed to support strikethroughs (\sout)
                                % normalem makes italics be italics, not underlines
    \usepackage{mathrsfs}

    % Colors for the hyperref package
    \definecolor{urlcolor}{rgb}{0,.145,.698}
    \definecolor{linkcolor}{rgb}{.71,0.21,0.01}
    \definecolor{citecolor}{rgb}{.12,.54,.11}

    % ANSI colors
    \definecolor{ansi-black}{HTML}{3E424D}
    \definecolor{ansi-black-intense}{HTML}{282C36}
    \definecolor{ansi-red}{HTML}{E75C58}
    \definecolor{ansi-red-intense}{HTML}{B22B31}
    \definecolor{ansi-green}{HTML}{00A250}
    \definecolor{ansi-green-intense}{HTML}{007427}
    \definecolor{ansi-yellow}{HTML}{DDB62B}
    \definecolor{ansi-yellow-intense}{HTML}{B27D12}
    \definecolor{ansi-blue}{HTML}{208FFB}
    \definecolor{ansi-blue-intense}{HTML}{0065CA}
    \definecolor{ansi-magenta}{HTML}{D160C4}
    \definecolor{ansi-magenta-intense}{HTML}{A03196}
    \definecolor{ansi-cyan}{HTML}{60C6C8}
    \definecolor{ansi-cyan-intense}{HTML}{258F8F}
    \definecolor{ansi-white}{HTML}{C5C1B4}
    \definecolor{ansi-white-intense}{HTML}{A1A6B2}
    \definecolor{ansi-default-inverse-fg}{HTML}{FFFFFF}
    \definecolor{ansi-default-inverse-bg}{HTML}{000000}

    % commands and environments needed by pandoc snippets
    % extracted from the output of `pandoc -s`
    \providecommand{\tightlist}{%
      \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
    \DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
    % Add ',fontsize=\small' for more characters per line
    \newenvironment{Shaded}{}{}
    \newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{{#1}}}}
    \newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.56,0.13,0.00}{{#1}}}
    \newcommand{\DecValTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
    \newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
    \newcommand{\FloatTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
    \newcommand{\CharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
    \newcommand{\StringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
    \newcommand{\CommentTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textit{{#1}}}}
    \newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{{#1}}}
    \newcommand{\AlertTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{{#1}}}}
    \newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.02,0.16,0.49}{{#1}}}
    \newcommand{\RegionMarkerTok}[1]{{#1}}
    \newcommand{\ErrorTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{{#1}}}}
    \newcommand{\NormalTok}[1]{{#1}}

    % Additional commands for more recent versions of Pandoc
    \newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.53,0.00,0.00}{{#1}}}
    \newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
    \newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
    \newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.73,0.40,0.53}{{#1}}}
    \newcommand{\ImportTok}[1]{{#1}}
    \newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.73,0.13,0.13}{\textit{{#1}}}}
    \newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{{#1}}}}}
    \newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{{#1}}}}}
    \newcommand{\VariableTok}[1]{\textcolor[rgb]{0.10,0.09,0.49}{{#1}}}
    \newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{{#1}}}}
    \newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.40,0.40,0.40}{{#1}}}
    \newcommand{\BuiltInTok}[1]{{#1}}
    \newcommand{\ExtensionTok}[1]{{#1}}
    \newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.74,0.48,0.00}{{#1}}}
    \newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.49,0.56,0.16}{{#1}}}
    \newcommand{\InformationTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{{#1}}}}}
    \newcommand{\WarningTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{{#1}}}}}

    % Define a nice break command that doesn't care if a line doesn't already
    % exist.
    \def\br{\hspace*{\fill} \\* }
    % Math Jax compatibility definitions
    \def\gt{>}
    \def\lt{<}
    \let\Oldtex\TeX
    \let\Oldlatex\LaTeX
    \renewcommand{\TeX}{\textrm{\Oldtex}}
    \renewcommand{\LaTeX}{\textrm{\Oldlatex}}
    % Document parameters
    % Document title
    \title{biology}

% Pygments definitions
\makeatletter
\def\PY@reset{\let\PY@it=\relax \let\PY@bf=\relax%
    \let\PY@ul=\relax \let\PY@tc=\relax%
    \let\PY@bc=\relax \let\PY@ff=\relax}
\def\PY@tok#1{\csname PY@tok@#1\endcsname}
\def\PY@toks#1+{\ifx\relax#1\empty\else%
    \PY@tok{#1}\expandafter\PY@toks\fi}
\def\PY@do#1{\PY@bc{\PY@tc{\PY@ul{%
    \PY@it{\PY@bf{\PY@ff{#1}}}}}}}
\def\PY#1#2{\PY@reset\PY@toks#1+\relax+\PY@do{#2}}

\expandafter\def\csname PY@tok@w\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.73,0.73}{##1}}}
\expandafter\def\csname PY@tok@c\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@cp\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.74,0.48,0.00}{##1}}}
\expandafter\def\csname PY@tok@k\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@kp\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@kt\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.69,0.00,0.25}{##1}}}
\expandafter\def\csname PY@tok@o\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@ow\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.67,0.13,1.00}{##1}}}
\expandafter\def\csname PY@tok@nb\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@nf\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\expandafter\def\csname PY@tok@nc\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\expandafter\def\csname PY@tok@nn\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\expandafter\def\csname PY@tok@ne\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.82,0.25,0.23}{##1}}}
\expandafter\def\csname PY@tok@nv\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@no\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.53,0.00,0.00}{##1}}}
\expandafter\def\csname PY@tok@nl\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.63,0.63,0.00}{##1}}}
\expandafter\def\csname PY@tok@ni\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.60,0.60,0.60}{##1}}}
\expandafter\def\csname PY@tok@na\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.49,0.56,0.16}{##1}}}
\expandafter\def\csname PY@tok@nt\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@nd\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.67,0.13,1.00}{##1}}}
\expandafter\def\csname PY@tok@s\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@sd\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@si\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.73,0.40,0.53}{##1}}}
\expandafter\def\csname PY@tok@se\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.73,0.40,0.13}{##1}}}
\expandafter\def\csname PY@tok@sr\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.40,0.53}{##1}}}
\expandafter\def\csname PY@tok@ss\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@sx\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@m\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@gh\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,0.50}{##1}}}
\expandafter\def\csname PY@tok@gu\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.50,0.00,0.50}{##1}}}
\expandafter\def\csname PY@tok@gd\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.63,0.00,0.00}{##1}}}
\expandafter\def\csname PY@tok@gi\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.63,0.00}{##1}}}
\expandafter\def\csname PY@tok@gr\endcsname{\def\PY@tc##1{\textcolor[rgb]{1.00,0.00,0.00}{##1}}}
\expandafter\def\csname PY@tok@ge\endcsname{\let\PY@it=\textit}
\expandafter\def\csname PY@tok@gs\endcsname{\let\PY@bf=\textbf}
\expandafter\def\csname PY@tok@gp\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,0.50}{##1}}}
\expandafter\def\csname PY@tok@go\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.53,0.53,0.53}{##1}}}
\expandafter\def\csname PY@tok@gt\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.27,0.87}{##1}}}
\expandafter\def\csname PY@tok@err\endcsname{\def\PY@bc##1{\setlength{\fboxsep}{0pt}\fcolorbox[rgb]{1.00,0.00,0.00}{1,1,1}{\strut ##1}}}
\expandafter\def\csname PY@tok@kc\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@kd\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@kn\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@kr\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@bp\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@fm\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\expandafter\def\csname PY@tok@vc\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@vg\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@vi\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@vm\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@sa\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@sb\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@sc\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@dl\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@s2\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@sh\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@s1\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@mb\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@mf\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@mh\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@mi\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@il\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@mo\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@ch\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@cm\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@cpf\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@c1\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@cs\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}

\def\PYZbs{\char`\\}
\def\PYZus{\char`\_}
\def\PYZob{\char`\{}
\def\PYZcb{\char`\}}
\def\PYZca{\char`\^}
\def\PYZam{\char`\&}
\def\PYZlt{\char`\<}
\def\PYZgt{\char`\>}
\def\PYZsh{\char`\#}
\def\PYZpc{\char`\%}
\def\PYZdl{\char`\$}
\def\PYZhy{\char`\-}
\def\PYZsq{\char`\'}
\def\PYZdq{\char`\"}
\def\PYZti{\char`\~}
% for compatibility with earlier versions
\def\PYZat{@}
\def\PYZlb{[}
\def\PYZrb{]}
\makeatother

    % For linebreaks inside Verbatim environment from package fancyvrb. 
    \makeatletter
        \newbox\Wrappedcontinuationbox 
        \newbox\Wrappedvisiblespacebox 
        \newcommand*\Wrappedvisiblespace {\textcolor{red}{\textvisiblespace}} 
        \newcommand*\Wrappedcontinuationsymbol {\textcolor{red}{\llap{\tiny$\m@th\hookrightarrow$}}} 
        \newcommand*\Wrappedcontinuationindent {3ex } 
        \newcommand*\Wrappedafterbreak {\kern\Wrappedcontinuationindent\copy\Wrappedcontinuationbox} 
        % Take advantage of the already applied Pygments mark-up to insert 
        % potential linebreaks for TeX processing. 
        %        {, <, #, %, $, ' and ": go to next line. 
        %        _, }, ^, &, >, - and ~: stay at end of broken line. 
        % Use of \textquotesingle for straight quote. 
        \newcommand*\Wrappedbreaksatspecials {% 
            \def\PYGZus{\discretionary{\char`\_}{\Wrappedafterbreak}{\char`\_}}% 
            \def\PYGZob{\discretionary{}{\Wrappedafterbreak\char`\{}{\char`\{}}% 
            \def\PYGZcb{\discretionary{\char`\}}{\Wrappedafterbreak}{\char`\}}}% 
            \def\PYGZca{\discretionary{\char`\^}{\Wrappedafterbreak}{\char`\^}}% 
            \def\PYGZam{\discretionary{\char`\&}{\Wrappedafterbreak}{\char`\&}}% 
            \def\PYGZlt{\discretionary{}{\Wrappedafterbreak\char`\<}{\char`\<}}% 
            \def\PYGZgt{\discretionary{\char`\>}{\Wrappedafterbreak}{\char`\>}}% 
            \def\PYGZsh{\discretionary{}{\Wrappedafterbreak\char`\#}{\char`\#}}% 
            \def\PYGZpc{\discretionary{}{\Wrappedafterbreak\char`\%}{\char`\%}}% 
            \def\PYGZdl{\discretionary{}{\Wrappedafterbreak\char`\$}{\char`\$}}% 
            \def\PYGZhy{\discretionary{\char`\-}{\Wrappedafterbreak}{\char`\-}}% 
            \def\PYGZsq{\discretionary{}{\Wrappedafterbreak\textquotesingle}{\textquotesingle}}% 
            \def\PYGZdq{\discretionary{}{\Wrappedafterbreak\char`\"}{\char`\"}}% 
            \def\PYGZti{\discretionary{\char`\~}{\Wrappedafterbreak}{\char`\~}}% 
        } 
        % Some characters . , ; ? ! / are not pygmentized. 
        % This macro makes them "active" and they will insert potential linebreaks 
        \newcommand*\Wrappedbreaksatpunct {% 
            \lccode`\~`\.\lowercase{\def~}{\discretionary{\hbox{\char`\.}}{\Wrappedafterbreak}{\hbox{\char`\.}}}% 
            \lccode`\~`\,\lowercase{\def~}{\discretionary{\hbox{\char`\,}}{\Wrappedafterbreak}{\hbox{\char`\,}}}% 
            \lccode`\~`\;\lowercase{\def~}{\discretionary{\hbox{\char`\;}}{\Wrappedafterbreak}{\hbox{\char`\;}}}% 
            \lccode`\~`\:\lowercase{\def~}{\discretionary{\hbox{\char`\:}}{\Wrappedafterbreak}{\hbox{\char`\:}}}% 
            \lccode`\~`\?\lowercase{\def~}{\discretionary{\hbox{\char`\?}}{\Wrappedafterbreak}{\hbox{\char`\?}}}% 
            \lccode`\~`\!\lowercase{\def~}{\discretionary{\hbox{\char`\!}}{\Wrappedafterbreak}{\hbox{\char`\!}}}% 
            \lccode`\~`\/\lowercase{\def~}{\discretionary{\hbox{\char`\/}}{\Wrappedafterbreak}{\hbox{\char`\/}}}% 
            \catcode`\.\active
            \catcode`\,\active 
            \catcode`\;\active
            \catcode`\:\active
            \catcode`\?\active
            \catcode`\!\active
            \catcode`\/\active 
            \lccode`\~`\~ 	
        }
    \makeatother

    \let\OriginalVerbatim=\Verbatim
    \makeatletter
    \renewcommand{\Verbatim}[1][1]{%
        %\parskip\z@skip
        \sbox\Wrappedcontinuationbox {\Wrappedcontinuationsymbol}%
        \sbox\Wrappedvisiblespacebox {\FV@SetupFont\Wrappedvisiblespace}%
        \def\FancyVerbFormatLine ##1{\hsize\linewidth
            \vtop{\raggedright\hyphenpenalty\z@\exhyphenpenalty\z@
                \doublehyphendemerits\z@\finalhyphendemerits\z@
                \strut ##1\strut}%
        }%
        % If the linebreak is at a space, the latter will be displayed as visible
        % space at end of first line, and a continuation symbol starts next line.
        % Stretch/shrink are however usually zero for typewriter font.
        \def\FV@Space {%
            \nobreak\hskip\z@ plus\fontdimen3\font minus\fontdimen4\font
            \discretionary{\copy\Wrappedvisiblespacebox}{\Wrappedafterbreak}
            {\kern\fontdimen2\font}%
        }%

        % Allow breaks at special characters using \PYG... macros.
        \Wrappedbreaksatspecials
        % Breaks at punctuation characters . , ; ? ! and / need catcode=\active 	
        \OriginalVerbatim[#1,codes*=\Wrappedbreaksatpunct]%
    }
    \makeatother

    % Exact colors from NB
    \definecolor{incolor}{HTML}{303F9F}
    \definecolor{outcolor}{HTML}{D84315}
    \definecolor{cellborder}{HTML}{CFCFCF}
    \definecolor{cellbackground}{HTML}{F7F7F7}

    % prompt
    \makeatletter
    \newcommand{\boxspacing}{\kern\kvtcb@left@rule\kern\kvtcb@boxsep}
    \makeatother
    \newcommand{\prompt}[4]{
        \ttfamily\llap{{\color{#2}[#3]:\hspace{3pt}#4}}\vspace{-\baselineskip}
    }

    % Prevent overflowing lines due to hard-to-break entities
    \sloppy 
    % Setup hyperref package
    \hypersetup{
      breaklinks=true,  % so long urls are correctly broken across lines
      colorlinks=true,
      urlcolor=urlcolor,
      linkcolor=linkcolor,
      citecolor=citecolor,
      }
    % Slightly bigger margins than the latex defaults

    \geometry{verbose,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}

\begin{document}

    \maketitle

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{1}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{k+kn}{from} \PY{n+nn}{math} \PY{k+kn}{import} \PY{n}{pi}\PY{p}{,} \PY{n}{sqrt}
\PY{k+kn}{from} \PY{n+nn}{scipy}\PY{n+nn}{.}\PY{n+nn}{optimize} \PY{k+kn}{import} \PY{n}{curve\PYZus{}fit}
\PY{k+kn}{import} \PY{n+nn}{numpy} \PY{k}{as} \PY{n+nn}{np}
\PY{k+kn}{import} \PY{n+nn}{matplotlib}\PY{n+nn}{.}\PY{n+nn}{pyplot} \PY{k}{as} \PY{n+nn}{plt}
\PY{k+kn}{from} \PY{n+nn}{scipy}\PY{n+nn}{.}\PY{n+nn}{constants} \PY{k+kn}{import} \PY{n}{elementary\PYZus{}charge}
\PY{k+kn}{from} \PY{n+nn}{pytexit} \PY{k+kn}{import} \PY{n}{py2tex}
\PY{k+kn}{from} \PY{n+nn}{scipy}\PY{n+nn}{.}\PY{n+nn}{stats} \PY{k+kn}{import} \PY{n}{gaussian\PYZus{}kde}
\PY{k+kn}{from} \PY{n+nn}{tabulate} \PY{k+kn}{import} \PY{n}{tabulate}

\PY{n}{MDa} \PY{o}{=} \PY{l+m+mf}{1.6605e\PYZhy{}21} \PY{c+c1}{\PYZsh{}kg}
\PY{n}{nm} \PY{o}{=} \PY{l+m+mf}{1e\PYZhy{}9}
\end{Verbatim}
\end{tcolorbox}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{2}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{c+c1}{\PYZsh{}[Lauffer 1944]: diameter 109 +/\PYZhy{} 16.65 nm}
\PY{c+c1}{\PYZsh{}[Ruigrok 1984]: diameter 115 +/\PYZhy{} 12 nm}

\PY{n}{mean\PYZus{}diameter} \PY{o}{=} \PY{p}{(}\PY{l+m+mf}{109.0}\PY{o}{+}\PY{l+m+mf}{115.0}\PY{p}{)}\PY{o}{/}\PY{l+m+mf}{2.0}

\PY{n}{sigma\PYZus{}diameter} \PY{o}{=} \PY{p}{(}\PY{l+m+mf}{16.65}\PY{o}{+}\PY{l+m+mi}{12}\PY{p}{)}\PY{o}{/}\PY{l+m+mf}{2.0} \PY{c+c1}{\PYZsh{}average}

\PY{c+c1}{\PYZsh{}[Ruigrok 1984]: mass 160 MDa +/\PYZhy{} 17 MDa}
\PY{n}{sigma\PYZus{}mass} \PY{o}{=} \PY{p}{(}\PY{l+m+mf}{17.0}\PY{o}{+}\PY{l+m+mf}{24.0}\PY{p}{)}\PY{o}{/}\PY{l+m+mf}{2.0}

\PY{n}{mean\PYZus{}mass} \PY{o}{=} \PY{l+m+mi}{160}
\end{Verbatim}
\end{tcolorbox}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{3}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{c+c1}{\PYZsh{}check if variation in  variation in volume corresponds to the variation in mass}
\PY{c+c1}{\PYZsh{} mass is only }
\PY{n}{avg\PYZus{}radius} \PY{o}{=} \PY{l+m+mf}{57.5} 
\PY{n}{one\PYZus{}sigma\PYZus{}pos\PYZus{}rad} \PY{o}{=} \PY{n}{avg\PYZus{}radius} \PY{o}{+} \PY{p}{(}\PY{n}{sigma\PYZus{}diameter}\PY{o}{/}\PY{l+m+mf}{2.0}\PY{p}{)}
\PY{n}{volume\PYZus{}sigma} \PY{o}{=} \PY{p}{(}\PY{p}{(}\PY{p}{(}\PY{l+m+mi}{4}\PY{o}{/}\PY{l+m+mf}{3.0}\PY{p}{)} \PY{o}{*} \PY{n}{pi} \PY{o}{*} \PY{p}{(}\PY{n}{one\PYZus{}sigma\PYZus{}pos\PYZus{}rad}\PY{p}{)}\PY{o}{*}\PY{o}{*}\PY{l+m+mf}{2.0}\PY{p}{)}\PY{o}{/}\PY{p}{(}\PY{p}{(}\PY{l+m+mi}{4}\PY{o}{/}\PY{l+m+mf}{3.0}\PY{p}{)} \PY{o}{*} \PY{n}{pi} \PY{o}{*} \PY{p}{(}\PY{n}{avg\PYZus{}radius}\PY{p}{)}\PY{o}{*}\PY{o}{*}\PY{l+m+mf}{2.0}\PY{p}{)}\PY{p}{)}\PY{o}{\PYZhy{}}\PY{l+m+mf}{1.0}
\PY{n}{volume\PYZus{}sigma}
\PY{n}{avg\PYZus{}mass} \PY{o}{=} \PY{l+m+mf}{75.0}
\PY{n}{vol\PYZus{}one\PYZus{}sigma\PYZus{}mass} \PY{o}{=} \PY{n}{avg\PYZus{}mass}\PY{o}{*}\PY{n}{volume\PYZus{}sigma}
\PY{n}{vol\PYZus{}one\PYZus{}sigma\PYZus{}mass}
\PY{c+c1}{\PYZsh{}it doesn\PYZsq{}t}
\end{Verbatim}
\end{tcolorbox}

            \begin{tcolorbox}[breakable, size=fbox, boxrule=.5pt, pad at break*=1mm, opacityfill=0]
\prompt{Out}{outcolor}{3}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
19.84851961247638
\end{Verbatim}
\end{tcolorbox}

    We know the variation in the diameter and therefore that in the volume.
There is, surprisingly, almost no variation in the total spike mass, so
we subtract that first. We would expect \(\sigma = 19.8\) MDa variation
if volume and mass were proportional, and see \(\sigma = 17\) MDa of
variation.

We therefore assume that mass and volume are proportional.

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{ }{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]

\end{Verbatim}
\end{tcolorbox}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{4}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{c+c1}{\PYZsh{}Extracted from [Li 2011] using https://apps.automeris.io/wpd/,}

\PY{c+c1}{\PYZsh{} count = np.array([2.9816513761467904,}
\PY{c+c1}{\PYZsh{} 6.0091743119266035,}
\PY{c+c1}{\PYZsh{} 15.045871559633028,}
\PY{c+c1}{\PYZsh{} 21.14678899082569,}
\PY{c+c1}{\PYZsh{} 17.93577981651376,}
\PY{c+c1}{\PYZsh{} 11.10091743119266,}
\PY{c+c1}{\PYZsh{} 11.972477064220184,}
\PY{c+c1}{\PYZsh{} 11.972477064220184,}
\PY{c+c1}{\PYZsh{} 15.458715596330272,}
\PY{c+c1}{\PYZsh{} 8.119266055045873,}
\PY{c+c1}{\PYZsh{} 19.174311926605505,}
\PY{c+c1}{\PYZsh{} 9.908256880733944,}
\PY{c+c1}{\PYZsh{} 6.834862385321103,}
\PY{c+c1}{\PYZsh{} 5.045871559633027,}
\PY{c+c1}{\PYZsh{} 7.018348623853214,}
\PY{c+c1}{\PYZsh{} 2.018348623853214,}
\PY{c+c1}{\PYZsh{} 1.0091743119266046])}

\PY{n}{breaking\PYZus{}force\PYZus{}count} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{p}{[} \PY{l+m+mf}{3.}\PY{p}{,}  \PY{l+m+mf}{6.}\PY{p}{,} \PY{l+m+mf}{15.}\PY{p}{,} \PY{l+m+mf}{21.}\PY{p}{,} \PY{l+m+mf}{18.}\PY{p}{,} \PY{l+m+mf}{11.}\PY{p}{,} \PY{l+m+mf}{12.}\PY{p}{,} \PY{l+m+mf}{12.}\PY{p}{,} \PY{l+m+mf}{15.}\PY{p}{,}  \PY{l+m+mf}{8.}\PY{p}{,} \PY{l+m+mf}{19.}\PY{p}{,} \PY{l+m+mf}{10.}\PY{p}{,}  \PY{l+m+mf}{7.}\PY{p}{,}
        \PY{l+m+mf}{5.}\PY{p}{,}  \PY{l+m+mf}{7.}\PY{p}{,}  \PY{l+m+mf}{2.}\PY{p}{,}  \PY{l+m+mf}{1.}\PY{p}{]}\PY{p}{)} \PY{c+c1}{\PYZsh{}rounded}

\PY{n}{breaking\PYZus{}force\PYZus{}bins} \PY{o}{=} \PY{p}{[}\PY{l+m+mf}{0.24179620034542312}\PY{p}{,}
\PY{l+m+mf}{0.33851468048359246}\PY{p}{,}
\PY{l+m+mf}{0.4421416234887737}\PY{p}{,}
\PY{l+m+mf}{0.5423143350604491}\PY{p}{,}
\PY{l+m+mf}{0.6528497409326425}\PY{p}{,}
\PY{l+m+mf}{0.753022452504318}\PY{p}{,}
\PY{l+m+mf}{0.8186528497409327}\PY{p}{,}
\PY{l+m+mf}{0.9395509499136444}\PY{p}{,}
\PY{l+m+mf}{1.0466321243523315}\PY{p}{,}
\PY{l+m+mf}{1.143350604490501}\PY{p}{,}
\PY{l+m+mf}{1.2469775474956826}\PY{p}{,}
\PY{l+m+mf}{1.3506044905008636}\PY{p}{,}
\PY{l+m+mf}{1.4300518134715028}\PY{p}{,}
\PY{l+m+mf}{1.5474956822107082}\PY{p}{,}
\PY{l+m+mf}{1.6165803108808294}\PY{p}{,}
\PY{l+m+mf}{1.7305699481865287}\PY{p}{,}
\PY{l+m+mf}{1.9412780656303976}\PY{p}{]} \PY{c+c1}{\PYZsh{} bin midpoints}
\end{Verbatim}
\end{tcolorbox}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{5}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{n}{N} \PY{o}{=} \PY{l+m+mi}{5000}
\end{Verbatim}
\end{tcolorbox}

    \hypertarget{fitting-breaking-force-with-gaussian---doesnt-work-particularly-well}{%
\subsubsection{Fitting breaking force with gaussian - doesn't work
particularly
well}\label{fitting-breaking-force-with-gaussian---doesnt-work-particularly-well}}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{6}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{k}{def} \PY{n+nf}{gaussian}\PY{p}{(}\PY{n}{x}\PY{p}{,} \PY{n}{mean}\PY{p}{,} \PY{n}{amplitude}\PY{p}{,} \PY{n}{standard\PYZus{}deviation}\PY{p}{)}\PY{p}{:}
    \PY{k}{return} \PY{n}{amplitude} \PY{o}{*} \PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(} \PY{o}{\PYZhy{}} \PY{p}{(}\PY{p}{(}\PY{n}{x} \PY{o}{\PYZhy{}} \PY{n}{mean}\PY{p}{)} \PY{o}{/} \PY{n}{standard\PYZus{}deviation}\PY{p}{)} \PY{o}{*}\PY{o}{*} \PY{l+m+mi}{2}\PY{p}{)}

\PY{n}{popt}\PY{p}{,} \PY{n}{\PYZus{}} \PY{o}{=} \PY{n}{curve\PYZus{}fit}\PY{p}{(}\PY{n}{gaussian}\PY{p}{,} \PY{n}{breaking\PYZus{}force\PYZus{}bins}\PY{p}{,} \PY{n}{breaking\PYZus{}force\PYZus{}count}\PY{p}{)}
\PY{n}{mean\PYZus{}breaking\PYZus{}force} \PY{o}{=} \PY{n}{popt}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]}
\PY{n}{sigma\PYZus{}breaking\PYZus{}force} \PY{o}{=} \PY{n+nb}{abs}\PY{p}{(}\PY{n}{popt}\PY{p}{[}\PY{l+m+mi}{2}\PY{p}{]}\PY{p}{)} \PY{c+c1}{\PYZsh{}curve\PYZus{}fit can sometimes return negative.}

\PY{n+nb}{print}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Liposome breaking force mean=}\PY{l+s+si}{\PYZob{}:.3f\PYZcb{}}\PY{l+s+s2}{ sigma=}\PY{l+s+si}{\PYZob{}:.3f\PYZcb{}}\PY{l+s+s2}{ pN}\PY{l+s+s2}{\PYZdq{}}\PY{o}{.}\PY{n}{format}\PY{p}{(}\PY{n}{mean\PYZus{}breaking\PYZus{}force}\PY{p}{,} \PY{n}{sigma\PYZus{}breaking\PYZus{}force}\PY{p}{)}\PY{p}{)}

\PY{c+c1}{\PYZsh{}this could also include some of the non\PYZhy{}infective mutants}
\end{Verbatim}
\end{tcolorbox}

    \begin{Verbatim}[commandchars=\\\{\}]
Liposome breaking force mean=0.839 sigma=0.733 pN
    \end{Verbatim}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{7}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{c+c1}{\PYZsh{}overriding with tweaked values because non\PYZhy{}bimodal}
\PY{c+c1}{\PYZsh{} mean\PYZus{}breaking\PYZus{}force = 0.839}
\PY{c+c1}{\PYZsh{} sigma\PYZus{}breaking\PYZus{}force = 0.45}
\end{Verbatim}
\end{tcolorbox}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{8}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{n}{weights} \PY{o}{=} \PY{p}{(}\PY{n}{breaking\PYZus{}force\PYZus{}count}\PY{o}{/}\PY{n}{np}\PY{o}{.}\PY{n}{sum}\PY{p}{(}\PY{n}{breaking\PYZus{}force\PYZus{}count}\PY{p}{)}\PY{p}{)}
\PY{n}{resamples} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{random}\PY{o}{.}\PY{n}{choice}\PY{p}{(}\PY{n}{breaking\PYZus{}force\PYZus{}bins}\PY{p}{,} \PY{n}{size}\PY{o}{=}\PY{n}{N}\PY{p}{,} \PY{n}{p}\PY{o}{=}\PY{n}{weights}\PY{p}{)}

\PY{n}{breaking\PYZus{}force\PYZus{}kernel} \PY{o}{=} \PY{n}{gaussian\PYZus{}kde}\PY{p}{(}\PY{n}{resamples}\PY{p}{)}
\PY{c+c1}{\PYZsh{} breaking\PYZus{}force\PYZus{}kernel.set\PYZus{}bandwidth(0.5)}
\end{Verbatim}
\end{tcolorbox}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{9}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{n}{mean\PYZus{}charge} \PY{o}{=} \PY{l+m+mf}{1e7}
\PY{n}{sigma\PYZus{}charge} \PY{o}{=} \PY{l+m+mf}{1e5} \PY{c+c1}{\PYZsh{}placeholder \PYZhy{} fixme}
\end{Verbatim}
\end{tcolorbox}

    Now we run into a problem. We don't know the dependence of k, the spring
constant, on any of the parameters in an actual virus. It is determined
by the strength of the intermolecular forces and is a free parameter.

From {[}Li 2011{]}, Figure 3a we see that the empty liposome stiffness
is negatively correlated with size; but the stiffness of the empty
liposome appears to be hundreds of times smaller than that of the full
virion.

From running ensembles with different values of k\_sigma, while the
distribution of the resonant frequencies is very sensitive to this
parameter, the inactivation threshold is not; so we guess a resonable
figure.

Figure 4b in Yang is dependent on k vs f\_res, and the overall
absorption cross-section data in Figure 3b includes the sum of all the
absorption cross-sections of all the variance. It is likely possible to
extract the remaining data from these plots; but, since none of this is
applicable to SARS-NCoV, this exceeds our patience.

The upshot is that all the resonant frequency distributions below are
just guesses.

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{10}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{n}{mean\PYZus{}mu} \PY{o}{=} \PY{l+m+mf}{14.5} \PY{o}{*} \PY{n}{MDa} 
\PY{n}{mean\PYZus{}k} \PY{o}{=} \PY{p}{(}\PY{p}{(}\PY{l+m+mf}{2.0} \PY{o}{*} \PY{n}{pi} \PY{o}{*} \PY{l+m+mf}{8.2e9}\PY{p}{)}\PY{o}{*}\PY{o}{*}\PY{l+m+mf}{2.0}\PY{p}{)} \PY{o}{*} \PY{n}{mean\PYZus{}mu} \PY{c+c1}{\PYZsh{}from [Yang]}

\PY{n}{sigma\PYZus{}spring\PYZus{}constant} \PY{o}{=} \PY{p}{(}\PY{l+m+mf}{0.07}\PY{o}{*}\PY{n}{mean\PYZus{}k}\PY{p}{)}\PY{o}{/}\PY{n}{sigma\PYZus{}diameter} \PY{c+c1}{\PYZsh{} nN / nm}
\end{Verbatim}
\end{tcolorbox}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{11}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{n}{means} \PY{o}{=} \PY{p}{[}\PY{n}{mean\PYZus{}diameter}\PY{p}{,} \PY{n}{mean\PYZus{}mass}\PY{p}{,} \PY{n}{mean\PYZus{}breaking\PYZus{}force}\PY{p}{,} \PY{n}{mean\PYZus{}charge}\PY{p}{,} \PY{n}{mean\PYZus{}k}\PY{p}{]} \PY{c+c1}{\PYZsh{}oh he\PYZsq{}s got the means all right.}

\PY{n}{var\PYZus{}diameter} \PY{o}{=} \PY{p}{(}\PY{n}{sigma\PYZus{}diameter}\PY{o}{*}\PY{o}{*}\PY{l+m+mf}{2.0}\PY{p}{)} \PY{c+c1}{\PYZsh{}variance is the square of the standard deviation.}
\PY{n}{var\PYZus{}mass} \PY{o}{=} \PY{p}{(}\PY{n}{sigma\PYZus{}mass}\PY{o}{*}\PY{o}{*}\PY{l+m+mf}{2.0}\PY{p}{)} \PY{c+c1}{\PYZsh{}inertia is a property of matter.}
\PY{n}{var\PYZus{}breaking\PYZus{}force} \PY{o}{=} \PY{p}{(}\PY{n}{sigma\PYZus{}breaking\PYZus{}force}\PY{o}{*}\PY{o}{*}\PY{l+m+mf}{2.0}\PY{p}{)}
\PY{n}{var\PYZus{}charge} \PY{o}{=} \PY{p}{(}\PY{n}{sigma\PYZus{}charge}\PY{o}{*}\PY{o}{*}\PY{l+m+mf}{2.0}\PY{p}{)}
\PY{n}{var\PYZus{}spring\PYZus{}constant} \PY{o}{=} \PY{p}{(}\PY{n}{sigma\PYZus{}spring\PYZus{}constant}\PY{o}{*}\PY{o}{*}\PY{l+m+mf}{2.0}\PY{p}{)}

\PY{c+c1}{\PYZsh{}diameter varies with diameter, varies with mass, with breaking force, and with charge}
\PY{n}{cov\PYZus{}diameter} \PY{o}{=}        \PY{p}{[}\PY{n}{var\PYZus{}diameter}\PY{p}{,} \PY{n}{sigma\PYZus{}diameter}\PY{o}{*}\PY{n}{sigma\PYZus{}mass}\PY{o}{*}\PY{l+m+mf}{0.95}\PY{p}{,} \PY{l+m+mi}{0}\PY{p}{,} \PY{l+m+mi}{0}\PY{p}{,} \PY{l+m+mi}{0}\PY{p}{]}

\PY{n}{cov\PYZus{}mass} \PY{o}{=}            \PY{p}{[}\PY{n}{sigma\PYZus{}diameter}\PY{o}{*}\PY{n}{sigma\PYZus{}mass}\PY{o}{*}\PY{l+m+mf}{0.95}\PY{p}{,} \PY{n}{var\PYZus{}mass}\PY{p}{,} \PY{l+m+mi}{0}\PY{p}{,} \PY{l+m+mi}{0}\PY{p}{,} \PY{l+m+mi}{0}\PY{p}{]}

\PY{n}{cov\PYZus{}breaking\PYZus{}force} \PY{o}{=}  \PY{p}{[}\PY{l+m+mi}{0}\PY{p}{,} \PY{l+m+mi}{0}\PY{p}{,} \PY{n}{var\PYZus{}breaking\PYZus{}force}\PY{p}{,} \PY{l+m+mi}{0}\PY{p}{,} \PY{l+m+mi}{0}\PY{p}{]}

\PY{n}{cov\PYZus{}charge} \PY{o}{=}          \PY{p}{[}\PY{l+m+mi}{0}\PY{p}{,} \PY{l+m+mi}{0}\PY{p}{,} \PY{l+m+mi}{0}\PY{p}{,} \PY{n}{var\PYZus{}charge}\PY{p}{,} \PY{l+m+mi}{0}\PY{p}{]}

\PY{n}{cov\PYZus{}spring\PYZus{}constant} \PY{o}{=} \PY{p}{[}\PY{l+m+mi}{0}\PY{p}{,} \PY{l+m+mi}{0}\PY{p}{,} \PY{l+m+mi}{0}\PY{p}{,} \PY{l+m+mi}{0}\PY{p}{,} \PY{n}{var\PYZus{}spring\PYZus{}constant}\PY{p}{]}

\PY{n}{covariance\PYZus{}matrix} \PY{o}{=} \PY{p}{[}\PY{n}{cov\PYZus{}diameter}\PY{p}{,} 
                     \PY{n}{cov\PYZus{}mass}\PY{p}{,}
                     \PY{n}{cov\PYZus{}breaking\PYZus{}force}\PY{p}{,}
                     \PY{n}{cov\PYZus{}charge}\PY{p}{,}
                     \PY{n}{cov\PYZus{}spring\PYZus{}constant}\PY{p}{]}

\PY{n}{covariance\PYZus{}matrix} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{n}{covariance\PYZus{}matrix}\PY{p}{)} \PY{c+c1}{\PYZsh{}must be symmetric positive semidefinite;}
\PY{c+c1}{\PYZsh{}eigenvalues must be }

\PY{n}{diameter\PYZus{}samples}\PY{p}{,}\PY{n}{mass\PYZus{}samples}\PY{p}{,}\PY{n}{breaking\PYZus{}force\PYZus{}samples}\PY{p}{,}\PY{n}{charge\PYZus{}samples}\PY{p}{,} \PY{n}{spring\PYZus{}constant\PYZus{}samples}\PYZbs{}
                \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{random}\PY{o}{.}\PY{n}{multivariate\PYZus{}normal}\PY{p}{(}\PY{n}{means}\PY{p}{,} \PY{n}{covariance\PYZus{}matrix}\PY{p}{,} \PY{n}{N}\PY{p}{)}\PY{o}{.}\PY{n}{T}

\PY{n}{diameter\PYZus{}samples} \PY{o}{=} \PY{n}{diameter\PYZus{}samples}\PY{o}{.}\PY{n}{T} \PY{c+c1}{\PYZsh{}first .T lets us access with ,, operator, second .T gets us our 1d array back}
\PY{n}{mass\PYZus{}samples} \PY{o}{=} \PY{n}{mass\PYZus{}samples}\PY{o}{.}\PY{n}{T}
\PY{n}{breaking\PYZus{}force\PYZus{}samples} \PY{o}{=} \PY{n}{breaking\PYZus{}force\PYZus{}samples}\PY{o}{.}\PY{n}{T} 
\PY{n}{charge\PYZus{}samples} \PY{o}{=} \PY{n}{charge\PYZus{}samples}\PY{o}{.}\PY{n}{T} 
\PY{n}{spring\PYZus{}constant\PYZus{}samples} \PY{o}{=} \PY{n}{spring\PYZus{}constant\PYZus{}samples}\PY{o}{.}\PY{n}{T} 
\end{Verbatim}
\end{tcolorbox}

    The liposome breaking force is distributed in an obstinately
non-gaussian bimodal manner, so we override the covariance matrix and
introduce a gaussian KDE sampled from the force histogram in {[}Li
2011{]}.

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{12}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{c+c1}{\PYZsh{}ignore the above covariant normal breaking forces, resample from KDE}
\PY{n}{breaking\PYZus{}force\PYZus{}samples} \PY{o}{=} \PY{n}{gaussian\PYZus{}kde}\PY{o}{.}\PY{n}{resample}\PY{p}{(}\PY{n}{breaking\PYZus{}force\PYZus{}kernel}\PY{p}{,} \PY{n}{N}\PY{p}{)}\PY{o}{.}\PY{n}{T}
\end{Verbatim}
\end{tcolorbox}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{13}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{c+c1}{\PYZsh{}choose only infectious particles [Lauffer 1944]}
\PY{n}{remove\PYZus{}indices} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{nonzero}\PY{p}{(}\PY{p}{(}\PY{n}{diameter\PYZus{}samples} \PY{o}{\PYZlt{}} \PY{l+m+mf}{80.0}\PY{p}{)}\PY{p}{)}\PY{p}{,} \PY{n}{np}\PY{o}{.}\PY{n}{nonzero}\PY{p}{(}\PY{p}{(}\PY{n}{diameter\PYZus{}samples} \PY{o}{\PYZgt{}} \PY{l+m+mf}{135.0}\PY{p}{)}\PY{p}{)}\PY{p}{)}

\PY{c+c1}{\PYZsh{}choose only positive breaking forces}
\PY{n}{remove\PYZus{}indices} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{remove\PYZus{}indices}\PY{p}{,} \PY{n}{np}\PY{o}{.}\PY{n}{nonzero}\PY{p}{(}\PY{n}{breaking\PYZus{}force\PYZus{}samples} \PY{o}{\PYZlt{}} \PY{l+m+mf}{0.0}\PY{p}{)}\PY{p}{)}

\PY{n}{remove\PYZus{}indices} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{unique}\PY{p}{(}\PY{n}{remove\PYZus{}indices}\PY{p}{)}

\PY{n}{diameter\PYZus{}samples} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{delete}\PY{p}{(}\PY{n}{diameter\PYZus{}samples}\PY{p}{,} \PY{n}{remove\PYZus{}indices}\PY{p}{)}
\PY{n}{mass\PYZus{}samples} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{delete}\PY{p}{(}\PY{n}{mass\PYZus{}samples}\PY{p}{,} \PY{n}{remove\PYZus{}indices}\PY{p}{)}
\PY{n}{breaking\PYZus{}force\PYZus{}samples} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{delete}\PY{p}{(}\PY{n}{breaking\PYZus{}force\PYZus{}samples}\PY{p}{,} \PY{n}{remove\PYZus{}indices}\PY{p}{)}
\PY{n}{charge\PYZus{}samples} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{delete}\PY{p}{(}\PY{n}{charge\PYZus{}samples}\PY{p}{,} \PY{n}{remove\PYZus{}indices}\PY{p}{)}
\PY{n}{spring\PYZus{}constant\PYZus{}samples} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{delete}\PY{p}{(}\PY{n}{spring\PYZus{}constant\PYZus{}samples}\PY{p}{,} \PY{n}{remove\PYZus{}indices}\PY{p}{)}

\PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{diameter\PYZus{}samples}\PY{p}{,}\PY{n}{mass\PYZus{}samples}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{.}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
\PY{n}{plt}\PY{o}{.}\PY{n}{figure}\PY{p}{(}\PY{p}{)}
\PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{diameter\PYZus{}samples}\PY{p}{,}\PY{n}{breaking\PYZus{}force\PYZus{}samples}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{.}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}

\PY{c+c1}{\PYZsh{}\PYZgt{} \PYZdq{}More than 95\PYZpc{} puncture events occurred above 0.4 nN.\PYZdq{}}
\PY{n}{above\PYZus{}point\PYZus{}4} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{shape}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{where}\PY{p}{(}\PY{n}{breaking\PYZus{}force\PYZus{}samples} \PY{o}{\PYZgt{}} \PY{l+m+mf}{0.4}\PY{p}{)}\PY{p}{)}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]} \PY{o}{/} \PY{n+nb}{len}\PY{p}{(}\PY{n}{breaking\PYZus{}force\PYZus{}samples}\PY{p}{)}
\PY{c+c1}{\PYZsh{} probably because of the clipped normal. np multivariate doesn\PYZsq{}t support beyond normal,}
\PY{c+c1}{\PYZsh{} so that\PYZsq{}ll have to be good enough.}
\PY{c+c1}{\PYZsh{} altered distribution to better fit breaking force; now it\PYZsq{}s 92\PYZpc{}}

\PY{n}{plt}\PY{o}{.}\PY{n}{figure}\PY{p}{(}\PY{p}{)}
\PY{n}{plt}\PY{o}{.}\PY{n}{hist}\PY{p}{(}\PY{n}{breaking\PYZus{}force\PYZus{}samples}\PY{p}{,}\PY{l+m+mi}{20}\PY{p}{)}

\PY{n}{plt}\PY{o}{.}\PY{n}{figure}\PY{p}{(}\PY{p}{)}
\PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{diameter\PYZus{}samples}\PY{p}{,} \PY{n}{spring\PYZus{}constant\PYZus{}samples}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{.}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}

\PY{n}{above\PYZus{}point\PYZus{}4}
\end{Verbatim}
\end{tcolorbox}

            \begin{tcolorbox}[breakable, size=fbox, boxrule=.5pt, pad at break*=1mm, opacityfill=0]
\prompt{Out}{outcolor}{13}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
0.9249410250911431
\end{Verbatim}
\end{tcolorbox}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_17_1.png}
    \end{center}
    { \hspace*{\fill} \\}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_17_2.png}
    \end{center}
    { \hspace*{\fill} \\}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_17_3.png}
    \end{center}
    { \hspace*{\fill} \\}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_17_4.png}
    \end{center}
    { \hspace*{\fill} \\}

    \begin{figure}
\centering
\includegraphics{attachment:Screenshot\%20from\%202020-06-29\%2013-11-21.png}
\caption{Screenshot\%20from\%202020-06-29\%2013-11-21.png}
\end{figure}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{14}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{c+c1}{\PYZsh{} convert everything to base SI}

\PY{n}{diameter\PYZus{}samples} \PY{o}{*}\PY{o}{=} \PY{l+m+mf}{1e\PYZhy{}9} \PY{c+c1}{\PYZsh{} nm}
\PY{n}{mass\PYZus{}samples} \PY{o}{*}\PY{o}{=} \PY{n}{MDa} \PY{c+c1}{\PYZsh{}MDa}
\PY{n}{breaking\PYZus{}force\PYZus{}samples} \PY{o}{*}\PY{o}{=} \PY{l+m+mf}{1e\PYZhy{}9} \PY{c+c1}{\PYZsh{}nN}
\PY{n}{charge\PYZus{}samples} \PY{o}{*}\PY{o}{=} \PY{n}{elementary\PYZus{}charge}

\PY{c+c1}{\PYZsh{} afm pressure}
\PY{n}{afm\PYZus{}tip\PYZus{}radius} \PY{o}{=} \PY{l+m+mf}{30e\PYZhy{}9} \PY{c+c1}{\PYZsh{}m}
\PY{n}{afm\PYZus{}area} \PY{o}{=} \PY{n}{pi}\PY{o}{*}\PY{p}{(}\PY{n}{afm\PYZus{}tip\PYZus{}radius}\PY{o}{*}\PY{o}{*}\PY{l+m+mf}{2.0}\PY{p}{)}

\PY{n}{breaking\PYZus{}stress\PYZus{}samples} \PY{o}{=} \PY{n}{breaking\PYZus{}force\PYZus{}samples} \PY{o}{/} \PY{n}{afm\PYZus{}area} \PY{c+c1}{\PYZsh{} now to Pa}
\end{Verbatim}
\end{tcolorbox}

    We very simply extend {[}Yang 2015{]}'s analysis to include the
distribution of viral particles.

We have to continue using Inf. A rather than the target SARS-NCoV-2
because of an apparent lack of AFM nanoindentation data. While both
virions have a lipid bilayer

\begin{verbatim}
The majority of virions (n = 78) may be described as spherical (axial ratio 1.2), the remainder are oval or   kidney-shaped with axial ratios up to 1.4 (n = 17) or more elongated with axial ratios as high as 7.7 (n = 15). The outer diameters of the spherical virions ranged from 84 to 170 nm (mean, 120 nm).
\end{verbatim}

Note that, per {[}Lauffer 1944{]}, of Inf A and B, ``the infectious
particles have diameters within the range 80 to 135{[}nm{]}''.

{[}Yang 2015{]}'s MDCK plaque assay is already sensitive to infectivity;
the extreme-sized non-infective mutants would already be filtered out.
Their PCR assay might not be; the DNA of all non-infectious mutants
would be considered.

{[}Yang 2015{]} use a minimum force of 400 pN, though their reference,
{[}Li 2011{]}, mention that

\begin{quote}
More than 95\% puncture events occurred above 0.4 nN.
\end{quote}

This probably accounts for the high 100\% threshold.

The distribution of breaking strengths in {[}Li 2011{]} (Figure 5b) is
bimodal, and a naive gaussian fit does not produce the above 95\%
figure. Rather than implement a unimodal+bimodal covariant sampling
function, we tweaked the gaussian parameters to accordingly. We hope
that the deities of statistical best practice are not displeased.

The mass, diameter, and breaking force are presumably not independently
distributed. The correlations between the three variables do not seem to
be documented in the literature.

{[}Li 2011{]}, the AFM data is from {[}H1N1{]} rather than the H3N1 or
H5N1.

We therefore need the CoV for NCoV.

There seems to be little variation in the mass of the spike proteins;
intact H3N1 is 161 MDa +/- 17, with spikes removed, 75 MDa +/- 17.
{[}Ruigrok 1984{]}

Influenza is found in two different morphologies; the one found in the
lab is almost entirely the spherical variant, whereas filamentous
variant is often associated with infections in humans. Because it is
rare in the lab, this is not part of the cause of {[}Yang 2015{]}'s
discrepancy; and NCoV does not seem to exhibit such pleomorphic
tendencies.

The average stiffness of the liposome varies approximately linearly from
0.025 to 0.015 from 80 to 135 nm {[}Li 2011{]}, plus a random
distribution with approx. 0.0025 sigma.

Size and weight are assumed to be uncorrelated with breaking strength.

From {[}Yang 2015{]}, eq. 7,

\[A = \frac{q E_0}{\mu \sqrt{((2 \pi f_{res})^2 - (2 \pi f_{excite})^2)^2 + \left(\frac{(2 \pi f_{res})(2 \pi f_{excite})}{Q}\right)^2}}\]

The resonant frequency varies as \(\sqrt{k/m^*}\).

Assuming (as Yang et al do) that the core and shell have 90\% and 10\%
of the mass,

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{15}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{n}{reduced\PYZus{}masses\PYZus{}mu} \PY{o}{=} \PY{p}{(}\PY{p}{(}\PY{l+m+mf}{0.9}\PY{o}{*}\PY{n}{mass\PYZus{}samples}\PY{p}{)} \PY{o}{*} \PY{p}{(}\PY{l+m+mf}{0.1}\PY{o}{*}\PY{n}{mass\PYZus{}samples}\PY{p}{)}\PY{p}{)}\PY{o}{/}\PY{p}{(}\PY{n}{mass\PYZus{}samples}\PY{p}{)} 
\end{Verbatim}
\end{tcolorbox}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{16}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{n}{resonant\PYZus{}frequencies} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{sqrt}\PY{p}{(}\PY{n}{spring\PYZus{}constant\PYZus{}samples}\PY{o}{/}\PY{n}{reduced\PYZus{}masses\PYZus{}mu}\PY{p}{)}\PY{o}{/}\PY{p}{(}\PY{l+m+mf}{2.0}\PY{o}{*}\PY{n}{pi}\PY{p}{)}
\end{Verbatim}
\end{tcolorbox}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{17}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{n}{plt}\PY{o}{.}\PY{n}{hist}\PY{p}{(}\PY{n}{resonant\PYZus{}frequencies}\PY{p}{,} \PY{l+m+mi}{50}\PY{p}{)}
\PY{n}{plt}\PY{o}{.}\PY{n}{title}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Predicted distribution of resonant frequencies of infective Inf. A}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
\PY{n}{plt}\PY{o}{.}\PY{n}{ticklabel\PYZus{}format}\PY{p}{(}\PY{n}{style}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{sci}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{axis}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{x}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{scilimits}\PY{o}{=}\PY{p}{(}\PY{l+m+mi}{9}\PY{p}{,}\PY{l+m+mi}{9}\PY{p}{)}\PY{p}{)}
\PY{n}{plt}\PY{o}{.}\PY{n}{xlabel}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Frequency}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
\PY{n}{plt}\PY{o}{.}\PY{n}{ylabel}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Count}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
\end{Verbatim}
\end{tcolorbox}

            \begin{tcolorbox}[breakable, size=fbox, boxrule=.5pt, pad at break*=1mm, opacityfill=0]
\prompt{Out}{outcolor}{17}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
Text(0, 0.5, 'Count')
\end{Verbatim}
\end{tcolorbox}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_23_1.png}
    \end{center}
    { \hspace*{\fill} \\}

    Unfortunately, this distribution is very sensitive to the values of k

    A surprising source the sadists that drag cracked virions through
acrylamide gel and then irradiate them for sport.

Two dimensional gel electrophoresis resolves both the mass and the
isoelectric point (where the net charge and that of the solution are in
equilibrium) of large structures. {[}Privalsky 1978{]} provides us a
coarse. view of the charges and relative abundances in the virus.

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{18}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{k+kn}{from} \PY{n+nn}{PIL} \PY{k+kn}{import} \PY{n}{Image}

\PY{n}{im} \PY{o}{=} \PY{n}{Image}\PY{o}{.}\PY{n}{open}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{../media/Inf\PYZus{}A\PYZus{}2d\PYZus{}gel\PYZus{}Privalsky.png}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)} \PY{c+c1}{\PYZsh{} Can be many different formats.}
\PY{n}{pix} \PY{o}{=} \PY{n}{im}\PY{o}{.}\PY{n}{load}\PY{p}{(}\PY{p}{)}

\PY{n}{plt}\PY{o}{.}\PY{n}{imshow}\PY{p}{(}\PY{n}{im}\PY{p}{)}
\PY{n}{plt}\PY{o}{.}\PY{n}{title}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{2d gel electrophoresis [Privalsky 1978]}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
\PY{n}{plt}\PY{o}{.}\PY{n}{xlabel}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Isoelectric point (proportional to net charge)}\PY{l+s+se}{\PYZbs{}n}\PY{l+s+s2}{ \PYZlt{}\PYZhy{} Basic | Neutral | Acid \PYZhy{}\PYZgt{}}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
\PY{n}{plt}\PY{o}{.}\PY{n}{ylabel}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Molecular weight}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}

\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{NP has MW 60000 Da}\PY{l+s+s2}{\PYZdq{}}
\end{Verbatim}
\end{tcolorbox}

            \begin{tcolorbox}[breakable, size=fbox, boxrule=.5pt, pad at break*=1mm, opacityfill=0]
\prompt{Out}{outcolor}{18}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
'NP has MW 60000 Da'
\end{Verbatim}
\end{tcolorbox}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_26_1.png}
    \end{center}
    { \hspace*{\fill} \\}

    There's substantial hetrogeneity in the charge of the proteins with the
exception of the nucleocapsid protein NP. The M proteins have run off
the basic end. The followup work {[}Privalsky 1980{]} indeed finds the M
protein to be very basic. {[}Shtykova 2017{]} discusses the charge on
the M1 matrix protein.

confusingly, there are two different M proteins, sometimes called ``M''
and sometimes called ``M1''.

{[}Bosch 1984{]} discusses the charge hetrogenetity a bit, but not quite
relevant.

    \begin{figure}
\centering
\includegraphics{attachment:influenza-virion3.jpg}
\caption{influenza-virion3.jpg}
\end{figure}

From https://www.virology.ws/2009/04/30/structure-of-influenza-virus/,
CC-BY-3.0

    \begin{figure}
\centering
\includegraphics{attachment:512px-Coronavirus_virion_structure.svg.png}
\caption{512px-Coronavirus\_virion\_structure.svg.png}
\end{figure}

https://commons.wikimedia.org/wiki/File:Coronavirus\_virion\_structure.svg

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{ }{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]

\end{Verbatim}
\end{tcolorbox}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{19}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{n}{excitation\PYZus{}frequency} \PY{o}{=} \PY{l+m+mf}{8.3e9}

\PY{n}{Q} \PY{o}{=} \PY{l+m+mf}{2.0} \PY{c+c1}{\PYZsh{} also assumed to be invariant}
\end{Verbatim}
\end{tcolorbox}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{ }{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]

\end{Verbatim}
\end{tcolorbox}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{20}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{k}{def} \PY{n+nf}{percentiles}\PY{p}{(}\PY{n}{inp}\PY{p}{)}\PY{p}{:}
    \PY{k}{for} \PY{n}{i} \PY{o+ow}{in} \PY{p}{[}\PY{l+m+mi}{6}\PY{p}{,} \PY{l+m+mi}{25}\PY{p}{,} \PY{l+m+mi}{38}\PY{p}{,} \PY{l+m+mi}{50}\PY{p}{,} \PY{l+m+mi}{63}\PY{p}{,} \PY{l+m+mi}{75}\PY{p}{,} \PY{l+m+mi}{90}\PY{p}{,} \PY{l+m+mf}{99.9}\PY{p}{]}\PY{p}{:}

        \PY{n+nb}{print}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+si}{\PYZob{}\PYZcb{}}\PY{l+s+s2}{th percentile: }\PY{l+s+si}{\PYZob{}:2f\PYZcb{}}\PY{l+s+s2}{\PYZdq{}}\PY{o}{.}\PY{n}{format}\PY{p}{(}\PY{n}{i}\PY{p}{,} \PY{n}{np}\PY{o}{.}\PY{n}{percentile}\PY{p}{(}\PY{n}{inp}\PY{p}{,} \PY{n}{i}\PY{p}{,} \PY{n}{axis}\PY{o}{=}\PY{l+m+mi}{0}\PY{p}{)}\PY{p}{)}\PY{p}{)}
\end{Verbatim}
\end{tcolorbox}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{21}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{n}{af} \PY{o}{=} \PY{l+m+mf}{2.0}\PY{o}{*}\PY{n}{pi}

\PY{k}{def} \PY{n+nf}{electric\PYZus{}field\PYZus{}threshold}\PY{p}{(}\PY{n}{i}\PY{p}{,} \PY{n}{excitation\PYZus{}frequency}\PY{p}{)}\PY{p}{:}
    \PY{n}{t1} \PY{o}{=} \PY{n}{breaking\PYZus{}stress\PYZus{}samples}\PY{p}{[}\PY{n}{i}\PY{p}{]} \PY{o}{*} \PY{n}{pi} \PY{o}{*} \PY{p}{(}\PY{p}{(}\PY{n}{diameter\PYZus{}samples}\PY{p}{[}\PY{n}{i}\PY{p}{]} \PY{o}{/} \PY{l+m+mf}{2.0}\PY{p}{)}\PY{o}{*}\PY{o}{*}\PY{l+m+mf}{2.0}\PY{p}{)}

    \PY{n}{t2} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{sqrt}\PY{p}{(}\PY{p}{(}\PY{n}{reduced\PYZus{}masses\PYZus{}mu}\PY{p}{[}\PY{n}{i}\PY{p}{]}\PY{o}{*}\PY{o}{*}\PY{l+m+mf}{2.0}\PY{p}{)} \PY{o}{*} \PY{p}{(}\PY{p}{(}\PY{p}{(}\PY{p}{(}\PY{p}{(}\PY{n}{resonant\PYZus{}frequencies}\PY{p}{[}\PY{n}{i}\PY{p}{]}\PY{o}{*}\PY{n}{af}\PY{p}{)}\PY{o}{*}\PY{o}{*}\PY{l+m+mf}{2.0}\PY{p}{)}\PY{p}{)} \PY{o}{\PYZhy{}} \PY{p}{(}\PY{p}{(}\PY{n}{excitation\PYZus{}frequency}\PY{o}{*}\PY{n}{af}\PY{p}{)}\PY{o}{*}\PY{o}{*}\PY{l+m+mf}{2.0}\PY{p}{)}\PY{p}{)}\PY{o}{*}\PY{o}{*}\PY{l+m+mf}{2.0}\PY{p}{)}\PYZbs{}
            \PY{o}{+} \PY{p}{(}\PY{p}{(}\PY{p}{(}\PY{p}{(}\PY{n}{resonant\PYZus{}frequencies}\PY{p}{[}\PY{n}{i}\PY{p}{]}\PY{o}{*}\PY{n}{af}\PY{p}{)}\PY{o}{*}\PY{n}{reduced\PYZus{}masses\PYZus{}mu}\PY{p}{[}\PY{n}{i}\PY{p}{]}\PY{p}{)}\PY{o}{/}\PY{n}{Q}\PY{p}{)}\PY{o}{*}\PY{o}{*}\PY{l+m+mf}{2.0}\PY{p}{)} \PY{o}{*} \PY{p}{(}\PY{p}{(}\PY{n}{excitation\PYZus{}frequency}\PY{o}{*}\PY{n}{af}\PY{p}{)}\PY{o}{*}\PY{o}{*}\PY{l+m+mf}{2.0}\PY{p}{)}\PY{p}{)}
    \PY{n}{b} \PY{o}{=} \PY{l+m+mf}{3.45} \PY{o}{*} \PY{n}{charge\PYZus{}samples}\PY{p}{[}\PY{n}{i}\PY{p}{]} \PY{o}{*} \PY{n}{reduced\PYZus{}masses\PYZus{}mu}\PY{p}{[}\PY{n}{i}\PY{p}{]} \PY{o}{*} \PY{p}{(}\PY{p}{(}\PY{n}{resonant\PYZus{}frequencies}\PY{p}{[}\PY{n}{i}\PY{p}{]}\PY{o}{*}\PY{n}{af}\PY{p}{)}\PY{p}{)}\PY{o}{*}\PY{o}{*}\PY{l+m+mf}{2.0}

    \PY{n}{electric\PYZus{}field\PYZus{}thresholds} \PY{o}{=} \PY{p}{(}\PY{n}{t1} \PY{o}{*} \PY{n}{t2}\PY{p}{)} \PY{o}{/} \PY{n}{b}

    \PY{k}{return} \PY{n}{electric\PYZus{}field\PYZus{}thresholds}

\PY{c+c1}{\PYZsh{}eq 12 in [Yang 2015]}
\PY{k}{def} \PY{n+nf}{electric\PYZus{}field\PYZus{}thresholds}\PY{p}{(}\PY{n}{excitation\PYZus{}frequency}\PY{p}{)}\PY{p}{:}

    \PY{n}{t1} \PY{o}{=} \PY{n}{breaking\PYZus{}stress\PYZus{}samples} \PY{o}{*} \PY{n}{pi} \PY{o}{*} \PY{p}{(}\PY{p}{(}\PY{n}{diameter\PYZus{}samples} \PY{o}{/} \PY{l+m+mf}{2.0}\PY{p}{)}\PY{o}{*}\PY{o}{*}\PY{l+m+mf}{2.0}\PY{p}{)}

    \PY{n}{t2} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{sqrt}\PY{p}{(}\PY{p}{(}\PY{n}{reduced\PYZus{}masses\PYZus{}mu}\PY{o}{*}\PY{o}{*}\PY{l+m+mf}{2.0}\PY{p}{)} \PY{o}{*} \PY{p}{(}\PY{p}{(}\PY{p}{(}\PY{p}{(}\PY{p}{(}\PY{n}{resonant\PYZus{}frequencies}\PY{o}{*}\PY{n}{af}\PY{p}{)}\PY{o}{*}\PY{o}{*}\PY{l+m+mf}{2.0}\PY{p}{)}\PY{p}{)} \PY{o}{\PYZhy{}} \PY{p}{(}\PY{p}{(}\PY{n}{excitation\PYZus{}frequency}\PY{o}{*}\PY{n}{af}\PY{p}{)}\PY{o}{*}\PY{o}{*}\PY{l+m+mf}{2.0}\PY{p}{)}\PY{p}{)}\PY{o}{*}\PY{o}{*}\PY{l+m+mf}{2.0}\PY{p}{)}\PYZbs{}
            \PY{o}{+} \PY{p}{(}\PY{p}{(}\PY{p}{(}\PY{p}{(}\PY{n}{resonant\PYZus{}frequencies}\PY{o}{*}\PY{n}{af}\PY{p}{)}\PY{o}{*}\PY{n}{reduced\PYZus{}masses\PYZus{}mu}\PY{p}{)}\PY{o}{/}\PY{n}{Q}\PY{p}{)}\PY{o}{*}\PY{o}{*}\PY{l+m+mf}{2.0}\PY{p}{)} \PY{o}{*} \PY{p}{(}\PY{p}{(}\PY{n}{excitation\PYZus{}frequency}\PY{o}{*}\PY{n}{af}\PY{p}{)}\PY{o}{*}\PY{o}{*}\PY{l+m+mf}{2.0}\PY{p}{)}\PY{p}{)}
    \PY{n}{b} \PY{o}{=} \PY{l+m+mf}{3.45} \PY{o}{*} \PY{n}{charge\PYZus{}samples} \PY{o}{*} \PY{n}{reduced\PYZus{}masses\PYZus{}mu} \PY{o}{*} \PY{p}{(}\PY{p}{(}\PY{n}{resonant\PYZus{}frequencies}\PY{o}{*}\PY{n}{af}\PY{p}{)}\PY{p}{)}\PY{o}{*}\PY{o}{*}\PY{l+m+mf}{2.0}

    \PY{n}{electric\PYZus{}field\PYZus{}thresholds} \PY{o}{=} \PY{p}{(}\PY{n}{t1} \PY{o}{*} \PY{n}{t2}\PY{p}{)} \PY{o}{/} \PY{n}{b}

    \PY{k}{return} \PY{n}{electric\PYZus{}field\PYZus{}thresholds}

\PY{n}{single\PYZus{}freq\PYZus{}elecric\PYZus{}field\PYZus{}thresholds} \PY{o}{=} \PY{n}{electric\PYZus{}field\PYZus{}thresholds}\PY{p}{(}\PY{n}{excitation\PYZus{}frequency}\PY{p}{)}

\PY{n}{plt}\PY{o}{.}\PY{n}{title}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Predicted distribution of electric fields required to inactivate infective Inf. A}\PY{l+s+se}{\PYZbs{}n}\PY{l+s+s2}{\PYZdq{}}\PY{o}{+}\PYZbs{}
        \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{given excitation at a single frequency}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
\PY{n}{plt}\PY{o}{.}\PY{n}{hist}\PY{p}{(}\PY{n}{single\PYZus{}freq\PYZus{}elecric\PYZus{}field\PYZus{}thresholds}\PY{p}{,} \PY{l+m+mi}{50}\PY{p}{)}
\PY{n}{plt}\PY{o}{.}\PY{n}{xlabel}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Electric field (V/m)}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
\PY{n}{plt}\PY{o}{.}\PY{n}{ylabel}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Count}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
\PY{n}{percentiles}\PY{p}{(}\PY{n}{single\PYZus{}freq\PYZus{}elecric\PYZus{}field\PYZus{}thresholds}\PY{p}{)}

\PY{c+c1}{\PYZsh{} Yang get:}
\PY{c+c1}{\PYZsh{} 100\PYZpc{}: 275 V/m}
\PY{c+c1}{\PYZsh{} 63\PYZpc{}: 171 V/m}
\PY{c+c1}{\PYZsh{} 38\PYZpc{}: 87 V/m}
\PY{c+c1}{\PYZsh{} 6\PYZpc{}: 68 V/m}
\end{Verbatim}
\end{tcolorbox}

    \begin{Verbatim}[commandchars=\\\{\}]
6th percentile: 104.519073
25th percentile: 178.738256
38th percentile: 226.608581
50th percentile: 272.961741
63th percentile: 329.662413
75th percentile: 395.087502
90th percentile: 512.626157
99.9th percentile: 870.175943
    \end{Verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_35_1.png}
    \end{center}
    { \hspace*{\fill} \\}

    IEEE et al appear to specify power densities as those in free space, a
small distance from the body:

    \[S = \frac{|E|^2}{Z_0}\]

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{22}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{n}{single\PYZus{}freq\PYZus{}power\PYZus{}densities} \PY{o}{=} \PY{p}{(}\PY{n}{single\PYZus{}freq\PYZus{}elecric\PYZus{}field\PYZus{}thresholds}\PY{o}{*}\PY{o}{*}\PY{l+m+mf}{2.0}\PY{p}{)} \PY{o}{/} \PY{l+m+mf}{377.0}

\PY{n}{plt}\PY{o}{.}\PY{n}{title}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Predicted distribution of power densities required to inactivate infective Inf. A}\PY{l+s+se}{\PYZbs{}n}\PY{l+s+s2}{\PYZdq{}}\PY{o}{+}\PYZbs{}
        \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{given excitation at a single frequency}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
\PY{n}{plt}\PY{o}{.}\PY{n}{hist}\PY{p}{(}\PY{n}{single\PYZus{}freq\PYZus{}power\PYZus{}densities}\PY{p}{,} \PY{l+m+mi}{50}\PY{p}{)}
\PY{n}{plt}\PY{o}{.}\PY{n}{xlabel}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Power density (W/m\PYZca{}2)}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
\PY{n}{plt}\PY{o}{.}\PY{n}{ylabel}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Count}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
\PY{n}{percentiles}\PY{p}{(}\PY{n}{single\PYZus{}freq\PYZus{}power\PYZus{}densities}\PY{p}{)}
\end{Verbatim}
\end{tcolorbox}

    \begin{Verbatim}[commandchars=\\\{\}]
6th percentile: 28.976758
25th percentile: 84.741023
38th percentile: 136.210741
50th percentile: 197.634249
63th percentile: 288.268717
75th percentile: 414.042797
90th percentile: 697.044008
99.9th percentile: 2008.529495
    \end{Verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_38_1.png}
    \end{center}
    { \hspace*{\fill} \\}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{23}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{k}{for} \PY{n}{i} \PY{o+ow}{in} \PY{n}{np}\PY{o}{.}\PY{n}{random}\PY{o}{.}\PY{n}{choice}\PY{p}{(}\PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{0}\PY{p}{,}\PY{n+nb}{len}\PY{p}{(}\PY{n}{resonant\PYZus{}frequencies}\PY{p}{)}\PY{p}{)}\PY{p}{,} \PY{n}{size} \PY{o}{=} \PY{l+m+mi}{20}\PY{p}{)}\PY{p}{:}

    \PY{n}{freqs} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{linspace}\PY{p}{(}\PY{l+m+mf}{1e9}\PY{p}{,}\PY{l+m+mf}{15e9}\PY{p}{)}
    \PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{freqs}\PY{p}{,}\PY{n}{electric\PYZus{}field\PYZus{}threshold}\PY{p}{(}\PY{n}{i}\PY{p}{,} \PY{n}{freqs}\PY{p}{)}\PY{p}{,}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{b}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
    \PY{n}{plt}\PY{o}{.}\PY{n}{title}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Electric field threshold of a sample of virions against excitation frequency}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
    \PY{n}{plt}\PY{o}{.}\PY{n}{ticklabel\PYZus{}format}\PY{p}{(}\PY{n}{style}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{sci}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{axis}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{x}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{scilimits}\PY{o}{=}\PY{p}{(}\PY{l+m+mi}{9}\PY{p}{,}\PY{l+m+mi}{9}\PY{p}{)}\PY{p}{)}
    \PY{n}{plt}\PY{o}{.}\PY{n}{xlabel}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Frequency (GHz)}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
    \PY{n}{plt}\PY{o}{.}\PY{n}{ylabel}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Theshold (V/m)}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}

    \PY{n}{optimal\PYZus{}excitation\PYZus{}frequency} \PY{o}{=} \PY{p}{(}\PY{n}{sqrt}\PY{p}{(}\PY{l+m+mf}{2.0} \PY{o}{*} \PY{n}{Q}\PY{o}{*}\PY{o}{*}\PY{l+m+mf}{2.0} \PY{o}{\PYZhy{}} \PY{l+m+mf}{1.0}\PY{p}{)} \PY{o}{*} \PY{p}{(}\PY{l+m+mf}{2.0}\PY{o}{*}\PY{n}{pi}\PY{o}{*}\PY{n}{resonant\PYZus{}frequencies}\PY{p}{[}\PY{n}{i}\PY{p}{]}\PY{p}{)}\PY{p}{)} \PY{o}{/} \PY{p}{(}\PY{p}{(}\PY{n}{sqrt}\PY{p}{(}\PY{l+m+mf}{2.0}\PY{p}{)}\PY{o}{*}\PY{n}{Q}\PY{p}{)}\PY{p}{)} \PY{o}{/} \PY{p}{(}\PY{l+m+mf}{2.0}\PY{o}{*}\PY{n}{pi}\PY{p}{)}
    \PY{n+nb}{print}\PY{p}{(}\PY{n}{optimal\PYZus{}excitation\PYZus{}frequency}\PY{p}{)}
\end{Verbatim}
\end{tcolorbox}

    \begin{Verbatim}[commandchars=\\\{\}]
7279284906.563067
7494657688.343927
7060094218.977478
7880199441.398486
7887076651.1556635
8391826356.039286
7687065355.281846
7674184760.335817
7851298608.500301
8105547455.286027
7543804559.687341
8037100367.448972
7135882289.73944
7124796958.367642
7740345854.416245
7688243255.571538
7908508087.189577
7891495836.990037
7598584570.812886
7735221662.281465
    \end{Verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_39_1.png}
    \end{center}
    { \hspace*{\fill} \\}

    The resonant frequency does not necessarily correspond to the optimal
excitation frequency. The positive critical point of (12) is

\[w = \frac{\sqrt{2 Q^2 - 1} f_{res}}{\sqrt{2} \ Q}\]

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{24}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{n}{optimal\PYZus{}excitation\PYZus{}frequencies} \PY{o}{=} \PY{p}{(}\PY{n}{sqrt}\PY{p}{(}\PY{l+m+mf}{2.0} \PY{o}{*} \PY{n}{Q}\PY{o}{*}\PY{o}{*}\PY{l+m+mf}{2.0} \PY{o}{\PYZhy{}} \PY{l+m+mf}{1.0}\PY{p}{)} \PY{o}{*} \PY{p}{(}\PY{l+m+mf}{2.0}\PY{o}{*}\PY{n}{pi}\PY{o}{*}\PY{n}{resonant\PYZus{}frequencies}\PY{p}{)}\PY{p}{)} \PY{o}{/} \PY{p}{(}\PY{p}{(}\PY{n}{sqrt}\PY{p}{(}\PY{l+m+mf}{2.0}\PY{p}{)}\PY{o}{*}\PY{n}{Q}\PY{p}{)}\PY{p}{)} \PY{o}{/} \PY{p}{(}\PY{l+m+mf}{2.0}\PY{o}{*}\PY{n}{pi}\PY{p}{)}

\PY{n}{plt}\PY{o}{.}\PY{n}{subplot}\PY{p}{(}\PY{p}{)}
\PY{n}{plt}\PY{o}{.}\PY{n}{hist}\PY{p}{(}\PY{n}{optimal\PYZus{}excitation\PYZus{}frequencies}\PY{p}{,} \PY{l+m+mi}{50}\PY{p}{)}
\PY{n}{plt}\PY{o}{.}\PY{n}{gca}\PY{p}{(}\PY{p}{)}\PY{o}{.}\PY{n}{ticklabel\PYZus{}format}\PY{p}{(}\PY{n}{style}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{sci}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{axis}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{x}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{scilimits}\PY{o}{=}\PY{p}{(}\PY{l+m+mi}{9}\PY{p}{,}\PY{l+m+mi}{9}\PY{p}{)}\PY{p}{)}
\end{Verbatim}
\end{tcolorbox}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_41_0.png}
    \end{center}
    { \hspace*{\fill} \\}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{ }{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]

\end{Verbatim}
\end{tcolorbox}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{25}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{n}{sweep\PYZus{}thresholds} \PY{o}{=} \PY{n}{electric\PYZus{}field\PYZus{}thresholds}\PY{p}{(}\PY{n}{optimal\PYZus{}excitation\PYZus{}frequencies}\PY{p}{)}

\PY{c+c1}{\PYZsh{}plt.hist(thresholds, 50)}

\PY{c+c1}{\PYZsh{} percent\PYZus{}under(sweep\PYZus{}thresholds, 200.0)}

\PY{n}{plt}\PY{o}{.}\PY{n}{hist}\PY{p}{(}\PY{n}{single\PYZus{}freq\PYZus{}thresholds}\PY{o}{\PYZhy{}}\PY{n}{sweep\PYZus{}thresholds}\PY{p}{,} \PY{l+m+mi}{100}\PY{p}{)}

\PY{n+nb}{print}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Given a frequency sweep in which each virion is excited with its frequency of maximum power dissipation,}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
\PY{n+nb}{print}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{The following threshold percentiles would be expected:}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
\PY{n}{percentiles}\PY{p}{(}\PY{n}{sweep\PYZus{}thresholds}\PY{p}{)}

\PY{n}{percentiles}\PY{p}{(}\PY{n}{single\PYZus{}freq\PYZus{}thresholds}\PY{o}{\PYZhy{}}\PY{n}{sweep\PYZus{}thresholds}\PY{p}{)}
\end{Verbatim}
\end{tcolorbox}

    \begin{Verbatim}[commandchars=\\\{\}]

        ---------------------------------------------------------------------------

        NameError                                 Traceback (most recent call last)

        <ipython-input-25-36c65eab0b34> in <module>
          5 \# percent\_under(sweep\_thresholds, 200.0)
          6 
    ----> 7 plt.hist(single\_freq\_thresholds-sweep\_thresholds, 100)
          8 
          9 print("Given a frequency sweep in which each virion is excited with its frequency of maximum power dissipation,")

        NameError: name 'single\_freq\_thresholds' is not defined

    \end{Verbatim}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{ }{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]

\end{Verbatim}
\end{tcolorbox}

    % Add a bibliography block to the postdoc

\end{document}

### 2020-08-12 documents/pamphlet.tex
Coplanar amp

@@
 
-This is a condensed version of a (horribly unfinished) paper at \href{https://www.github.com/0xDBFB7/covidinator/documents/paper.pdf}{\faGithub/0xDBFB7/covidinator}.\footnote{Daniel Correia [TODO: affiliation] \orcidlink{0000-0002-9353-0216}}
+This is a condensed version of a (horribly unfinished) paper at \href{https://www.github.com/0xDBFB7/covidinator/documents/paper.pdf}{\faGithub/0xDBFB7/covidinator}.\footnote{Daniel Correia [TODO: affiliation] \orcidlink{0000-0002-9353-0216}} A paltry few more details and a bibliography are available therein.
 
@@
 
+\begin{figure}[H]
+	\includegraphics[width=\textwidth]{../media/eppenwolf.jpg}
+	\caption{Failure is just success rounded down.}
+\end{figure}
+
+\clearpage
+
 {\Large \textbf{The mechanism}}
 
-\cite{Microwave2009} \textrightarrow \ (\cite{focusing2014} $\parallel$ \cite{Efficient2015} $\parallel$ \cite{Resonant2017})\footnote{A great many papers are involved.} appear to establish that the net charge, mass distribution, and envelope stiffness of a few species of viruses support a weak resonance mode in the microwave spectrum, with a peak at roughly 8 GHz for Inf.
+\cite{Microwave2009} \textrightarrow \ (\cite{focusing2014} $\parallel$ \cite{Efficient2015} $\parallel$ \cite{Resonant2017})\footnote{A great many more papers are involved.} appear to establish that the net charge, mass distribution, and envelope stiffness of a few species of viruses support a weak resonance mode in the microwave spectrum, with a peak at roughly 8 GHz for Inf.
 A.
@@
 
-However, this work would seem to be more useful if extended with the following assertion: the virus' Q factor is only about 2, meaning that the steady-state amplitude and stresses should be reached in some nanoseconds.
+However, this work would seem to be more useful if extended with the following assertion: the virus' Q factor has been determined to be only about 2, meaning that the steady-state amplitude and stresses should be reached in some nanoseconds.
 
-Barring protein mechanical fatigue \cite{Mechanical2013} or some other mechanism that could prolong the inactivation duration, it appears to be possible to reduce the required power density to a minuscule fraction of all safety limits by pulsing the field at nanosecond scales.
-This incidentally allows scanning of a focal point, a significant area can be treated with a relatively small transmit power.
+Barring protein mechanical fatigue \cite{Mechanical2013} or some other mechanism that could prolong the inactivation duration, it appears to be possible to reduce the required dissipated energy density to a minuscule fraction of all safety limits by pulsing the field at nanosecond scales.
+This incidentally also permits scanning of a focal point so that a significant area can be treated with a relatively small transmit power.
 
-\cite{Efficient2015} test with various strains of Influenza A, we are testing with Coliphage T4; structural similarities with NCoV mean this is may be transferable.
+\cite{Efficient2015} test with various strains of Influenza A, we are testing with Coliphage T4; structural similarities with NCoV mean this may be transferable.
 
@@
 \begin{autem}
-	It should be noted that all of the claims we make hinge on this nanosecond inactivation.
+	It should be noted that all of the claims we make hinge on this hypothesis of nanosecond-scale inactivation.
 \cite{Efficient2015} and \cite{focusing2014} use a 15-minute exposure, which is apparently the norm for this field.
+We are trying to obtain data to more firmly establish this now.
 \end{autem}
@@
 From crude attenuation data, this pulsed field can be safely produced at least 3 cm deep in tissue.
-This would seem to be unlike any other mechanisms like near or far\cite{Germicidal2017}UV.
-suitable for targeted sterilization of with bronchoscopic techniques), opening up a particularly interesting direct treatment modality.
-We are trying to verify this now with FDTD sims.
+This would seem to be unlike any other mechanisms in its specificity; near or far\cite{Germicidal2017}UV, chemical sterilization, etc.
+This opens up a particularly interesting direct treatment modality.
 
 Also unlike UV, the X-band is minimally attenuated by air; in the extreme, installations with megawatt-scale klystrons could potentially prevent airborne transmission in square-kilometer areas.
+
+Equally unlike other techniques, if the assumptions above hold, this would act instantaneously, providing $>$ 80\% inactivation in the targeted area (depending on some population parameters).
+
+The amplifiers for this frequency range fall within the regime of many off-the-shelf radar systems; miniature personal emitters could be produced for $ < \$10$ with semiconductor amplifiers; and the high-power systems for direct treatment are only a few orders of magnitude above that.
 
@@
 
-\clearpage 
-{\Large \textbf{How do we wield this sword?}}
-
-This is not a particularly demanding requirement, and lends itself to a wide variety of applications, many of which could be implemented almost immediately.
-
-On an individual level, the free-space-combined output of, say, a few dozen SiGe:C or GaAs transistors (\$0.3 apiece [BFP620]), very similarly to our reference design, should suffice to locally protect the major vulnerabilities like mouth, nose, eyes, hair and any surfaces that the hands contact.
-This arguably wouldn't provide many advantages over simple masks, however.
-
 %\centering {\color{red} \faHeart}
@@
 
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=\textwidth]{biology/output_35_1.png}
+\end{figure}
+
 \printbibliography[heading=none, title={}]

### 2020-08-12 documents/supplemental.tex
Coplanar amp

@@
 In case you're wondering, like I was, why the voltage coefficient of capacitors
+
+\rule{\linewidth}{0.2pt}
+
+Much of this project was done in 1.5 mm microstrip with a 2.5 to 3 mm routed isolation.
+However, it became apparent that the inductance of vias with the ground plane was too great.
+It has been suggested that low-inductance vias in prototypes \cite{Microwavee}
+
+Grounded coplanar waveguide, where the primary ground plane is on the top side of the board, presents many advantages, and in later testing appeared to provide much better performance.
+connectors can interface with the top side; the sizes are much more compatible with small SMD devices.
 

### 2020-08-12 documents/supplemental.tex
Here we go.

--- 2020-08-06 documents/supplemental.tex
@@
 In case you're wondering, like I was, why the voltage coefficient of capacitors
+
+\rule{\linewidth}{0.2pt}
+
+Much of this project was done in 1.5 mm microstrip with a 2.5 to 3 mm routed isolation.
+However, it became apparent that the inductance of vias with the ground plane was too great.
+It has been suggested that low-inductance vias in prototypes \cite{Microwavee}
+
+Grounded coplanar waveguide, where the primary ground plane is on the top side of the board, presents many advantages, and in later testing appeared to provide much better performance and easier design.
+connectors can interface with the top side; trace sizes are much more compatible with small SMD devices.
 

### 2020-08-12 documents/microwave_spectrum.tex
Writing the protocol

@@
 \nwfilename{microwave_spectrum.pnw}\nwbegincode{1}\moddef{microwave_spectrum.py}\endmoddef\nwstartdeflinemarkup\nwenddeflinemarkup
+import sys
+sys.path.append('/home/arthurdent/covidinator/firmware/eppendoofus/host/')
+
 import device_comms
 import sweep
+
 \nwendcode{}\nwbegindocs{2}\nwdocspar
 
+It cannot be overstated how sensitive this measurement is. At 12 GHz, merely bringing one's hand near the coaxial line almost doubled
+the power sensor reading.
+
 \nwenddocs{}\nwbegincode{3}\moddef{}\endmoddef\nwstartdeflinemarkup\nwenddeflinemarkup
+import random
 
@@
 
+We randomize \cite{first2000}
+
+\nwenddocs{}\nwbegincode{5}\moddef{}\plusendmoddef\nwstartdeflinemarkup\nwenddeflinemarkup
+
+\nwendcode{}\nwbegindocs{6}\nwdocspar
+
 \end{document}

### 2020-08-12 firmware/eppenwolf/host/functions.py

@@ -143,3 +143,8 @@ def pulse(link, duration):
     clear_buffers(link)
 
     return val
+
+def read_multimeter():
+    multimeter.write("val?\r\n".encode())
+    val = float(multimeter.readline())
+    return val

### 2020-08-12 firmware/eppenwolf/host/functions.py
Still overflowed flash

@@ -4,10 +4,12 @@ from device_comms import *
 position = 0
 
 def set_VCO(link, base_bias_voltage, varactor_voltage, supply_voltage, power_state):
+    max_supply = 5.0
+
     send_size = 0
     send_size = add_float(link, send_size, base_bias_voltage)
     send_size = add_float(link, send_size, varactor_voltage)
-    send_size = add_float(link, send_size, supply_voltage)
+    send_size = add_float(link, send_size, np.clip(supply_voltage, 0, max_supply))
     send_size = add_float(link, send_size, power_state)
 
     link.send(send_size, packet_id=0)
@@ -166,3 +168,15 @@ def read_multimeter():
     multimeter.write("val?\r\n".encode())
     val = float(multimeter.readline())
     return val
+
+def measure_spectrum(link, voltage_list, averages, amplifier_supply):
+    data = np.zeros_like(voltage_list)
+    for a in range(0, averages):
+        for idx, v in enumerate(voltage_list):
+            print(f"Capturing spectrum: {v}")
+            set_VCO(link, 0, v, amplifier_supply, 1)
+            read_multimeter()
+            data[idx] += read_multimeter()
+
+    data /= averages
+    return data

### 2020-08-12 firmware/eppenwolf/protocols/microwave_spectrum.py

@@ -4,3 +4,9 @@ sys.path.append('/home/arthurdent/covidinator/firmware/eppendoofus/host/')
 import device_comms
 import sweep
 
+import random
+
+
+
+
+

### 2020-08-12 firmware/eppenwolf/src/debug_helpers.hpp

@@ -1,19 +1,19 @@
 
-#include "comms.hpp"
-
-
-#define DEBUG_PRINT
-
-#define __FILENAME__ (strrchr(__FILE__, '/') ? strrchr(__FILE__, '/') + 1 : __FILE__)
-//make filename__ preprocessor directive relative - thanks red1ynx!
-
-
-template<typename T>
-void pretty_print_array(T * input, int start, int end);
-
-
-void debug_preamble_printer(String function, int line, String file, String name);
-
-#define debug_array(input, start, end) debug_preamble_printer(__FUNCTION__, __LINE__, __FILENAME__, #input); pretty_print_array(input, start, end);
-#define debug_val(input) debug_preamble_printer(__FUNCTION__, __LINE__, __FILENAME__, #input); debug_serial.println(" = " + input);
-#define debug(input) debug_preamble_printer(__FUNCTION__, __LINE__, __FILENAME__, #input); debug_serial.println(input);
+// #include "comms.hpp"
+//
+//
+// #define DEBUG_PRINT
+//
+// #define __FILENAME__ (strrchr(__FILE__, '/') ? strrchr(__FILE__, '/') + 1 : __FILE__)
+// //make filename__ preprocessor directive relative - thanks red1ynx!
+//
+//
+// template<typename T>
+// void pretty_print_array(T * input, int start, int end);
+//
+//
+// void debug_preamble_printer(String function, int line, String file, String name);
+//
+// #define debug_array(input, start, end) debug_preamble_printer(__FUNCTION__, __LINE__, __FILENAME__, #input); pretty_print_array(input, start, end);
+// #define debug_val(input) debug_preamble_printer(__FUNCTION__, __LINE__, __FILENAME__, #input); debug_serial.println(" = " + input);
+// #define debug(input) debug_preamble_printer(__FUNCTION__, __LINE__, __FILENAME__, #input); debug_serial.println(input);

### 2020-08-12 firmware/eppenwolf/src/except.cpp

@@ -1,9 +1,9 @@
-#include "except.hpp"
-
-int aborted = 0;
-
-
-void run_abort(String cause){
-    debug("Aborting!");
-
-}
+// #include "except.hpp"
+//
+// int aborted = 0;
+//
+//
+// void run_abort(String cause){
+//     debug("Aborting!");
+//
+// }

### 2020-08-12 firmware/eppenwolf/src/except.hpp

@@ -1,6 +1,6 @@
-#include <string>
-#include <debug_helpers.hpp>
-
-extern int aborted;
-
-void run_abort(String cause);
+// #include <string>
+// #include <debug_helpers.hpp>
+//
+// extern int aborted;
+//
+// void run_abort(String cause);

### 2020-08-12 firmware/eppenwolf/src/main.cpp

@@ -3,7 +3,7 @@
 #include "VCO_driver.hpp"
 #include "turbidimeter.hpp"
 #include "stepper.hpp"
-
+#include "thermal.hpp"
 int main(void)
 {
 

### 2020-08-15 documents/clinical_protocol.tex
Coplanar

--- 2020-08-12 documents/pamphlet.tex
@@
 
-\title{{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation}
+\title{ {\it Proposal:}\\ Determining the efficacy of pulsed microwave-acoustic viral envelope disruption in COVID-19 treatment}
 
@@
 \maketitle
-
-%\footnote{The}
-
-This is a condensed version of a (horribly unfinished) paper at \href{https://www.github.com/0xDBFB7/covidinator/documents/paper.pdf}{\faGithub/0xDBFB7/covidinator}.\footnote{Daniel Correia [TODO: affiliation] \orcidlink{0000-0002-9353-0216}} A paltry few more details and a bibliography are available therein.
-
-%\subfile{pulse_1.tex}
-
-Both the microwave and microbiology components of this field appear to be unusually sensitive to experimental design and exceptionally prone to artifacts that cause false positive results: \cite{Microwave1982} $\neq$ \cite{Resonances1987}, \cite{Effects1985a} $\neq$ \cite{Cytogenetic1986}, \cite{Comprehensive2018}.
-Though the cited articles have taken care to avoid these effects, it is entirely possible that none of what is discussed below actually exists.
-
-Please distrust our analysis.
-
-%The literature is littered with irreproducible claims of non-thermal effects; however, this appears to be a singular anomaly.
-
-\begin{figure}[H]
-	\includegraphics[width=\textwidth]{../media/eppenwolf.jpg}
-	\caption{Failure is just success rounded down.}
-\end{figure}
-
-\clearpage
 
@@
 
-\cite{Efficient2015} specifically provides a reasonable spherical-cow model for how this could occur that agrees well with experiment.\footnote{See also \ghfile{documents/biology.ipynb}}
+\cite{Efficient2015} specifically provides a reasonable "spherical-cow" model for how this could occur that agrees well with experiment.\footnote{See also \ghfile{documents/biology.ipynb}}
 
-However, this work would seem to be more useful if extended with the following assertion: the virus' Q factor has been determined to be only about 2, meaning that the steady-state amplitude and stresses should be reached in some nanoseconds.
+This work would seem to be more useful if extended with the following assertion: the virus' Q factor has been determined to be only about 2, meaning that the steady-state amplitude and stresses should be reached in some nanoseconds.
 
-Barring protein mechanical fatigue \cite{Mechanical2013} or some other mechanism that could prolong the inactivation duration, it appears to be possible to reduce the required dissipated energy density to a minuscule fraction of all safety limits by pulsing the field at nanosecond scales.
+Barring protein mechanical fatigue\cite{Mechanical2013} or some other mechanism that could prolong the inactivation duration, it appears to be possible to reduce the required dissipated energy density to a minuscule fraction of all safety limits by pulsing the field at nanosecond scales.
 This incidentally also permits scanning of a focal point so that a significant area can be treated with a relatively small transmit power.
@@
 
-%\centering {\color{red} \faHeart}
-
-\clearpage
-
 \begin{figure}[H]
@@
 
-\printbibliography[heading=none, title={}]
+microwave diathermy and hyperthermia;
+
+Several more recent papers \cite{Theoretical2020} on the technique have been published, but these are largely pseudoscientific and lack detail.
+
+We are not aware of any clinical trial using microwave at these frequencies.
+
+Research question: 
+Does 
+Null Hypothesis: There is no difference in fluoride release between the Compomer and Glass- ionomer cement.
+Alternate Hypothesis: There is a difference in fluoride release between the Compomer and Glass-ionomer cement.
+Disease progression
+
+Proposed intervention:
+
+\section{Potential Benefits and Risks to Patients:}
+
+\section{Operational Planning and Budgeting:}
+
+Keysight / Agilent 83732B
 

### 2020-08-15 electronics/simple_fdtd/run/coplanar.py

@@ -112,7 +112,7 @@ pcb.copper_mask[pcb.xy_margin:centerline-m_w_N-int(microstrip_gap/pcb.cell_size)
 
 
 pcb.copper_mask[centerline-m_w_N:centerline+m_w_N, \
-                    pcb.xy_margin:int(pcb.xy_margin+(int(microstrip_length/pcb.cell_size))), z_slice] = 1
+                    pcb.xy_margin:int(pcb.xy_margin+(int(microstrip_length/2.0/pcb.cell_size))), z_slice] = 1
 
 
 

### 2020-08-18 documents/supplemental.tex
IT.IS models
Extract distribution

@@
 In practice, the timestep required to obtain convergence in particularly tight corners of the SPICE simulation can drop to 1e-20, which is far below the Courant limit of the FDTD simulation.
-To eek out a bit more performance, a simple adaptive-timestep technique from [ a ] is used; we simply set the timestep so that the maximum change in voltage per timestep from the SPICE portion is less than some threshold.
+To eek out a bit more performance, a simple adaptive-timestep technique from [ a ] is used; we simply set the timestep so that the maximum change in voltage per timestep from the SPICE portion is less than
+some threshold.
+
+\PRLsep{{\itshape Sampling time-domain spectrometry}}
+
+\begin{quote}
+A rapidly increasing voltage step V tŽ . is applied to the 0
+line and recorded, along with the reflected voltage R tŽ .
+returned from the sample and delayed by the cable propagation time Figure 2 . Any cable or instrument artifacts Ž .
+are separated from the sample response due to the propagation delay, thus making them easy to identify and control. The entire frequency spectrum is captured at once,
+thus eliminating drift and distortion between frequencies.
+\end{quote}
+
+The pulse is usually recorded in real-time with a many-GHz oscilloscope. However, by using a sampling oscilloscope, massively undersampling the signal,
+
+Another advantage of this technique is that no high-Q filters are required to select the frequency;
+discrimination is in the time-domain, and is spread out over many seconds. It is also much easier to generate a 10+ GHz fast edge than it is to generate a CW signal.
 

### 2020-08-18 documents/clinical_protocol.tex
d
State

@@
 \maketitle
+
+Minister of Health
+Patricia Hajdu
 
@@
 \end{autem}
-
-{\Large \textbf{Advantages over existing techniques}}
 
@@
 
+The spike proteins, essential to the virus's infectivity, are
+
 Several more recent papers \cite{Theoretical2020} on the technique have been published, but these are largely pseudoscientific and lack detail.
@@
 We are not aware of any clinical trial using microwave at these frequencies.
+
+\cite{neuroinvasive2020}
+
+On the other hand, increasing evidence
+shows that CoVs may first invade peripheral nerve terminals, and
+then gain access to the CNS via a synapse‐connected route.
+
+to, er, head them off at the head.
+
+alveolar damage
+
+https://www.nature.com/articles/s41379-020-0595-z
+
+Inclusion criteria:
+
+dyspnea
+
+Patients where disease progression indicates that hypoxic respiratory failure is likely to occur.
+
+Dyspnea
+Oxygen saturation
+CT: lung opacities
+
+Without metal piercings or
+
+Non-thermal nerve stimulation leading to temporary paralysis has been reported.
+
+Since the genitals are not involved in the infection; and they will not receive a dose above background.\cite{Organ2004}.
+
+(2) The application must contain sufficient information and material to enable the Minister to determine whether to issue the authorization and must include the following:
+
+the name and contact information of the applicant 
+the name and class of the device;
+a description of the device and of the materials used in its manufacture and packaging;
+a description of the features of the device that permit it to be used for the medical conditions, purposes and uses for which it is manufactured, sold or represented, including its performance specifications if those specifications are necessary for proper use;
+the identifier of the device, including the identifier of any medical device that is part of a system, test kit, medical device group, medical device family or medical device group family;
+the name and contact information of the manufacturer as they appear on the device label;
+the address where the device is manufactured, if the address is different from the one provided in the contact information under paragraph (f);
+the diagnosis, treatment, mitigation or prevention for which the device is required;
+a list of the countries other than Canada where the device has been sold, the total number of units sold in those countries and a summary of any reported problems with the device and of any recalls of the device in those countries;
+the known information in relation to the quality, safety and effectiveness of the device;
+the directions for use, unless directions are not required for the device to be used safely and effectively;
+an attestation by the applicant that documented procedures are in place in respect of distribution records, complaint handling, incident reporting and recalls;
+a copy of the label of the device;
+the name of the qualified investigator and their qualifications, including their training and experience;
+the name and contact information of the institution at which the clinical trial is proposed to be conducted;
+the protocol of the proposed clinical trial, including the number of clinical trial subjects, the number of units of the device proposed to be used for the clinical trial, the hypothesis for and objective of the clinical trial, the period of time during which the clinical trial will be conducted and a copy of the informed consent form;
+a written undertaking from the qualified investigator to:
+conduct the clinical trial in accordance with the protocol provided by the applicant,
+inform each clinical trial subject of any risks and benefits associated with the use of the device and obtain the subject's informed consent for its use, and
+not permit the device to be used by any other person except under the direction of the qualified investigator; and
+in the case of a Class III or IV device, for each clinical trial site, the name and contact information of the research ethics board that approved the protocol and informed consent form referred to in paragraph (p), if known at the time of submitting the application.
+Class II devices
+(3) Despite subsection (2), if the application for the authorization is in respect of a Class II COVID-19 medical device, the information and material set out in paragraphs (2)‍(c), (h) to (j), (n) and (q) may be omitted from the application.
 

### 2020-08-18 electronics/simple_fdtd/fdtd_PCB_extensions/fdtd_PCB_extensions/tissue.py

@@ -1,0 +1,8 @@
+from .PCB import *
+
+
+def raw_voxels_to_numpy(filename):
+    np.frombuffer(s, dtype='int', count=5, offset=6)
+    
+
+# def import_raw(grid, filename, tissue_prop_filename, origin, ):

### 2020-08-20 documents/clinical_protocol.tex
Protocol

@@
 
+In female patients, much of the lung is shielded by breast tissues. However, since fat is not particularly conductive,
+
 The spike proteins, essential to the virus's infectivity, are
@@
 
+preliminary
+
 dyspnea
@@
 
-Since the genitals are not involved in the infection; and they will not receive a dose above background.\cite{Organ2004}.
+Since the reproductive organs are not involved in the infection; and they will not receive a dose above background.\cite{Organ2004}.
 

### 2020-08-22 documents/paper.tex
Integrated amp progress

@@
 
-Protein net charges extracted from protein sequences compiled by the proteome-pI database \cite{ProteomepI2017} and UniProt using localCIDER \cite{CIDER2017} \ghfile{biology/data/net_charge.py}.
+Protein net charges extracted from primary protein sequences compiled by the proteome-pI database \cite{ProteomepI2017} and UniProt using localCIDER \cite{CIDER2017} \ghfile{biology/data/net_charge.py}.
 

### 2020-08-23 documents/clinical_protocol.tex
Driver

@@
 
-\title{ {\it Proposal:}\\ Determining the efficacy of pulsed microwave-acoustic viral envelope disruption in COVID-19 treatment}
+\title{ {\it Proposal:}\\ Ultrashort pulsed microwave viral envelope disruption as a COVID-19 treatment}
 
@@
 
-\cite{Microwave2009} \textrightarrow \ (\cite{focusing2014} $\parallel$ \cite{Efficient2015} $\parallel$ \cite{Resonant2017})\footnote{A great many more papers are involved.} appear to establish that the net charge, mass distribution, and envelope stiffness of a few species of viruses support a weak resonance mode in the microwave spectrum, with a peak at roughly 8 GHz for Inf.
+\cite{Microwave2009} \textrightarrow \ (\cite{focusing2014} $\parallel$ \cite{Efficient2015} $\parallel$ \cite{Resonant2017})\footnote{A great many more papers are involved.} appear to establish that the net charge, mass distribution, and envelope stiffness, and viscous damping of a few species of viruses support a weak resonance mode in the microwave spectrum, with a peak at roughly 8 GHz for Influenza.
 A.

### 2020-08-27 firmware/eppenwolf/src/VCO_driver.cpp
turbidimeter

@@ -113,21 +113,21 @@ void start_amplifier(){
         float current = get_drain_current();
         debug_serial.println(current);
         set_amp_gate_voltage(i);
-        if(current > 0.22){
+        if(current > 0.14){
             debug_serial.println(i);
             break;
         }
         delay(20);
     }
-    set_VCO(10,1);
-    delay(1000);
+    set_VCO(2,1);
+    delay(7000);
     // }
     float current = get_drain_current();
 
     debug_serial.print("current:");
     debug_serial.println(current, 8);
     get_power_levels();
-    set_VCO(10,0);
+    set_VCO(2,0);
     set_amp_gate_voltage(1.6);
     set_amp_power_state(0);
 }
@@ -169,7 +169,7 @@ void set_VCO(float varactor_voltage, bool power_state){
 // }
 //
 // void LO_tune(float value){
-//
+//7
 //     const int mosfet_threshold = 0.7;
 //     int lo_val = (ANALOG_WRITE_MAX_VAL - (value*ANALOG_WRITE_MAX_VAL)) + ((mosfet_threshold / 3.3)*ANALOG_WRITE_MAX_VAL);
 //     debug_serial.printf("LO tune set to %i\n", lo_val);

### 2020-08-28 documents/safety.tex
a

@@
 
-While from which epidemiological data could be derived.\footnote{The cloud service [scite.ai] was irreplaceable during this. It's like a mirror to an alternate universe where literature made sense.}
+While from which epidemiological data could be derived.\footnote{The cloud service [scite.ai] was useful during this review.}
 

### 2020-08-28 firmware/eppenwolf/src/power_sensor.cpp

@@ -15,6 +15,12 @@ ADS1115_lite far_adc(ADS1115_ADDRESS_ADDR_VDD);
 #define PGA ADS1115_REG_CONFIG_PGA_4_096V
 #define PGA_scale 4.096
 
+const int scale_settings[] = {0x0000, 0x0200, 0x0400, 0x0600, 0x0800, 0x0A00};
+const float scale_voltages[] = {6.144, 4.096, 2.048, 1.024, 0.512, 0.256};
+
+int near_scale = 0;
+int far_scale = 0;
+
 void init_ADCs(){
 
     near_adc.setMux(ADS1115_REG_CONFIG_MUX_SINGLE_1);
@@ -36,16 +42,17 @@ void init_ADCs(){
 }
 
 void get_power_levels(){
-
+    //worst-case, on highest PGA scale,
+    
     near_adc.triggerConversion();
     uint16_t near_single_diode_value = near_adc.getConversion();
 
     far_adc.triggerConversion();
     uint16_t far_single_diode_value = far_adc.getConversion();
 
-    debug_serial.print(((float)((near_single_diode_value)/(float)32768))*PGA_scale, 7);
+    debug_serial.print(((float)((near_single_diode_value)/(float)32768))*scale_voltages[near_scale], 7);
     debug_serial.print(",");
-    debug_serial.println(((float)(far_single_diode_value)/(float)32768)*PGA_scale, 7);
+    debug_serial.println(((float)(far_single_diode_value)/(float)32768)*scale_voltages[far_scale], 7);
 
 
 }

### 2020-08-28 documents/supplemental.tex
a

@@
 Simulating the aggregate bose condensate wavefunction is well beyond us.
+
+Both finite-element, molecular-dynamics, and stiffness-eigenvalue normal mode techniques have been used to great effect for this purpose.
 
@@
 
+Many
+
 Three incorrect pieces of information conspired to lead us to try to develop an inexpensive ultrawideband oscillator.
@@
 	\item The ideal 
-	\item The assumption that the only YIG-tuned 
+	\item The assumption that the only commercially available oscillators in this frequency range were expensive YIG-tuned devices.
 \end{itemize}
@@
 
+\rule{\linewidth}{0.2pt}
+
+\begin{quote}
+With four parameters I can fit an elephant, and with five I can make him wiggle his trunk.
+\end{quote}
+- von Neumann
+
+with six parameters, you can do it with only physical constants. Beware numerology.
+
+\rule{\linewidth}{0.2pt}
+
+Most passives (inductors, capacitors) companies supply S-parameters for their parts. Use them.
+
+\rule{\linewidth}{0.2pt}
+
 \PRLsep{{\itshape The antenna itself }}
@@
 \rule{\linewidth}{0.2pt}
+
+Lesson learned: implementing safeties in hardware when possible, even in non-critical systems, can greatly speed development.
+
+Like many microwave semiconductor HBT or pHEMT MMICs, the HMC996 amplifier requires.
+
+\rule{\linewidth}{0.2pt}
+
+Sometimes vertical integration is the wrong move. Objectively, in this case, it was simply the *wrong decision*.
+
+\rule{\linewidth}{0.2pt}
+
 %
@@
 
+% This is
+
 \rule{\linewidth}{0.2pt}

### 2020-08-29 firmware/eppenwolf/src/VCO_driver.hpp
Plate reader

@@ -29,7 +29,7 @@ void set_amp_power_state(bool power_state);
 void init_VCO();
 void set_VCO(float varactor_voltage, bool power_state);
 void start_amplifier();
-
+void determine_gate_spectrum();
 //
 // void LO_power(bool power);
 // void LO_tune(float target_value);

### 2020-08-30 documents/pulse_1.tex
Thermal sensor

@@
 {\Large \it Experiment 2:}\\
-
-Our aims with this experiment are to perform the following:
-
-\begin{itemize}
-\item Crudely test the pulse hypothesis. \cite{Efficient2015}'s use of a 15 minute exposure caused us some consternation.
-    While T4 is quite unlike enveloped viruses, it at least provides a first approximation.
-\item Avoid any ambiguity regarding the temperature rise seen in the previous paper.
-\end{itemize}
-
-In the end, performing this was a mistake; but by the time we realized this we had already put in the bulk of the time.
-
-Inspired by \cite{Biocoder2010}, we write the microbiology protocol directly into the {\it Eppenwolf} firmware using \cite{Noweb}.
 
@@
 
+It cannot be overstated how difficult this measurement is to interpret.
+
+Positions of the three quantities on the slide are randomized\cite{first2000}.
+
+Our aims with this experiment were to perform the following:
+
+\begin{itemize}
+\item Crudely demonstrate the pulse hypothesis. \cite{Efficient2015}'s use of a 15 minute exposure caused us some consternation.
+    While T4 is quite unlike enveloped viruses, it at least provides a first approximation.
+\item Simulataneously, avoid any ambiguity related to the 7 C temperature rise seen in the previous paper.
+\item Crudely measure the damage feedback mechanism.
+\item Demonstrate a cheap microwave spectrometer that could be quickly used on NCoV.
+\end{itemize}
+
+In the end, performing this was probably a mistake; but by the time we realized this we had already put in the bulk of the time.
+
+Inspired by \cite{Biocoder2010}, we write the microbiology protocol directly into the {\it Eppenwolf} firmware using \cite{Noweb}.
+
 For each of the animal and human published studies, four
@@
 avoid individual ‘‘bias’’, B or nB;
+
+// Add a delay to make all cuvettes take the same amount of time
+
 2. Whether or not there was detailed/adequate description of
@@
 confirmation studies, D or nD.
+
+got that, check
+
 3. Whether or not ‘‘positive controls’’ were included in the
 experiment(s) to replicate/confirm the observations, P or nP.
+
+For phage, this is easy; use autoclaved phage.
+
 4. Whether or not ‘‘sham-exposed controls’’ (more appropriate to
@@
 
+\cite{Efficient2015} use freeze-thaw to crack the viral capsid as a positive control.
+T4 appeared to be more resistant.
+
+Properties:
+
+active phage/sterile broth/autoclaved phage/dilute phage in saliva
+e. coli / no e. coli (sterile broth)
+300 exposed / 200 exposed / 100 exposed / un- or sham-exposed
+1 unit time pulse-exposed / 10 unit time pulse-exposed / continuous-exposed
+on-resonance exposed / off-resonance exposed
+
+Of these, the following combinations make sense:
+
+"negative control": Active phage & e. coli & sham-exposed
+"e.coli control": Sterile broth & e. coli & sham-exposed
+"sterility control": Sterile broth & no e. coli & sham-exposed
+"positive control": Autoclaved phage & e. coli & sham-exposed
+"continuous trial": Autoclaved phage & e. coli & sham-exposed
+
+Each on two plates.
+
+The signal used was spectrally impure; phase noise was very high. However, all spurs are at about 3 dB down.
+
+(A downconverter using an HMB and a custom 6.4 GHz LO was tried, but it was found that this was much less informative and more confusing
+due to a lack of effective mixer image and LO spur rejection.)
+
+From FDTD simulations of this cuvette arrangement \ghfile{electronics/simple_fdtd/runs/coplanar}, the fringe field in the fluid
+is approximately 90 V/m per volt of amplitude.
+
+It is possible to subtract the diode drop using [], but because of design flaws in the AC coupling of the detectors, this was not done.
+A Shottky drop of 0.25 V is assumed in all cases.
+
+- Un-exposed phage-only control:
+
+Add 1 unit phage to cuvette. Monitor turbidity.
+
+- Un-exposed e. coli control.
+- Exposed e. coli control.
+- Exposed phage control.
+- Un-exposed e. coli + phage control
+- Un-exposed e. coli + positive autoclaved phage control
+- 1 - minute exposed
+
+To preclude the possibility of damage to the sample while the spectrum is recorded.
+
+0.3 V on a 50-ohm line is
+
+0.4 mW × 10 s / ((4 J / (g × K)) × 0.2 µL × (1 g / mL)) ➞ K
+
+ = 5 K
+
+0.001/(0.256/(2^15))
+
+We further postulate the following. When the virus is lysed, the resonator is destroyed. This should be reflected in the impedance spectrum.
+We expect a non-reversible decrease in the resonance peak after the application of power. This should also appear in the time-domain pulse envelope;
+we expect a "notch" on the rising edge, with a slow taper upwards, which does not repeat on the next pulse.
+
+If this exists, it would provide a great deal of feedback. Not only would the virus would be destroyed, but we would have a quantitative determination of
+of how much was destroyed. In practice, this could be done by applying two pulses in quick succession and monitoring the change in the reflected power;
+or perhaps by a time-domain method. Whether such a signature can be discriminated in a clinical setting remains to be seen.
+
+\section{Silicon carbide test}
+
+To verify that we can detect a resonance with this setup, we use the microwave susceptor mixture described by \cite{Effect2016}, which can be tuned to the correct range by varying the concentration of SiC to binder.
+We use the S-1 mixture.
+
+0.6g 2000-mesh silicon carbide powder was added to 1.4 g white Elmer's glue, mixed manually until homogeneous,
+ applied to a mylar film, and dried with a hair dryer. A small wafer of the hardened mixture, perhaps 0.3 mm thick, 5 mm x 2 mm, was placed directly on top of the coplanar waveguide.
+
+The spectrum was then captured, averaging (?10) sweeps of the VCO. The background spectrum was taken without the wafer in place.
+
+\begin{figure}[H]
+        \includesvg[width=\textwidth]{sic_9_1}
+        \caption{}
+\end{figure}
+
+\begin{figure}[H]
+        \includesvg[width=\textwidth]{firmware/eppenwolf/runs/sic_susceptor/sic_9_2}
+        \caption{}
+\end{figure}
+
+\cite{Effect2016} measures a peak at about 7.2 GHz. Our peak is at approximately 7.849 GHz, which is well within variation in powder grain sizes and concentration.
+
+The paper specifies the reflection loss, S$_{11}$. Unfortunately, having no directional couplers, it is probably not possible to directly determine S$_{21}$ and S$_{11}$ with this setup.
+
+Naively, we might expect the peak to appear as a decrease at both sensors; instead it appears as an increase in transmission and decrease in reflection.
+It could be possible that the presence of the dielectric wafer has merely detuned an existing resonance, that the peak is a coincidence, and that these data mean nothing.
+The raw voltage plots do not suggest that this is the case; but it is nonetheless concerning.
+
+\footnote{The paper mentions that the "blending fraction of silicon carbide powders to epoxy resin was 30 \%, 35 \%, 40 \%, 45 \% and 50\% by weight".
+That seems a little ambiguous as to whether that's "weight per total mass" or "weight per epoxy".}
+
+\section{Microwave spectrum determination}
+
+active phage/sterile broth/autoclaved phage
+
+\section
+
 # T - 5 hours
-
-# Phage+Bacteria / Bacteria-only / phage only?
-
-# expose (parameters) / sham / thermal positives
 

### 2020-08-30 documents/test.tex
Thermal sensor

--- 2020-08-01 documents/pulse_1.tex
@@
-\documentclass[paper.tex]{subfiles}% ===> this file was generated automatically by noweave --- better not edit it
+\documentclass[fleqn,10pt]{paper}
+
+\usepackage[left=2cm,right=2cm,
+top=0.5cm,
+bottom=1.5cm,%
+headheight=11pt,%
+letterpaper]{geometry}
+
+\include{preamble}
+
+\title{{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation}
+
 \begin{document}
 
-\clearpage
-{\Large \it Experiment 2:}\\
+\section{Silicon carbide test}
 
-Our aims with this experiment are to perform the following:
+To verify that we can detect a resonance with this setup, we use the microwave susceptor mixture described by \cite{Effect2016}, which can be tuned to the correct range by varying the concentration of SiC to binder.
+We use the S-1 mixture.
 
-\begin{itemize}
-\item Crudely test the pulse hypothesis. \cite{Efficient2015}'s use of a 15 minute exposure caused us some consternation.
-    While T4 is quite unlike enveloped viruses, it at least provides a first approximation.
-\item Avoid any ambiguity regarding the temperature rise seen in the previous paper.
-\end{itemize}
+0.6g 2000-mesh silicon carbide powder was added to 1.4 g white Elmer's glue, mixed manually until homogeneous,
+applied to a mylar film, and dried with a hair dryer. A small wafer of the hardened mixture, perhaps 0.3 mm thick, 5 mm x 2 mm, was placed directly on top of the coplanar waveguide.
 
-In the end, performing this was a mistake; but by the time we realized this we had already put in the bulk of the time.
+The spectrum was then captured, averaging (?10) sweeps of the VCO. The background spectrum was taken without the wafer in place.
 
-Inspired by \cite{Biocoder2010}, we write the microbiology protocol directly into the {\it Eppenwolf} firmware using \cite{Noweb}.
+\begin{figure}[H]
+	\includesvg[width=\textwidth]{sic_9_1}
+	\caption{}
+\end{figure}
 
-\nwfilename{pulse_1.pnw}\nwbegincode{1}\moddef{pulse_1.py}\endmoddef\nwstartdeflinemarkup\nwenddeflinemarkup
-import device_comms
-import sweep
+\begin{figure}[H]
+	\includesvg[width=\textwidth]{sic_9_2}
+	\caption{}
+\end{figure}
 
-\nwendcode{}\nwbegindocs{2}\nwdocspar
+\cite{Effect2016} measures a peak at about 7.2 GHz. Our peak is at approximately 7.849 GHz, which is well within variation in powder grain sizes and concentration.
 
-For each of the animal and human published studies, four
-predetermined and specific quality control measures were used to
-assess the quality of the publication.
-1. Whether or not the researchers have used ‘‘blind’’ evaluations to
-avoid individual ‘‘bias’’, B or nB;
-2. Whether or not there was detailed/adequate description of
-‘‘dosimetry’’ in the publication for independent replication/
-confirmation studies, D or nD.
-3. Whether or not ‘‘positive controls’’ were included in the
-experiment(s) to replicate/confirm the observations, P or nP.
-4. Whether or not ‘‘sham-exposed controls’’ (more appropriate to
-compare with the observations made in RF exposure conditions)
-were included in the experiments, S or nS. However, it was not our
-intention to ‘‘rank’’ the publications either to exclude or include
-the reported data in the meta-analysis.
+The paper specifies the reflection loss, S$_{11}$. Unfortunately, having no directional couplers, it is probably not possible to directly determine S$_{21}$ and S$_{11}$ with this setup.
 
-# T - 5 hours
+Naively, we might expect the peak to appear as a decrease at both sensors; instead it appears as an increase in transmission and decrease in reflection.
+It could be possible that the presence of the dielectric wafer has merely detuned an existing resonance, that the peak is a coincidence, and that these data mean nothing.
+The raw voltage plots do not suggest that this is the case; but it is nonetheless concerning.
 
-# Phage+Bacteria / Bacteria-only / phage only?
-
-# expose (parameters) / sham / thermal positives
-
-def initialize():
-    # Name this run
-    # Fluidic plate ID
-
-    print("Fill phage into all selected cuvettes.")
-    Simulataneously and separately
-
-#centrifuge down bacteria lightly to concentrate
-#Mix with fresh broth
-#Vortex for X seconds?
-#
-# Rajnovic 2019
-# Overnight cultures of E. coli were centrifuged and the pellets resuspended in 0.1 mM PB to
-# achieve a concentration of 10^10 cfu/mL.
-# The resulting suspensions were subject to serial dilution
-#
-# For each assay, 160 μL of LB were mixed with
-# 20 μL phage solution, 20 μL of bacteria solution and 20μL of PB in
-
-def bacteria_alone_control():
-    //repeated twice
-
-    # fill_phage()
-
-def bacteria_and_phage_control():
-    //repeated twice
-
-def bacteria_and_inactivated_phage_positive_control():
-    //
-
-"Blank" repeatablity test with just water in all cuvettes
-
-Add a small amount of growing e.coli to a new nutrient broth,
-aerate vigorously, then add to culture chamber.
-
-Expose phage.
-Fill culture.
-Monitor culture for log stage.
-Mix culture and phage.
-Monitor mixture.
-
-Types of exposure:
-
-RF
-
-Expose phage, mix with log bacteria, monitor.
-
-Bare
-
-Sham
-
-?
-
-Positive control
-
-Bring phage cuvette temperature to 120c with trace.
-
-Autoclaved
+\footnote{The paper mentions that the "blending fraction of silicon carbide powders to epoxy resin was 30 \%, 35 \%, 40 \%, 45 \% and 50\% by weight".
+That seems a little ambiguous as to whether that's "weight per total mass" or "weight per epoxy".}
 
 \end{document}
-\nwenddocs{}

### 2020-08-30 firmware/eppenwolf/src/VCO_driver.cpp

@@ -155,6 +155,7 @@ void start_amplifier(){
 
     // set_amp_gain_voltage(2.5);
     set_amp_gain_voltage(3.0);
+    //gain varies from 2.2 to 3.4.
     // set_ADC_scales(5, 4);
     set_VCO(4.5,1);
     debug_serial.println("========================================================");
@@ -168,7 +169,6 @@ void start_amplifier(){
             debug_serial.print(",");
             debug_serial.print(get_drain_current());
             debug_serial.println();
-            delay(1000);
         }
         delay(1000);
     }

### 2020-08-30 firmware/eppenwolf/src/thermal.cpp

@@ -1,9 +1,21 @@
-// #include "thermal.hpp"
+#include "thermal.hpp"
+
+MLX90621 thermal_sensor;
+
+float temperatures[64];
+
+void init_thermal(){
+    thermal_sensor.initialise(4);
+
+}
+
+void get_max_temp(){
+    thermal_sensor.get_temperatures(temperatures);
+
+    float max = 0;
+    for(int i=0;i<64;i++){
+        if(temperatures[i] > max){
+            max = temperatures[i];
+        }
+    }
 //
-// MLX90621 thermal_sensor;
-//
-// void init_thermal(){
-//     thermal_sensor.initialise(4);
-//
-// }
-// //

### 2020-08-30 firmware/eppenwolf/src/thermal.hpp

@@ -1,6 +1,7 @@
-// 
-// #include "MLX90621.h"
-//
-// void init_thermal();
-//
-// extern MLX90621 thermal_sensor; //no getters for now
+
+#include "MLX90621.h"
+
+void init_thermal();
+
+extern MLX90621 thermal_sensor; //no getters for now
+void get_max_temp();

### 2020-08-31 documents/paper.tex
Plate reader
Phage run 1

@@
 
-We've got a thing 
-that's called 
-Radar Love
-We've got a wave
-in the air
-
-The phased-array techdemo.
-
 \subfile{title}
@@
 \clearpage
+
+\begin{figure}[H]
+	\makebox[\textwidth][c]{
+		\includegraphics[width=\textwidth*2]{chunk_4_line_2_1.png}
+	}%
+	\caption{Chunk 4, it.is Founda}
+\end{figure}
+
+\clearpage
+
+\begin{figure}[H]
+	\captionsetup{singlelinecheck = false, justification=justified}
+	\centering
+	\includegraphics[width=\textwidth]{chunk_4}
+	\caption{
+		\light{
+		\\
+		We've got a thing\\
+		that's called\\
+		{\it Radar Love}\\}
+		We've got a wave\\
+		in the air}
+\end{figure}
 
@@
 
-There are a substantial number of papers in the literature which show positive effect sizes; these are listed in the bibliography. \\
+There are a substantial number of papers in the literature which show positive effect sizes; a select few of these are listed in the bibliography. \\
 
@@
 \end{autem}
+
+Applying microwave power to the body is already used extensively in diathermy (the internal heating of tissue for therapeutic effect) and hyperthermy (the overheating or cauterization of tissue for destructive effect).
+While most diathermy systems use much lower frequencies for deeper penetration, several papers have explored the 10 GHz band.
+
+Fat and
+
+The penetration of microwave power is very sensitive to
 

### 2020-08-31 firmware/eppenwolf/src/VCO_driver.cpp

@@ -138,7 +138,9 @@ void master_loop(){
     debug_serial.println("========================================================");
     for(int iter_count = 0; iter_count < 2; iter_count++){ // see if anything's changed
         for(int power_level = 0; power_level < no_power_levels; power_level++){
-
+            if(power_level == 2){
+                debug_serial.println("Remove cover film");
+            }
             for(int cuvette = 0; cuvette < no_cuvettes; cuvette++){
                 set_VCO(0,0);
 

### 2020-09-04 documents/acknowledgement.tex
Minted garbage
Quick ol' FDTD sim of lung

@@
+%!TeX root = acknowledgement
+\documentclass[paper.tex]{subfiles}
+\begin{document}
+
 \clearpage
@@
 
-This paper would have been absolutely impossible without the support of hundreds of open-source software packages, ranging from monolithic industry-supported tools like Paraview and Chimera to poorly-compensated but equally invaluable scripts like zonca.
+Thanks to (Dr. ) Peter Barfuss for spending time reviewing drafts.
+
+This paper would have been absolutely impossible without the support of thousands of open-source software packages, ranging from monolithic industry-supported tools like Paraview and Chimera to poorly-compensated but equally invaluable scripts like zonca.
 Thank you to all the dedicated authors that develop and maintain these tools.
@@
 
-Dr. Dainis' videos on microbiological technique were also useful. The Thought Emporium's videos on PCB prototyping and
+Dr. Alex Dainis' videos on microbiological technique were also useful. The Thought Emporium's videos on PCB prototyping and
 
@@
 
-Thanks to L.H. for wisdom regarding this project; P.B and H.P. and ice9 for tolerating midnight ramblings and M.Q. for the hug.
+Thanks to L.H. for wisdom regarding this project; and H.P. and i.9. for tolerating midnight ramblings and M.Q. for the hug.
 
@@
 
-The authors acknowledge the Computational Electromagnetics Group at The University of Texas at Austin for developing and making the AustinMan and AustinWoman human body models available at https://sites.utexas.edu/austinmanaustinwomanmodels/.
+The authors acknowledge the Computational Electromagnetics Group at The University of Texas at Austin for developing and making the AustinMan and AustinWoman human body models unavailable at https://sites.utexas.edu/austinmanaustinwomanmodels/.
 
@@
 {\Large <3}
+
+\end{document}

### 2020-09-04 documents/safety.tex
Quick ol' FDTD sim of lung

@@
 
-Because this is an ostensibly novel and niche mechanism, it may behoove us to breifly review the biological basis for the safety limits set by standards organizations.
-\footnote{The idea of biological microwave resonances appears to have originated in [Frohlich 1968, 1980].} a loophole in the guidelines
+Because this is an ostensibly novel and niche mechanism, it may behoove us to briefly review the biological basis for the safety limits set by standards organizations.
+\footnote{The idea of biological microwave resonances appears to have originated in [Frohlich 1968, 1980].}
 

### 2020-09-04 electronics/simple_fdtd/run/dipole_applicator.py

@@ -1,0 +1,88 @@
+# import torch
+# import numpy as np
+# import gc
+# torch.cuda.empty_cache()
+#
+# gc.collect()
+
+# np.seterr(all='raise')
+# torch.autograd.set_detect_anomaly(True)
+import fdtd_PCB_extensions as fd
+from fdtd_PCB_extensions import fdtd
+from fdtd_PCB_extensions import X,Y,Z, gaussian_derivative_pulse
+from scipy.constants import mu_0, epsilon_0
+import scipy.constants
+from math import sin, pi, pow, exp, sqrt
+import time
+import os
+import matplotlib.pyplot as plt
+import copy
+from scipy.signal import gausspulse
+import dill
+from pytexit import py2tex
+import pickle
+
+import numpy as np
+import math
+
+
+fdtd.set_backend("torch.cuda.float32")
+
+
+sys.path.append('/home/arthurdent/covidinator/biology/FDTD/')
+import tissue
+
+# fdtd.set_backend("numpy")
+
+#include store.py
+import sys
+sys.path.append('/home/arthurdent/covidinator/electronics/')
+import store
+
+os.system("rm dumps/*")
+os.system("rm data/*")
+
+#Polycarb. permittivity @ 10 GHz: 2.9 [10.6028/jres.071C.014] - conductivity is very low, no need for absorb.
+#Water permittivity @ 10 GHz: 65 - use AbsorbingObject
+
+
+pcb = fd.PCB(0.002, xy_margin=15, z_margin=15)
+fd.initialize_grid(pcb,int((sim_width)/pcb.cell_size),int((microstrip_length)/pcb.cell_size),
+                                int(0.0025/pcb.cell_size), courant_number = 0.4)
+
+
+
+fd.dump_to_vtk(pcb,'dumps/test',0)
+
+dipole_source_position = 0
+
+print_step = 500
+dump_step = 2e-12
+
+prev_dump_time = 0
+
+f = 8e9
+while(pcb.time < (2.0 * 2.0 * pi * f)):
+
+    source_voltage = sin(pcb.time * 2.0 * pi * f)
+    print(source_voltage)
+
+    current = pcb.component_ports[0].get_current(pcb)
+    #[Luebbers 1996]
+
+    source_resistive_voltage = (50.0 * current)
+
+
+    pcb.component_ports[0].set_voltage(pcb, source_voltage + source_resistive_voltage)
+
[…]

### 2020-09-08 documents/application.tex
Bunch of simulations, bunch of garbage

%!TeX root = application
\documentclass[paper.tex]{subfiles}
\begin{document}

Applying microwave power to the body is already used extensively in diathermy (the internal heating of tissue for therapeutic effect) and hyperthermy (the overheating or cauterization of tissue for destructive effect). While the majority of diathermy systems use much lower frequencies  for deeper heating penetration, several papers have explored the 10 GHz band.

Industry Canada limits on the instantaneous electric field anywhere inside the body are $1.35 \times 10^{-4}$ V/m $\times$ Hz (\cite{RSS1022015}, Table 4) - that is, $0.81 \times 10^6$ V/m @ 6 GHz to $1.2 \times 10^6$ V/m @ 9 GHz. It should be noted that more recent standards have abandoned instantaneous electric field limits, finding that they have little biological rationale (\cite{C95}, B.4.3, {\it Rationale for pulsed RF field limits}).

\footnote{In our case, it seems to make the most sense to discuss the attenuation of the electric field, V/m, rather than the field power (also referred to as the {\it intensity}),\Wsqm, since the inactivation seems most closely related to the former. Penetration depth refers to the depth at which the power is reduced by 1/$e$; skin depth, where the electric field is 1/$e$. The penetration depth is simply half the skin depth.\cite{Penetration2019a}}

Considering the electric field skin depth of average lung tissue\cite{gabriel1996compilation} (which changes considerably based on )

\footnote{It should also be noted that at very specific pulsed regimes at millimeter wavelengths (far beyond our study) mere adherence to the letter of the law may not be sufficient for protection\cite{Limitations}.}

6 cm of l

The

Fat and

The penetration of microwave power is very sensitive to

Conduction effects. Because the transmission line voltage only goes as the to the square root of the input power

There seems to be some sort of focusing effect which makes internal bronchoscopic treatment slightly more effective than might be expected.

My kingdom for a Bragg peak!

\clearpage
\printbibliography[heading=none, title={}, keyword={Flagship}]
\printbibliography[heading=none, title={}, keyword={standards}]

\end{document}

### 2020-09-08 documents/paper.tex
Bunch of simulations, bunch of garbage

@@
 
+Industry Canada limits on the instantaneous electric field anywhere inside the body are $1.35 \times 10^-4$ V/m * Hz ()\cite{RSS1022015}, Table 4), $0.81 \times 10^6$ V / m \@ 6 GHz to $1.2 \times 10^6$ / m \@ 9 GHz
+
+6 cm of l
+
+The
+
 Fat and
@@
 The penetration of microwave power is very sensitive to
+
+Conduction effects. Because the transmission line voltage only goes as the to the square root of the input power
+
+There seems to be some sort of focusing effect which makes internal bronchoscopic treatment slightly more effective than might be expected.
 

### 2020-09-08 electronics/simple_fdtd/fdtd_PCB_extensions/fdtd_PCB_extensions/tissue.py

@@ -160,44 +160,56 @@ def voxel_to_fdtd_grid_import(grid, raw, import_offset, voxel_file_cell_size, fd
     # a.repeat(upsample, axis=0).repeat(upsample, axis=1)
     #just shift array by some to offset
 
+    #
+    # if(not isinstance(fdtd.backend, NumpyBackend)):
+    #     active_tissue = bd.zeros((grid.Nx-2*pml_,grid.Ny,grid.Nz,3)).bool()
+    #     inverse_permittivity = bd.ones((grid.Nx,grid.Ny,grid.Nz,3))
+    #     absorption_factor = bd.zeros((grid.Nx,grid.Ny,grid.Nz,3))
+    # else:
+    #     active_tissue = np.zeros((grid.Nx,grid.Ny,grid.Nz,3), dtype=bool)
+    #     inverse_permittivity = np.ones((grid.Nx,grid.Ny,grid.Nz,3), dtype=fdtd.backend.float)
+    #     absorption_factor = np.zeros((grid.Nx,grid.Ny,grid.Nz,3), dtype=fdtd.backend.float)
+    #
+    #
 
-    if(not isinstance(fdtd.backend, NumpyBackend)):
-        active_tissue = bd.zeros((grid.Nx,grid.Ny,grid.Nz,3)).bool()
-        inverse_permittivity = bd.ones((grid.Nx,grid.Ny,grid.Nz,3))
-        absorption_factor = bd.zeros((grid.Nx,grid.Ny,grid.Nz,3))
-    else:
-        active_tissue = np.zeros((grid.Nx,grid.Ny,grid.Nz,3), dtype=bool)
-        inverse_permittivity = np.ones((grid.Nx,grid.Ny,grid.Nz,3), dtype=fdtd.backend.float)
-        absorption_factor = np.zeros((grid.Nx,grid.Ny,grid.Nz,3), dtype=fdtd.backend.float)
-
-
+    conductivity = bd.zeros((100,100,100,3))
+    permittivity = bd.ones((100,100,100,3))
 
     for i in np.unique(raw):
         if(i in exclude):
             continue
-
-        i = int(i)
-        dielectric_constant, conductivity, penetration_depth = lookup_tissue_properties(i, center_frequency)
-        conductivity = conductivity * (fdtd_grid_cell_size / epsilon_0) #flaport's units
-
-        cell_indices = np.where(raw == i)
-
-        inverse_permittivity[cell_indices] /= dielectric_constant
-
[…]

### 2020-09-08 electronics/simple_fdtd/fdtd_PCB_extensions/fdtd_PCB_extensions/visualize.py

@@ -36,8 +36,13 @@ def dump_to_vtk(pcb, filename, iteration, Ex_dump=False, Ey_dump=False, Ez_dump=
     if(objects_dump):
         objects = np.zeros_like(E_copy[:,:,:,X])
         for obj in pcb.grid.objects:
-            objects[obj.x.start:obj.x.stop, obj.y.start:obj.y.stop, obj.z.start:obj.z.stop] = obj.permittivity
-        objects += cu_mask*2
+            try:
+                objects[obj.x.start:obj.x.stop, obj.y.start:obj.y.stop, obj.z.start:obj.z.stop] = obj.permittivity.cpu().numpy()
+            except:
+                objects[obj.x.start:obj.x.stop, obj.y.start:obj.y.stop, obj.z.start:obj.z.stop] = obj.permittivity.cpu().numpy()[:,:,:,0]
+
+        objects[cu_mask] = 2
+        # objects += cu_mask*2
         cellData['objects'] = objects
 
     if(ports_dump):

### 2020-09-09 documents/application.tex
Turbidimeter actually working now

@@
 While the majority of diathermy systems use much lower frequencies for deeper heating penetration, several papers have explored the 10 GHz band.
+
+High microwave frequencies are very strongly attenuated by tissue. However, we have a large amount of margin in the electric field - 4 orders of magnitude - that we can trade for penetration depth.
+
+\cite{neuroinvasive2020} \cite{situ2020}
 
@@
 
-Considering the electric field skin depth of average lung tissue\cite{gabriel1996compilation} (which changes considerably based on )
+Considering only the electric field skin depth\cite{Safety2001}\cite{Physical1982} of average lung tissue\cite{gabriel1996compilation}\cite{Dielectricb}\cite{Dielectric}\cite{Tissue2018} (which changes considerably based on inflation), on the face of it is possible to achieve a field of 150 V/m at a very reasonable depth of 60 mm.
+We could not find any data on the distribution of gas exchange throughout the cross-section of the lung; however,
 
 \footnote{It should also be noted that at very specific pulsed regimes at millimeter wavelengths (far beyond our study) mere adherence to the letter of the law may not be sufficient for protection\cite{Limitations}.}
-
-6 cm of l
-
-The
-
-Fat and
-
-The penetration of microwave power is very sensitive to
 

### 2020-09-09 documents/application.tex
Culturing a whole crapload of bacteria

--- 2020-09-08 documents/application.tex
@@
 
+SARS is found widely distributed throughout many of the most favoured organs \cite{Organ2004}, shielded by an average of 4 cm of chest wall [Schroeder 2013]; so safe external treatment of the body is unlikely.
+
+\cite{neuroinvasive2020} \cite{situ2020}
+
+However, it would be an understatement to say that destruction of lung tissue is significant in the lethality of SARS [Nicholls 2006].
+
+A bronchoscopic technique may therefore be effective, very similarly to that demonstrated by [Yuan 2019]: in adults, the bronchi are less than 2 mm thick [Theriault 2018] and the lungs themselves are only on the order of 7 mm thick [Chekan 2016].
+The main bronchus is about 8 mm in diameter.
+
 Applying microwave power to the body is already used extensively in diathermy (the internal heating of tissue for therapeutic effect) and hyperthermy (the overheating or cauterization of tissue for destructive effect).
@@
 
+High microwave frequencies are very strongly attenuated by tissue. However, we have a large amount of margin in the electric field - 4 orders of magnitude - that we can trade for penetration depth.
+
 Industry Canada limits on the instantaneous electric field anywhere inside the body are $1.35 \times 10^{-4}$ V/m $\times$ Hz (\cite{RSS1022015}, Table 4) - that is, $0.81 \times 10^6$ V/m @ 6 GHz to $1.2 \times 10^6$ V/m @ 9 GHz.
-It should be noted that more recent standards have abandoned instantaneous electric field limits, finding that they have little biological rationale (\cite{C95}, B.4.3, {\it Rationale for pulsed RF field limits}).
+It should be noted that more recent standards have abandoned instantaneous electric field limits, finding that they have little biological rationale (\cite{C95}, B.4.3, {\it Rationale for pulsed RF field limits}).\footnotemark
 
-\footnote{In our case, it seems to make the most sense to discuss the attenuation of the electric field, V/m, rather than the field power (also referred to as the {\it intensity}),\Wsqm, since the inactivation seems most closely related to the former.
+$$S = \frac{|E|^2}{Z_0}$$
+
+\footnotetext{It should also be noted that at very specific pulsed regimes at millimeter wavelengths (far beyond our study) mere adherence to the letter of the law may not be sufficient for protection\cite{Limitations}.}
+
+Considering only the electric field skin depth\footnotemark\cite{Safety2001}\cite{Physical1982} of average lung tissue\cite{gabriel1996compilation}\cite{Dielectricb}\cite{Dielectric}\cite{Tissue2018} (which changes considerably based on inflation), at 8 GHz it appears to be possible to achieve the required field of 150 V/m at a very reasonable depth of 60 mm.
+We could not find any data on the distribution of gas exchange throughout the cross-section of the lung.
+
+Two complications present themselves. An annoying layer of muscle
+
+From cursory simulations, it seems quite difficult to generate such high electric fields with a small dipole antenna in the bronchi unless almost implausibly high powers are input.
+On the other hand, well-tuned.
+Second, these results are sensitive to the precise
+
+\footnotetext{In our case, it seems to make the most sense to discuss the attenuation of the electric field, V/m, rather than the field power (also referred to as the {\it intensity}),\Wsqm, since the inactivation seems most closely related to the former.
 Penetration depth refers to the depth at which the power is reduced by 1/$e$; skin depth, where the electric field is 1/$e$.
 The penetration depth is simply half the skin depth.\cite{Penetration2019a}}
-
-Considering the electric field skin depth of average lung tissue\cite{gabriel1996compilation} (which changes considerably based on )
-
-\footnote{It should also be noted that at very specific pulsed regimes at millimeter wavelengths (far beyond our study) mere adherence to the letter of the law may not be sufficient for protection\cite{Limitations}.}
-
-6 cm of l
-
-The
-
-Fat and
-
-The penetration of microwave power is very sensitive to
 
@@
 There seems to be some sort of focusing effect which makes internal bronchoscopic treatment slightly more effective than might be expected.
+
+The 8 GHz tone does not necessarily need to be the fundamental. A carrier wave with a more deeply penetrating wavelength could be used.
+
+If the carrier is lower in frequency, non-linear materials\cite{Theory1973} will be needed for harmonic generation, or implantable resonators and re-radiators.
+There are a few paramagnetic contrast agents used in MRI that might be useful for this if the efficiency is sufficient.
+If the carrier is higher, it can simply be modulated with an 8 GHz tone.
+In the latter case, there are so-called 'optical windows' in the absorption spectra of tissues, particularly in the near-IR range; however, none seem sufficiently transparent to be useful.
 

### 2020-09-09 documents/paper.tex
Culturing a whole crapload of bacteria

@@
 
-Via [Hand 1982], the $E_{mag}=1/e$ penetration depth\footnote{"skin skin depth?"} is approximately 40 mm for 'dry' tissues and 5 mm for 'wet'.
-
-SARS is found widely distributed throughout many of the most favoured organs \cite{Organ2004}, shielded by an average of 4 cm of chest wall [Schroeder 2013]; so safe external treatment of the body is unlikely.
-
-However, destruction of lung tissue appears to be significant in the lethality of SARS [Nicholls 2006].
-
-A bronchoscopic technique may therefore be effective, very similarly to that demonstrated by [Yuan 2019]: in adults, the bronchi are less than 2 mm thick [Theriault 2018] and the lungs themselves are only on the order of 7 mm thick [Chekan 2016].
-
-The main bronchus is about 8 mm in diameter, which is smaller than the patch antenna used here; a monopole (or multiple, phased monopoles) like is probably more suitable.
-
 {\color{red} speculation \{ }
@@
 \paragraph{\textbf{Subharmonics}}\
-
-The 8 GHz wave need not be the fundamental.
-A modulated carrier wave with a more deeply penetrating wavelength which then locally interferes to produce the 8 GHz tone within the tissue could be useful.
-
-The penetration depth shortens as frequency increases, until the so-called 'optical windows' in the absorption spectra of tissues, particularly in the near-IR range.
 

### 2020-09-09 electronics/simple_fdtd/run/waveguide_applicator.py

@@ -119,15 +119,6 @@ while(pcb.time < (2.0 * 2.0 * pi * f)):
 
     source_resistive_voltage = (50.0 * current)
 
-    pcb.grid.E[dipole_source_position[X]:dipole_source_position[X]+1,\
-                dipole_source_position[Y]:dipole_source_position[Y]+1,\
-                    dipole_source_position[Z]+1:dipole_source_position[Z]+1+dipole_length,:] = 0 # zero dipole arm voltage
-
-    pcb.grid.E[dipole_source_position[X]:dipole_source_position[X]+1,\
-                dipole_source_position[Y]:dipole_source_position[Y]+1,\
-                    dipole_source_position[Z]-dipole_length:dipole_source_position[Z],:] = 0 # zero dipole arm voltage
-
-
     pcb.grid.E[dipole_source_position[X],dipole_source_position[Y],z_slice,Z] = sqrt(epsilon_0) * ((source_voltage) / (pcb.cell_size))
     #
 

### 2020-09-09 documents/distribution.tex
Assay still didn't work! Darnit!

%!TeX root = distribution
\documentclass[paper.tex]{subfiles}
\begin{document}

\cite{Efficient2015} theoretically model the virus to determine the minimum electric field required to destroy it.

They assume that the virus is a simple damped harmonic oscillator, where the 'core' and 'shell' oscillate in opposition.

They determine the net charge experimentally from microwave absorption measurements.

Since [Yang] try to compute the {\it threshold} field to obtain some amount of inactivation, they use a value of 400 piconewtons for the breaking stress of the envelope, obtained from \cite{Bending2011}. This threshold value agrees very well. However, \cite{Bending2011} also mentions that

\begin{quote}
	More than 95\% [of] puncture events occurred above 0.4 nN.
\end{quote}

The liposome breaking force is distributed in an obstinately non-gaussian bimodal manner, so we override the covariance matrix and introduce a gaussian KDE sampled from the force histogram in \cite{Bending2011}.

"95%.".

The distribution of breaking strengths in [Li 2011] (Figure 5b) is bimodal, and a naive gaussian fit does not produce the above 95\% figure.

Smudged

The simple-harmonic

This problem has a long history, stretching back to Cole-Cole's landmark paper in 1942\cite{Dispersion1941}.

T4 bacteriophage has far greater restraint, with only a 2.5\% $\pm \sigma$ variation in the icosahedral head dimensions \cite{Head1988}. \footnote{}

This also

Since this covariance process will have to be repeated for SARS-NCoV-2 - that is, the CoV for NCoV -

\begin{center}
	\begin{tabular}{||c c c c||} 
		\hline
		Col1 & Col2 & Col2 & Col3 \\ [0.5ex] 
		\hline\hline
		1 & 6 & 87837 & 787 \\ 
		\hline
		2 & 7 & 78 & 5415 \\
		\hline
		3 & 545 & 778 & 7507 \\
		\hline
		4 & 545 & 18744 & 7560 \\
		\hline
		5 & 88 & 788 & 6344 \\ [1ex] 
		\hline
	\end{tabular}
\end{center}

\end{document}

### 2020-09-09 documents/paper.tex
Assay still didn't work! Darnit!

@@
 \clearpage
-{\Large \it Talkin' 'bout the Variation}\\
-
-To re-cap, [Yang 2015] theoretically model the virus to determine the minimum electric field required to destroy it.
-
-They assume that the virus is a simple damped harmonic oscillator, where the 'core' and 'shell' oscillate in opposition.
-
-They determine the net charge experimentally from microwave absorption measurements.
-
-Since [Yang] try to compute the {\it threshold}, they use a value of 400 pN for the breaking strength of the envelope, obtained from [Li 2011]. However,
-
-"95%.".
-
-\begin{center}
- \begin{tabular}{||c c c c||} 
- \hline
- Col1 & Col2 & Col2 & Col3 \\ [0.5ex] 
- \hline\hline
- 1 & 6 & 87837 & 787 \\ 
- \hline
- 2 & 7 & 78 & 5415 \\
- \hline
- 3 & 545 & 778 & 7507 \\
- \hline
- 4 & 545 & 18744 & 7560 \\
- \hline
- 5 & 88 & 788 & 6344 \\ [1ex] 
- \hline
-\end{tabular}
-\end{center}
 

### 2020-09-10 documents/distribution.tex
Drum shaker thing

@@
 
-Since [Yang] try to compute the {\it threshold} field to obtain some amount of inactivation, they use a value of 400 piconewtons for the breaking stress of the envelope, obtained from \cite{Bending2011}.
-This threshold value agrees very well.
+Since \cite{Efficient2015} try to compute the {\it threshold} field to obtain some amount of inactivation, they use a value of 400 piconewtons for the breaking stress of the envelope, obtained from \cite{Bending2011}.
+This threshold value agrees very well with their experimental data.
 However, \cite{Bending2011} also mentions that
@@
 
-This problem has a long history, stretching back to Cole-Cole's landmark paper in 1942\cite{Dispersion1941}.
+This problem has a long history, stretching back to Cole-Cole's landmark paper in 1942\cite{Dispersion1941} and \cite{Electrical1941}.
 
-T4 bacteriophage has far greater restraint, with only a 2.5\% $\pm \sigma$ variation in the icosahedral head dimensions \cite{Head1988}. \footnote{}
+\begin{quote}
+	As Fuoss and Kirkwood have shown, it is possible to calculate the distribution necessary to account for any given experimental results from the observed $\epsilon''$ - frequency relation.
+\end{quote}
+
+Within a sample of a single species, there is $\approx$ 12.7\%  ($109 \pm 16.65 \text{ nm}$\cite{lauffer1944biophysical}, $115 \pm 12 \text{ nm}$ \cite{Characterization1984}) variation in diameter and  \cite{Characterization1984} variation in mass.
+
+Note that, per \cite{lauffer1944biophysical}, of Inf.
+A and B, "the infectious particles have diameters within the range 80 to 135[nm]".
+\cite{Efficient2015}'s MDCK plaque assay is already sensitive to infectivity; the extreme-sized non-infective mutants would already be filtered out.
+Their PCR assay might not be; the DNA of all non-infectious mutants would be considered.
+
+Worse still, influenza exhibits pleiomorphy \cite{Influenza2006};
+
+NCoV is closer to \cite{Viral2020}, but does not exhibit pleiomorphy.
+
+A cursory fit found parameters $\bar{\text{Q}}$=3.736,  $\sigma \ \text{Q} = $0.738, $\bar{F}_{res}=$8.606 GHz and $\sigma {F_{res}}=$1.073 and covariance of +1.001.
+This describes the observed spectrum equally well:
+
+Whether these values also explain the other datasets in \cite{Efficient2015}, such as the inactivation threshold vs frequency has not yet been determined.
+
+Plugging a (single, non-distributed, which must be fixed) Q of 3.75 into the above breaking force distribution, and applying some guesses for the covariance of various parameters, we get:
+
+								Yang get:
+6th percentile: 59.234       68 V/m
+38th percentile: 127.376		87 V/m
+63th percentile: 186.803		171 V/m
+90th percentile: 298.882     100\% 275 V/m
+99.9th percentile: 565.126
+
+Of course, 
+\begin{quote}
+	With four parameters I can fit an elephant, and with five I can make him wiggle his trunk. \\- J.v.N
+\end{quote}
+
+and here we have some dozen parameters. So these approximations should be regarded with great skepticism.
+
+T4 bacteriophage has far greater restraint, with only a 2.5\% $\pm \sigma$ variation in the icosahedral head dimensions \cite{Head1988}.\footnotemark
+
+\footnotetext{T4 also occasionally finds itself as an isometric mutant (See PDB 5VF3).}
 
@@
 
-Since this covariance process will have to be repeated for SARS-NCoV-2 - that is, the CoV for NCoV -
+Since this entire covariance process will have to be repeated for SARS-NCoV-2 - that is, the CoV for NCoV, we have not bothered to fine-tune any of these fits.
+This must still be regarded as only a hypothesis.
 

### 2020-09-10 documents/supplemental.tex
Quick ol' FDTD sim of lung
Wonderful turbidimeter

@@
+%!TeX root = supplemental
 \documentclass[paper.tex]{subfiles}
@@
 \rule{\linewidth}{0.2pt}
+
+\PRLsep{{\itshape Turbidimeter }}
+
+Essentially the only method of determining the activity of phage is to have it infect a suitable host.
+
+Typically, this is done either in a large tube or a flat-sided optical cuvette.
+
+Because the variation in the optical density is quite small, this poses some rather.
+
+A small vial of liquid has a much larger surface area relative to its thermal mass.
+sis removed, the temperature drops very rapidly; if the temperature drops outside the physiological range of about 33-40 C, growth is stunted.\cite{effect2003}
+
+As a faculative aerobe, E.coli requires a concentration of oxygen to be present in the mixture for speedy replication \cite{Effect1965}; and this supply must also be kept sterile.
+One method to ensure this is by using a bubbler aerator; Carolina recommends an aquarium pump with cotton-ball filters.
+
+Another method, often used in microfluidics\cite{Microfluidic}, is that of \cite{method1951}; manganese dioxide catalyzed decomposition of hydrogen peroxide.
+MnO2 is readily obtained from alkaline batteries; and in this case no sterility issues are presented.
+However, it is not obvious how all h2o2 vapor can be prevented from contacting the culture.
+
+Bottles of zero air may be more effective.
+
+In commercial fluid transfer machines, this is often resolved by HEPA filtering the input to the cabinet.
+
+Shaking incubators, which simply rock the
+
+In our case, ensuring that a great deal of headspace was present in the tube was sufficient for brief growth.
+
+As the size of the well decreases, the Reynolds number also decreases \footnote{In fact, in the case of a circular well, it's not obvious that this is the case - the cross section decreases faster than the characteristic length}, and turbulent flow is greatly hampered.
+
+Using 2.5 mm diameter x 3 mm high wells cut in polycarbonate and sealed with clear packing tape. However, the presence of small bubbles in the headspace of the wells prevented a consistent reading.
+
+We tried simply adding 1 uL of culture to the microscope slide;
+
+The 8-bit resolution of most cameras did not seem sufficient to discern the turbidity.
+
+\cite{Vision2016} use an ingenious technique.
 

### 2020-09-10 documents/supplemental.tex
finally

@@
 A small vial of liquid has a much larger surface area relative to its thermal mass.
-sis removed, the temperature drops very rapidly; if the temperature drops outside the physiological range of about 33-40 C, growth is stunted.\cite{effect2003}
+sis removed, the temperature drops very rapidly; if the temperature drops outside the physiological range of about 33-40 C, growth is stunted \cite{effect2003}.
+\cite{growth1946}.
 
@@
 
+Even slight rotation of the tube, such that the graduations
+
+"Chromogenic" substances \cite{Fluorogenic1991}, or the degradation of various dyes like Methylene Blue.
+
 Using 2.5 mm diameter x 3 mm high wells cut in polycarbonate and sealed with clear packing tape. However, the presence of small bubbles in the headspace of the wells prevented a consistent reading.
@@
 
-The 8-bit resolution of most cameras did not seem sufficient to discern the turbidity.
+The 8-bit resolution and dynamic range of most cameras did not seem sufficient to discern the turbidity; and masking and correcting for
 
-\cite{Vision2016} use an ingenious technique.
+\cite{Vision2016} use an ingenious technique. A background with sharp light-to-dark edges is used. Slicing the image into chunks only slightly larger than the object,
+
+Another very interesting technique is that of \cite{Study2003},
 

### 2020-09-10 software/turbidimeter_samples/turbidimeter.py

@@ -1,16 +1,31 @@
 import cv2
 import numpy as np
 from matplotlib import pyplot as plt
+import serial
 
-background_image = cv2.imread('my_photo-1.jpg',0)
-turbid_img = cv2.imread('my_photo-5.jpg',0)
-turbid_img_2 = cv2.imread('my_photo-4.jpg',0)
-clear_img = cv2.imread('my_photo-2.jpg',0)
-clear_img_2 = cv2.imread('my_photo-3.jpg',0)
+from time import sleep
+import time
+import sys
+from scipy.signal import find_peaks
+from matplotlib import pyplot as plt
+
+# background_image = cv2.imread('my_photo-1.jpg',0)
+# turbid_img = cv2.imread('my_photo-7.jpg',0)
+# turbid_img_2 = cv2.imread('my_photo-8.jpg',0)
+# clear_img = cv2.imread('my_photo-9.jpg',0)
+# clear_img_2 = cv2.imread('my_photo-10.jpg',0)
 
 #https://stackoverflow.com/questions/48482317/slice-an-image-into-tiles-using-numpy/48483743
 
-print(np.shape(clear_img))
+# print(np.shape(clear_img))
+
+
+f = open(sys.argv[2], "a")
+ser = serial.Serial(sys.argv[1], 115200, timeout=2)
+
+
+
+# detector = cv2.QRCodeDetector()
 
 def blockshaped(arr, nrows, ncols):
     """
@@ -28,150 +43,105 @@ def blockshaped(arr, nrows, ncols):
                .reshape(-1, nrows, ncols))
 
 
-chunks =  blockshaped(clear_img, 144, 160)
+while True:
 
-t = []
-for j in chunks:
-    i = np.fft.fft2(j)
-    t.append(np.linalg.norm(i[:,0:np.shape(i)[1]//4])/np.linalg.norm(i[:,np.shape(i)[1]//4:-1]))
-
-print(np.max(t))
-
-
-chunks =  blockshaped(clear_img_2, 144, 160)
-
-t = []
-for j in chunks:
-    i = np.fft.fft2(j)
-    t.append(np.linalg.norm(i[:,0:np.shape(i)[1]//4])/np.linalg.norm(i[:,np.shape(i)[1]//4:-1]))
-
-print(np.max(t))
-
-#
-
-t = []
-chunks =  blockshaped(turbid_img, 144, 160)
-for j in chunks:
-    i = np.fft.fft2(j)
[…]

### 2020-09-11 documents/lessons_learned.tex
Pouring agars

--- 2020-08-28 documents/supplemental.tex
@@
+%!TeX root = lessons_learned
 \documentclass[paper.tex]{subfiles}
@@
 
-\clearpage
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-{\Huge Captain's Log, Supplemental}\\
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\paragraph{Molecular dynamics simulation}
-\
-%\begin{multicols}{1}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-It was originally expected that a large part of this work would be done in-silico, as we did not anticipate having access to suitable RF test equipment.
-
-Some time was spent attempting to set up a molecular dynamics toolchain capable of simulating an entire virus.
-
-Having an approximate simulation of the this technique would be useful for a number of reasons:
-
-We would have a better idea of the transferability to SARS, without wasting the time of experts with BSL-3/4 labs.
-
-The impulse could be subjected to the same optimization as the RF feedback loop. A number of parameters (such as phase, polarization)
-
-Coarse-graining also greatly increases the allowable timestep.
-
-We also did not understand the *confined* part in the *confined* acoustic resonance.
-
-Simulating the aggregate bose condensate wavefunction is well beyond us.
-
-Both finite-element, molecular-dynamics, and stiffness-eigenvalue normal mode techniques have been used to great effect for this purpose.
-
-%\end{multicols}
-
-\PRLsep{{\itshape Virus structural data }}
-
-One extreme can be seen in
-
-Because CryoEM is sensitive to the
-
-\clearpage
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-{\Large Optical centrifuge polarization chirp}\\
-\begin{multicols}{1}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\includepdf[
-    %% Include all pages of the PDF
-    pages=-,
-    %% make this page have the usual page style
-    %% (you can change it to plain etc). By default pdfpages
-    %% sets the pagecommand to \pagestyle{empty}
-    pagecommand={\thispagestyle{empty}},  
-    %% Add a "section" entry to the ToC with the heading
-    %% "Quilling Shapes" and the label "sec:shapes"
-    addtotoc={1,section,1,Quilling Shapes,sec:shapes}]
-%% The pdf file itself
-{optical_centrifuge.pdf}
-
-\includepdf[
-%% Include all pages of the PDF
-pages=-,
-%% make this page have the usual page style
-%% (you can change it to plain etc). By default pdfpages
-%% sets the pagecommand to \pagestyle{empty}
-pagecommand={\thispagestyle{empty}},  
-%% Add a "section" entry to the ToC with the heading
-%% "Quilling Shapes" and the label "sec:shapes"
-addtotoc={1,section,1,Quilling Shapes,sec:shapes}]
-%% The pdf file itself
-{biology.pdf}
-
-\end{multicols}
-
-Contrary to some [Hardell 2017] reports, we do not find the FCC and ICNIRP to be significantly affected by special interest groups; their rationales appear to be transparent.
-[FCC-19-126A1], for instance, is a particularly entertaining memorandum:
-
-\begin{quote} 
-Similarly, IEEE-ICES urges the Commission to adopt a higher SAR exposure limit of 2 W/kg averaged over 10 g.
-[snip] We are not persuaded that the IEC standard should be adopted at this time.", "Medtronic and the AAMI-CRMD recommend a more relaxed threshold of 20 mW.
-We decline to increase the 1-mW threshold.".
-
-\end{quote}
-
-Things heating up at the Microwave Safety fandom.
-
-\clearpage
-\rule{\linewidth}{0.2pt}
-
-We do not intend to denigrate the work or otherwise cast aspersions on the authors of the mentioned papers; their experiment extremely well-designed and performed.
-
-However, since the result is unexpected, we would like to mention a few means by which the effect described could be achieved without strong non-thermal coupling.
-
-\begin{quote}
-
- To confirm that our observation is not due to the microwave thermal heating effect, we had monitored the sample temperature change during the microwave illumination experiments with a radiated power density of 486W/m2 at a frequency of 6GHz by using an infrared thermal imaging camera with a temperature accuracy of 0.05°C (CHCT, P384-20).
-The temperature rise after 15 minutes radiation was 7°C, from 27.5°C up to 34.5°C.
-We thus exclude the possible contribution of microwave thermal heating effect to inactivation H3N2 viruses under our experimental condition.
-
-\end{quote}
-
-The frequency-dependent inactivation result in Figure 4b of \cite{Efficient2015} is difficult to explain without invoking non-thermal mechanisms.
-Only one  It is not mentioned how this applied power level was measured.
-
-The amplifier in question is not available on the supplier's website \cite{Microwaved} has gain flatness of 3.5 dB over 6-12 GHz - just over 1 octave.
-The amplifier used in [Hung] is not mentioned; because the frequency range mentioned (6 GHz to 18 GHz) is the same as that of the amplifier, we assume the same amplifier was used.
-
-If the amplifier happened to be matched better at 8 GHz than 12 GHz.
-
-QPJ-06183640
-
-Similarly, the gain of the EM-6969 antenna\cite{EM6969} varies from 17 dBi to 21 dBi over the frequency range in Figure 3.
-
-However, that the spectra of all these effects would combine to produce a peak at precisely the resonant frequency determined by the entirely different microwave cuvette is highly implausible; and so Figure 4b really does seem to be good evidence of such an effect.
-
-\clearpage
-\rule{\linewidth}{0.2pt}
-
-There seems to be a discrepancy between \cite{Efficient2015} and our reading of [C95.1-2005].
-
-They use a threshold in open public space of $100(f/3)^{1/5} \text{ W/m}^2$. The 115 W @ 6 GHz figure they provide corresponds to this equation with a coefficient of 100.
-
-For Table 9, general public, the equation is $18.56 (f)^{0.699} \text{ W/m}^2$, or $64.93 \text{ W}/\text{m}^2$ @ 6 GHz.
-
-Different versions of the IEEE standard have used equations of equivalent form but with different coefficients [Wu 2015]; it is entirely possible that we have retrieved the wrong standard.
+\paragraph{Lessons Learned} \
 
@@
 
-\PRLsep{{\itshape Wherein an oscillator is designed }}
-
-Many
-
-Three incorrect pieces of information conspired to lead us to try to develop an inexpensive ultrawideband oscillator.
-
-\begin{itemize}
-	\item The assumption that a broadband frequency sweep would drastically improve the inactivation threshold, and moreover that 
-	\item The ideal 
-	\item The assumption that the only commercially available oscillators in this frequency range were expensive YIG-tuned devices.
-\end{itemize}
-
-There are really two different conflicting criteria:
-
-A low-cost, wide-band
-
-Unfortunately, designing wideband microwave circuits is significantly more difficult than for a particular frequency. Quarter-wavelength
-
-Varactor diodes are a GaAs hyper-abrupt junction diode.
-
-We were warned that this would be difficult:
-
-CEL did not supply a SPICE model for the GaAs FET device used in early prototypes. A FET was originally because a gate is ostensibly easier to bias than a base; but this turned out to be unfounded.
-
-[Steenput 1999] has an interesting analytic method to synthesize a SPICE model suitable for a transient simulations from S-parameter measurements using negative resistances.
-However, this neglects the I/V characteristic.
-
-[Polyfet 1998] describes a simple optimization method to synthesize a SPICE model for an active device, and CEL appnote provides some details for GaAs devices.
-
-\rule{\linewidth}{0.2pt}
-
-OpenEMS is excellent, with Python bindings, some lumped components, and mesh refinement. However, embarrassingly, we were not able to resolve all the dependency issues in order to install it.
-
-\paragraph{Biasing}\
-
-In our simulations, the varactor-tuned feedback circuit appeared to be particularly sensitive to the introduction of bias-tees.
-
-The gate must be weakly pulled to ground, otherwise stray charge destroys the oscillation.
-
-\fancyhead[C]{style 1 with thin line}
-
-With 0.79 mm FR4 substrate and 0.2 mm (8 mil) wide traces, the maximum impedance achievable was about 115 ohms, which did not appear to be sufficient as an RF choke.
-Use of defected grounds can increase inductance, but this was not evaluated.
-
-If suitably high-impedance traces are not available, a common technique is to use a quarter-wavelength line (approximately 6 mm long with the above parameters at 8 GHz) terminated with a stub to produce a virtual short or open circuit [Seo 2007].
-
-However, reflections from these structures still appeared to distort the frequency/phase response beyond repair, even with ostensibly wideband stubs [Syrett 1980].
-
-\noindent\fbox{\parbox{\linewidth}{
-	Rebuke: despite this blather, many other papers have had success with bias-tees at these frequencies.
-}}
-
-Alternate methods evaluated, failures:
-
-In production, these could be accomodated by graphite-polymer printed resistors.
-
-Odd-pole varactor-loaded combline filters appeared to have excellent phase and frequency response; however, the geometry necessitates low-inductance via stitching to the ground plane.
-
-%\noindent\fbox{\parbox{\linewidth}{
-\begin{autem}
-	{\it autem} Others have had great success with varactor-tuned comblines, especially non-grounded lines.
-\end{autem}
-
-[Tsuru 2008 fig. 10] is an excellent review of various oscillator designs.
-
-The parasitic inductance of common varactors appears to become problematic at these frequencies (but not for non-wideband use).
-
-\paragraph{\textbf{Spacing}}\
-
-FDTD results still yielded some coupling at 2 mm isolation.
-
-\paragraph{\textbf{Via stitching}}\
-
-Rather than the almost universal technique of via stitching components immediately to the ground plane (a tedious process with our prototyping setup), a large ground pour on the component layer was used wherever ground was needed, as mentioned in [Hunter?
-combline].
-Since we use microstrip rather than coplanar waveguide,
-
-Since the ground plane does not participate in the DC bias at all, no vias are required in the final device.
-This means that the drilling, electroless strike and electroplating steps are unnecessary for production.
-
-\PRLsep{{\itshape The wideband oscillator }}
-
-Not having access to any RF equipment, we needed an oscillator tunable over the X-band.
-
-There are many oscillators. The HB100 uses a dielectric resonator, for instance; cavity-based methods with mechanical tuning; active antennas using.
-
-The literature is quite mature, partly due to the FCC's recent ultrawideband communications guides.
-
-As a result of our gross incompetence, the oscillator was designed via an inane, roundabout, and fiendishly tedious manner, and our description of this technique only contributes to the field by being suitable for a dartboard; our analysis can only hold water when combined with paper mache; and a lesser invertebrate in posession of a copy of Grebennikov's excellent Microwave Oscillator Design would have accomplished the task faster.
-
-Designing an oscillator of this type in one step with a few kindergarten equations appears to be well within the reach of modern network analytical techniques.
-Genetic algorithms are quite well matched to this problem, and many commercial software packages are  [computer microwave design book].
-
-We began experimentally by building a scaled version of [Mueller 2008]'s active antenna crudely with copper tape, using a CEL [] GaAs FET.
-
-We then manually tried a number of filter designs, using the manufacturer's S-parameters and QUCS' microstrip approximations.
-This intially appeared to yield good agreement with experiment.
-Peaks in the feedback voltage simulation corresponded approximately with peaks in the observed spectrum.
-[figures from LO prototype N].
-
-A crude, inane, and extremely disorganized trial-and-error procedure was performed for many weeks.
-A wide variety of analytical methods for filter design were attempted [documents/global.ipynb], but simultaneously obtaining the correct phase shift and frequency response was somewhat difficult.
-Adding the parasitic inductance of the varactors always seemed to destroy our most perfect creations.
-
-Using an SIR filter has the added advantage of confusing epidemiologists.
-
-Eventually, QUCS, zonca/python-qucs, and scipy's basinhopper were used with a cost function somewhat similar to that described in [Kaplevich]:
-
-\begin{verbatim}
-    freq_coeff = 1
-    phase_coeff = 1.5
-    ratio_coeff = 0.5
-    insertion_loss_coeff = 0.2
-
-    frequency_cost = freq_coeff * (abs(desired_center_frequency-fb_peak_frequencies[0])/1e9)
-    phase_cost = phase_coeff * abs(1.0 - phase_at_peak)
-    ratio_cost = ratio_coeff * fb_peak_ratio
-    insertion_loss_cost = insertion_loss_coeff*(1.0 - fb_peak_values[0])
-    cost = frequency_cost + phase_cost + fb_peak_ratio + insertion_loss_cost
-\end{verbatim}
-
-Optimizing first for the high frequency, fixing the inductor and microstrip values, and then optimizing for the varactor values at the low frequency.
-
-This produced a seemingly acceptable feedback loop (note the group delay / phase progression):
-
-\includegraphics[scale=1]{LO_2_pole_test.png}
-
-However, when this was built, varactor tuning performance was abysmal, with hops and peaks; and the tuning range was far smaller than expected.
-
-It was thought that a transient simulation - to determine how the spectrum actually evolved - would improve the situation.
-
-As of 0.0.20, QUCS' microstrip models are not yet compatible with transient simulations; and some improved filter designs required simulating coupling between more than two microstrips, which QUCS did not yet support natively.
-
-\begin{figure}[H]
-\includegraphics[width=\textwidth]{3d_spectrum_2.png}
-\end{figure}
-
-The complete transient simulation matched reality very closely.
-
-\begin{figure}[H]
-	\includesvg[width=\textwidth]{wideband_LO_2_simulated_tuning}
- 	\caption{"Wideband VCO 2": BFP620  \\
- 	 Oscillator tuning simulated with electronics/ngspice/oscillator\_designer\_2.py commit <>, eLabID 20200613-d28a8004c...}
-\end{figure}
-
-The oscillator design is a testament  This highlights that a computation is not a substitute for understanding.
-
-The key sticking point seems to be that as frequency increases, using microstrip design techniques, the parasitics of any filter structure are so large that the small change in impedance that the varactors can provide does not tune the circuit by any meaningful amount.
-
-The two varactors on each tuning circuit each contribute 0.7 nH and between 0.35 to 2.4 pF; each blocking capacitor contributes about 0.2 nH.
-The frequency range of the oscillator can be selected by adding between 0.5 nH to 1.5 nH symmetrically to both tuning circuits.
-
-"Using the lead inductances of the bipolar transistor and varactors provides the required value of the base inductance".
-
-Indeed, [Tsuru 2008]'s "tuned circuit" in Fig 8 is, in fact, just the varactors, plus an almost invisible high-impedance line.
-
-The final oscillator is a 'wideband double-tuned varactor VCO', based almost verbatim on [Tsuru 2008] and the reference design in Figure 8.36, p378 of [Grebennikov 2007].
-
-The rest of the papers in the bibliography were highly enlightening regarding the principles of microwave oscillator design.
-
-For ease of design and simulation, selecting a device with both Touchstone S-parameters and SPICE models is greatly preferable.
-
-It is commonly claimed that FR4 is a 'slow' substrate, and that the high loss tangent of ~0.02 makes it unsuitable for microwave systems.
-
-However, with this PCB substrate, the expected loss of only 0.026 dB/mm on signals of minimum 0 dBm is patently acceptable.
-As viruses do not have a discriminating palate, we are also only minimally concerned with $S_{11}$ reflections, noise, or spurs, so precise impedance control is not required; the wideband VCO sweep accomodates for any variations in resonant frequency due to wide manufacturing tolerances.
-
-This topology of oscillator worked marvellously on essentially the first try.
-
-Not having a good analytical understanding, we resorted to using a purely computational method.
-
-In addition, the design of wideband feedback-loop VCOs is a relatively well-explored field, and many reference designs exist.
-
-Merely scaling designs like [] was not effective.
-
-Several analytical filter design methods were
-
-This is apparently known as a "double-tuned" wideband.
-
-Oscillators must meet the Barkhausen criterion:
-
-\begin{itemize}
-
-\item A 360 degree phase shift around the feedback loop (including the phase shift contribution from the amplifier, which itself varies greatly with frequency)
-\item A loop gain $>1.$
-
-\end{itemize}\
-%
-However, a third element is also required:
-%
-\begin{itemize}
-\item A frequency-selective element that restricts oscillation modes and decreases phase noise.
-\end{itemize}
-%
-
-With large feedback-loop structures, such as long PiN-switched phasing lines, proximity effects from nearby flesh would detune the oscillator significantly.
-
- design of a triple-tuned oscillator.
-
-\paragraph{}
-The buffer amplifiers
-
-\rule{\linewidth}{0.2pt}
-
-In case you're wondering, like I was, why the voltage coefficient of capacitors
-
-\rule{\linewidth}{0.2pt}
-
-Much of this project was done in 1.5 mm microstrip with a 2.5 to 3 mm routed isolation.
-However, it became apparent that the inductance of vias with the ground plane was too great.
-It has been suggested that low-inductance vias in prototypes \cite{Microwavee}
-
-Grounded coplanar waveguide, where the primary ground plane is on the top side of the board, presents many advantages, and in later testing appeared to provide much better performance and easier design.
-connectors can interface with the top side; trace sizes are much more compatible with small SMD devices.
-
-\rule{\linewidth}{0.2pt}
-
-Again, inductive choke biasing in the feedback loop was practically impossible.
-Biasing PiN diodes with a 10kohm resistor, (with 330 ohm safety resistor) one to 48V bias and another through an 2N7002P N-channel mosfet worked fine.
-
-The oscillator ran fine with a PiN bias of 2.34 mA.
-[LO prototype N].
-A high bias voltage of 48V was required to get sufficient current through the two 10K resistors and the PiN diode to obtain a low impedance while remaining delicate with the vfb.
-
-The PiN diode used has a resting resistance of 500 ohms, 5 ohms at 2 mA and 2 ohms at ??.
-
-48V is a little tight on the 50V rated voltage of our DC blocking capacitors.
-
-Each activated PiN diode should be biased separately, since putting 2x 2 mA through 20K would take an impractical 80V.
-
-\rule{\linewidth}{0.2pt}
-
-Conductors are represented by zeroing all components of the electric field in those regions.
-
-There are many different possible source geometries, each introducing their own distortions.
-
-There are many ways of linking SPICE and FDTD.
-
-\rule{\linewidth}{0.2pt}
-
-Bandpass filters can be designed by first designing a low-pass filter prototype (usually Chebychev) (or, in our case, using reference filter component tables), and then transforming this low-pass into a band-pass.
-[Hunter 2001] is an excellent overview of this process, with many design examples for different filter topologies.
-
-The coupling coefficient between two low-pass filters determines the band-pass bandwidth.[Hui 2012]
-
-[Hunter 2001] also describes an analytical method to create a filter with the precise group delay - phase shift versus frequency - required for stable oscillation.
-However, simultaneously compensating for the group delay introduced by the amplifier itself (nearly 180 degrees over the frequency range for the CEL part) seemed complex.
-
-Phase shift can be introduced either via a length of microstrip, or a high-pass/low-pass filter [Microwave101].
-Adding a fixed microstrip line restricts the tuning range, however, and the filter inevitably affects the frequency response.
-
-\rule{\linewidth}{0.2pt}
-
-NGSPICE's KSPICE coupled transmission lines require the capacitance and inductance per unit length in Maxwell matrix form, rather than the physical $C_{even}$/$L_{even}$ (each line's capacitance and inductance to ground) and $_{odd}$ (between elements) form provided by tools like wcalc.
-"matrix not positive definite".
-[Schutt-Aine] discusses this; we reproduce here for convienience.
-
-\[ L_{11} = L_{22} = L_{even}  \]
-\[ L_{12} = L_{21} = L_{odd}  \]
-\[ C_{11} = C_{22} = C_{even}+C_{odd}  \]
-\[ C_{12} = C_{21} {\it{(unused)}} = -C_{odd}  \]
-
-\rule{\linewidth}{0.2pt}
-
-In practice, the timestep required to obtain convergence in particularly tight corners of the SPICE simulation can drop to 1e-20, which is far below the Courant limit of the FDTD simulation.
-To eek out a bit more performance, a simple adaptive-timestep technique from [ a ] is used; we simply set the timestep so that the maximum change in voltage per timestep from the SPICE portion is less than
-some threshold.
-
-\PRLsep{{\itshape Sampling time-domain spectrometry}}
-
-\begin{quote}
-A rapidly increasing voltage step V tŽ . is applied to the 0
-line and recorded, along with the reflected voltage R tŽ .
-returned from the sample and delayed by the cable propagation time Figure 2 . Any cable or instrument artifacts Ž .
-are separated from the sample response due to the propagation delay, thus making them easy to identify and control. The entire frequency spectrum is captured at once,
-thus eliminating drift and distortion between frequencies.
-\end{quote}
-
-The pulse is usually recorded in real-time with a many-GHz oscilloscope. However, by using a sampling oscilloscope, massively undersampling the signal,
-
-Another advantage of this technique is that no high-Q filters are required to select the frequency;
-discrimination is in the time-domain, and is spread out over many seconds. It is also much easier to generate a 10+ GHz fast edge than it is to generate a CW signal.
-
-\PRLsep{{\itshape Power amplifier }}
-
-The amplifier and oscillator are separate for ease of design; this way the phase response of the amplifier is of no consequence.
-
-Our target power for the test is about 0.01 W, mandating a $2 \sqrt(2)$ V peak to peak RF swing on the Z=50 output.
-
-The $V_{CEO}$ breakdown of the bipolar transistor in question is only 2.3V.
-Above this value, current begins to flow from the emitter to the base, turning on the transistor and causing thermal runaway.
-If the base bias has a low enough impedance and can source current, this $V_{CEO}$ can be violated safely.
-[Toshiba, Bipolar Transistors, some other paper on the strong base bias]
-
-One solution would be to match the output to a lower impedance [Leuschner 2010]:
-
-\begin{quote}
-Generating high RF power from low supply voltages poses also another problem: the optimum load impedance of the PA output stage transistors becomes very small.
-A matching network with a high transformation ratio is needed to transform the antenna impedance of 50 to the optimum load impedance.
-High transformation ratios usually result in small bandwidth and higher losses.
-Possible solutions are the use of either non-standard high power RF devices or special circuit topologies using only the available standard devices.
-\end{quote}
-
-Use of so-called stacked, HiVP, or collector-feedback cascode designs can also allow the RF voltage to be distributed over many devices.
-
-It should also be noted that when stressed, these devices can fail with a slow power-output degradation over weeks, an effect not usually found in lower-frequency designs.
-
-\printbibliography[heading=none, title={}, keyword={amplifier}]
-
-\clearpage
-\PRLsep{ Wherein antennas are characterized}
-
-Method-of-moments solvers like NEC-2 are the standard for simulating these sorts of antennas.
-However, most commonly-available packages don't seem to handle multiple dielectric constants, such as the air and substrate of a patch antenna.
-
-The impedance of a structure over frequency can be determined in FDTD by:
-
-\begin{itemize}
-  \item Applying a gaussian pulse to a voltage source - in our case, applied to a via connecting the path (or probe)
-  \item Running the simulation until the transients have all died out below some threshold, while logging the source voltage and current at each timestep
-  \item Taking the fourier transform of the (real) excitation voltage and current (producing a complex result, mind you)
-  \item Taking the magnitude of the ratio of the two complex spectra.
-\end{itemize}
-
-This is the computational equivalent of dropping a piano off a balcony to see which key is stuck.
-
-See [Penney 1994], [Luebbers 1992], [Luebbers 1991], [Luk 1997].
-
-Our implementation is in \ghfile{electronics/simple_fdtd/runs/U.py}.
-
-A similar mismatch to the SPICE exists for fourier methods - but in the other direction.
-The courant limit often demands fine timesteps, but since each FFT bin is $ f_{bin} = n_{bin} / (N_{simulation} \ dt) $ , the majority of the FFT bins exist into the hundreds or thousands of GHz, leaving no resolution in the low-frequency domain of interest unless $N_{simulation}$ is extremely large - even if all the transients in the simulation have died down, you still have to keep the sim running to make the FFT happy!
-
-There's more than enough 'information entropy' in 4000 FDTD points for most antennas. But you need some 30,000 points to get 10 bins below 20 GHz!
-
-There are a few methods of changing the FFT bin size artificially, which [Bi 1992] reviews. You can "use a manual fourier integration over the frequency region of interest".
-
-But, in a staggering turn of events which will presumably be familiar to statisticans and preposterous to everyone else, a far simpler method is to {\it discard} 95\% of the data, by down-sampling to 1/10th or so.
-
-An equally simple method that seemed to produce better results in our case is to pad the voltage and current samples to the correct length.
-The jump discontinuity introduced by padding with zeros has a negligible effect.
-
-It's so thumpingly unintuitive to me that adding 50,000 zeros to a 5000 value dataset can improve the resolution of a measurement by 300-fold.
-
-It is important to remember to normalize the gaussian pulse, or else numerical noise will be introduced. The magnitude is not important - [Luebbers 1992] use 100v, others use 1v, etc.
-
-Though uneven dt FFTs exist, the time step can be constant at the courant limit for this simulation.
-
-A step impulse (1 first timestep, 0 otherwise) has been used in some works, though in our case performance was quite horrid.
-
-A correction factor due to the staggered magnetic field of the Yee lattice must be introduced; [Fang 1994]. Their $Z_2$ equation (correcting for spatial inaccuracies, but not temporal) was sufficient.
-
-This technique is equivalent to that used in electrochemistry, known as fourier impedance spectroscopy - except they seem to usually use a known impedance source rather than a hard source, presumably because ideal hard sources don't exist in reality.
-
-Allowing the simulation to run for long enough that all transients dissipate is important for accuracy - deceptive dips in the current can cause early termination.
-A surprising amount of detail is contributed by even the smallest current levels.
-Our threshold is 1e-7 amps for 700 iterations.
-
-[Samaras 2004] has a very useful set of experimental and FDTD data for calibration and comparison.
-Comparing a probe via source in the different positions, we obtained agreement of $\sim 7\%$ in impedance and $\sim 5\%$ in frequency.
-
-The use of a hard source feed-port affects the number of timesteps required by introducing unphysical transients.
-Using a port with a virtual 50-ohm resistance reduces the computational requirements by a large factor; see [Luebbers 1996].
-
-Simply monitoring the source current during the simulation is somewhat deceptive. Periodically monitoring the change in the fourier transform seems to be a better convergence metric.
-
-The units of the FFT (unlike those of the continuous FT) remain in volts.
-
-\rule{\linewidth}{0.2pt}
-
-Most equations in papers on the FDTD method are supplied without making the scaling factors explicit; some need multiplying by the Courant number, For use with flaport/fdtd the H-field to current line integral in [] requires scaling by $\mu_0 * (dx/dt)$, where $\mu_0$ is the vacuum magnetic permittivity, dx the cell size, and dt the timestep - despite the equation already possessing a deceptive set of $dx$-es.
-
-Naturally, if one is competent, this discrepancy will be immediately obvious.
-Those not dimensionally-intuitive, such as myself, find it useful to run dimensional analysis using a unit-aware calculator such as {\it sharkdp/insect}.
-
-\rule{\linewidth}{0.2pt}
-
-\begin{quote}
-With four parameters I can fit an elephant, and with five I can make him wiggle his trunk.
-\end{quote}
-- von Neumann
-
-with six parameters, you can do it with only physical constants. Beware numerology.
-
-\rule{\linewidth}{0.2pt}
-
-Most passives (inductors, capacitors) companies supply S-parameters for their parts. Use them.
-
-\rule{\linewidth}{0.2pt}
-
-\PRLsep{{\itshape The antenna itself }}
-
-The impedance of a patch antenna varies with position on its surface. Probe feeds to a specific point on the patch
-
-Unfortunately, patch antennas have a relatively narrow bandwidth.
-
-\rule{\linewidth}{0.2pt}
-
-\PRLsep{{\itshape Power sensing }}
-
-The diode detector power sensor is based on the Infineon appnote [] and [], itself based on a circuit from The Art Of Electronics.
-
-A detailed description of various diode detectors are found in []. Because the steady-state current through the detector is very small, the microstrip can simply be terminated in the standard manner.
-
-The Mini-Circuits ZX47-40-S+ would be an excellent low-cost COTS alternative.
-
-\printbibliography[heading=none, title={}, keyword={rectifier}]
-
-\PRLsep{{\itshape Microfluidics: small channels, big headaches }}
-
-We had anticipated having to perform a large number of tests for optimization of the impulse.
-Automating tests also has the advantage of removing operator bias, and (in our case) minimizing artifacts from the sample holder.
-Since all the components were already computer-controlled, it seemed little extra effort.
-
-We originally planned on using techniques from the rapidly accelerating field of centrifugal microfluidics, using a broadband patch antenna smaller than the cuvette, and measuring transmission through the cuvette.
-
-Centrifugal microfluidics has the advantage of getting a pump for free; mixing can be effected by generating vortexes by accelerating and decelerating quickly; and because everything is circular, it is easier to design equidistant.
-
-The most important feature is the consistent "down" vector; because capillary forces
-
-However, aligning seemed liable to produce artifacts; runout in the spindle;
-
-Sterilization is often effected by cytotoxic gas []. UV we resorted to autoclaving, warping.
-
-Th edges are charred; however, we have not found any discussion of toxicity of the laser cut edges, so we assume they're fine.
-
-In a crude version of transmission welding.
-Tx welding usually relies on one material being transparent, and the other opaque - clear and black plastics, for instance.
-We obtained nearly useable results by scuffing one surface and rubbing in fine graphite powder.
-
-Both the hydrophobicity / wetting angle of the substrate (useful for valves with a certain threshold pressure, among other things), the adhesive surface energy, and sterilization can all be effected by UVC exposure.
-Unfortunately, we were not confident in the homogeneity of the
-
-Not all plastics can be laser welded.
-
-3DuF; this is an excellent program
-
-The final process was as follows:
-
-Just using a single-sided tape over micromachined channels didn't work for us; the tape remains sticky and stuck to the bottom of the channel, blocking it.
-
-\begin{itemize}
-	\item 1/16" 003 size Viton O-rings McMaster-Carr \#9464K103, 
-	\item 3M 467MP 0.051 mm double-sided adhesive transfer tape with 200MP acrylic adhesive, DigiKey 3M9726-ND.
-	Various other tapes were tried, such as 9495MP; the laser was not powerful enough to cut these.
-	While the intermittent temperature rating is over 121 C, the high-pressure steam environment does seem to degrade any exposed regions of tape.
-
-	A CO2 laser is usually used to cut these otherwise transparent materials.
-We only had a diode laser.
-However, the front and back paper liners absorb sufficient laser power to melt the tape between.
-This produces horrible results, but was sufficient for this purpose.
-With our 2.5 W, ~0.15 mm spot size, 450 mm/min for the tape.
-
-	\item MG Chemicals 416-T Laser Printer Transparency Film, 0.1 mm thick. Presumably a PET/Mylar material.
-
-	\item A vinyl cutter was used to cut the openings in the top mylar cover slip.
-	\item Frame machined from polycarbonate with a 1/16" two-flute carbide endmill, 24000 RPM, between 500 and 1000 mm/min, up to 1.5 mm step-down.
-G-code generated with MeshCAM.
-This seems to withstand the autoclave without any damage.
-	\item Note: the tape preferentially sticks to the back liner, rather than the front.
-	With both adhesive liners on, rub the thing hard with a rounded edge and rolling pin.
-	Aluminum foil tape backing on the adhesive layer.
-	Don't de-weed yet.
-
-\end{itemize}
-
-Note that cutting many of these materials with a laser is a bad idea. The residue will
-
-\begin{itemize}
-	\item Tape mylar to a cardstock backing with masking tape on the sides. Cut mylar on plotter with InkCut. 175 g force. 
-	\item Apply aluminum foil tape to the rear backing (with "3M" text) of the adhesive transfer tape. This supports the cut structures, without being cut itself.
-	\item Stick the adhesive to the laser bed with Kapton, foil-side down. It's not a good idea to use masking tape; it'll catch fire.
-	\item 
-\end{itemize}
-
-Making this device ourselves was a grave mistake that potentially cost many lives. We should have used \cite{Straight}, a COTS version which we discovered halfway through.
-
-I'm sorry.
-
-\paragraph{Lessons learned:}
-
-When trying to characterize the response to some process parameters (say, laser power), iteratively trying different parameters in series can be somewhat useful, as each trial informs the next.
-In this instance, we would try a speed and power, unstick the material from the bed, observe the result, decide on the course of action, and repeat.
-However, if it is possible to try many parameters in parallel just as fast as in series, (that is, in our case, make a coupon using [] that tries all reasonable values simultaneously), it would be very dumb not to do this.
-
-We are very dumb.
-
-\printbibliography[title={General fluidics resources}, keyword={microfluidics}]
-
-\printbibliography[title={Centrifugal}, keyword={centrifugal}]
-
-\PRLsep{{\itshape aaaaa }}
-
-One problem with the formal, academic paper format is that one starts to believe what is written, which is a death sentence for accurate reasoning. We try to avoid this by being unprofessional.
-
-\label{para}
-\ref{para}
-
-\paragraph{Timeline}
-
-\paragraph{Comments by others}
-
-\paragraph{Lessons Learned} \
+Writing a paper by writing the chapters and headings that you want, and then filling in the text, is quite hard.
+Just writing a big chunk of text, and then breaking that into many smaller sections, works a bit better.
 
@@
 Software such as Sumatra, Sacred, recipy, and others. In our case, we used eLabFTW's elabapy bindings.
+
+I think this is a good general rule: record as much detail automatically as possible
 
@@
 
+\rule{\linewidth}{0.2pt}
+
 Sometimes vertical integration is the wrong move. Objectively, in this case, it was simply the *wrong decision*.
@@
 
-%
-%An expert and distinguished gentleman that we contacted regarding assistance resolving transients in our microstrip VCO stated the following:
-%
-%
-%
-%This was a perfectly sensible remark; it is almost always the case that (at X-band, no less!) a custom IC would have been needed to build a VCO.
-%
-%Also, if taken in the context of a tired, overworked PI getting an unsolicited email from an excessively verbose undergraduate at a different university, I hardly think I would have replied differently.
-%
-%However, I think this person may have missed out. Learning 
-%
-%So perhaps it is wise to ponder the ideas of fools for skeet; one always learns target practice, if only an example what not to do, and occasionally one learns positively.
+An expert and distinguished gentleman that we contacted regarding assistance resolving transients in our microstrip VCO stated the following:
+
+This was a perfectly sensible remark; it is almost always the case that (at X-band, no less!) a custom IC would have been needed to build a VCO.
+
+Also, if taken in the context of a tired, overworked PI getting an unsolicited email from an excessively verbose undergraduate at a different university, I hardly think I would have replied differently.
+
+However, I think this person may have missed out. Learning
+
+So perhaps it is wise to ponder the ideas of fools for skeet; one always learns target practice, if only an example what not to do, and occasionally one learns positively.
 I have often found that I learn greatly from working on the projects of others.
-%
-%We present this only as a cautionary tale in the hopes that someday I will listen.
 
-% This is
+We present this only as a cautionary tale in the hopes that someday I will listen.
+
+ This is
+
+but, some months later, it was found that he was *right* - absolutely right.
 
@@
 
-\Acrobatmenu{GoBack}{Back}
-
 \end{document}

### 2020-09-11 documents/supplemental.tex
Pouring agars

@@
 
-\paragraph{Lessons Learned} \
-
-\rule{\linewidth}{0.2pt}
-
-It might be useful to watch file changes and autoreload. Practically every program in this project required the same three keystrokes to recompile; a recipe for RSI.
-
-\rule{\linewidth}{0.2pt}
-
-Automatic, no-effort documentation of simulation and experiment runs is critical.
-
-It may be helpful to think of simulations very similarly to IRL experiments.
-
-A simulation is just a universe in a bottle that you can examine more closely; as with real-world, you can learn much from observation, but
-
-But this need for documentation conflicts with the rapid, iterative cycle necessary for productivity.
-
-This is obvious to all compentent, but when rapidly iteratively testing with simulations, it may be helpful to automatically save a package with images of all the components (schematics, graphs, input files) of each distinct test.
-
-For comparison to experiment, having a webcam take an image of the assembled board is also helpful.
-
-Many months of testing have vanished into the ether due to
-
-Version control alone isn't quite enough.
-Just having a simulation setup file somewhere in the commit history isn't "discoverable" - that is, you must be able to see what the input and output was without re-running the simulation.
-
-Manually taking notes tended to disrupt the flow of testing; and in any case, just noting "SIR filter has appropriate phase response" is almost useless. What {\it was} the phase response? Plot it!
-
-Software such as Sumatra, Sacred, recipy, and others. In our case, we used eLabFTW's elabapy bindings.
-
-\rule{\linewidth}{0.2pt}
-
-It is far easier to use existing, well-characterized reference designs verbatim than to modify
-
-\rule{\linewidth}{0.2pt}
-
-When rapidly testing data analyses which aren't really conducive to unit testing, I previously used to run the whole simulation, look at the analysis, re-run the sim, etc.
-
-This is slow. I often don't change the input parameters for the sim, but just the analysis. However, there's often a large amount of state to persist to disk.
-
-Saving the entire session with 'dill' is very helpful.
-
-\rule{\linewidth}{0.2pt}
-
-Software opacity is evil.
-
-\rule{\linewidth}{0.2pt}
-
-A great deal of time was spent trying to resolve version conflicts and dependency hells with the numerous libraries used by all the simulation programs.
-Over a week was spent trying to recursively track down all the This also wastes developer time - some fraction of issues raised are due to library version conflicts.
-
-Packaged binaries help this slightly, but of course don't help if modifications are required, and managing shared libraries is still a tricky matter.
-
-Good solutions include OpenFOAM's Docker installation. In some cases, using chroot with the original developer's Linux distribution is also of some utility.
-
-But this all seems like quite a lot of overhead and opacity for what ultimately doesn't seem a super-complex problem: deterministically obtain a known-good version of a library, build locally, and set paths appropriately.
-
-A good example might be gTest's cmake integration.
-
-In the extreme, systems exist to extract every
-
-In some situations (especially where the library has a permissive licence) perhaps it could be useful to consider packaging a complete, batteries-included 'known good' repository, either with the source of all the correct library versions included, or with a script to clone and compile the specific version used, integrating all the libraries with the build system.
-
-For instance, this was done with the PDB reader in the OpenMM wrapper and JAMES.
-
-\rule{\linewidth}{0.2pt}
-
-There's also a very neat thing that seems to be common in computational biology, but which doesn't seem popular in other fields.
-After an algorithm or software tool is written (and the source published seperately), a simple CGI frontend is written around it and hosted on the university's servers.
-eLNemo and the CHARMMing web interface are advanced examples of this.
-This way, anyone with an input file can get results without futzing around with installation.
-
-The computational biologists have beat us at our own game.
-
-\rule{\linewidth}{0.2pt}
-
-We have always encountered wasting extreme amounts of time on subtle assembly mistakes in hardware prototypes.
-
-In one example in this project, many hours were wasted because the enamel insulation on a bodge wire had not burned off completely in the solder joint, leading to a high-impedance connection.
-
-The same has occurred in previous projects; in one example, many days were spent debugging software to fix an apparently slow hardware interrupt, which ended up being the result of a poor solder paste stencil leading to a hidden high-impedance connection to a leadless package.
-
-Many failures are the result of carelessness in modification and lack of inspection. Others would only have been found by a 100\% electrical test.
-
-If flying-probe or bed-of-nails tests can be made sufficiently rapid and closely coupled with the existing toolchain,
-
-In {\it 2001: A space odyssey}, an automated system is shown guiding the troubleshooting of an assembly, apparently generating a fault tree of all the
-
-Boundary-scan features might really help
-
-\rule{\linewidth}{0.2pt}
-
-Numerology doesn't pay
-
-\rule{\linewidth}{0.2pt}
-
-The ability to almost immediately compare simulation to experiment was essential.
-
-\rule{\linewidth}{0.2pt}
-
-This project started at the tail end of a project to produce ceramics. Many weeks were wasted; I had convinced myself that ceramics were required over FR4.
-
-\rule{\linewidth}{0.2pt}
-
-I originally rationalized not contacting others about . There are some 10,000 labs working on a cure; it's not helpful to have random amateurs tying up expert time with ignorant flights of fancy.
-
-Later, as the project became more mature and seemed likely, this morphed into a sort of arrogance.
-
-An expert in microwave engineering could probably have completed this entire project in a few days, rather than the months it took us.
-
-\rule{\linewidth}{0.2pt}
-
-\paragraph{Hall of Hubris} \
-
-Lest our hats stop fitting
-
-\rule{\linewidth}{0.2pt}
-
-An inane remark:
-
-\begin{displayquote}
-We believe once we have the P. Syringae host, we from environmental samples
-\end{displayquote}
-
-Truly the depths of Dunning-Kruger.
-
-\rule{\linewidth}{0.2pt}
-
-Lesson learned: implementing safeties in hardware when possible, even in non-critical systems, can greatly speed development.
-
-Like many microwave semiconductor HBT or pHEMT MMICs, the HMC996 amplifier requires.
-
-\rule{\linewidth}{0.2pt}
-
-Sometimes vertical integration is the wrong move. Objectively, in this case, it was simply the *wrong decision*.
-
-\rule{\linewidth}{0.2pt}
-
-%
-%An expert and distinguished gentleman that we contacted regarding assistance resolving transients in our microstrip VCO stated the following:
-%
-%
-%
-%This was a perfectly sensible remark; it is almost always the case that (at X-band, no less!) a custom IC would have been needed to build a VCO.
-%
-%Also, if taken in the context of a tired, overworked PI getting an unsolicited email from an excessively verbose undergraduate at a different university, I hardly think I would have replied differently.
-%
-%However, I think this person may have missed out. Learning 
-%
-%So perhaps it is wise to ponder the ideas of fools for skeet; one always learns target practice, if only an example what not to do, and occasionally one learns positively.
-I have often found that I learn greatly from working on the projects of others.
-%
-%We present this only as a cautionary tale in the hopes that someday I will listen.
-
-% This is
-
-\rule{\linewidth}{0.2pt}
-
-%\end{multicols}
-
 \Acrobatmenu{GoBack}{Back}

### 2020-09-14 documents/distribution.tex
Impedance

@@
 They determine the net charge experimentally from microwave absorption measurements.
+
+\cite{Microwave2009} already mention this effect; \cite{Elastic} does a much better analysis than we do.
 
@@
 
-Plugging a (single, non-distributed, which must be fixed) Q of 3.75 into the above breaking force distribution, and applying some guesses for the covariance of various parameters, we get:
+Plugging a (single, non-distributed, which must be fixed; FIXME) Q of 3.75 into the above breaking force distribution, and applying some guesses for the covariance of various parameters, we get:
 
@@
 \begin{quote}
-	With four parameters I can fit an elephant, and with five I can make him wiggle his trunk. \\- J.v.N
+	With four parameters I can fit an elephant, and with five I can make him wiggle his trunk. \\- J.v.N.
 \end{quote}
@@
 
-This also
+Since this entire covariance process will have to be repeated for SARS-NCoV-2 - that is, the CoV for NCoV, we have not bothered to fine-tune any of these fits.
+This must still be regarded as only a speculative hypothesis.
 
-Since this entire covariance process will have to be repeated for SARS-NCoV-2 - that is, the CoV for NCoV, we have not bothered to fine-tune any of these fits.
-This must still be regarded as only a hypothesis.
+However, it offers a slight optimization: rather than applying a pulse of a single frequency, the pulses should be swept across the frequency distribution.
+From the (extremely crude) approximations on Inf.
+A above, this has little effect on $<$ 90-th percentile virions, but decreases the inactivation field of the last 10\% by perhaps 50 V/m.
+
+In practice, not having a single frequency to design a microwave system around makes engineering quite a bit more complex; whether this tradeoff is worth making depends.
+"Broadbanding" makes all the $\lambda / 4$ structures behave rather poorly; depending on the bandwidth required, biasing may need to be made inductive or resistive.
+
+In the case of patch antennas for phased arrays, U-slots have to be added to dull the impedance bandwidth; all sorts of free-space injection-locking techniques become untenable; waveguide applicators start to run into overlapping transmission modes.
+
+For the pre-engineered, off-the-shelf clinical without cost constraints, this is probably not a serious issue.
+
+It may be useful to choose a few
 

### 2020-09-17 documents/distribution.tex
test

@@
 \begin{document}
+
+\begin{center}
+	{\bf \cite{Microwave2009} already mention this effect; \cite{Elastic} does a much better analysis than we do.}
+\end{center}
 
@@
 They determine the net charge experimentally from microwave absorption measurements.
-
-\cite{Microwave2009} already mention this effect; \cite{Elastic} does a much better analysis than we do.
 
@@
 
-This problem has a long history, stretching back to Cole-Cole's landmark paper in 1942\cite{Dispersion1941} and \cite{Electrical1941}.
+This problem has a long history, stretching back to Cole-Cole's landmark 1942\cite{Dispersion1941} paper and \cite{Electrical1941}.
+Such concerning statements as 'mathematically ill-posed' are bandied about; however, standard optimization techniques work fine.
 
@@
 
-Worse still, influenza exhibits pleiomorphy \cite{Influenza2006};
+Worse still, influenza exhibits pleiomorphy, stretching into a variety of \cite{Influenza2006};
 
-NCoV is closer to \cite{Viral2020}, but does not exhibit pleiomorphy.
+NCoV is closer to \cite{Viral2020}, but does not appear to exhibit pleiomorphy.
 
-A cursory fit found parameters $\bar{\text{Q}}$=3.736,  $\sigma \ \text{Q} = $0.738, $\bar{F}_{res}=$8.606 GHz and $\sigma {F_{res}}=$1.073 and covariance of +1.001.
-This describes the observed spectrum equally well:
+A cursory fit found parameters $\bar{\text{Q}}$=3.736,  $\sigma \ \text{Q} = $0.738, $\bar{F}_{res}=$8.606 GHz and $\sigma {F_{res}}=$1.073 \st{and covariance of +1.001}\footnote{warning}.
+This describes the observed spectrum equally well as Q=2.0:
 
@@
 
+Since this entire covariance process will have to be repeated for SARS-NCoV-2 - that is, the CoV for NCoV, we have not bothered to fine-tune any of these fits; and so the idea that the Q-factor is higher than previously reported must still be regarded as only a speculative hypothesis.
+
 T4 bacteriophage has far greater restraint, with only a 2.5\% $\pm \sigma$ variation in the icosahedral head dimensions \cite{Head1988}.\footnotemark
@@
 
-Since this entire covariance process will have to be repeated for SARS-NCoV-2 - that is, the CoV for NCoV, we have not bothered to fine-tune any of these fits.
-This must still be regarded as only a speculative hypothesis.
-
-However, it offers a slight optimization: rather than applying a pulse of a single frequency, the pulses should be swept across the frequency distribution.
+However, it offers a self-evident optimization: rather than applying a pulse of a single frequency, the pulses should be swept across the frequency distribution.
 From the (extremely crude) approximations on Inf.
@@
 
-In the case of patch antennas for phased arrays, U-slots have to be added to dull the impedance bandwidth; all sorts of free-space injection-locking techniques become untenable; waveguide applicators start to run into overlapping transmission modes.
+In the case of patch antennas for phased arrays, U-slots have to be added to dull the impedance bandwidth; all sorts of free-space injection-locking techniques become untenable; waveguides and cavities start to run into overlapping transmission modes.
+Structures like magnetron cavities are hard to
 
@@
 
-\begin{center}
-	\begin{tabular}{||c c c c||} 
-		\hline
-		Col1 & Col2 & Col2 & Col3 \\ [0.5ex] 
-		\hline\hline
-		1 & 6 & 87837 & 787 \\ 
-		\hline
-		2 & 7 & 78 & 5415 \\
-		\hline
-		3 & 545 & 778 & 7507 \\
-		\hline
-		4 & 545 & 18744 & 7560 \\
-		\hline
-		5 & 88 & 788 & 6344 \\ [1ex] 
-		\hline
-	\end{tabular}
-\end{center}
+Are such high pulse powers achievable?
 

### 2020-09-17 documents/distribution.tex
Personal device

@@
 \begin{center}
-	{\bf \cite{Microwave2009} already mention this effect; \cite{Elastic} does a much better analysis than we do.}
+	{\bf \cite{Microwave2009} already mention this inhomogeneity; \cite{Elastic} perform a much better analysis than we do.}
 \end{center}
@@
 \end{quote}
+
+Inputting this yield stress distribution produces an inactivation field distribution that is far higher than that of \cite{Efficient2015}'s experimental data by some 200 V/m.
+
+Let us therefore re-examine the reason why.
 

### 2020-09-17 documents/paper.tex
Personal device

@@
 
-We therere demonstrate this form factor because, superficially, there are fewer people than there are places.
-
-On the other hand, a personal device may present issues with participation and production volume.
-
 \paragraph{\textbf{Direct treatments at the fundamental}}\
-
-{\color{red} speculation \{ }
 
@@
 
-Surprisingly, there is little discussion on microwave virus detection, with the notable exception of [Mehrotra 2019].
+there is little discussion on microwave virus detection, with the notable exception of [Mehrotra 2019].
 Such scholarly silence is usually an indicator that a technique is impossible for reasons so obvious they scarcely bear repeating.

### 2020-09-17 documents/personal_device.tex
Personal device

%!TeX root = personal_device
\documentclass[paper.tex]{subfiles}
\begin{document}

\begin{autem}
What follows is intended to be a casual, first-principles e. Be very careful with its conclusions.
\end{autem}

{\color{red} speculation \{ }

Trivially extending great work by \cite{Focusing}, a 40-element phased array using active-antenna techniques, each element of which consists of a negative-resistance device such as the BFP620 transistor, a tuning varactor, a patch antenna, and a resonator, each contributing a pulsed tone of 500 nanoseconds length and 10 milliwatts of RF power, and a focal point spatial scan rate and pulse repetition frequency of 6 KHz. produces a field pattern which, when scanned, appears to be suitable to deny respiratory transmission in a 'face shield' configuration.

Even point-blank, such a field would comply with all regulations by a factor of .

Injection locking rather than discrete phase shifters saves a number of components.

Such a device would cost about \$12 in silicon at prototype prices, provide half a month of battery life on two alkaline AAA cells,

We demonstrate this form factor because, superficially, there are fewer people than there are places. But is such a device really necessary or useful? Is it sufficiently superior to a fiber mask to justify spending energy developing it? It has the advantage of being self-cleaning; and hair, eyes; a hand brought near the face is immediately sterilized.

%figure from ipynb

% a prototype oscillator

On the other hand, a personal device may present issues with participation and production volume.

Interference

If HFSS or ADS are not available, coupled SPICE-FDTD methods appear to be particularly simple and effective for these types of problems.

The advantage of the phased array is in the free-space power combining and the near-field focusing.

In our crude experiments, the loss tangent and poor impedance control of inexpensive substrates did not appear to pose a problem in itself; standard FR-4 or even PET substrate and screen-printed metal techniques seen in high-volume RFID tag production may be of some use.

However, the Q factor of tuning elements on such lossy materials appears to be too high to form useful oscillators. Air-dielectric coaxial, Barium titanate dielectric slab resonators, or various types of substrate-independent resonators may all be suitable for this purpose.

{\color{red} \} speculation }

\end{document}

### 2020-09-18 documents/application.tex
Assay still didn't work! Darnit!
Drum shaker thing
Soliton 1

@@
 While the majority of diathermy systems use much lower frequencies for deeper heating penetration, several papers have explored the 10 GHz band.
+Superficial vs deep-tissue hyperthermia.
 
@@
 It should be noted that more recent standards have abandoned instantaneous electric field limits, finding that they have little biological rationale (\cite{C95}, B.4.3, {\it Rationale for pulsed RF field limits}).\footnotemark
-
-$$S = \frac{|E|^2}{Z_0}$$
 
@@
 
+While such waveguide applicators provide excellent efficiency, at these frequency ranges the area of high field is quite tightly concentrated and may not be
+
 The 8 GHz tone does not necessarily need to be the fundamental. A carrier wave with a more deeply penetrating wavelength could be used.
@@
 
+It is difficult to intuit how 40,000 watts can possibly be safe.
+It's useful to note, however, that the total energy dissipated in each pulse is .
+An oft-cited figure for the energy in a whisper is 10 mJ[wolframalpha]; and, while no clinical data are available, whispering into someone's chest is rarely considered calamitous.
+
+Thermoacoustic effects should also be considered.
+
 \clearpage

### 2020-09-18 documents/safety.tex
Soliton 1

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+One could subsist on non-thermal effects literature alone.
+There is drama, mystery, intrigue, paragraphs of sardonic ire; ad-hominem analogies; effects spanning 10 orders of magnitude in strength and scale; where the tiniest of atomic murmurs sparks.
+
+The picture is certainly much more complicated than "non-ionizing cannot have effects".
 

### 2020-09-20 documents/application.tex
Stuff and things

@@
 It's useful to note, however, that the total energy dissipated in each pulse is .
-An oft-cited figure for the energy in a whisper is 10 mJ[wolframalpha]; and, while no clinical data are available, whispering into someone's chest is rarely considered calamitous.
+An oft-cited figure for the energy in a whisper is 10 mJ[wolframalpha]; while no clinical data are available, whispering at someone is rarely considered calamitous!
+
+Laser treatments can exceed hundreds of megawatts.
 
@@
 \clearpage
-\printbibliography[heading=none, title={}, keyword={Flagship}]
 \printbibliography[heading=none, title={}, keyword={standards}]

### 2020-09-20 documents/distribution.tex
Stuff and things

@@
 
+Charge \footnotemark
+
+\footnotetext{
+	It has been shown that, over decades, single species of viruses can effect large-scale changes in the net charges of their proteins without altering their function\cite{Dynamics2010}.
+Use of this technique will provide a selection bias towards immunity to electromagnetic fields.
+We do not have the biological knowledge to determine whether this is plausible; it simply seemed worth mentioning.
+
+}
+
 NCoV is closer to \cite{Viral2020}, but does not appear to exhibit pleiomorphy.
@@
 
-Whether these values also explain the other datasets in \cite{Efficient2015}, such as the inactivation threshold vs frequency has not yet been determined.
+We have not yet determined whether these values also explain the other datasets in \cite{Efficient2015}, such as the inactivation vs frequency plot.
+
+T4 bacteriophage has far greater restraint, with only a 2.5\% $\pm \sigma$ variation in the dimensions of the icosahedral head \cite{Head1988}.\footnotemark
+
+\footnotetext{T4 also occasionally finds itself as an isometric mutant (See PDB 5VF3).}
 
@@
 
-and here we have some dozen parameters. So these approximations should be regarded with great skepticism.
+and here we have some dozen parameters. So these approximations should be regarded with skepticism.
 
-Since this entire covariance process will have to be repeated for SARS-NCoV-2 - that is, the CoV for NCoV, we have not bothered to fine-tune any of these fits; and so the idea that the Q-factor is higher than previously reported must still be regarded as only a speculative hypothesis.
+Since this entire covariance process will have to be repeated for SARS-NCoV \footnotemark we have not bothered to fine-tune any of these fits; and so the idea that the Q-factor is higher than previously reported must still be regarded as only a speculative hypothesis.
 
-T4 bacteriophage has far greater restraint, with only a 2.5\% $\pm \sigma$ variation in the icosahedral head dimensions \cite{Head1988}.\footnotemark
+\footnotetext{...the CoV of NCoV}
 
-\footnotetext{T4 also occasionally finds itself as an isometric mutant (See PDB 5VF3).}
-
-However, it offers a self-evident optimization: rather than applying a pulse of a single frequency, the pulses should be swept across the frequency distribution.
+This introduces a self-evident optimization: rather than applying a pulse of a single frequency, the pulses should be swept across the distribution.
 From the (extremely crude) approximations on Inf.
@@
 
-In practice, not having a single frequency to design a microwave system around makes engineering quite a bit more complex; whether this tradeoff is worth making depends.
+In practice, not having a single frequency to design a microwave system around makes the engineering quite a bit more difficult whether this tradeoff is worth making depends.
 "Broadbanding" makes all the $\lambda / 4$ structures behave rather poorly; depending on the bandwidth required, biasing may need to be made inductive or resistive.

### 2020-09-20 documents/paper.tex
Stuff and things

@@
 
-\begin{table} 
-	\centering
-	\begin{threeparttable}
-		\caption{Safety limits from various standards}
-		\begin{tabular}{lllll}
-			\toprule
-			Stubhead & \( df \) & \( f \) & \( \Wsqm \) & \( p \) \\
-			\midrule
-			&     \multicolumn{4}{c}{Spanning text}     \\
-			Row 1    & 1        & 0.67    & 0.55       & 0.41    \\
-			Row 2    & 2        & 0.02    & 0.01       & 0.39    \\
-			Row 3    & 3        & 0.15    & 0.33       & 0.34    \\
-			Row 4    & 4        & 1.00    & 0.76       & 0.54    \\
-			\bottomrule
-		\end{tabular}
-		\begin{tablenotes}
-			\small
-			\item This is where authors provide additional information about
-			the data, including whatever notes are needed.
-		\end{tablenotes}
-	\end{threeparttable}
-\end{table}
+%
+%\begin{table} 
+%	\centering
+%	\begin{threeparttable}
+%		\caption{Safety limits from various standards}
+%		\begin{tabular}{lllll}
+%			\toprule
+%			Stubhead & \( df \) & \( f \) & \( \Wsqm \) & \( p \) \\
+%			\midrule
+%			&     \multicolumn{4}{c}{Spanning text}     \\
+%			Row 1    & 1        & 0.67    & 0.55       & 0.41    \\
+%			Row 2    & 2        & 0.02    & 0.01       & 0.39    \\
+%			Row 3    & 3        & 0.15    & 0.33       & 0.34    \\
+%			Row 4    & 4        & 1.00    & 0.76       & 0.54    \\
+%			\bottomrule
+%		\end{tabular}
+%		\begin{tablenotes}
+%			\small
+%			\item This is where authors provide additional information about
+%			the data, including whatever notes are needed.
+%		\end{tablenotes}
+%	\end{threeparttable}
+%\end{table}
 
@@
 
-Unfortunately, the buried lede is that the power levels shown by [Yang 2015] are about twice the continuous safety levels.
+and,
+
+\begin{quote}
+	 ...the two major groups that develop RF safety standards and
+	guidelines (ICES and ICNIRP) agree that thermal effects continue to be the appropriate basis for protection
+	against RF exposure at frequencies above 100 kHz.
+\end{quote}
 
@@
 
-It has been shown that virions can effect large-scale changes in the electric charges of their \cite{Dynamics2010}.
-
-Use of this technique will provide a selection bias towards immunity to electromagnetic fields, which could perhaps be effected by preferring extreme-sized mutants (shifting the resonance away from the applied field).
-
-We do not have the biological knowledge to know if this is plausible; it simply seemed worth mentioning.
-
 \subfile{acknowledgement}

### 2020-09-20 documents/personal_device.tex
Stuff and things

@@
 
-Trivially extending great work by \cite{Focusing}, a 40-element phased array using active-antenna techniques, each element of which consists of a negative-resistance device such as the BFP620 transistor, a tuning varactor, a patch antenna, and a resonator, each contributing a pulsed tone of 500 nanoseconds length and 10 milliwatts of RF power, and a focal point spatial scan rate and pulse repetition frequency of 6 KHz.
+Trivially extending great work by \cite{Focusing} on passive reflectarrays, a 40-element active-antenna phased array, each element of which consists of a negative-resistance device such as the BFP620 transistor, a tuning varactor, a patch antenna, and a resonator, each contributing a pulsed tone of 500 nanoseconds length and 10 milliwatts of RF power, and a focal point spatial scan rate and pulse repetition frequency of 6 KHz.
 produces a field pattern which, when scanned, appears to be suitable to deny respiratory transmission in a 'face shield' configuration.
 
-Even point-blank, such a field would comply with all regulations by a factor of .
+%figure from ipynb
+
+% a prototype oscillator
+
+Such a field would comply with all  standards by at least a factor of 20.
 
@@
 It has the advantage of being self-cleaning; and hair, eyes; a hand brought near the face is immediately sterilized.
-
-%figure from ipynb
-
-% a prototype oscillator
 

### 2020-09-20 documents/pseudo_soliton.tex
Stuff and things

%!TeX root = pseudo_soliton
\documentclass[paper.tex]{subfiles}
\begin{document}

Precursor waves do not appear to be explicitly mentioned in current standards, but are implicitly governed by the Fourier-spectrum clauses. Ultra-short wavepackets of a similar nature are widely used in MRI systems with a repetition rate up to 300 MHz. We can make some mechanistic claims.

Assuming that a torso is about 10 penetration depths in radius, this would decrease the required surface field for complete eradication of the virus from the body to only 1 kV/m, rather than 6.6 MV/m ($1/\sqrt{10}=0.316$ rather than $e^{-10}=4.5e-5$).

\end{document}

### 2020-09-20 documents/supplemental.tex
Stuff and things

@@
 
-\PRLsep{{\itshape Turbidimeter }}
+\PRLsep{{\itshape Phage lysis sensing }}
 
@@
 
-"Chromogenic" substances \cite{Fluorogenic1991}, or the degradation of various dyes like Methylene Blue.
+"Chromogenic" substances \cite{Fluorogenic1991}, or the degradation of various dyes like Methylene Blue; tetrazolium dye methods;
 
@@
 \cite{Vision2016} use an ingenious technique. A background with sharp light-to-dark edges is used. Slicing the image into chunks only slightly larger than the object,
+
+The 0.8 uL sample in each was not sufficient to produce a measurable change in turbidity in a 0.2 uL - or we were not experienced enough to perform the phage lysis protocol properly.
+
+However, we were not able to make smaller volumes of culture enter the log phase.
 

### 2020-09-20 electronics/simple_fdtd/run/waveguide.py

@@ -1,0 +1,188 @@
+# import torch
+# import numpy as np
+# import gc
+# torch.cuda.empty_cache()
+#
+# gc.collect()
+
+# np.seterr(all='raise')
+# torch.autograd.set_detect_anomaly(True)
+import fdtd_PCB_extensions as fd
+from fdtd_PCB_extensions import fdtd
+from fdtd_PCB_extensions import tissue
+from fdtd_PCB_extensions import X,Y,Z, gaussian_derivative_pulse
+from scipy.constants import mu_0, epsilon_0, c
+import scipy.constants
+from math import sin, pi, pow, exp, sqrt
+import time
+import os
+import matplotlib.pyplot as plt
+import copy
+from scipy.signal import gausspulse
+import dill
+from pytexit import py2tex
+import pickle
+
+import numpy as np
+import math
+
+
+fdtd.set_backend("torch.cuda.float32")
+
+import sys
+#
+# sys.path.append('/home/arthurdent/covidinator/biology/FDTD/')
+# import tissue
+
+# fdtd.set_backend("numpy")
+
+#include store.py
+sys.path.append('/home/arthurdent/covidinator/electronics/')
+import store
+
+os.system("rm dumps/*")
+os.system("rm data/*")
+
+N_x = 120
+N_y = 120
+N_z = 110
+
+pcb = fd.PCB(0.002, xy_margin=0, z_margin=0)
+fd.initialize_grid(pcb,N_x,N_y,N_z, courant_number = 0.45)
+
+f = 9e9
+
+fd.dump_to_vtk(pcb,'dumps/test',0)
+
+dipole_length = int(0.008/pcb.cell_size) #cells
+dipole_source_position = np.array([33,25,70]) # bronch
+# dipole_source_position = np.array([45,60,70]) #pleural
+dipole_source_position += pcb.pml_cells
+z_slice = slice(dipole_source_position[Z],dipole_source_position[Z]+1)
+
+raw = tissue.import_raw_voxel_file('/home/arthurdent/covidinator/biology/FDTD/chunks/2mm_100x100x100_left_lung_5.raw', [100,100,100])
+
+# raw = np.pad(raw, [(pcb.pml_cells, pcb.pml_cells), (pcb.pml_cells, pcb.pml_cells), (pcb.pml_cells, pcb.pml_cells)], mode='constant')
+
+def waveguide(pcb, position, f, lower_cutoff_frequency):
+    #EIA WR102 rectangular waveguide 1.02 [25.908]	0.51 [12.954]
[…]

### 2020-09-21 documents/acknowledgement.tex
text

--- 2020-06-29 documents/acknowledgement.tex
@@
 
-Professor Shahramian's excellent video blog {\it The Signal Path} inspired this work.
+Thanks to (Dr. ) Peter Barfuss for spending time reviewing early drafts.
 
-Dr. Dainis' videos on microbiological technique were also useful.
+This paper would have been absolutely impossible without the support of thousands of open-source software packages, ranging from monolithic nation-state supported tools like Paraview and Chimera to poorly-compensated but equally invaluable scripts like zonca.
+A special thanks to the dedicated authors that develop and maintain these tools.
 
-Thanks to the professors at York and beyond for returning my emails.
+Professor Shahramian's excellent video blog {\it The Signal Path} greatly informed this work. Dr. Dainis' videos on microbiological technique were also particularly useful.
 
-Thanks to L.H. for wisdom regarding this project.
+Thanks to all the professors at York and beyond for returning my emails and checking their biofridges for phages.
 
-Thanks to P.B and H.P. for tolerating ramblings and M. for the hug.
+GThanks to L.H. for wisdom regarding this project; and H.P. and ice9 for tolerating midnight ramblings and M.Q. for the hug.
 
-Special thanks to all the people - most equally capable of writing this paper if provided the opportunity - who work menial shifts at the component suppliers that remained open that were so critical.
+Special thanks to all the people - all equally capable of writing this paper if provided the opportunity - who circumstance led to work menial shifts at the component suppliers that remained open that were so critical.
 Hopfstader be damned; despite the name below the abstract, this paper is of course entirely the result of circumstance and luck.
@@
 
+\rule{\linewidth}{0.2pt}
+
+The authors reluctantly acknowledge the Computational Electromagnetics Group at The University of Texas at Austin for going through the trouble to develop the AustinMan and AustinWoman human body models and then making them unavailable at https://sites.utexas.edu/austinmanaustinwomanmodels/, and also unavailable via email.
+
+\rule{\linewidth}{0.2pt}
+
+The authors acknowledge the IT.IS foundation for doing the same, but actually replying to emails.
+
+\rule{\linewidth}{0.2pt}
+
 One Very Important Thought
+
+{\Large <3}
+
+\end{document}

### 2020-09-21 documents/distribution.tex
text

@@
 
-Let us therefore re-examine the reason why.
+Let us therefore re-examine the microwave spectrum. Much of this data was found in order to try to simulate the inactivation mechanism by molecular dynamics, so it was not a complete waste of time.
 
 The liposome breaking force is distributed in an obstinately non-gaussian bimodal manner, so we override the covariance matrix and introduce a gaussian KDE sampled from the force histogram in \cite{Bending2011}.
+
+Lorentzian
 
@@
 
-Charge \footnotemark
+Charge can be determined by the primary structure sequence. A table of net charges of Inf. A, and T4. however, a few influzena proteins have been found to have anomalous secondary structure charge.
+
+Because CryoEM uses charged particles, it is technically feasible to determine the net charge distribution in the whole virus using an ingenious \cite{Identification2018} technique.
+However, this has not yet been implemented in any
+
+\footnotemark
 

### 2020-09-21 documents/paper.tex
Wrote a better abstract
text

@@
 \clearpage
+
+\begin{figure}[H]
+	\captionsetup{singlelinecheck = false, justification=justified}
+	\centering
+	\includegraphics[width=\textwidth]{eppenwolf_2.jpg}
+	\caption{\\ The {\it Eppenwolf} pulsed X-Band microwave spectrometer used in this study, pictured with the near-field cuvette installed.}
+
+\end{figure}
 
@@
 Certainly the proteins of the virion locally absorb energy and increase in temperature.
-The key is that, when excited in this manner, the energies in the envelope are poorly modelled by a Maxwell-Boltzmann distribution; they are not given sufficient time to 'thermalize'.
+The key is that, when excited in this manner, the energies in the envelope are poorly modeled by a Maxwell-Boltzmann distribution; they are not given sufficient time to 'thermalize'.
 In contrast, with typical 2.4 GHz microwave exposure, sterilization can only occur by aggregate heating of the fluid and tissue.}

### 2020-09-21 documents/pseudo_soliton.tex
text

@@
 
-Assuming that a torso is about 10 penetration depths in radius, this would decrease the required surface field for complete eradication of the virus from the body to only 1 kV/m, rather than 6.6 MV/m ($1/\sqrt{10}=0.316$ rather than $e^{-10}=4.5e-5$).
+At 9 GHz, assuming that a torso is about 10 penetration depths in radius, implementing this would decrease the required surface field for complete eradication of the virus from the body to only 1 kV/m, rather than 6.6 MV/m ($1/\sqrt{10}=0.316$ rather than $e^{-10}=4.5e-5$).
 

### 2020-09-21 documents/supplemental.tex
text

@@
 
+This has nothing to do with , but it's an amusing parlor trick that I accidentally ran into while trying to carbothermally reduce copper oxide powder.
+It led me to the SiC susceptor resonator, so it wasn't a total waste.
+
+Add a thimblefull of fine copper powder to the bottom of a mason jar. Cover the mouth with a layer of Kapton tape. Next, inject pure argon gas for a few minutes, then seal the tape fully.
+
+Put the whole shebang in a friend's microwave oven.
+
+Wait patiently. There will be a sizable bang and a terrific plasma.
+
+My hypothesis is that this is due to the higher ionization energy of Ar. Air seems to slowly leak in, decreasing the
+
 \PRLsep{{\itshape The antenna itself }}

### 2020-09-21 electronics/simple_fdtd/run/waveguide.py

@@ -69,6 +69,10 @@ def waveguide(pcb, position, f, lower_cutoff_frequency):
     #https://www.everythingrf.com/tech-resources/waveguides-sizes
     # https://www.microwaves101.com/encyclopedias/waveguide-mathematics for guide wavelength
 
+
+    # [1]Waveguide Theory n.d. http://emlab.uiuc.edu/ece451/appnotes/r-waveguide.pdf (accessed September 20, 2020).
+
+
     # scratch that -
     # lambda_ = (1.0/f)*c
     #

### 2020-09-24 documents/application.tex
Little progress

@@
 \footnotetext{In our case, it seems to make the most sense to discuss the attenuation of the electric field, V/m, rather than the field power (also referred to as the {\it intensity}),\Wsqm, since the inactivation seems most closely related to the former.
-Penetration depth refers to the depth at which the power is reduced by 1/$e$; skin depth, where the electric field is 1/$e$.
-The penetration depth is simply half the skin depth.\cite{Penetration2019a}}
+Strictly speaking, penetration depth refers to the depth at which the power is reduced by 1/$e$; skin depth, where the electric field is 1/$e$.
+The penetration depth is simply half the skin depth.\cite{Penetration2019a} If we refer to penetration depth without making this explicit, we are referring to the electric field penetration depth.}
 
@@
 It's useful to note, however, that the total energy dissipated in each pulse is .
-An oft-cited figure for the energy in a whisper is 10 mJ[wolframalpha]; while no clinical data are available, whispering at someone is rarely considered calamitous!
+An oft-cited figure for the energy in a whisper is 10 mJ[wolframalpha]; while no clinical data are available, whispering at someone is rarely considered calamitous\citationneeded!
 

### 2020-09-24 documents/supplemental.tex
Little progress

@@
 A small vial of liquid has a much larger surface area relative to its thermal mass.
-sis removed, the temperature drops very rapidly; if the temperature drops outside the physiological range of about 33-40 C, growth is stunted \cite{effect2003}.
+sis removed, the temperature drops very rapidly; if the temperature drops outside the "physiological range" of around 33-40 C, growth is stunted \cite{effect2003}.
 \cite{growth1946}.
+I'm not sure if this was the problem I encountered,
 

### 2020-09-27 documents/personal_device.tex
fuck fucking fucking fucker

@@
 
+Such a field would comply with all standards by at least a factor of 20.
+
 %figure from ipynb
 
+\begin{figure}[H]
+	\captionsetup{singlelinecheck = false, justification=justified}
+	\centering
+	\includegraphics[width=\textwidth]{muller_test_cropped.jpg}
+	\caption{\\ How simple an active antenna element can be.
+This is based on the feedback-loop oscillator of \cite{SmallSize2008}, and uses a single CEL CE3520K3 GaAs FET (\$2.5) and one 100pF capacitor.
+It oscillated with extreme instability at about 5 GHz.}
+\end{figure}
+
+\begin{figure}[H]
+	\captionsetup{singlelinecheck = false, justification=justified}
+	\centering
+	\includegraphics[width=\textwidth]{my_photo-17.jpg}
+	\caption{\\ An ultrawideband tunable 7 GHz VCO based on \cite{TripleTuned2008}.
+This uses an Infineon BFP620 SiGe:C transistor (\$0.3) and a network of four varactor diodes.
+Unfortunately, the Si varactors did not appear to have a sufficiently high Q to prevent mode-hopping, and the output spectrum reflects the ignorance of its designer; however, it appeared to be capable of producing the 10 dBm required above.}
+\end{figure}
+
 % a prototype oscillator
-
-Such a field would comply with all  standards by at least a factor of 20.
 

### 2020-10-05 documents/distribution.tex
Words
Propagation

@@
 \begin{center}
-	{\bf \cite{Microwave2009} already mention this inhomogeneity; \cite{Elastic} perform a much better analysis than we do.}
+	{\bf \cite{Microwave2009} already mention this inhomogeneity; \cite{Elastic} probably perform a much better analysis than we do.}
 \end{center}
@@
 
-Inputting this yield stress distribution produces an inactivation field distribution that is far higher than that of \cite{Efficient2015}'s experimental data by some 200 V/m.
+Inputting this AFM-determined yield stress distribution produces an inactivation field distribution that is far higher than that of \cite{Efficient2015}'s experimental data by some 200 V/m.
 
-Let us therefore re-examine the microwave spectrum. Much of this data was found in order to try to simulate the inactivation mechanism by molecular dynamics, so it was not a complete waste of time.
+This is not very surprising. Many reasonable assumptions are made that could account for this discrepancy; the homogeneous-sphere core-shell assumption, for instance.
+
+However, it may be useful to re-examine the microwave spectrum with an eye towards the distribution.
+
+\begin{toolchain}
+Much of this data was found in order to try to simulate the inactivation mechanism by molecular dynamics, so it was not a complete waste of time.
+\end{toolchain}
 
@@
 Lorentzian
-
-"95%.".
 
@@
 
-This problem has a long history, stretching back to Cole-Cole's landmark 1942\cite{Dispersion1941} paper and \cite{Electrical1941}.
-Such concerning statements as 'mathematically ill-posed' are bandied about; however, standard optimization techniques work fine.
+This problem has a long history, stretching back to Cole-Cole's landmark 1942\cite{Dispersion1941} paper:
 
@@
 
-Within a sample of a single species, there is $\approx$ 12.7\%  ($109 \pm 16.65 \text{ nm}$\cite{lauffer1944biophysical}, $115 \pm 12 \text{ nm}$ \cite{Characterization1984}) variation in diameter and  \cite{Characterization1984} variation in mass.
+and \cite{Electrical1941}. Such concerning statements as 'mathematically ill-posed' are bandied about; however, standard stochastic fitting techniques work fine.
+
+Within a sample of a single species of Inf.
+A, there is $\approx$ 12.7\%  ($109 \pm 16.65 \text{ nm}$\cite{lauffer1944biophysical}, $115 \pm 12 \text{ nm}$ \cite{Characterization1984}) variation in diameter and  \cite{Characterization1984} variation in mass.
 
@@
 
-Charge can be determined by the primary structure sequence. A table of net charges of Inf. A, and T4. however, a few influzena proteins have been found to have anomalous secondary structure charge.
+Charge can be determined by the primary structure sequence.
+A table of net charges of Inf.
+A, SARS, and T4 proteins is in the github.
+However, a few influzena proteins have been found to have anomalous secondary structure charge.
+
+TODO: verify charge is $10^7$ e as found by Yang
 

### 2020-10-08 documents/pseudo_soliton.tex
tests
More propagation
Stuff

@@
 
-Precursor waves do not appear to be explicitly mentioned in current standards, but are implicitly governed by the Fourier-spectrum clauses.
+Precursor waves do not appear to be explicitly mentioned in C95- but are implicitly governed by the Fourier-spectrum clauses.
 Ultra-short wavepackets of a similar nature are widely used in MRI systems with a repetition rate up to 300 MHz.
@@
 
+As saliently noted by Adair:
+
+\begin{quote}
+	“the energy of the pulse at a depth of 1 cm is about 0.8% of the initial energy;
+	the maximum electric field strength, E is reduced by a factor of about 12, and the maximum rate-ofchange of the field, dE/dt, is reduced by a factor of 20.
+Every characteristic of the pulse at depth is
+	contained, albeit attenuated, in the initial pulse. Consequently, we do not find it credible that the
+	strongly attenuated pulse – albeit with a different shape – can induce biological effects beyond that of
+	the initial pulse.”
+\end{quote}
+
+The 2018 NATO Research Task Group 189 report \cite{treatyelectromagnetic} is an excellent source of data for these.
+
+\begin{quote}
+	Other basic bioeffects research [50], [52], [53], [66], [81], [83] has failed to provide support for Albanese’s multiple	theoretical postulates.
+\end{quote}
+
+The real killer
+
+temporal Soliton-producing nonlinear transmission lines, and NLTL oscillators constructed therefrom, particularly well suited
+
 \end{document}

### 2020-10-08 documents/supplemental.tex
Stuff

@@
 
+Phage releases several amino acids such as putrescine and spermadine when broken. These can be indicated at ppm scales with ninhydrin, or at nanogram scales via fluorescamine.
+
 Essentially the only method of determining the activity of phage is to have it infect a suitable host.
@@
 Because the variation in the optical density is quite small, this poses some rather.
+
+A lot of the basic facts of phage were determined in the 1930s;
 
@@
 
-Another method, often used in microfluidics\cite{Microfluidic}, is that of \cite{method1951}; manganese dioxide catalyzed decomposition of hydrogen peroxide.
-MnO2 is readily obtained from alkaline batteries; and in this case no sterility issues are presented.
-However, it is not obvious how all h2o2 vapor can be prevented from contacting the culture.
+Another method, often used in microfluidics\cite{Microfluidic}, is that of \cite{method1951}; the Manganese dioxide catalyzed decomposition of hydrogen peroxide.
+$MnO_2$ is readily obtained from alkaline batteries; and in this case no sterility issues are presented.
+However, it is not obvious how antimicrobial $H_2O_2$ vapor can be prevented from contacting the culture.
 
@@
 
-In commercial fluid transfer machines, this is often resolved by HEPA filtering the input to the cabinet.
+In commercial fluid transfer machines, this is often resolved by HEPA filtering the input to an enclosing cabinet.
 
-Shaking incubators, which simply rock the
+Shaking incubators, where the flasks are
 
-In our case, ensuring that a great deal of headspace was present in the tube was sufficient for brief growth.
+Ensuring that a great deal of headspace was present in a sealed tube (that is, culturing 2.5 mL in a 15 mL falcon tube) was sufficient for brief, low-density.
 

### 2020-10-09 documents/acknowledgement.tex
Protein charges processed

@@
 
-This paper would have been absolutely impossible without the support of thousands of open-source software packages, ranging from monolithic nation-state supported tools like Paraview and Chimera to poorly-compensated but equally invaluable scripts like zonca.
+This paper would have been absolutely impossible without the support of thousands of open-source software packages, ranging from monolithic nation-state supported tools like Paraview to poorly-compensated but equally invaluable scripts like zonca.
 A special thanks to the dedicated authors that develop and maintain these tools.
@@
 
-GThanks to L.H. for wisdom regarding this project; and H.P. and ice9 for tolerating midnight ramblings and M.Q. for the hug.
+Prof. Griffiths and Dr. Brovko at UGuelph, Dr. Anany at the Guelph Research and Development Centre for tips on the Beta-Glo assay.
+
+Thanks to L.H. for wisdom regarding this project; Profs David and Taylor (among others) at YorkU for being super nice, and H.P. and ice9 for tolerating midnight ramblings.
 

### 2020-10-09 documents/charge.tex
Protein charges processed

%!TeX root = charge
\documentclass[paper.tex]{subfiles}
\begin{document}

Protein net charges extracted from primary protein sequences compiled by the proteome-pI database \cite{ProteomepI2017} and UniProt using localCIDER \cite{CIDER2017} \ghfile{biology/data/net_charge.py}.

*detailed source information will be added later! There are several hundred.*

\cite{Vibrational2002}
\begin{quote}
Although the value q = e, chosen to describe the oscillating dipole moment already implies a very large permanent dipole moment, if the oscillating charge were greater
than $2\times 10^4 e$, the radiative absorption from the canonical
incident microwave power density would be increased to
detectable levels if the relaxation time is as large as 5 ns.
But so large a charge leads to a moment that seems far
outside of our understanding of DNA or any other molecule.

The conclusion that there can be no microwave resonances in DNA in water is in accord with the results of
measurements in three different laboratories (Gabriel et al.,
1987; Foster et al., 1987) using techniques designed to
detect resonances with amplitudes less than 1/20th of that
reported by Edwards et al. (1984).
\end{quote}

Adair's \cite{Vibrational2002}, in the section {\it \bf Coherent Processes}.

$$\frac{4 \pi (100 \text{nm}^2)}{(10 \text{ micrometers} \times 10 \text{ micrometers})} 10^7 e^- = $$

The arguments regarding Resonances in microtubules are also

\end{document}

### 2020-10-09 documents/charge.tex
Charge and molecular weights

@@
 
+In my field, I am used to being able to make a definite mechanistic claim.
+Such and such a gamma ray will not break the bond in so and so; the energy is too low.
+However, we might not be able to expect such a clear answer from biology; how many treatments do we know of where the interaction with every structure in the body is known?
+In some cases, all we appear to be able to say is that we've tested it in a convincingly large number of ways and just don't see it.
+
+That seems defeatist, but it perhaps should be something we can prepare for.
+
 \end{document}

### 2020-10-09 biology/data/net_charge.py

@@ -29,9 +29,12 @@ for file in files:
         net_charge = seq_param.get_NCPR(pH=7.0)*seq_param.get_length()
         print(net_charge)
 
+
         output.write(header)
         output.write(", ")
         output.write(str(7.0))
+        output.write(str(", "))
+        output.write(str(seq_param.get_molecular_weight()))
         output.write(str(", "))
         output.write(str(net_charge))
         output.write('\n')

### 2020-10-12 documents/charge.tex
lab notebook note
Propagation?

@@
 
+As might be expected, the electrostatic properties of the virus differ from that of host cells, both \cite{Icosahedral2019} on the sub-protein level:
+
+\begin{quote}
+	Different from insect, plant, and human, viruses had more positively charged than negatively charged segments.
+In Fig.
+1B we show the log (base 10) net-charge frequency value for a selected group of proteins (e.g., Viral proteins) subtracted of the log expected frequency value calculated from the total proteome distribution (i.e., log10-fold-change).
+Viral proteins were the only class enriched in extremely high positively charged segments (charge ≥ + 17) when compared to the overall proteome (1B-inset with p-values).
+\end{quote}
+
+and in the lipid bilayer \cite{Lipid2015} \footnotemark.
+
+\footnotetext{The virus steals its envelope from the host cell; but it tie dyes its duds before it bounces.}
+
+On the largest scale, the net charges of the 11 major proteins coded for by the influenza genome
+
 Protein net charges extracted from primary protein sequences compiled by the proteome-pI database \cite{ProteomepI2017} and UniProt using localCIDER \cite{CIDER2017} \ghfile{biology/data/net_charge.py}.
@@
 *detailed source information will be added later! There are several hundred.*
+
+Other enzymes
 
@@
 
+\cite{Identification2018}
+
 \end{document}

### 2020-10-12 documents/pseudo_soliton.tex
Propagation?

@@
 
+\footnotemark
+
+\footnotetext{Some of the initial work on these precursors (or "forerunners", as they were known at the time) apparently neglected some of the higher-order terms, leading to the conclusion that the signals were "very weak" (Sommerfield).
+However, the amplitude is often greater than that of the carrier.}
+
+\footnotemark
+\footnotetext{Honestly, how cool is this?
+Like, this unimportant factor (as simple as the rise time!) connects so deeply with Schrodinger's wave-packets - the very same functions that apply for probability distributions - and produces a result so striking - a complete change }
+
+The "asymptotic method", and the fourier series method. Unfortunately, the fourier coefficients and phases provide little intuitive sense for how different input pulses propagate.
+
+%The Somerfield precursor is high-frequency,
+
 \end{document}

### 2020-10-13 documents/charge.tex
testing

@@
 \begin{document}
+
+Yang et al determine that, to fit their microwave absorption cross-section data, the "core" and "shell" of the virus should have an effective charge of about $10^7 e^-$.
+
+Is such a charge plausible?
+
+Protein net charges extracted from primary protein sequences compiled by the proteome-pI database \cite{ProteomepI2017} and UniProt using localCIDER \cite{CIDER2017} \ghfile{biology/data/net_charge.py}.
+
+On the largest scale, at a pH of 7, the net charges of the 11 proteins coded for by the Influenza A genome only contribute
+
+The polarization potential example that Adair borrows from Frolich, with a membrane potential of 100 V (see []) still only contributes.
+
+$$(4.523 \times 10^-14 \text{m}^2 \cdot 0.01 \text{F/m}^2 \cdot 100 \text{V}) \approx 10^5 e^- $$
 
@@
 \footnotetext{The virus steals its envelope from the host cell; but it tie dyes its duds before it bounces.}
-
-On the largest scale, the net charges of the 11 major proteins coded for by the influenza genome
-
-Protein net charges extracted from primary protein sequences compiled by the proteome-pI database \cite{ProteomepI2017} and UniProt using localCIDER \cite{CIDER2017} \ghfile{biology/data/net_charge.py}.
 

### 2020-10-13 electronics/propagation/propogation.jl

@@ -1,5 +1,0 @@
-
-
-@test dipole_E_field_at_point() == 9
-
-isapprox()

### 2020-10-14 documents/acknowledgement.tex
v

@@
 
-Thanks to (Dr. ) Peter Barfuss for spending time reviewing early drafts.
+Chiefly among the enablers are of course my parents, Doris and Brian, without whom this work would have been done by someone else, and who also supported this work financially.
 
-This paper would have been absolutely impossible without the support of thousands of open-source software packages, ranging from monolithic nation-state supported tools like Paraview to poorly-compensated but equally invaluable scripts like zonca.
+Thanks to (Dr. ) Barfuss for spending time reviewing an early draft.
+
+This paper would have been absolutely impossible without the support of thousands of open-source software packages, ranging from monolithic state-supported tools like Paraview to poorly-compensated but equally invaluable scripts like zonca.
 A special thanks to the dedicated authors that develop and maintain these tools.
 
-Professor Shahramian's excellent video blog {\it The Signal Path} greatly informed this work. Dr. Dainis' videos on microbiological technique were also particularly useful.
+Professor Shahramian's excellent video blog {\it The Signal Path} greatly informed this work. Dr. Dainis' videos on microbiology were also particularly useful.
 
@@
 
-Thanks to L.H. for wisdom regarding this project; Profs David and Taylor (among others) at YorkU for being super nice, and H.P. and ice9 for tolerating midnight ramblings.
+Thanks to L.H. for wisdom regarding this project; Profs David and Taylor (among others) at YorkU for being super nice, and H.P. and ice9 for tolerating ramblings.
 
@@
 
-Chiefly among the enablers are of course my parents, Doris and Brian, without whom this work would have been done by someone else, and who also supported this work financially.
+R.I.P. to Dr. Robert Adair, whose work features prominently here, died Sep. 2020.
 
@@
 
-The authors acknowledge the IT.IS foundation for doing the same, but actually replying to emails.
+The authors acknowledge the IT.IS foundation for doing precisely the same, but actually replying to emails.
 

### 2020-10-14 electronics/propagation/propagation.py

@@ -7,7 +7,3 @@ from scipy.constants import epsilon_0, mu_0
 import scipy.constants
 from fdtd_PCB_extensions.tissue import cole_cole_4, complex_permittivity_to_er_and_sigma, electric_field_penetration_depth
 from mpl_toolkits.mplot3d import Axes3D
-
-
-
-ef, sigma, deltas, alphas, taus = get_tissue_cole_cole_coefficients(id)

### 2020-10-19 documents/pseudo_soliton.tex
DNA
Reconstruction just fine

@@
 At 9 GHz, assuming that a torso is about 10 penetration depths in radius, implementing this would decrease the required surface field for complete eradication of the virus from the body to only 1 kV/m, rather than 6.6 MV/m ($1/\sqrt{10}=0.316$ rather than $e^{-10}=4.5e-5$).
+
+There are some extremely tricky subtleties in the simulation.
+\cite{propagation1992}.
+In \cite{Comments1993}, Leubbers says FDTD and FFT both are better than Asympt, Ogh says no there's no problem, Asymptotic is really accurate.
+Frankly, I can't make heads or tails of any of these, not understanding the asymptotic method at all.
 

### 2020-10-19 electronics/propagation/propagation_lib.py

@@ -17,20 +17,20 @@ class propagator:
         pass
 
 
-    def fourier_transform(self, input_data, sampling_frequency, frequency_scale):
+    def fourier_transform(self, input_data, sampling_frequency, frequency_scale_factor):
         self.input_fft = np.fft.rfft(input_data)
 
-        self.a_n_coefficients = fft.real
-        self.b_n_coefficients = fft.imag
+        self.a_n_coefficients = self.input_fft.real
+        self.b_n_coefficients = self.input_fft.imag
 
         # duration =
-        self.base_period = sampling_frequency/len(input_data)
+        # self.base_period = sampling_frequency/len(input_data)
 
+        frequency_step = (sampling_frequency * frequency_scale_factor)/len(self.a_n_coefficients)
+        self.times = np.linspace(0, len(self.a_n_coefficients)*(1.0/(sampling_frequency*frequency_scale_factor)), len(self.a_n_coefficients))
+        self.mode_frequencies = np.linspace(frequency_step, (len(self.a_n_coefficients)/2)*frequency_step, len(self.a_n_coefficients))
 
-        self.times = np.arange(0, len(input_data)*(1.0/(sampling_frequency*frequency_scale)), len(input_data))
-        self.mode_frequencies = np.arange((sampling_frequency * frequency_scale)/len(input_data), (base_period))
-
-        return fft, self.a_n_coefficients, self.b_n_coefficients, base_period
+        # return fft, self.a_n_coefficients, self.b_n_coefficients, base_period
 
 
 
@@ -43,61 +43,59 @@ class propagator:
     def wavenumber(n, base_period, dielectric_constants):
          return self.modes*(base_period)*2*pi*np.sqrt(mu_0*dielectric_constants*epsilon_0)
 
+        #
+        #
+        # fft, a_n, b_n, base_period = fourier_transform(input_data)
+        #
+        # #split into the two phases
+        #
+        # # 1000
+        #
+        # a_n, b_n = attenuate(a_n, b_n, 1,0.5)
+        #
+        # output = np.zeros_like(ts)
+        #
+        # plt.plot(input_data)
+        #
+        # #
+        # # ef, sigma, deltas, alphas, taus = get_tissue_cole_cole_coefficients(100)
+        # # dielectric_constants = np.ones_like(input_data)
+        # # penetration_depth = np.ones_like(input_data)
+        #
[…]

### 2020-10-22 documents/charge.tex
:((((((((((((
Gelgreen

@@
 Protein net charges extracted from primary protein sequences compiled by the proteome-pI database \cite{ProteomepI2017} and UniProt using localCIDER \cite{CIDER2017} \ghfile{biology/data/net_charge.py}.
+
+look into the Gibbs–Donnan effect
 
@@
 
+it would be interesting to compare the potential energy of assembling such a structure to the known host metabolic burden of assembling a virus.
+
+%https://www.macmillanlearning.com/studentresources/college/physics/tiplermodernphysics6e/classial_concept_review/chapter_11_ccr_20_electrostatic_energy_of_a_sphere_of_charge.pdf
+
+$U = 3/5 * 1/4 pi epsilon_0 Q^2 / R \approx 2.3e-7 $
+%U = (3/5) * 1/(4*pi*electricConstant) *((1e7 electricCharge)^2 / 60 nanometers) = 2.30708e-7 J
+
+The total is $6 \times 10^11$ ATP-equivalent.
+
+%50 kJ per mole, 6.022*10^23 = 9.9634673e-13 * 50 kj = 5e-8 J
+
+of course, much of the potential energy may have already existed in the host cell, so this is probably an invalid comparison.
+And if most of the charge is contributed by osmotic, ion , this potential energy may not be counted.
+
+todo: is it possible for the charged core to compensate for the potential energy of the charged shell?
+
 \end{document}

### 2020-10-24 documents/charge.tex
Run 5 prep

@@
 
-Yang et al determine that, to fit their microwave absorption cross-section data, the "core" and "shell" of the virus should have an effective charge of about $10^7 e^-$.
+Back-of-the-envelope.
+
+Yang et al determine that, to fit their microwave absorption cross-section data and produce the decrease in infectivity via the route they suggest, the "core" and "shell" of the virus should have an effective charge of about $10^7 e^-$.
 
@@
 
+\section{Hello World}
+\subsection{Hello World}
+\label{sec:hello}
+
+\hyperref[sec:hello]{See section.}
+
+Rather than, for instance, less than 1/100 for Arginine or 1/600 for DNA.
+
 it would be interesting to compare the potential energy of assembling such a structure to the known host metabolic burden of assembling a virus.
@@
 of course, much of the potential energy may have already existed in the host cell, so this is probably an invalid comparison.
-And if most of the charge is contributed by osmotic, ion , this potential energy may not be counted.
+And if most of the charge is contributed by osmotic, ion , this potential energy may not be considered in the above.
 

### 2020-11-04 documents/charge.tex
pmt counter

@@
 look into the Gibbs–Donnan effect
+
+blood plasma
+
+If we assume that the charge is not as. All other properties being equal, to account for the same coupling and absorption, one of the following would seem to need to be true:
+
+1. the effective path length of the fancy test waveguide used by Yang may not be as they expected.
+2. The concentration of virus was higher than measured.
+3.
 

### 2020-11-04 documents/fluorescence.tex
pmt counter

\begin{document}

Low background is required.

Xu's method \cite{Quantification2020}

Nanodrop, using 280 nm absorbance.

the input edge is considered a clock; the minimum pulse width limits apply, but are not clearly specified in the datasheet. In this case (1/155 mhz) = 6 ns.

### 2020-11-04 documents/molecular_dynamics.tex
pmt counter

--- 2020-09-21 documents/supplemental.tex
@@
-%!TeX root = supplemental
-\documentclass[paper.tex]{subfiles}
-\begin{document}
-
-\clearpage
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-{\Huge Captain's Log, Supplemental}\\
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \paragraph{Molecular dynamics simulation}
@@
 Because CryoEM is sensitive to the
-
-\clearpage
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-{\Large Optical centrifuge polarization chirp}\\
-\begin{multicols}{1}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\includepdf[
-    %% Include all pages of the PDF
-    pages=-,
-    %% make this page have the usual page style
-    %% (you can change it to plain etc). By default pdfpages
-    %% sets the pagecommand to \pagestyle{empty}
-    pagecommand={\thispagestyle{empty}},  
-    %% Add a "section" entry to the ToC with the heading
-    %% "Quilling Shapes" and the label "sec:shapes"
-    addtotoc={1,section,1,Quilling Shapes,sec:shapes}]
-%% The pdf file itself
-{optical_centrifuge.pdf}
-
-\includepdf[
-%% Include all pages of the PDF
-pages=-,
-%% make this page have the usual page style
-%% (you can change it to plain etc). By default pdfpages
-%% sets the pagecommand to \pagestyle{empty}
-pagecommand={\thispagestyle{empty}},  
-%% Add a "section" entry to the ToC with the heading
-%% "Quilling Shapes" and the label "sec:shapes"
-addtotoc={1,section,1,Quilling Shapes,sec:shapes}]
-%% The pdf file itself
-{biology.pdf}
-
-\end{multicols}
-
-Contrary to some [Hardell 2017] reports, we do not find the FCC and ICNIRP to be significantly affected by special interest groups; their rationales appear to be transparent.
-[FCC-19-126A1], for instance, is a particularly entertaining memorandum:
-
-\begin{quote} 
-Similarly, IEEE-ICES urges the Commission to adopt a higher SAR exposure limit of 2 W/kg averaged over 10 g.
-[snip] We are not persuaded that the IEC standard should be adopted at this time.", "Medtronic and the AAMI-CRMD recommend a more relaxed threshold of 20 mW.
-We decline to increase the 1-mW threshold.".
-
-\end{quote}
-
-Things heating up at the Microwave Safety fandom.
-
-\clearpage
-\rule{\linewidth}{0.2pt}
-
-We do not intend to denigrate the work or otherwise cast aspersions on the authors of the mentioned papers; their experiment extremely well-designed and performed.
-
-However, since the result is unexpected, we would like to mention a few means by which the effect described could be achieved without strong non-thermal coupling.
-
-\begin{quote}
-
- To confirm that our observation is not due to the microwave thermal heating effect, we had monitored the sample temperature change during the microwave illumination experiments with a radiated power density of 486W/m2 at a frequency of 6GHz by using an infrared thermal imaging camera with a temperature accuracy of 0.05°C (CHCT, P384-20).
-The temperature rise after 15 minutes radiation was 7°C, from 27.5°C up to 34.5°C.
-We thus exclude the possible contribution of microwave thermal heating effect to inactivation H3N2 viruses under our experimental condition.
-
-\end{quote}
-
-The frequency-dependent inactivation result in Figure 4b of \cite{Efficient2015} is difficult to explain without invoking non-thermal mechanisms.
-Only one  It is not mentioned how this applied power level was measured.
-
-The amplifier in question is not available on the supplier's website \cite{Microwaved} has gain flatness of 3.5 dB over 6-12 GHz - just over 1 octave.
-The amplifier used in [Hung] is not mentioned; because the frequency range mentioned (6 GHz to 18 GHz) is the same as that of the amplifier, we assume the same amplifier was used.
-
-If the amplifier happened to be matched better at 8 GHz than 12 GHz.
-
-QPJ-06183640
-
-Similarly, the gain of the EM-6969 antenna\cite{EM6969} varies from 17 dBi to 21 dBi over the frequency range in Figure 3.
-
-However, that the spectra of all these effects would combine to produce a peak at precisely the resonant frequency determined by the entirely different microwave cuvette is highly implausible; and so Figure 4b really does seem to be good evidence of such an effect.
-
-\clearpage
-\rule{\linewidth}{0.2pt}
-
-There seems to be a discrepancy between \cite{Efficient2015} and our reading of [C95.1-2005].
-
-They use a threshold in open public space of $100(f/3)^{1/5} \text{ W/m}^2$. The 115 W @ 6 GHz figure they provide corresponds to this equation with a coefficient of 100.
-
-For Table 9, general public, the equation is $18.56 (f)^{0.699} \text{ W/m}^2$, or $64.93 \text{ W}/\text{m}^2$ @ 6 GHz.
-
-Different versions of the IEEE standard have used equations of equivalent form but with different coefficients [Wu 2015]; it is entirely possible that we have retrieved the wrong standard.
-
-\rule{\linewidth}{0.2pt}
-
-\PRLsep{{\itshape Phage lysis sensing }}
-
-Essentially the only method of determining the activity of phage is to have it infect a suitable host.
-
-Typically, this is done either in a large tube or a flat-sided optical cuvette.
-
-Because the variation in the optical density is quite small, this poses some rather.
-
-A small vial of liquid has a much larger surface area relative to its thermal mass.
-sis removed, the temperature drops very rapidly; if the temperature drops outside the physiological range of about 33-40 C, growth is stunted \cite{effect2003}.
-\cite{growth1946}.
-
-As a faculative aerobe, E.coli requires a concentration of oxygen to be present in the mixture for speedy replication \cite{Effect1965}; and this supply must also be kept sterile.
-One method to ensure this is by using a bubbler aerator; Carolina recommends an aquarium pump with cotton-ball filters.
-
-Another method, often used in microfluidics\cite{Microfluidic}, is that of \cite{method1951}; manganese dioxide catalyzed decomposition of hydrogen peroxide.
-MnO2 is readily obtained from alkaline batteries; and in this case no sterility issues are presented.
-However, it is not obvious how all h2o2 vapor can be prevented from contacting the culture.
-
-Bottles of zero air may be more effective.
-
-In commercial fluid transfer machines, this is often resolved by HEPA filtering the input to the cabinet.
-
-Shaking incubators, which simply rock the
-
-In our case, ensuring that a great deal of headspace was present in the tube was sufficient for brief growth.
-
-As the size of the well decreases, the Reynolds number also decreases \footnote{In fact, in the case of a circular well, it's not obvious that this is the case - the cross section decreases faster than the characteristic length}, and turbulent flow is greatly hampered.
-
-Even slight rotation of the tube, such that the graduations
-
-"Chromogenic" substances \cite{Fluorogenic1991}, or the degradation of various dyes like Methylene Blue; tetrazolium dye methods;
-
-Using 2.5 mm diameter x 3 mm high wells cut in polycarbonate and sealed with clear packing tape. However, the presence of small bubbles in the headspace of the wells prevented a consistent reading.
-
-We tried simply adding 1 uL of culture to the microscope slide;
-
-The 8-bit resolution and dynamic range of most cameras did not seem sufficient to discern the turbidity; and masking and correcting for
-
-\cite{Vision2016} use an ingenious technique. A background with sharp light-to-dark edges is used. Slicing the image into chunks only slightly larger than the object,
-
-The 0.8 uL sample in each was not sufficient to produce a measurable change in turbidity in a 0.2 uL - or we were not experienced enough to perform the phage lysis protocol properly.
-
-However, we were not able to make smaller volumes of culture enter the log phase.
-
-Another very interesting technique is that of \cite{Study2003},
-
-\PRLsep{{\itshape Wherein an oscillator is designed }}
-
-Many
-
-Three incorrect pieces of information conspired to lead us to try to develop an inexpensive ultrawideband oscillator.
-
-\begin{itemize}
-	\item The assumption that a broadband frequency sweep would drastically improve the inactivation threshold, and moreover that 
-	\item The ideal 
-	\item The assumption that the only commercially available oscillators in this frequency range were expensive YIG-tuned devices.
-\end{itemize}
-
-There are really two different conflicting criteria:
-
-A low-cost, wide-band
-
-Unfortunately, designing wideband microwave circuits is significantly more difficult than for a particular frequency. Quarter-wavelength
-
-Varactor diodes are a GaAs hyper-abrupt junction diode.
-
-We were warned that this would be difficult:
-
-CEL did not supply a SPICE model for the GaAs FET device used in early prototypes. A FET was originally because a gate is ostensibly easier to bias than a base; but this turned out to be unfounded.
-
-[Steenput 1999] has an interesting analytic method to synthesize a SPICE model suitable for a transient simulations from S-parameter measurements using negative resistances.
-However, this neglects the I/V characteristic.
-
-[Polyfet 1998] describes a simple optimization method to synthesize a SPICE model for an active device, and CEL appnote provides some details for GaAs devices.
-
-\rule{\linewidth}{0.2pt}
-
-OpenEMS is excellent, with Python bindings, some lumped components, and mesh refinement. However, embarrassingly, we were not able to resolve all the dependency issues in order to install it.
-
-\paragraph{Biasing}\
-
-In our simulations, the varactor-tuned feedback circuit appeared to be particularly sensitive to the introduction of bias-tees.
-
-The gate must be weakly pulled to ground, otherwise stray charge destroys the oscillation.
-
-\fancyhead[C]{style 1 with thin line}
-
-With 0.79 mm FR4 substrate and 0.2 mm (8 mil) wide traces, the maximum impedance achievable was about 115 ohms, which did not appear to be sufficient as an RF choke.
-Use of defected grounds can increase inductance, but this was not evaluated.
-
-If suitably high-impedance traces are not available, a common technique is to use a quarter-wavelength line (approximately 6 mm long with the above parameters at 8 GHz) terminated with a stub to produce a virtual short or open circuit [Seo 2007].
-
-However, reflections from these structures still appeared to distort the frequency/phase response beyond repair, even with ostensibly wideband stubs [Syrett 1980].
-
-\noindent\fbox{\parbox{\linewidth}{
-	Rebuke: despite this blather, many other papers have had success with bias-tees at these frequencies.
-}}
-
-Alternate methods evaluated, failures:
-
-In production, these could be accomodated by graphite-polymer printed resistors.
-
-Odd-pole varactor-loaded combline filters appeared to have excellent phase and frequency response; however, the geometry necessitates low-inductance via stitching to the ground plane.
-
-%\noindent\fbox{\parbox{\linewidth}{
-\begin{autem}
-	{\it autem} Others have had great success with varactor-tuned comblines, especially non-grounded lines.
-\end{autem}
-
-[Tsuru 2008 fig. 10] is an excellent review of various oscillator designs.
-
-The parasitic inductance of common varactors appears to become problematic at these frequencies (but not for non-wideband use).
-
-\paragraph{\textbf{Spacing}}\
-
-FDTD results still yielded some coupling at 2 mm isolation.
-
-\paragraph{\textbf{Via stitching}}\
-
-Rather than the almost universal technique of via stitching components immediately to the ground plane (a tedious process with our prototyping setup), a large ground pour on the component layer was used wherever ground was needed, as mentioned in [Hunter?
-combline].
-Since we use microstrip rather than coplanar waveguide,
-
-Since the ground plane does not participate in the DC bias at all, no vias are required in the final device.
-This means that the drilling, electroless strike and electroplating steps are unnecessary for production.
-
-\PRLsep{{\itshape The wideband oscillator }}
-
-Not having access to any RF equipment, we needed an oscillator tunable over the X-band.
-
-There are many oscillators. The HB100 uses a dielectric resonator, for instance; cavity-based methods with mechanical tuning; active antennas using.
-
-The literature is quite mature, partly due to the FCC's recent ultrawideband communications guides.
-
-As a result of our gross incompetence, the oscillator was designed via an inane, roundabout, and fiendishly tedious manner, and our description of this technique only contributes to the field by being suitable for a dartboard; our analysis can only hold water when combined with paper mache; and a lesser invertebrate in posession of a copy of Grebennikov's excellent Microwave Oscillator Design would have accomplished the task faster.
-
-Designing an oscillator of this type in one step with a few kindergarten equations appears to be well within the reach of modern network analytical techniques.
-Genetic algorithms are quite well matched to this problem, and many commercial software packages are  [computer microwave design book].
-
-We began experimentally by building a scaled version of [Mueller 2008]'s active antenna crudely with copper tape, using a CEL [] GaAs FET.
-
-We then manually tried a number of filter designs, using the manufacturer's S-parameters and QUCS' microstrip approximations.
-This intially appeared to yield good agreement with experiment.
-Peaks in the feedback voltage simulation corresponded approximately with peaks in the observed spectrum.
-[figures from LO prototype N].
-
-A crude, inane, and extremely disorganized trial-and-error procedure was performed for many weeks.
-A wide variety of analytical methods for filter design were attempted [documents/global.ipynb], but simultaneously obtaining the correct phase shift and frequency response was somewhat difficult.
-Adding the parasitic inductance of the varactors always seemed to destroy our most perfect creations.
-
-Using an SIR filter has the added advantage of confusing epidemiologists.
-
-Eventually, QUCS, zonca/python-qucs, and scipy's basinhopper were used with a cost function somewhat similar to that described in [Kaplevich]:
-
-\begin{verbatim}
-    freq_coeff = 1
-    phase_coeff = 1.5
-    ratio_coeff = 0.5
-    insertion_loss_coeff = 0.2
-
-    frequency_cost = freq_coeff * (abs(desired_center_frequency-fb_peak_frequencies[0])/1e9)
-    phase_cost = phase_coeff * abs(1.0 - phase_at_peak)
-    ratio_cost = ratio_coeff * fb_peak_ratio
-    insertion_loss_cost = insertion_loss_coeff*(1.0 - fb_peak_values[0])
-    cost = frequency_cost + phase_cost + fb_peak_ratio + insertion_loss_cost
-\end{verbatim}
-
-Optimizing first for the high frequency, fixing the inductor and microstrip values, and then optimizing for the varactor values at the low frequency.
-
-This produced a seemingly acceptable feedback loop (note the group delay / phase progression):
-
-\includegraphics[scale=1]{LO_2_pole_test.png}
-
-However, when this was built, varactor tuning performance was abysmal, with hops and peaks; and the tuning range was far smaller than expected.
-
-It was thought that a transient simulation - to determine how the spectrum actually evolved - would improve the situation.
-
-As of 0.0.20, QUCS' microstrip models are not yet compatible with transient simulations; and some improved filter designs required simulating coupling between more than two microstrips, which QUCS did not yet support natively.
-
-\begin{figure}[H]
-\includegraphics[width=\textwidth]{3d_spectrum_2.png}
-\end{figure}
-
-The complete transient simulation matched reality very closely.
-
-\begin{figure}[H]
-	\includesvg[width=\textwidth]{wideband_LO_2_simulated_tuning}
- 	\caption{"Wideband VCO 2": BFP620  \\
- 	 Oscillator tuning simulated with electronics/ngspice/oscillator\_designer\_2.py commit <>, eLabID 20200613-d28a8004c...}
-\end{figure}
-
-The oscillator design is a testament  This highlights that a computation is not a substitute for understanding.
-
-The key sticking point seems to be that as frequency increases, using microstrip design techniques, the parasitics of any filter structure are so large that the small change in impedance that the varactors can provide does not tune the circuit by any meaningful amount.
-
-The two varactors on each tuning circuit each contribute 0.7 nH and between 0.35 to 2.4 pF; each blocking capacitor contributes about 0.2 nH.
-The frequency range of the oscillator can be selected by adding between 0.5 nH to 1.5 nH symmetrically to both tuning circuits.
-
-"Using the lead inductances of the bipolar transistor and varactors provides the required value of the base inductance".
-
-Indeed, [Tsuru 2008]'s "tuned circuit" in Fig 8 is, in fact, just the varactors, plus an almost invisible high-impedance line.
-
-The final oscillator is a 'wideband double-tuned varactor VCO', based almost verbatim on [Tsuru 2008] and the reference design in Figure 8.36, p378 of [Grebennikov 2007].
-
-The rest of the papers in the bibliography were highly enlightening regarding the principles of microwave oscillator design.
-
-For ease of design and simulation, selecting a device with both Touchstone S-parameters and SPICE models is greatly preferable.
-
-It is commonly claimed that FR4 is a 'slow' substrate, and that the high loss tangent of ~0.02 makes it unsuitable for microwave systems.
-
-However, with this PCB substrate, the expected loss of only 0.026 dB/mm on signals of minimum 0 dBm is patently acceptable.
-As viruses do not have a discriminating palate, we are also only minimally concerned with $S_{11}$ reflections, noise, or spurs, so precise impedance control is not required; the wideband VCO sweep accomodates for any variations in resonant frequency due to wide manufacturing tolerances.
-
-This topology of oscillator worked marvellously on essentially the first try.
-
-Not having a good analytical understanding, we resorted to using a purely computational method.
-
-In addition, the design of wideband feedback-loop VCOs is a relatively well-explored field, and many reference designs exist.
-
-Merely scaling designs like [] was not effective.
-
-Several analytical filter design methods were
-
-This is apparently known as a "double-tuned" wideband.
-
-Oscillators must meet the Barkhausen criterion:
-
-\begin{itemize}
-
-\item A 360 degree phase shift around the feedback loop (including the phase shift contribution from the amplifier, which itself varies greatly with frequency)
-\item A loop gain $>1.$
-
-\end{itemize}\
-%
-However, a third element is also required:
-%
-\begin{itemize}
-\item A frequency-selective element that restricts oscillation modes and decreases phase noise.
-\end{itemize}
-%
-
-With large feedback-loop structures, such as long PiN-switched phasing lines, proximity effects from nearby flesh would detune the oscillator significantly.
-
- design of a triple-tuned oscillator.
-
-\paragraph{}
-The buffer amplifiers
-
-\rule{\linewidth}{0.2pt}
-
-In case you're wondering, like I was, why the voltage coefficient of capacitors
-
-\rule{\linewidth}{0.2pt}
-
-Much of this project was done in 1.5 mm microstrip with a 2.5 to 3 mm routed isolation.
-However, it became apparent that the inductance of vias with the ground plane was too great.
-It has been suggested that low-inductance vias in prototypes \cite{Microwavee}
-
-Grounded coplanar waveguide, where the primary ground plane is on the top side of the board, presents many advantages, and in later testing appeared to provide much better performance and easier design.
-connectors can interface with the top side; trace sizes are much more compatible with small SMD devices.
-
-\rule{\linewidth}{0.2pt}
-
-Again, inductive choke biasing in the feedback loop was practically impossible.
-Biasing PiN diodes with a 10kohm resistor, (with 330 ohm safety resistor) one to 48V bias and another through an 2N7002P N-channel mosfet worked fine.
-
-The oscillator ran fine with a PiN bias of 2.34 mA.
-[LO prototype N].
-A high bias voltage of 48V was required to get sufficient current through the two 10K resistors and the PiN diode to obtain a low impedance while remaining delicate with the vfb.
-
-The PiN diode used has a resting resistance of 500 ohms, 5 ohms at 2 mA and 2 ohms at ??.
-
-48V is a little tight on the 50V rated voltage of our DC blocking capacitors.
-
-Each activated PiN diode should be biased separately, since putting 2x 2 mA through 20K would take an impractical 80V.
-
-\rule{\linewidth}{0.2pt}
-
-Conductors are represented by zeroing all components of the electric field in those regions.
-
-There are many different possible source geometries, each introducing their own distortions.
-
-There are many ways of linking SPICE and FDTD.
-
-\rule{\linewidth}{0.2pt}
-
-Bandpass filters can be designed by first designing a low-pass filter prototype (usually Chebychev) (or, in our case, using reference filter component tables), and then transforming this low-pass into a band-pass.
-[Hunter 2001] is an excellent overview of this process, with many design examples for different filter topologies.
-
-The coupling coefficient between two low-pass filters determines the band-pass bandwidth.[Hui 2012]
-
-[Hunter 2001] also describes an analytical method to create a filter with the precise group delay - phase shift versus frequency - required for stable oscillation.
-However, simultaneously compensating for the group delay introduced by the amplifier itself (nearly 180 degrees over the frequency range for the CEL part) seemed complex.
-
-Phase shift can be introduced either via a length of microstrip, or a high-pass/low-pass filter [Microwave101].
-Adding a fixed microstrip line restricts the tuning range, however, and the filter inevitably affects the frequency response.
-
-\rule{\linewidth}{0.2pt}
-
-NGSPICE's KSPICE coupled transmission lines require the capacitance and inductance per unit length in Maxwell matrix form, rather than the physical $C_{even}$/$L_{even}$ (each line's capacitance and inductance to ground) and $_{odd}$ (between elements) form provided by tools like wcalc.
-"matrix not positive definite".
-[Schutt-Aine] discusses this; we reproduce here for convienience.
-
-\[ L_{11} = L_{22} = L_{even}  \]
-\[ L_{12} = L_{21} = L_{odd}  \]
-\[ C_{11} = C_{22} = C_{even}+C_{odd}  \]
-\[ C_{12} = C_{21} {\it{(unused)}} = -C_{odd}  \]
-
-\rule{\linewidth}{0.2pt}
-
-In practice, the timestep required to obtain convergence in particularly tight corners of the SPICE simulation can drop to 1e-20, which is far below the Courant limit of the FDTD simulation.
-To eek out a bit more performance, a simple adaptive-timestep technique from [ a ] is used; we simply set the timestep so that the maximum change in voltage per timestep from the SPICE portion is less than
-some threshold.
-
-\PRLsep{{\itshape Sampling time-domain spectrometry}}
-
-\begin{quote}
-A rapidly increasing voltage step V tŽ . is applied to the 0
-line and recorded, along with the reflected voltage R tŽ .
-returned from the sample and delayed by the cable propagation time Figure 2 . Any cable or instrument artifacts Ž .
-are separated from the sample response due to the propagation delay, thus making them easy to identify and control. The entire frequency spectrum is captured at once,
-thus eliminating drift and distortion between frequencies.
-\end{quote}
-
-The pulse is usually recorded in real-time with a many-GHz oscilloscope. However, by using a sampling oscilloscope, massively undersampling the signal,
-
-Another advantage of this technique is that no high-Q filters are required to select the frequency;
-discrimination is in the time-domain, and is spread out over many seconds. It is also much easier to generate a 10+ GHz fast edge than it is to generate a CW signal.
-
-\PRLsep{{\itshape Power amplifier }}
-
-The amplifier and oscillator are separate for ease of design; this way the phase response of the amplifier is of no consequence.
-
-Our target power for the test is about 0.01 W, mandating a $2 \sqrt(2)$ V peak to peak RF swing on the Z=50 output.
-
-The $V_{CEO}$ breakdown of the bipolar transistor in question is only 2.3V.
-Above this value, current begins to flow from the emitter to the base, turning on the transistor and causing thermal runaway.
-If the base bias has a low enough impedance and can source current, this $V_{CEO}$ can be violated safely.
-[Toshiba, Bipolar Transistors, some other paper on the strong base bias]
-
-One solution would be to match the output to a lower impedance [Leuschner 2010]:
-
-\begin{quote}
-Generating high RF power from low supply voltages poses also another problem: the optimum load impedance of the PA output stage transistors becomes very small.
-A matching network with a high transformation ratio is needed to transform the antenna impedance of 50 to the optimum load impedance.
-High transformation ratios usually result in small bandwidth and higher losses.
-Possible solutions are the use of either non-standard high power RF devices or special circuit topologies using only the available standard devices.
-\end{quote}
-
-Use of so-called stacked, HiVP, or collector-feedback cascode designs can also allow the RF voltage to be distributed over many devices.
-
-It should also be noted that when stressed, these devices can fail with a slow power-output degradation over weeks, an effect not usually found in lower-frequency designs.
-
-\printbibliography[heading=none, title={}, keyword={amplifier}]
-
-\clearpage
-\PRLsep{ Wherein antennas are characterized}
-
-Method-of-moments solvers like NEC-2 are the standard for simulating these sorts of antennas.
-However, most commonly-available packages don't seem to handle multiple dielectric constants, such as the air and substrate of a patch antenna.
-
-The impedance of a structure over frequency can be determined in FDTD by:
-
-\begin{itemize}
-  \item Applying a gaussian pulse to a voltage source - in our case, applied to a via connecting the path (or probe)
-  \item Running the simulation until the transients have all died out below some threshold, while logging the source voltage and current at each timestep
-  \item Taking the fourier transform of the (real) excitation voltage and current (producing a complex result, mind you)
-  \item Taking the magnitude of the ratio of the two complex spectra.
-\end{itemize}
-
-This is the computational equivalent of dropping a piano off a balcony to see which key is stuck.
-
-See [Penney 1994], [Luebbers 1992], [Luebbers 1991], [Luk 1997].
-
-Our implementation is in \ghfile{electronics/simple_fdtd/runs/U.py}.
-
-A similar mismatch to the SPICE exists for fourier methods - but in the other direction.
-The courant limit often demands fine timesteps, but since each FFT bin is $ f_{bin} = n_{bin} / (N_{simulation} \ dt) $ , the majority of the FFT bins exist into the hundreds or thousands of GHz, leaving no resolution in the low-frequency domain of interest unless $N_{simulation}$ is extremely large - even if all the transients in the simulation have died down, you still have to keep the sim running to make the FFT happy!
-
-There's more than enough 'information entropy' in 4000 FDTD points for most antennas. But you need some 30,000 points to get 10 bins below 20 GHz!
-
-There are a few methods of changing the FFT bin size artificially, which [Bi 1992] reviews. You can "use a manual fourier integration over the frequency region of interest".
-
-But, in a staggering turn of events which will presumably be familiar to statisticans and preposterous to everyone else, a far simpler method is to {\it discard} 95\% of the data, by down-sampling to 1/10th or so.
-
-An equally simple method that seemed to produce better results in our case is to pad the voltage and current samples to the correct length.
-The jump discontinuity introduced by padding with zeros has a negligible effect.
-
-It's so thumpingly unintuitive to me that adding 50,000 zeros to a 5000 value dataset can improve the resolution of a measurement by 300-fold.
-
-It is important to remember to normalize the gaussian pulse, or else numerical noise will be introduced. The magnitude is not important - [Luebbers 1992] use 100v, others use 1v, etc.
-
-Though uneven dt FFTs exist, the time step can be constant at the courant limit for this simulation.
-
-A step impulse (1 first timestep, 0 otherwise) has been used in some works, though in our case performance was quite horrid.
-
-A correction factor due to the staggered magnetic field of the Yee lattice must be introduced; [Fang 1994]. Their $Z_2$ equation (correcting for spatial inaccuracies, but not temporal) was sufficient.
-
-This technique is equivalent to that used in electrochemistry, known as fourier impedance spectroscopy - except they seem to usually use a known impedance source rather than a hard source, presumably because ideal hard sources don't exist in reality.
-
-Allowing the simulation to run for long enough that all transients dissipate is important for accuracy - deceptive dips in the current can cause early termination.
-A surprising amount of detail is contributed by even the smallest current levels.
-Our threshold is 1e-7 amps for 700 iterations.
-
-[Samaras 2004] has a very useful set of experimental and FDTD data for calibration and comparison.
-Comparing a probe via source in the different positions, we obtained agreement of $\sim 7\%$ in impedance and $\sim 5\%$ in frequency.
-
-The use of a hard source feed-port affects the number of timesteps required by introducing unphysical transients.
-Using a port with a virtual 50-ohm resistance reduces the computational requirements by a large factor; see [Luebbers 1996].
-
-Simply monitoring the source current during the simulation is somewhat deceptive. Periodically monitoring the change in the fourier transform seems to be a better convergence metric.
-
-The units of the FFT (unlike those of the continuous FT) remain in volts.
-
-\rule{\linewidth}{0.2pt}
-
-Most equations in papers on the FDTD method are supplied without making the scaling factors explicit; some need multiplying by the Courant number, For use with flaport/fdtd the H-field to current line integral in [] requires scaling by $\mu_0 * (dx/dt)$, where $\mu_0$ is the vacuum magnetic permittivity, dx the cell size, and dt the timestep - despite the equation already possessing a deceptive set of $dx$-es.
-
-Naturally, if one is competent, this discrepancy will be immediately obvious.
-Those not dimensionally-intuitive, such as myself, find it useful to run dimensional analysis using a unit-aware calculator such as {\it sharkdp/insect}.
-
-\rule{\linewidth}{0.2pt}
-
-\begin{quote}
-With four parameters I can fit an elephant, and with five I can make him wiggle his trunk.
-\end{quote}
-- von Neumann
-
-with six parameters, you can do it with only physical constants. Beware numerology.
-
-\rule{\linewidth}{0.2pt}
-
-Most passives (inductors, capacitors) companies supply S-parameters for their parts. Use them.
-
-\rule{\linewidth}{0.2pt}
-
-This has nothing to do with , but it's an amusing parlor trick that I accidentally ran into while trying to carbothermally reduce copper oxide powder.
-It led me to the SiC susceptor resonator, so it wasn't a total waste.
-
-Add a thimblefull of fine copper powder to the bottom of a mason jar. Cover the mouth with a layer of Kapton tape. Next, inject pure argon gas for a few minutes, then seal the tape fully.
-
-Put the whole shebang in a friend's microwave oven.
-
-Wait patiently. There will be a sizable bang and a terrific plasma.
-
-My hypothesis is that this is due to the higher ionization energy of Ar. Air seems to slowly leak in, decreasing the
-
-\PRLsep{{\itshape The antenna itself }}
-
-The impedance of a patch antenna varies with position on its surface. Probe feeds to a specific point on the patch
-
-Unfortunately, patch antennas have a relatively narrow bandwidth.
-
-\rule{\linewidth}{0.2pt}
-
-\PRLsep{{\itshape Power sensing }}
-
-The diode detector power sensor is based on the Infineon appnote [] and [], itself based on a circuit from The Art Of Electronics.
-
-A detailed description of various diode detectors are found in []. Because the steady-state current through the detector is very small, the microstrip can simply be terminated in the standard manner.
-
-The Mini-Circuits ZX47-40-S+ would be an excellent low-cost COTS alternative.
-
-\printbibliography[heading=none, title={}, keyword={rectifier}]
-
-\PRLsep{{\itshape Microfluidics: small channels, big headaches }}
-
-We had anticipated having to perform a large number of tests for optimization of the impulse.
-Automating tests also has the advantage of removing operator bias, and (in our case) minimizing artifacts from the sample holder.
-Since all the components were already computer-controlled, it seemed little extra effort.
-
-We originally planned on using techniques from the rapidly accelerating field of centrifugal microfluidics, using a broadband patch antenna smaller than the cuvette, and measuring transmission through the cuvette.
-
-Centrifugal microfluidics has the advantage of getting a pump for free; mixing can be effected by generating vortexes by accelerating and decelerating quickly; and because everything is circular, it is easier to design equidistant.
-
-The most important feature is the consistent "down" vector; because capillary forces
-
-However, aligning seemed liable to produce artifacts; runout in the spindle;
-
-Sterilization is often effected by cytotoxic gas []. UV we resorted to autoclaving, warping.
-
-Th edges are charred; however, we have not found any discussion of toxicity of the laser cut edges, so we assume they're fine.
-
-In a crude version of transmission welding.
-Tx welding usually relies on one material being transparent, and the other opaque - clear and black plastics, for instance.
-We obtained nearly useable results by scuffing one surface and rubbing in fine graphite powder.
-
-Both the hydrophobicity / wetting angle of the substrate (useful for valves with a certain threshold pressure, among other things), the adhesive surface energy, and sterilization can all be effected by UVC exposure.
-Unfortunately, we were not confident in the homogeneity of the
-
-Not all plastics can be laser welded.
-
-3DuF; this is an excellent program
-
-The final process was as follows:
-
-Just using a single-sided tape over micromachined channels didn't work for us; the tape remains sticky and stuck to the bottom of the channel, blocking it.
-
-\begin{itemize}
-	\item 1/16" 003 size Viton O-rings McMaster-Carr \#9464K103, 
-	\item 3M 467MP 0.051 mm double-sided adhesive transfer tape with 200MP acrylic adhesive, DigiKey 3M9726-ND.
-	Various other tapes were tried, such as 9495MP; the laser was not powerful enough to cut these.
-	While the intermittent temperature rating is over 121 C, the high-pressure steam environment does seem to degrade any exposed regions of tape.
-
-	A CO2 laser is usually used to cut these otherwise transparent materials.
-We only had a diode laser.
-However, the front and back paper liners absorb sufficient laser power to melt the tape between.
-This produces horrible results, but was sufficient for this purpose.
-With our 2.5 W, ~0.15 mm spot size, 450 mm/min for the tape.
-
-	\item MG Chemicals 416-T Laser Printer Transparency Film, 0.1 mm thick. Presumably a PET/Mylar material.
-
-	\item A vinyl cutter was used to cut the openings in the top mylar cover slip.
-	\item Frame machined from polycarbonate with a 1/16" two-flute carbide endmill, 24000 RPM, between 500 and 1000 mm/min, up to 1.5 mm step-down.
-G-code generated with MeshCAM.
-This seems to withstand the autoclave without any damage.
-	\item Note: the tape preferentially sticks to the back liner, rather than the front.
-	With both adhesive liners on, rub the thing hard with a rounded edge and rolling pin.
-	Aluminum foil tape backing on the adhesive layer.
-	Don't de-weed yet.
-
-\end{itemize}
-
-Note that cutting many of these materials with a laser is a bad idea. The residue will
-
-\begin{itemize}
-	\item Tape mylar to a cardstock backing with masking tape on the sides. Cut mylar on plotter with InkCut. 175 g force. 
-	\item Apply aluminum foil tape to the rear backing (with "3M" text) of the adhesive transfer tape. This supports the cut structures, without being cut itself.
-	\item Stick the adhesive to the laser bed with Kapton, foil-side down. It's not a good idea to use masking tape; it'll catch fire.
-	\item 
-\end{itemize}
-
-Making this device ourselves was a grave mistake that potentially cost many lives. We should have used \cite{Straight}, a COTS version which we discovered halfway through.
-
-I'm sorry.
-
-\paragraph{Lessons learned:}
-
-When trying to characterize the response to some process parameters (say, laser power), iteratively trying different parameters in series can be somewhat useful, as each trial informs the next.
-In this instance, we would try a speed and power, unstick the material from the bed, observe the result, decide on the course of action, and repeat.
-However, if it is possible to try many parameters in parallel just as fast as in series, (that is, in our case, make a coupon using [] that tries all reasonable values simultaneously), it would be very dumb not to do this.
-
-We are very dumb.
-
-\printbibliography[title={General fluidics resources}, keyword={microfluidics}]
-
-\printbibliography[title={Centrifugal}, keyword={centrifugal}]
-
-\PRLsep{{\itshape aaaaa }}
-
-One problem with the formal, academic paper format is that one starts to believe what is written, which is a death sentence for accurate reasoning. We try to avoid this by being unprofessional.
-
-\label{para}
-\ref{para}
-
-\paragraph{Timeline}
-
-\paragraph{Comments by others}
-
-\Acrobatmenu{GoBack}{Back}
-
-\end{document}

### 2020-11-04 documents/supplemental.tex
DNA
pmt counter

@@
 
-\paragraph{Molecular dynamics simulation}
-\
-%\begin{multicols}{1}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{quote}
+The accumulated insight of a [] worker frequently merits recording when no documentation can be given.
+\end{quote}
 
-It was originally expected that a large part of this work would be done in-silico, as we did not anticipate having access to suitable RF test equipment.
-
-Some time was spent attempting to set up a molecular dynamics toolchain capable of simulating an entire virus.
-
-Having an approximate simulation of the this technique would be useful for a number of reasons:
-
-We would have a better idea of the transferability to SARS, without wasting the time of experts with BSL-3/4 labs.
-
-The impulse could be subjected to the same optimization as the RF feedback loop. A number of parameters (such as phase, polarization)
-
-Coarse-graining also greatly increases the allowable timestep.
-
-We also did not understand the *confined* part in the *confined* acoustic resonance.
-
-Simulating the aggregate bose condensate wavefunction is well beyond us.
-
-Both finite-element, molecular-dynamics, and stiffness-eigenvalue normal mode techniques have been used to great effect for this purpose.
-
-%\end{multicols}
-
-\PRLsep{{\itshape Virus structural data }}
-
-One extreme can be seen in
-
-Because CryoEM is sensitive to the
+- W. G. Cochran et al, \cite{Statistical1953}
 
@@
 Phage releases several amino acids such as putrescine and spermadine when broken. These can be indicated at ppm scales with ninhydrin, or at nanogram scales via fluorescamine.
+
+Otherwise, GFP-flouresecent strains of E. coli, or phage which has been labelled with a
 

### 2020-11-05 documents/acknowledgement.tex
test

@@
 
-Thanks to (Dr. ) Barfuss for spending time reviewing an early draft.
+Thanks to (Dr. ) P. Barfuss for spending time reviewing an early draft.
 
@@
 
-Prof. Griffiths and Dr. Brovko at UGuelph, Dr. Anany at the Guelph Research and Development Centre for tips on the Beta-Glo assay.
+Prof. Griffiths and Dr. Brovko at UGuelph, Dr. Anany at the GRDC for tips on the Beta-Glo assay
 
-Thanks to L.H. for wisdom regarding this project; Profs David and Taylor (among others) at YorkU for being super nice, and H.P. and ice9 for tolerating ramblings.
+Professor Z-G Wang at Caltech for a note on electrostatics,
+
+Profs David and Taylor (among others) at YorkU for being super nice, and H.P. and ice9 for tolerating ramblings.
+
+Thanks to L.H. for wisdom regarding this project;
 
@@
 
-R.I.P. to Dr. Robert Adair, whose work features prominently here, died Sep. 2020.
+R.I.P. to Dr. Robert Adair, whose work features prominently here, who died Sep. 2020.
 
@@
 
-The authors reluctantly acknowledge the Computational Electromagnetics Group at The University of Texas at Austin for going through the trouble to develop the AustinMan and AustinWoman human body models and then making them unavailable at https://sites.utexas.edu/austinmanaustinwomanmodels/, and also unavailable via email.
+The authors reluctantly acknowledge the Computational Electromagnetics Group at The University of Texas at Austin for going through the trouble to develop the AustinMan and AustinWoman human body models and then making them unavailable at https://sites.utexas.edu/austinmanaustinwomanmodels/, and also not replying to email.
+
+It's okay, I'm not bitter.
 
@@
 
-The authors acknowledge the IT.IS foundation for doing precisely the same, but actually replying to emails.
+The authors gratefully acknowledge the IT.IS foundation for the same, and also compiling the tissue property databases.
 
@@
 
-{\Large <3}
+{\Large {\verbatim <3}}
 

### 2020-11-06 documents/supplemental.tex
TCL dump

@@
 - W. G. Cochran et al, \cite{Statistical1953}
+
+For in-vitro research, it seems to me that perhaps this field is running into the issues Feynman's rat-races \cite{Cargo}.
+There are a large number of very tricky variables.
+Requires analysis fo the very details of how the study was conducted, rather than simply its results.
+While the measurements
+
+Of course, we commit the very same mistakes and fall into the same traps, we are not immune from criticism.
+
+In some cases, these are thoroughly characterized and described. UWB rat paper.
+
+But it seems to me that each worker (myself included!) is using their own test arrangement; and yet the studies are not so different as to require such customization.
+
+It occurs to me that perhaps a set of exquisitely characterized standardized test cells and procedures would be helpful; and a requirement that any papers on the topic either use such a cell, or if their study requires some exceptional treatment, to follow an established procedure to add a new cell to the standard.
+
+Alternatively, methods such as the optical hetrodyne one,
+
+If possible, very specific buffer compositions should be made universal.
+
+What heating patterns can be expected from a certain microwave input? What modes can be introduced by deviations in machining tolerances?
+
+Then, of course, are the questions of the excitation: what brand of attenuators are satisfactory?
+
+Of course, one cell could not suffice for the whole range of microwave frequencies.
+
+There is also the matter that the scientific publishing infrastructure could perhaps provide for a "scientific lineage".
+We often hear of a "scientific record": journals will retract a paper from "the record"; but where {\it is} this record?
+Where is the chain of trust upon which new results can be added?
+Each paper is forced to supply its own context; each worker is forced to re-dredge the entire chain of truth, to discover the controversy which clouds some papers; each offers its own interpretation of the literature.
+It is inevitable that some history will be lost; that the wrong starting point will be taken up; a veritable fork in the literature.
+Especially as the volume of scientific research increases as society proceeds.
+The only data is a few references per paper, and a date for each!
+Another such record exists in comprehensive books written by workers on the topic.
+
+But is this not an artifact of the limitations of printed journals, whereby papers must necessarily be individual entities?
+Is there no way by which papers can be arranged so that they each supply a visible part of the jigsaw, where each paper brings with it the complete story of the field?
+
+Scite.ai and similar services, but it feels like these are tacked-on workarounds to re-add metadata which should have existed in the first place.
+
+Consider the non-thermal effects literature. It starts, perhaps, in the 1800s;
 

### 2020-11-14 documents/lessons_learned.tex
Propagation
e

@@
 \paragraph{Lessons Learned} \
+
+\rule{\linewidth}{0.2pt}
+
+There seems to be a drive towards small volumes and microfluidics. This is great; these are cool technologies; but in our case these were a huge hindrance.
+
+There are a lot of reasons why small volumes are useful: you can run more tests with a given quantity of sample - a 1500-well microplate assay would be a hard sell with even 1.5 mL tubes; small samples are diluted to a lesser degree.
+
+However, it should also be considered that most tolerances and precisions do not scale with volume. 
+Rheology does not scale with volume, so bacterial culture becomes a challenge.
+Dust and contaminants do not scale.
+Optical path lengths are much shorter.
+Most assays will have decreased resolution.
+Precision in dispensing is much more critical, as is deformation due to autoclaving.
+The "hairs" that appear on machined polypropylene, which are almost impossible to remove, can be as large as your sample.
+Evaporation is much more critical.
+
+Most importantly, annoyance scales inversely with size. It is hard to work with a quantity of fluid which is barely visible.
+
+\rule{\linewidth}{0.2pt}
+
+Minor errors in .
+Reproducible coding helps, but it would be much better if we had used standard software engineering best practices; red-teaming, unit testing on generated data, etc.
+It might also be helpful if the data itself are blinded against randomly generated controls - in many cases that's not possible, but it might be useful in some circumstances.
+
+See Phosphine.
+
+\rule{\linewidth}{0.2pt}
+
+The phage field - and many other fields - seem to have a problem where most of the really important base discoveries related to practice -
+
+Some things actually seem to have been lost.
 
@@
 
-This is obvious to all compentent, but when rapidly iteratively testing with simulations, it may be helpful to automatically save a package with images of all the components (schematics, graphs, input files) of each distinct test.
+This is obvious to all competent, but when rapidly iteratively testing with simulations, it may be helpful to automatically save a package with images of all the components (schematics, graphs, input files) of each distinct test.
 
@@
 
-When rapidly testing data analyses which aren't really conducive to unit testing, I previously used to run the whole simulation, look at the analysis, re-run the sim, etc.
+When rapidly testing data analyses of simulations which aren't really conducive to unit testing, I previously used to run the whole simulation, look at the analysis, re-run the sim, etc.
 
-This is slow. I often don't change the input parameters for the sim, but just the analysis. However, there's often a large amount of state to persist to disk.
+This is slow.
+I often don't change the input parameters for the sim, but just the analysis.
+However, there's often a large amount of state to persist to disk, so it's not worth writing a serializer just to store this throwaway run.
 
-Saving the entire session with 'dill' is very helpful.
+In this case, saving the entire simulation session with 'dill' is very helpful.
 
@@
 There's also a very neat thing that seems to be common in computational biology, but which doesn't seem popular in other fields.
-After an algorithm or software tool is written (and the source published seperately), a simple CGI frontend is written around it and hosted on the university's servers.
+After an algorithm or software tool is written (and the source published separately), a simple CGI frontend is written around it and hosted on the university's servers.
 eLNemo and the CHARMMing web interface are advanced examples of this.

### 2020-11-14 documents/paper.tex
Protein charges processed
e

@@
 
-Protein net charges extracted from primary protein sequences compiled by the proteome-pI database \cite{ProteomepI2017} and UniProt using localCIDER \cite{CIDER2017} \ghfile{biology/data/net_charge.py}.
-
 \clearpage
@@
 \subfile{safety}
-
-\clearpage
-{\Large \it The plausibility of low-cost microwave masks}\\
-
-With the most recent few generations of semiconductor processes, producing significant powers in the X-band has become inexpensive.
-Silicon transistors are limited in their output power and gain; Silicon-on-insulator topologies
-
-This is perhaps most readily illustrated with the HB100 radar module.
-This device implements a complete doppler radar with two RF MOSFETS and a dielectric resonator.
-It operates at 10.6 GHz, yet are produced for under \$3.
-The PCB is stock FR4.
-
-Our crude experimentation has yielded about 10 mW with a single SiGe:C transistor, the Infineon BFP620 (\$ 0.34 apiece \@ 1000-of.).
-For the personal microwave sterilizer, given the threshold levels found by Yang, this corresponds to a cost per sterilized cubic centimeter of approx.
-\cite{BFP620H7764XTSA1}.
 

### 2020-11-14 documents/personal_device.tex
tests
e

@@
 {\color{red} speculation \{ }
+
+\clearpage
+{\Large \it The plausibility of low-cost microwave masks}\\
+
+With the most recent few generations of semiconductor processes, producing significant powers in the X-band has become inexpensive.
+Silicon transistors are limited in their output power and gain; Silicon-on-insulator topologies
+
+This is perhaps most readily illustrated with the HB100 radar module.
+This device implements a complete doppler radar with two RF MOSFETS and a dielectric resonator.
+It operates at 10.6 GHz, yet are produced for under \$3.
+The PCB is stock FR4.
+
+Our crude experimentation has yielded about 10 mW with a single SiGe:C transistor, the Infineon BFP620 (\$ 0.34 apiece \@ 1000-of.).
+For the personal microwave sterilizer, given the threshold levels found by Yang, this corresponds to a cost per sterilized cubic centimeter of approx.
+\cite{BFP620H7764XTSA1}.
 
@@
 	\includegraphics[width=\textwidth]{my_photo-17.jpg}
-	\caption{\\ An ultrawideband tunable 7 GHz VCO based on \cite{TripleTuned2008}.
+	\caption{\\ A wideband tunable 7 GHz VCO based on \cite{TripleTuned2008}.
 This uses an Infineon BFP620 SiGe:C transistor (\$0.3) and a network of four varactor diodes.

### 2020-11-18 documents/charge.tex
data

@@
 
-As might be expected, the electrostatic properties of the virus differ from that of host cells, both \cite{Icosahedral2019} on the sub-protein level:
+As might be expected, the electrostatic properties of the virus differ from that of host cells, both on the sub-protein level\footnotemark
 
-\begin{quote}
+\footnotetext{
+\cite{Icosahedral2019}\begin{quote}
 	Different from insect, plant, and human, viruses had more positively charged than negatively charged segments.
-In Fig.
-1B we show the log (base 10) net-charge frequency value for a selected group of proteins (e.g., Viral proteins) subtracted of the log expected frequency value calculated from the total proteome distribution (i.e., log10-fold-change).
 Viral proteins were the only class enriched in extremely high positively charged segments (charge ≥ + 17) when compared to the overall proteome (1B-inset with p-values).
 \end{quote}
+}
 
@@
 
-todo: is it possible for the charged core to compensate for the potential energy of the charged shell?
+\begin{autem}
+TODO: is it possible for the charged core to compensate for the potential energy of the charged shell?
+\end{autem}
+
+Using electroporation data, is osmotic transfer a common
+
+If the intracellular concentration of 500 mM of ions  from https://www.cell.com/action/showPdf?pii=S0006-3495%2899%2976974-2 is extrapolated to viruses,
+
+$500 millimolar * (4/3 pi * ( 60 nanometers)^3)  3e5 e-$
+
+Indeed, the intracellular concentration would need to reach almost 25 molar for these results to be explained.
+
+This is actually not too extreme. Bacteriophages can reach 3 M.
+
+"Osmotic Shock and the Strength of Viral Capsids"
+
+For an impermeable virus like the even-numbered T's, the inside salt concentration is set by the incubation solution's value of nb.
+Anderson et al.
+(1953) found in the case of T6, upon rapid dilution with distilled water, for example, that incubation nb values on the order of 1.5 M were required for osmotic shock.
+From Eq.
+2, and n0 ≈ 3 M, it follows that nin ≈ 0.62 M and hence n++ n− ≈ 4.2 M, which because of the Donnan equilibrium is indeed significantly larger than 2nb ≈ 3 M.
+
+https://www-sciencedirect-com.ezproxy.library.yorku.ca/science/article/pii/S0006349503744555
 

### 2020-11-18 documents/fluorescence.tex
e
Tube 3
data

@@
+%!TeX root = fluroescence
+\documentclass[paper.tex]{subfiles}
 \begin{document}
+
+If time-domain filtering is sufficient,
 
@@
 
-Nanodrop, using 280 nm absorbance.
+Contrary to standard microscopy, you want as little excitation light to enter the objective as possible. Using the existing
+
+Nanodrop, using 280 nm absorbance. They're also \$10,000.
 
 the input edge is considered a clock; the minimum pulse width limits apply, but are not clearly specified in the datasheet. In this case (1/155 mhz) = 6 ns.
+
+However, we had no luck with precipitation.
+
+Luckily, a recent paper has the answer: direct fluorescent detection of DNA in solution, outside using dyes that bind to (intercalate into) DNA. GelGreen doesn’t penetrate.
+
+As noted by [xi?], this is a saturating effect; if too many flurophores intercalate into the DNA the fluorescence is weaker.
+A “1/4000” solution of GG in distilled water mixed 50/50 with the sample (“1/8000”) worked great in our case.
+
+(Phi6 uses an RNA - many dyes have different responses to single-stranded (ss)DNA, dsDNA, or
+
+With the setup we’re using and the small quantities, the excitation light is somewhere around ~10^5 times as powerful as the emission.
+This doesn’t seem to be a big issue gel-docs, picking out bands on gels - they don’t usually seem to use excitation filters; however, to get the excitation bleed-through low enough to do this quantitative assay, the bleed-through must be really low, and in our testing proper dielectric filters are required on both the excitation and emission sides.
+
+There are a few sources of noise:
+
+PMT dark counts
+Some be filtered out by judicious use of comparator pulse height threshold, the lock-in takes care of it. A non-issue in our case.
+Ambient light leakage
+Using microscope optics and the lock-in, essentially a non-issue for use, surprisingly. Some fluorescence microscopes use micron-size apertures to limit the depth of field to avoid Putting 
+Figure out the average current limit for your PMT, the expected voltage based on your load resistor value and watch that it never exceeds it. It’ll be fine. Even with the room lights
+
+Note that PMTs are happy to endure very high pulse currents, like flashbulbs for exciting.
+
+No shutters or anything required.
+
+The PMT was at maximum sensitivity (in fact, slightly above max voltage)
+
+Gel-docs , with spectra specified using the Wratten scale. These do not seem to have optical density (OD - logarithmic value of transmission in the blocking band) values sufficient for this qfluor.
+
+Epiflurorescence means the Most commercial microscopes use dichroic beamsplitters, allowing the excitation beam beam to go through the same objective.
+The dichroic only removes the excitation to the 1\% level - you still need the dielectric filters, and they’re really expensive.
+With fiber optic excitation at right angles to the objective, scattering was low enough that the dichroic was completely unnecessary.
+
+You might be wondering why the filters are even required - why not just subtract the excitation bleed-through with a control?
+Unfortunately, any miniscule variation in the scattering of the excitation will be orders of magnitude larger than the fluorescence signal you’re looking for.
+
+Some papers discuss adding a third chopper or gate period or photomultiplier or to measure the drift of the excitation light source.
+
+Gating the photomultiplier HV is another technique.
+
+PCR is another method
+
+I thought the pulse height
+
+An even better Phase-shift time domain fluorimetry.
+Iwata use a 20 MHz DSO to measure a 5 ns $\tau$ fluorophore.
+However, this involves a light source with a fast modulation bandwidth; and in the implementation they describe, the PMT must be in the voltage mode.
+
+Called time-correlated photon counting.
+
+Then your
+
+Cree recommends staying below 300\% of the continuous power when modulating an LED.
+
+While there are ways to deconvolve a slow falling edge, there’s another problem: per time interval, the time spent in the excitation-off, flurophore exponential decay time is proportional to the frequency of the excitation light.
+If you’re only getting 1000 photons from the sample per second, the dye lifetime is 5 ns, and you’re turning the light on and off at 1 MHz, you’re only getting a [] photons from the exponential decay region.
+Even with a long exposure, that doesn’t seem to be enough to pick up the decay.
+
+Another way to pick up this phase shift is to make your lock-in amplifier phase-sensitive - very simple (a 2x clock put into a flip-flop divider, then the middle).
+This also wasn’t nearly good enough, completely useless.
+
+Simple spectrally-filtered intensity is good enough.
+
+Contrary to luminescence, you have control over when the excitation and emission light turns on, so you can do a lock-in. This doesn’t subtract the excitation bleed-through, but it
+
+Polarization is a neat way to filter; linearly polarize the excitation, the emission comes out whatever orientation the DNA happens to be, which is usually random. Apparently
+
+\end{document}

### 2020-11-18 documents/pamphlet.tex
Quick ol' FDTD sim of lung
data

@@
+%!TeX root = pamphlet
 \documentclass[fleqn,10pt]{paper}
@@
 
-Both the microwave and microbiology components of this field appear to be unusually sensitive to experimental design and exceptionally prone to artifacts that cause false positive results: \cite{Microwave1982} $\neq$ \cite{Resonances1987}, \cite{Effects1985a} $\neq$ \cite{Cytogenetic1986}, \cite{Comprehensive2018}.
+Both the microwave and microbiology components of this field appear to be unusually sensitive to experimental design and exceptionally prone to artifacts that cause false positive results: \cite{Microwave1982} $\neq$ \cite{Resonances1987}, , \cite{Comprehensive2018}.
 Though the cited articles have taken care to avoid these effects, it is entirely possible that none of what is discussed below actually exists.

### 2020-11-18 documents/personal_device.tex
data

@@
 
-This is perhaps most readily illustrated with the HB100 radar module.
-This device implements a complete doppler radar with two RF MOSFETS and a dielectric resonator.
+This is perhaps most readily illustrated with the commercial HB100 radar module.
+This device implements a complete Doppler radar with two RF FETs and one dielectric resonator on a standard FR4 substrate.
 It operates at 10.6 GHz, yet are produced for under \$3.
-The PCB is stock FR4.
 

### 2020-11-18 documents/sic_susceptor.tex
data

--- 2020-08-30 documents/test.tex
@@
-\documentclass[fleqn,10pt]{paper}
-
-\usepackage[left=2cm,right=2cm,
-top=0.5cm,
-bottom=1.5cm,%
-headheight=11pt,%
-letterpaper]{geometry}
-
-\include{preamble}
-
-\title{{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation}
-
+%!TeX root = sic_susceptor
+\documentclass[paper.tex]{subfiles}
 \begin{document}
@@
 
-To verify that we can detect a resonance with this setup, we use the microwave susceptor mixture described by \cite{Effect2016}, which can be tuned to the correct range by varying the concentration of SiC to binder.
-We use the S-1 mixture.
+To verify that we can detect a resonance with this setup, we use a microwave susceptor mixture described by \cite{Effect2016}, which can be tuned to the correct range by varying the concentration of SiC to binder.
+We used the S-1 mixture.
 
 0.6g 2000-mesh silicon carbide powder was added to 1.4 g white Elmer's glue, mixed manually until homogeneous,
-applied to a mylar film, and dried with a hair dryer. A small wafer of the hardened mixture, perhaps 0.3 mm thick, 5 mm x 2 mm, was placed directly on top of the coplanar waveguide.
+ applied to a Mylar film, and dried with a hair dryer. A small wafer of the hardened mixture, perhaps 0.3 mm thick, 5 mm x 2 mm, was placed directly on top of the coplanar waveguide.
 
-The spectrum was then captured, averaging (?10) sweeps of the VCO. The background spectrum was taken without the wafer in place.
+The spectrum was then captured, averaging multiple sweeps of the VCO. A background spectrum was taken without the wafer in place, and then the two sweeps were subtracted.
 
@@
 
-\cite{Effect2016} measures a peak at about 7.2 GHz. Our peak is at approximately 7.849 GHz, which is well within variation in powder grain sizes and concentration.
+\cite{Effect2016} measures a peak at about 7.2 GHz. Our peak is at approximately $7.84 \pm \approx 0.25$ GHz, which is well within variation in powder grain sizes and concentration.
 
-The paper specifies the reflection loss, S$_{11}$. Unfortunately, having no directional couplers, it is probably not possible to directly determine S$_{21}$ and S$_{11}$ with this setup.
+The paper specifies the reflection loss, S$_{11}$. Unfortunately, having not designed in directional couplers, it is probably not possible to directly determine S$_{21}$ and S$_{11}$ with this setup.
 
-Naively, we might expect the peak to appear as a decrease at both sensors; instead it appears as an increase in transmission and decrease in reflection.
+Naively, we might expect the peak to appear as a decrease at both sensors; instead it appears as an increase in the far sensor and decrease in the near sensor.
 It could be possible that the presence of the dielectric wafer has merely detuned an existing resonance, that the peak is a coincidence, and that these data mean nothing.
+
 The raw voltage plots do not suggest that this is the case; but it is nonetheless concerning.

### 2020-11-20 documents/lessons_learned.tex
done

@@
 Minor errors in .
-Reproducible coding helps, but it would be much better if we had used standard software engineering best practices; red-teaming, unit testing on generated data, etc.
+Reproducible coding helps, but it would be much better if we had used standard software engineering best practices; red-teaming, unit testing on randomly generated data, etc.
 It might also be helpful if the data itself are blinded against randomly generated controls - in many cases that's not possible, but it might be useful in some circumstances.

### 2020-11-20 electronics/propagation/propagation_lib.py

@@ -115,6 +115,8 @@ class test_fourier(unittest.TestCase):
         print(p.mode_frequencies)
         print(times[-1])
 
+
+
     def test_fourier_reconstruction(self):
         sampling_frequency = 50000
         input_frequency = 1000.0
@@ -142,7 +144,7 @@ class test_fourier(unittest.TestCase):
         aux_phase = np.zeros_like(spatial_phase,dtype=np.float32)
         output = p.fourier_sum(spatial_phase, aux_phase, times)
 
-
+        assert(output - input == 0)
 
         plt.plot(times,output)
         plt.show()

### 2020-11-20 documents/fluorescence.tex
basic run done
nah.

@@
 Xu's method \cite{Quantification2020}
+
+Performance of this arrangement was satisfactory.
+A 10-second integration time, with, produced a background fluorescence signal of ~1500 counts, with per-sample stability of approximately \pm 1500 counts.
 
@@
 
+Silicon photomultipliers like ON's C−Series are almost certainly sufficient for this application, eliminating the HV requirements of PMTs at the cost of a higher dark count and slightly smaller active area.
+
+half-life is 0.693 times the average lifetime.
+
 I thought the pulse height
@@
 Called time-correlated photon counting.
+
+Another neat technique is to add
 

### 2020-11-20 firmware/eppenwolf/runs/sic_susceptor/sic_subtract.py

@@ -54,5 +54,9 @@ plt.savefig("sic_9_2.svg")
 # plt.show()
 
 plt.figure()
-plt.plot(freqs, (averaged_sic[:,2]/averaged_sic[:,1]) / (averaged_background[:,2]/averaged_background[:,1]),label="'Far' sensor,  $\propto$S$_{21}$")
+plt.plot(freqs, (averaged_sic[:,2]/averaged_sic[:,1]) / (averaged_background[:,2]/averaged_background[:,1]),label="")
+plt.legend()
+plt.xlabel("Frequency (GHz)")
+plt.ylabel("Absorbance")
+plt.savefig("sic_9_3.svg")
 plt.show()

### 2020-11-21 documents/background.tex
Wording

We have cycled between condemning as pathological science, and lauding it as the cure. Barring

Previous works (Liu et al, ) appear to demonstrate that several species of viruses exhibit an anomalous dielectric relaxation time of $> 75 \text{ ps}$, as opposed to $< 20 \text{ ps}$ \footnotemark measured in the structures of human tissue.\\

Other studies (Yang et al, Hung et al, Sun et al) then appear to demonstrate experimentally that - due to this effect and the favorable combination of envelope and genome net charge, envelope and capsid yield stress, mass distribution, and overall stiffness - certain viruses can  apparently be made to ring up, leading their envelope to shatter, when exposed to intense but ostensibly safe CW tones in the X-band - very much like a singer might shatter a wine glass.\\

Such a non-thermal mechanism is quite unprecedented and extremely dubious, oft-posited but never substantiated; so it has taken some convincing that this is not a particularly abstruse artifact, especially when considered in the context of the broader non-thermal effects literature. For instance, the very paper (Edwards) which spurred development of the hydration-layer damping hypothesis used to explain these results, is has been quite\cite{Resonances1987} definitively\cite{Microwave1993a} shown to be an artifact, one which we unfortunately have not excluded in our study.\footnotemark \ In fact, even in light of the fine evidence that the other groups have collected, and the poor-quality data we have collected, we are still not entirely convinced that this effect exists - but perhaps this skepticism is unjustified.\\

\footnotetext{we should verify, based on simple solvated sphere damping, whether the damping is of the right order of magnitude}

We contribute almost nothing to the record (much of our discussion has already been covered by []), except by apparently replicating the effect in a T4 bacteriophage surrogate, using both microwave feedback and a luminometric beta-galactosidase infectivity assay. We appear to demonstrate that inactivation does not require 15 minutes, but is complete in less than 500 nanoseconds. This provides a headroom of some $10^6$ to all safety limits imposed by all known harm mechanisms, which can be traded for depth in tissue or distance in space. \\

This technique appears to be unique in that it is selective, save for Far UV or cold-plasma sterilization. Its advantages over those is that it operates over large volumes with inexpensive emitters, but, most critically, can be made to penetrate tissue without harm.

We briefly review the biological basis for the safety. There is solid in vitro and limited in vivo evidence of safety in this regime.

\footnotetext{This value for human structures is the aggregate Cole-Cole relaxation time from Gabriel, in the case of breast tissue (which has the highest value). This is somewhat an unfair comparison; the relaxation time of a heterogeneous mixture such as tissue often appears smaller than that of a pure sample. However, this value agrees well with the individual findings of cellular modes (for instance, the damping from Adair's estimates is approx. 10 ps)}

We briefly examine three applications. All depend significantly on what the microwave spectrum of SARS-NCoV-2 ends up being, which must be measured - or possibly reconstructed from existing whole-virion data or determined from coarse-grained MD simulation.

With refinements, our inexpensive pulsed microwave spectrometer can obtain the required absorption and threshold data with sufficiently concentrated specimens; but proper dielectric spectroscopy labs (or, in a pinch, swept-EPR/ESR equipment \st{when used improperly}) will provide a much more detailed spectrum. A slightly safer low-titer primary specimen may be usable to avoid BSL-3 requirements. \\

First, free-space techniques are easily implemented to prevent respiratory transmission. A \$10 emitter appears to suffice on a personal level, and \$100 systems for room-scale.\\

%
Second, via cursory FDTD simulations, using off-the-shelf equipment and modified non-invasive microwave diathermy techniques, it appears to be possible to inactivate all virions in the outer 2 cm of the lungs and inner 1 cm of the bronchi without any effect on the surrounding tissue. 
\\

[] notes that with a bit more effort, by harnessing the dispersive nature of tissue using modulated Brillouin precursors, it may be possible to remove the virus from the body altogether.\\

The mechanism also provides a few distinctive microwave signatures that may be useful for detection; it remains to be seen whether these can be discerned in practice.

The claims above are extraordinary. We do not provide the extraordinary quality of evidence required to support them. Consider: is it more likely that an undergraduate in his parent's basement, with no experience in biology or microwave design, has misinterpreted a blip from a cobbled-together machine, or that

expelling its viral contents into solution and

Not to be confused with pseudoscientific 'resonance therapies', nor reports of a connection with 5G communications.

This means that the technique is {\it selective}.

### 2020-11-21 documents/charge.tex
Wording

--- 2020-11-04 documents/charge.tex
@@
 
-Back-of-the-envelope.
+\section{Charge}
 
-Yang et al determine that, to fit their microwave absorption cross-section data and produce the decrease in infectivity via the route they suggest, the "core" and "shell" of the virus should have an effective charge of about $10^7 e^-$.
+Yang et al determine that in order to fit their microwave absorption cross-section data, and produce the decrease in infectivity via precisely the mechanism they suggest, the "core" and "shell" of Influenza A should have an effective charge of about $q=1 \times 10^7 e^-$.
 
@@
 
-Protein net charges extracted from primary protein sequences compiled by the proteome-pI database \cite{ProteomepI2017} and UniProt using localCIDER \cite{CIDER2017} \ghfile{biology/data/net_charge.py}.
+As might be expected, the electrostatic properties of the virus differ from that of host cells, both on the sub-protein level\cite{Icosahedral2019} \footnotemark \ and in the lipid bilayer \cite{Lipid2015} \footnotemark.
+The mechanism given is that ions from solution counteract the protein charges to form an "electric double layer".
+In any case, the best representation is two concentric spheres with a net charge each.
 
-look into the Gibbs–Donnan effect
+\footnotetext{
+	\cite{Icosahedral2019}: \begin{quote}
+		Different from insect, plant, and human, viruses had more positively charged than negatively charged segments.
+Viral proteins were the only class enriched in extremely high positively charged segments (charge greaterthan + 17) when compared to the overall proteome (1B-inset with p-values).
+	\end{quote}
+}
 
-blood plasma
+\footnotetext{The virus steals its envelope from the host cell; but it tie dyes its duds before it bounces.}
 
-If we assume that the charge is not as. All other properties being equal, to account for the same coupling and absorption, one of the following would seem to need to be true:
+\begin{autem}
+	autem: Are you sure you're understanding the nature of this "effective" charge properly?
+\end{autem}
 
-1. the effective path length of the fancy test waveguide used by Yang may not be as they expected.
-2. The concentration of virus was higher than measured.
-3.
+\subsection{Major proteins and other components}
 
-On the largest scale, at a pH of 7, the net charges of the 11 proteins coded for by the Influenza A genome only contribute
+Protein net charges extracted from primary protein sequences compiled by the proteome-pI database \cite{ProteomepI2017} and UniProt using localCIDER \cite{CIDER2017}.
+See \ghfile{biology/data/net_charge.py} and structure.csv.
+Detailed source information will be added later!
+There are many.
+
+Note that this is considering the net charge of a whole isolated protein.
+Some proteins poke through the envelope; if a zwitterionic polarization existed from one end to another, for instance, this would not count here but would affect the coupling to an EM field.
+Given the size of most proteins, however, this doesn't seem like a likely effect.
+
+\subsection{Electrostatic energy}
+
+Let's compare the potential energy that would be required to assemble a single sphere of such a charge to the known host metabolic burden of assembling a virus.
+
+%https://www.macmillanlearning.com/studentresources/college/physics/tiplermodernphysics6e/classial_concept_review/chapter_11_ccr_20_electrostatic_energy_of_a_sphere_of_charge.pdf
+
+$$ U = \frac{3}{5}  \frac{1}{4 \pi \epsilon_0} \frac{Q^2}{R} \approx 2.3\text{e}^{-7} \text{ J} $$
+%U = (3/5) * 1/(4*pi*electricConstant) *((1e7 electricCharge)^2 / 60 nanometers) = 2.30708e-7 J
+
+The total is $6 \times 10^{11}$ ATP-equivalent.
+
+%50 kJ per mole, 6.022*10^23 = 9.9634673e-13 * 50 kj = 5e-8 J
+
+Mahmoudabadi\cite{Energetic2017} provide a total per-virion energetic cost of $10^8 $ ATP-equivalent , so this appears to be 3 orders of magnitude too large.
+
+Of course, much of the potential energy may have already existed in the host cell, so this is probably an invalid comparison.
+And if most of the charge is contributed by osmotic, ion, this potential energy may not be considered in the above.
+
+\begin{autem}
+	autem: is it possible for the charged core to compensate for the potential energy of the charged shell?
+\end{autem}
+
+\subsection{First principles}
+
+Influenza is approximately 174 MDa Ruigrok.
+Assuming a typical 50\% H concentration, such a charge would require about 1 in every 15 atoms to have a free electron.
+Compare to less than 1/100 for Arginine or 1/600 for DNA.
+
+\begin{autem}
+	autem: What does a "free" electron mean in this context? Over what spatial extent does the "free" charge act?
+\end{autem}
+
+\subsection{Membrane potential perspective}
 
@@
 $$(4.523 \times 10^-14 \text{m}^2 \cdot 0.01 \text{F/m}^2 \cdot 100 \text{V}) \approx 10^5 e^- $$
-
-As might be expected, the electrostatic properties of the virus differ from that of host cells, both \cite{Icosahedral2019} on the sub-protein level:
-
-\begin{quote}
-	Different from insect, plant, and human, viruses had more positively charged than negatively charged segments.
-In Fig.
-1B we show the log (base 10) net-charge frequency value for a selected group of proteins (e.g., Viral proteins) subtracted of the log expected frequency value calculated from the total proteome distribution (i.e., log10-fold-change).
-Viral proteins were the only class enriched in extremely high positively charged segments (charge ≥ + 17) when compared to the overall proteome (1B-inset with p-values).
-\end{quote}
-
-and in the lipid bilayer \cite{Lipid2015} \footnotemark.
-
-\footnotetext{The virus steals its envelope from the host cell; but it tie dyes its duds before it bounces.}
-
-*detailed source information will be added later! There are several hundred.*
-
-Other enzymes
 
@@
 
-The conclusion that there can be no microwave resonances in DNA in water is in accord with the results of
-measurements in three different laboratories (Gabriel et al.,
-1987; Foster et al., 1987) using techniques designed to
-detect resonances with amplitudes less than 1/20th of that
-reported by Edwards et al. (1984).
 \end{quote}
+
+\subsection{Osmosis, ion ingress}
+
+As noted previously, electroporation involves the ingress of large amounts of charge. This requires a pseudo-DC pulse to drive this charge ingress.
+
+%If the intracellular concentration of 500 mM of ions  from https://www.cell.com/action/showPdf?pii=S0006-3495%2899%2976974-2 is extrapolated to viruses,
+
+%\[ 500 millimolar * (4/3 pi * ( 60 nanometers)^3)  3e5 e- \]
+
+Indeed, the intracellular concentration would need to reach almost 25 molar for these results to be explained.
+
+This is actually not too extreme. Some small bacteriophages can reach 3 M.
+
+"Osmotic Shock and the Strength of Viral Capsids"
+
+\footnotetext{
+For an impermeable virus like the even-numbered T's, the inside salt concentration is set by the incubation solution's value of nb.
+Anderson et al.
+(1953) found in the case of T6, upon rapid dilution with distilled water, for example, that incubation nb values on the order of 1.5 M were required for osmotic shock.
+From Eq.
+2, and n0 \approx 3 M, it follows that nin \approx 0.62 M and hence n++ n- \approx 4.2 M, which because of the Donnan equilibrium is indeed significantly larger than 2nb \approx 3 M.
+}
+https://www-sciencedirect-com.ezproxy.library.yorku.ca/science/article/pii/S0006349503744555
+
+\begin{autem}
+	autem: research the Gibbs-Donnan equilibrium
+\end{autem}
+
+If we assume that the charge is not as. All other properties being equal, to account for the same coupling and absorption, one of the following would seem to need to be true:
+
+1. the effective path length of the waveguide used by Sun may not be as they expected.
+2. The concentration of virus was higher than measured.
+
+On the largest scale, at a pH of 7, the net charges of the 11 proteins coded for by the Influenza A genome only contribute
 
@@
 The arguments regarding Resonances in microtubules are also
+
+\cite{Vibrational2002}
+The conclusion that there can be no microwave resonances in DNA in water is in accord with the results of
+measurements in three different laboratories (Gabriel et al.,
+1987; Foster et al., 1987) using techniques designed to
+detect resonances with amplitudes less than 1/20th of that
+reported by Edwards et al. (1984).
 
@@
 \section{Hello World}
-\subsection{Hello World}
 \label{sec:hello}
-
 \hyperref[sec:hello]{See section.}
 
-Rather than, for instance, less than 1/100 for Arginine or 1/600 for DNA.
-
-it would be interesting to compare the potential energy of assembling such a structure to the known host metabolic burden of assembling a virus.
-
-%https://www.macmillanlearning.com/studentresources/college/physics/tiplermodernphysics6e/classial_concept_review/chapter_11_ccr_20_electrostatic_energy_of_a_sphere_of_charge.pdf
-
-$U = 3/5 * 1/4 pi epsilon_0 Q^2 / R \approx 2.3e-7 $
-%U = (3/5) * 1/(4*pi*electricConstant) *((1e7 electricCharge)^2 / 60 nanometers) = 2.30708e-7 J
-
-The total is $6 \times 10^11$ ATP-equivalent.
-
-%50 kJ per mole, 6.022*10^23 = 9.9634673e-13 * 50 kj = 5e-8 J
-
-of course, much of the potential energy may have already existed in the host cell, so this is probably an invalid comparison.
-And if most of the charge is contributed by osmotic, ion , this potential energy may not be considered in the above.
-
-todo: is it possible for the charged core to compensate for the potential energy of the charged shell?
-
 \end{document}

### 2020-11-21 documents/sic_susceptor.tex
Wording

@@
 \begin{figure}[H]
-	\includesvg[width=\textwidth]{sic_9_1}
+	\includesvg[width=\textwidth]{../firmware/eppenwolf/runs/sic_susceptor/sic_9_1}
  	\caption{}
@@
 \begin{figure}[H]
-	\includesvg[width=\textwidth]{sic_9_2}
+	\includesvg[width=\textwidth]{../firmware/eppenwolf/runs/sic_susceptor/sic_9_2}
  	\caption{}
@@
 
-The raw voltage plots do not suggest that this is the case; but it is nonetheless concerning.
+\strike The raw voltage plots do not suggest that this is the case; but it is nonetheless concerning.
 

### 2020-11-21 documents/charge.tex
more charge section words

@@
 
+Liu et al mention that "Counterions
+dissolved in solution will thus be adsorbed on the surface of
+a protein and form an electric double layer."
+
+The mechanism given is that ions from solution counteract the protein charges to form an "electric double layer". In any case, the best representation is two concentric spheres with a net charge each.
+
 Is such a charge plausible?
@@
 As might be expected, the electrostatic properties of the virus differ from that of host cells, both on the sub-protein level\cite{Icosahedral2019} \footnotemark \ and in the lipid bilayer \cite{Lipid2015} \footnotemark.
-The mechanism given is that ions from solution counteract the protein charges to form an "electric double layer".
-In any case, the best representation is two concentric spheres with a net charge each.
 
@@
 
+\footnote{Influenza also has several other fascinating electrostatic properties. First, the net charge }
+
 \begin{autem}
@@
 
-Protein net charges extracted from primary protein sequences compiled by the proteome-pI database \cite{ProteomepI2017} and UniProt using localCIDER \cite{CIDER2017}.
+On the largest scale, at a pH of 7, the net charges of the 11 proteins coded for by the Influenza A genome only contribute
+
+Protein net charges extracted from protein primary structure sequences\footnotemark compiled by the proteome-pI database \cite{ProteomepI2017} and UniProt\footnotemark using localCIDER \cite{CIDER2017}.
 See \ghfile{biology/data/net_charge.py} and structure.csv.
@@
 Given the size of most proteins, however, this doesn't seem like a likely effect.
+
+\footnotetext{
+	It should be noted that these are the simplest primary structure charges.
+The charge in practice is determined by the secondary structure and the bonding to adjacent structures.
+More precise charges appear to be somewhat inconsistent.
+[] Find that the isoelectric point of the M protein charge is so low that it runs off the end of their 2D electrophoresis gel.
+However, the predicted value by [] is about 3.
+	This is not of much importance for here, but may be important when setting up MD simulations.
+}
+
+\footnotetext{
+
+Because CryoEM uses charged particles, it is possible to extract the actual charge distribution of a structure directly from an un-fit \cite{Identification2018}.
+
+}
 
@@
 
-On the largest scale, at a pH of 7, the net charges of the 11 proteins coded for by the Influenza A genome only contribute
-
 Adair's \cite{Vibrational2002}, in the section {\it \bf Coherent Processes}.
@@
 
-In my field, I am used to being able to make a definite mechanistic claim.
-Such and such a gamma ray will not break the bond in so and so; the energy is too low.
-However, we might not be able to expect such a clear answer from biology; how many treatments do we know of where the interaction with every structure in the body is known?
-In some cases, all we appear to be able to say is that we've tested it in a convincingly large number of ways and just don't see it.
-
-That seems defeatist, but it perhaps should be something we can prepare for.
-
-\cite{Identification2018}
-
 \section{Hello World}

### 2020-11-22 documents/background.tex
osmotically-stressed phage doesn't do it either

@@
+%!TeX root = background
+\documentclass[paper.tex]{subfiles}
+\begin{document}
+
 We have cycled between condemning as pathological science, and lauding it as the cure. Barring
+
+we appear to have lost confidence in the concept of measurement itself.
+
+the only analagous non-thermal mechansism we are aware of is electroporation; and that requires the diffusion of ionized sodium and potassium charge carriers through the membrane, which would seem to necessarily require a non-
+
+Laser
+
+A poignant summary of the consensus is found in \cite{IEEE2006}, Annex B, "Identification of levels of RF exposure responsible for adverse effects: summary of the literature".
+
+\begin{quote}
+	Further examination of the RF literature reveals no reproducible low level (non-thermal) effect that would
+	occur even under extreme environmental exposures. The scientific consensus is that there are no accepted
+	theoretical mechanisms that would suggest the existence of such effects. This consensus further supports the
+	analysis presented in this section, i.e., that harmful effects are and will be due to excessive absorption of
+	energy, resulting in heating that can result in a detrimentally elevated temperature.
+
+	The accepted mechanism is RF energy absorbed by the biological system through interaction with polar molecules (dielectric relaxation) or interactions with ions (ohmic loss) is rapidly dispersed to all modes of the system leading to an average energy rise or temperature elevation.
+
+	Since publication of ANSI C95.1-1982 [B6], significant advances have been made in our knowledge of the biological effects of exposure to RF energy.
+This increased knowledge strengthens the basis for and confidence in the statement that the MPEs and BRs in this	standard are protective against established adverse health effects with a large margin of safety.
+\end{quote}
+
+and,
+
+\begin{quote}
+	...the two major groups that develop RF safety standards and
+	guidelines (ICES and ICNIRP) agree that thermal effects continue to be the appropriate basis for protection
+	against RF exposure at frequencies above 100 kHz.
+\end{quote}
 
@@
 This means that the technique is {\it selective}.
+
+is is apparently easy to draw the wrong conculsion from a funnel plot, however. Here's one example of a flawed analysis: http://ies.fsv.cuni.cz/sci/publication/show/id/5277/lang/cs
+
+Thanks to James Picone https://skeptics.stackexchange.com/a/49751/ for the analysis.
+
+"The funnels are heavily asymmetrical: the left-hand side of the funnels is almost completely missing, hence we have good reason to believe that publication selection bias is strong in this literature." -
+
+\subsection{Artifacts in past absorption spectroscopy experiments}
+
+Edwards et al in 1984 and 1985 measured the reflection from an open-ended coaxial line dipped in DNA solution and found that DNA appeared to have a resonance-like peak.
+
+Such an effect is so unexpected - Bigio et  aldescribe it as “astonishing”.
+Edwards hypothesized that the outer hydration layers could have a sort of elastic, non-viscous isolating effect.
+This result seems to have triggered a large amount of work to model this interaction, and various other interactions, in an attempt to explain the observed resonance.
+
+Footnote [At first blush, such an explanation does not seem unreasonable.
+In the case of the virus, for instance, the expected amplitude of oscillation for which this mechanism applies is on the order of one water molecule (~0.1 nm).
+
+Treating the interaction between the first few solvent layers surrounding some biological structure is indeed quite difficult; we encountered this in trying to setup MD This can be seen in [MD paper], so it is reasonable that continuum-like damping assumptions might break down.
+
+In the case of a uniform rotating sphere, for instance, the [Einstein - ?] viscous drag force diverges from the continuum hypothesis toward zero.]
+
+This really shouldn’t be treated classically, either - Frolich
+
+Unfortunately for these hypotheses, Foster 1986, replicating Edwards’ coaxial line method with a more rigorous error analysis on plus an equally rigorous transmission-line absorption, and Bigio in 1993, an ingenious thermo-optical technique, quite definitively demonstrate - to absurd precision -  that the previous results were a characteristic artifact of coaxial-line spectrometry, and that DNA does not have any resonance mode at any microwave frequency.
+
+In Bigio’s words “Extreme care”. Because it involves a differential measurement of two samples.
+
+Hagmann and Gandhi \cite{Substitution1982}
+
+For a 0.5% tolerance in the frequency of a dielectric resonator (which), it must be machined to an accuracy of less than 0.05 mm.
+
+https://exxelia.com/uploads/PDF/e6000-v1.pdf
+
+crude, amateurish equipment, by making completely justifiable changes in calibration and post-processing correction for thermal drift, normalization, etc, we could produce a resonance mode at many frequencies.
+almost any frequency we liked.
+We were able to produce many candidate peaks even in pure water.
+
+autem We have not yet examined the details of the hydration-layer theory.
+
+Liu and Yang use a coplanar waveguide, and offer hydration layers along the lines of Edwards as a theoretical basis.
+
+However, as Foster et al demonstrated, there is nothing necessarily wrong with VNA-based dielectric spectrometry, if it is well conducted.
+The Liu and Yang group seem very competent experimenters, and the experiments are very well conducted; but history would seem to suggest that we take some degree of caution.
+
+\subsection{Thermal controls}
+
+In inevitable temperature rise as a confounding factor.
+Power dissipation necessarily produces a  As anyone who has scalded their mouths on microwaved dinner may know, microwave irradiation can produce unintuitive temperature gradients, with local hot-spots that can be difficult to measure directly.
+
+Microwave engineering is, itself  difficult. What type of attenuator you use?
+
+Publication bias in the positive direction.
+A p=0.001.
+Something along an anthropic principle.
+In effect, the literature selects for causes of a false positive that would be expected to be an extremely improbable set of circumstances;
+
+T4 capsid withstands a pressure differential of more than 30 atmospheres, crystallizing the genome packed within.
+
+\cite{Osmotic2003}
+
+\end{document}

### 2020-11-22 documents/detection.tex
osmotically-stressed phage doesn't do it either

%!TeX root = background
\documentclass[paper.tex]{subfiles}
\begin{document}

It should be noted that

- Detect the growth of the host bacteria, and measure effects of the phage on that growth

- Plaque plating

Contamination - in both directions: if you don’t wash your hands properly before working, you might end up with a thick soup of some truly horrific bacteria.

Plates are super sensitive, but in general I didn’t have huge issues with contamination; even my bad aseptic technique was fine - perhaps 1 contaminant region per plate.

- Detect the lysis of bacteria, the release of intracellular material

beta-galactosidase

A fingerprint, for instance, has only about 0.2 ng of DNA (Subhani), so contamination is not a huge issue.

Detect the lysis of the virus, and the release of intra-viral material

 It’s probably in principle possible to synthesize them yourself, but it’s totally impractical. You will probably need a corporate address HS codes.

T4 has a comparatively huge genome, which makes this easier.

Directly detect the virus itself

PEG apparently concentrates to 10^12 or 13 no matter what the starting concentration is (huh?), very convenient.

Concentrated can be put into the microgram range of many standard protein assays like BCA, but that requires propagation and PEG precipitation, plus many such assays pose disposal hazards and stain labware.

### 2020-11-22 documents/paper.tex
Wording
osmotically-stressed phage doesn't do it either

@@
 \clearpage
-
-A poignant summary of the consensus is found in \cite{IEEE2006}, Annex B, "Identification of levels of RF exposure responsible for adverse effects: summary of the literature".
-
-\begin{quote}
-%%%%%%%%%%%
-Further examination of the RF literature reveals no reproducible low level (non-thermal) effect that would
-occur even under extreme environmental exposures. The scientific consensus is that there are no accepted
-theoretical mechanisms that would suggest the existence of such effects. This consensus further supports the
-analysis presented in this section, i.e., that harmful effects are and will be due to excessive absorption of
-energy, resulting in heating that can result in a detrimentally elevated temperature. The accepted mechanism
-is RF energy absorbed by the biological system through interaction with polar molecules (dielectric relaxation) or interactions with ions (ohmic loss) is rapidly dispersed to all modes of the system leading to an
-average energy rise or temperature elevation. Since publication of ANSI C95.1-1982 [B6], significant
-advances have been made in our knowledge of the biological effects of exposure to RF energy. This
-increased knowledge strengthens the basis for and confidence in the statement that the MPEs and BRs in this
-standard are protective against established adverse health effects with a large margin of safety.
-
-\end{quote}
-
-and,
-
-\begin{quote}
-	 ...the two major groups that develop RF safety standards and
-	guidelines (ICES and ICNIRP) agree that thermal effects continue to be the appropriate basis for protection
-	against RF exposure at frequencies above 100 kHz.
-\end{quote}
 
@@
 \clearpage
-\paragraph{}
+
+%\paragraph{}
 

### 2020-11-22 documents/application.tex
writing!

@@
 
-SARS is found widely distributed throughout many of the most favoured organs \cite{Organ2004}, shielded by an average of 4 cm of chest wall [Schroeder 2013]; so safe external treatment of the body is unlikely.
+SARS is found widely distributed throughout many of the most favoured organs \cite{Organ2004}, shielded by an average of 4 cm of chest wall [Schroeder 2013].
 
@@
 Strictly speaking, penetration depth refers to the depth at which the power is reduced by 1/$e$; skin depth, where the electric field is 1/$e$.
-The penetration depth is simply half the skin depth.\cite{Penetration2019a} If we refer to penetration depth without making this explicit, we are referring to the electric field penetration depth.}
+The penetration depth is simply half the skin depth.\cite{Penetration2019a} If we refer to penetration depth without making this distinction explicit, we are referring to the electric field penetration depth.}
 
-Conduction effects. Because the transmission line voltage only goes as the to the square root of the input power
+Conduction effects. Because the transmission line voltage only goes as the square root of the input power
 
@@
 It's useful to note, however, that the total energy dissipated in each pulse is .
-An oft-cited figure for the energy in a whisper is 10 mJ[wolframalpha]; while no clinical data are available, whispering at someone is rarely considered calamitous\citationneeded!
+An oft-cited figure for the energy in a whisper is 10 mJ; while no clinical data are available, whispering at someone is rarely considered calamitous\citationneeded!
 

### 2020-11-22 documents/background.tex
writing!

@@
 
-Previous works (Liu et al, ) appear to demonstrate that several species of viruses exhibit an anomalous dielectric relaxation time of $> 75 \text{ ps}$, as opposed to $< 20 \text{ ps}$ \footnotemark measured in the structures of human tissue.\\
+One of the assumptions that underpin
+
+Previous works (Liu et al, ) appear to demonstrate that several species of viruses exhibit an anomalous dielectric relaxation time of $> 75 \text{ ps}$, as opposed to $<< 20 \text{ ps}$ \footnotemark measured in the structures of human tissue.\\
 
@@
 
-is is apparently easy to draw the wrong conculsion from a funnel plot, however. Here's one example of a flawed analysis: http://ies.fsv.cuni.cz/sci/publication/show/id/5277/lang/cs
-
-Thanks to James Picone https://skeptics.stackexchange.com/a/49751/ for the analysis.
-
-"The funnels are heavily asymmetrical: the left-hand side of the funnels is almost completely missing, hence we have good reason to believe that publication selection bias is strong in this literature." -
-
-\subsection{Artifacts in past absorption spectroscopy experiments}
+\subsection{Artifacts in past absorption spectroscopy experiments, and the subsequent development of non-classical damping hypotheses}
 
@@
 
-Such an effect is so unexpected - Bigio et  aldescribe it as “astonishing”.
+Such an effect is so unexpected - Bigio et al describe it as “astonishing”.
 Edwards hypothesized that the outer hydration layers could have a sort of elastic, non-viscous isolating effect.
@@
 
-Unfortunately for these hypotheses, Foster 1986, replicating Edwards’ coaxial line method with a more rigorous error analysis on plus an equally rigorous transmission-line absorption, and Bigio in 1993, an ingenious thermo-optical technique, quite definitively demonstrate - to absurd precision -  that the previous results were a characteristic artifact of coaxial-line spectrometry, and that DNA does not have any resonance mode at any microwave frequency.
+\lettrine{U}nfortunately for these hypotheses, Foster 1986, replicating Edwards’ coaxial line method with a more rigorous error analysis on plus an equally rigorous transmission-line absorption, and Bigio in 1993, an ingenious thermo-optical technique, quite definitively demonstrate - to absurd precision -  that the previous results were a characteristic artifact of coaxial-line spectrometry, and that DNA does not have any resonance mode at any microwave frequency.
 
@@
 
+\subsection{Meta issues with the field}
+
+\footnotetext{
+It is apparently easy to draw the wrong conculsion from a funnel plot, however. Here's one example of a flawed analysis: http://ies.fsv.cuni.cz/sci/publication/show/id/5277/lang/cs
+
+Thanks to James Picone https://skeptics.stackexchange.com/a/49751/ for the analysis.
+}
+
 Publication bias in the positive direction.
@@
 In effect, the literature selects for causes of a false positive that would be expected to be an extremely improbable set of circumstances;
+
+anthropic principle
+
+\subsection{Raman spectroscopy}
+
+Very recently, Burkhartsmeyer \cite{Optical2020} have published data replicating the findings using a single-particle Raman spectroscopy technique.
+We have not examined these claims in detail, but they are good evidence.
+
+Non-photothermal optical Raman methods can also apparently synthesize artifacts - see unpublished, personal communication with Taylor \cite{mechanisms1981}.
 

### 2020-11-22 documents/detection.tex
writing!

@@
-%!TeX root = background
+%!TeX root = detection
 \documentclass[paper.tex]{subfiles}
@@
 
+\begin{autem}
+	I hasten to note that quantifying phage titer is a completely solved problem, and is a procedure often done in kindergarten labs.
+The amount of time and effort we spent here was completely unjustifiable.
+It was driven by an acute lack of competence, equipment, and the small volume constraints of our original poorly designed microwave setup.
+\end{autem}
+
+\begin{figure}[H]
+	\captionsetup{singlelinecheck = false, justification=justified}
+	\centering
+	\includegraphics[width=\textwidth]{chunk_4}
+	\caption{
+		\light{
+			\\
+			We've got a thing\\
+			that's called\\
+			{\it Radar Love}\\}
+		We've got a wave\\
+		in the air}
+\end{figure}
+
+Essentially the only method of determining the activity of phage is to have it infect a suitable host.
+
+Typically, this is done either in a large tube or a flat-sided optical cuvette.
+
+Because the variation in the optical density is quite small, this poses some rather.
+
+A lot of the basic facts of phage were determined in the 1930s;
+
+A small vial of liquid has a much larger surface area relative to its thermal mass.
+sis removed, the temperature drops very rapidly; if the temperature drops outside the "physiological range" of around 33-40 C, growth is stunted \cite{effect2003}.
+\cite{growth1946}.
+I'm not sure if this was the problem I encountered,
+
+As a faculative aerobe, E.coli requires a concentration of oxygen to be present in the mixture for speedy replication \cite{Effect1965}; and this supply must also be kept sterile.
+One method to ensure this is by using a bubbler aerator; Carolina recommends an aquarium pump with cotton-ball filters.
+
+Another method, often used in microfluidics\cite{Microfluidic}, is that of \cite{method1951}; the Manganese dioxide catalyzed decomposition of hydrogen peroxide.
+$MnO_2$ is readily obtained from alkaline batteries; and in this case no sterility issues are presented.
+However, it is not obvious how antimicrobial $H_2O_2$ vapor can be prevented from contacting the culture.
+
+Bottles of zero air may be more effective.
+
+In commercial fluid transfer machines, this is often resolved by HEPA filtering the input to an enclosing cabinet.
+
+Shaking incubators, where the flasks are
+
+Ensuring that a great deal of headspace was present in a sealed tube (that is, culturing 2.5 mL in a 15 mL falcon tube) was sufficient for brief, low-density.
+
+As the size of the well decreases, the Reynolds number also decreases \footnote{In fact, in the case of a circular well, it's not obvious that this is the case - the cross section decreases faster than the characteristic length}, and turbulent flow is greatly hampered.
+
+Even slight rotation of the tube, such that the graduations
+
+"Chromogenic" substances \cite{Fluorogenic1991}, or the degradation of various dyes like Methylene Blue; tetrazolium dye methods;
+
+Using 2.5 mm diameter x 3 mm high wells cut in polycarbonate and sealed with clear packing tape. However, the presence of small bubbles in the headspace of the wells prevented a consistent reading.
+
+We tried simply adding 1 uL of culture to the microscope slide;
+
+The 8-bit resolution and dynamic range of most cameras did not seem sufficient to discern the turbidity; and masking and correcting for
+
+\cite{Vision2016} use an ingenious technique. A background with sharp light-to-dark edges is used. Slicing the image into chunks only slightly larger than the object,
+
+The 0.8 uL sample in each was not sufficient to produce a measurable change in turbidity in a 0.2 uL - or we were not experienced enough to perform the phage lysis protocol properly.
+
+However, we were not able to make smaller volumes of culture enter the log phase.
+
+Another very interesting technique is that of \cite{Study2003},
+
 It should be noted that
 
-- Detect the growth of the host bacteria, and measure effects of the phage on that growth
+\subsection{Detect the growth of the host, and measure effects of the virus on that growth}
 
-- Plaque plating
+\subsubsection{Plaque assay}
+
+The plaque assay for viruses has remained essentially unchanged since Delbruck's era.
+
+Advantages over broth methods are the longer infective period without agitation or
 
@@
 
-Plates are super sensitive, but in general I didn’t have huge issues with contamination; even my bad aseptic technique was fine - perhaps 1 contaminant region per plate.
+Despite poor aseptic technique, contamination was not a serious issue - perhaps 1 contaminant region per plate.
 
-- Detect the lysis of bacteria, the release of intracellular material
+Incubating the bacterial lawn for sufficient contrast to read the plaques imposes a ~1 to 3 day delay between test and results. Each test requires several dilution tubes
+
+\subsubsection{Broth assays}
+
+This, however, requires a microplate reader which can simultaneously agitate for sufficient oxygen, incubate, and
+
+Tetrazolium dyes are metabolized
+
+GFP
+
+\subsubsection{Detect the release of intracellular material due to the lysis of the host}
+
+One common target is the enzyme $\beta$-galactosidase. E. coli and other. Both  isopropyl $\beta$-D-thiogalactoside. Lactose itself is a reasonable substitute (Borralho \cite{Lactose2002}).
+
+Ijzerman
+
+X-gal \cite{Improved}
+
+I was introduced to this by Ijzerman \cite{liquid1993}, who recommend chlorophenol red $\beta$-D-galactopyranoside (CPRG) as the chromogen for a high sensitivity.
+CPRG is very hard to obtain except through Sigma.
 
@@
 
-A fingerprint, for instance, has only about 0.2 ng of DNA (Subhani), so contamination is not a huge issue.
+\includegraphics[width=\textwidth]{x_gal.jpg}
 
-Detect the lysis of the virus, and the release of intra-viral material
+\includegraphics[width=\textwidth]{x_gal_and_flourescence/CIMG6810.JPG}
 
@@
 
-Directly detect the virus itself
+\subsubsection{Detect the lysis of the virus, and the release of intra-viral material}
 
-PEG apparently concentrates to 10^12 or 13 no matter what the starting concentration is (huh?), very convenient.
+A fingerprint, for instance, has only about 0.2 ng of DNA (Subhani), so contamination is not a huge issue.
+
+\subsubsection{Directly detect the virus itself}
+
+Phages release several small compounds like putrescine and spermadine when broken (Minagawa\cite{characteristics1961}).
+These can be indicated colorimetrically at ppm scales with ninhydrin, or at nanogram scales via fluorescamine.
+
+Otherwise, GFP-flouresecent strains of E. coli, or phage which has been labelled with a
+
+PEG apparently concentrates to $10^{12}$ or 13 no matter what the starting concentration is (huh?), very convenient.
 
 Concentrated can be put into the microgram range of many standard protein assays like BCA, but that requires propagation and PEG precipitation, plus many such assays pose disposal hazards and stain labware.
+
+\end{document}

### 2020-11-22 documents/paper.tex
writing!

@@
 \begin{multicols}{1}
-
-\paragraph{{\Large the gist}}\
-
-The chain of literature 
-%
-\cite{Longrange1968} \textrightarrow \ \cite{Biological1980} \textrightarrow \ \cite{Microwave2009} \textrightarrow \ (\cite{focusing2014} $\parallel$ \cite{Efficient2015} $\parallel$ \cite{Resonant2017})\footnote{We have not conducted a thorough review; many more papers are probably involved.} apparently culminates in the flagship work we focus on in this paper,
-
-{\it Efficient Structure Resonance Energy Transfer from Microwaves to Confined Acoustic Vibrations in Viruses} \cite{Efficient2015}.
-%
 

### 2020-11-22 documents/pseudo_soliton.tex
writing!

@@
 
-Precursor waves do not appear to be explicitly mentioned in C95- but are implicitly governed by the Fourier-spectrum clauses.
+Uzunoglu \cite{Theoretical2020} cite a very handy way to circumvent this lossy-flesh problem: the Brilloin and Somerfield precursors.
+
+At 9 GHz, assuming that a torso is about 10 penetration depths in radius and the brilluoin train drives the virus with an equally, implementing this would decrease the surface field required for complete eradication of the virus from the body to a perfectly practicable 1 kV/m, rather than an air-ionizing 6.6 MV/m ($\frac{1}{\sqrt{10}}=0.316$ versus $e^{-10}=4.5e-5$).
+
+Precursor waves do not appear to be explicitly mentioned in IEEE standards, but are implicitly governed by the Fourier-spectrum clauses and more recent FCC ultrawideband regulations.
 Ultra-short wavepackets of a similar nature are widely used in MRI systems with a repetition rate up to 300 MHz.
@@
 
-At 9 GHz, assuming that a torso is about 10 penetration depths in radius, implementing this would decrease the required surface field for complete eradication of the virus from the body to only 1 kV/m, rather than 6.6 MV/m ($1/\sqrt{10}=0.316$ rather than $e^{-10}=4.5e-5$).
+\footnotetext{
+	Sincere thanks go to the legendary Kurt Oughstun for taking the time to thoroughly answer some of our questions.
+}
 
+\begin{sidenote}
 There are some extremely tricky subtleties in the simulation.
@@
 Frankly, I can't make heads or tails of any of these, not understanding the asymptotic method at all.
+\end{sidenote}
 

### 2020-11-22 documents/supplemental.tex
Wording
writing!

@@
 \rule{\linewidth}{0.2pt}
-
-\PRLsep{{\itshape Phage lysis sensing }}
-
-Phage releases several amino acids such as putrescine and spermadine when broken. These can be indicated at ppm scales with ninhydrin, or at nanogram scales via fluorescamine.
-
-Otherwise, GFP-flouresecent strains of E. coli, or phage which has been labelled with a
-
-Essentially the only method of determining the activity of phage is to have it infect a suitable host.
-
-Typically, this is done either in a large tube or a flat-sided optical cuvette.
-
-Because the variation in the optical density is quite small, this poses some rather.
-
-A lot of the basic facts of phage were determined in the 1930s;
-
-A small vial of liquid has a much larger surface area relative to its thermal mass.
-sis removed, the temperature drops very rapidly; if the temperature drops outside the "physiological range" of around 33-40 C, growth is stunted \cite{effect2003}.
-\cite{growth1946}.
-I'm not sure if this was the problem I encountered,
-
-As a faculative aerobe, E.coli requires a concentration of oxygen to be present in the mixture for speedy replication \cite{Effect1965}; and this supply must also be kept sterile.
-One method to ensure this is by using a bubbler aerator; Carolina recommends an aquarium pump with cotton-ball filters.
-
-Another method, often used in microfluidics\cite{Microfluidic}, is that of \cite{method1951}; the Manganese dioxide catalyzed decomposition of hydrogen peroxide.
-$MnO_2$ is readily obtained from alkaline batteries; and in this case no sterility issues are presented.
-However, it is not obvious how antimicrobial $H_2O_2$ vapor can be prevented from contacting the culture.
-
-Bottles of zero air may be more effective.
-
-In commercial fluid transfer machines, this is often resolved by HEPA filtering the input to an enclosing cabinet.
-
-Shaking incubators, where the flasks are
-
-Ensuring that a great deal of headspace was present in a sealed tube (that is, culturing 2.5 mL in a 15 mL falcon tube) was sufficient for brief, low-density.
-
-As the size of the well decreases, the Reynolds number also decreases \footnote{In fact, in the case of a circular well, it's not obvious that this is the case - the cross section decreases faster than the characteristic length}, and turbulent flow is greatly hampered.
-
-Even slight rotation of the tube, such that the graduations
-
-"Chromogenic" substances \cite{Fluorogenic1991}, or the degradation of various dyes like Methylene Blue; tetrazolium dye methods;
-
-Using 2.5 mm diameter x 3 mm high wells cut in polycarbonate and sealed with clear packing tape. However, the presence of small bubbles in the headspace of the wells prevented a consistent reading.
-
-We tried simply adding 1 uL of culture to the microscope slide;
-
-The 8-bit resolution and dynamic range of most cameras did not seem sufficient to discern the turbidity; and masking and correcting for
-
-\cite{Vision2016} use an ingenious technique. A background with sharp light-to-dark edges is used. Slicing the image into chunks only slightly larger than the object,
-
-The 0.8 uL sample in each was not sufficient to produce a measurable change in turbidity in a 0.2 uL - or we were not experienced enough to perform the phage lysis protocol properly.
-
-However, we were not able to make smaller volumes of culture enter the log phase.
-
-Another very interesting technique is that of \cite{Study2003},
 

### 2020-11-24 documents/EPA_paper.tex
Writing

%!TeX root = EPA_paper
\documentclass[paper.tex]{subfiles}
\begin{document}

There is an interesting citation in the Gray literature \cite{Indexa}, particularly because it seems to have progressed to the clinic:

FELLOWES, O. N. GRAY, O. S. SANDERS, M. SELECTIVE EFFECT OF EM ENERGY ON VIRUSES 
NEW YORK ACADEMY OF SCIENCES SYMPOSIUM 'EFFECT OF CONTROLLED EM ENERGY ON BIOLOGICAL SYSTEMS', 4 NOV. 1970

SCHLUTZ, C. A. GRAY, O. S. SANDERS, M. FELLOWES, O. N. 
THE EM CONTROLLED EFFECT OF ENERGY ON VIRUSES IN HUMAN BLOOD NEW YORK ACADEMY OF SCIENCES SYMPOSIUM 'EFFECT OF CONTROLLED EM ENERGY ON BIOLOGICAL SYSTEMS', 4 NOV. 1970

I can find no reference to such a conference in Annals of the NYAS, but it may be recorded in Transactions. It is a shame to see good work fade into the mist of time, especially since research in this field attained an acceptable level of quality even in the 1940s. O. N. Fellowes was of the Plum Island Animal Disease Laboratory. Oscar S. Gray was of Gray Industries Inc, Florida.

From Mr. Gray's U.S. patents, however, we are not given any reason to believe that this effect was non-thermal in nature.

\end{document}

### 2020-11-24 documents/background.tex
Writing

@@
 
+\begin{autem}
+
+{\Large {This has \textbf{nothing to do} with 5G communications. }}\\
+
+I am comfortable making such a definitive statement.
+
+The power levels required to even begin to observe this inactivation effect in practice are so high that, if conditions are not specifically tailored for clinical use, extensive burns will result within seconds.
+Even in this case, the effect is to eviscerate the virus, not to aid its spread.
+
+Moreover, these frequency bands have been in almost continuous use not long after Jagadish Chandra Bose 1894; the world has been bathed in high-power 10 GHz pulses at least since the commissioning of the first centimeter-wave weather radars in 1959.
+
+Countless far more prosaic explanations exist in the modern world, such as air travel.
+
+If you have any concerns regarding this statement, please contact me. I would be happy to discuss this.
+
+\end{autem}
+
 We have cycled between condemning as pathological science, and lauding it as the cure. Barring
+
+In fact, it seems like at some point in the 1970, a selective effect on viruses was discovered and progressed as far as a clinical trial.
+The only record we have of this trial are two citations regarding a conference paper submitted to a New York Academy of Sciences symposium in a 1981 index.
+This symposium is not listed in Transactions of.
+The National Institutes of Health may have a copy.
 

### 2020-11-24 documents/detection.tex
Writing

@@
 \begin{autem}
-	I hasten to note that quantifying phage titer is a completely solved problem, and is a procedure often done in kindergarten labs.
+	I hasten to note that quantifying viral titer is a completely solved problem, and is a procedure often done in kindergarten labs.
 The amount of time and effort we spent here was completely unjustifiable.
@@
 One method to ensure this is by using a bubbler aerator; Carolina recommends an aquarium pump with cotton-ball filters.
+Probably Syringe filters are a good alternative.
 

### 2020-11-24 documents/lessons_learned.tex
nah.
Writing

@@
 \paragraph{Lessons Learned} \
+
+\rule{\linewidth}{0.2pt}
+
+Indexes of papers compiled by government agencies, and gray literature in general, appear to be very useful.
+
+\rule{\linewidth}{0.2pt}
+
+Rigorous literature reviews are very important. de Seze has a good example: search terms are specified. If we had come across the paper by Bigior earlier, we may have
+
+\rule{\linewidth}{0.2pt}
+
+Papers only carry the scientific heritage that their authors saw fit to include in the references section.
 

### 2020-11-24 documents/pseudo_soliton.tex
Writing

@@
 
+The prototypical Vircator (not varactor) pinched electron beam tubes
+
+step recovery diodes
+
 \begin{sidenote}
@@
 \end{sidenote}
-
-As saliently noted by Adair:
-
-\begin{quote}
-	“the energy of the pulse at a depth of 1 cm is about 0.8% of the initial energy;
-	the maximum electric field strength, E is reduced by a factor of about 12, and the maximum rate-ofchange of the field, dE/dt, is reduced by a factor of 20.
-Every characteristic of the pulse at depth is
-	contained, albeit attenuated, in the initial pulse. Consequently, we do not find it credible that the
-	strongly attenuated pulse – albeit with a different shape – can induce biological effects beyond that of
-	the initial pulse.”
-\end{quote}
+\begin{tab}
+	content
+\end{tab}
 

### 2020-11-24 electronics/propagation/propagation_lib.py

@@ -1,4 +1,4 @@
-from math import sin, cos, pi, sqrt, e, log, isclose, exp
+from math import atan,sin, cos, pi, sqrt, e, log, isclose, exp
 from scipy.optimize import curve_fit
 import numpy as np
 import matplotlib.pyplot as plt
@@ -8,6 +8,9 @@ import scipy.constants
 from fdtd_PCB_extensions.tissue import cole_cole_4, complex_permittivity_to_er_and_sigma, electric_field_penetration_depth, get_tissue_cole_cole_coefficients, tissue_properties
 from mpl_toolkits.mplot3d import Axes3D
 
+def average(arr, n):
+    end =  n * int(len(arr)/n)
+    return np.mean(arr[:end].reshape(-1, n), 1)
 
 import unittest
 
@@ -17,45 +20,36 @@ class propagator:
         pass
 
 
-    def fourier_transform(self, input_data, sampling_frequency, frequency_scale_factor, threshold_amplitude = 1e-4):
+    def fourier_transform(self, input_data, sampling_frequency, frequency_scale_factor):
         self.input_fft = np.fft.rfft(input_data)
 
         self.a_n_coefficients = self.input_fft.real
         self.b_n_coefficients = self.input_fft.imag
 
-        # duration =
-        # self.base_period = sampling_frequency/len(input_data)
-
         frequency_step = (sampling_frequency * frequency_scale_factor)/len(self.a_n_coefficients)
+        
         self.times = np.linspace(0, len(self.a_n_coefficients)*(1.0/(sampling_frequency*frequency_scale_factor)), len(self.a_n_coefficients))
         self.mode_frequencies = np.linspace(frequency_step, (len(self.a_n_coefficients)/2)*frequency_step, len(self.a_n_coefficients))
 
-        print(len(self.mode_frequencies))
-        magnitudes = np.sqrt(self.a_n_coefficients**2.0 + self.b_n_coefficients**2.0)
-        filted_indices = magnitudes > threshold_amplitude*np.max(magnitudes)
-        self.mode_frequencies = self.mode_frequencies[filted_indices]
-        self.a_n_coefficients = self.a_n_coefficients[filted_indices]
-        self.b_n_coefficients = self.b_n_coefficients[filted_indices]
-        print(len(self.mode_frequencies))
-        # return fft, self.a_n_coefficients, self.b_n_coefficients, base_period
+
+        
+
+    def attenuate(self,distance):
[…]

### 2020-11-25 documents/background.tex
words

@@
 
-{\Large {This has \textbf{nothing to do} with 5G communications. }}\\
+{\Large {This has \textbf{nothing to do} with 5G communications.}}\\
 
@@
 
-In fact, it seems like at some point in the 1970, a selective effect on viruses was discovered and progressed as far as a clinical trial.
-The only record we have of this trial are two citations regarding a conference paper submitted to a New York Academy of Sciences symposium in a 1981 index.
-This symposium is not listed in Transactions of.
-The National Institutes of Health may have a copy.
-
-we appear to have lost confidence in the concept of measurement itself.
+we appear to have lost confidence in the concept of accurate measurement itself.
 
@@
 Laser
+
+So far as we are aware, there are no fundamental physical obstacles to non-thermal effects in biological systems.
+As an example, electroporation is a well-established - now a common laboratory procedure, in which an enormous electric field causes ions in solution to migrate across the membrane,
+
+However, there equally appear to be no fundamental reasons why some small-molecule drug could not bind to the wrong receptor, why
 
@@
 
+A previous report of microwave resonance, Grundler \cite{Sharp1983}, use a calorimeter, a stream of cooling water controlled to within 0.1 C, an interferometric thermometer, and can state definitively that at no point does the temperature inhomogeneity exceed 0.02 C.
+
+The experiments of the Sun group
+
+An electric field necessarily dissipates energy in the surrounding solvent, and
+
 In inevitable temperature rise as a confounding factor.
-Power dissipation necessarily produces a  As anyone who has scalded their mouths on microwaved dinner may know, microwave irradiation can produce unintuitive temperature gradients, with local hot-spots that can be difficult to measure directly.
+
+As any researchers who have scalded their mouths on microwaved dinner may know, microwave irradiation can produce unintuitive temperature gradients, with local hot-spots that can be difficult to measure directly.
+
+Kozempel \cite{Preliminary1997} and \cite{Inactivationa}.
+They take great pains to map the temperature profile using a fiber-optic thermometer; use thermographic indicators; and find substantial, almost complete inactivation of {\it Pediococcus sp.} with a measured discharge temperature of only 40 C.
+
+This is a fascinating result, and one which should be compared to the existing literature and very carefully replicated to isolate the mechanism.
+However, unless it is suggested that {\it Pediococcus sp.} also exhibits a confined microwave resonance of the same nature, it appears that periodic temperature measurements within the physiological range are not necessarily a sufficiently stringent control to definitively isolate resonant effects from other mechanisms.
+
+Conversely, if temperature control is not possible,
+
+In Gandhi \cite{Basic1983}, nichrome heaters and copper-constantan thermocouples are used to generate the same temperature-time profile in both the treatment and the control to within 0.02 C, finding no effect.
+
+Burton\cite{Effects1950} describe the use of thermochromic pigments to examine heating profiles. Using low-frequency exposure, they are able to produce localized regions in excess of 50 C.
 

### 2020-11-25 documents/viscosity.tex
words

%!TeX root = viscosity
\documentclass[paper.tex]{subfiles}
\begin{document}

\begin{autem}
	Burkheartsmeier and others have already computed this. We add this to satisfy our own curiosity, and because it is a central point and must be correct.
\end{autem}

We use Persson's description of purely classical Navier-Stokes drag \cite{nature1986} on a homogeneous sphere in a viscous liquid. The first breathing mode is used for a conservative estimate.

To compare with Yang's results, Influenza A. Density is equal to that of the surrounding solution: $\rho_{liquid} = \rho_{solid} = 1000 \text{kg/m}^3$. R = 50 nm. An approximate c=1000 m/s is used. Viscosity of $\mu=10e-3 Ns/m^2$ is used.

$$ b = \frac{4\mu}{R^2 \rho_{solid}} = \frac{4 \cdot 1\times 10^{-3}\  \text{N}\cdot \text{s} / \text{m}^2 }{(50 \text{nm})^2 1000 \text{kg /m}^2} = 1.6 \times 10^9\ \text{N}\cdot \text{s} /( \text{m}\cdot\text{kg})$$

Where $\mu$ is the viscosity of the fluid, R is the radius of the sphere, $\rho_{solid}$. \footnotemark

\footnotetext{I must remember to disambiguate denominators by adding brackets. Is $1/R^2\rho$ = $1/(R^2 \rho)$ or $(1/R^2)\cdot\rho$ ?}

$$m = \rho_{solid}  (4/3) \pi r^3 = 5.2 \times 10^{-19} \text{ kg} $$

(In the case of Influenza A, this yields 313 MDa, which is a 1/3 overestimate).

The exponential damping time constant (units 1 / s ) is then

$$\gamma = \frac{b}{2m} = $$

Finally,

$$ \omega_{res} = \sqrt{\frac{(\rho_{solid} / \rho_{liquid})c^2}{R^2}} $$

\end{document}

### 2020-11-25 firmware/eppenwolf/src/VCO_driver.cpp

@@ -321,7 +321,7 @@ void master_loop(){
 
     // bool treatment = Entropy.random(2);
     //REENABLE IN PROD
-    bool treatment = 0;
+    bool treatment = 1;
     debug_serial.println("Treatment:\u001b[8m ");
     debug_serial.println(treatment);
     debug_serial.println("\e[0m");

### 2020-11-25 documents/viscosity.tex
Huh, viscous damping works out

@@
 
+Let us use a first-order Fermi estimate of the drag force to see if speculative mechanisms are required.
+
 We use Persson's description of purely classical Navier-Stokes drag \cite{nature1986} on a homogeneous sphere in a viscous liquid. The first breathing mode is used for a conservative estimate.
@@
 R = 50 nm.
-An approximate c=1000 m/s is used.
 Viscosity of $\mu=10e-3 Ns/m^2$ is used.
 
-$$ b = \frac{4\mu}{R^2 \rho_{solid}} = \frac{4 \cdot 1\times 10^{-3}\  \text{N}\cdot \text{s} / \text{m}^2 }{(50 \text{nm})^2 1000 \text{kg /m}^2} = 1.6 \times 10^9\ \text{N}\cdot \text{s} /( \text{m}\cdot\text{kg})$$
+$$ \gamma = \frac{4\mu}{R^2 \rho_{solid}} = \frac{4 \cdot 1\times 10^{-3}\  \text{N}\cdot \text{s} / \text{m}^2 }{(50 \text{nm})^2 1000 \text{kg /m}^2} = 1.6 \times 10^9 \text{s}^{-1} = 1.6\ \text{GHz}$$
 
-Where $\mu$ is the viscosity of the fluid, R is the radius of the sphere, $\rho_{solid}$. \footnotemark
+Where $\mu$ is the viscosity of the fluid, R is the radius of the sphere, $\rho_{solid}$. \footnotemark \footnotemark
 
 \footnotetext{I must remember to disambiguate denominators by adding brackets. Is $1/R^2\rho$ = $1/(R^2 \rho)$ or $(1/R^2)\cdot\rho$ ?}
+
+\footnotetext{Persson seems to go against modern convention, using 1/s as the damping in the differential equation.}
 
@@
 
-$$\gamma = \frac{b}{2m} = $$
+Finally, where the densities of the two materials are equal (a reasonable approximation), An approximate c=1000 m/s is used.
 
-Finally,
+$$ \omega_{res} = c / R = 20 \text{GHz}$$
 
-$$ \omega_{res} = \sqrt{\frac{(\rho_{solid} / \rho_{liquid})c^2}{R^2}} $$
+This is about double that seen by Sun. Most critically, however,
+
+$$ Q = \omega_{res}/(2\gamma) = 6.25 $$
+
+Which is distinctly in the underdamped regime.
+
+Contrast this with Adair's arguments along the same lines reporting sub-picosecond relaxation times.
+
+However, if we apply the same arguments to microtubules \cite{Viscous2000}, omega_c = 80 GHz, and Q=11.2. Such an effect is so trivial that we find it hard to believe.
 

### 2020-11-25 documents/viscosity.tex
Microfluidic channel

@@
 
-Contrast this with Adair's arguments along the same lines reporting sub-picosecond relaxation times.
+Contrast this with Adair's arguments along similar lines, but reporting sub-picosecond relaxation times.
 
-However, if we apply the same arguments to microtubules \cite{Viscous2000}, omega_c = 80 GHz, and Q=11.2. Such an effect is so trivial that we find it hard to believe.
+However, if we apply the same arguments to microtubules \cite{Viscous2000}, omega_c = 80 GHz, and Q=11.2. The effects of these exposures should have been
 

### 2020-11-26 electronics/propagation/propagation_lib.py
NLTL doesn't seem to help.

@@ -27,12 +27,12 @@ class propagator:
         self.b_n_coefficients = self.input_fft.imag
 
         frequency_step = (sampling_frequency * frequency_scale_factor)/len(self.a_n_coefficients)
-        
+
         self.times = np.linspace(0, len(self.a_n_coefficients)*(1.0/(sampling_frequency*frequency_scale_factor)), len(self.a_n_coefficients))
         self.mode_frequencies = np.linspace(frequency_step, (len(self.a_n_coefficients)/2)*frequency_step, len(self.a_n_coefficients))
 
 
-        
+
 
     def attenuate(self,distance):
         attenuation = np.exp(-distance/self.E_penetration_depth)
@@ -85,99 +85,138 @@ class propagator:
 
     def analytic_oscillator_phase(self, beta, resonant_frequency):
 
-        return np.arctan((2.0 * beta * 2*pi*self.mode_frequencies) / 
+        return -1.0 * np.arctan((2.0 * beta * 2*pi*self.mode_frequencies) /
             ((2*pi*resonant_frequency)**2.0 - (2*pi*self.mode_frequencies)**2.0))
         #angular frequencies?
-        
+
         #mode_freq is not correct
 
     def analytic_oscillator_scaling(self, beta, resonant_frequency):
         p1 = ((2*pi*resonant_frequency)**2.0 - (2*pi*self.mode_frequencies)**2.0)**2.0
         p2 = (4.0 * (beta**2.0) * (2*pi*self.mode_frequencies)**2.0)
+
+        #numpy uses weird normalization
+        # undo_normalization = len(self.mode_frequencies ** 2.0)
+
         return 1/np.sqrt(p1+p2)
-        
-    
+
+    # def dU_dx(U, t, E_field, charge):
+    #     # Here U is a vector such that y=U[0] and z=U[1]. This function should return [y', z']
+    #     k = *8.9e9
+    #     return [U[1], -2*U[1] - 2*U[0] + E_field*charge]
+
+
+
 class test_fourier(unittest.TestCase):
 
-    def test_sine_fourier(self):
-
-        sampling_frequency = 1000000
-        input_frequency = 1000.0
-        frequency_scale_factor = 1.0e6
-        times = np.linspace(0, 1.0, sampling_frequency)
-        input_data = np.zeros_like(times, dtype=np.float32)
-        input_data = np.sin(2.0*pi*times*1000.0)
-
-        p = propagator()
[…]

### 2020-11-26 documents/detection.tex
Wooords

@@
 
+Biotium Gelgreen has a very specific advantage: to increase the safety of the dye, the flurophore is tied to some huge, unknown proprietary molecule, preventing it from diffusing through membranes or capsids.
+This has the side effect of making the fluorescence intensity strictly related to the quantity of genomic material dispersed in the solvent, rather than
+
 \end{document}

### 2020-11-27 documents/application.tex
Optimal control

@@
 Industry Canada limits on the instantaneous electric field anywhere inside the body are $1.35 \times 10^{-4}$ V/m $\times$ Hz (\cite{RSS1022015}, Table 4) - that is, $0.81 \times 10^6$ V/m @ 6 GHz to $1.2 \times 10^6$ V/m @ 9 GHz.
-It should be noted that more recent standards have abandoned instantaneous electric field limits, finding that they have little biological rationale (\cite{C95}, B.4.3, {\it Rationale for pulsed RF field limits}).\footnotemark
+It should be noted that more recent standards have abandoned instantaneous electric field limits altogether, asserting that they have little biological rationale (\cite{C95}, B.4.3, {\it Rationale for pulsed RF field limits}).\footnotemark
+
+In addition to these limits, the "microwave hearing threshold" - the pulse energy density threshold at which nerve stimulation begins to occur, should be respected.
+
+ It is difficult to intuit how 40,000 watts can possibly be safe.
+It's useful to note, however, that the total energy dissipated in each pulse is .
+An oft-cited figure for the energy in a whisper is 10 mJ; while no clinical data are available, whispering at someone is rarely considered calamitous\citationneeded!
+
+ Laser treatments can exceed hundreds of megawatts.
+
+ Thermoacoustic effects should also be considered.
 
@@
 Considering only the electric field skin depth\footnotemark\cite{Safety2001}\cite{Physical1982} of average lung tissue\cite{gabriel1996compilation}\cite{Dielectricb}\cite{Dielectric}\cite{Tissue2018} (which changes considerably based on inflation), at 8 GHz it appears to be possible to achieve the required field of 150 V/m at a very reasonable depth of 60 mm.
+
 We could not find any data on the distribution of gas exchange throughout the cross-section of the lung.
@@
 
-It is difficult to intuit how 40,000 watts can possibly be safe.
-It's useful to note, however, that the total energy dissipated in each pulse is .
-An oft-cited figure for the energy in a whisper is 10 mJ; while no clinical data are available, whispering at someone is rarely considered calamitous\citationneeded!
-
-Laser treatments can exceed hundreds of megawatts.
-
-Thermoacoustic effects should also be considered.
-
 \clearpage

### 2020-11-27 documents/brillouin_pulse_math.tex
Optimal control

%!TeX root = brillouin_pulse_math
\documentclass[paper.tex]{subfiles}
\begin{document}

%http://web.physics.ucsb.edu/~fratus/phys103/LN/DHM.pdf
% section on Greens functions
% and also 
% and
% https://www.int.washington.edu/users/dbkaplan/228_01/green.pdf

This problem is called "optimal control"?

\end{document}

### 2020-11-27 documents/detection.tex
Optimal control

--- 2020-11-24 documents/detection.tex
@@
 
+Biotium Gelgreen has a very specific advantage: to increase the safety of the dye, the flurophore is tied to some huge proprietary molecule, preventing it from diffusing through membranes or capsids.
+This has the side effect of making the fluorescence intensity strictly related to the quantity of genomic material dispersed in the solvent, rather than
+
 \end{document}

### 2020-11-29 documents/acknowledgement.tex
Fluor. working great
Wording
No analytic solution

@@
 
-Prof. Griffiths and Dr. Brovko at UGuelph, Dr. Anany at the GRDC for tips on the Beta-Glo assay
+Prof. Griffiths and Dr. Brovko at UGuelph, Dr. Anany at the GRDC for useful tips on the Beta-Glo assay.
 
@@
 
-Profs David and Taylor (among others) at YorkU for being super nice, and H.P. and ice9 for tolerating ramblings.
+Profs H. Kassiri, C. David and W. Taylor (among others) at YorkU for being super nice, and H.P. and ice9 for tolerating ramblings.
 
-Thanks to L.H. for wisdom regarding this project;
+Thanks to L.H. for wisdom regarding this project.
 
@@
 
-R.I.P. to Dr. Robert Adair, whose work features prominently here, who died Sep. 2020.
+R.I.P. to Dr. Robert Adair, whose work features prominently here, died Sep. 2020.
 
@@
 
-The authors reluctantly acknowledge the Computational Electromagnetics Group at The University of Texas at Austin for going through the trouble to develop the AustinMan and AustinWoman human body models and then making them unavailable at https://sites.utexas.edu/austinmanaustinwomanmodels/, and also not replying to email.
+The authors gratefully acknowledge the IT.IS foundation
 
-It's okay, I'm not bitter.
+and also compiling the tissue property databases.
 
@@
 
-The authors gratefully acknowledge the IT.IS foundation for the same, and also compiling the tissue property databases.
+Thanks to Biotium Inc for support on GelGreen.
 

### 2020-11-29 documents/application.tex
No analytic solution

@@
 
-SARS is found widely distributed throughout many of the most favoured organs \cite{Organ2004}, shielded by an average of 4 cm of chest wall [Schroeder 2013].
+Free-space "vaccination" of people or spaces is all well and good; but a treatment would seem to be superior.
+Far fewer installations would be required, cost would be of less object, and effectiveness would not depend on widespread public acceptance.
+Safety concerns due to continuous exposures would also be lessened.
 
-\cite{neuroinvasive2020} \cite{situ2020}
+And so, is it possible to non-invasively produce this effect deep within infected tissue - to break every capsid in the body wholesale?
 
-However, it would be an understatement to say that destruction of lung tissue is significant in the lethality of SARS [Nicholls 2006].
+There is much historical precedent for applying microwave power to the body diathermy (the internal heating of tissue for therapeutic effect) and hyperthermy (the overheating or cauterization of tissue for destructive effect).
+
+While the majority of diathermy systems use much lower frequencies for deeper heating penetration, several papers have explored the 10 GHz band, almost exclusively for superficial hyperthermia.
+
+NCoV has a unique appreciation for nervous system \cite{neuroinvasive2020}, and SARS is usually found widely distributed throughout many of the most well-regarded organs \cite{Organ2004}, shielded by an average of 4 cm of chest wall [Schroeder 2013].
+
+However, it would be an understatement to say that destruction of lung tissue is significant in the lethality of SARS [Nicholls 2006], \cite{situ2020}; largely the lung type II alveolar cells
 
@@
 The main bronchus is about 8 mm in diameter.
-
-Applying microwave power to the body is already used extensively in diathermy (the internal heating of tissue for therapeutic effect) and hyperthermy (the overheating or cauterization of tissue for destructive effect).
-While the majority of diathermy systems use much lower frequencies for deeper heating penetration, several papers have explored the 10 GHz band.
-Superficial vs deep-tissue hyperthermia.
 
@@
 
-In addition to these limits, the "microwave hearing threshold" - the pulse energy density threshold at which nerve stimulation begins to occur, should be respected.
+In addition to these limits, the "microwave hearing threshold" - the pulse energy density threshold at which the slightest nerve stimulation begins to occur, should also be respected.
+In fact, ultra-high pnerve stimulation has been
 

### 2020-11-29 documents/background.tex
NLTL doesn't seem to help.
No analytic solution

@@
 
-we appear to have lost confidence in the concept of accurate measurement itself.
-
 the only analagous non-thermal mechansism we are aware of is electroporation; and that requires the diffusion of ionized sodium and potassium charge carriers through the membrane, which would seem to necessarily require a non-
@@
 However, there equally appear to be no fundamental reasons why some small-molecule drug could not bind to the wrong receptor, why
+
+Most things with a stiffness matrix has some resonant frequency\citationneeded. As far as we can tell, two justifications underpin the categorical implausibility of resonance-like behavior in
+
+\begin{itemize}
+		\item Viscous damping from biological solvents is so strong that the relaxation time is 
+\end{itemize}
+
+To a first order, this simply doesn't seem to be true in the case of the virion.
+
+\begin{itemize}
+		\item The charge 
+\end{itemize}
 
@@
 
-\subsection{Artifacts in past absorption spectroscopy experiments, and the subsequent development of non-classical damping hypotheses}
+\subsection{Artifacts in past absorption spectroscopy experiments, and the subsequent development and debunking of non-classical damping hypotheses}
 
@@
 
-crude, amateurish equipment, by making completely justifiable changes in calibration and post-processing correction for thermal drift, normalization, etc, we could produce a resonance mode at many frequencies.
-almost any frequency we liked.
+In the case of our crude, amateurish equipment, by making completely justifiable changes in calibration and post-processing correction for thermal drift, normalization, etc, we could produce a resonance mode at almost any frequency we liked.
 We were able to produce many candidate peaks even in pure water.
-
-autem We have not yet examined the details of the hydration-layer theory.
 
@@
 
-However, as Foster et al demonstrated, there is nothing necessarily wrong with VNA-based dielectric spectrometry, if it is well conducted.
+However, as Foster et al demonstrated, there is nothing necessarily wrong with VNA-based dielectric spectroscopy if it is well conducted.
 The Liu and Yang group seem very competent experimenters, and the experiments are very well conducted; but history would seem to suggest that we take some degree of caution.

### 2020-11-29 documents/charge.tex
osmotically-stressed phage doesn't do it either
No analytic solution

--- 2020-11-21 documents/charge.tex
@@
 \documentclass[paper.tex]{subfiles}
+\usepackage{parselines}
+
 \begin{document}
@@
 
+\begin{autem}
+	What is the charge on phage x174 from Burkhauzens Raman spectroscopy data?
+\end{autem}
+
 Yang et al determine that in order to fit their microwave absorption cross-section data, and produce the decrease in infectivity via precisely the mechanism they suggest, the "core" and "shell" of Influenza A should have an effective charge of about $q=1 \times 10^7 e^-$.
 
-Is such a charge plausible?
+The mechanism given is that ions from solution counteract the protein charges to form an "electric double layer".
+In any case, the best representation is two concentric spheres, with a net charge each.
 
-As might be expected, the electrostatic properties of the virus differ from that of host cells, both on the sub-protein level\cite{Icosahedral2019} \footnotemark \ and in the lipid bilayer \cite{Lipid2015} \footnotemark.
-The mechanism given is that ions from solution counteract the protein charges to form an "electric double layer".
-In any case, the best representation is two concentric spheres with a net charge each.
+What specifically contributes to this charge? For the purposes of coarse MD simulation, it seemed useful to localize the charge concentration.
+
+As might be expected, the electrostatic properties of the virus differ from that of host cell, both on the sub-protein level\cite{Icosahedral2019} \footnotemark \ and in the lipid bilayer \cite{Lipid2015} \footnotemark.
 
@@
 		Different from insect, plant, and human, viruses had more positively charged than negatively charged segments.
-Viral proteins were the only class enriched in extremely high positively charged segments (charge greaterthan + 17) when compared to the overall proteome (1B-inset with p-values).
+Viral proteins were the only class enriched in extremely high positively charged segments (charge $> +17$) when compared to the overall proteome (1B-inset with p-values).
 	\end{quote}
@@
 
+\footnote{Influenza also has several other fascinating electrostatic properties. First, the net charge on the virion changes}
+
 \begin{autem}
@@
 
-\subsection{Major proteins and other components}
+\subsection{Major components}
 
-Protein net charges extracted from primary protein sequences compiled by the proteome-pI database \cite{ProteomepI2017} and UniProt using localCIDER \cite{CIDER2017}.
-See \ghfile{biology/data/net_charge.py} and structure.csv.
+At the largest scale, at a pH of 7 the net charges of the 4 proteins that comprise ~88\% of the protein mass\cite{Quantitative1981} of the virus (of the 11 coded for by the Influenza A genome) only contribute at most  $\approx 1 \times 10^5\  e^-$.
+
+\begin{sidenote}
+Protein net charges extracted from protein primary structure sequences\footnotemark compiled by the proteome-pI database \cite{ProteomepI2017} and UniProt\footnotemark using localCIDER \cite{CIDER2017}.
+See \ghfile{biology/data/net_charge.py} and structure.xlsx.
 Detailed source information will be added later!
-There are many.
+\end{sidenote}
+Assuming a charge of $2e^-$ per base pair due to phosphate groups, the 13.5 kbp of RNA can hardly contribute $> 3e^- \times10^4$
 
 Note that this is considering the net charge of a whole isolated protein.
-Some proteins poke through the envelope; if a zwitterionic polarization existed from one end to another, for instance, this would not count here but would affect the coupling to an EM field.
-Given the size of most proteins, however, this doesn't seem like a likely effect.
+Some proteins poke through the envelope; if a zwitterionic polarization existed from one end of a protein to another, for instance, this would not count here but would affect the coupling to an EM field.
+Given the small extent of most of the structural proteins, however, this doesn't seem like a likely effect.
+
+\begin{sidenote}
+	It should be noted that these are the simplest, first-order primary structure charges. In practice, the charge is determined by the secondary structure and the bonding to adjacent structures.
+
+	 Penhoet \cite{Structurea}, "the viral glycoproteins and nonstructural protein are heterogeneous in isoelectric point, forming constellations of interrelated protein spots." whether this is intra- or inter-virion hetrogenity is unknown to us.
+
+	Empirically-determined charges appear to be somewhat inconsistent:
+
+	Privalsky and Penhoet \cite{Influenza1978} and Penhoet \cite{Structurea} find that the isoelectric point of the M protein is so acidic that it runs right off the end of their 2D electrophoresis gel.
+They also note that
+
+	However, the predicted value by [] is about 3.
+
+	This is not of much importance for this section, but may be important when setting up MD simulations.
+
+	Because CryoEM uses charged particles, it is theoretically possible to extract the actual charge distribution of a macrostructure directly from an un-fit CryoEM map \cite{Identification2018}. 
+\end{sidenote}
 
@@
 
-$$ U = \frac{3}{5}  \frac{1}{4 \pi \epsilon_0} \frac{Q^2}{R} \approx 2.3\text{e}^{-7} \text{ J} $$
+$$ U = \frac{3}{5}  \frac{1}{4 \pi \epsilon_0} \frac{Q^2}{R} \approx 2.3\text{e}^{-7} \text{ J} \approx 6 \times 10^{11}\  \text{ATP-equivalent} $$
 %U = (3/5) * 1/(4*pi*electricConstant) *((1e7 electricCharge)^2 / 60 nanometers) = 2.30708e-7 J
-
-The total is $6 \times 10^{11}$ ATP-equivalent.
 
@@
 Influenza is approximately 174 MDa Ruigrok.
-Assuming a typical 50\% H concentration, such a charge would require about 1 in every 15 atoms to have a free electron.
+Assuming a typical 50\% H concentration, such a charge would require about 1 in every 15 atoms to have a free electron - a very different definition of "blood plasma".
 Compare to less than 1/100 for Arginine or 1/600 for DNA.
@@
 From Eq.
-2, and n0 \approx 3 M, it follows that nin \approx 0.62 M and hence n++ n- \approx 4.2 M, which because of the Donnan equilibrium is indeed significantly larger than 2nb \approx 3 M.
+2, and n0 \approx 3 M, it follows that nin $\approx 0.62 M$ and hence n++ n- \approx 4.2 M, which because of the Donnan equilibrium is indeed significantly larger than 2nb \approx 3 M.
 }
@@
 
-If we assume that the charge is not as. All other properties being equal, to account for the same coupling and absorption, one of the following would seem to need to be true:
+\subsection{Discussion}
 
-1. the effective path length of the waveguide used by Sun may not be as they expected.
-2. The concentration of virus was higher than measured.
+If we assume that the charge is not as. All other properties being equal, to account for the same coupling and absorption, it seems one or many of the following would seem to need to be true:
 
-On the largest scale, at a pH of 7, the net charges of the 11 proteins coded for by the Influenza A genome only contribute
+\begin{itemize}
+\item We have grossly misunderstood the nature of the charge imbalance. Most likely.
+\item The effective path length of the waveguide used by Sun may not be as they expected, or otherwise the corrections made are not of the correct scale.
+\item The concentration of virus was higher than measured by plaque assay - perhaps a dilution was missed.
+\end{itemize}
 

### 2020-12-02 documents/fluorescence.tex
Wording
osmotically-stressed phage doesn't do it either
writing!
math

@@
 \begin{document}
+
+virus-specific
+
+hemagglutinin test
+
+bleaching was not obviously an issue
+
+A white LED with a high color-rendering index (DK) seemed to have more power in the passband; however, green leakage around the filter was too strong.
+
+Unlike gels or plastic-glass sandwiches as used by Tiffen, thin-film filters have the disadvantage that the pass-band depends greatly on the angle of incidence.
+
+$$\lambda = \lambda \sqrt{1-sin(\theta)^2}$$
+
+The wavelength shifts shorter (bluer) as $\theta$ increases.
+
+This isn't an issue for the excitation filter, but is an issue for the.
+
+Since the LEDs and flurophore emissions are not naturally collimated, this poses a little bit of an issue.
+The microscope objective seems to provide sufficient collimation for the emission filter.
+
+The Edmund filter was unmounted glass. Also, these thin-film filters do not extend to the edge of the glass. Edge-blankening ("inked") fil
+
+The LED was about 3 cm away, and put through a ~3 mm aperture. The output from the filter was directly into the 1 mm fiber, itself improving the bandpass.
+
+The 10 nm FWHM emission filter is much narrower than professional GFP filters, especially the super-wide edge-pass ones; a lot of photons are lost that way. However, it's still more than sufficient.
 
@@
 A 10-second integration time, with, produced a background fluorescence signal of ~1500 counts, with per-sample stability of approximately \pm 1500 counts.
+The
 

### 2020-12-02 documents/lessons_learned.tex
math

@@
 \paragraph{Lessons Learned} \
+
+\rule{\linewidth}{0.2pt}
+
+It is interesting to think about the meta-issues surrounding this project. Beta-glo assay, not a few kilometers away the food bank ran out of food and people were not able.
+
+\rule{\linewidth}{0.2pt}
+
+This one was taught to me by Yuriy!
+
+We were trying to write a pre-baked math worksheet into Wolfram Mathematica.
+
+It is useful to first strictly implement precisely as written, and only when all parts are operational and understood, begin modifying for your own use.
+
+This is common practice in many fields, but hadn't occurred to me for math.
 
@@
 
-Papers only carry the scientific heritage that their authors saw fit to include in the references section.
+Papers only carry the scientific heritage that their authors saw fit to include in the references section, and only provide the context included in the "introduction".
 
@@
 
-Minor errors in .
+We often came across a situation in which minor errors in software,  would completely change the conclusion of our results.
+
 Reproducible coding helps, but it would be much better if we had used standard software engineering best practices; red-teaming, unit testing on randomly generated data, etc.
@@
 See Phosphine.
+
+It may be useful to make explicit to the reader where particular sensitivities - high gradients of conclusion against some factor - might exist in your research.
 
@@
 
-Manually taking notes tended to disrupt the flow of testing; and in any case, just noting "SIR filter has appropriate phase response" is almost useless. What {\it was} the phase response? Plot it!
+Manually taking notes tended to disrupt the flow of testing; and in any case, just noting "SIR filter has appropriate phase response" is almost useless.
+What {\it was} the phase response?
+Plot it, and upload it!
 
@@
 
-I think this is a good general rule: record as much detail automatically as possible
+I think this is a good general rule: record as much detail as automatically as possible
 
@@
 \rule{\linewidth}{0.2pt}
+
+Dill
 
@@
 
+Honestly, this might already account for a difference in productivity between, say, Python, and C++. the package manager.
+
 \rule{\linewidth}{0.2pt}
@@
 eLNemo and the CHARMMing web interface are advanced examples of this.
-This way, anyone with an input file can get results without futzing around with installation.
+This way, anyone with an input file can get results without futzing around with installation, at least for the few decades that the servers are maintained.
 
@@
 
-In one example in this project, many hours were wasted because the enamel insulation on a bodge wire had not burned off completely in the solder joint, leading to a high-impedance connection.
+In one example in this project, many hours were wasted because the enamel insulation on a bodge wire had not burned off completely in a solder joint, leading to a high-impedance connection.
 
@@
 
-The ability to almost immediately compare simulation to experiment was essential.
+The ability to almost immediately compare simulation to experiment was of great use almost everywhere in this project.
+This hybrid, "lockstep" approach between theory, simulation, and practice works, I think, extremely well.
+Even if all these intermediate experiments fail, the mere process of setting up an experiment offers you insight - and forces you to persue leads - which would not otherwise have been gained.
+Is it better than, say, spending a year carefully establishing the theory behind an experiment, and then doing one?
+I'm not sure.
+Other teams have had great success with this.
 
@@
 
-but, some months later, it was found that he was *right* - absolutely right.
+but, some months later, it was found that he was *right* - absolutely right. This was a grave error in management!
 

### 2020-12-11 documents/brillouin_pulse_math.tex
No analytic solution
Replicated Z,C's result using functionalDerivative! yay

@@
 
-This problem is called "optimal control"?
+The Euler-Lagrange equation is usually brought up in the case of the Brachistochrone problem, or the Principle of Least Action (see Feynman lectures).
+In this case, the path through space, endpoints a to b, where space would seem to be replaced with the frequency domain.
+
+Aha! That's the ticket!
+
+Search terms: "first variation", gateaux derivative,
 

### 2020-12-12 documents/background.tex
Apparent success?

@@
 
-As any researchers who have scalded their mouths on microwaved dinner may know, microwave irradiation can produce unintuitive temperature gradients, with local hot-spots that can be difficult to measure directly.
+As any researchers who have scalded their mouths on a cheap dinner may know, microwave irradiation can produce unintuitive temperature gradients, with local hot-spots that can be difficult to measure directly.
 
@@
 This is a fascinating result, and one which should be compared to the existing literature and very carefully replicated to isolate the mechanism.
-However, unless it is suggested that {\it Pediococcus sp.} also exhibits a confined microwave resonance of the same nature, it appears that periodic temperature measurements within the physiological range are not necessarily a sufficiently stringent control to definitively isolate resonant effects from other mechanisms.
+However, unless it is suggested that {\it Pediococcus sp.} also exhibits a confined microwave resonance of the same nature, it appears that periodic temperature measurements within the physiological range are not necessarily a sufficiently stringent control to definitively {\it isolate} resonant effects from other mechanisms.
 
@@
 Burton\cite{Effects1950} describe the use of thermochromic pigments to examine heating profiles. Using low-frequency exposure, they are able to produce localized regions in excess of 50 C.
+
+\subsection{Other artifacts}
+
+Bergqvist \cite{Effect1994a} find that the permeabilizing of their liposomes was not due to microwave exposure, but apparently a very peculiar interaction with the Teflon dish that was used only for positive microwave trials.
+Therefore, every part of the experimental protocol should be maintained precisely identical for non-sham and thermal sham trials.
+
+Some Russian research has, in the past, been discounted due to attenuators that leak high
 

### 2020-12-13 documents/brillouin_pulse_math.tex
Apparent success?
lipidwrapping

@@
 
+Pulse energy, rather than peak field, is not obviously the ideal constraint for this problem; however, it is the one most compatible with lagrange multiplier techniques.
+
 The Euler-Lagrange equation is usually brought up in the case of the Brachistochrone problem, or the Principle of Least Action (see Feynman lectures).
-In this case, the path through space, endpoints a to b, where space would seem to be replaced with the frequency domain.
+In this case, the path through space from endpoints a to b is replaced with the whole frequency domain from -$\inf$ to +$\inf$.
 
@@
 
+As noted by Pozar, the complex conjugate arises from the concept of "adjointness". Franks.
+
+Note the ni in the complex conjugate!
+
 \end{document}

### 2020-12-13 documents/charge.tex
Replicated Z,C's result using functionalDerivative! yay
Apparent success?
lipidwrapping

@@
 
+(these values were only taken at a pH of 7.
+A larger charge imbalance might be found at less neutral pHes.
+However, any effect would be of little practical use if it does not occur at physiological pH.)
+
 \begin{sidenote}
@@
 
+This also agrees roughly with Perilla \cite{Physical2017}
+
 \subsection{Electrostatic energy}
+
+Viral capsids self-assemble; it is energetically favorable to.
 

### 2020-12-13 documents/viscosity.tex
lipidwrapping

@@
 
-However, if we apply the same arguments to microtubules \cite{Viscous2000}, omega_c = 80 GHz, and Q=11.2. The effects of these exposures should have been
+However, if we apply the same arguments to microtubules \cite{Viscous2000}, we get omega_c = 80 GHz and Q=11.2.
+The effects of these exposures should have been noticed in the previous studies, so there is probably something gravely wrong with this analysis.
+
+In the steady-state, producing 1 nN from a charge of 10^5 takes some 60 kV/m.
 

### 2020-12-13 biology/simulation/GROMACS/simple_bilayer/lipidwrap.sh

@@ -1,0 +1,14 @@
+python2 lipidwrapper_py2.py\
+    --surface_equation "z = math.sqrt((x*x)+(y*y)+(10*10))"\
+    --lipid_pdb_filename lipid_example.pdb \
+    --delete_clashing_lipids TRUE \
+    --clash_cutoff 1.0 \
+    --fill_holes TRUE \
+    --fill_hole_exhaustiveness 10 \
+    --output_directory output \
+    --number_of_processors 16 \
+    --clashing_potential_margin 15.0 \
+    --memory_optimization_factor 1
+
+
+#python2 lipidwrapper_py2.py --surface_filename influenza_mesh.pdb --lipid_pdb_filename lipid_example.pdb --delete_clashing_lipids TRUE --fill_holes TRUE --clash_cutoff 1.0 --output_directory output --number_of_processors 24 --use_disk_instead_of_memory FALSE --show_grid_points TRUE --create_triangle_tcl_file TRUE --clashing_potential_margin 15.0 --memory_optimization_factor 1

### 2020-12-13 math/pulse_optimization.m

@@ -7,13 +7,13 @@ G(omega) = 1/(omega_res^2 - (2*i*beta*omega) - omega^2)
 n(omega) = sqrt(eps_inf + (eps_s - eps_inf)/((1-i*omega*tau)*(1-i*omega*tau_f)))
 
 
-e_x = G(omega) * (F(omega)*exp(-1i*(omega/c0)*n(omega)*z)*exp(1i*omega*t))
+e_x = G(omega) * (F(omega)*exp(1i*(omega/c0)*n(omega)*z)*exp(-1i*omega*t))
 
 W = (1/Z0) * real(n(omega))*abs(F(omega))^2
 
 W = subs(W)
 
-xi = -e_x + lambda*W
+xi = conj(-e_x) + lambda*W
 grad_xi = functionalDerivative(xi,F)
 
 % note the sneaky n_i and n_r in the complex conjugate!
@@ -45,15 +45,25 @@ F_optimal = subs(F_optimal, beta, 10^-10)
 F_optimal = subs(F_optimal, Z0, 377)
 F_optimal = subs(F_optimal, c0, 3e8)
 
-F_optimal = subs(F_optimal, t, 0)
-F_optimal = subs(F_optimal, z, 0)
+F_optimal = subs(F_optimal, t, 0.0)
+F_optimal = subs(F_optimal, z, 0.05)
 
 
 F(omega) = rhs(F_optimal)
 
 %simplify(F(10))
-fplot(real(F(omega)),[1e8, 10000e9])
-fplot(imag(F(omega)),[1e8, 10000e9])
+fplot(real(F(omega)),[1e8, 10000e9]);
+fplot(imag(F(omega)),[1e8, 10000e9]);
+
+x = 1e4:5e8:3000e9;
+
+vpa(F(x))
+
+time = ifft(complex(double(real(vpa(F(x)))),double(imag(vpa(F(x))))));
+
+time = repmat(time,1,3);
+
+plot(real(time))
 
 %sol = isolate(grad_xi,F(omega))
 %pretty(sol)

### 2020-12-15 electronics/propagation/propagation_numerical_optimize.py
just a scale issue

@@ -17,18 +17,18 @@ omega_res = 2.0*pi*8e9
 
 Z0 = 377.0
 c0 = 3e8
-m_reduced = 1
-q = 1
+m_reduced = 1.16e-19
+q = 10e4 * 10e-19
 
 t= 0.0
 z = 0.5
 
 
 Q = 2.0
-gamma = omega_res / q
+gamma = omega_res / Q
 
 def greens_function(omega):
-    return 1.0/(omega_res**2.0 - omega**2.0 + 1j*gamma*omega)
+    return q/(m_reduced*(omega_res**2.0 - omega**2.0 + (1j*gamma*omega)))
 
 def refractive_index(omega):
     #refractive index is n = sqrt(mu/epsilon)
@@ -38,8 +38,7 @@ def propagate(F, omega, z):
 
     frequency_domain = np.fft.fft(F)
     # greens_function(omega) * q/m_reduced *
-    print(greens_function(omega))
-    propagated =  greens_function(omega) * (frequency_domain*np.exp(-1j*(omega/c0)*refractive_index(omega)*z))
+    propagated =  greens_function(omega) * frequency_domain * 
     # watch the sign here - fix if needed
 
     return np.fft.ifft(propagated)
@@ -48,8 +47,8 @@ def propagate(F, omega, z):
 def cost_function(F, omega, z):
     return abs(-np.max(propagate(F, omega, z)) + np.max(F**2.0))
 
-duration = 1000e-10
-samples = 300
+duration = 100e-10
+samples = 10000
 times = np.linspace(-duration,duration,samples)
 
 F=np.ones(samples)
@@ -69,3 +68,6 @@ output = F
 plt.plot(times, output)
 plt.plot(times, propagate(output, omega, z))
 plt.show()
+
+# plt.plot(omega,greens_function(omega)/1e-10)
+# plt.show()

### 2020-12-15 documents/brillouin_pulse_math.tex
Got lazy, doing it numerically
yay apparently solved?

@@
 \begin{document}
+
+Uzunoglu \cite{Theoretical2020} mention a handy way to circumvent this lossy-flesh problem: the Brillouin and Sommerfeld precursors.
+
+The original text of these papers are in German; translations can be found in Léon Brillouin's 1960 book\cite{Wave1960} on the topic. \footnotemark
+
+\footnotetext{Some of the initial work on these precursors (or "forerunners", as they were known at the time) apparently neglected some of the higher-order terms, leading to the conclusion that the signals were "very weak".
+However, the amplitude is often much greater than that of the carrier.
+See wikipedia.}
+
+These are fascinating structures which arise as a result of two aspects Albanese \cite{Shortrisetime1989}:
+
+The highly dispersive nature of tissue, which
+
+The change in loss - and increase in penetration depth -
+
+A third aspect leads to the formation of the prototypical brilluoin precursor: any "sharp" beginning or end of a wave, or other spatially confined structure, includes harmonics up to these \footnotemark
+
+\footnotetext{it is interesting to note that a similar - if not equivalent - effect leads to the Heisenberg uncertainty principle. The more localized a }
+
+At 9 GHz, assuming that a torso is about 10 penetration depths in radius and the brilluoin train drives the virus with an equally, implementing this would decrease the surface field required for complete eradication of the virus from the body to a perfectly practicable 1 kV/m, rather than an air-ionizing 6.6 MV/m ($\frac{1}{\sqrt{10}}=0.316$ versus $e^{-10}=4.5e-5$).
+
+However, the energy
 
@@
 
+by Wait \cite{Propagation1965}:
+
+\begin{quote}
+In such cases, it may be feasible to evaluate the integral by a purely numerical procedure.
+With the wide availability of the digital computer, this is certainly fashionable at the moment.
+Consequently, one might say that the problem has been solved and no further discussion is needed.
+
+However, it would be a pity if one accepted this answer since all physical insight into the nature of transient processes has been ignored. 
+\end{quote}
+
+Chirped-gaussian Macke \cite{Simple2012}.
+
+One route of inquiry was the following: Unfortunately, despite NLTLs producing strong wideband components, they do not appear to satisfy the requirements for Brillouin pulses. 
+\begin{autem}
+	This should be replicated.
+\end{autem}
+
+temporal Soliton-producing nonlinear transmission lines, and NLTL oscillators constructed therefrom, particularly well suited
+
+Transient solution
+
+A qualitative statement of the problem, for context:
+An arbitrary waveform, given in the frequency domain as F(ω),
+propagates through a dispersive, lossy medium. It then drives a
+damped harmonic oscillator that is initially at rest.
+
+What F produces the peak transient amplitude on the oscillator?
+
+Using an energy constraint, appears to tend towards a step-function impulse, perhaps as a result of Pontryagin's maximum principle.
+
 Pulse energy, rather than peak field, is not obviously the ideal constraint for this problem; however, it is the one most compatible with lagrange multiplier techniques.
 
+Tufts \cite{Optimum1964}
+
 The Euler-Lagrange equation is usually brought up in the case of the Brachistochrone problem, or the Principle of Least Action (see Feynman lectures).
-In this case, the path through space from endpoints a to b is replaced with the whole frequency domain from -$\inf$ to +$\inf$.
+In this case, it appears that the path through space from endpoints a to b is replaced with the whole frequency domain from -$\inf$ to +$\inf$.
 
@@
 
+Left-hand and right-handed complex.
+
 \end{document}

### 2020-12-15 documents/pseudo_soliton.tex
words
No analytic solution
yay apparently solved?

@@
 \begin{document}
-
-Uzunoglu \cite{Theoretical2020} cite a very handy way to circumvent this lossy-flesh problem: the Brilloin and Somerfield precursors.
-
-At 9 GHz, assuming that a torso is about 10 penetration depths in radius and the brilluoin train drives the virus with an equally, implementing this would decrease the surface field required for complete eradication of the virus from the body to a perfectly practicable 1 kV/m, rather than an air-ionizing 6.6 MV/m ($\frac{1}{\sqrt{10}}=0.316$ versus $e^{-10}=4.5e-5$).
 
@@
 \end{sidenote}
-\begin{tab}
-	content
-\end{tab}
 
@@
 The real killer
-
-temporal Soliton-producing nonlinear transmission lines, and NLTL oscillators constructed therefrom, particularly well suited
-
-\footnotemark
-
-\footnotetext{Some of the initial work on these precursors (or "forerunners", as they were known at the time) apparently neglected some of the higher-order terms, leading to the conclusion that the signals were "very weak" (Sommerfield).
-However, the amplitude is often greater than that of the carrier.}
 

### 2020-12-15 electronics/propagation/propagation_numerical_optimize.py

@@ -22,7 +22,7 @@ q = 10e3 * 10e-19
 picometer = 1e-12
 
 t= 0.0
-z = 0.05
+z = 0.08
 
 
 Q = 2.0
@@ -48,21 +48,21 @@ def debye_refractive_index(omega):
 #cole-cole refractive index
 ef, sigma, deltas, alphas, taus = get_tissue_cole_cole_coefficients(48)
 
-def cole_refractive_index(omega):
-    '''
-    See "Compilation of the dielectric properties of body tissues at RF and microwave frequencies.", Gabriel 1996
-    Equation 3, page 12.
-    '''
-    angular_frequency = omega
-    complex_permittivity = complex(ef, 0)
-    for n in range(0, 4):
-        complex_permittivity += deltas[n] / (1.0 + ((complex(0, 1)*angular_frequency*taus[n])**(1.0-alphas[n])))
 
-
-    complex_permittivity[angular_frequency > 0] += (sigma/((complex(0, 1)*angular_frequency[angular_frequency > 0]*epsilon_0)))
-
-    n = np.sqrt(1.0 / complex_permittivity)
-    return n
+# def cole_refractive_index(omega):
+#     '''
+#     See "Compilation of the dielectric properties of body tissues at RF and microwave frequencies.", Gabriel 1996
+#     Equation 3, page 12.
+#     '''
+#     angular_frequency = omega
+#     complex_permittivity = complex(ef, 0)
+#     for n in range(0, 4):
+#         complex_permittivity += deltas[n] / (1.0 + ((complex(0, 1)*angular_frequency*taus[n])**(1.0-alphas[n])))
+#
+#     complex_permittivity[angular_frequency > 0] += (sigma/((complex(0, 1)*angular_frequency[angular_frequency > 0]*epsilon_0)))
+#
+#     n = np.sqrt(complex_permittivity)
+#     return complex_permittivity
 
 
 def propagate(F, omega, z):
@@ -70,7 +70,9 @@ def propagate(F, omega, z):
     frequency_domain = np.fft.fft(F)
     # greens_function(omega) * q/m_reduced *
 
-    propagated =  greens_function(omega) * frequency_domain * np.exp(1j*(omega/c0)*cole_refractive_index(omega)*z)
+    n = np.sqrt(cole_cole_4(omega/(2.0*pi), ef, sigma, deltas, alphas, taus))
[…]

### 2020-12-15 electronics/simple_fdtd/fdtd_PCB_extensions/fdtd_PCB_extensions/tissue.py

@@ -50,7 +50,7 @@ def cole_cole_4(center_frequency, ef, sigma, deltas, alphas, taus):
     for n in range(0, 4):
         complex_permittivity += deltas[n] / (1.0 + ((complex(0, 1)*angular_frequency*taus[n])**(1.0-alphas[n])))
 
-    complex_permittivity += (sigma/((complex(0, 1)*angular_frequency*epsilon_0)))
+    complex_permittivity[angular_frequency > 0] += (sigma/((complex(0, 1)*angular_frequency[angular_frequency > 0]*epsilon_0)))
 
 
     return complex_permittivity

### 2020-12-16 documents/acknowledgement.tex
math
Writing notes

@@
 
+Yuriy S at Indiana, and Prof. Sarris at UofT.
+
+The legend of dispersion himself, Professor Oughstun, for sending me some thoughts and his paper.
+
 Thanks to (Dr. ) P. Barfuss for spending time reviewing an early draft.
@@
 
+Sandra at the Resources Sharing Department at YorkU for spending an hour looking for the Gray paper.
+
 Prof. Griffiths and Dr. Brovko at UGuelph, Dr. Anany at the GRDC for useful tips on the Beta-Glo assay.
 
-Professor Z-G Wang at Caltech for a note on electrostatics,
+Professor Z-G Wang at Caltech for a note on viral electrostatics,
 
-Profs H. Kassiri, C. David and W. Taylor (among others) at YorkU for being super nice, and H.P. and ice9 for tolerating ramblings.
+Profs H. Kassiri, C. David and W. Taylor (among others) at YorkU for encouragement, and H.P. and ice9 for tolerating midnight ramblings.
 
-Thanks to L.H. for wisdom regarding this project.
+Thanks to L.H. for wisdom regarding this project, and to my friend Eric and friends at SimCoLab.
 
@@
 
-R.I.P. to Dr. Robert Adair, whose work features prominently here, died Sep. 2020.
+R.I.P. to Dr. Robert Adair and Dr. Lewis Franks, whose work features prominently here, died 2020 and 2019.
 

### 2020-12-16 documents/brillouin_pulse_math.tex
Writing notes

@@
 
-At 9 GHz, assuming that a torso is about 10 penetration depths in radius and the brilluoin train drives the virus with an equally, implementing this would decrease the surface field required for complete eradication of the virus from the body to a perfectly practicable 1 kV/m, rather than an air-ionizing 6.6 MV/m ($\frac{1}{\sqrt{10}}=0.316$ versus $e^{-10}=4.5e-5$).
+At a depth of 8 cm in Cole-Cole muscle, an 8 GHz resonance, attack pattern alpha appears to achieve 4 picometers of oscillation amplitude, rather than 0.01 picometers with $\sin(t\ \omega_{resonance})$.
 
-However, the energy
+At 9 GHz, assuming that a torso is about 10 penetration depths in radius and the brilluoin train drives the virus with an equally, implementing this would decrease the field at the skin required for complete eradication of the virus from the body to a perfectly practicable 1 kV/m, rather than an air-ionizing 6.6 MV/m ($\frac{1}{\sqrt{10}}=0.316$ versus $e^{-10}=4.5e^{-5}$).
+
+However, the energy contained in such a standard pulsed-sine or gaussian train decays very quickly,
+
+These precursors have been used in practice, by Ong \cite{Detection2003} using simple square waves to detect respiration\footnotemark, Ossberger \cite{Noninvasive2004} for the same purpose,
+
+\footnotetext{Well, Ong don't really observe the precursor itself, it seems.}
 
@@
 
-by Wait \cite{Propagation1965}:
+Note: this isn't truly transient - the fourier integral is still periodic, wrapping around every x cycles. It's just more transient than the steady-state.
 
-\begin{quote}
-In such cases, it may be feasible to evaluate the integral by a purely numerical procedure.
-With the wide availability of the digital computer, this is certainly fashionable at the moment.
-Consequently, one might say that the problem has been solved and no further discussion is needed.
+attack pattern alpha
 
-However, it would be a pity if one accepted this answer since all physical insight into the nature of transient processes has been ignored. 
-\end{quote}
-
-Chirped-gaussian Macke \cite{Simple2012}.
-
-One route of inquiry was the following: Unfortunately, despite NLTLs producing strong wideband components, they do not appear to satisfy the requirements for Brillouin pulses. 
+ Unfortunately, despite NLTLs producing strong wideband components, they do not appear to satisfy the requirements for Brillouin pulses. 
 \begin{autem}
@@
 
-A qualitative statement of the problem, for context:
-An arbitrary waveform, given in the frequency domain as F(ω),
-propagates through a dispersive, lossy medium. It then drives a
-damped harmonic oscillator that is initially at rest.
+\pagebreak
+A qualitative statement of the problem:
 
-What F produces the peak transient amplitude on the oscillator?
+\begin{toolchain}
+An arbitrary waveform propagates through a dispersive, lossy medium with a certain analytic dispersion relation. It then drives a
+damped harmonic oscillator that is initially at rest.\\
 
-Using an energy constraint, appears to tend towards a step-function impulse, perhaps as a result of Pontryagin's maximum principle.
+What waveform produces the peak transient amplitude on the oscillator?
+\end{toolchain}
+
+\subsection{Analytic techniques}
+
+Quote Wait \cite{Propagation1965}:
+
+\begin{quote}
+	In such cases, it may be feasible to evaluate the integral by a purely numerical procedure.
+With the wide availability of the digital computer, this is certainly fashionable at the moment.
+Consequently, one might say that the problem has been solved and no further discussion is needed.
+\\
+
+	However, it would be a pity if one accepted this answer since all physical insight into the nature of transient processes has been ignored. 
+\end{quote}
+
+\begin{autem}
+Reflection from tissue interfaces?
+
+Thermal noise will kick the oscillator around; it won't necessarily start at rest. Will this affect the 
+\end{autem}
+
+One might suggest try to find the optimal transient solution first, and then try to build an input waveform deconvolved through the  transfer function of the tissue.
+This hardly seems liable to produce a truly optimal solution, however.
+
+Each problem has been solved separately.
+There are some nearly equivalent but not mathematically identical formulations for optimal control of quantum systems with dispersion.\footnotemark However, in the classical domain, this appears to be unprecedented in the literature.
+
+\footnotetext{While not strictly related, \cite{Wavepacket1989} tune a light pulse to match the wavefunction of the desired chemical products in a photo-reaction, which is just pretty darned awesome}
+
+Also, this seems similar to a pulse propagating through the tissue's Cole medium and then dissipating the maximum power in a uniform Lorentz medium, which might be another route to attacking it.
+
+Another route might be to set up two ODEs for the wave equation and the oscillator and solve them simultaneously.
+
+Progress was hindered by the ~6 conventions for Fourier normalization, the sign or handedness of the imaginary number.
+What self-respecting field has completely antipodal definitions of the same concept.
+
+oh, on the same topic, can we finally settle the i / j convention. Also, everyone that doesn't explicitly note
+
+Optimal pulses for several situations in Debye and Lorentz media have been determined by Oughstun's asymptotic method, which appears to be highly satisfactory in terms of physical intution, and also avoids truncation issues that befall fourier-transform techniques.
+In general, these optimal pulses are simple gaussian monopulses or higher-order gaussian derivatives \cite{Optimal2017} \cite{Optimal2015}.
+
+Macke \cite{Simple2012} have come up with a number of other analytic representations for various signals, such as chirped gaussian pulses.
+
+\section{Zhu et al 's dispersive waveform optimization propagation formulation}
+
+The most promising analytical technique that we explored was essentially equivalent to Zhu, Hum, Costas formulation in \cite{Microwave2012b}, previously discussed by Pozar \cite{Waveform2003}, This is based on a lagrange multiplier technique and variational calculus\footnotetext .
+
+$$ e_x(z,t) = \frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{+\infty}{F(\omega) e^{- j (\omega/c_0)n(\omega)z}\ e^{j\omega t} d\omega} $$
+
+where $\int e^{j \omega t} d\omega$ is the inverse fourier transform.
+
+$$W = \frac{1}{\eta_0} \int_{-\infty}^{+\infty}{(n_r(\omega))\ |F(\omega)|^2}\ d\omega$$\\
+
+Where $n(\omega)$ is a complex refractive index per Debye relaxation equation, $n_r()$ is the real part of the same, everything else is a real constant.
+Set up a functional with a lagrange multiplier\\
+
+$$\xi = -e_x(z,t) + \lambda W$$\\
+
+Take the functional ("variational") gradient with respect to $F(\omega)$.
+
+$$ \nabla \xi = -\frac{1}{\sqrt{2\pi}} \left(e^{- j (\omega/c_0)n(\omega)z}\right)^\star \  e^{-j\omega T} + \lambda...$$
+
+At this point, you could choose to perform a second integral over the time-domain Greens function solution to the harmonic oscillator\cite{Complex2020}, eq. 4 and 15,
+
+$$x(t) = \int_{-\infty}^{+\infty}{G(t,t')\ \frac{q\cdot e_x(z,t'))}{m}\ } dt'$$\\
+
+(eq. 15, for the underdamped case)
+
+$$G(t,t') = UnitStep(t-t') \frac{1}{\sqrt{\gamma^2-\omega_0^2}  }\sinh\left({\sqrt{\gamma^2-\omega_0^2}}\ (t-t')\right)$$
+
+But a much more straightforward
+
+Where * is the complex conjugate.\\
+
+The $\nabla H() = H()^\star$ thing seems to come from Franks, Signal Theory, 1969, page 140 onwards; I cannot make heads or tails of his formulation.
+
+Neither Mathematica's VariationalD, Matlab's Fundiff, nor Maple's functionalDerivative seem to yield any meaningful result for grad xi.\\
+
+Then set
+
+$$x(t) = \int_{-\infty}^{+\infty}{G(t,t')\ \frac{q\cdot e_x(z,t'))}{m}\ } dt'$$\\
+
+Anyhow, then modify the lagrange multiplier,
+
+$$\xi = -x(t) + \lambda W$$\\
+
+And now,
+
+$$\nabla \xi = 0$$
 
@@
 The Euler-Lagrange equation is usually brought up in the case of the Brachistochrone problem, or the Principle of Least Action (see Feynman lectures).
-In this case, it appears that the path through space from endpoints a to b is replaced with the whole frequency domain from -$\inf$ to +$\inf$.
+In these types of problems, it appears that the path of integration through space from endpoints a to b is replaced with the whole frequency domain from -$\infty$ to +$\infty$.
 
@@
 
-Left-hand and right-handed complex.
+\subsection{Laziness prevails; a return to numerical optimization}
+
+Numerically solving optimal control problems using CG was noted by Lasdon \cite{conjugate1967} and revisited by Kek \cite{Conjugate}.
+
+Using an energy constraint, appears to tend towards a square step function or a sharp impulse, perhaps as a result of Pontryagin's maximum principle\cite{Optimum1964}.
+
+\subsection{Laziness prevails; a return to numerical optimization}
 

### 2020-12-16 documents/fluorescence.tex
Replicated Z,C's result using functionalDerivative! yay
Writing notes

@@
 \begin{document}
+
+Should make a discord as lab notebook
 
@@
 
-bleaching was not obviously an issue
+bleaching was not obviously an issue, nor was storage with the dye bound to DNA.
 
-A white LED with a high color-rendering index (DK) seemed to have more power in the passband; however, green leakage around the filter was too strong.
+A white LED with a high color-rendering index (DK) seemed to have more power in the blue passband; however, green leakage around the filter was too strong.
 
@@
 
-Performance of this arrangement was satisfactory.
+Performance of this arrangement was very satisfactory.
 A 10-second integration time, with, produced a background fluorescence signal of ~1500 counts, with per-sample stability of approximately \pm 1500 counts.
@@
 Contrary to standard microscopy, you want as little excitation light to enter the objective as possible. Using the existing
+
+autofluroescneces Lexan
 
@@
 (Phi6 uses an RNA - many dyes have different responses to single-stranded (ss)DNA, dsDNA, or
+
+autof
 
@@
 The dichroic only removes the excitation to the 1\% level - you still need the dielectric filters, and they’re really expensive.
-With fiber optic excitation at right angles to the objective, scattering was low enough that the dichroic was completely unnecessary.
+With fiber optic excitation at right angles to the objective, scattering was low enough that the dichroic was unnecessary.
 
@@
 
+Relaxation times of acrynylomadfnium dyes extend from a few picoseconds up to once the complex is produced.
+This is a saturable, hormetic effect; if all the binding sites are filled on the DNA the intensity is quenched, as noted by Xie.
+
 \end{document}

### 2020-12-16 math/test.tex
Writing notes

--- 2020-12-13 documents/brillouin_pulse_math.tex
@@
-%!TeX root = brillouin_pulse_math
-\documentclass[paper.tex]{subfiles}
+\documentclass[]{article}
+
+\usepackage{pdfpages}
+
 \begin{document}
 
-%http://web.physics.ucsb.edu/~fratus/phys103/LN/DHM.pdf
-% section on Greens functions
-% and also 
-% and
-% https://www.int.washington.edu/users/dbkaplan/228_01/green.pdf
+A qualitative statement of the problem, for context:
 
-Pulse energy, rather than peak field, is not obviously the ideal constraint for this problem; however, it is the one most compatible with lagrange multiplier techniques.
+\begin{quote}
+An arbitrary waveform, given in the frequency domain as $F(\omega)$, propagates through a dispersive, lossy medium. It then drives a damped harmonic oscillator that is initially at rest. \\
 
-The Euler-Lagrange equation is usually brought up in the case of the Brachistochrone problem, or the Principle of Least Action (see Feynman lectures).
-In this case, the path through space from endpoints a to b is replaced with the whole frequency domain from -$\inf$ to +$\inf$.
+What $F$ produces the peak {\it transient} amplitude on the oscillator?
 
-Aha! That's the ticket!
+\end{quote}
 
-Search terms: "first variation", gateaux derivative,
+(this might be completely ill-posed or otherwise intractable - I grasp very little of the below, unfortunately)
 
-As noted by Pozar, the complex conjugate arises from the concept of "adjointness". Franks.
+(there're lots of different approaches to this - Oughston's asympototic method, Macke and Segard - but this one seems sensible) \\
 
-Note the ni in the complex conjugate!
+Zhu et al, in doi: 10.1109/APS.2012.6348428 offer a method to maximize the electric field $e_x(z,t)$, (see Franzen's fourier-transform method \\ http://www.dtic.mil/docs/citations/ADA371944)\\
+
+Prof. Costas gave me a page (unpublished it seems) with more details - see the blue attached pdf.\\
+
+Given
+
+$$ e_x(z,t) = \frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{+\infty}{F(\omega) e^{- j (\omega/c_0)n(\omega)z}\ e^{j\omega t} d\omega} $$
+
+$$W = \frac{1}{\eta_0} \int_{-\infty}^{+\infty}{(n_r(\omega))\ |F(\omega)|^2}\ d\omega$$\\
+
+Where $n(\omega)$ is a complex refractive index per Debye relaxation equation, $n_r()$ is the real part of the same, everything else is a real constant.
+Set up a functional with a lagrange multiplier\\
+
+$$\xi = -e_x(z,t) + \lambda W$$\\
+
+Take the functional ("variational") gradient with respect to $F(\omega)$.
+
+$$ \nabla \xi = -\frac{1}{\sqrt{2\pi}} \left(e^{- j (\omega/c_0)n(\omega)z}\right)^\star \  e^{-j\omega T} + \lambda...$$
+
+Where * is the complex conjugate.\\
+
+The $\nabla H() = H()^\star$ thing seems to come from Franks, Signal Theory, 1969, page 140 onwards; I cannot make heads or tails of his formulation. \\
+
+Neither Mathematica's VariationalD, Matlab's Fundiff, nor Maple's functionalDerivative seem to yield any meaningful result for grad xi.\\
+
+Then set
+
+$$\nabla \xi = 0$$
+
+and solve for $F(\omega)$ normally. (then fourier transform back to $F(t)$, whatever)
+
+\section{Harmonic oscillator Green's function}
+
+From the below pdf, (renamed F(force) to $e_x$ to avoid confusion), where q is a charge, oscillation amplitude is
+
+$$x(t) = \int_{-\infty}^{+\infty}{G(t,t')\ \frac{q\cdot e_x(z,t'))}{m}\ } dt'$$\\
+
+Where G() is listed therein (eq.
+15, for the underdamped case) (Keeping the Green function in the frequency-domain could maybe simplify things a bit?
+Wouldn't have to fourier-transform back and forth?)\\
+
+Anyhow, then modify the lagrange multiplier,
+
+$$\xi = -x(t) + \lambda W$$\\
+
+And now,
+
+$$\nabla \xi = 0$$
+
+That seems to be the hard part.\\
+
+How do you take the functional derivative of such an equation?
+
+\includepdf[pages=-,pagecommand={}]{paper.pdf}
+
+\includepdf[pages=-,pagecommand={}]{10_greens_function.pdf}
 

### 2020-12-16 math/test_simplified.tex
Writing notes

\documentclass[]{article}

\usepackage{pdfpages}

\begin{document}

Existing worked example from a paper:

$$ e_x(z,t) = \frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{+\infty}{F(\omega) e^{- j (\omega/c_0)n(\omega)z}\ e^{j\omega t} d\omega} $$

$$W = \frac{1}{\eta_0} \int_{-\infty}^{+\infty}{(n_r(\omega))\ |F(\omega)|^2}\ d\omega$$\\

Where $n(\omega)$ is a complex function, $n_r()$ is the real part of the same, everything else is a real constant. An existing paper sets up the functional with a lagrange multiplier\\

$$\xi = -e_x(z,t) + \lambda W$$\\

Takes the functional ("variational") gradient with respect to $F(\omega)$.

$$ \nabla \xi = -\frac{1}{\sqrt{2\pi}} \left(e^{- j (\omega/c_0)n(\omega)z}\right)^\star \  e^{-j\omega T} + \lambda...$$

Where * is the complex conjugate.\\

The $\nabla H() = H()^\star$ thing seems to come from Franks, Signal Theory, 1969, page 140 onwards; I can't seem to make heads or tails of his formulation... \\

Neither Mathematica's VariationalD, Matlab's Fundiff, nor Maple's functionalDerivative seem to yield any meaningful result for grad xi, but I probably set things up wrong.\\

They then set

$$\nabla \xi = 0$$

and solve for $F(\omega)$ normally. (then fourier transform back to $F(t)$)\\

\pagebreak

What I'd like to do is modify this to maximize the amplitude x(t) of oscillation of a harmonic oscillator. Using the Greens function solution, \\

where q is a charge, oscillation amplitude is

listed therein (eq. 15, for the underdamped case).\\

Anyhow, then modify the lagrange multiplier,

$$\xi = -x(t) + \lambda W$$\\

And now,

$$\nabla \xi = 0$$

That seems to be the hard part.\\

Is there any chance you could suggest a route to attack this gradient?

\end{document}

### 2020-12-16 documents/brillouin_pulse_math.tex
Liposome test

@@
 Uzunoglu \cite{Theoretical2020} mention a handy way to circumvent this lossy-flesh problem: the Brillouin and Sommerfeld precursors.
+
+Are similar to soliton
 
@@
 At a depth of 8 cm in Cole-Cole muscle, an 8 GHz resonance, attack pattern alpha appears to achieve 4 picometers of oscillation amplitude, rather than 0.01 picometers with $\sin(t\ \omega_{resonance})$.
+The sharp edges are at approx.
+250 GHz.
 
@@
 \begin{toolchain}
-An arbitrary waveform propagates through a dispersive, lossy medium with a certain analytic dispersion relation. It then drives a
+An arbitrary waveform propagates through a dispersive, lossy medium with a certain analytic complex permittivity. It then drives a
 damped harmonic oscillator that is initially at rest.\\
@@
 
-Quote Wait \cite{Propagation1965}:
-
-\begin{quote}
+\begin{fquote}[Wait][ \cite{Propagation1965}]
 	In such cases, it may be feasible to evaluate the integral by a purely numerical procedure.
@@
 	However, it would be a pity if one accepted this answer since all physical insight into the nature of transient processes has been ignored. 
-\end{quote}
+\end{fquote}
 
@@
 
-The most promising analytical technique that we explored was essentially equivalent to Zhu, Hum, Costas formulation in \cite{Microwave2012b}, previously discussed by Pozar \cite{Waveform2003}, This is based on a lagrange multiplier technique and variational calculus\footnotetext .
+The most promising analytical technique that we explored was essentially equivalent to Zhu, Hum, Costas formulation in \cite{Microwave2012b}, previously discussed by Pozar \cite{Waveform2003}, This is based on a lagrange multiplier technique\cite{Methods1989} and variational calculus\footnotetext .
 

### 2020-12-16 biology/simulation/GROMACS/BUMPy_bilayer/wrap.sh

@@ -1,1 +1,25 @@
-bumpy.py -f flat_input.pdb -o cylindrical_output.pdb -n index.ndx -p topol.top -s sphere -z 10 -g r_sphere:100
+
+python3 bumpy.py -f bilayer.pdb -o membrane.pdb -n index.ndx -p topol.top -s sphere -z 250 -g r_sphere:500
+
+
+# There appears to be a bug in bumpy with Z values > 100
+# bumpy.py:161: RuntimeWarning: Mean of empty slice.
+#   self.coords[:, 0:2] -= self.coords.mean(axis=0)[0:2]
+# /home/arthurdent/Programs/miniconda/lib/python3.7/site-packages/numpy/core/_methods.py:154: RuntimeWarning: invalid value encountered in true_divide
+#   ret, rcount, out=ret, casting='unsafe', subok=False)
+# []
+# []
+# Traceback (most recent call last):
+#   File "bumpy.py", line 1500, in <module>
+#     main()
+#   File "bumpy.py", line 1464, in main
+#     shape = shape_tobuild.gen_shape(template_bilayer, zo, **geometric_args)
+#   File "bumpy.py", line 934, in gen_shape
+#     top_half = shapes.semisphere.gen_shape(template_bilayer, zo, r_sphere, False)
+#   File "bumpy.py", line 782, in gen_shape
+#     bot_leaflet.scale_flat_to_spherical(r_sphere, r_sphere - zo[0])
+#   File "bumpy.py", line 260, in scale_flat_to_spherical
+#     print(phi_sections.max())
+#   File "/home/arthurdent/Programs/miniconda/lib/python3.7/site-packages/numpy/core/_methods.py", line 30, in _amax
+#     return umr_maximum(a, axis, None, out, keepdims, initial, where)
+# ValueError: zero-size array to reduction operation maximum which has no identity

### 2020-12-17 documents/background.tex
just a scale issue
liposome

@@
 
+Notice that a non-zero resonant frequency
+requires
+ωR 6= 0 ⇒ β < ω/√
+2. (49)
+That is, the oscillator must be sufficiently under-damped in order to exhibit a
+resonance response
+
 \subsection{Other artifacts}
@@
 
-Some Russian research has, in the past, been discounted due to attenuators that leak high
+Some research has been discounted due to attenuators that leak high
 

### 2020-12-19 biology/simulation/GROMACS/BUMPy_bilayer/s3_water_box.sh
VMD signal library

@@ -5,6 +5,8 @@ GMX_DIR="/home/arthurdent/Programs/gromacs-2020.1/gromacs-2020.1/build/bin"
 
 rm ./output/s3/*
 
+#dodecahedron
+
 $GMX_DIR/gmx_mpi editconf -box 35 -f ./output/s2/minimized_bilayer.pdb -o ./output/s3/centered.pdb -bt cubic
 
 #$GMX_DIR/gmx_mpi solvate -cs polarize-water.gro -cp ./output/s3/centered.pdb -p output/topol.top -o output/s3/solvated.pdb -shell 30

### 2020-12-26 documents/comment.tex
"Prompt" electroporation

%!TeX root = comment
\documentclass[fleqn,10pt]{paper}

\usepackage[left=2cm,right=2cm,
top=0.5cm,
bottom=1.5cm,%
headheight=11pt,%
letterpaper]{geometry}

\include{preamble}

\begin{document}

Hello you wonderful people.

Perhaps you are here because of the papers

\begin{quote}
	Yang S-C, Lin H-C, Liu T-M, Lu J-T, Hung W-T, Huang Y-R, et al. Efficient Structure Resonance Energy Transfer from Microwaves to Confined Acoustic Vibrations in Viruses. Scientific Reports 2015;5:1–10. https://doi.org/10.1038/srep18030.
\end{quote}

\begin{quote}
Liu T-M, Chen H-P, Wang L-T, Wang J-R, Luo T-N, Chen Y-J, et al. Microwave resonant absorption of viruses through dipolar coupling with confined acoustic vibrations. Appl Phys Lett 2009;94:043902. https://doi.org/10.1063/1.3074371.
\end{quote}

Or other reports by this team.

These papers have received some attention due to the apocalypse: for instance,

\begin{quote}
	Burkhartsmeyer J, Wang Y, Wong KS, Gordon R. Optical Trapping, Sizing, and Probing Acoustic 
	Modes of a Small Virus. Applied Sciences 2020;10:394. https://doi.org/10.3390/app10010394.
\end{quote}

\begin{quote}
Uzunoglu N. Theoretical Analysis of the Induction of Forced Resonance Mechanical Oscillations to Virus Particles by Microwave Irradiation:Prospects as an Anti-virus Modality 2020. https://doi.org/10.20944/preprints202004.0462.v1.
\end{quote}

I have attempted to replicate these results, primarily in Bacteriophage T4, without success. 
However, I have not attained the same regime of electric field, and I cannot yet register anything 
approaching a conclusion into the scientific record.

However, I think it may be useful to note a few things; to register a tentative negative result in light of the large positive publication bias observed in this field (see the excellent meta-analysis by Vijayalaxmi \cite{Comprehensive2018}).

I do not wish to even slightly degrade the work of the Sun group. It must have taken a great deal of time and effort to conduct, and it is very carefully designed, with many orthogonal measurements.

Indeed, I have no conclusion as to whether the effect seen exists. The effect ultimately requires a 
fully atomistic treatment, involving a very subtle re-arrangement of the lipid bilayer; ample 
mechanisms for such an effect exist to account for Sun et al's observations. For instance, see 
Liburdy's observations of liposome leakage due to oxygen.

Ultimately I do not believe sufficient high-quality data exists to make a determination.

Any expert would probably have immediately identified this; I am not one.

\section{The observed charge of q=$10^7 e^-$ appears to be difficult to account for via the 
suggested hypothesis.}

The proteins coded for by the influenza genome do not suggest such a large charge imbalance. The 
HIV capsid, for instance, has a charge not greater than $4\times 10^3 e^-$.

Such a charge would imply that some 1 in 20 atoms in the virus are associated with a mobile 
electron. This is an exceptional charge, beyond that of any amino acid species.

Neither can osmotic pressure account for such a charge.

Induced polarization and/or the associated ion migration is seen in electroporation experiments, 
and could account for such a charge, but is not expected at frequencies > 100 MHz or at  See ICNIRP 
reviews on the topic.

\section{Reliable microwave absorption spectra are extremely difficult to obtain.}

Precisely the same story has played out before. Edwards et al.

The experimenters go to great lengths to use various different test jigs, but, crucially, no error analysis like Foster's is mentioned for any of them. Indeed, in the previous paper on nanoparticle resonance, the experimenters note that the effect was not observed until the jig was modified.

\section{It is possible, with some imagination, to explain the result as a thermal artifact.}

The temperature is measured via a conventional infrared thermometer to be below the lipid melting point, but is otherwise uncontrolled. Previous experiments have shown that such readings are not sufficient to isolate non-thermal effects.

Figure 6 is then difficult to explain. If the effect is thermal, why would the peak of the inactivation curve lie correspond perfectly to the one obtained by spectroscopy? The gain flatness of the antenna and amplifier may

{\Huge \textbf{However}}

\section{Q=2 is somewhat reasonable, surprisingly.}

As noted in the papers, unlike other biological systems it's plausible that the virion would have modes that are at least very close to being under-damped. Burkhartsmeyer offer reasonable evidence for this (although resonance-like artifacts are not unheard-of in Raman spectroscopy).

This is expected by e.g. basic Stokes viscous drag. The distinction is perhaps because of the large mass that coherently contributes to the oscillation unlike the situations Adair consider with small patches of membranes. A small catch is that the same Stokes continuum arguments suggest that microtubules (if imbued with the same polarization) would exhibit similar behavior, which is not obviously observed in previous studies.

Coarse molecular dynamics sims also concur with Q=1.5. Experiments by Tsen on femtosecond impulses 
do too (although some care must be taken here as some of these results have been discredited).

This has some pretty awesome implications if it is correct, but whether the small amplitude 
amplification factor associated with this effect will be important is not known to me.

\section{None of the issues raised above necessarily rule out a non-thermal "keyhole" with 
megavolt/m fields.}

There is data to support a little-known "prompt" electroporation effect of viruses at 
some $10^7 \text{V/m}$. Single pulses along these lines are not obviously damaging, per NATO 
Research Task Group 189. With some optimization, a keyhole between the electroporation threshold 
for may be found.

\section{The suggestion by Uzunoglu that precursor pulses are satisfactory is prescient.}

The centimeter-thick layer of highly-conductive muscle which surrounds the lungs prevents treatment 
without thermal damage.

However, a carefully shaped pulse that matches the Cole-Cole dispersion relation of tissue 
(apparently, a sawtooth) appears to side-step Beer's law decay and drives the oscillator some 300x 
more strongly.

\end{document}

### 2021-01-04 documents/supplemental.tex
scd5000 import?

@@
 - W. G. Cochran et al, \cite{Statistical1953}
+
+many of the base facts - and some of the most useful and simplest methods - are in the early 
+papers, and later papers generally just refer to the previous ones. it can be of some use to try to 
+find the earliest papers. For instance, when searching for methods for the bacteriophage, lots of 
+modern detail-scarce papers appear, but none of the most important Delbruck papers.
+
+"when searching for old papers, use the terminology of the day. millimicrosecond, for instance, for 
+nanosecond".
 

### 2021-01-07 documents/acknowledgement.tex
"Prompt" electroporation
scd5000 import?
fuckeradfkljaldkf jaldskfj fuck fuck fuck fuck

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph{Acknowledgements}\
+\section{Acknowledgements}\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-Yuriy S at Indiana, and Prof. Sarris at UofT.
+Yuriy S at Indiana, and Prof. Sarris at UofT. Sean Hum and [that other guy?] from UofT.
 
@@
 
-Sandra at the Resources Sharing Department at YorkU for spending an hour looking for the Gray paper.
+Sandra and colleagues at the Resources Sharing Department at YorkU for spending an hour looking for 
+the Gray paper.
 
@@
 
-Thanks to L.H. for wisdom regarding this project, and to my friend Eric and friends at SimCoLab.
+Thanks to L.H. for wisdom regarding this project, and to my friend Eric, and friends at SimCoLab.
 

### 2021-01-07 documents/background.tex
Minimization
VMD signal library
scd5000 import?
fuckeradfkljaldkf jaldskfj fuck fuck fuck fuck

@@
 
+Unfortunately, this cannot be an exhaustive list. 20,000 papers.
+
+significant work on elecroporation for cancer, water treatment, and food sterilization.
+
+can we bind a highly-charged something-or-other to the virus?
+or a little magnetite crystal - like that magnetoacoustic paper?
+
 We have cycled between condemning as pathological science, and lauding it as the cure. Barring
+
+\subsection{Liburdy's oxidation-dependent lipid leakage}
+
+\subsection{Tsen femtosecond laser ISRU}
+
+Impulsive stimulated Raman scattering. We confess to not having studied these mechanisms in great detail. Does not directly act on 
+the vibrational mode; the optimal pulse duration is some fraction of the period of the mode in question.
+ Unfortunately, these results appear to have failed replication \cite{No2011}. In any case, inactivation requires a very long duration; 
+ unlikely to be of great clinical use.
+
+Ultrafast femtosecond laser pulses
+
+\subsection{Free-electron-laser }
 

### 2021-01-07 documents/brillouin_pulse_math.tex
liposome
fuckeradfkljaldkf jaldskfj fuck fuck fuck fuck

@@
 
+\section{The Brillouin precursors}
+
 Uzunoglu \cite{Theoretical2020} mention a handy way to circumvent this lossy-flesh problem: the Brillouin and Sommerfeld precursors.
 
-Are similar to soliton
+The original text of these papers are in German; translations can be found in Léon Brillouin's 1960 
+book\cite{Wave1960} on the topic. \footnotemark
 
-The original text of these papers are in German; translations can be found in Léon Brillouin's 1960 book\cite{Wave1960} on the topic. \footnotemark
+These are fascinating structures which arise as a result of two aspects (Albanese 
+\cite{Shortrisetime1989}):
 
-\footnotetext{Some of the initial work on these precursors (or "forerunners", as they were known at the time) apparently neglected some of the higher-order terms, leading to the conclusion that the signals were "very weak".
-However, the amplitude is often much greater than that of the carrier.
-See wikipedia.}
+The highly dispersive nature of tissue, which causes a peculiar distortion of short pulses,
 
-These are fascinating structures which arise as a result of two aspects Albanese \cite{Shortrisetime1989}:
+The change in loss (the complex part of the permittivity, or the) and increase in penetration depth 
+-
 
-The highly dispersive nature of tissue, which
-
-The change in loss - and increase in penetration depth -
-
-A third aspect leads to the formation of the prototypical brilluoin precursor: any "sharp" beginning or end of a wave, or other spatially confined structure, includes harmonics up to these \footnotemark
+A third aspect leads to the formation of the prototypical brilluoin precursor: any "sharp" 
+beginning or end of a tone, or other spatially confined structure in a waveform, includes harmonics 
+up to these \footnotemark
 
@@
 
-At 9 GHz, assuming that a torso is about 10 penetration depths in radius and the brilluoin train drives the virus with an equally, implementing this would decrease the field at the skin required for complete eradication of the virus from the body to a perfectly practicable 1 kV/m, rather than an air-ionizing 6.6 MV/m ($\frac{1}{\sqrt{10}}=0.316$ versus $e^{-10}=4.5e^{-5}$).
+At 9 GHz, assuming that a torso is about 10 penetration depths in radius and the Brillouin train 
+drives the virus with an equally, implementing this would decrease the field at the skin required 
+for complete eradication of the virus from the body to a perfectly practicable 1 kV/m, rather than 
+an air-ionizing 6.6 MV/m ($\frac{1}{\sqrt{10}}=0.316$ versus $e^{-10}=4.5e^{-5}$).
 
@@
 These precursors have been used in practice, by Ong \cite{Detection2003} using simple square waves to detect respiration\footnotemark, Ossberger \cite{Noninvasive2004} for the same purpose,
+
+Also another really good paper that I can't find.
 
@@
 
- Unfortunately, despite NLTLs producing strong wideband components, they do not appear to satisfy the requirements for Brillouin pulses. 
+Unfortunately, despite NLTLs producing strong wideband components, in cursory simulations they do 
+not appear to satisfy the requirements for Brillouin pulses. Our working hypothesis is that this is 
+because of destructive interference from the falling edge that immediately follows; but this is 
+mere speculation.
 \begin{autem}
@@
 \begin{toolchain}
-An arbitrary waveform propagates through a dispersive, lossy medium with a certain analytic complex permittivity. It then drives a
-damped harmonic oscillator that is initially at rest.\\
+An arbitrary waveform propagates through a dispersive, lossy medium with a certain analytic complex 
+permittivity.
+
+It then drives a damped harmonic oscillator that is initially at rest.\\
 
@@
 
-\section{Zhu et al 's dispersive waveform optimization propagation formulation}
+\printendnotes
 
-The most promising analytical technique that we explored was essentially equivalent to Zhu, Hum, Costas formulation in \cite{Microwave2012b}, previously discussed by Pozar \cite{Waveform2003}, This is based on a lagrange multiplier technique\cite{Methods1989} and variational calculus\footnotetext .
+\subsubsection{Zhu et al 's dispersive waveform optimization propagation formulation}
+
+The most promising analytical technique that we explored was essentially equivalent to Zhu, Hum, 
+Costas formulation in \cite{Microwave2012b}, previously discussed by Pozar \cite{Waveform2003}, 
+This is based on a lagrange multiplier technique\cite{Methods1989} and variational 
+calculus\footnotetext{} .
 
@@
 
-Neither Mathematica's VariationalD, Matlab's Fundiff, nor Maple's functionalDerivative seem to yield any meaningful result for grad xi.\\
+Neither Maxima, SageMath, Mathematica's VariationalD, Matlab's Fundiff, nor Maple's 
+functionalDerivative seem to yield any meaningful result for grad xi.\\
 
@@
 
-The Euler-Lagrange equation is usually brought up in the case of the Brachistochrone problem, or the Principle of Least Action (see Feynman lectures).
-In these types of problems, it appears that the path of integration through space from endpoints a to b is replaced with the whole frequency domain from -$\infty$ to +$\infty$.
-
-Aha! That's the ticket!
+The Euler-Lagrange equation is usually brought up in the case of the Brachistochrone problem, or 
+the Principle of Least Action (see Feynman lectures). In these types of problems, it appears that 
+the path of integration through space from endpoints a to b is replaced with the whole frequency 
+domain from -$\infty$ to +$\infty$.
 
@@
 
-Numerically solving optimal control problems using CG was noted by Lasdon \cite{conjugate1967} and revisited by Kek \cite{Conjugate}.
+Numerically solving optimal control problems using CG was noted by Lasdon \cite{conjugate1967} and 
+revisited by Kek \cite{Conjugate}. They reduce the computational workload by first computing the 
+gradient function by hand.
 

### 2021-01-07 documents/paper.tex
fuckeradfkljaldkf jaldskfj fuck fuck fuck fuck

@@
 
-\subfile{introduction}
+%\subfile{introduction}
 
@@
 \end{figure}
+
+\subfile{background}
 
@@
 \clearpage
-\printbibliography[heading=none, title={}, keyword={Flagship}]
+%\printbibliography[heading=none, title={}, keyword={Flagship}]
 \printbibliography[heading=none, title={}, keyword={standards}]
@@
 \subfile{safety}
-
-\clearpage
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{multicols}{1}
-{\Large The Experiment}\\
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\paragraph{\textbf{Centrifugal microfluidics}}\
-
-The field of centrifugal microfluidics is accelerating.
-
-Many CD microfluidics systems use standard CD molding techniques for the channels and machining techniques, using either acrylic or silicone.
-The turbidity sensor is most sensitive if the plastic is clear.
-Sterilization does not seem to be discussed.
-
-Polypropylene is the ideal material, being almost indefinitely autoclavable. It is quite difficult to machine.
-
-\end{multicols}
 
@@
 
-\subfile{acknowledgement}
+%\subfile{acknowledgement}
 
@@
 
-\printbibliography[ title={All references}]
+%\printbibliography[]
+%\printbibliography[title={All references}]
 

### 2021-01-07 documents/scan_converter.tex
fuckeradfkljaldkf jaldskfj fuck fuck fuck fuck

We would like real-time rather than equivalent-time sampling,

Possible routes:

make the plates super small like Von Ardenne (thin wires). see the papers on thin wires.

make the plates slow-wave structures matched to the speed of the electron; travelling-wave deflection plates.
unfortunately, travelling wave structures necessarily absorb power and affect the impedance of the circuit in question

multiple beams with different path lengths to have different phases?

put the x-axis at a 45 degree angle?

radiation damage to sensor

A digital oscilloscope capable of real-time sampling such a transient is no small feat, and it was deemed unlikely that we would be 
able to obtain access, There is also the concern that, when working with a system producing kilovolt 
pulses and an input of 5v, some harm might come to a machine worth more than the experimenter.

Possibly some optical method.

however, recording such transients is quite a solved problem, having been accomplished to the required degree

taking "direct access" tube to its logical conclusion.

since the sensor will inevitably outgas, a sealed tube is impractical.

The distortion due to transit-time phasing is

$$ \frac{\sin(\frac{2\pi F \tau}{2})}{(2\pi F)/2} $$

where \tau is the transit time of the electron through the deflection region

### 2021-01-07 documents/supplemental.tex
fuckeradfkljaldkf jaldskfj fuck fuck fuck fuck

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-{\Huge Captain's Log, Supplemental}\\
+\section{\Huge Captain's Log, Supplemental}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{fquote}[Paraphrased from W. G. Cochran][\cite{Statistical1953}]
+The accumulated insight of a worker frequently merits recording when no documentation can be given.
+\end{fquote}
 
-\begin{quote}
-The accumulated insight of a [] worker frequently merits recording when no documentation can be given.
-\end{quote}
+Materials
 
-- W. G. Cochran et al, \cite{Statistical1953}
+polycarbonate
+
+infinitely autoclaveable. However, clear has possible issues with flurosescence background. white 
+is 
+generally recommended for fluro.
+
+polypropylene
+autoclaveable, although softening causes warping if not supported. Difficult form strong bonds to 
+with adhesives. causes "hairs" when machining.
+
+There is some good advice in the Government Accountability one is especially sage:
+
+"Be as quantitative as possible."
+
+source of truth in the home lab. For instance, you can build an oscilloscope, or a pulse generator, 
+but not both.
+
+\subsubsection{Old papers}
 
@@
 papers, and later papers generally just refer to the previous ones. it can be of some use to try to 
-find the earliest papers. For instance, when searching for methods for the bacteriophage, lots of 
-modern detail-scarce papers appear, but none of the most important Delbruck papers.
+find the earliest papers.
 
-"when searching for old papers, use the terminology of the day. millimicrosecond, for instance, for 
+For instance, when searching for methods for the bacteriophage, lots of modern detail-scarce papers 
+appear, but none of the most important Delbruck papers. Books are one way to side-step this issues
+
+When searching for old papers, use the terminology of the day. millimicrosecond, for instance, for 
 nanosecond".
+
+find government gray-literature publications on the topic. They are often
+
+find research groups with "lists of publications".
+
+\subsubsection{Cargo-cult}
 
@@
 \begin{quote}
+
 Similarly, IEEE-ICES urges the Commission to adopt a higher SAR exposure limit of 2 W/kg averaged over 10 g.
@@
 
-\printbibliography[heading=none, title={}, keyword={amplifier}]
+%\printbibliography[heading=none, title={}, keyword={amplifier}]
 
@@
 
-\printbibliography[heading=none, title={}, keyword={rectifier}]
+%\printbibliography[heading=none, title={}, keyword={rectifier}]
 

### 2021-01-08 documents/brillouin_pulse_math.tex
scan converter, but fucking why

@@
 Uzunoglu \cite{Theoretical2020} mention a handy way to circumvent this lossy-flesh problem: the Brillouin and Sommerfeld precursors.
+
+Such thin
 
@@
 The change in loss (the complex part of the permittivity, or the) and increase in penetration depth
--
+
+While it is clearly possible to produce this abnormal penetration (any sharp edge suffices), it was not obvious to us that a waveform 
+could be constructed that would be 
+an effective driver for the normal modes in question. Oughston ; if the pulses are too close together, they distort the precursor thus 
+formed.
 

### 2021-01-08 documents/fluorescence.tex
VMD signal library
scan converter, but fucking why

@@
 \begin{document}
+
+Fluoris
+
+ LOL
+
+(apologies to Floris Laporte)
+
+sketches of light source in inkscape
+
+from [], using ImageJ to stack. works great on cheap cmos cameras - interestingly doesn't work at all on more expensive cameras. - 
+almost good enough - great for diagnostics
+
+interestingly, the fact that the camera has color is quite valuable; filtering the green out can increase sensitivity a lot
+
+a 30-s exposure on a cheap camera also almost got there.
 

### 2021-01-11 documents/molecular_dynamics.tex
fuckeradfkljaldkf jaldskfj fuck fuck fuck fuck
pdftex

@@
-\paragraph{Molecular dynamics simulation}
+%!TeX root = molecular_dynamics
+\documentclass[paper.tex]{subfiles}
+\begin{document}
+
+\section{Molecular dynamics simulation}
 \
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+An illustrative - to ensure that there was nothing egregiously wrong with the Stokes drag calculation and to extract various.
+Certainly this has been done dozens of times in the past.
+For other reasons to play around with.
+]\
+
+\begin{figure}[H]
+%	\makebox[\textwidth][c]{
+	\centering
+	\subfloat[Flower one.]{
+	\includegraphics[width=0.4\textwidth]{Vescicle.png}
+
+	}
+	\hfill
+	\subfloat[The observed spectrum]{
+		\includesvg[width=0.4\textwidth]{spectrum}
+
+	}
+		\caption{Second.}
+
+\end{figure}
+
+These results are not in any way quantitative, nor do they truly suggest that the effect exists.
+Lipid vesicle simulations with MARTINI force fields have yielded large-scale stiffness values which are orders of magnitude\cite{Determining2014} from those found experimentally; the speed of sound is also.
+
+A very large amount of tuning and comparison  to obtain any kind of meaningful
+
+Liposome wrapped with BUMPy\cite{BUMPy2018}. \footnote{Durrant's LipidWrapper are equally good options}. MARTINI 
+coarse-grained 
+lipid and water force field. Run with GROMACS (5?) on the GPU.\footnote{\it "H. H. Williams: Furious activity is no substitute 
+	for understanding.".}  A non-equlibrium simulation (very weak thermostat on lipid) with a thick layer of explicit water and then one monolayer of water with restraints (?
+N/m spring constant) and a strong thermostat () to crudely emulate a large thermal bath (an "open boundary").
+This may not be a good way to do this.
+
+molecular dynamics simulation of a lipid vescicle of 30 nm diameter. A mix of POPC and PUPI added to bring liposome charge to 
+observed levels.
+
+Rather than use built-in normal-mode methods, Fourier analysis of the (lipid-only) trajectory was performed with TRAVIS\footnote{a 
+really fantastic program. Clever user interface too!}, zero-padded at the end to obtain sufficient low-frequency bins with short simulations. The initial "spring Note the non-zero y-intercept.
+
+Computational pipeline available at \ghfile{biology/simulation/GROMACS/BUMPy_bilayer} \footnote{GALAXY or some other, more repeatable "pipeline manager" should have been used}. Elec
+
+Coarse-grained models of COVID with mechanically have recently
+
+\printbibliography{}
 
@@
 Because CryoEM is sensitive to the
+
+\end{document}

### 2021-01-11 documents/background.tex
Writing, re-organizing references

@@
 
+NATO Research Task Group 189 \cite{treatyelectromagnetic}
+
+HFM-189 found no published and replicated adverse health effects or biological mechanisms, beyond
+thermal interaction, for pulses shorter than 100 ms which suggested that neither the peak E-field limit in the
+IEEE C95.1TM-2005 safety standard nor the proposed limit in the Directive 2004/40/EC [33] (subsequently
+promulgated as 2013/35/EU [34]) have scientific basis.
+
+The group noted that physical laws governing the propagation of E-fields in air already limit the maximum allowable peak E-field at ~3 MV/m (air breakdown).
+Current research efforts by members to expose biological organism(s), tissues, and cells to environmental
+fields up to this magnitude have been unable to elicit an acute biological response.
+
+C95.1-2019, B.4.3 Rationale for pulsed RF field limits
+
+Cancer treatment involving irreversible electroporation is in a different regime. Long pulses involving high conduction currents through needles. Cardiac arrest.
+
+H. H. Williams: Furious activity is no substitute for understanding.
+
 Unfortunately, this cannot be an exhaustive list. 20,000 papers.
@@
 
-\subsection{Liburdy's oxidation-dependent lipid leakage}
+\subsection{Liburdy's oxygen-dependent lipid leakage}
 
-\subsection{Tsen femtosecond laser ISRU}
+\subsection{Tsen's femtosecond laser ISRU}
 
 Impulsive stimulated Raman scattering. We confess to not having studied these mechanisms in great detail. Does not directly act on 
-the vibrational mode; the optimal pulse duration is some fraction of the period of the mode in question.
- Unfortunately, these results appear to have failed replication \cite{No2011}. In any case, inactivation requires a very long duration; 
- unlikely to be of great clinical use.
+the vibrational mode; the optimal pulse duration is some small fraction of the period of the mode in question.
+
+Unfortunately, these results appear to have failed replication \cite{No2011}. In any case, inactivation requires a very long duration of exposure; unlikely to be of great clinical use.
 
@@
 
+If this mechanism exists, it would seem to provide significant advantages over existing UV or cold-plasma sterilization.
+
+If the extensions made in our paper are valid, this is a non-ionizing, non-thermal
+%
+\footnote{It may be useful to define 'non-thermal'; it caused us some confusion.
+Certainly the proteins of the virion locally absorb energy and increase in temperature.
+The key is that, when excited in this manner, the energies in the envelope are poorly modeled by a Maxwell-Boltzmann distribution; they are not given sufficient time to 'thermalize'.
+In contrast, with typical 2.4 GHz microwave exposure, sterilization can only occur by aggregate heating of the fluid and tissue.}
+%
+, non-chemical technique, harmless for continuous exposure to tissue, which can sterilize air and surfaces alike, including skin, eyes, and within hair; it evolves no ozone, can readily be generated with \$1 USD - scale devices, acts instantaneously, and - perhaps most critically - could be made to act {\bf within infected tissues}.
+
+The X-band is also minimally absorbed by air, allowing action in the far-field and scaling to square-kilometer areas with single installations.
+
+\footnote{``{[B]elow about 6 GHz, where EMFs penetrate deep into tissue (and thus require depth to be considered), it is useful to describe this in terms of “specific energy absorption rate” (SAR), which is the power absorbed per unit mass $(W/kg)$.
+Conversely, above 6 GHz, where EMFs are absorbed more superficially (making depth less relevant), it is useful to describe exposure in terms of the density of absorbed power over area $W/m^2$, which we refer to as “absorbed power density”}'' [ICNIRP 2020 \faExternalLink] }
+
+\footnote{It should be noted that this {\it confined} acoustic resonance is subtly distinct from common-and-garden pipe-organ acoustic resonance; this is apparently not a strictly classical phenomenon.
+Besides standard Coulomb-like and Lennard-Jones-like interactions between constituent particles, if Fr\"{o}hlich is to be believed at these nanoscopic scales there are also wave-function interactions among the particles of the virus which can shift storage to modes not otherwise expected.
+
+	We confess to not yet understanding this phenomenon; fortunately, while helpful, the details of how this mode appears are not critical to implementing this technique.}
+
+\footnote{All values have been converted to $\text{W/m}^2$ to avoid confusion. 100 $\text{W/m}^2 = 10 \text{ mW/cm}^2 = 10 \text{ dBm/cm}^2$.}
+
 the only analagous non-thermal mechansism we are aware of is electroporation; and that requires the diffusion of ionized sodium and potassium charge carriers through the membrane, which would seem to necessarily require a non-
@@
 Laser
+
+Additionally, other sterilization techniques may produce superior results with less faffing about and should be evaluated in the same context.
+For instance, data on far UV [Buonanno 2017] indicates safety.\\
 
@@
 Most things with a stiffness matrix has some resonant frequency\citationneeded. As far as we can tell, two justifications underpin the categorical implausibility of resonance-like behavior in
+
+Notice that a non-zero resonant frequency
+requires
+ωR 6= 0 ⇒ β < ω/√
+2. (49)
+That is, the oscillator must be sufficiently under-damped in order to exhibit a
+resonance response
 
@@
 
+To illustrate how sensitive this research is, [Chemeris 2004] mention:
+
+\begin{quote}
+
+	The increase in DNA damage after exposure of cells to HPPP EMF shown in Table 2 was due to the temperature rise in the cell suspension by $3.5\pm0.1^{\circ}  $C.
+This was confirmed in sham-exposure experiments and experiments with incubation of cells for 40 min under the corresponding temperature conditions."
+
+\end{quote}
+
 A previous report of microwave resonance, Grundler \cite{Sharp1983}, use a calorimeter, a stream of cooling water controlled to within 0.1 C, an interferometric thermometer, and can state definitively that at no point does the temperature inhomogeneity exceed 0.02 C.
@@
 Burton\cite{Effects1950} describe the use of thermochromic pigments to examine heating profiles. Using low-frequency exposure, they are able to produce localized regions in excess of 50 C.
-
-Notice that a non-zero resonant frequency
-requires
-ωR 6= 0 ⇒ β < ω/√
-2. (49)
-That is, the oscillator must be sufficiently under-damped in order to exhibit a
-resonance response
 

### 2021-01-11 documents/fluorescence.tex
Writing, re-organizing references

@@
-%!TeX root = fluroescence
+%!TeX root = fluorescence
 \documentclass[paper.tex]{subfiles}
 \begin{document}
+
+\begin{figure}[H]
+	\captionsetup{singlelinecheck = false, justification=justified}
+	\centering
+	\includegraphics[width=\textwidth]{fluro_1}
+	\caption{}
+\end{figure}
+
+\begin{figure}[H]
+	\captionsetup{singlelinecheck = false, justification=justified}
+	\centering
+	\includegraphics[width=\textwidth]{fluro_2}
+	\caption{}
+\end{figure}
+
+For one thing, GelGreen appears to be eminiently stable - samples can be stored for long periods of time; pre-mixed batches.
+
+\subsection{Light source}
+
+A modulation frequency of
+
+Lexan fluro was unex
+
+Acridine orange (N-alkylacridinium)
+
+Orange 16
 
@@
 
+the microscope is largely unnecessary.
+
 bleaching was not obviously an issue, nor was storage with the dye bound to DNA.
@@
 
-The LED was about 3 cm away, and put through a ~3 mm aperture. The output from the filter was directly into the 1 mm fiber, itself improving the bandpass.
+The LED was about 3 cm away, and put through a ~3 mm aperture in a piece of PVC pipe. The output from the filter was directly into the 1 mm fiber, itself improving the bandpass.
 
@@
 Performance of this arrangement was very satisfactory.
-A 10-second integration time, with, produced a background fluorescence signal of ~1500 counts, with per-sample stability of approximately \pm 1500 counts.
+A 10-second integration time, with, produced a background fluorescence signal of ~1500 counts, with per-sample stability of approximately $\pm 1500$ counts.
 The
@@
 
-With the setup we’re using and the small quantities, the excitation light is somewhere around ~10^5 times as powerful as the emission.
+With the setup we’re using and the small quantities, the excitation light is somewhere around ~$10^5$ times as powerful as the emission.
 This doesn’t seem to be a big issue gel-docs, picking out bands on gels - they don’t usually seem to use excitation filters; however, to get the excitation bleed-through low enough to do this quantitative assay, the bleed-through must be really low, and in our testing proper dielectric filters are required on both the excitation and emission sides.
@@
 
-Note that PMTs are happy to endure very high pulse currents, like flashbulbs for exciting.
-
-No shutters or anything required.
+Note that PMTs are happy to endure very high pulse currents, like flashbulbs for exciting; no shutters or anything required. Gating the photomultiplier HV is another technique.
 
@@
 
-Gel-docs , with spectra specified using the Wratten scale. These do not seem to have optical density (OD - logarithmic value of transmission in the blocking band) values sufficient for this qfluor.
+Gel-docs , with spectra specified using the Wratten scale.
+These filters alone do not seem to have optical density (OD - logarithmic value of transmission in the blocking band) values sufficient for this qfluor.
 
-Epiflurorescence means the Most commercial microscopes use dichroic beamsplitters, allowing the excitation beam beam to go through the same objective.
+Most commercial microscopes use dichroic beamsplitters, allowing the excitation and emission beam to go through the same objective.
 The dichroic only removes the excitation to the 1\% level - you still need the dielectric filters, and they’re really expensive.
-With fiber optic excitation at right angles to the objective, scattering was low enough that the dichroic was unnecessary.
+With fiber optic excitation at right angles to the objective, excitation scattering was low enough that the dichroic was unnecessary.
 
@@
 
-Gating the photomultiplier HV is another technique.
-
 PCR is another method
 
-Silicon photomultipliers like ON's C−Series are almost certainly sufficient for this application, eliminating the HV requirements of PMTs at the cost of a higher dark count and slightly smaller active area.
+Silicon photomultipliers like ON's C-Series are almost certainly sufficient for this application, eliminating the HV requirements of PMTs at the cost of a higher dark count and slightly smaller active area.
 

### 2021-01-11 documents/molecular_dynamics.tex
Writing, re-organizing references

@@
 coarse-grained 
-lipid and water force field. Run with GROMACS (5?) on the GPU.\footnote{\it "H. H. Williams: Furious activity is no substitute 
-	for understanding.".}  A non-equlibrium simulation (very weak thermostat on lipid) with a thick layer of explicit water and then one monolayer of water with restraints (?
+lipid and water force field.
+Run with GROMACS (5?) on the GPU.
+A non-equlibrium simulation (very weak thermostat on lipid) with a thick layer of explicit water and then one monolayer of water with restraints (?
 N/m spring constant) and a strong thermostat () to crudely emulate a large thermal bath (an "open boundary").
@@
 
-Rather than use built-in normal-mode methods, Fourier analysis of the (lipid-only) trajectory was performed with TRAVIS\footnote{a 
-really fantastic program. Clever user interface too!}, zero-padded at the end to obtain sufficient low-frequency bins with short simulations. The initial "spring Note the non-zero y-intercept.
+Rather than use standard eigenmode-style normal-mode methods (ProDy), Fourier analysis of the (lipid-only) trajectory was performed with TRAVIS\footnote{a really fantastic program.
+Clever user interface too!}, zero-padded at the end to obtain sufficient low-frequency bins with short simulations.
+The initial "spring Note the non-zero y-intercept.
 
-Computational pipeline available at \ghfile{biology/simulation/GROMACS/BUMPy_bilayer} \footnote{GALAXY or some other, more repeatable "pipeline manager" should have been used}. Elec
+Computational pipeline available at \ghfile{biology/simulation/GROMACS/BUMPy_bilayer} \footnote{GALAXY or RENKU or some other, more repeatable and reproducible "pipeline manager" should have been used}.
 
-Coarse-grained models of COVID with mechanically have recently
+Polarizable water is usually required
+
+Coarse-grained models of COVID with mechanically have recently been created; as of this writing the all-important nucleocapsid and RNA
 

### 2021-01-11 documents/paper.tex
Writing, re-organizing references

@@
 
-If this mechanism exists, it would seem to provide significant advantages over existing UV or cold-plasma sterilization.
-
-If the extensions made in our paper are valid, this is a non-ionizing, non-thermal
-%
-\footnote{It may be useful to define 'non-thermal'; it caused us some confusion.
-Certainly the proteins of the virion locally absorb energy and increase in temperature.
-The key is that, when excited in this manner, the energies in the envelope are poorly modeled by a Maxwell-Boltzmann distribution; they are not given sufficient time to 'thermalize'.
-In contrast, with typical 2.4 GHz microwave exposure, sterilization can only occur by aggregate heating of the fluid and tissue.}
-%
-, non-chemical technique, harmless for continuous exposure to tissue, which can sterilize air and surfaces alike, including skin, eyes, and within hair; it evolves no ozone, can readily be generated with \$1 USD - scale devices, acts instantaneously, and - perhaps most critically - could be made to act {\bf within infected tissues}.
-
-The X-band is also minimally absorbed by air, allowing action in the far-field and scaling to square-kilometer areas with single installations.
-
 \begin{autem}
@@
 The precise structure and charge of the virion appears to be a singular anomaly in this otherwise categorical non-existence.
-
-\footnote{It should be noted that this {\it confined} acoustic resonance is subtly distinct from common-and-garden pipe-organ acoustic resonance; this is apparently not a strictly classical phenomenon.
-Besides standard Coulomb-like and Lennard-Jones-like interactions between constituent particles, if Fr\"{o}hlich is to be believed at these nanoscopic scales there are also wave-function interactions among the particles of the virus which can shift storage to modes not otherwise expected.
-
-We confess to not yet understanding this phenomenon; fortunately, while helpful, the details of how this mode appears are not critical to implementing this technique.}
-
-\footnote{``{[B]elow about 6 GHz, where EMFs penetrate deep into tissue (and thus require depth to be considered), it is useful to describe this in terms of “specific energy absorption rate” (SAR), which is the power absorbed per unit mass $(W/kg)$.
-Conversely, above 6 GHz, where EMFs are absorbed more superficially (making depth less relevant), it is useful to describe exposure in terms of the density of absorbed power over area $W/m^2$, which we refer to as “absorbed power density”}'' [ICNIRP 2020 \faExternalLink] }
-
-\footnote{All values have been converted to $\text{W/m}^2$ to avoid confusion. 100 $\text{W/m}^2 = 10 \text{ mW/cm}^2 = 10 \text{ dBm/cm}^2$.}
 
@@
 2019], listing the requirements for reliable in-vitro RF experiments.\\
-
-To illustrate how sensitive this research is, [Chemeris 2004] mention:
-
-\begin{quote}
-
-The increase in DNA damage after exposure of cells to HPPP EMF shown in Table 2 was due to the temperature rise in the cell suspension by $3.5\pm0.1^{\circ}  $C.
-This was confirmed in sham-exposure experiments and experiments with incubation of cells for 40 min under the corresponding temperature conditions."
-
-\end{quote}
 

### 2021-01-13 documents/background.tex
scan-converter

@@
 
-\begin{autem}
+NATO Research Task Group 189 \cite{treatyelectromagnetic}
 
-{\Large {This has \textbf{nothing to do} with 5G communications.}}\\
-
-I am comfortable making such a definitive statement.
-
-The power levels required to even begin to observe this inactivation effect in practice are so high that, if conditions are not specifically tailored for clinical use, extensive burns will result within seconds.
-Even in this case, the effect is to eviscerate the virus, not to aid its spread.
-
-Moreover, these frequency bands have been in almost continuous use not long after Jagadish Chandra Bose 1894; the world has been bathed in high-power 10 GHz pulses at least since the commissioning of the first centimeter-wave weather radars in 1959.
-
-Countless far more prosaic explanations exist in the modern world, such as air travel.
-
-If you have any concerns regarding this statement, please contact me. I would be happy to discuss this.
-
-\end{autem}
-
-NATO Research Task Group 189 \cite{treatyelectromagnetic}
+zotero citation graph?
 
@@
 
+\footnote{``{[B]elow about 6 GHz, where EMFs penetrate deep into tissue (and thus require depth to be considered), it is useful to describe this in terms of “specific energy absorption rate” (SAR), which is the power absorbed per unit mass $(W/kg)$.
+Conversely, above 6 GHz, where EMFs are absorbed more superficially (making depth less relevant), it is useful to describe exposure in terms of the density of absorbed power over area $W/m^2$, which we refer to as “absorbed power density”}'' [ICNIRP 2020 \faExternalLink] }
+
 C95.1-2019, B.4.3 Rationale for pulsed RF field limits
@@
 Cancer treatment involving irreversible electroporation is in a different regime. Long pulses involving high conduction currents through needles. Cardiac arrest.
+
+Pakhomov \cite{Comparative} expose frog heart cells. No effects.
+
+In fact, this specific question is briefly noted in a comment by Saviot \cite{Comment2004} on
+
+We also would like to point out that these normal modes
+are damped when the virus particle is embedded inside a
+liquid...when the virus is inside water, for example, there is not much acoustic impedance mismatch at the surface.
+For this reason the normal modes will be broad and have short lifetimes.
+Therefore, the objective of killing viruses by sending out sound waves that resonate and destroy them is probably unworkable in such a configuration.
 
@@
 The X-band is also minimally absorbed by air, allowing action in the far-field and scaling to square-kilometer areas with single installations.
-
-\footnote{``{[B]elow about 6 GHz, where EMFs penetrate deep into tissue (and thus require depth to be considered), it is useful to describe this in terms of “specific energy absorption rate” (SAR), which is the power absorbed per unit mass $(W/kg)$.
-Conversely, above 6 GHz, where EMFs are absorbed more superficially (making depth less relevant), it is useful to describe exposure in terms of the density of absorbed power over area $W/m^2$, which we refer to as “absorbed power density”}'' [ICNIRP 2020 \faExternalLink] }
 
@@
 
+Of course, this is using an extremely sensitive assay, not an aggregate inactivation
+
 A previous report of microwave resonance, Grundler \cite{Sharp1983}, use a calorimeter, a stream of cooling water controlled to within 0.1 C, an interferometric thermometer, and can state definitively that at no point does the temperature inhomogeneity exceed 0.02 C.

### 2021-01-17 documents/background.tex
Progress

@@
 \begin{document}
+
+I was hoping I would have a definitive demonstration, so as to not redirect resources from more promising avenues.
+
+TRL 0
+
+(more data exists for influenza A; it is sufficiently structurally similar that ).
+
+We don't want a purely membrane-electroporative effect since the lipid membrane of the virus is similar to (derived from) the host cell and little selectivity can be expected.
+Unless the virus has a lower capacitance and charges faster than the cell.
+
+Also, the pore must stay open for long enough that damage is dealt to the virus.
+
+Viral electroporation specifically has been observed.
+
+Mizuno \cite{Inactivation1990} 100\% inactivate SVD Enterovirus (a 27 nm non-enveloped encapsidated ssRNA) and EHV (a 100 nm enveloped dsDNA) with 120 pulses, 500 or 600 nanoseconds each, at 3 MV/m.
+
+The thermal artifact  the energy \footnote{(43 cal/cc * (3 microliters)) / (3 milligrams * 4.2 J/(g K))}. The electrodes were un-insulated, so electrochemical effects are possible.
+
+Temperature rise
+
+at a slow field of approximately $10^7$ V/m, in the Vaccinia poxvirus (a 300 nm enveloped dsDNA virus). \cite{AC2017}. Interestingly, the same effect is not observed in T4 \cite{Manipulation2013}.
+
+\cite{comparative2003} discuss the relative inactivation of bacterial hosts and MS2 and PRD1 phages.
+
+Electric field has many more free variables than other treatments;
+
+best practices were not followed.
+
+A wave propagating into tissue with $e_r=70$ has a refractive index $n=\sqrt{\mu/\epsilon}$, and is transmitted as $\frac{2 n_1}{n_1 + n_2}$; therefore about 0.2x the electric field is transmitted.
+This is of no concern for waveguide or bolus applicators, since the reflected energy is captured and returned.
 
@@
 thermal interaction, for pulses shorter than 100 ms which suggested that neither the peak E-field limit in the
-IEEE C95.1TM-2005 safety standard nor the proposed limit in the Directive 2004/40/EC [33] (subsequently
-promulgated as 2013/35/EU [34]) have scientific basis.
+IEEE C95.1-2005 safety standard [n.b.
+4.3, Table 9, subsection e.
+peak E field 100 kV/m] nor the proposed limit in the Directive 2004/40/EC [33] (subsequently promulgated as 2013/35/EU [34]) have scientific basis.
 
-The group noted that physical laws governing the propagation of E-fields in air already limit the maximum allowable peak E-field at ~3 MV/m (air breakdown).
+" physical laws governing the propagation of E-fields in air already limit the maximum allowable peak E-field at ~3 MV/m (air breakdown).
 Current research efforts by members to expose biological organism(s), tissues, and cells to environmental
-fields up to this magnitude have been unable to elicit an acute biological response.
+fields up to this magnitude have been unable to elicit an acute biological response."
 
-\footnote{``{[B]elow about 6 GHz, where EMFs penetrate deep into tissue (and thus require depth to be considered), it is useful to describe this in terms of “specific energy absorption rate” (SAR), which is the power absorbed per unit mass $(W/kg)$.
-Conversely, above 6 GHz, where EMFs are absorbed more superficially (making depth less relevant), it is useful to describe exposure in terms of the density of absorbed power over area $W/m^2$, which we refer to as “absorbed power density”}'' [ICNIRP 2020 \faExternalLink] }
+\footnote{A note on units, from ICNIRP: ``{[B]elow about 6 GHz, where EMFs penetrate deep into tissue (and thus require depth to be considered), it is useful to describe this in terms of “specific energy absorption rate” (SAR), which is the power absorbed per unit mass $(W/kg)$.
+Conversely, above 6 GHz, where EMFs are absorbed more superficially (making depth less relevant), it is useful to describe exposure in terms of the density of absorbed power over area $W/m^2$, which we refer to as “absorbed power density”}''.
+}
+
+A provisional limit of 100 kV/m; the standard now that the fourier transform instantaneous pulse energy must not exceed 1/5 the energy over some specified averaging time.
+
+C95.1-2005
+
+When the waveform of the external electric field is non-sinusoidal, such as with pulsed or mixed frequency
+waveforms, the rms value of the spatially averaged external field shall conform to the MPEs of Table 4, and
+also to either of the criteria stated in 4.1.2.4.1 and 4.1.2.4.2.
 
@@
 
-Pakhomov \cite{Comparative} expose frog heart cells. No effects.
+Pakhomov \cite{Comparative} expose frog heart cells. No effects on pacemaker at 0.9 kV/m (although the field inside the ).
+
+Note: Not being biologists or microwave engineers, the trained reader may find that we are too verbose in simple technique and not in another.
+
+\begin{fquote}[Saviot][ \cite{Comment2004}]
+	We also would like to point out that these normal modes are damped when the virus particle is embedded inside a liquid...when the virus is inside water, for example, there is not much acoustic impedance mismatch at the surface.
+For this reason the normal modes will be broad and have short lifetimes.
+Therefore, the objective of killing viruses by sending out sound waves that resonate and destroy them is probably unworkable in such a configuration.
+\end{fquote}
 
@@
 
-We also would like to point out that these normal modes
-are damped when the virus particle is embedded inside a
-liquid...when the virus is inside water, for example, there is not much acoustic impedance mismatch at the surface.
-For this reason the normal modes will be broad and have short lifetimes.
-Therefore, the objective of killing viruses by sending out sound waves that resonate and destroy them is probably unworkable in such a configuration.
+Perilla \cite{}, in a trustworthy explicitly solvated all-atom MD simulation, describe a few surface-wave modes.
+
+electropermeabilization
 
@@
 
+add "timeline"
+
 \subsection{Liburdy's oxygen-dependent lipid leakage}
@@
 Unfortunately, these results appear to have failed replication \cite{No2011}. In any case, inactivation requires a very long duration of exposure; unlikely to be of great clinical use.
-
-Ultrafast femtosecond laser pulses
 
@@
 Notice that a non-zero resonant frequency
-requires
-ωR 6= 0 ⇒ β < ω/√
-2. (49)
-That is, the oscillator must be sufficiently under-damped in order to exhibit a
-resonance response
+requires $\beta = b/(2m) \i-t \sqrt{2}$ \cite{Driven}
 
@@
 
+Matzumoto \cite{Inactivation1991} find that in one case, an arc was struck within the medium, and that the UV light produced was sufficient to inactivate the organism.
+
 Microwave engineering is, itself  difficult. What type of attenuator you use?

### 2021-01-17 documents/paper.tex
Progress

@@
 
-Industry Canada limits on the instantaneous electric field anywhere inside the body are $1.35 \times 10^-4$ V/m * Hz ()\cite{RSS1022015}, Table 4), $0.81 \times 10^6$ V / m \@ 6 GHz to $1.2 \times 10^6$ / m \@ 9 GHz
+Industry Canada only appeaars to offer an instantaneous limit at $1.35 \times 10^-4$.
 
@@
 
+\subfile{viscosity}
+
 \subfile{supplemental}

### 2021-01-18 documents/background.tex
Pulse generator

@@
 
+Regurgitating Yang et al's line of reasoning, with a few; they study a 1 kV/m, 15 minute exposure, whereas we are concerned with a 3 MV/m, 500 picosecond regime.
+
+T4 capsid withstands a pressure differential of more than 30 atmospheres, crystallizing the genome packed within. \cite{Osmotic2003}
+
 (more data exists for influenza A; it is sufficiently structurally similar that ).
@@
 
-Viral electroporation specifically has been observed.
+Electroporation of viral membranes and capsids has been observed.
 
@@
 
-The thermal artifact  the energy \footnote{(43 cal/cc * (3 microliters)) / (3 milligrams * 4.2 J/(g K))}. The electrodes were un-insulated, so electrochemical effects are possible.
+The thermal artifact cannot necessarily be discounted.
+The energy \footnote{(43 cal/cc * (3 microliters)) / (3 milligrams * 4.2 J/(g K))}.
+The electrodes were un-insulated, so electrochemical effects are possible.
 
-Temperature rise
+Interestingly
 
-at a slow field of approximately $10^7$ V/m, in the Vaccinia poxvirus (a 300 nm enveloped dsDNA virus). \cite{AC2017}. Interestingly, the same effect is not observed in T4 \cite{Manipulation2013}.
-
-\cite{comparative2003} discuss the relative inactivation of bacterial hosts and MS2 and PRD1 phages.
+Madiyar observe rapid permeabilization at a field of approximately $10^7$ V/m, in the Vaccinia poxvirus (a 300 nm enveloped dsDNA virus).
+\cite{AC2017}.
+Interestingly, the same effect is not observed in T4 \cite{Manipulation2013}.
 
@@
 
-A wave propagating into tissue with $e_r=70$ has a refractive index $n=\sqrt{\mu/\epsilon}$, and is transmitted as $\frac{2 n_1}{n_1 + n_2}$; therefore about 0.2x the electric field is transmitted.
-This is of no concern for waveguide or bolus applicators, since the reflected energy is captured and returned.
+\footnote{A wave propagating into tissue with $\epsilon=70$ has a refractive index $n=\sqrt{\mu/\epsilon}$, and is transmitted as $\frac{2 n_1}{n_1 + n_2}$.
+This is of no concern for waveguide or bolus applicators, since the reflected energy is captured and returned.}
 
@@
 
+In fact, this specific question is briefly noted in a comment by Saviot \cite{Comment2004} on
+
 \begin{fquote}[Saviot][ \cite{Comment2004}]
@@
 \end{fquote}
-
-In fact, this specific question is briefly noted in a comment by Saviot \cite{Comment2004} on
 
@@
 
+Electrolysi
+
+\cite{comparative2003} discuss the relative inactivation of bacterial hosts and MS2 and PRD1 phages.
+
+\subsection{Artifacts in past absorption spectroscopy experiments, and the subsequent development and debunking of non-classical damping hypotheses}
+
+Edwards et al in 1984 and 1985 measured the reflection from an open-ended coaxial line dipped in DNA solution and found that DNA appeared to have a resonance-like peak.
+
+Such an effect is so unexpected - Bigio et al describe it as “astonishing”.
+Edwards hypothesized that the outer hydration layers could have a sort of elastic, non-viscous isolating effect.
+This result seems to have triggered a large amount of work to model this interaction, and various other interactions, in an attempt to explain the observed resonance.
+
+Footnote [At first blush, such an explanation does not seem unreasonable.
+In the case of the virus, for instance, the expected amplitude of oscillation for which this mechanism applies is on the order of one water molecule (~0.1 nm).
+
+Treating the interaction between the first few solvent layers surrounding some biological structure is indeed quite difficult; we encountered this in trying to setup MD This can be seen in [MD paper], so it is reasonable that continuum-like damping assumptions might break down.
+
+In the case of a uniform rotating sphere, for instance, the [Einstein - ?] viscous drag force diverges from the continuum hypothesis toward zero.]
+
+This really shouldn’t be treated classically, either - Frolich
+
+\lettrine{U}nfortunately for these hypotheses, Foster 1986, replicating Edwards’ coaxial line method with a more rigorous error analysis on plus an equally rigorous transmission-line absorption, and Bigio in 1993, an ingenious thermo-optical technique, quite definitively demonstrate - to absurd precision -  that the previous results were a characteristic artifact of coaxial-line spectrometry, and that DNA does not have any resonance mode at any microwave frequency.
+
+In Bigio’s words “Extreme care”. Because it involves a differential measurement of two samples.
+
+Hagmann and Gandhi \cite{Substitution1982}
+
+For a 0.5% tolerance in the frequency of a dielectric resonator (which), it must be machined to an accuracy of less than 0.05 mm.
+
+https://exxelia.com/uploads/PDF/e6000-v1.pdf
+
+In the case of our crude, amateurish equipment, by making completely justifiable changes in calibration and post-processing correction for thermal drift, normalization, etc, we could produce a resonance mode at almost any frequency we liked.
+We were able to produce many candidate peaks even in pure water.
+
+Liu and Yang use a coplanar waveguide, and offer hydration layers along the lines of Edwards as a theoretical basis.
+
+However, as Foster et al demonstrated, there is nothing necessarily wrong with VNA-based dielectric spectroscopy if it is well conducted.
+The Sun group seem very competent experimenters, and the experiments are very well conducted; but history would seem to suggest that we take some degree of caution.
+
+\subsection{Thermal controls}
+
+To illustrate how sensitive this research is, [Chemeris 2004] mention:
+
+\begin{quote}
+
+	The increase in DNA damage after exposure of cells to HPPP EMF shown in Table 2 was due to the temperature rise in the cell suspension by $3.5\pm0.1^{\circ}  $C.
+This was confirmed in sham-exposure experiments and experiments with incubation of cells for 40 min under the corresponding temperature conditions."
+
+\end{quote}
+
+Of course, this is using an extremely sensitive assay, not an aggregate inactivation
+
+A previous report of microwave resonance, Grundler \cite{Sharp1983}, use a calorimeter, a stream of cooling water controlled to within 0.1 C, an interferometric thermometer, and can state definitively that at no point does the temperature inhomogeneity exceed 0.02 C.
+
+The experiments of the Sun group
+
+An electric field necessarily dissipates energy in the surrounding solvent, and
+
+In inevitable temperature rise as a confounding factor.
+
+As any researchers who have scalded their mouths on a cheap dinner may know, microwave irradiation can produce unintuitive temperature gradients, with local hot-spots that can be difficult to measure directly.
+
+Kozempel \cite{Preliminary1997} and \cite{Inactivationa}.
+They take great pains to map the temperature profile using a fiber-optic thermometer; use thermographic indicators; and find substantial, almost complete inactivation of {\it Pediococcus sp.} with a measured discharge temperature of only 40 C.
+
+This is a fascinating result, and one which should be compared to the existing literature and very carefully replicated to isolate the mechanism.
+However, unless it is suggested that {\it Pediococcus sp.} also exhibits a confined microwave resonance of the same nature, it appears that periodic temperature measurements within the physiological range are not necessarily a sufficiently stringent control to definitively {\it isolate} resonant effects from other mechanisms.
+
+Conversely, if temperature control is not possible, the temperature can be allowed to rise so long as a positive control is present in which
+
+In Gandhi \cite{Basic1983}, nichrome heaters and copper-constantan thermocouples are used to generate the same temperature-time profile in both the treatment and this positive control to within 0.02 C, finding no effect.
+
+Burton\cite{Effects1950} describe the use of thermochromic pigments to examine heating profiles. Using low-frequency exposure, they are able to produce localized regions in excess of 50 C.
+
+[Vj] mention the importance of precise dosimetry. Even simple structures can produce hot-spots 
+Yang et al use both a plastic cuvette, and a single drop of solution on a glass slide; in either case, a sharp change dielectric constant is present.
+
+We do not intend to denigrate the work or otherwise cast aspersions on the authors of the mentioned papers; their experiment extremely well-designed and performed.
+
+However, since the result is unexpected, we would like to mention a few means by which the effect described could be achieved without strong non-thermal coupling.
+
+\begin{quote}
+
+	To confirm that our observation is not due to the microwave thermal heating effect, we had monitored the sample temperature change during the microwave illumination experiments with a radiated power density of 486W/m2 at a frequency of 6GHz by using an infrared thermal imaging camera with a temperature accuracy of 0.05°C (CHCT, P384-20).
+The temperature rise after 15 minutes radiation was 7°C, from 27.5°C up to 34.5°C.
+We thus exclude the possible contribution of microwave thermal heating effect to inactivation H3N2 viruses under our experimental condition.
+
+\end{quote}
+
+The frequency-dependent inactivation seen in Figure 4b of \cite{Efficient2015} is difficult to explain without invoking non-thermal mechanisms.
+Only one  It is not mentioned how this applied power level was measured.
+
+The QPJ-06183640 amplifier in question is not available on the supplier's website \cite{Microwaved} has gain flatness of 3.5 dB over 6-12 GHz - just over 1 octave.
+The amplifier used in [Hung] is not mentioned; because the frequency range mentioned (6 GHz to 18 GHz) is the same as that of the amplifier, we assume the same amplifier was used.
+
+If the amplifier happened to be matched better at 8 GHz than 12 GHz.
+
+If the output power was calculated based on the input power (which appears to have been done) rather than being measured in free-space, a shape very similar to that seen will be formed.
+
+Similarly, the gain of the EM-6969 antenna\cite{EM6969} varies from 17 dBi to 21 dBi over the frequency range in Figure 3.
+
+However, that the spectra of all these effects would combine to produce a peak at precisely the resonant frequency determined by the entirely different microwave cuvette is highly implausible; and so Figure 4b really does seem to be good evidence of such an effect.
+
+\subsection{Other artifacts}
+
+Bergqvist \cite{Effect1994a} find that the permeabilizing of their liposomes was not due to microwave exposure, but apparently a very peculiar interaction with the Teflon dish that was used only for positive microwave trials.
+Therefore, every part of the experimental protocol should be maintained precisely identical for non-sham and thermal sham trials.
+
+Some research has been discounted due to attenuators that leak high
+
+Matzumoto \cite{Inactivation1991} find that in one case, an arc was struck within the medium, and that the UV light produced was sufficient to inactivate the organism.
+
+\subsection{Meta issues with the field}
+
+\footnotetext{
+It is apparently easy to draw the wrong conculsion from a funnel plot, however. Here's one example of a flawed analysis: http://ies.fsv.cuni.cz/sci/publication/show/id/5277/lang/cs
+
+Thanks to James Picone https://skeptics.stackexchange.com/a/49751/ for the analysis.
+}
+
+Publication bias in the positive direction.
+A p=0.001.
+Something along an anthropic principle.
+In effect, the literature selects for causes of a false positive that would be expected to be an extremely improbable set of circumstances;
+
+anthropic principle
+
+\subsection{Raman spectroscopy}
+
+Very recently, Burkhartsmeyer \cite{Optical2020} have published data replicating the findings using a single-particle Raman spectroscopy technique.
+We have not examined these claims in detail, but they are good evidence.
+
+Non-photothermal optical Raman methods can also apparently synthesize artifacts - see unpublished, personal communication with Taylor \cite{mechanisms1981}.
+
 Previous works (Liu et al, ) appear to demonstrate that several species of viruses exhibit an anomalous dielectric relaxation time of $> 75 \text{ ps}$, as opposed to $<< 20 \text{ ps}$ \footnotemark measured in the structures of human tissue.\\
@@
 
-\subsection{Artifacts in past absorption spectroscopy experiments, and the subsequent development and debunking of non-classical damping hypotheses}
-
-Edwards et al in 1984 and 1985 measured the reflection from an open-ended coaxial line dipped in DNA solution and found that DNA appeared to have a resonance-like peak.
-
-Such an effect is so unexpected - Bigio et al describe it as “astonishing”.
-Edwards hypothesized that the outer hydration layers could have a sort of elastic, non-viscous isolating effect.
-This result seems to have triggered a large amount of work to model this interaction, and various other interactions, in an attempt to explain the observed resonance.
-
-Footnote [At first blush, such an explanation does not seem unreasonable.
-In the case of the virus, for instance, the expected amplitude of oscillation for which this mechanism applies is on the order of one water molecule (~0.1 nm).
-
-Treating the interaction between the first few solvent layers surrounding some biological structure is indeed quite difficult; we encountered this in trying to setup MD This can be seen in [MD paper], so it is reasonable that continuum-like damping assumptions might break down.
-
-In the case of a uniform rotating sphere, for instance, the [Einstein - ?] viscous drag force diverges from the continuum hypothesis toward zero.]
-
-This really shouldn’t be treated classically, either - Frolich
-
-\lettrine{U}nfortunately for these hypotheses, Foster 1986, replicating Edwards’ coaxial line method with a more rigorous error analysis on plus an equally rigorous transmission-line absorption, and Bigio in 1993, an ingenious thermo-optical technique, quite definitively demonstrate - to absurd precision -  that the previous results were a characteristic artifact of coaxial-line spectrometry, and that DNA does not have any resonance mode at any microwave frequency.
-
-In Bigio’s words “Extreme care”. Because it involves a differential measurement of two samples.
-
-Hagmann and Gandhi \cite{Substitution1982}
-
-For a 0.5% tolerance in the frequency of a dielectric resonator (which), it must be machined to an accuracy of less than 0.05 mm.
-
-https://exxelia.com/uploads/PDF/e6000-v1.pdf
-
-In the case of our crude, amateurish equipment, by making completely justifiable changes in calibration and post-processing correction for thermal drift, normalization, etc, we could produce a resonance mode at almost any frequency we liked.
-We were able to produce many candidate peaks even in pure water.
-
-Liu and Yang use a coplanar waveguide, and offer hydration layers along the lines of Edwards as a theoretical basis.
-
-However, as Foster et al demonstrated, there is nothing necessarily wrong with VNA-based dielectric spectroscopy if it is well conducted.
-The Liu and Yang group seem very competent experimenters, and the experiments are very well conducted; but history would seem to suggest that we take some degree of caution.
-
-\subsection{Thermal controls}
-
-To illustrate how sensitive this research is, [Chemeris 2004] mention:
-
-\begin{quote}
-
-	The increase in DNA damage after exposure of cells to HPPP EMF shown in Table 2 was due to the temperature rise in the cell suspension by $3.5\pm0.1^{\circ}  $C.
-This was confirmed in sham-exposure experiments and experiments with incubation of cells for 40 min under the corresponding temperature conditions."
-
-\end{quote}
-
-Of course, this is using an extremely sensitive assay, not an aggregate inactivation
-
-A previous report of microwave resonance, Grundler \cite{Sharp1983}, use a calorimeter, a stream of cooling water controlled to within 0.1 C, an interferometric thermometer, and can state definitively that at no point does the temperature inhomogeneity exceed 0.02 C.
-
-The experiments of the Sun group
-
-An electric field necessarily dissipates energy in the surrounding solvent, and
-
-In inevitable temperature rise as a confounding factor.
-
-As any researchers who have scalded their mouths on a cheap dinner may know, microwave irradiation can produce unintuitive temperature gradients, with local hot-spots that can be difficult to measure directly.
-
-Kozempel \cite{Preliminary1997} and \cite{Inactivationa}.
-They take great pains to map the temperature profile using a fiber-optic thermometer; use thermographic indicators; and find substantial, almost complete inactivation of {\it Pediococcus sp.} with a measured discharge temperature of only 40 C.
-
-This is a fascinating result, and one which should be compared to the existing literature and very carefully replicated to isolate the mechanism.
-However, unless it is suggested that {\it Pediococcus sp.} also exhibits a confined microwave resonance of the same nature, it appears that periodic temperature measurements within the physiological range are not necessarily a sufficiently stringent control to definitively {\it isolate} resonant effects from other mechanisms.
-
-Conversely, if temperature control is not possible,
-
-In Gandhi \cite{Basic1983}, nichrome heaters and copper-constantan thermocouples are used to generate the same temperature-time profile in both the treatment and the control to within 0.02 C, finding no effect.
-
-Burton\cite{Effects1950} describe the use of thermochromic pigments to examine heating profiles. Using low-frequency exposure, they are able to produce localized regions in excess of 50 C.
-
-\subsection{Other artifacts}
-
-Bergqvist \cite{Effect1994a} find that the permeabilizing of their liposomes was not due to microwave exposure, but apparently a very peculiar interaction with the Teflon dish that was used only for positive microwave trials.
-Therefore, every part of the experimental protocol should be maintained precisely identical for non-sham and thermal sham trials.
-
-Some research has been discounted due to attenuators that leak high
-
-Matzumoto \cite{Inactivation1991} find that in one case, an arc was struck within the medium, and that the UV light produced was sufficient to inactivate the organism.
-
-Microwave engineering is, itself  difficult. What type of attenuator you use?
-
-\subsection{Meta issues with the field}
-
-\footnotetext{
-It is apparently easy to draw the wrong conculsion from a funnel plot, however. Here's one example of a flawed analysis: http://ies.fsv.cuni.cz/sci/publication/show/id/5277/lang/cs
-
-Thanks to James Picone https://skeptics.stackexchange.com/a/49751/ for the analysis.
-}
-
-Publication bias in the positive direction.
-A p=0.001.
-Something along an anthropic principle.
-In effect, the literature selects for causes of a false positive that would be expected to be an extremely improbable set of circumstances;
-
-anthropic principle
-
-\subsection{Raman spectroscopy}
-
-Very recently, Burkhartsmeyer \cite{Optical2020} have published data replicating the findings using a single-particle Raman spectroscopy technique.
-We have not examined these claims in detail, but they are good evidence.
-
-Non-photothermal optical Raman methods can also apparently synthesize artifacts - see unpublished, personal communication with Taylor \cite{mechanisms1981}.
-
-T4 capsid withstands a pressure differential of more than 30 atmospheres, crystallizing the genome packed within.
-
-\cite{Osmotic2003}
-
 \end{document}

### 2021-01-18 documents/supplemental.tex
Pulse generator

@@
 Things heating up at the Microwave Safety fandom.
-
-\clearpage
-\rule{\linewidth}{0.2pt}
-
-We do not intend to denigrate the work or otherwise cast aspersions on the authors of the mentioned papers; their experiment extremely well-designed and performed.
-
-However, since the result is unexpected, we would like to mention a few means by which the effect described could be achieved without strong non-thermal coupling.
-
-\begin{quote}
-
- To confirm that our observation is not due to the microwave thermal heating effect, we had monitored the sample temperature change during the microwave illumination experiments with a radiated power density of 486W/m2 at a frequency of 6GHz by using an infrared thermal imaging camera with a temperature accuracy of 0.05°C (CHCT, P384-20).
-The temperature rise after 15 minutes radiation was 7°C, from 27.5°C up to 34.5°C.
-We thus exclude the possible contribution of microwave thermal heating effect to inactivation H3N2 viruses under our experimental condition.
-
-\end{quote}
-
-The frequency-dependent inactivation result in Figure 4b of \cite{Efficient2015} is difficult to explain without invoking non-thermal mechanisms.
-Only one  It is not mentioned how this applied power level was measured.
-
-The amplifier in question is not available on the supplier's website \cite{Microwaved} has gain flatness of 3.5 dB over 6-12 GHz - just over 1 octave.
-The amplifier used in [Hung] is not mentioned; because the frequency range mentioned (6 GHz to 18 GHz) is the same as that of the amplifier, we assume the same amplifier was used.
-
-If the amplifier happened to be matched better at 8 GHz than 12 GHz.
-
-QPJ-06183640
-
-Similarly, the gain of the EM-6969 antenna\cite{EM6969} varies from 17 dBi to 21 dBi over the frequency range in Figure 3.
-
-However, that the spectra of all these effects would combine to produce a peak at precisely the resonant frequency determined by the entirely different microwave cuvette is highly implausible; and so Figure 4b really does seem to be good evidence of such an effect.
 

### 2021-01-18 documents/background.tex
progress

@@
 Regurgitating Yang et al's line of reasoning, with a few; they study a 1 kV/m, 15 minute exposure, whereas we are concerned with a 3 MV/m, 500 picosecond regime.
+
+\begin{multicols}{1}
 
@@
 
-Mizuno \cite{Inactivation1990} 100\% inactivate SVD Enterovirus (a 27 nm non-enveloped encapsidated ssRNA) and EHV (a 100 nm enveloped dsDNA) with 120 pulses, 500 or 600 nanoseconds each, at 3 MV/m.
+Mizuno \cite{Inactivation1990} inactivate SVD Enterovirus (a 27 nm non-enveloped encapsidated ssRNA) and EHV (a 100 nm enveloped dsDNA) with 100\% effectiveness at 120 pulses, about 500 nanoseconds each, at 3 MV/m.
 
@@
 
+Is this resonance of Q=2 really of any practical use?
+
 In fact, this specific question is briefly noted in a comment by Saviot \cite{Comment2004} on
@@
 
-Perilla \cite{}, in a trustworthy explicitly solvated all-atom MD simulation, describe a few surface-wave modes.
+Perilla \cite{}, in a trustworthy explicitly solvated all-atom MD simulation, describe a few surface-wave modes around 10 MHz, but don't report (or don't consider) modes in the GHz.
 
 electropermeabilization
-
-H. H. Williams: Furious activity is no substitute for understanding.
 
@@
 , non-chemical technique, harmless for continuous exposure to tissue, which can sterilize air and surfaces alike, including skin, eyes, and within hair; it evolves no ozone, can readily be generated with \$1 USD - scale devices, acts instantaneously, and - perhaps most critically - could be made to act {\bf within infected tissues}.
-
-The X-band is also minimally absorbed by air, allowing action in the far-field and scaling to square-kilometer areas with single installations.
 
@@
 
+\end{multicols}
+
 \end{document}

### 2021-01-18 documents/paper.tex
Pulse generator
progress

@@
 
-Industry Canada only appeaars to offer an instantaneous limit at $1.35 \times 10^-4$.
+Industry Canada only appears to offer an instantaneous limit at $1.35 \times 10^-4$.
 
@@
 
-[Vj] mention the importance of precise dosimetry. Even simple structures can produce hot-spots 
-Yang et al use both a plastic cuvette, and a single drop of solution on a glass slide; in either case, a sharp change dielectric constant is present.
-
 To the extreme, some papers have used
@@
 
-\clearpage
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-{\Large Microwave Musings}\\
-\begin{multicols}{1}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\noindent\fbox{\parbox{\linewidth}{
-	Toolchain:
-	\begin{itemize}
-	\item Failed oscillator feedback-loop optimization toolchain: QUCS 0.0.20 + python-qucs + scipy's 'basinhopper'
-	\item Successful A slightly modified ngspice + ngspyce + pyEVTK
-	\item gprMax for FDTD EM simulation
-	\item KiCAD, wcalc, scikit-rf, ngspice
-	\end{itemize}
-}}
-%
-
-Microwave design has a reputation for being the purview of wizards. Modern RF software packages like HFSS, Microwave Office, Agilent's ADS, and Mathworks' RF toolbox, for which; component models
-
-Luckily, this project falls perfectly within the subset of microwave technologies that do not require a goatee.
-The vast majority of the behavior of most circuits can be accurately modelled with the very same SPICE tools as one would use at low frequencies.
-With judicious application of reference designs, it seems to be possible to design
-
-Before about 2005, however, it seems to have been somewhat the norm to write a simple numerical code to solve the problem at hand based on underlying principles.
-
-We are also aided by the fact that what took a \$150,000 computing cluster a single decade ago can now be done in a few minutes by a single budget GPU.
-
-\end{multicols}
-
-\clearpage
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-{\Large Interference}\\
-\begin{multicols}{1}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-{\Large Mass production}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Almost all components on the device can be replicated with fully vertically-integrated first-principles. Capacitors can be
-
-If this 'electromagnetic mask' form is the ideal (not nearly),
-
-The largest RFID plants can produce
-
-a minimum of 5 GaAs or SiGe:C transistors will be required. Without SOI or, it does not appear that
-
-As a lower bound, there are 1 million hospital beds in the U.S. [AHA 2018]; and as an upper bound obtaining global herd immunity would take 1.75 billion units.
-
-It is difficult to determine the supply capacity for these semiconductor processes; information is not forthcoming from the manufacturers.
-Fermi estimates \footnote{GaAs MMIC market of \$2.2 Bn USD / random sample of MMIC prices = about 2 Bil devices / yr, 3e9 wifi connected devices produced each year,}
-
-It is possible to use common Si-based devices at these frequencies, especially with second-harmonic techniques [Winch 1982].
-However, obtaining the required gain and output power is not a trivial matter.
-
-The techniques and equipment required to produce these devices are extremely complex; load-lock UHV,
-
-Figures are not forthcoming,
-
-Given the supply difficulties of comparatively simple materials such as Tyvek at pandemic scales, it is difficult to imagine that RF semiconductor production can be immediately re-tasked and scaled to this degree.
-
-\paragraph{\textbf{Vacuum RF triode}}\
-
-Especially combined with an integrated titanium sorption pump,
-
-One concern is the large filament heater power, which prevents the use of low-cost button cells for power.
-Use of cold-cathode field-emitter arrays would alleviate this issue, but at the cost of complexity.
-
-Small tungsten incandescent lights are available down to 0.05 watts. With a suitable high-efficiency cathode coating, a pulsed heater power of less than 0.02
-
-\end{multicols}
-
-\clearpage
-
 %\paragraph{}

### 2021-01-18 documents/personal_device.tex
progress

@@
 
+\end{multicols}
+
+\clearpage
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+{\Large Interference}\\
+\begin{multicols}{1}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+{\Large Mass production}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Almost all components on the device can be replicated with fully vertically-integrated first-principles. Capacitors can be
+
+If this 'electromagnetic mask' form is the ideal (not nearly),
+
+The largest RFID plants can produce
+
+a minimum of 5 GaAs or SiGe:C transistors will be required. Without SOI or, it does not appear that
+
+As a lower bound, there are 1 million hospital beds in the U.S. [AHA 2018]; and as an upper bound obtaining global herd immunity would take 1.75 billion units.
+
+It is difficult to determine the supply capacity for these semiconductor processes; information is not forthcoming from the manufacturers.
+Fermi estimates \footnote{GaAs MMIC market of \$2.2 Bn USD / random sample of MMIC prices = about 2 Bil devices / yr, 3e9 wifi connected devices produced each year,}
+
+It is possible to use common Si-based devices at these frequencies, especially with second-harmonic techniques [Winch 1982].
+However, obtaining the required gain and output power is not a trivial matter.
+
+The techniques and equipment required to produce these devices are extremely complex; load-lock UHV,
+
+Figures are not forthcoming,
+
+Given the supply difficulties of comparatively simple materials such as Tyvek at pandemic scales, it is difficult to imagine that RF semiconductor production can be immediately re-tasked and scaled to this degree.
+
+\paragraph{\textbf{Vacuum RF triode}}\
+
+Especially combined with an integrated titanium sorption pump,
+
+One concern is the large filament heater power, which prevents the use of low-cost button cells for power.
+Use of cold-cathode field-emitter arrays would alleviate this issue, but at the cost of complexity.
+
+Small tungsten incandescent lights are available down to 0.05 watts. With a suitable high-efficiency cathode coating, a pulsed heater power of less than 0.02
+
+\end{multicols}
+
+The X-band is also minimally absorbed by air, allowing action in the far-field and scaling to square-kilometer areas with single installations.
+
+\clearpage
+
 \end{document}

### 2021-01-18 documents/supplemental.tex
progress

@@
 
-\paragraph{Timeline}
+\clearpage
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+{\Large Microwave Musings}\\
+\begin{multicols}{1}
+	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+	\noindent\fbox{\parbox{\linewidth}{
+			Toolchain:
+			\begin{itemize}
+				\item Failed oscillator feedback-loop optimization toolchain: QUCS 0.0.20 + python-qucs + scipy's 'basinhopper'
+				\item Successful A slightly modified ngspice + ngspyce + pyEVTK
+				\item gprMax for FDTD EM simulation
+				\item KiCAD, wcalc, scikit-rf, ngspice
+			\end{itemize}
+	}}
+	%
+
+	Microwave design has a reputation for being the purview of wizards. Modern RF software packages like HFSS, Microwave Office, Agilent's ADS, and Mathworks' RF toolbox, for which; component models
+
+	Luckily, this project falls perfectly within the subset of microwave technologies that do not require a goatee.
+The vast majority of the behavior of most circuits can be accurately modelled with the very same SPICE tools as one would use at low frequencies.
+With judicious application of reference designs, it seems to be possible to design
+
+	Before about 2005, however, it seems to have been somewhat the norm to write a simple numerical code to solve the problem at hand based on underlying principles.
+
+	We are also aided by the fact that what took a \$150,000 computing cluster a single decade ago can now be done in a few minutes by a single budget GPU.
+
+\section{Timeline}
 

### 2021-01-19 electronics/simple_fdtd/run/microfluidic_coplanar.py
why's fdtd broken?

@@ -1,0 +1,165 @@
+# import torch
+# import numpy as np
+# import gc
+# torch.cuda.empty_cache()
+#
+# gc.collect()
+
+# np.seterr(all='raise')
+# torch.autograd.set_detect_anomaly(True)
+import fdtd_PCB_extensions as fd
+from fdtd_PCB_extensions import fdtd
+from fdtd_PCB_extensions import X,Y,Z, gaussian_derivative_pulse
+from scipy.constants import mu_0, epsilon_0
+import scipy.constants
+from math import sin, pi, pow, exp, sqrt
+import time
+import os
+import matplotlib.pyplot as plt
+import copy
+from scipy.signal import gausspulse
+import dill
+from pytexit import py2tex
+import pickle
+
+import numpy as np
+import math
+
+
+fdtd.set_backend("torch.cuda.float32")
+
+
+# fdtd.set_backend("numpy")
+
+#include store.py
+import sys
+sys.path.append('/home/arthurdent/covidinator/electronics/')
+import store
+
+os.system("rm dumps/*")
+os.system("rm data/*")
+
+#Polycarb. permittivity @ 10 GHz: 2.9 [10.6028/jres.071C.014] - conductivity is very low, no need for absorb.
+#Water permittivity @ 10 GHz: 65 - use AbsorbingObject
+
+substrate_thickness = 0.79e-3
+substrate_dielectric_constant = 4.4
+
+
+microstrip_width = 1e-3
+microstrip_length = 10e-3
+
+fluid_dielectric_constant = 65
+
+
+sim_width = 5e-3
+
+pcb = fd.PCB(40e-5, xy_margin=15, z_margin=15)
+fd.initialize_grid(pcb,int((sim_width)/pcb.cell_size),int((microstrip_length)/pcb.cell_size),
+                                int(0.0025/pcb.cell_size), courant_number = 0.4)
+
+fd.create_planes(pcb, 0.032e-3, 6e7)
+fd.create_substrate(pcb, substrate_thickness, substrate_dielectric_constant, 0.02, 9e9)
+
+
+z_slice = slice(pcb.component_plane_z,(pcb.component_plane_z+1))
+
+
+centerline = int((sim_width / pcb.cell_size ) / 2.0) + pcb.xy_margin
+
+
+#wipe copper
[…]

### 2021-01-19 electronics/simple_fdtd/fdtd_PCB_extensions/fdtd_PCB_extensions/visualize.py
still broken sources

@@ -41,12 +41,16 @@ def dump_to_vtk(pcb, filename, iteration, Ex_dump=False, Ey_dump=False, Ez_dump=
                     objects[obj.x.start:obj.x.stop, obj.y.start:obj.y.stop, obj.z.start:obj.z.stop] = obj.permittivity.cpu().numpy()
                 except:
                     objects[obj.x.start:obj.x.stop, obj.y.start:obj.y.stop, obj.z.start:obj.z.stop] = obj.permittivity.cpu().numpy()[:,:,:,0]
-                objects[cu_mask] = 2
+                # objects[cu_mask] = 2
             else:
                 objects[obj.x.start:obj.x.stop, obj.y.start:obj.y.stop, obj.z.start:obj.z.stop] = obj.permittivity
-                objects += cu_mask*2
+        # objects += cu_mask*2
 
         cellData['objects'] = objects
+
+
+    cellData['copper'] = cu_mask*2
+
 
     if(ports_dump):
         ports = np.zeros_like(E_copy[:,:,:,X])

### 2021-01-19 electronics/simple_fdtd/run/microfluidic_coplanar.py

@@ -47,14 +47,14 @@ substrate_dielectric_constant = 4.4
 
 
 microstrip_width = 1e-3
-microstrip_length = 20e-3
+microstrip_length = 4e-3
 
 fluid_dielectric_constant = 65
 
 
 sim_width = 4e-3
 
-pcb = fd.PCB(0.040e-3, xy_margin=13, z_margin=13)
+pcb = fd.PCB(0.05e-3, xy_margin=15, z_margin=15)
 fd.initialize_grid(pcb,int((sim_width)/pcb.cell_size),int((microstrip_length)/pcb.cell_size),
                                 int(0.0015/pcb.cell_size), courant_number = 0.4)
 
@@ -79,14 +79,21 @@ microstrip_gap = 0.2e-3 # distance to ground plane
 m_w_N = int((microstrip_width/2)/pcb.cell_size)
 
 #stitch ends of coplanar
-pcb.copper_mask[centerline+m_w_N+int(microstrip_gap/pcb.cell_size)+1, pcb.xy_margin,pcb.ground_plane_z_top:pcb.component_plane_z] = 1 # vias
-pcb.copper_mask[centerline-m_w_N-int(microstrip_gap/pcb.cell_size)-1, pcb.xy_margin,pcb.ground_plane_z_top:pcb.component_plane_z] = 1 # vias
-pcb.copper_mask[centerline+m_w_N+int(microstrip_gap/pcb.cell_size)+1, -pcb.xy_margin-1,pcb.ground_plane_z_top:pcb.component_plane_z] = 1 # vias
-pcb.copper_mask[centerline-m_w_N-int(microstrip_gap/pcb.cell_size)-1, -pcb.xy_margin-1,pcb.ground_plane_z_top:pcb.component_plane_z] = 1 # vias
+# pcb.copper_mask[centerline+m_w_N+int(microstrip_gap/pcb.cell_size)+1, pcb.xy_margin+2,pcb.ground_plane_z_top:pcb.component_plane_z] = 1 # vias
+# pcb.copper_mask[centerline-m_w_N-int(microstrip_gap/pcb.cell_size)-1, pcb.xy_margin+2,pcb.ground_plane_z_top:pcb.component_plane_z] = 1 # vias
+# pcb.copper_mask[centerline+m_w_N+int(microstrip_gap/pcb.cell_size)+1, -pcb.xy_margin-2,pcb.ground_plane_z_top:pcb.component_plane_z] = 1 # vias
[…]

### 2021-01-21 electronics/simple_fdtd/run/impedance_analyzer.py
Coplanar exposure cell working

@@ -6,7 +6,7 @@ import sys
 sys.path.append('/home/arthurdent/covidinator/electronics/')
 import store
 
-dill.load_session("microfluidic.pkl")
+dill.load_session(sys.argv[1])
 
 
 desired_res = 300 #100 points below F_max

### 2021-01-22 documents/background.tex
why's fdtd broken?
Coplanar exposure cell working
Delay line functioning great

@@
 TRL 0
+
+suggestive, especially because a model organism
 
@@
 Interestingly, the same effect is not observed in T4 \cite{Manipulation2013}.
+
+The field strengths are high enough to lead to Townsend breakdowns in air (if the duration is longer than the formative lag). In some sense, we are concerned with field magn
+
+Dielectric measurements on different proteins demonstrate that the slowest relaxation
+
+The very high voltage means that low-sensitivity diagnostics, like lithium niobate optical probes.
+Not having a suitable optical bench, an electron-beam probe, similar to a streak camera, itself similar in principle to scan-conversion digitizer tubes in Tek SCD and 7912 series transient digitizers.
+
+If a low voltage sensitivity is required, and because modern high-pixel-density CMOS sensors allow the required deflection and the entire structure to be minimized, these are simple to design and inexpensive (much of the complexity being in the slow-wave or travelling-wave structure which is usually required to match the signal velocity to the - slowing down light without affecting its properties or drawing power is an extremely difficult problem) and can offer sample rates in the terasamples/s and analog bandwidths , albeit with low vertical resolution.
+
+original von Ardenne
 

### 2021-01-22 electronics/simple_fdtd/run/microfluidic_coplanar.py

@@ -127,7 +127,7 @@ pcb.copper_mask[centerline-m_w_N:centerline+m_w_N, \
 #fluid
 conductivity_scaling = 1.0/(pcb.cell_size / epsilon_0) #again, flaport's thesis.
 #
-pcb.grid[centerline+m_w_N:(centerline+m_w_N+int(microstrip_gap/pcb.cell_size)), int((microstrip_length*0.25)/pcb.cell_size):int((microstrip_length*0.75)/pcb.cell_size), \
+pcb.grid[centerline+m_w_N:(centerline+m_w_N+int(microstrip_gap/pcb.cell_size))-1, int((microstrip_length*0.25)/pcb.cell_size):int((microstrip_length*0.75)/pcb.cell_size), \
             int(pcb.component_plane_z-(0.1e-3//pcb.cell_size)): pcb.component_plane_z+2 ] \
                         = fdtd.AbsorbingObject(conductivity=0.010*conductivity_scaling, permittivity=fluid_dielectric_constant, name="fluid")
 
@@ -143,7 +143,8 @@ voltages = np.array([])
 currents = np.array([])
 
 print_step = 500
-dump_step = 2e-12
+# dump_step = 2e-12
+dump_step = 1e-11
 
 prev_dump_time = 0
 
@@ -157,7 +158,7 @@ while(pcb.time < (2.0 * 2.0 * pi * f)):
         pcb.grid.E[pcb.copper_mask] = 0
 
 
-        source_voltage = normalized_gaussian_derivative_pulse(pcb,1e-9)
+        source_voltage = normalized_gaussian_derivative_pulse(pcb,0.1e-9)
         # source_voltage = gaussian_derivative_pulse(pcb, 4e-12, 32)/(26.804e9)
 
         # source_voltage = (pcb.time*f)/((pcb.time*f)+1) # smooth ramp
@@ -191,10 +192,10 @@ while(pcb.time < (2.0 * 2.0 * pi * f)):
 
         print(pcb.time)
         #
-        # if((dump_step and abs(pcb.time-prev_dump_time) > dump_step) or pcb.grid.time_steps_passed == 0):
-        #     #paraview gets confused if the first number isn't zero.
-        #     fd.dump_to_vtk(pcb,'dumps/test',pcb.grid.time_steps_passed)
-        #     prev_dump_time = pcb.time
+        if((dump_step and abs(pcb.time-prev_dump_time) > dump_step) or pcb.grid.time_steps_passed == 0):
[…]

### 2021-01-23 documents/background.tex
Dialogue

--- 2021-01-18 documents/background.tex
@@
 
+Note that it is possible that this has already been worked on. The last review was several months ago, and the literature is changing very rapidly.
+
 TRL 0
+
+suggestive, especially because a model organism
+
+An abundance of mechanisms exist to.
+Irritatingly, such mechanisms have almost universally been ruled out by careful experiment.
+Many entirely plausible mechanisms exist for which the only valid answer is that they simply do not occur in practice.
 
@@
 
+formal literature review; In particular no search criteria were defined.
+
+%
+\footnote{It may be useful to clarify 'non-thermal'; it caused us some confusion, as the proteins of the virion locally absorb energy and undoubtedly increase in temperature; indeed the same denaturation processes may occur.
+The key is that, when excited in this manner, the energies in the envelope are poorly modeled by a Maxwell-Boltzmann distribution; they are not given sufficient time to 'thermalize'.}
+%
+
+Additionally, other sterilization techniques may produce superior results with less faffing about and should be evaluated in the same context.
+For instance, data on far UV [Buonanno 2017] indicates safety.\\
+
+"Windows" of the same sort have been found, both in thermal and pulsed ultra-high-power UV Prodouz \cite{Use1987a}.
+
 (more data exists for influenza A; it is sufficiently structurally similar that ).
+
+Excellent theoretical arguments against the possibility of non-thermal effects can be found Adair \cite{Vibrational2002}, Adair \cite{Biological2002}, and Foster \cite{Viscous2000} on microtubules.
+
+Adair \cite{Biophysics2000} on Brillouin.
+
+\nameref{sec:viscousdamping}
+
+Data cannot be trusted implicitly. By time-domain spectrometry (a reasonably trustworthy technique), Miura \cite{Microwave1994} find
+
+Owrutsky Vibrational1994
 
@@
 
+The field strengths are high enough to lead to Townsend breakdowns in air (if the duration is longer than the formative lag). In some sense, we are concerned with field magn
+
+This idea, that resonances, is backed up by measurements by Gabriel; the slowest relaxation time in the microwave regime appear to be in the mammary glands, and.
+Small resonances will be disguised by the aggregation, however.
+
+Dielectric measurements on different proteins demonstrate that the slowest relaxation
+
 Electric field has many more free variables than other treatments;
@@
 best practices were not followed.
-
-\footnote{A wave propagating into tissue with $\epsilon=70$ has a refractive index $n=\sqrt{\mu/\epsilon}$, and is transmitted as $\frac{2 n_1}{n_1 + n_2}$.
-This is of no concern for waveguide or bolus applicators, since the reflected energy is captured and returned.}
 
@@
 
+\begin{fquote}[Wait][ \cite{treatyelectromagnetic}]
 HFM-189 found no published and replicated adverse health effects or biological mechanisms, beyond
@@
 IEEE C95.1-2005 safety standard [n.b.
-4.3, Table 9, subsection e.
+chapter 4.3, Table 9, subsection e.
 peak E field 100 kV/m] nor the proposed limit in the Directive 2004/40/EC [33] (subsequently promulgated as 2013/35/EU [34]) have scientific basis.
+\end{fquote}
 
@@
 
+\footnote{A wave propagating into tissue with $\epsilon_r=70$ has a refractive index $n=\sqrt{\mu_r/\epsilon_r}$, and is transmitted as $\frac{2 n_1}{n_1 + n_2}$.
+This is of no concern for waveguide or bolus applicators, since the reflected energy is captured and returned.}
+
 Cancer treatment involving irreversible electroporation is in a different regime. Long pulses involving high conduction currents through needles. Cardiac arrest.
 
-Pakhomov \cite{Comparative} expose frog heart cells. No effects on pacemaker at 0.9 kV/m (although the field inside the ).
+Pakhomov \cite{Comparative} expose frog heart cells, and find no effects on functioning pacemaker cells at 0.9 kV/m (although the field inside the waveguide may be lower).
 
-Note: Not being biologists or microwave engineers, the trained reader may find that we are too verbose in simple technique and not in another.
+Note: The author not being biologists or microwave engineers, the trained reader may find that we are too verbose in simple technique and methodology and not detailed in another.
 
@@
 
-\subsection{Tsen's femtosecond laser ISRU}
+\subsection{Coherent control and laser chemistry}
 
-Impulsive stimulated Raman scattering. We confess to not having studied these mechanisms in great detail. Does not directly act on 
-the vibrational mode; the optimal pulse duration is some small fraction of the period of the mode in question.
+Man \cite{Picosecond2016b} perform a trustworthy all-atom molecular dynamics simulation of .
+As with most molecular dynamics simulations, the applied field was enhanced by several orders of magnitude to an unrealistic 2 gigavolts per meter to make the reaction proceed fast enough to be captured without excessive computation time.
 
-Unfortunately, these results appear to have failed replication \cite{No2011}. In any case, inactivation requires a very long duration of exposure; unlikely to be of great clinical use.
+\subsection{Picosecond and femtosecond laser studies}
+
+A group of literature exists concerning the excitation of these modes with picosecond or femtosecond lasers.
+A pulse some 300 fs long and with a carrier of around 600 nm.
+Impulsive stimulated Raman scattering.
+We confess to not having studied these mechanisms in great detail.
+The pulse does not directly act on the vibrational mode; the optimal pulse duration is some small fraction of the period of the mode in question.
+
+M13 is a 880 nm by 6.6 nm rod \cite{M132015}.
+
+Dykeman \cite{Vibrational2009} perform an all-atom molecular dynamics simulation of ISRU of phage M13, albeit without a heat bath to accurately represent damping.
+An interesting result is that despite the broadband nature of the pulse, \char`~80\% of the pulse energy couples into only 5 modes, starting at approx.
+20 GHz.
+The binding energy is implied to be too high to explain the experimental results.
+
+Zhou \cite{Maximum2010} consider the optimal control theory for this problem.
+
+Unfortunately, the experimental results on M13 appear to have completely failed replication by Wigle \cite{No2011}, and those on lymphocytes do not agree with existing literature by two orders of magnitude \cite{Targeted2002}, observing that over 1 TW of incident power is required to reproduce the effects by .
+
+1 TW / (100 ps / 0.3 ps) = 3 GW
+
+In any case, inactivation through this mechanism appears to require a very long duration of exposure.
 
@@
 If the extensions made in our paper are valid, this is a non-ionizing, non-thermal
-%
-\footnote{It may be useful to define 'non-thermal'; it caused us some confusion.
-Certainly the proteins of the virion locally absorb energy and increase in temperature.
-The key is that, when excited in this manner, the energies in the envelope are poorly modeled by a Maxwell-Boltzmann distribution; they are not given sufficient time to 'thermalize'.
-In contrast, with typical 2.4 GHz microwave exposure, sterilization can only occur by aggregate heating of the fluid and tissue.}
-%
+
 , non-chemical technique, harmless for continuous exposure to tissue, which can sterilize air and surfaces alike, including skin, eyes, and within hair; it evolves no ozone, can readily be generated with \$1 USD - scale devices, acts instantaneously, and - perhaps most critically - could be made to act {\bf within infected tissues}.
@@
 the only analagous non-thermal mechansism we are aware of is electroporation; and that requires the diffusion of ionized sodium and potassium charge carriers through the membrane, which would seem to necessarily require a non-
-
-Laser
-
-Additionally, other sterilization techniques may produce superior results with less faffing about and should be evaluated in the same context.
-For instance, data on far UV [Buonanno 2017] indicates safety.\\
 
@@
 
+\section{Matters to consider in the design of experiments and the evaluation of literature}
+
 \subsection{Artifacts in past absorption spectroscopy experiments, and the subsequent development and debunking of non-classical damping hypotheses}
 
-Edwards et al in 1984 and 1985 measured the reflection from an open-ended coaxial line dipped in DNA solution and found that DNA appeared to have a resonance-like peak.
+Edwards et al in 1984 and 1985 measured the reflection from an open-ended coaxial line dipped in DNA solution and found that DNA appeared to produce a resonance-like peak.
 
@@
 
-Footnote [At first blush, such an explanation does not seem unreasonable.
+At first blush, such an explanation does not seem unreasonable.
 In the case of the virus, for instance, the expected amplitude of oscillation for which this mechanism applies is on the order of one water molecule (~0.1 nm).
@@
 
-In the case of a uniform rotating sphere, for instance, the [Einstein - ?] viscous drag force diverges from the continuum hypothesis toward zero.]
+In the case of a uniform rotating sphere, for instance, the [Einstein - ?] viscous drag force diverges strikingly from the continuum hypothesis toward zero.
 
@@
 
-\lettrine{U}nfortunately for these hypotheses, Foster 1986, replicating Edwards’ coaxial line method with a more rigorous error analysis on plus an equally rigorous transmission-line absorption, and Bigio in 1993, an ingenious thermo-optical technique, quite definitively demonstrate - to absurd precision -  that the previous results were a characteristic artifact of coaxial-line spectrometry, and that DNA does not have any resonance mode at any microwave frequency.
+\lettrine{U}nfortunately for these hypotheses, Foster 1986, replicating Edwards’ coaxial line method with a more rigorous error analysis on plus an equally rigorous transmission-line absorption, Gabriel, and Bigio in 1993, an ingenious thermo-optical technique, quite definitively demonstrate - to absurd precision -  that the previous results were a characteristic artifact of coaxial-line spectrometry, and that DNA does not have any resonance mode at any microwave frequency.
 

### 2021-01-23 documents/brillouin_pulse_math.tex
pdftex
Dialogue

@@
 
+\pagebreak
 \section{The Brillouin precursors}
@@
 
-Such thin
+The extremely high losses from such thin coaxial cables should be considered.
 
@@
 
-While it is clearly possible to produce this abnormal penetration (any sharp edge suffices), it was not obvious to us that a waveform 
-could be constructed that would be 
-an effective driver for the normal modes in question. Oughston ; if the pulses are too close together, they distort the precursor thus 
-formed.
-
 A third aspect leads to the formation of the prototypical brilluoin precursor: any "sharp" 
@@
 
+Precursors have been used in practice, by Ong \cite{Detection2003} using simple square waves to detect respiration\footnotemark, Ossberger \cite{Noninvasive2004} for the same purpose; and various techniques for breast cancer detection.
+
+Also another really good paper that I can't find.
+
+\footnotetext{Well, Ong don't really observe the precursor itself, it seems.}
+
+While it is clearly possible to produce this abnormal penetration (any sharp edge suffices), it was not obvious to us that a waveform 
+could be constructed that would be an effective driver for the normal modes in question. 
+Oughston ; if the pulses are too close together, they distort the precursor thus formed.
+
 \footnotetext{it is interesting to note that a similar - if not equivalent - effect leads to the Heisenberg uncertainty principle. The more localized a }
+
+\begin{figure}[H]
+	%	\makebox[\textwidth][c]{
+		\includesvg[width=\textwidth]{muscle_pulse_8cm_minimize_test1}
+	\caption{Second.}
+\end{figure}
 
@@
 However, the energy contained in such a standard pulsed-sine or gaussian train decays very quickly,
-
-These precursors have been used in practice, by Ong \cite{Detection2003} using simple square waves to detect respiration\footnotemark, Ossberger \cite{Noninvasive2004} for the same purpose,
-
-Also another really good paper that I can't find.
-
-\footnotetext{Well, Ong don't really observe the precursor itself, it seems.}
 
@@
 
+\paragraph{\textbf{Subharmonics}}\
+
 \begin{fquote}[Wait][ \cite{Propagation1965}]
@@
 
-Macke \cite{Simple2012} have come up with a number of other analytic representations for various signals, such as chirped gaussian pulses.
+Macke \cite{Simple2012} have come up with a number of other analytic dispersion representations for various signals, such as chirped gaussian pulses.
 
-\printendnotes
+%\printendnotes
 

### 2021-01-23 documents/safety.tex
Stuff and things
Wrote a better abstract
Gelgreen
data
Dialogue

@@
+%!TeX root = safety
 \documentclass[paper.tex]{subfiles}
@@
 
+Manikowska [] "showed a highly significant (P > 0.001)", and "Therefore, under our experimental conditions, effects of heat stress and local heating are unlikely.".
+Promptly disproved by \cite{Cytogenetic1986}.
+
 One could subsist on non-thermal effects literature alone.
@@
 
+We borrow the "teleological why" from \cite{mechanisms1981}.
+
 Because this is an ostensibly novel and niche mechanism, it may behoove us to briefly review the biological basis for the safety limits set by standards organizations.
@@
 
-\includegraphics[scale=0.5]{cells.png}
+\begin{figure}[H]
+	\includegraphics[scale=0.5]{cells_2x.png}
+	\caption{xkcd.com/1217}
+\end{figure}
 
@@
 
-There are some 20,000 papers on the topic of RF safety, with solid in vitro, in vivo and epidemiological evidence of safety in the 2.4 GHz and 5.8 GHz bands.
+There are some 20,000 papers on the topic of RF safety, with solid mechanistic, in vitro, in vivo and epidemiological evidence of safety in the 2.4 GHz and 5.8 GHz bands.
 

### 2021-01-23 documents/scan_converter.tex
scan converter, but fucking why
Progress
Dialogue

@@
+The very high voltage means that low-sensitivity diagnostics, like lithium niobate optical probes.
+Not having a suitable optical bench, an electron-beam probe, similar to a streak camera, itself similar in principle to scan-conversion digitizer tubes in Tek SCD and 7912 series transient digitizers.
+
+If a low voltage sensitivity is required, and because modern high-pixel-density CMOS sensors allow the required deflection and the entire structure to be minimized, these are simple to design and inexpensive (much of the complexity being in the slow-wave or travelling-wave structure which is usually required to match the signal velocity to the - slowing down light without affecting its properties or drawing power is an extremely difficult problem) and can offer sample rates in the terasamples/s and analog bandwidths , albeit with low vertical resolution.
+
+original von Ardenne
+
 We would like real-time rather than equivalent-time sampling,
@@
 
-$$ \frac{\sin(\frac{2\pi F \tau}{2})}{(2\pi F)/2} $$
+$$ \frac{\sin(\frac{2\pi F \tau}{2})}{(2\pi F \tau)/2} $$
 
 where \tau is the transit time of the electron through the deflection region
+
+Image intensifier microchannel plates where angled holes cause secondary electron

### 2021-01-23 documents/viscosity.tex
Progress
Dialogue

--- 2020-11-25 documents/viscosity.tex
@@
 \begin{document}
+
+\section{Viscous damping}
+\label{sec:viscousdamping}
 
@@
 
-However, if we apply the same arguments to microtubules \cite{Viscous2000}, omega_c = 80 GHz, and Q=11.2. The effects of these exposures should have been
+However, if we apply the same arguments to microtubules \cite{Viscous2000}, we get $omega_c$ = 80 GHz and Q=11.2.
+The effects of these exposures should have been noticed in previous studies, so there is probably something gravely wrong with this analysis.
+
+In the steady-state, producing 1 nN from a charge of $10^5$ takes some 60 kV/m.
 

### 2021-01-24 documents/background.tex
More discussion

@@
 
+Much of the work in this paper was concerned with this paper
+
 TRL 0
@@
 Many entirely plausible mechanisms exist for which the only valid answer is that they simply do not occur in practice.
+
+On the other hand, the maximum amplitude of oscillation is only expected to be on the order of 50 picometers.
 
@@
 
-\begin{fquote}[Wait][ \cite{treatyelectromagnetic}]
+\begin{fquote}[NATO Research Task Group 189][ \cite{treatyelectromagnetic}]
 HFM-189 found no published and replicated adverse health effects or biological mechanisms, beyond
@@
 Dykeman \cite{Vibrational2009} perform an all-atom molecular dynamics simulation of ISRU of phage M13, albeit without a heat bath to accurately represent damping.
-An interesting result is that despite the broadband nature of the pulse, \char`~80\% of the pulse energy couples into only 5 modes, starting at approx.
+An interesting result is that despite the broadband nature of the pulse, \ntilde80\% of the pulse energy couples into only 5 modes, starting at approx.
 20 GHz.

### 2021-01-24 documents/brillouin_pulse_math.tex
I find a bug in prop_num_optimize
More discussion

@@
 \footnotetext{it is interesting to note that a similar - if not equivalent - effect leads to the Heisenberg uncertainty principle. The more localized a }
-
-\begin{figure}[H]
-	%	\makebox[\textwidth][c]{
-		\includesvg[width=\textwidth]{muscle_pulse_8cm_minimize_test1}
-	\caption{Second.}
-\end{figure}
 
@@
 Costas formulation in \cite{Microwave2012b}, previously discussed by Pozar \cite{Waveform2003}, 
-This is based on a lagrange multiplier technique\cite{Methods1989} and variational 
-calculus\footnotetext{} .
+This is based on a lagrange multiplier technique and variational 
+calculus\cite{Methods1989} \footnotetext{Based on personal communication with Professor Costas Sarris}.
 
@@
 
-Note the ni in the complex conjugate!
+Note the ni specifically in the complex conjugate!
 
@@
 
-Using an energy constraint, appears to tend towards a square step function or a sharp impulse, perhaps as a result of Pontryagin's maximum principle\cite{Optimum1964}.
+Using an energy constraint as above appears to tend towards a square step function or a sharp impulse, perhaps as a result of Pontryagin's maximum principle\cite{Optimum1964}.
 
-\subsection{Laziness prevails; a return to numerical optimization}
+However, a maximum absolute value constraint produces fantastic results.
+
+\begin{figure}[H]
+	%	\makebox[\textwidth][c]{
+	\includesvg[width=\textwidth]{muscle_pulse_8cm_minimize_test1}
+	\caption{Second.}
+\end{figure}
+
+\begin{figure}[H]
+	%	\makebox[\textwidth][c]{
+	\includesvg[width=\textwidth]{muscle_pulse_8cm_minimize_test2}
+	\caption{Second.}
+\end{figure}
+
+ Believed to be FFT window artifacts. Increasing the window size with the same sample rate caused CG convergence to stall.
 

### 2021-01-24 documents/charge.tex
Progress
progress
why's fdtd broken?
More discussion

@@
 \documentclass[paper.tex]{subfiles}
-\usepackage{parselines}
+%\usepackage{parselines}
 
@@
 \section{Charge}
+
+Induced polarization
+
+Nuclocapsid
+
+The adsorption of metal ions onto the surface of the genome,
+
+effective
+
+\subsection{Birefringence }
+
+\subsection{Electrorotation }
+
+\subsection{Poisson-Boltzmann }
 
@@
 
-\footnote{Influenza also has several other fascinating electrostatic properties. First, the net charge on the virion changes}
+\footnote{Influenza also has several other fascinating electrostatic properties. First, the net charge on the virion changes on a decade-by-decade basis \cite{Dynamics2010}. }
 
@@
 \subsection{Electrostatic energy}
-
-Viral capsids self-assemble; it is energetically favorable to.
 
@@
 From Eq.
-2, and n0 \approx 3 M, it follows that nin $\approx 0.62 M$ and hence n++ n- \approx 4.2 M, which because of the Donnan equilibrium is indeed significantly larger than 2nb \approx 3 M.
+2, and n0 \ntilde 3 M, it follows that nin $\approx 0.62 M$ and hence n++ n- \ntilde 4.2 M, which because of the Donnan equilibrium is indeed significantly larger than 2nb \ntilde 3 M.
 }
-https://www-sciencedirect-com.ezproxy.library.yorku.ca/science/article/pii/S0006349503744555
+%https://www-sciencedirect-com.ezproxy.library.yorku.ca/science/article/pii/S0006349503744555
 
@@
 
-\section{Hello World}
-\label{sec:hello}
-\hyperref[sec:hello]{See section.}
+Bosch \cite{Studies1985}
 

### 2021-01-24 documents/background.tex
Building the thing

@@
 Regurgitating Yang et al's line of reasoning, with a few; they study a 1 kV/m, 15 minute exposure, whereas we are concerned with a 3 MV/m, 500 picosecond regime.
+
+for which our working hypothesis is that there are no clinically useful mechanisms,
+
+It stands to reason, then, that any pulse longer than the relaxation time is not efficiently.
+
+Less than 1 nanosecond (where poration and thermal effects start to become significant, and any previous absorbed power has been dispersed in the solvent) but greater than about 10 picoseconds (covered by existing laser research) and electric fields between 0.1 MV/m (for which biological effects at these timescales are only barely plausible) and 10 MV/m (the production of pulses which strain credulity).
+
+as dt decreases, there's lots of room to add more zeros. a pulse 4 orders of magnitude higher than the maximum field used by practically any existing system.
 

### 2021-01-24 documents/brillouin_pulse_math.tex
Building the thing

@@
 
-Uzunoglu \cite{Theoretical2020} mention a handy way to circumvent this lossy-flesh problem: the Brillouin and Sommerfeld precursors.
+Uzunoglu \cite{Theoretical2020} mention a handy way to circumvent this lossy-flesh problem: the Brillouin and Sommerfeld precursors, and dispersion in general.
 
@@
 
-The highly dispersive nature of tissue, which causes a peculiar distortion of short pulses,
+\begin{itemize}
+	\item The highly dispersive nature of tissue, which causes a peculiar distortion of short pulses,
+	\item The variation in loss (the imaginary part of the complex permittivity) and penetration depth versus frequency. 
+\end{itemize}
 
-The change in loss (the complex part of the permittivity, or the) and increase in penetration depth
-
-A third aspect leads to the formation of the prototypical brilluoin precursor: any "sharp" 
-beginning or end of a tone, or other spatially confined structure in a waveform, includes harmonics 
-up to these \footnotemark
+A third aspect leads to the formation of the prototypical Brillouin precursor specifically: any sharp 
+beginning or end of a tone, or other sharply defined structure in a waveform, includes harmonics beyond the tone's carrier wave up to the rise time \footnotemark. \wikinote{add image}
 
@@
 \footnotetext{Well, Ong don't really observe the precursor itself, it seems.}
+
+By putting more power in higher frequencies,
 
@@
 	\includesvg[width=\textwidth]{muscle_pulse_8cm_minimize_test1}
-	\caption{Second.}
+	\caption{}
 \end{figure}
+
+The (noisy) output of the optimization for z=0.08 m in muscle.
+The low-frequency component is believed to be due to the FFT window size.
+Increasing the window size with the same sample rate caused CG convergence to stall.
+However, it's interesting that this appears to result in a larger amplitude.
 
@@
 
- Believed to be FFT window artifacts. Increasing the window size with the same sample rate caused CG convergence to stall.
-
 \end{document}

### 2021-01-26 documents/supplemental.tex
still broken sources
Dialogue
More discussion
Progress on RPi cal

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{\Huge Captain's Log, Supplemental}
+\section[Appendix]{\Huge Captain's Log, Supplemental}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{fquote}
+
+%tonsil
 
@@
 with adhesives. causes "hairs" when machining.
+
+Rationale for doing this alone.
+Science is nothing without collaboration.
+However, it's also nothing without acknowledging the shortfalls of your research.
+There remains no physical reason to expect this to work - it is indistinguishable from crackpottery - and, in fact, the first route of investigation did not work.
+Therefore, seemed irresponsible to redirect resources or involve other people.
+
+at least that's the story I tell myself.
 
@@
 {\Large Microwave Musings}\\
-\begin{multicols}{1}
+
 	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+many programs try to implement their own command scripting language
+if the api doesn't expose access to the data on each timestep, then you're limited to the features that have already been implemented
+
 \section{Timeline}

### 2021-01-26 firmware/chengxiang/rpi/run.py

@@ -1,0 +1,127 @@
+import RPi.GPIO as GPIO
+from time import sleep
+
+STEP_PIN = 7
+DIR_PIN = 21
+LIMIT_PIN = 22
+TRIGGER_PIN = 11
+ENABLE_PIN = 19 #might be 16
+
+GPIO.setmode(GPIO.BOARD)
+
+DEG_PER_STEP = 18.0
+SCREW_PITCH = 0.5 # //mm
+MICROSTEPS = 4
+distance_per_step = ((DEG_PER_STEP / 360.0) * SCREW_PITCH);
+#
+GPIO.setup(STEP_PIN, GPIO.OUT)
+GPIO.setup(DIR_PIN, GPIO.OUT)
+GPIO.setup(TRIGGER_PIN, GPIO.OUT)
+GPIO.setup(ENABLE_PIN, GPIO.OUT)
+
+GPIO.setup(LIMIT_PIN, GPIO.IN)
+
+
+
+position = 0.0
+
+def move_absolute(new_position):
+    print("Moving to {} from {}\n".format(new_position, position))
+    delta = new_position - position
+    move_relative((delta < 0), abs(delta))
+    position = new_position
+
+
+
+def move_relative(direction, distance):
+    GPIO.output(DIR_PIN, direction)
+    GPIO.output(ENABLE_PIN, 0)
+
+    num_steps = distance/distance_per_step * MICROSTEPS;
+
+    for i in range(int(num_steps)):
+    	GPIO.output(STEP_PIN, 1)
+    	sleep(600 * 1e-6) #microseconds
+
+    	GPIO.output(STEP_PIN, 0)
+    	sleep(600 * 1e-6) #microseconds
+
+    GPIO.output(ENABLE_PIN, 1)
+
+
+def home():
+    while(GPIO.input(LIMIT_PIN)):
+        move_relative(1,1)
+
+    GPIO.output(DIR_PIN, 0)
+    GPIO.output(ENABLE_PIN, 0)
+
+    while(not GPIO.input(LIMIT_PIN)):
+    	GPIO.output(STEP_PIN, 1)
+    	sleep(1500 * 1e-6) #microseconds
+
+    	GPIO.output(STEP_PIN, 0)
+    	sleep(1500 * 1e-6) #microseconds
+
+    GPIO.output(ENABLE_PIN, 1)
+    position = 0
+
+while True:
+    home()
+    sleep(1)
+
+
+
+
+
+
+#
+# digitalWrite(13, HIGH);
+#
[…]

### 2021-01-28 documents/background.tex
Progress on RPi cal
dammit the precursor's at the wrong frequency

--- 2021-01-24 documents/background.tex
@@
 
+\begin{multicols}{1}
+
+\footnote{A note on units, from ICNIRP: ``{[B]elow about 6 GHz, where EMFs penetrate deep into tissue (and thus require depth to be considered), it is useful to describe this in terms of “specific energy absorption rate” (SAR), which is the power absorbed per unit mass $(W/kg)$.
+Conversely, above 6 GHz, where EMFs are absorbed more superficially (making depth less relevant), it is useful to describe exposure in terms of the density of absorbed power over area $W/m^2$, which we refer to as “absorbed power density”}''.
+}
+
 I was hoping I would have a definitive demonstration, so as to not redirect resources from more promising avenues.
 
-Note that it is possible that this has already been worked on. The last review was several months ago, and the literature is changing very rapidly.
+Note that it is possible that this has already been worked on. The last review was several months ago, and the literature is changing very rapidly. Reuben
 
@@
 
-\begin{multicols}{1}
+for which our working hypothesis is that there are no clinically useful mechanisms,
+
+It stands to reason, then, that any pulse longer than the relaxation time is not efficiently.
+
+vestiges
+
+Less than 1 nanosecond (where poration and thermal effects start to become significant at these fields, and any previous absorbed power has been dispersed in the solvent) but greater than about 10 picoseconds (covered by existing laser research) and electric fields between 0.1 MV/m (for which biological effects at these timescales are only barely plausible) and 10 MV/m (the production of pulses which strain credulity).
+
+as dt decreases, there's lots of room to add more zeros. a pulse 4 orders of magnitude higher than the maximum field used by practically any existing system.
 
@@
 
-Electroporation of viral membranes and capsids has been observed.
+Scope for this effect can be seen in the following contrast. The statement which echos the concensus of a number of literature reviews by standards organizations:
 
-Mizuno \cite{Inactivation1990} inactivate SVD Enterovirus (a 27 nm non-enveloped encapsidated ssRNA) and EHV (a 100 nm enveloped dsDNA) with 100\% effectiveness at 120 pulses, about 500 nanoseconds each, at 3 MV/m.
+\begin{fquote}[\textit{NATO Research Task Group 189}, as cited by \textit{C95.1-2019, B.4.3 Rationale for pulsed RF field limits}][ \cite{treatyelectromagnetic}]
+	HFM-189 found no published and replicated adverse health effects or biological mechanisms, beyond
+	thermal interaction, for pulses shorter than 100 ms which suggested that neither the peak E-field limit in the
+	IEEE C95.1-2005 safety standard {\normalfont[NB chapter 4.3, Table 9, subsection e.
+peak E field 100 kV/m]} nor the proposed limit in the Directive 2004/40/EC [33] (subsequently promulgated as 2013/35/EU [34]) have scientific basis.
 
-The thermal artifact cannot necessarily be discounted.
-The energy \footnote{(43 cal/cc * (3 microliters)) / (3 milligrams * 4.2 J/(g K))}.
-The electrodes were un-insulated, so electrochemical effects are possible.
+	Physical laws governing the propagation of E-fields in air already limit the maximum allowable peak E-field at ~3 MV/m (air breakdown).
+Current research efforts by members to expose biological organism(s), tissues, and cells to environmental
+	fields up to this magnitude have been unable to elicit an acute biological response.
+\end{fquote}
 
-Interestingly
+\subsection{Precedent}
 
-Madiyar observe rapid permeabilization at a field of approximately $10^7$ V/m, in the Vaccinia poxvirus (a 300 nm enveloped dsDNA virus).
+Electropermeabilization of viral membranes and capsids has been observed.
+
+Mizuno \cite{Inactivation1990} inactivate SVD Enterovirus (a 27 nm non-enveloped protein encapsidated ssRNA) and EHV (a 100 nm enveloped dsDNA) with 100\% effectiveness with 120 pulses, about 500 nanoseconds each, at 3 MV/m.
+Electron microscopy demonstrates that the mechanism is irreversible damage to the capsid or envelope respectively and release of the core.
+
+\begin{autem}
+Extreme care must be taken in interpreting the results of any one study in isolation, especially in this field.
+
+In this observation, the thermal artifact cannot necessarily be discounted.
+The energy dissipated was sufficient to cause a significant temperature rise if localized hot-spots appeared \footnote{(43 cal/cc * (3 microliters)) / (3 milligrams * 4.2 J/(g K)) = ~50 $\Delta$C, whereas melting temperatures are typically about 90 C for capsids and 50 C for envelopes\cite{Stability1985}}.
+The electrodes were not insulated, so electrochemical effects are possible but unlikely given the short duration of the pulses.
+\end{autem}
+
+Madiyar \cite{Manipulation2013} observe rapid permeabilization (likely through the slow, conventional electroporation mechanism) at a field of poorly-defined intensity up to about 10 MV/m, in the Vaccinia poxvirus (a 300 nm enveloped dsDNA virus).
 \cite{AC2017}.
-Interestingly, the same effect is not observed in T4 \cite{Manipulation2013}.
+Interestingly, the same effect is not observed in T4 bacteriophage.
+
+Moreover, these results could easily be explained by a first-order theoretical.
+Both AFM data and surmised from osmotic pressure, the force scale required to crack the viral envelopes and capsids is about 1 nanonewton.
+
+de Seze
+
+\pagebreak
+
+(we use the term electropermeabilization)
+
+If we compare in-vitro with in-vitro host cells, the issue becomes less clear.
+
+NATO Research Task Group 189 \cite{treatyelectromagnetic}
+
+zotero citation graph?
 
@@
 
-This idea, that resonances, is backed up by measurements by Gabriel; the slowest relaxation time in the microwave regime appear to be in the mammary glands, and.
+This idea, that resonances, is backed up by measurements on aggregate tissues by Gabriel; the slowest relaxation time in the microwave regime appear to be in the mammary glands, and.
 Small resonances will be disguised by the aggregation, however.
@@
 best practices were not followed.
-
-NATO Research Task Group 189 \cite{treatyelectromagnetic}
-
-zotero citation graph?
-
-\begin{fquote}[NATO Research Task Group 189][ \cite{treatyelectromagnetic}]
-HFM-189 found no published and replicated adverse health effects or biological mechanisms, beyond
-thermal interaction, for pulses shorter than 100 ms which suggested that neither the peak E-field limit in the
-IEEE C95.1-2005 safety standard [n.b.
-chapter 4.3, Table 9, subsection e.
-peak E field 100 kV/m] nor the proposed limit in the Directive 2004/40/EC [33] (subsequently promulgated as 2013/35/EU [34]) have scientific basis.
-\end{fquote}
-
-" physical laws governing the propagation of E-fields in air already limit the maximum allowable peak E-field at ~3 MV/m (air breakdown).
-Current research efforts by members to expose biological organism(s), tissues, and cells to environmental
-fields up to this magnitude have been unable to elicit an acute biological response."
-
-\footnote{A note on units, from ICNIRP: ``{[B]elow about 6 GHz, where EMFs penetrate deep into tissue (and thus require depth to be considered), it is useful to describe this in terms of “specific energy absorption rate” (SAR), which is the power absorbed per unit mass $(W/kg)$.
-Conversely, above 6 GHz, where EMFs are absorbed more superficially (making depth less relevant), it is useful to describe exposure in terms of the density of absorbed power over area $W/m^2$, which we refer to as “absorbed power density”}''.
-}
 
@@
 
-C95.1-2019, B.4.3 Rationale for pulsed RF field limits
+Ultrasonic excitation or acoustic pulses have been considered in the literature; we have not analyzed these claims in any depth.
 
@@
 
-Pakhomov \cite{Comparative} expose frog heart cells, and find no effects on functioning pacemaker cells at 0.9 kV/m (although the field inside the waveguide may be lower).
-
-Note: The author not being biologists or microwave engineers, the trained reader may find that we are too verbose in simple technique and methodology and not detailed in another.
+Pakhomov \cite{Comparative} find no non-thermal effects on functioning frog heart pacemaker cells at 0.9 MV/m (although the field inside the tissue was not measured and could have been lower).
 

### 2021-01-28 documents/brillouin_pulse_math.tex
Progress on RPi cal
dammit the precursor's at the wrong frequency

@@
 
+The extremely high losses from such thin coaxial cables should be considered.
+
 \pagebreak
-\section{The Brillouin precursors}
+\section{Dispersion and the Brillouin precursors}
 
-Uzunoglu \cite{Theoretical2020} mention a handy way to circumvent this lossy-flesh problem: the Brillouin and Sommerfeld precursors, and dispersion in general.
+Uzunoglu \cite{Theoretical2020} mention a handy way to circumvent this lossy-flesh problem: the Brillouin and Sommerfeld precursors, and pulse dispersion in tissues in general.
 
-The extremely high losses from such thin coaxial cables should be considered.
+Of course, 10x attenuation at 1 MV/m still takes us outside.
+However, the loss that makes phased-array near-field focusing systems impractical at baseband is no longer a concern.
+A dispersive phased array with more than 10 elements may allow the complete elimination of attenuation without exceeding the limit field at any point in the body.
 
@@
 \cite{Shortrisetime1989}):
+
+\footnote{"precursor" is perhaps a misnomer when single pulses are used rather than trapezoidally-modulated tones - Oughston and Najafabadi call these Brillouin pulses \cite{Optimal2015} \cite{Optimal2017} \cite{Heat2010}.}
 
@@
 beginning or end of a tone, or other sharply defined structure in a waveform, includes harmonics beyond the tone's carrier wave up to the rise time \footnotemark. \wikinote{add image}
+
+The aspect that makes the precursors useful is that they sidestep Bragg's Law decay, decaying as $1/\sqrt{z}$ rather than $e^{-z}$.
+Note that Bragg's law is still strictly obeyed in the frequency domain (excepting second-order "bleaching" or induced transparency-like effects).
 

### 2021-01-28 documents/charge.tex
dammit the precursor's at the wrong frequency

@@
 
-Induced polarization
+\begin{autem}
+Deserves a more detailed treatment.
+\end{autem}
 
-Nuclocapsid
+The adsorption of metal ions onto the surface of the genome
+\begin{itemize}
+\item The nucleocapsid. 
+\item Induced polarization
+		Persson cite a re-arrangement of electrons as a source of drag. Polarization-like effects are not expected. We have not followed up on this.
 
-The adsorption of metal ions onto the surface of the genome,
+\item 
+\end{itemize}
 
@@
 
-\subsection{Birefringence }
+Birefringence e
 
-\subsection{Electrorotation }
+It is easy to determine an upper limit.
 
-\subsection{Poisson-Boltzmann }
+Božič \cite{How2012} consider an empty capsid.
+
+Donnan equilibrium
 
@@
 
-Yang et al determine that in order to fit their microwave absorption cross-section data, and produce the decrease in infectivity via precisely the mechanism they suggest, the "core" and "shell" of Influenza A should have an effective charge of about $q=1 \times 10^7 e^-$.
+Yang et al determine that in order to fit their microwave absorption data, and produce the decrease in infectivity via precisely the mechanism they suggest, the "core" and "shell" of Influenza A should have an effective charge of about $q=1 \times 10^7 e^-$.
 
-The mechanism given is that ions from solution counteract the protein charges to form an "electric double layer".
-In any case, the best representation is two concentric spheres, with a net charge each.
+The mechanism given is that ions from solution counteract the protein charges to form an electric double layer. In any case, the best representation is two concentric spheres, with a net charge each.
 

### 2021-01-28 documents/paper.tex
Dialogue
More discussion
Building the thing
dammit the precursor's at the wrong frequency

@@
 
-%\subfile{introduction}
-
-\clearpage
+\begin{figure}[H]
+	\captionsetup{singlelinecheck = false, justification=justified}
+	\centering
+	\includegraphics[width=\textwidth]{pulse_exposure_setup.JPG}
+	\caption{\\ Pulse exposure jig. Autosampler Pulse shaper not shown. Aluminum disc belongs to the scan-conversion digitizer, not used in this study.}
+\end{figure}
 
@@
 	\includegraphics[width=\textwidth]{eppenwolf_2.jpg}
-	\caption{\\ The {\it Eppenwolf} pulsed X-Band microwave spectrometer used in this study, pictured with the near-field cuvette installed.}
+	\caption{\\ The misguided {\it Eppenwolf} pulsed X-Band microwave spectrometer used in this study, pictured with the near-field cuvette installed.}
+\end{figure}
 
-\end{figure}
+\clearpage
 
@@
 
-\paragraph{\textbf{Subharmonics}}\
-
 \paragraph{\textbf{More fanciful concepts}}\
@@
 
+\subfile{brillouin_pulse_math}
+
 %\paragraph{}
@@
 
+\subfile{charge}
+
 \subfile{viscosity}
 
+\subfile{molecular_dynamics}
+
 \subfile{supplemental}
+
+\subfile{fluorescence}
+
+\subfile{detection}
 

### 2021-01-28 documents/pseudo_soliton.tex
dammit the precursor's at the wrong frequency

@@
 
-The prototypical Vircator (not varactor) pinched electron beam tubes
-
-step recovery diodes
-
-\begin{sidenote}
-There are some extremely tricky subtleties in the simulation.
-\cite{propagation1992}.
-In \cite{Comments1993}, Leubbers says FDTD and FFT both are better than Asympt, Ogh says no there's no problem, Asymptotic is really accurate.
-Frankly, I can't make heads or tails of any of these, not understanding the asymptotic method at all.
-\end{sidenote}
-
-The 2018 NATO Research Task Group 189 report \cite{treatyelectromagnetic} is an excellent source of data for these.
-
-\begin{quote}
-	Other basic bioeffects research [50], [52], [53], [66], [81], [83] has failed to provide support for Albanese’s multiple	theoretical postulates.
-\end{quote}
-
-The real killer
-
 \footnotemark
@@
 
-The "asymptotic method", and the fourier series method. Unfortunately, the fourier coefficients and phases provide little intuitive sense for how different input pulses propagate.
-
-%The Somerfield precursor is high-frequency,
-
 \end{document}

### 2021-01-28 documents/pulse_generator.tex
dammit the precursor's at the wrong frequency

--- 2021-01-24 documents/brillouin_pulse_math.tex
@@
-%!TeX root = brillouin_pulse_math
+%!TeX root = pulse_generator
 \documentclass[paper.tex]{subfiles}
@@
 
-\pagebreak
-\section{The Brillouin precursors}
-
-Uzunoglu \cite{Theoretical2020} mention a handy way to circumvent this lossy-flesh problem: the Brillouin and Sommerfeld precursors.
-
-The extremely high losses from such thin coaxial cables should be considered.
-
-The original text of these papers are in German; translations can be found in Léon Brillouin's 1960 
-book\cite{Wave1960} on the topic. \footnotemark
-
-These are fascinating structures which arise as a result of two aspects (Albanese 
-\cite{Shortrisetime1989}):
-
-The highly dispersive nature of tissue, which causes a peculiar distortion of short pulses,
-
-The change in loss (the complex part of the permittivity, or the) and increase in penetration depth
-
-A third aspect leads to the formation of the prototypical brilluoin precursor: any "sharp" 
-beginning or end of a tone, or other spatially confined structure in a waveform, includes harmonics 
-up to these \footnotemark
-
-Precursors have been used in practice, by Ong \cite{Detection2003} using simple square waves to detect respiration\footnotemark, Ossberger \cite{Noninvasive2004} for the same purpose; and various techniques for breast cancer detection.
-
-Also another really good paper that I can't find.
-
-\footnotetext{Well, Ong don't really observe the precursor itself, it seems.}
-
-While it is clearly possible to produce this abnormal penetration (any sharp edge suffices), it was not obvious to us that a waveform 
-could be constructed that would be an effective driver for the normal modes in question. 
-Oughston ; if the pulses are too close together, they distort the precursor thus formed.
-
-\footnotetext{it is interesting to note that a similar - if not equivalent - effect leads to the Heisenberg uncertainty principle. The more localized a }
-
-At a depth of 8 cm in Cole-Cole muscle, an 8 GHz resonance, attack pattern alpha appears to achieve 4 picometers of oscillation amplitude, rather than 0.01 picometers with $\sin(t\ \omega_{resonance})$.
-The sharp edges are at approx.
-250 GHz.
-
-At 9 GHz, assuming that a torso is about 10 penetration depths in radius and the Brillouin train 
-drives the virus with an equally, implementing this would decrease the field at the skin required 
-for complete eradication of the virus from the body to a perfectly practicable 1 kV/m, rather than 
-an air-ionizing 6.6 MV/m ($\frac{1}{\sqrt{10}}=0.316$ versus $e^{-10}=4.5e^{-5}$).
-
-However, the energy contained in such a standard pulsed-sine or gaussian train decays very quickly,
-
-%http://web.physics.ucsb.edu/~fratus/phys103/LN/DHM.pdf
-% section on Greens functions
-% and also 
-% and
-% https://www.int.washington.edu/users/dbkaplan/228_01/green.pdf
-
-Note: this isn't truly transient - the fourier integral is still periodic, wrapping around every x cycles. It's just more transient than the steady-state.
-
-attack pattern alpha
-
-Unfortunately, despite NLTLs producing strong wideband components, in cursory simulations they do 
-not appear to satisfy the requirements for Brillouin pulses. Our working hypothesis is that this is 
-because of destructive interference from the falling edge that immediately follows; but this is 
-mere speculation.
-\begin{autem}
-	This should be replicated.
-\end{autem}
-
-temporal Soliton-producing nonlinear transmission lines, and NLTL oscillators constructed therefrom, particularly well suited
-
-Transient solution
-
-\pagebreak
-A qualitative statement of the problem:
-
-\begin{toolchain}
-An arbitrary waveform propagates through a dispersive, lossy medium with a certain analytic complex 
-permittivity.
-
-It then drives a damped harmonic oscillator that is initially at rest.\\
-
-What waveform produces the peak transient amplitude on the oscillator?
-\end{toolchain}
-
-\subsection{Analytic techniques}
-
-\paragraph{\textbf{Subharmonics}}\
-
-\begin{fquote}[Wait][ \cite{Propagation1965}]
-	In such cases, it may be feasible to evaluate the integral by a purely numerical procedure.
-With the wide availability of the digital computer, this is certainly fashionable at the moment.
-Consequently, one might say that the problem has been solved and no further discussion is needed.
-\\
-
-	However, it would be a pity if one accepted this answer since all physical insight into the nature of transient processes has been ignored. 
-\end{fquote}
-
-\begin{autem}
-Reflection from tissue interfaces?
-
-Thermal noise will kick the oscillator around; it won't necessarily start at rest. Will this affect the 
-\end{autem}
-
-One might suggest try to find the optimal transient solution first, and then try to build an input waveform deconvolved through the  transfer function of the tissue.
-This hardly seems liable to produce a truly optimal solution, however.
-
-Each problem has been solved separately.
-There are some nearly equivalent but not mathematically identical formulations for optimal control of quantum systems with dispersion.\footnotemark However, in the classical domain, this appears to be unprecedented in the literature.
-
-\footnotetext{While not strictly related, \cite{Wavepacket1989} tune a light pulse to match the wavefunction of the desired chemical products in a photo-reaction, which is just pretty darned awesome}
-
-Also, this seems similar to a pulse propagating through the tissue's Cole medium and then dissipating the maximum power in a uniform Lorentz medium, which might be another route to attacking it.
-
-Another route might be to set up two ODEs for the wave equation and the oscillator and solve them simultaneously.
-
-Progress was hindered by the ~6 conventions for Fourier normalization, the sign or handedness of the imaginary number.
-What self-respecting field has completely antipodal definitions of the same concept.
-
-oh, on the same topic, can we finally settle the i / j convention. Also, everyone that doesn't explicitly note
-
-Optimal pulses for several situations in Debye and Lorentz media have been determined by Oughstun's asymptotic method, which appears to be highly satisfactory in terms of physical intution, and also avoids truncation issues that befall fourier-transform techniques.
-In general, these optimal pulses are simple gaussian monopulses or higher-order gaussian derivatives \cite{Optimal2017} \cite{Optimal2015}.
-
-Macke \cite{Simple2012} have come up with a number of other analytic dispersion representations for various signals, such as chirped gaussian pulses.
-
-%\printendnotes
-
-\subsubsection{Zhu et al 's dispersive waveform optimization propagation formulation}
-
-The most promising analytical technique that we explored was essentially equivalent to Zhu, Hum, 
-Costas formulation in \cite{Microwave2012b}, previously discussed by Pozar \cite{Waveform2003}, 
-This is based on a lagrange multiplier technique and variational 
-calculus\cite{Methods1989} \footnotetext{Based on personal communication with Professor Costas Sarris}.
-
-$$ e_x(z,t) = \frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{+\infty}{F(\omega) e^{- j (\omega/c_0)n(\omega)z}\ e^{j\omega t} d\omega} $$
-
-where $\int e^{j \omega t} d\omega$ is the inverse fourier transform.
-
-$$W = \frac{1}{\eta_0} \int_{-\infty}^{+\infty}{(n_r(\omega))\ |F(\omega)|^2}\ d\omega$$\\
-
-Where $n(\omega)$ is a complex refractive index per Debye relaxation equation, $n_r()$ is the real part of the same, everything else is a real constant.
-Set up a functional with a lagrange multiplier\\
-
-$$\xi = -e_x(z,t) + \lambda W$$\\
-
-Take the functional ("variational") gradient with respect to $F(\omega)$.
-
-$$ \nabla \xi = -\frac{1}{\sqrt{2\pi}} \left(e^{- j (\omega/c_0)n(\omega)z}\right)^\star \  e^{-j\omega T} + \lambda...$$
-
-At this point, you could choose to perform a second integral over the time-domain Greens function solution to the harmonic oscillator\cite{Complex2020}, eq. 4 and 15,
-
-$$x(t) = \int_{-\infty}^{+\infty}{G(t,t')\ \frac{q\cdot e_x(z,t'))}{m}\ } dt'$$\\
-
-(eq. 15, for the underdamped case)
-
-$$G(t,t') = UnitStep(t-t') \frac{1}{\sqrt{\gamma^2-\omega_0^2}  }\sinh\left({\sqrt{\gamma^2-\omega_0^2}}\ (t-t')\right)$$
-
-But a much more straightforward
-
-Where * is the complex conjugate.\\
-
-The $\nabla H() = H()^\star$ thing seems to come from Franks, Signal Theory, 1969, page 140 onwards; I cannot make heads or tails of his formulation.
-
-Neither Maxima, SageMath, Mathematica's VariationalD, Matlab's Fundiff, nor Maple's 
-functionalDerivative seem to yield any meaningful result for grad xi.\\
-
-Then set
-
-$$x(t) = \int_{-\infty}^{+\infty}{G(t,t')\ \frac{q\cdot e_x(z,t'))}{m}\ } dt'$$\\
-
-Anyhow, then modify the lagrange multiplier,
-
-$$\xi = -x(t) + \lambda W$$\\
-
-And now,
-
-$$\nabla \xi = 0$$
-
-Pulse energy, rather than peak field, is not obviously the ideal constraint for this problem; however, it is the one most compatible with lagrange multiplier techniques.
-
-Tufts \cite{Optimum1964}
-
-The Euler-Lagrange equation is usually brought up in the case of the Brachistochrone problem, or 
-the Principle of Least Action (see Feynman lectures). In these types of problems, it appears that 
-the path of integration through space from endpoints a to b is replaced with the whole frequency 
-domain from -$\infty$ to +$\infty$.
-
-Search terms: "first variation", gateaux derivative,
-
-As noted by Pozar, the complex conjugate arises from the concept of "adjointness". Franks.
-
-Note the ni specifically in the complex conjugate!
-
-\subsection{Laziness prevails; a return to numerical optimization}
-
-Numerically solving optimal control problems using CG was noted by Lasdon \cite{conjugate1967} and 
-revisited by Kek \cite{Conjugate}. They reduce the computational workload by first computing the 
-gradient function by hand.
-
-Using an energy constraint as above appears to tend towards a square step function or a sharp impulse, perhaps as a result of Pontryagin's maximum principle\cite{Optimum1964}.
-
-However, a maximum absolute value constraint produces fantastic results.
-
-\begin{figure}[H]
-	%	\makebox[\textwidth][c]{
-	\includesvg[width=\textwidth]{muscle_pulse_8cm_minimize_test1}
-	\caption{Second.}
-\end{figure}
-
-\begin{figure}[H]
-	%	\makebox[\textwidth][c]{
-	\includesvg[width=\textwidth]{muscle_pulse_8cm_minimize_test2}
-	\caption{Second.}
-\end{figure}
-
- Believed to be FFT window artifacts. Increasing the window size with the same sample rate caused CG convergence to stall.
-
 \end{document}

### 2021-01-28 documents/acknowledgement.tex
why's fdtd broken?
Coplanar exposure cell working
Building the thing
Brillouin cleanups

@@
 
+Special thanks to my parents, Doris and Brian, without whom this work would have been accomplished by someone else, and whose extraordinary support made this paper possible.
+
 The authors of the original papers deserve the credit for this entire work; it is rare that such a monumental finding is served on a silver platter.
-
-Chiefly among the enablers are of course my parents, Doris and Brian, without whom this work would have been done by someone else, and who also supported this work financially.
 
@@
 
+Greenland for patience
+
+James Hawthorne for Autoleveller
+
+Chengxiang Li and the team of who appear to have spent a decade iterating the Marx avalanche generator we use in this paper. It is an excellent, very high performance design.
+
 \rule{\linewidth}{0.2pt}

### 2021-01-28 documents/brillouin_pulse_math.tex
Brillouin cleanups

--- 2021-01-24 documents/brillouin_pulse_math.tex
@@
 
+The extremely high losses from such thin coaxial cables should be considered.
+
 \pagebreak
-\section{The Brillouin precursors}
+\section{Dispersion Timothy and the Brillouin Precursors}
 
-Uzunoglu \cite{Theoretical2020} mention a handy way to circumvent this lossy-flesh problem: the Brillouin and Sommerfeld precursors, and dispersion in general.
+Uzunoglu \cite{Theoretical2020} mention a handy way to circumvent this lossy-flesh problem: the Brillouin and Sommerfeld precursors\footnotemark, and pulse or wavepacket dispersion in tissues in general.\footnotemark
 
-The extremely high losses from such thin coaxial cables should be considered.
+\footnotetext{
+	Sincere thanks go to the legendary Kurt Oughstun for taking the time to reply to our emails.
+}
+
+\footnotetext{"precursor" is perhaps a misnomer when single pulses are used rather than trapezoidally-modulated tones - Oughston and Najafabadi both call these \textit{Brillouin pulses}.\\ \cite{Optimal2015} \cite{Optimal2017} \cite{Heat2010}.}
 
@@
 
-These are fascinating structures which arise as a result of two aspects (Albanese 
+These are fascinating structures somewhat similar to solitons, which arise as a result of an interplay between two aspects (Albanese 
 \cite{Shortrisetime1989}):
@@
 \begin{itemize}
-	\item The highly dispersive nature of tissue, which causes a peculiar distortion of short pulses,
-	\item The variation in loss (the imaginary part of the complex permittivity) and penetration depth versus frequency. 
+	\item The highly dispersive nature of tissue, which causes a peculiar distortion of pulses with broadband spectral content,
+	\item The variation in loss (the imaginary part of the complex permittivity and the penetration depth) versus frequency. 
 \end{itemize}
@@
 beginning or end of a tone, or other sharply defined structure in a waveform, includes harmonics beyond the tone's carrier wave up to the rise time \footnotemark. \wikinote{add image}
+
+The aspect that makes the precursors useful is that they sidestep Bragg's Law decay, with an amplitude that decays as $1/\sqrt{z}$ rather than $e^{-z}$.
+Note that Bragg's law is still strictly obeyed in the frequency domain (excepting second-order "bleaching" (Lukofsky \cite{Can}) or induced transparency-like (\cite{Electromagnetically1997}) effects).
 
@@
 
-While it is clearly possible to produce this abnormal penetration (any sharp edge suffices), it was not obvious to us that a waveform 
+While it is clearly possible to produce this abnormal penetration (any sharp edge sufficiently distant from  suffices to produce a dispersive pulse), it was not obvious to us that a waveform 
 could be constructed that would be an effective driver for the normal modes in question. 
-Oughston ; if the pulses are too close together, they distort the precursor thus formed.
+Oughston ; if the pulses are too close together, they interfere as they propagate and distort the precursor thus formed.
+
+For instance, despite the waveform from nonlinear transmission lines producing strong wideband components, in cursory simulations they did not appear to satisfy the requirements for Brillouin pulses\wikinote{dubious-discuss}\wikinote{citation-needed}.
+Our working hypothesis is that this is because of destructive interference from the falling edge that immediately follows; but this is mere speculation.\wikinote{dubious-discuss}
+
+temporal Soliton-producing nonlinear transmission lines, and NLTL oscillators constructed therefrom, particularly well suited
 
@@
 
-Unfortunately, despite NLTLs producing strong wideband components, in cursory simulations they do 
-not appear to satisfy the requirements for Brillouin pulses. Our working hypothesis is that this is 
-because of destructive interference from the falling edge that immediately follows; but this is 
-mere speculation.
-\begin{autem}
-	This should be replicated.
-\end{autem}
-
-temporal Soliton-producing nonlinear transmission lines, and NLTL oscillators constructed therefrom, particularly well suited
-
 Transient solution
@@
 \pagebreak
-A qualitative statement of the problem:
+A qualitative statement of the problem we were trying to solve (which may not be correct, especially if Q turns out to be < 1):
 
@@
 \end{toolchain}
+
+Each problem has been solved separately.
+There are some nearly equivalent but not mathematically identical formulations for optimal control of quantum systems with dispersion.\footnotemark However, in the classical domain, this appears to be unprecedented in the literature.
+
+\footnotetext{While not strictly related, \cite{Wavepacket1989} tune a light pulse to match the wavefunction of the desired chemical products in a photo-reaction, which is just pretty darned awesome}
+
+Optimal pulses for several situations in Debye and Lorentz media have been determined by Oughstun's asymptotic method, which appears to be highly satisfactory in terms of physical intution, and also avoids truncation issues that befall fourier-transform techniques.
+In general, these optimal pulses are simple gaussian monopulses or higher-order gaussian derivatives \cite{Optimal2017} \cite{Optimal2015}.
+
+Macke \cite{Simple2012} have come up with a number of analytic dispersion representations for various signals, such as chirped gaussian pulses; however, as it turns out, it was important that we not constrain ourselves to parameterized shapes.
 
@@
 
-Each problem has been solved separately.
-There are some nearly equivalent but not mathematically identical formulations for optimal control of quantum systems with dispersion.\footnotemark However, in the classical domain, this appears to be unprecedented in the literature.
-
-\footnotetext{While not strictly related, \cite{Wavepacket1989} tune a light pulse to match the wavefunction of the desired chemical products in a photo-reaction, which is just pretty darned awesome}
-
 Also, this seems similar to a pulse propagating through the tissue's Cole medium and then dissipating the maximum power in a uniform Lorentz medium, which might be another route to attacking it.
@@
 
-Optimal pulses for several situations in Debye and Lorentz media have been determined by Oughstun's asymptotic method, which appears to be highly satisfactory in terms of physical intution, and also avoids truncation issues that befall fourier-transform techniques.
-In general, these optimal pulses are simple gaussian monopulses or higher-order gaussian derivatives \cite{Optimal2017} \cite{Optimal2015}.
-
-Macke \cite{Simple2012} have come up with a number of other analytic dispersion representations for various signals, such as chirped gaussian pulses.
-
 %\printendnotes
@@
 
-The most promising analytical technique that we explored was essentially equivalent to Zhu, Hum, 
-Costas formulation in \cite{Microwave2012b}, previously discussed by Pozar \cite{Waveform2003}, 
-This is based on a lagrange multiplier technique and variational 
-calculus\cite{Methods1989} \footnotetext{Based on personal communication with Professor Costas Sarris}.
+The most promising analytical technique that we explored was a slight modification of a formulation for optimal-energy pulses, largely supplied by Prof.
+Costas Sarris in a yet-unpublished personal communication, based on Zhu, Hum, Costas formulation in \cite{Microwave2012b}, previously discussed by Pozar \cite{Waveform2003}.
+
+This is based on lagrange multipliers and 'functional' or 'variational' calculus\cite{Methods1989}.
+
+Here, rather than taking the derivative with respect to a small change in a variable, we take the derivative with respect to a small change in the function itself - a very useful technique (that the author was not aware of) which imposes little to no limitation on the form of the solution.
+For some intuition, the definition of the first variation and the Gateaux derivative may be of some use.
+
+The Euler-Lagrange equation is usually brought up in the case of the Brachistochrone problem, or 
+the Principle of Least Action \footnote{For background, see The Feynman Lectures, vol II chapter 19}.
+In these types of problems, it appears that the path of integration through space from endpoints a to b can be replaced with the whole frequency domain from -$\infty$ to +$\infty$.
 
@@
 
-Pulse energy, rather than peak field, is not obviously the ideal constraint for this problem; however, it is the one most compatible with lagrange multiplier techniques.
-
-Tufts \cite{Optimum1964}
-
-The Euler-Lagrange equation is usually brought up in the case of the Brachistochrone problem, or 
-the Principle of Least Action (see Feynman lectures). In these types of problems, it appears that 
-the path of integration through space from endpoints a to b is replaced with the whole frequency 
-domain from -$\infty$ to +$\infty$.
-
-Search terms: "first variation", gateaux derivative,
+This lagrange multiplier technique has, however, a fundamental limitation (noted by Tufts \cite{Optimum1964}): for reasons that the author does not comprehend, only the pulse energy can be used as a constraint, rather than the value of the peak field.
+This seems to turn out to be of some importance.
 
@@
 
-Numerically solving optimal control problems using CG was noted by Lasdon \cite{conjugate1967} and 
+Numerically solving optimal control problems using conjugate-gradient was noted by Lasdon \cite{conjugate1967} and 
 revisited by Kek \cite{Conjugate}. They reduce the computational workload by first computing the 
@@
 
+Of course, 10x attenuation at 1 MV/m still takes us outside.
+However, the loss that makes phased-array near-field focusing systems impractical at baseband is no longer a concern.
+A dispersive phased array with more than 10 elements may allow the complete elimination of attenuation without exceeding the limit field at any point in the body.
+
 \end{document}

### 2021-01-28 documents/charge.tex
Brillouin cleanups

@@
 \end{itemize}
+
+Poisson-Boltzmann family of equations is an extension of standard Laplace and Poisson potentials to solutions containing ions.
+
+Most situations solve this in equilibrium. However, we are specifically designing the pulse to be so short that ion equilibriation effects cannot occur.
+
+First the Poisson-Boltzmann equation is run to determine the screened charge density.
+
+$$
 

### 2021-01-29 documents/acknowledgement.tex
gosh darnit

@@
 
+Conflicts of interest
+
+Funded in part by the author's company, SafeSump Inc., and Ideal Consulting Inc., whatever that's worth.
+
 This paper is not novel enough to deserve this chapter, but those to be acknowledged are.
@@
 Special thanks to my parents, Doris and Brian, without whom this work would have been accomplished by someone else, and whose extraordinary support made this paper possible.
+
+Sci-Hub
 
@@
 
-Chengxiang Li and the team of who appear to have spent a decade iterating the Marx avalanche generator we use in this paper. It is an excellent, very high performance design.
+Chengxiang Li and the team of who appear to have spent a half-decade iterating the Marx avalanche generator we use in this paper. It is an excellent, very high performance design.
 

### 2021-01-29 documents/charge.tex
gosh darnit

--- 2021-01-28 documents/charge.tex
@@
 \item Induced polarization
-		Persson cite a re-arrangement of electrons as a source of drag. Polarization-like effects are not expected. We have not followed up on this.
-
+		Persson cite a polarization re-arrangement of electrons as a source of drag. Polarization-like effects are not expected. We have not followed up on this.
 \item 
@@
 
+\section{Weakened phage}
+
+should try weakened phage again!
+
+Poisson-Boltzmann family of equations is an extension of standard Laplace and Poisson potentials to solutions containing ions.
+As with all models, there are many nuances to using these correctly; whether various approximations hold, etc.
+We will ignore all subtleties.
+
+Božič \cite{How2012} consider an empty capsid.
+
+The generalized Poisson equation is
+
+$$\nabla \cdot \left(\epsilon\ \nabla \bar\phi \right) = - \rho$$
+
+We shamelessly steal Brackley \cite{Electrostatic2020}'s formulation (thanks for such detail!)  with one exception.
+Most solutions consider an equilibrium.
+However, we are specifically designing the pulse to be too short for ion equilibriation to occur.
+Therefore we solve in two steps: First the Poisson-Boltzmann equation is run to determine the charge density due to screening; then this is used as a constant to solve when a field is applied.
+
+Reproducing here for convenience:
+
+$$\nabla \cdot \left(\epsilon\ \nabla \bar\phi \right) - \epsilon \kappa^2 \sinh(\bar\phi) = - \rho$$
+
+is the potential in V, kappa is a Debye-Huckel parameter. They use an internal dielectric constant of 5, an external of 80 ($\epsilon =  80\epsilon_0$). 1/10 k1
+
+$$\hat\phi = \frac{e_0 \phi}{}$$
+
+where $e_0$ is the electron charge, $k_b$ the Boltzmann constant, and
+
 effective
+
+\subsection{Empirical methods}
 
@@
 
+electroroattion
+
 It is easy to determine an upper limit.
-
-Božič \cite{How2012} consider an empty capsid.
 
@@
 
+(29.8 kb to 29.9 kbp for NCoV-2 \cite{Genomic2020}).
+
 (these values were only taken at a pH of 7.
@@
 \end{sidenote}
-Assuming a charge of $2e^-$ per base pair due to phosphate groups, the 13.5 kbp of RNA can hardly contribute $> 3e^- \times10^4$
+
+NOTE SSRNA Assuming a charge of $1e^-$ per base pair due to phosphate groups, the 13.5 kbp of ssRNA can hardly contribute $> 1.5e^- \times10^4$
 

### 2021-01-29 documents/detection.tex
Writing notes
Writing, re-organizing references
gosh darnit

@@
 The amount of time and effort we spent here was completely unjustifiable.
-It was driven by an acute lack of competence, equipment, and the small volume constraints of our original poorly designed microwave setup.
+It was driven by an acute lack of competence, equipment, and the 0.8 uL volume constraints of our original poorly designed microwave setup.
 \end{autem}
@@
 
-\subsubsection{Detect the release of intracellular material due to the lysis of the host}
+\subsection{Detect the release of intracellular material due to the lysis of the host}
 
@@
 
-\subsubsection{Detect the lysis of the virus, and the release of intra-viral material}
+\subsection{Detect the lysis of the virus, and the release of intra-viral material}
 
@@
 
-\subsubsection{Directly detect the virus itself}
+\subsection{Directly detect the virus itself}
 

### 2021-01-30 documents/background.tex
gosh darnit
I keep re-writing things but they don't get any better!

@@
 \begin{multicols}{1}
+
+\section{Background}
 
@@
 
-TRL 0
+%3 MV/m * 1000 electronCharge * 1 angstrom / (boltzmannConstant * 310 K) = 1.12 kT
+From a pessimistic energetic perspective, 
+, where 0.1 angstrom is derived from the lipid MD simulation.
+[that's not right!] Compare to ~5 $k_b T$ per protein for capsid binding \cite{Energies2012} \cite{Weak2002} and $ (\text{17 to 78 kJ/mol})  / (310 \text{ K}\ k_b) = $ 6 to 30 $k_b T$ for lipid bilayer pore formation \cite{Atomistic2014a}.
+%17 or 78 kJ/mol / (boltzmannConstant * 310 K) / avogadroConstant = 6.5 to 30.3 kT
 
@@
 Mizuno \cite{Inactivation1990} inactivate SVD Enterovirus (a 27 nm non-enveloped protein encapsidated ssRNA) and EHV (a 100 nm enveloped dsDNA) with 100\% effectiveness with 120 pulses, about 500 nanoseconds each, at 3 MV/m.
-Electron microscopy demonstrates that the mechanism is irreversible damage to the capsid or envelope respectively and release of the core.
+Electron microscopy demonstrates that the mechanism is irreversible damage to the capsid or envelope respectively and subsequent release of the core, and is unlike thermal treatment.
 
@@
 
-In this observation, the thermal artifact cannot necessarily be discounted.
-The energy dissipated was sufficient to cause a significant temperature rise if localized hot-spots appeared \footnote{(43 cal/cc * (3 microliters)) / (3 milligrams * 4.2 J/(g K)) = ~50 $\Delta$C, whereas melting temperatures are typically about 90 C for capsids and 50 C for envelopes\cite{Stability1985}}.
-The electrodes were not insulated, so electrochemical effects are possible but unlikely given the short duration of the pulses.
+Though the temperature was monitored, In this observation, the thermal artifact cannot necessarily be completely discounted.
+The energy dissipated was sufficient to cause a significant temperature rise if localized hot-spots appeared \footnote{(43 cal/cc * (3 microliters)) / (3 milligrams * 4.2 J/(g K)) = ~50 $\Delta$C, whereas melting temperatures are typically about 90 C for capsids \cite{Thermal1999} and 50 C for envelopes\cite{Stability1985}}.
+\\ The electrodes were not insulated, so electrochemical effects are possible but unlikely given the short duration of the pulses.
 \end{autem}
@@
 Both AFM data and surmised from osmotic pressure, the force scale required to crack the viral envelopes and capsids is about 1 nanonewton.
+
+Electrorotation large field but not seen.
 

### 2021-01-30 documents/lessons_learned.tex
Apparent success?
I keep re-writing things but they don't get any better!

@@
 
+There is something of an over-arching lesson learned - maybe it's not actually good to learn this lesson, maybe it's more useful to assume, but...
+
 It is interesting to think about the meta-issues surrounding this project. Beta-glo assay, not a few kilometers away the food bank ran out of food and people were not able.
+
+We have seen time and again that investment in science and technology - even basic research, so distant from the mechanics of society - can produce outsized effects on quality-of-life.
+Both NASA and CERN, neither of which do much related to people, produce a 7-to-1 and 3-to-1 return on investment.
+
+All of which will be a great comfort to the dead.
+
+You could fit a pandemic through a good-sized breakthrough. The vaccines are an excellent example, really. Moreover you learn more to be more useful in the future. Phage display  -
+
+So what went wrong here?
+
+Is it the avenue of investigation? Perhaps a lack of peer input. Maybe there were too few people involved - now that science is "bigger", we need bigger groups to efficiently manage it?
+
+Maybe if you don't have sufficient resources (knowledge, equipment, peers) to persue something efficiently, maybe it's not worth you pursuing it at all.
+
+If a well-stocked lab and a few specialists could have banged this out in a week (which they could), was it worth it to bang this out in a year?
+Did anything actually go wrong, or is this just how it works?
+
+It's interesting thoughts to toy with, but probably not a great idea to get wrapped up in this sort of self-pity and melancholic thinking. Or maybe it is. Who knows.
+
+Doing the same thing that I was doing before - sitting in a basement, working on electronics. What are the odds that the thing that I was doing before was the right thing to do against a virus?
+
+\rule{\linewidth}{0.2pt}
+
+When to publish
+
+One the one hand, there're some pretty good reasons to want embargoes, like the Ingelfinger rules - no need to lather up a furor just for some idle musings, and publishing too early is a terrible idea.
+In retrospect, it was extremely good that I did not make a fuss about some extremely positive data; it turned out to be an embarrassing mistake in
+
+On the other hand, embargo rules came from publishers, and (like ) these decisions were probably somewhat motivated by financial considerations.
+
+There's a recent movement towards more "live" and open science - it's hard to tell when the, especially in a pandemic.
+Fortunately, it's not like any of what we're discussing here actually matters, anyways.
 
@@
 
-It is useful to first strictly implement precisely as written, and only when all parts are operational and understood, begin modifying for your own use.
+It is useful to first strictly implement a method precisely as written, and only when all parts are operational and understood, begin modifying for your own use.
 

### 2021-01-30 documents/molecular_dynamics.tex
still broken sources
More discussion
Building the thing
I keep re-writing things but they don't get any better!

@@
 
-An illustrative - to ensure that there was nothing egregiously wrong with the Stokes drag calculation and to extract various.
-Certainly this has been done dozens of times in the past.
-For other reasons to play around with.
-]\
+An illustrative - to ensure that there was nothing egregiously wrong with the Stokes drag calculation and to extract rotational friction coefficients.
+Certainly equivalent simulations have been done dozens of times in the past.
 
@@
 	\subfloat[Flower one.]{
-	\includegraphics[width=0.4\textwidth]{Vescicle.png}
+	\includegraphics[width=0.4\textwidth]{vescicleds.png}
 
@@
 These results are not in any way quantitative, nor do they truly suggest that the effect exists.
+Critical issues include the lack of deconvolution from the input impulse bandwidth.
 Lipid vesicle simulations with MARTINI force fields have yielded large-scale stiffness values which are orders of magnitude\cite{Determining2014} from those found experimentally; the speed of sound is also.
@@
 A very large amount of tuning and comparison  to obtain any kind of meaningful
+
+the intitial transient must be deconvolved
 
@@
 
-\printbibliography{}
+Interestingly, finite-element analysis appears to be a perfectly sensible approach to coarse-graining, just like might be done with a macro-scale structure.
 

### 2021-01-30 documents/paper.tex
gosh darnit
I keep re-writing things but they don't get any better!

@@
 
+\begin{table}[h!]
+	\centering
+	\begin{tabular}{ |c|c|c|c| } 
+		\hline
+		col1 & col2 & col3 \\
+		\hline
+		& cell2 & cell3 \\ 
+		& cell5 & cell6 \\ 
+		& Negative & 5 \\ 
+		\hline
+	\end{tabular}
+
+	\caption{Data from testing on bacteriophage. Data rounded to the nearest thousand photon counts. Not thoroughly characterized. Repeatability between test conditions   Background was no. 
+	The flurometer printed a constant stream of the integration, all within the random error between capture windows $\sigma=0.5$ kcounts. }
+\end{table}
+
 \begin{figure}[H]
@@
 	\includegraphics[width=\textwidth]{pulse_exposure_setup.JPG}
-	\caption{\\ Pulse exposure jig. Autosampler Pulse shaper not shown. Aluminum disc belongs to the scan-conversion digitizer, not used in this study.}
+	\caption{\\ \textit{Chengxiang} pulse exposure jig.
+pulser seen off the left.
+Autosampler Pulse shaping plate not shown.
+Aluminum disc belongs to the scan-conversion digitizer, not used in this study.}
 \end{figure}
@@
 	\includegraphics[width=\textwidth]{eppenwolf_2.jpg}
-	\caption{\\ The misguided {\it Eppenwolf} pulsed X-Band microwave spectrometer used in this study, pictured with the near-field cuvette installed.}
+	\caption{\\ \textit{Eppenwolf} misguided pulsed X-Band microwave spectrometer used in this study, pictured with the near-field cuvette installed.}
 \end{figure}
@@
 
-The mechanism restricts the possible modes of application; it would be useful to
+\section{Sensing}
 
-\paragraph{\textbf{Personal 'electromagnetic mask'}}\
+There is little discussion on microwave virus detection, with the notable exception of [Mehrotra 2019].
 
-Even with judicious use of phased-arrays, spatial power-combining, etc, each transistor can only reasonably maintain sterility in approx. $ 0.1 \text{ m}^3 $.
+However, \cite{Microwave2012} find that - in controlled conditions - they can detect a single E. Coli bacterium in 50 uL of broth via a microwave cavity.
 
-\paragraph{\textbf{Direct treatments at the fundamental}}\
+Havelka \cite{Highfrequency2011} discuss microtubules.
 
-\paragraph{\textbf{More fanciful concepts}}\
+With an extremely high power excitation pulse, the problem may become somewhat easier; especially if the virus has a ring-down that can be subjected to autocorrelation.
 
-Many systems operate in these X-band frequency ranges; and precision
+However, the dipole radiation power expected in even the most implausibly optimistic case would be about as follows:
 
-It is easy to produce megawatts of power at these frequency ranges using Klystrons.
-Assuming an appropriate antenna, a single 50MW SLAC XL-class klystron with a PRF of 180 Hz could sanitize almost a square kilometer every second.
-\footnote{Giving 'asceptic field' new meaning.}
+$$P={\frac {\mu _{0}(2 \pi \cdot 20 GHz) ^{4}(0.5 \text{nm} * 10^6 e^-)^{2}}{12\pi c}} = 7.1 \times10^{-16} \text{W} $$
 
-On the other hand, if this is conducted in outdoor free-space, sunlight
+which for most reasonable conditions would $\approx 0.5 Janskies$, meaning that the power radiated from the virus would be considerably overpowered by the milky way.
 
-Existing marine, weather, and aviation radar systems often use the X-band; depending on the focusing power
-
-\paragraph{Sensing}
-
-there is little discussion on microwave virus detection, with the notable exception of [Mehrotra 2019].
-Such scholarly silence is usually an indicator that a technique is impossible for reasons so obvious they scarcely bear repeating.
-
-However, [Oberoi 2012] find that - in controlled conditions - they can detect a single E. Coli bacterium in 50 uL of broth via a microwave cavity.
-
-Of course, discriminating miniscule returns in free-space is not easy; but with precise knowledge of this resonance mode, it may become somewhat easier.
-Frequency-domain measurements can be made with incredible precision; and there are many parameters by which virions could be discriminated; ring-up time of the resonance, excitation non-linearity, etc.
+% (magneticConstant*(2 pi * 20 GHz)^4 * (0.1 nm * 1000 * electronCharge)^2)/(12*pi * c) -> W
 
@@
 
+\section{Appendix on microwave design}
+
 \subfile{supplemental}
+
+\section{Appendix on microbiology}
 
@@
 \subfile{detection}
+
+\subfile{lessons_learned}
 

### 2021-01-31 documents/application.tex
Brillouin cleanups
I keep re-writing things but they don't get any better!
goddamnit, going down the same path again...

@@
 
+Assume that the virus has a resonant frequency about 100 V/m.
+
 And so, is it possible to non-invasively produce this effect deep within infected tissue - to break every capsid in the body wholesale?
+
+ Applying microwave power to the body is already used extensively in diathermy (the internal heating of tissue for therapeutic effect) and hyperthermy (the overheating or cauterization of tissue for destructive effect).
+While most diathermy systems use much lower frequencies for deeper penetration, several papers have explored the 10 GHz band.
+
+ Industry Canada only appears to offer an instantaneous limit at $1.35 \times 10^-4$.
+
+ 6 cm of l
+
+ The
+
+ Fat and
+
+ The penetration of microwave power is very sensitive to
+
+ Conduction effects. Because the transmission line voltage only goes as the to the square root of the input power
+
+ There seems to be some sort of focusing effect which makes internal bronchoscopic treatment slightly more effective than might be expected.
 

### 2021-01-31 documents/background.tex
goddamnit, going down the same path again...

@@
 \section{Background}
+
+We were inspired by Yang (gordon reuben following up)
+bona fide clinically useful effect
 
@@
 %3 MV/m * 1000 electronCharge * 1 angstrom / (boltzmannConstant * 310 K) = 1.12 kT
-From a pessimistic energetic perspective, 
+From a pessimistic energetic perspective,  !!! we know what the spring constant k should be !!!
 , where 0.1 angstrom is derived from the lipid MD simulation.
@@
 
-formal literature review; In particular no search criteria were defined.
+formal systematic review; in particular no search criteria were defined.
 
@@
 %
+
+The effects that we are concerned with occur 4 orders of magnitude above
+
+Windows between caused by structural or
 
@@
 
+which establishes that - unique to certain viruses, and apparently unlike human cellular structures, as we shall see - coincidentally have just the right size, shape, stiffness, and net charge distribution to form a weak (Q=2) spherical dipole resonance mode which couples well to the microwave spectrum at approximately 8 GHz.
+
+More critically, [] (and, in parallel, [Hung 2014]) theoretically model and then experimentally validate in various strains of Influenza A that - due to this acoustic-resonance effect - the power density levels required to crack the lipid envelope are near the safety limits for continuous exposure to humans.\footnote{Sort of.
+See below and supplemental.}
+
+They demonstrate this with both a plaque and PCR assay, finding good agreement with the theoretical model.\footnote{As we will discuss, there are a few issues with the experimental technique.; sham, blinding, and dosimetry demanded by [Vjl.] are not mentioned.}
+
+Like pumping a swing, this effect allows an otherwise inconsequential field magnitude to store energy over a small number of cycles until the virus is destroyed. \\
+\\\\
+
+\paragraph{Ramifications}\
+
+\begin{autem}
+
+	{\it autem}\\
+	The previous paragraph may cut an impressive figure; but it hinges on all the rest of this paper being correct.
+
+\end{autem}
+
+\lettrine{It} cannot be overstated how unexpected and positively dubious this finding appears to be - that is, based on our limited research and inexperience to date.
+
+For even the RF power limits set by standards organizations like \cite{ICNIRP2020} \cite{IEEE2006} appear to be based on the observation that no significant resonance modes exist in biological tissues due to damping forces from the surrounding tissue \cite{Vibrational2002}.
+As we shall see, this is grounded in solid {\it in vitro} (albeit more limited {\it in vivo}) evidence.
+
+This may account for why this paper has been largely ignored.
+
+The precise structure and charge of the virion appears to be a singular anomaly in this otherwise categorical non-existence.
+
 \end{multicols}

### 2021-01-31 documents/paper.tex
goddamnit, going down the same path again...

@@
 
-\paragraph{To-do list}
-
-We see the following steps that must be undertaken before production can be started:
-
-\begin{itemize}
-  \item Re-run the experiment with 
-  \item Verify 
-  \item Failure-tree to ensure that power levels can never go above specified values.
-  \item Obtain special permission from the FCC?
-\end{itemize}
-
-\clearpage	
-\begin{multicols}{1}
-
-which establishes that - unique to certain viruses, and apparently unlike human cellular structures, as we shall see - coincidentally have just the right size, shape, stiffness, and net charge distribution to form a weak (Q=2) spherical dipole resonance mode which couples well to the microwave spectrum at approximately 8 GHz.
-
-More critically, [] (and, in parallel, [Hung 2014]) theoretically model and then experimentally validate in various strains of Influenza A that - due to this acoustic-resonance effect - the power density levels required to crack the lipid envelope are near the safety limits for continuous exposure to humans.\footnote{Sort of.
-See below and supplemental.}
-
-They demonstrate this with both a plaque and PCR assay, finding good agreement with the theoretical model.\footnote{As we will discuss, there are a few issues with the experimental technique.; sham, blinding, and dosimetry demanded by [Vjl.] are not mentioned.}
-
-Like pumping a swing, this effect allows an otherwise inconsequential field magnitude to store energy over a small number of cycles until the virus is destroyed. \\
-\\\\
-
-\paragraph{Ramifications}\
-
-\begin{autem}
-
-{\it autem}\\
-The previous paragraph may cut an impressive figure; but it hinges on all the rest of this paper being correct.
-
-\end{autem}
-
-\lettrine{It} cannot be overstated how unexpected and positively dubious this finding appears to be - that is, based on our limited research and inexperience to date.
-
-For even the RF power limits set by standards organizations like \cite{ICNIRP2020} \cite{IEEE2006} appear to be based on the observation that no significant resonance modes exist in biological tissues due to damping forces from the surrounding tissue \cite{Vibrational2002}.
-As we shall see, this is grounded in solid {\it in vitro} (albeit more limited {\it in vivo}) evidence.
-
-This may account for why this paper has been largely ignored.
-
-The precise structure and charge of the virion appears to be a singular anomaly in this otherwise categorical non-existence.
-
-\end{multicols}
-\clearpage
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-Applying microwave power to the body is already used extensively in diathermy (the internal heating of tissue for therapeutic effect) and hyperthermy (the overheating or cauterization of tissue for destructive effect).
-While most diathermy systems use much lower frequencies for deeper penetration, several papers have explored the 10 GHz band.
-
-Industry Canada only appears to offer an instantaneous limit at $1.35 \times 10^-4$.
-
-6 cm of l
-
-The
-
-Fat and
-
-The penetration of microwave power is very sensitive to
-
-Conduction effects. Because the transmission line voltage only goes as the to the square root of the input power
-
-There seems to be some sort of focusing effect which makes internal bronchoscopic treatment slightly more effective than might be expected.
-
 \clearpage
@@
 \clearpage
-
-Of course, this application is hardly much better than an N95 mask, except that it is non-disposable and provides protection for eyes and skin.
-
-Vomit
-
-To the extreme, some papers have used
 
@@
 
+\subfile{sic_susceptor}
+
 \subfile{detection}

### 2021-01-31 biology/simulation/poisson_boltzmann/pb.jl

@@ -1,0 +1,39 @@
+
+#=
+
+don't want to fall into the same trap as with JAMES!
+
+APBE and Pygpe both are more suited for atom-structure-like sims,
+don't seem to support simple dielectrics?
+fenics requires it in a "weak form",
+
+
+
+=#
+
+using PhysicalConstants.CODATA2018
+
+VacuumElectricPermittivity
+
+Nx, Ny, Nz = 100
+
+A = zeros(Nx,Ny,Nz)
+
+dielectric = ones(Nx,Ny,Nz)
+charge_distribution = zeros(Nx,Ny,Nz)
+
+kappa_external =
+
+
+function poisson_boltzmann()
+    for x = 1:Nx-2
+        for y = 1:Nx-2
+            for z = 1:Nx-2
+        (2.0 / )
+        #wait, julia is 1 indexed?
+        # wtf?
+        a1 =
+    end
+
+
+end

### 2021-01-31 electronics/propagation/propagation_numerical_optimize.py

@@ -14,7 +14,7 @@ import dill
 
 
 
-omega_res = 2.0*pi*8e9
+omega_res = 2.0*pi*30e9
 
 electron_charge = 1.602e-19 # Coulomb
 Z0 = 377.0
@@ -28,7 +28,7 @@ q = 10e3 * electron_charge # effective charge -
 picometer = 1e-12
 
 t= 0.0
-z = 0.08
+z = 0.06
 
 
 Q = 1.5
@@ -51,8 +51,10 @@ def debye_refractive_index(omega):
     #refractive index is n = sqrt(mu/epsilon)
     return np.sqrt(eps_inf + (eps_s - eps_inf)/((1.0-1j*omega*tau)*(1.0-1j*omega*tau_f)))
 
+muscle_id = 48
+lung_id = 41
 #cole-cole refractive index
-ef, sigma, deltas, alphas, taus = get_tissue_cole_cole_coefficients(48)
+ef, sigma, deltas, alphas, taus = get_tissue_cole_cole_coefficients(lung_id)
 
 
 #     '''
@@ -62,13 +64,12 @@ ef, sigma, deltas, alphas, taus = get_tissue_cole_cole_coefficients(48)
 
 
 
-def propagate(F, omega, z, oscillator=True):
+def propagate(F, n, omega, z, oscillator=True):
 
     frequency_domain = np.fft.fft(F)
     # greens_function(omega) * q/m_reduced *
 
-    n = np.sqrt(cole_cole_4(omega/(2.0*pi), ef, sigma, deltas, alphas, taus))
-    n[omega == 0] = 1
+
 
     # frequency_domain[(omega/(2.0*pi)) < 1e9] = 0
     # frequency_domain[(omega/(2.0*pi)) > 10e9] = 0
@@ -84,8 +85,8 @@ def propagate(F, omega, z, oscillator=True):
 
 #energy constraint always tends toward a step function
 
-def cost_function(F, omega, z):
-    return abs(-np.max(propagate(F, omega, z))/picometer) + np.max(F**2.0)
+def cost_function(F, n, omega, z):
+    return abs(-np.max(propagate(F, n, omega, z))/picometer) + np.max(F**2.0)
 
 
 
@@ -98,6 +99,8 @@ F=np.ones(samples)
 omega = 2*pi*np.fft.fftfreq(samples)*(samples/(duration*2))
 print(f"Samples: {samples} | < 1e10: {np.count_nonzero(omega < 1e10)}")
 
[…]

### 2021-01-31 biology/simulation/poisson_boltzmann/pb_fenics.py
Poisson boltzmann

@@ -1,0 +1,86 @@
+from fenics import *
+from mshr import *
+
+
+# swf = Point ( 0.0, 0.0, 0.0 )
+# neb = Point ( 10.0, 4.0, 2.0 )
+# mesh = BoxMesh ( swf, neb, 10, 10, 10 )
+# print ( 'Plotting a BoxMesh' )
+# plot ( mesh, title = 'BoxMesh' )
+# filename = 'boxmesh.png'
+# plt.savefig ( filename )
+# print ( 'Graphics saved as "%s"' % ( filename ) )
+# plt.close ( )
+
+# center = Point ( 1.0, 2.0, 3.0 )
+# mesh = generate_mesh ( Sphere ( center, 1 ), 32 )
+# print ( 'Plotting a Sphere Mesh' )
+# plot ( mesh, title = 'Sphere Mesh' )
+# filename = 'spheremesh.png'
+# plt.savefig ( filename )
+# print ( 'Graphics saved as "%s"' % ( filename ) )
+# plt.close ( )
+
+#https://fenicsproject.org/pub/tutorial/html/._ftut1008.html
+# Scaled variables
+L = 1; W = 0.2
+mu = 1
+rho = 1
+delta = W/L
+gamma = 0.4*delta**2
+beta = 1.25
+lambda_ = beta
+g = gamma
+
+# Create mesh and define function space
+mesh = BoxMesh(Point(0, 0, 0), Point(L, W, W), 10, 3, 3)
+V = VectorFunctionSpace(mesh, 'P', 1)
+
+# Define boundary condition
+tol = 1E-14
+
+def clamped_boundary(x, on_boundary):
+    return on_boundary and x[0] < tol
+
+bc = DirichletBC(V, Constant((0, 0, 0)), clamped_boundary)
+
+# Define strain and stress
+
+def epsilon(u):
+    return 0.5*(nabla_grad(u) + nabla_grad(u).T)
+    #return sym(nabla_grad(u))
+
+def sigma(u):
+    return lambda_*nabla_div(u)*Identity(d) + 2*mu*epsilon(u)
+
+# Define variational problem
+u = TrialFunction(V)
+d = u.geometric_dimension()  # space dimension
+v = TestFunction(V)
+f = Constant((0, 0, -rho*g))
+T = Constant((0, 0, 0))
+a = inner(sigma(u), epsilon(v))*dx
+L = dot(f, v)*dx + dot(T, v)*ds
+
+
+# Compute solution
+u = Function(V)
[…]

### 2021-02-01 biology/simulation/poisson_boltzmann/DelPhi/run.sh
delphi

@@ -1,0 +1,1 @@
+~/Programs/delphicpp_v8.4.5_serial 

### 2021-02-01 biology/simulation/poisson_boltzmann/pb.cpp
MEDUSA

@@ -11,9 +11,10 @@
 //
 
 
-const int n = 10;
+const int n = 500;
 const int ncubed = (n*n*n);
-
+const double dl = 1;
+const double dl2 = (1.0/(dl*dl));
 //tolerable even at 700. nice!
 
 uint16_t idx(int x, int y, int z){
@@ -46,6 +47,7 @@ int main(){
 
 
     for(int iter = 0; iter < 5000; iter++){
+        base_type residual = 0;
 
         #pragma omp parallel
         {
@@ -54,26 +56,42 @@ int main(){
                 for(int y = 1; y < n-1; y++){
                     for(int z = 1; z < n-1; z++){
                         base_type value = 0;
-                        value += 1.0*eps[idx(x-1,y,z)] * (V[idx(x-1,y,z)]);
-                        value += 1.0*eps[idx(x,y,z)] * (V[idx(x+1,y,z)]);
-                        value += 1.0*eps[idx(x,y-1,z)] * (V[idx(x,y-1,z)]);
-                        value += 1.0*eps[idx(x,y,z)] * (V[idx(x,y+1,z)]);
-                        value += 1.0*eps[idx(x,y,z-1)] * (V[idx(x,y,z-1)]);
-                        value += 1.0*eps[idx(x,y,z)] * (V[idx(x,y,z+1)]);
+                        // u[i,j,k]= Ap*((u[i+1,j,k]+u[i-1,j,k])
+                        //          + Ay*(u[i,j+1,k]+u[i,j-1,k])
+                        //          + Az*(u[i,j,k+1]+u[i,j,k-1])
+
+                                 // - f[i,j,k])
+                        value += dl2*(V[idx(x+1,y,z)]+V[idx(x-1,y,z)]);
+                        value += dl2*(V[idx(x,y+1,z)]+V[idx(x,y-1,z)]);
+                        value += dl2*(V[idx(x,y,z+1)]+V[idx(x,y,z-1)]);
+
+                        // value += 1.0*eps[idx(x-1,y,z)] * (V[idx(x-1,y,z)]);
+                        // value += 1.0*eps[idx(x,y,z)] * (V[idx(x+1,y,z)]);
+                        // value += 1.0*eps[idx(x,y-1,z)] * (V[idx(x,y-1,z)]);
+                        // value += 1.0*eps[idx(x,y,z)] * (V[idx(x,y+1,z)]);
+                        // value += 1.0*eps[idx(x,y,z-1)] * (V[idx(x,y,z-1)]);
[…]

### 2021-02-03 documents/background.tex
Poisson boltzmann
delphi

@@
 
-We were inspired by Yang (gordon reuben following up)
+\footnote{"nsPEFs"}
+
+We were inspired to undertake this project by a set of publications by Yang et al, Hung et al, Sun et al.
+
 bona fide clinically useful effect
+
+Any technique that requires background subtraction (see).
+
+We distinct regimes, which overlap in physical mechanisms (both involve the charge distribution and relaxation time) but which cite different bodies of literature. Vestiges
+
+frequency-dependent inactivation
+
+(gordon reuben following up)
 
@@
 
-%3 MV/m * 1000 electronCharge * 1 angstrom / (boltzmannConstant * 310 K) = 1.12 kT
+%3 MV/m * 10000 electronCharge * 0.1 angstrom / (boltzmannConstant * 310 K) = 11 kT per cycle
 From a pessimistic energetic perspective,  !!! we know what the spring constant k should be !!!
-, where 0.1 angstrom is derived from the lipid MD simulation.
-[that's not right!] Compare to ~5 $k_b T$ per protein for capsid binding \cite{Energies2012} \cite{Weak2002} and $ (\text{17 to 78 kJ/mol})  / (310 \text{ K}\ k_b) = $ 6 to 30 $k_b T$ for lipid bilayer pore formation \cite{Atomistic2014a}.
+. We can obtain the spring constant $k = \omega_{res}^2 m^*$ from the resonant frequency, where $m^*$ is the reduced mass.
+, where 0.1 angstrom is derived from the lipid MD simulation. [that's not right!]
+
+Compare to ~5 $k_b T$ per protein for capsid binding \cite{Energies2012} \cite{Weak2002} and $ (\text{17 to 78 kJ/mol})  / (310 \text{ K}\ k_b) = $ 6 to 30 $k_b T$ for lipid bilayer pore formation \cite{Atomistic2014a}.
 %17 or 78 kJ/mol / (boltzmannConstant * 310 K) / avogadroConstant = 6.5 to 30.3 kT
+
+%(2*pi*(20 GHz))^2 * 100 MDa to N/m \approx 3000 N/m
+% 1 nanonewton / (3000 N/m) = 3e-13 m
+
+% (2*pi*(5 GHz))^2 * 60 MDa to N/m = 100 N/m
+% 0.1 angstroms
+
+% 1000 N/m = 0.01 Angstroms
 
@@
 \end{itemize}
+
+involving Schnelle
 

### 2021-02-03 documents/charge.tex
goddamnit, going down the same path again...
Poisson boltzmann

--- 2021-01-28 documents/charge.tex
@@
 
-effective
+\subsection{Empirical methods}
+
+Bosch \cite{Studies1985}
 
@@
 	outside of our understanding of DNA or any other molecule.
-
 \end{quote}
@@
 
-Bosch \cite{Studies1985}
-
 \end{document}

### 2021-02-03 documents/poisson_boltzmann.tex
Poisson boltzmann

%!TeX root = poisson_boltzmann
\documentclass[paper.tex]{subfiles}
\begin{document}

\begin{autem}
	TODO: Fix this up. This is a central point that should have been done a long time ago. 
\end{autem}

Poisson-Boltzmann family of equations is an extension of standard Laplace and Poisson potentials to solutions containing ions. It considers an equilibrium. As with all models, there are many nuances to using these correctly; whether various approximations hold, etc. We will ignore all subtleties for now..

\textit{Sparselizard} has built-in support for membranes and stokes drag, and might be a good next step. Almost all finite-element programs require PB to be input in weak form, which is pretty tricky. Sympde can help with the weak form. Medusa allows input in strong form, which is convenient.

Mathematica has great support for FEM, but seems to choke on the nonlinear Poisson-Boltzmann for some reason.

DelPhi poisson-boltzmann solver versions before 6.0 support spherical geometric objects, but flatly refuse to solve a problem this big. A few other solvers exist but are more suited for.

Božič \cite{How2012} consider an empty capsid.

The generalized Poisson equation is

$$\nabla \cdot \left(\epsilon\ \nabla \bar\phi \right) = - \rho$$

We shamelessly steal Brackley \cite{Electrostatic2020}'s formulation (thanks for such detail!) with one exception. Most solutions consider an equilibrium. However, we are specifically designing the pulse to be too short for ion equilibriation to occur. Therefore we solve in two steps: First the Poisson-Boltzmann equation is run to determine the charge density due to screening.

Reproducing here for convenience:

$$\nabla \cdot \left(\epsilon\ \nabla \bar\phi \right) - \epsilon \kappa^2 \sinh(\bar\phi) = - \rho$$

is the potential in V, kappa is a Debye-Huckel parameter. They use an internal dielectric constant of 5, an external of 80 ($\epsilon =  80\epsilon_0$). 1/10 k1

$$\hat\phi = \frac{e_0 \phi}{}$$

where $e_0$ is the electron charge, $k_b$ the Boltzmann constant, and

Brackley provide a very convenient analytical solution to the potential in the solvated two-shell case. With \cite{Deformation1991} \cite{Electrostatic2013}.

With the

\end{document}

### 2021-02-03 documents/brillouin_pulse_math.tex
gosh darnit
Writing!

@@
 	\item The highly dispersive nature of tissue, which causes a peculiar distortion of pulses with broadband spectral content,
-	\item The variation in loss (the imaginary part of the complex permittivity and the penetration depth) versus frequency. 
+	\item The variation in loss (the imaginary part of the complex permittivity and the penetration depth) versus frequency. \wikinote{add image from that mathematica code}
 \end{itemize}
@@
 
-\subsubsection{Zhu et al 's dispersive waveform optimization propagation formulation}
+\subsubsection{Attempt at analytical solution: Zhu et al 's dispersive waveform optimization propagation formulation}
 
@@
 
-The Euler-Lagrange equation is usually brought up in the case of the Brachistochrone problem, or 
-the Principle of Least Action \footnote{For background, see The Feynman Lectures, vol II chapter 19}.
-In these types of problems, it appears that the path of integration through space from endpoints a to b can be replaced with the whole frequency domain from -$\infty$ to +$\infty$.
+A common setup for such a problem is to use the Euler-Lagrange equation; this is usually brought up in the case of the Brachistochrone problem, or the Principle of Least Action \footnote{For background, see The Feynman Lectures, vol II chapter 19}.
+In these types of problems, it appears that the path of integration through space from endpoints a to b is instead replaced by the whole frequency domain from -$\infty$ to +$\infty$.
 
@@
 
+\ghfile{electronics/propagation/propagation_numerical_optimize.py}
+
 However, a maximum absolute value constraint produces fantastic results.
@@
 
+\section{Pulse shaping}
+
+Arbitrary pulses can be formed by
+
 \end{document}

### 2021-02-03 documents/detection.tex
I keep re-writing things but they don't get any better!
Writing!

@@
 \end{autem}
+
+Two
+
+T4r+,
 
@@
 
-The plaque assay for viruses has remained essentially unchanged since Delbruck's era.
+The plaque assay for viruses has remained essentially unchanged since d'Herelle and Delbruck's era.
 
-Advantages over broth methods are the longer infective period without agitation or
+Advantages over broth methods are the apparently longer infective period without agitation or
 
@@
 Incubating the bacterial lawn for sufficient contrast to read the plaques imposes a ~1 to 3 day delay between test and results. Each test requires several dilution tubes
+
+\subsubsection{Protocol and observations}
+
+\begin{toolchain}
+
+To simplify and for higher throughput we use the drop-cast absorption protocol of \cite{Simple2018}, which uses only a single layer of 1\% agar.
+
+150 mL water in a 250 mL beaker covered with alu foil, with stirring, and boiled in a pot of water.
+1.5 grams of nutrient agar powder \footnote{Seaweed Inc, Amazon} was added to 150  until molten.
+A magnetic stir bar was used to ensure all was fully melted,
+and then the beaker was autoclaved for 15 minutes.
+After cooling to 60 C for 25 minutes in a water bath on a hotplate, 20 mL of agar was poured onto [100 mm?] polystyrene plates.
+The plates were left to set, then dried inverted with a flamed bent copper wire spacer for air exchange at 70 C for [1 hours?].
+The plates were then stored inverted in plastic bags at 4 C until use.
+\footnote{How agar percentages are specified seems somewhat ambiguous to me - is the percent of the agar itself (a viscosity measure), or the nutrient-agar mix (a growth measure)?
+	Weight/weight? It appears to be w/v of the whole dry powder in distilled water.}
+
+After cooling, 1 mL of overnight culture was poured across the plate, excess drained onto the next plate, and allowed to dry for 35 minutes at room temperature.
+
+A control plate was made with pure stock phage and autoclaved phage.
+
+The sample was retrieved from the cuvette by carefully removing the tape backing and withdrawing 0.8 uL from the reverse side, to avoid a silicone oil bubble.
+
+Unfortunately, this ended up being very inconsistent.
+
+Not having a 10 uL pipette, the 0.8 uL sample of phage was diluted in 7.5 uL of sterile broth in a microplate, then all 7.5 uL was added in 2.5 uL steps to the agar.
+
+\st{Each 0.8 uL sample was diluted in 0.2 mL of nutrient broth, a 250x dilution. If the $10^6$ pfu.}
+
+60c to pour was I think too high - condensation was high, even after 1 hour at 37c no change.
+
+". The dryness of the agar is very important; if too moist, the
+drops will run and coalesce, if too dry, the bacteria will grow
+poorly"
+
+The plates were dried at ~70 C in an oven with the slightly open.
+
+The plates were incubated overnight. The lawn was very nicely formed; the phage concentration was
+
+It was difficult to tell where the drops were placed, and they ran together.
+
+\begin{figure}[H]
+	\captionsetup{singlelinecheck = false, justification=justified}
+	\centering
+	\includegraphics[width=\textwidth]{plaque_assay}
+\end{figure}
+
+\end{toolchain}
 
@@
 GFP
+
+\subsubsection{Impedance assay}
+
+Because it would be difficult to maintain temperature on and multiplexing was difficult, low-frequency E. coli culture monitoring impedance spectra were performed separately.
+
+An ultra-simple KHz impedance spectrometer was built, following \cite{unconventional2015}.
+
+Purely contactless, capacitively coupled impedance measurement was found to have an unworkably small signal level;
+however, a single conduction path and a single capacitive coupling through the Kapton film yielded a 10 mV signal level with 5V Vpp drive. A 110x amplifier was used to bring levels up.
+
+0.7 mm gold-plated spring pins ('pogo' pins) pierced the silicone oil layer and pressed against the bottom tape; 1.4 mm pads were the second electrode.\footnote{Platinum, gold wire, anodized aluminum, or graphite would likely have worked equally well.} The pins were wiped with 99\% alcohol before each test.
+
+2.5 uL stationary e. coli culture was added to 5 uL broth and 2.5 uL phage or autoclaved phage.
+
+0 - 3 were phage; 4-7 were autoclaved phage.
+
+Failure. decrease in signal rather than the expected increase, and no difference between autoclaved and phage.
+
+Looking at this later - the fluid has leaked out of the wells after some time. That might be why this didn't work.
+
+\section{E. coli flavin autofluorescence}
+
+Added 2.5 uL to 5 uL broth. There does seem to be an fluorescence signal from; 100 uS long pulse, -70 mV is a good threshold.
+Hz w/e.c, 2.9-5 Hz broth
+
+Put the original eppendorf culture full of e. coli in. Jumped to 18 Hz @ -81 mV! Fantastic!
+
+Thought I was all clever-like, using the oscope trigger out as the comparator and plugging that into a counter,
+but above 20 Hz there's no thingy.
+
+No. No go.
+
+Weird background noise.
+
+" By moving into this hydrophobic environment and away from the solvent, the ethidium cation is forced to shed any water molecules that were associated with it.
+As water is a highly efficient fluorescence quencher, the removal of these water molecules allows the ethidium to fluoresce.[citation needed]"
 
@@
 
+\subsubsection{Nucleic acid UV extinction }
+
+The 260 nm extinction due to 60 MDa DNA at concentration $10^8 = 10e-9$. With a 1 mm path length is 0.002x. that's going to be swamped by everything else.
+
 \subsection{Directly detect the virus itself}

### 2021-02-03 documents/experiment_1.tex
Writing!

%!TeX root = experiment_1
\documentclass[paper.tex]{subfiles}
\begin{document}

\section{Experiment 1: Attempts at microwave absorption spectroscopy and

\section{Microwave lysis feedback}

We postulate the following. When the virus is lysed, the resonator is destroyed. This should be reflected in the impedance spectrum.
We expect a non-reversible decrease in the resonance peak after the application of power. This should also appear in the time-domain pulse envelope; we expect a "notch" on the rising edge, with a slow taper upwards, which does not repeat on the next pulse.

If this exists, it would provide a great deal of feedback. Not only would the virus be destroyed, but we would have an instant, quantitative determination of of how effective each treatment was. In practice, this could be done by applying two pulses in quick succession and monitoring the change in the reflected power; or perhaps by a time-domain pulse-shape method. Whether such a signature can be discriminated from background in a clinical setting remains to be seen.

At the time, this seemed important to establish, as it would allow the inactivation threshold to be determined without a time-intensive and potentially dangerous infectivity assay step (making it more plausible that we would get biosafety approval on NCoV).

One could imagine it to be otherwise. For instance, the lysis that occurs after phage infection of bacteria does little harm to the cell; only the permeability of the membrane is damaged\cite{GROWTH}. Similarly, the results of the previous studies could perhaps have been obtained without necessarily breaking the virus' envelope.

\end{document}

### 2021-02-08 documents/background.tex
Restructuring, maybe?
words

@@
 
+ (of course, it turns out )
+
+There are some 20,000 papers on the topic of RF safety, with solid mechanistic, in vitro, in vivo and epidemiological evidence of safety in the 2.4 GHz and 5.8 GHz bands.
+
+However, "There are limited experimental human data upon which to set limits on exposures above 6 GHz" [Chan 2019]. Only 2\% of the above papers are on frequencies $>6$ GHz [Vijayalaxmi 2018].
+
+In addition, what data remains in this category is of varying quality.
+
+As has been starkly demonstrated in the recent hydroxychloroquine contradictions [Gautret 2020] [Geleris 2020], biological research must be essentially perfectly conducted to offer any meaningful results.
+
+So, turning to, we find an entirely new set of problems.
+This effect is presumed to depend on mechanical forces of the entire virus.
+The large scales of physical virology all but prevent all-atom simulations that include the genome, but the genome is essential to the effectiveness of this technique.
+The same reasons currently rule out simulations including chemical reactions, important for lipid oxidation effects.
+Attempts at coarse-graining require careful tuning \footnote{or "parameterizing" in MD parlance}, where slight mis-steps in problem setup can lead to unphysical effects that completely alter the conclusion, particularly where solvent polarization.
+The kind which can only be obtained through extensive hard-wrought expertise (which the author does not possess) and careful verification,
+
+Multiscale or hybrid techniques would seem to offer one route out of this pickle. Simulating a small patch of lipid in explicit solvent, with the pressure provided by
+
+The stymied writer turns to writing inconclusive high-level summaries which lack sufficient detail to be of true use.
+
 \footnote{"nsPEFs"}
@@
 
-bona fide clinically useful effect
+We put some
+
+which establishes that - unique to certain viruses, and apparently unlike human cellular structures, as we shall see - coincidentally have just the right size, shape, stiffness, and net charge distribution to form a weak (Q=2) spherical dipole resonance mode which couples well to the microwave spectrum at approximately 8 GHz.
+
+More critically, [] (and, in parallel, [Hung 2014]) theoretically model and then experimentally validate in various strains of Influenza A that - due to this acoustic-resonance effect - the power density levels required to crack the lipid envelope are near the safety limits for continuous exposure to humans.
+
+The experiments are competently designed and many orthogonal measurements are made to confirm the effect.
+
+There are a few minor issues with the experimental technique; sham, blinding, and dosimetry demanded by Vjl. are not mentioned.
+
+\lettrine{U}nfortunately, we later realized that for both the absorption cross section and the requires the virus, a structure with not more than $6 \times 10^8$ atoms, to have an effective charge of $q=10^7$.
+It is very difficult to account for such a charge by any known mechanisms.
+
+% 300 MDa of hydrogen has 3e8 H atoms
+% ((100 nm)^3 * (1000 kg/m^3))/((18.15 g/mol) / avogadroConstant)
+% 600 MDa
+
+While induced polarization is not expected to occur on GHz time scales, especially where solvent ions are the charge carriers, (see ICNIRP arguments), it is possible that some subtle, extremely fast polarization effect regarding electrons could be used to explain this \cite{nature1986}.
+We have not investigated this in any depth.
+
+In another attempt to explain non-thermally, it is possible that this result could be explained by lipid membrane leakage, attributed to oxidation, which has been observed in strikingly similar regime in liposomes; but this would not necessarily explain the frequency-dependent inactivation seen in Figure 4b of \cite{Efficient2015}.
+
+We are thoroughly mystified by the data presented.
+For the purposes of this paper, we accept a working hypothesis that this does not represent a clinically useful effect - especially as the exposures required are close to - or greatly exceed - the thermal limit for safety.
+
+In any case, this is a very interesting result, and should be replicated with better controls.
+Gordon Reuben's team appear to be on the case, so we will not address this regime, 100 V/m, 15 minute, 8 GHz, any further.
+
+We leave this section here because it will be useful to inform us in the next section.
+
+First, free-space techniques are easily implemented to prevent respiratory transmission. A \$10 emitter appears to suffice on a personal level, and \$100 systems for room-scale.\\
+
+Second, via cursory FDTD simulations, using off-the-shelf equipment and modified non-invasive microwave diathermy techniques, it appears to be possible to inactivate all virions in the outer 2 cm of the lungs and inner 1 cm of the bronchi without any effect on the surrounding tissue.
+
+One might be tempted to cite long wavelength of microwaves as an advantage. A UV photon is approximately the same wavelength as the virus itself;  In the case of, the wavelength is >> diameter, d
+
+Like pumping a swing, this effect allows an otherwise inconsequential field magnitude to store energy over a small number of cycles until the virus is destroyed. \\
+\\\\
+
+If this mechanism exists, it would seem to provide significant advantages over existing UV or cold-plasma sterilization.
+
+If the extensions made in our paper are valid, this is a non-ionizing, non-thermal
+
+, non-chemical technique, harmless for continuous exposure to tissue, which can sterilize air and surfaces alike, including skin, eyes, and within hair; it evolves no ozone, can readily be generated with \$1 USD - scale devices, acts instantaneously, and - perhaps most critically - could be made to act {\bf within infected tissues}.
+
+\footnote{It should be noted that this {\it confined} acoustic resonance is subtly distinct from common-and-garden pipe-organ acoustic resonance; this is apparently not a strictly classical phenomenon.
+Besides standard Coulomb-like and Lennard-Jones-like interactions between constituent particles, if Fr\"{o}hlich is to be believed at these nanoscopic scales there are also wave-function interactions among the particles of the virus which can shift storage to modes not otherwise expected.
+
+	We confess to not yet understanding this phenomenon; fortunately, while helpful, the details of how this mode appears are not critical to implementing this technique.}
+
+\footnote{All values have been converted to $\text{W/m}^2$ to avoid confusion. 100 $\text{W/m}^2 = 10 \text{ mW/cm}^2 = 10 \text{ dBm/cm}^2$.}
+
+the only analagous non-thermal mechansism we are aware of is electroporation; and that requires the diffusion of ionized sodium and potassium charge carriers through the membrane, which would seem to necessarily require a non-
+
+So far as we are aware, there are no fundamental physical obstacles to non-thermal effects in biological systems.
+As an example, electroporation is a well-established - now a common laboratory procedure, in which an enormous electric field causes ions in solution to migrate across the membrane,
+
+Such a non-thermal mechanism is quite unprecedented and extremely dubious, oft-posited but never substantiated; so it has taken some convincing that this is not a particularly abstruse artifact, especially when considered in the context of the broader non-thermal effects literature.
+For instance, the very paper (Edwards) which spurred development of the hydration-layer damping hypothesis used to explain these results, is has been quite\cite{Resonances1987} definitively\cite{Microwave1993a} shown to be an artifact, one which we unfortunately have not excluded in our study.\ In fact, even in light of the fine evidence that the other groups have collected, and the poor-quality data we have collected, we are still not entirely convinced that this effect exists - but perhaps this skepticism is unjustified.\\
+
+\lettrine{It} cannot be overstated how unexpected and positively dubious this finding appears to be - that is, based on our limited research and inexperience to date.
+
+For even the RF power limits set by standards organizations like \cite{ICNIRP2020} \cite{IEEE2006} appear to be based on the observation that no significant resonance modes exist in biological tissues due to damping forces from the surrounding tissue \cite{Vibrational2002}.
+As we shall see, this is grounded in solid {\it in vitro} (albeit more limited {\it in vivo}) evidence.
+
+This may account for why this paper has been largely ignored.
+
+The precise structure and charge of the virion appears to be a singular anomaly in this otherwise categorical non-existence.
 
@@
 %3 MV/m * 10000 electronCharge * 0.1 angstrom / (boltzmannConstant * 310 K) = 11 kT per cycle
-From a pessimistic energetic perspective,  !!! we know what the spring constant k should be !!!
-. We can obtain the spring constant $k = \omega_{res}^2 m^*$ from the resonant frequency, where $m^*$ is the reduced mass.
-, where 0.1 angstrom is derived from the lipid MD simulation. [that's not right!]
+%3 MV/m * 10000 electronCharge * 0.1 angstrom / (boltzmannConstant * 310 K) = 11 kT per cycle
+From an energetics perspective, we can obtain the spring constant $k = \omega_{res}^2 m^*$ from the resonant frequency, where $m^*$ is the reduced mass.
+With relatively sane choices of screened charge and resonant frequency, the energy per monocycle at 5 MV/m varies from 0.01 to 20 times the thermal energy $k_b T$.
 
@@
 
-Unfortunately, the experimental results on M13 appear to have completely failed replication by Wigle \cite{No2011}, and those on lymphocytes do not agree with existing literature by two orders of magnitude \cite{Targeted2002}, observing that over 1 TW of incident power is required to reproduce the effects by .
+Unfortunately, the experimental results on M13 appear to have completely failed replication by Wigle \cite{No2011}, and those on lymphocytes do not agree with existing literature by two orders of magnitude \cite{Targeted2002}, observing that over 1 T$\text{W/m}^2$ of incident power is required to reproduce the effects by .
 
-1 TW / (100 ps / 0.3 ps) = 3 GW
+$1\ \text{TW/m}^2 / (100\ \text{ps} / 0.3\ \text{ps}) = 3\ \text{GW/m}^2$
 
@@
 
-If this mechanism exists, it would seem to provide significant advantages over existing UV or cold-plasma sterilization.
-
-If the extensions made in our paper are valid, this is a non-ionizing, non-thermal
-
-, non-chemical technique, harmless for continuous exposure to tissue, which can sterilize air and surfaces alike, including skin, eyes, and within hair; it evolves no ozone, can readily be generated with \$1 USD - scale devices, acts instantaneously, and - perhaps most critically - could be made to act {\bf within infected tissues}.
-
-\footnote{It should be noted that this {\it confined} acoustic resonance is subtly distinct from common-and-garden pipe-organ acoustic resonance; this is apparently not a strictly classical phenomenon.
-Besides standard Coulomb-like and Lennard-Jones-like interactions between constituent particles, if Fr\"{o}hlich is to be believed at these nanoscopic scales there are also wave-function interactions among the particles of the virus which can shift storage to modes not otherwise expected.
-
-	We confess to not yet understanding this phenomenon; fortunately, while helpful, the details of how this mode appears are not critical to implementing this technique.}
-
-\footnote{All values have been converted to $\text{W/m}^2$ to avoid confusion. 100 $\text{W/m}^2 = 10 \text{ mW/cm}^2 = 10 \text{ dBm/cm}^2$.}
-
-the only analagous non-thermal mechansism we are aware of is electroporation; and that requires the diffusion of ionized sodium and potassium charge carriers through the membrane, which would seem to necessarily require a non-
-
-So far as we are aware, there are no fundamental physical obstacles to non-thermal effects in biological systems.
-As an example, electroporation is a well-established - now a common laboratory procedure, in which an enormous electric field causes ions in solution to migrate across the membrane,
-
-However, there equally appear to be no fundamental reasons why some small-molecule drug could not bind to the wrong receptor, why
+It is common for.
+However, non-zero resonant frequency requires the ratio of the the loss in energy to the surroundings to the mass, to be greater than $b/(2m) < \omega_{res} \sqrt{2}$ \cite{Driven}; the solution to the harmonic oscillator equation is piecewise around this value.
 
@@
 
-Notice that a non-zero resonant frequency
-requires $\beta = b/(2m) \i-t \sqrt{2}$ \cite{Driven}
+Indeed, relatively trustworthy time-domain spectroscopy of proteins \cite{Microwave1994} has found that the relaxation time is proportional to the molecular weight of the structure (of which viruses are perhaps the ultimate example), and can be as slow as 100 MHz in some cases.
 
@@
 
-\section{Matters to consider in the design of experiments and the evaluation of literature}
+\clearpage
+\end{multicols}
+\section{Commentary on the Sun group results; matters to consider in the design of experiments and the evaluation of literature}
 
-\subsection{Artifacts in past absorption spectroscopy experiments, and the subsequent development and debunking of non-classical damping hypotheses}
+When confronted by an extremely surprising and novel result, it seems useful to consider precisely where deficiencies may lie, so that our follow up work might address these concerns; to consider all the ways in which the ultimate conclusion could be falsified; in this case, by exploring what ways the observed facts could be explained without invoking non-thermal mechanisms, so that scope for such explanations may later be reduced.
 
-Edwards et al in 1984 and 1985 measured the reflection from an open-ended coaxial line dipped in DNA solution and found that DNA appeared to produce a resonance-like peak.
+\begin{toolchain}
+We must now stress decisively that, as with all scientific critique, this commentary must not be construed as a reflection on the quality of the original study, and especially not towards its authors.\\
 
-Such an effect is so unexpected - Bigio et al describe it as “astonishing”.
+We are adamant that, in all cases cited, we believe their studies were well designed and conducted: the authors went to considerable and sufficient lengths to demonstrate its validity. 
+\end{toolchain}
+
+\begin{fquote}[Professor David Baltimore][\cite{Issues2008}]
+	The scientific literature is a conversation among scientists; we describe to each other what we have done, and we implicitly ask our colleagues to try to build on our results, testing their value and their ability to support a growing edifice.
+
+	In fact, a scientist's first response upon reading a new paper may be to see a new interpretation, to conceive a different experiment that could provide a wholly new thrust for the paper.
+This is a thought process that is encouraged in all young scientists, and it is one of the driving forces in science.
+\end{fquote}
+
+\begin{multicols}{1}
+
+\subsection{Artifacts in past absorption spectroscopy experiments, and the subsequent development and invalidation of non-classical damping hypotheses}
+
+Edwards et al in a series papers in 1984 and 1985 measured the reflection from an open-ended coaxial line dipped in DNA solution and found that DNA appeared to produce a resonance-like peak in the absorption spectrum.
+
+Such an effect is so unexpected - Bigio et al describe it as “astonishing”. \\
+
 Edwards hypothesized that the outer hydration layers could have a sort of elastic, non-viscous isolating effect.
-This result seems to have triggered a large amount of work to model this interaction, and various other interactions, in an attempt to explain the observed resonance.
+
+This result seems to have triggered a large amount of work, both theoretical and experimental\cite{Structure1989}, in an attempt to model this interaction, and various other similar interactions, in an attempt to explain the observed resonance.
 
@@
 In the case of the virus, for instance, the expected amplitude of oscillation for which this mechanism applies is on the order of one water molecule (~0.1 nm).
+Indeed, it is now well-known that the layers formed by explicit solvents have significant effect on the conformations of proteins.
 
-Treating the interaction between the first few solvent layers surrounding some biological structure is indeed quite difficult; we encountered this in trying to setup MD This can be seen in [MD paper], so it is reasonable that continuum-like damping assumptions might break down.
-
-In the case of a uniform rotating sphere, for instance, the [Einstein - ?] viscous drag force diverges strikingly from the continuum hypothesis toward zero.
+In the case of a uniform rotating sphere\cite{Molecular1963}, for instance, continuum Einsten-Stokes drag and discrete molecular drag diverge completely!
 
@@
 
-In Bigio’s words “Extreme care”. Because it involves a differential measurement of two samples.
+The same issue, where a resonance is reported using microwave spectroscopy and subsequently irreplicable has occurred many times in the past - with Hagmann and Gandhi \cite{Substitution1982}.
 
-Hagmann and Gandhi \cite{Substitution1982}
+In Bigio’s words “Extreme care”. Because it necessarily involves performing differential measurement of two samples, subtracting an enormous background from a minuscule sample.
+
+Of course, such subtraction and de-embedding are very common techniques in the
+
+In terms of volume, the
+
+%((120 nm)^3 * 10^13) / 50 ml = 0.035%
+
+Whereas a 50 microliter pipette will have a volume tolerance of 2\%!
+
+Indeed, a sample of on a diean E5000 dielectric resonator
+
+The difficulty is that the loss tangent of water varies fro about 0.3 at 6 GHz to 0.45 at 10 GHz \cite{Metamaterial2015}.
+A microstrip might optimistically have a loss of 0.315 dB/cm - perhaps 2.5 or to 5\% power loss.
+
+$$f = \frac{233}{\sqrt{e_r}\cdot{V^{1/3}}}$$
+
+%((1e7 * (electron charge) * 100 V/m)^2 / ((2*pi*(5 GHz))^2 * 50 MDa) * (10^13 / ml) * (50 microliter)) / (100 ps) = 1.56628917 watts
+
+% 1 nanonewton * 1 nanometer  * 10^13
 
@@
 
-In the case of our crude, amateurish equipment, by making completely justifiable changes in calibration and post-processing correction for thermal drift, normalization, etc, we could produce a resonance mode at almost any frequency we liked.
-We were able to produce many candidate peaks even in pure water.
+In the case of our (admittedly crude, amateurish equipment), by making completely justifiable changes in calibration and post-processing correction for thermal drift, normalization, etc, we could produce a resonance mode at almost any frequency we liked.
+We were able to produce a candidate resonance even in pure water.
 
@@
 
-However, as Foster et al demonstrated, there is nothing necessarily wrong with VNA-based dielectric spectroscopy if it is well conducted.
-The Sun group seem very competent experimenters, and the experiments are very well conducted; but history would seem to suggest that we take some degree of caution.
+However, as Foster et al demonstrated, there is nothing necessarily wrong with VNA-based dielectric spectroscopy if it is well conducted; but history would seem to suggest that we take some degree of caution with such results.
 
 \subsection{Thermal controls}
+
+As any researchers who have scalded their mouths on a cheap dinner may know, microwave irradiation can produce unintuitive temperature gradients, with local hot-spots that can be difficult to measure directly.
 
@@
 
-As any researchers who have scalded their mouths on a cheap dinner may know, microwave irradiation can produce unintuitive temperature gradients, with local hot-spots that can be difficult to measure directly.
-
 Kozempel \cite{Preliminary1997} and \cite{Inactivationa}.
@@
 
-We do not intend to denigrate the work or otherwise cast aspersions on the authors of the mentioned papers; their experiment extremely well-designed and performed.
-
-However, since the result is unexpected, we would like to mention a few means by which the effect described could be achieved without strong non-thermal coupling.
-
 \begin{quote}
@@
 \end{quote}
+
+Glass and water are not infrared transmissible; only the surface temperature of the sample can be measured.
 
@@
 Therefore, every part of the experimental protocol should be maintained precisely identical for non-sham and thermal sham trials.
+
+Electrochemical the presence of various ions
+
+$20 \text{W/m}^2 * 6 minutes to \text{J/m}^2 = 7200 \text{J/m}^2$
 
@@
 
-Previous works (Liu et al, ) appear to demonstrate that several species of viruses exhibit an anomalous dielectric relaxation time of $> 75 \text{ ps}$, as opposed to $<< 20 \text{ ps}$ \footnotemark measured in the structures of human tissue.\\
-
-Other studies (Yang et al, Hung et al, Sun et al) then appear to demonstrate experimentally that - due to this effect and the favorable combination of envelope and genome net charge, envelope and capsid yield stress, mass distribution, and overall stiffness - certain viruses can  apparently be made to ring up, leading their envelope to shatter, when exposed to intense but ostensibly safe CW tones in the X-band - very much like a singer might shatter a wine glass.\\
-
-Such a non-thermal mechanism is quite unprecedented and extremely dubious, oft-posited but never substantiated; so it has taken some convincing that this is not a particularly abstruse artifact, especially when considered in the context of the broader non-thermal effects literature.
-For instance, the very paper (Edwards) which spurred development of the hydration-layer damping hypothesis used to explain these results, is has been quite\cite{Resonances1987} definitively\cite{Microwave1993a} shown to be an artifact, one which we unfortunately have not excluded in our study.\footnotemark \ In fact, even in light of the fine evidence that the other groups have collected, and the poor-quality data we have collected, we are still not entirely convinced that this effect exists - but perhaps this skepticism is unjustified.\\
-
-\footnotetext{we should verify, based on simple solvated sphere damping, whether the damping is of the right order of magnitude}
-
-We contribute almost nothing to the record (much of our discussion has already been covered by []), except by apparently replicating the effect in a T4 bacteriophage surrogate, using both microwave feedback and a luminometric beta-galactosidase infectivity assay.
-We appear to demonstrate that inactivation does not require 15 minutes, but is complete in less than 500 nanoseconds.
-This provides a headroom of some $10^6$ to all safety limits imposed by all known harm mechanisms, which can be traded for depth in tissue or distance in space.
-\\
-
-This technique appears to be unique in that it is selective, save for Far UV or cold-plasma sterilization.
-Its advantages over those is that it operates over large volumes with inexpensive emitters, but, most critically, can be made to penetrate tissue without harm.
-
-We briefly review the biological basis for the safety. There is solid in vitro and limited in vivo evidence of safety in this regime.
+ $<< 20 \text{ ps}$ \footnotemark measured in the structures of human tissue.\\
 
@@
 
-We briefly examine three applications.
-All depend significantly on what the microwave spectrum of SARS-NCoV-2 ends up being, which must be measured - or possibly reconstructed from existing whole-virion data or determined from coarse-grained MD simulation.
-
-With refinements, our inexpensive pulsed microwave spectrometer can obtain the required absorption and threshold data with sufficiently concentrated specimens; but proper dielectric spectroscopy labs (or, in a pinch, swept-EPR/ESR equipment \st{when used improperly}) will provide a much more detailed spectrum.
-A slightly safer low-titer primary specimen may be usable to avoid BSL-3 requirements.
-\\
-
-First, free-space techniques are easily implemented to prevent respiratory transmission. A \$10 emitter appears to suffice on a personal level, and \$100 systems for room-scale.\\
-
-%
-Second, via cursory FDTD simulations, using off-the-shelf equipment and modified non-invasive microwave diathermy techniques, it appears to be possible to inactivate all virions in the outer 2 cm of the lungs and inner 1 cm of the bronchi without any effect on the surrounding tissue.
-\\
-
-[] notes that with a bit more effort, by harnessing the dispersive nature of tissue using modulated Brillouin precursors, it may be possible to remove the virus from the body altogether.\\
-
-The mechanism also provides a few distinctive microwave signatures that may be useful for detection; it remains to be seen whether these can be discerned in practice.
-
-The claims above are extraordinary.
-We do not provide the extraordinary quality of evidence required to support them.
-Consider: is it more likely that an undergraduate in his parent's basement, with no experience in biology or microwave design, has misinterpreted a blip from a cobbled-together machine, or that
-
-expelling its viral contents into solution and
-
-Not to be confused with pseudoscientific 'resonance therapies', nor reports of a connection with 5G communications.
-
-This means that the technique is {\it selective}.
-
-which establishes that - unique to certain viruses, and apparently unlike human cellular structures, as we shall see - coincidentally have just the right size, shape, stiffness, and net charge distribution to form a weak (Q=2) spherical dipole resonance mode which couples well to the microwave spectrum at approximately 8 GHz.
-
-More critically, [] (and, in parallel, [Hung 2014]) theoretically model and then experimentally validate in various strains of Influenza A that - due to this acoustic-resonance effect - the power density levels required to crack the lipid envelope are near the safety limits for continuous exposure to humans.\footnote{Sort of.
-See below and supplemental.}
-
-They demonstrate this with both a plaque and PCR assay, finding good agreement with the theoretical model.\footnote{As we will discuss, there are a few issues with the experimental technique.; sham, blinding, and dosimetry demanded by [Vjl.] are not mentioned.}
-
-Like pumping a swing, this effect allows an otherwise inconsequential field magnitude to store energy over a small number of cycles until the virus is destroyed. \\
-\\\\
-
-\paragraph{Ramifications}\
-
-\begin{autem}
-
-	{\it autem}\\
-	The previous paragraph may cut an impressive figure; but it hinges on all the rest of this paper being correct.
-
-\end{autem}
-
-\lettrine{It} cannot be overstated how unexpected and positively dubious this finding appears to be - that is, based on our limited research and inexperience to date.
-
-For even the RF power limits set by standards organizations like \cite{ICNIRP2020} \cite{IEEE2006} appear to be based on the observation that no significant resonance modes exist in biological tissues due to damping forces from the surrounding tissue \cite{Vibrational2002}.
-As we shall see, this is grounded in solid {\it in vitro} (albeit more limited {\it in vivo}) evidence.
-
-This may account for why this paper has been largely ignored.
-
-The precise structure and charge of the virion appears to be a singular anomaly in this otherwise categorical non-existence.
+This technique appears to be unique in that it is selective, save for Far UV or cold-plasma sterilization.
+Its advantages over those is that it operates over large volumes with inexpensive emitters, but, most critically, can be made to penetrate tissue without harm.
 

### 2021-02-08 documents/comment.tex
Writing, re-organizing references
words

@@
 mechanisms for such an effect exist to account for Sun et al's observations. For instance, see 
-Liburdy's observations of liposome leakage due to oxygen.
+Liburdy's observations of liposome leakage due to oxidation.
 
@@
 
-The temperature is measured via a conventional infrared thermometer to be below the lipid melting point, but is otherwise uncontrolled.
-Previous experiments have shown that such readings are not sufficient to isolate non-thermal effects.
+The temperature is measured via a conventional infrared thermograph to be below the lipid melting point, but is otherwise uncontrolled.
+Previous experiments have shown that such readings are not sufficient to isolate non-thermal effects with continuous wave exposures.
 
@@
 If the effect is thermal, why would the peak of the inactivation curve lie correspond perfectly to the one obtained by spectroscopy?
-The gain flatness of the antenna and amplifier may
+The gain flatness of the antenna and amplifier may be an explanation.
 
 {\Huge \textbf{However}}
+
+The fundamental idea of inducing mechanical stresses with large electric fields is quite interesting.
+
+these lines are not obviously damaging to tissue, even in-vivo, per NATO 
+Research Task Group 189.
+
+Mizuno \cite{Inactivation1990} inactivate SVD Enterovirus (a 27 nm non-enveloped protein encapsidated ssRNA) and EHV (a 100 nm enveloped dsDNA) with 100\% effectiveness with 120 pulses, about 500 nanoseconds each, at 3 MV/m.
+Electron microscopy demonstrates that the mechanism is irreversible damage to the capsid or envelope respectively and subsequent release of the core, and is somewhat unlike thermal treatment.
+
+\begin{autem}
+	Extreme care must be taken in interpreting the results of any one study in isolation, especially in this field.
+
+	Though the temperature was monitored, In this observation, the thermal artifact cannot necessarily be completely discounted.
+The energy dissipated was sufficient to cause a significant temperature rise if localized hot-spots appeared \footnote{(43 cal/cc * (3 microliters)) / (3 milligrams * 4.2 J/(g K)) = ~50 $\Delta$C, whereas melting temperatures are typically about 90 C for capsids \cite{Thermal1999} and 50 C for envelopes\cite{Stability1985}}.
+\\ The electrodes were not insulated, so electrochemical effects are possible but unlikely given the short duration of the pulses.
+\end{autem}
+
+Madiyar \cite{Manipulation2013} observe rapid permeabilization (likely through the slow, conventional electroporation mechanism) at a field of poorly-defined intensity up to about 10 MV/m, in the Vaccinia poxvirus (a 300 nm enveloped dsDNA virus).
+\cite{AC2017}.
+Interestingly, the same effect is not observed in T4 bacteriophage.
 
@@
 As noted in the papers, unlike other biological systems it's plausible that the virion would have modes that are at least very close to being under-damped.
-Burkhartsmeyer offer reasonable evidence for this (although resonance-like artifacts are not unheard-of in Raman spectroscopy).
+Burkhartsmeyer and the Reuben team offer reasonable evidence for this (although resonance-like artifacts are not unheard-of in Raman spectroscopy).
+
+Indeed, relatively trustworthy time-domain spectroscopy of proteins \cite{Microwave1994} has found that the relaxation time is proportional to the molecular weight of the structure (of which viruses are perhaps the ultimate example), and can be as slow as 100 MHz in some cases.
 
@@
 This has some pretty awesome implications if it is correct, but whether the small amplitude 
-amplification factor associated with this effect will be important is not known to me.
+amplification factor associated with this effect will be of any utility is not known to me.
 
@@
 
+Less than 5 to 10 nanoseconds (where membrane breakdown, ion diffusion, and thermal effects start to become significant at these fields, and any previous absorbed power has been dispersed in the solvent) but greater than about 10 picoseconds (covered by existing laser research) and electric fields between 0.1 MV/m (for which biological effects at these timescales are only barely plausible) and 20 MV/m (the production of pulses which strain credulity).
+
 There is data to support a little-known "prompt" electroporation effect of viruses at 
-some $10^7 \text{V/m}$. Single pulses along these lines are not obviously damaging, per NATO 
-Research Task Group 189. With some optimization, a keyhole between the electroporation threshold 
-for may be found.
+some $10^7 \text{V/m}$.
+
+%3 MV/m * 10000 electronCharge * 0.1 angstrom / (boltzmannConstant * 310 K) = 11 kT per cycle
+From an energetics perspective, we can obtain the spring constant $k = \omega_{res}^2 m^*$ from the resonant frequency, where $m^*$ is the reduced mass.
+With relatively sane choices of screened charge and resonant frequency, the energy per monocycle at 5 MV/m varies from 0.01 to 20 times the thermal energy $k_b T$.
+
+Compare to ~5 $\times k_b T$ per protein for capsid binding \cite{Energies2012} \cite{Weak2002} and $ (\text{17 to 78 kJ/mol})  / (310 \text{ K}\ k_b) = $ 6 to 30 $k_b T$ for lipid bilayer pore formation \cite{Atomistic2014a}.
+%17 or 78 kJ/mol / (boltzmannConstant * 310 K) / avogadroConstant = 6.5 to 30.3 kT
 
@@
 However, a carefully shaped pulse that matches the Cole-Cole dispersion relation of tissue 
-(apparently, a sawtooth) appears to side-step Beer's law decay and drives the oscillator some 300x 
-more strongly.
+(apparently, a sawtooth) appears to side-step Beer's law decay, and is able to drive the oscillator of the virus many times more strongly than might be expected.
 

### 2021-02-08 documents/detection.tex
words

@@
 	I hasten to note that quantifying viral titer is a completely solved problem, and is a procedure often done in kindergarten labs.
-The amount of time and effort we spent here was completely unjustifiable.
-It was driven by an acute lack of competence, equipment, and the 0.8 uL volume constraints of our original poorly designed microwave setup.
+The amount of time and effort we spent on this problem was completely unjustifiable.
+It was driven by an acute lack of competence, equipment, and the 0.8 uL volume constraints of our original poorly designed microwave setup.\\
+
+	None of the techniques that we mention are even remotely novel, and we present only the barest of experiences with each.
+	Indeed, the fluorescence technique that were eventually decided on is common practice for lysis detection; our use is not novel in the slightest.
 \end{autem}
@@
 
-\includegraphics[width=\textwidth]{x_gal.jpg}
+\begin{figure}[H]
+	\captionsetup{singlelinecheck = false, justification=justified}
+	\centering
+	\includegraphics[width=0.3\textwidth]{x_gal.jpg}
+	\caption{The very pretty opalescent blue culture caused by E. coli B trying to metabolize lactose in an X-gal $\beta$-galactosidase enzyme indicator.}
+\end{figure}
 

### 2021-02-08 documents/lessons_learned.tex
goddamnit, going down the same path again...
words

@@
 
-\paragraph{Lessons Learned} \
+\section{Lessons Learned} \
+
+\rule{\linewidth}{0.2pt}
+
+Rather than focus effort on making marginal improvements to avoid errors in a certain technique, it may be better to find an experimental technique that is totally immune to these problems.
+Obviously this isn't always possible or practical.
+
+\rule{\linewidth}{0.2pt}
+
+Lesson learned: implementing safeties in hardware when possible, even in non-critical systems, can greatly speed development.
+
+Like many microwave semiconductor HBT or pHEMT MMICs, the HMC996 amplifier requires careful biasing (discussed in section blah), or else it destroys itself.
 
@@
 
-When to publish
+When to publish?
 
 One the one hand, there're some pretty good reasons to want embargoes, like the Ingelfinger rules - no need to lather up a furor just for some idle musings, and publishing too early is a terrible idea.
-In retrospect, it was extremely good that I did not make a fuss about some extremely positive data; it turned out to be an embarrassing mistake in
+In retrospect, it was extremely good that I did not make a fuss about (or obtain funding for the original ) some extremely positive data; it turned out to be an embarrassing mistake in a data analysis script.
 
@@
 
-\paragraph{Hall of Hubris} \
+\subsection{Hall of Hubris} \
 
-Lest our hats stop fitting
+Lest our hats stop fitting - a reminder that arrogance, fallacious beliefs, etc can creep in at any point
 
@@
 Truly the depths of Dunning-Kruger.
-
-\rule{\linewidth}{0.2pt}
-
-Lesson learned: implementing safeties in hardware when possible, even in non-critical systems, can greatly speed development.
-
-Like many microwave semiconductor HBT or pHEMT MMICs, the HMC996 amplifier requires.
-
-\rule{\linewidth}{0.2pt}
 
@@
 
+Photomultiplier
+
+"Does anyone know of a circuit that can discriminate color PMT"?
+
+only works if scintillator
+
 %\end{multicols}

### 2021-02-08 documents/molecular_dynamics.tex
words

@@
 
+combine spherical geometry PB with small lipid section
+
 These results are not in any way quantitative, nor do they truly suggest that the effect exists.
@@
 
-Rather than use standard eigenmode-style normal-mode methods (ProDy), Fourier analysis of the (lipid-only) trajectory was performed with TRAVIS\footnote{a really fantastic program.
+Rather than use standard algebraic normal-mode methods (ProDy), Fourier analysis of the (lipid-only) trajectory was performed with TRAVIS\footnote{a really fantastic program.
 Clever user interface too!}, zero-padded at the end to obtain sufficient low-frequency bins with short simulations.

### 2021-02-08 documents/old_garbage_for_later.tex
words

--- 2021-01-31 documents/paper.tex
@@
-\documentclass[fleqn,10pt]{article}
-
-\include{preamble}
-
-\begin{document}
-
-\subfile{title}
-
-\begin{table}[h!]
-	\centering
-	\begin{tabular}{ |c|c|c|c| } 
-		\hline
-		col1 & col2 & col3 \\
-		\hline
-		& cell2 & cell3 \\ 
-		& cell5 & cell6 \\ 
-		& Negative & 5 \\ 
-		\hline
-	\end{tabular}
-
-	\caption{Data from testing on bacteriophage. Data rounded to the nearest thousand photon counts. Not thoroughly characterized. Repeatability between test conditions   Background was no. 
-	The flurometer printed a constant stream of the integration, all within the random error between capture windows $\sigma=0.5$ kcounts. }
-\end{table}
-
-\begin{figure}[H]
-	\captionsetup{singlelinecheck = false, justification=justified}
-	\centering
-	\includegraphics[width=\textwidth]{pulse_exposure_setup.JPG}
-	\caption{\\ \textit{Chengxiang} pulse exposure jig.
-pulser seen off the left.
-Autosampler Pulse shaping plate not shown.
-Aluminum disc belongs to the scan-conversion digitizer, not used in this study.}
-\end{figure}
-
-\begin{figure}[H]
-	\captionsetup{singlelinecheck = false, justification=justified}
-	\centering
-	\includegraphics[width=\textwidth]{eppenwolf_2.jpg}
-	\caption{\\ \textit{Eppenwolf} misguided pulsed X-Band microwave spectrometer used in this study, pictured with the near-field cuvette installed.}
-\end{figure}
-
-\clearpage
-
-\subfile{background}
-
-\begin{figure}[H]
-	\makebox[\textwidth][c]{
-		\includegraphics[width=\textwidth*2]{chunk_4_line_2_1.png}
-	}%
-	\caption{Chunk 4, it.is Founda}
-\end{figure}
-
-\clearpage
-
-\begin{figure}[H]
-	\captionsetup{singlelinecheck = false, justification=justified}
-	\centering
-	\includegraphics[width=\textwidth]{chunk_4}
-	\caption{
-		\light{
-		\\
-		We've got a thing\\
-		that's called\\
-		{\it Radar Love}\\}
-		We've got a wave\\
-		in the air}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%
-%\begin{table} 
-%	\centering
-%	\begin{threeparttable}
-%		\caption{Safety limits from various standards}
-%		\begin{tabular}{lllll}
-%			\toprule
-%			Stubhead & \( df \) & \( f \) & \( \Wsqm \) & \( p \) \\
-%			\midrule
-%			&     \multicolumn{4}{c}{Spanning text}     \\
-%			Row 1    & 1        & 0.67    & 0.55       & 0.41    \\
-%			Row 2    & 2        & 0.02    & 0.01       & 0.39    \\
-%			Row 3    & 3        & 0.15    & 0.33       & 0.34    \\
-%			Row 4    & 4        & 1.00    & 0.76       & 0.54    \\
-%			\bottomrule
-%		\end{tabular}
-%		\begin{tablenotes}
-%			\small
-%			\item This is where authors provide additional information about
-%			the data, including whatever notes are needed.
-%		\end{tablenotes}
-%	\end{threeparttable}
-%\end{table}
-
-All pertinent restrictions for frequency $<$ 6 GHz, for general public.
-ICNIRP 2020, Table 2, "Basic restrictions for electromagnetic field exposure",
-20 \Wsqm, averaged over a 6 min period, averaged over a square $4 \text{cm}^2$ surface area of the body.
-
-Whole-body average SAR $<$ 0.08 W/kg
-
-And, additionally,
-
-ICNIRP 2020, Table 3, Basic Restrictions
-
-\clearpage
-{\Large \it The contenders}\\
-
-\clearpage
-
 \paragraph{Time-domain modulation}
@@
 
-\subfile{safety}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\clearpage
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{multicols}{1}
-{\Large Modes of application}\\
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%\begin{table} 
+%	\centering
+%	\begin{threeparttable}
+%		\caption{Safety limits from various standards}
+%		\begin{tabular}{lllll}
+%			\toprule
+%			Stubhead & \( df \) & \( f \) & \( \Wsqm \) & \( p \) \\
+%			\midrule
+%			&     \multicolumn{4}{c}{Spanning text}     \\
+%			Row 1    & 1        & 0.67    & 0.55       & 0.41    \\
+%			Row 2    & 2        & 0.02    & 0.01       & 0.39    \\
+%			Row 3    & 3        & 0.15    & 0.33       & 0.34    \\
+%			Row 4    & 4        & 1.00    & 0.76       & 0.54    \\
+%			\bottomrule
+%		\end{tabular}
+%		\begin{tablenotes}
+%			\small
+%			\item This is where authors provide additional information about
+%			the data, including whatever notes are needed.
+%		\end{tablenotes}
+%	\end{threeparttable}
+%\end{table}
 
-\section{Sensing}
+All pertinent restrictions for frequency $<$ 6 GHz, for general public.
+ICNIRP 2020, Table 2, "Basic restrictions for electromagnetic field exposure",
+20 \Wsqm, averaged over a 6 min period, averaged over a square $4 \text{cm}^2$ surface area of the body.
 
-There is little discussion on microwave virus detection, with the notable exception of [Mehrotra 2019].
+Whole-body average SAR $<$ 0.08 W/kg
 
-However, \cite{Microwave2012} find that - in controlled conditions - they can detect a single E. Coli bacterium in 50 uL of broth via a microwave cavity.
+And, additionally,
 
-Havelka \cite{Highfrequency2011} discuss microtubules.
+ICNIRP 2020, Table 3, Basic Restrictions
+.
 
-With an extremely high power excitation pulse, the problem may become somewhat easier; especially if the virus has a ring-down that can be subjected to autocorrelation.
+We briefly review the biological basis for the safety. There is solid in vitro and limited in vivo evidence of safety in this regime.
 
-However, the dipole radiation power expected in even the most implausibly optimistic case would be about as follows:
+We briefly examine three applications.
+All depend significantly on what the microwave spectrum of SARS-NCoV-2 ends up being, which must be measured - or possibly reconstructed from existing whole-virion data or determined from coarse-grained MD simulation.
 
-$$P={\frac {\mu _{0}(2 \pi \cdot 20 GHz) ^{4}(0.5 \text{nm} * 10^6 e^-)^{2}}{12\pi c}} = 7.1 \times10^{-16} \text{W} $$
-
-which for most reasonable conditions would $\approx 0.5 Janskies$, meaning that the power radiated from the virus would be considerably overpowered by the milky way.
-
-% (magneticConstant*(2 pi * 20 GHz)^4 * (0.1 nm * 1000 * electronCharge)^2)/(12*pi * c) -> W
-
-\end{multicols}
-
-{\color{red} speculation \} }
-
-\subfile{brillouin_pulse_math}
-
-%\paragraph{}
-
-%\subfile{acknowledgement}
-
-\subfile{charge}
-
-\subfile{viscosity}
-
-\subfile{molecular_dynamics}
-
-\section{Appendix on microwave design}
-
-\subfile{supplemental}
-
-\section{Appendix on microbiology}
-
-\subfile{fluorescence}
-
-\subfile{sic_susceptor}
-
-\subfile{detection}
-
-\subfile{lessons_learned}
-
-\nocite{*}
-
-%\printbibliography[]
-%\printbibliography[title={All references}]
-
-\end{document}
+With refinements, our inexpensive pulsed microwave spectrometer can obtain the required absorption and threshold data with sufficiently concentrated specimens; but proper dielectric spectroscopy labs (or, in a pinch, swept-EPR/ESR equipment \st{when used improperly}) will provide a much more detailed spectrum.

### 2021-02-08 documents/paper.tex
words

@@
 
+\section{Figures which have nothing to do with our conclusion but are pretty nonetheless}
+
 \begin{figure}[H]
@@
 
-\clearpage
-
-\subfile{background}
+\begin{figure}[H]
+	\captionsetup{singlelinecheck = false, justification=justified}
+	\centering
+	\includegraphics[width=\textwidth]{bronch_9GHz_500W_2_transparent.png}
+	\caption{\\ \textit{Eppenwolf} misguided pulsed X-Band microwave spectrometer used in this study, pictured with the near-field cuvette installed.}
+\end{figure}
 
@@
 	\centering
-	\includegraphics[width=\textwidth]{chunk_4}
+	\includegraphics[width=\textwidth]{CPWG_sim_pretty_2}
+	\caption{FDTD simulation geometry of the 0.3 mm coplanar waveguide exposure cell. Red object is the fluid channel. Visualized with Paraview.
+		\ghfile{covidinator/electronics/simple_fdtd/run/microfluidic_coplanar.py}}
+\end{figure}
+
+\begin{figure}[H]
+	\captionsetup{singlelinecheck = false, justification=justified}
+	\centering
+	\includesvg[width=\textwidth]{compChargePlot}
 	\caption{
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\clearpage
 
-%
-%\begin{table} 
-%	\centering
-%	\begin{threeparttable}
-%		\caption{Safety limits from various standards}
-%		\begin{tabular}{lllll}
-%			\toprule
-%			Stubhead & \( df \) & \( f \) & \( \Wsqm \) & \( p \) \\
-%			\midrule
-%			&     \multicolumn{4}{c}{Spanning text}     \\
-%			Row 1    & 1        & 0.67    & 0.55       & 0.41    \\
-%			Row 2    & 2        & 0.02    & 0.01       & 0.39    \\
-%			Row 3    & 3        & 0.15    & 0.33       & 0.34    \\
-%			Row 4    & 4        & 1.00    & 0.76       & 0.54    \\
-%			\bottomrule
-%		\end{tabular}
-%		\begin{tablenotes}
-%			\small
-%			\item This is where authors provide additional information about
-%			the data, including whatever notes are needed.
-%		\end{tablenotes}
-%	\end{threeparttable}
-%\end{table}
-
-All pertinent restrictions for frequency $<$ 6 GHz, for general public.
-ICNIRP 2020, Table 2, "Basic restrictions for electromagnetic field exposure",
-20 \Wsqm, averaged over a 6 min period, averaged over a square $4 \text{cm}^2$ surface area of the body.
-
-Whole-body average SAR $<$ 0.08 W/kg
-
-And, additionally,
-
-ICNIRP 2020, Table 3, Basic Restrictions
-
-\clearpage
-{\Large \it The contenders}\\
+\subfile{background}
 
@@
 
-\paragraph{Time-domain modulation}
-
-However, there is an obvious avenue of optimization.
-If the virus is destroyed in a few dozen nanoseconds via an electric field amplitude incidentally caused by an instantaneous power $\text{P}$, but tissue damage requires a temperature rise due to an energy deposition $\text{P} \  \text{dt}$, then we should minimize dt.\
-
-We thus turn the CW microwave signal into a series of effectively instantaneous pulses.
-
-Note that contrary to the limits at lower frequencies, neither ICNIRP nor IEEE appear to explicitly specify a maximum electric field; only the maximum power is specified (thereby implicitly restricting the electric field magnitude).
-
-The safety standards of [IEEE] and [ICNIRP] account for such time-domain modulation by specifying both an average power limit over a 6 minute period, and a time-integrated energy deposition limit.
-All known non-thermal and thermal physiological effects, including changes in the permeability of membranes, direct nerve stimulation, etc, are accounted for by obeying those two limits.
-
-To drive home this point, apparently the best-quality evidence available fulfills sham requirements provide in-vitro.
-They expose blood lymphocytes to pulse power in precisely the regime required in this work; 8.2 GHz, 8 ns duration and 50 khz repetition rate, a whopping pulse power density of 250,000 $\text{W/m}^2$\footnote{computed from average power / duty cycle} (2500x the time-averaged power density safety limit), average power density 100 $\text{W/m}^2$ (the safety limit), for 2 hours, finding no change in any of the measured quantities.
-
-Similarly, [Chemeris 2004] use 8.8 GHz, 180 ns pulse width, peak power 65,000 W, repetition rate 50 Hz, exposure duration 40 min, and find genotoxicity purely due to the temperature rise.
-
-So it appears that this is not merely rules-lawyering to exploit a loophole in the regulations; it is a physically-informed effect.
-
-\begin{autem}
-
-These papers (the best quality we are aware of) were extensively cherry-picked from the literature based on the results of a meta-analysis [Vj.
-2019], listing the requirements for reliable in-vitro RF experiments.\\
-
-There are a substantial number of papers in the literature which show positive effect sizes; a select few of these are listed in the bibliography. \\
-
-The literature reviews conducted by standards organizations.\\
-
-We are not aware of any past uses of these microwave en-masse. We do not have the
-
-Moreover, 
-\begin{quote}
-
-In the absence of publication bias, since the sampling error is random, all studies will be distributed symmetrically around the mean d value.
-
-\end{quote}
-
-\end{autem}
-
-\clearpage
-%\printbibliography[heading=none, title={}, keyword={Flagship}]
-\printbibliography[heading=none, title={}, keyword={standards}]
-
-\clearpage
-{\Large \it Time-dependence}\\
-
-The fact that the viral inactivation is non-thermal
-
-Both [Yang 2015] and [Hung 2014] use an apparently arbitrary 15-minute exposure in their tests - a very reasonable decision, given the focus of their paper.
-
-The effectiveness against airborne particles, and to minimize the power required in a dwelling phased-array beam, we must establish the required duration of exposure.
-
-{\color{red} speculative hypothesizing \{ }
-
-In contrast to chemical inactivation, where the time dependence appears to be dominated by viscous fluid dynamic effects [Hirose 2017], or UV inactivation, where a certain quantized dose of photons must be absorbed, we expected RF to act instantaneously.
-
-As a damped, driven oscillator, the ring-up time of the virus depends on the Q factor.
-Yang et al.
-state the Q of Inf.
-A as between 2 and 10, so at 8 GHz the steady-state amplitude should be reached in well under 100 nanoseconds.???????????FIXME
-
-[] found a significant mechanical fatigue effect in phage capsids, where a small strain applied repetitively eventually causes a fracture.
-Such a mechanism could perhaps extend the exposure required to break the capsid or membrane.
-Other mechanisms could include some sort of lipid denaturation, requiring an absolute amount of energy absorption to break or twist bonds and modify properties before the envelope fractures.
-
-{\color{red}  \} }
-
-\clearpage
-
-\subfile{safety}
-
-\clearpage
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{multicols}{1}
-{\Large Modes of application}\\
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Sensing}
-
-There is little discussion on microwave virus detection, with the notable exception of [Mehrotra 2019].
-
-However, \cite{Microwave2012} find that - in controlled conditions - they can detect a single E. Coli bacterium in 50 uL of broth via a microwave cavity.
-
-Havelka \cite{Highfrequency2011} discuss microtubules.
-
-With an extremely high power excitation pulse, the problem may become somewhat easier; especially if the virus has a ring-down that can be subjected to autocorrelation.
-
-However, the dipole radiation power expected in even the most implausibly optimistic case would be about as follows:
-
-$$P={\frac {\mu _{0}(2 \pi \cdot 20 GHz) ^{4}(0.5 \text{nm} * 10^6 e^-)^{2}}{12\pi c}} = 7.1 \times10^{-16} \text{W} $$
-
-which for most reasonable conditions would $\approx 0.5 Janskies$, meaning that the power radiated from the virus would be considerably overpowered by the milky way.
-
-% (magneticConstant*(2 pi * 20 GHz)^4 * (0.1 nm * 1000 * electronCharge)^2)/(12*pi * c) -> W
-
-\end{multicols}
-
-{\color{red} speculation \} }
+%\subfile{safety}
 
@@
 
-\subfile{fluorescence}
-
 \subfile{sic_susceptor}
@@
 \subfile{detection}
+
+\subfile{fluorescence}
 

### 2021-02-08 documents/pulse_generator.tex
words

@@
 
+Impedance matching to appears to be a solved problem.
+\cite{Microchamber2011} provide a good review, and offer a design using a high-impedance exposure cell in parallel with a 50 ohm resistor, which offers excellent performance to at least 1 GHz.
+Attenuator for diagnostics are also built in.
+
+Almost   Diagnostics of such pulses are difficult.
+
+ Attenuators with such high peak powers are difficult to obtain.
+
+\cite{Characterization2012}
+
 \end{document}

### 2021-02-08 documents/scan_converter.tex
words

--- 2021-01-07 documents/scan_converter.tex
@@
-We would like real-time rather than equivalent-time sampling,
+%!TeX root = scan_converter
+\documentclass[paper.tex]{subfiles}
+\begin{document}
+
+\begin{autem}
+This is an example of how the course of action can be distorted by engineering.
+In a non-pandemic scenario such a diversion might have been a reasonable.
+Indefensible.
+I am consoled that it did not account for more than 2 to 3 weeks of work.
+\end{autem}
+
+\begin{autem}
+	This section is deliberately kept vague and without reference to construction details to avoid export restrictions.
+In any case, it is hard to imagine a technique fully developed and published in the 1940s would be of great secrecy now.
+\end{autem}
+
+Because of the small sizes of viruses, all interesting time-domain spectroscopy results require resolving signals with greater than 10 GHz bandwidth.
+
+So called "equivalent-time" or "sampling" oscilloscopes are less expensive; but it was hoped that it would be possible to resolve the breaking of the capsid - a transient, single-shot phenomenon -   A digital oscilloscope capable of real-time sampling such a transient is a tall order, and it did not appear that an undergraduate would be allowed access.
+
+There is also the concern that, when measuring a system producing kilovolt pulses using an instrument with an extremely electrically delicate 1V maximum input, some harm might come to a machine worth more than the experimenter.
+
+This turned out to be not unfounded - the kilovolt pulser used was observed to cause the RPi controlling the experiment to
+
+However, transient recordings of sub-nanosecond phenomena were made as early as 1938 by Manfred Von Ardenne using a "micro-oscillograph".
+By 1946, such oscillographs - now with bandwidths in excess of 10 GHz - were readily available commercially\cite{3beam1946}, and by 1949 found extensive use for quantitative measurements of ultrafast phenomena by Fletcher\cite{Production1949} and others.
+
+"Direct access" tubes to the logical conclusion. The design of Fletcher puts the cathode ray deflection plates essentially inside the.
+
+The main practical limitations on oscilloscope sweep speed are discussed by Mackay\cite{New1948}, and are imposed by the Y axis deflection plate electron transit time and bandwidth (the X-axis speed is of less importance), and the beam current and sensitivity of the phosphor (faster sweeps reduce the electron flux and brightness of the dot).
+
+\begin{figure}[H]
+	%	\makebox[\textwidth][c]{
+	\centering
+	\subfloat[Damage to the sensor, believed to be due to. ]{
+	\includegraphics[width=0.3\textwidth]{e_beam_damage_2}
+
+}
+	\hfill
+	\subfloat[]{
+		\includegraphics[width=0.3\textwidth]{e_beam_damage}
+
+	}
+		\hfill
+
+	\subfloat[Direct electron beam detection]{
+	\includegraphics[width=0.3\textwidth]{direct_electron_beam}
+}
+	\caption{Second.}
+		\hfill
+
+\end{figure}
+
+\begin{figure}[H]
+	\captionsetup{singlelinecheck = false, justification=justified}
+	\centering
+
+	\caption{}
+\end{figure}
+
+\begin{figure}[H]
+	\captionsetup{singlelinecheck = false, justification=justified}
+	\centering
+
+	\caption{}
+\end{figure}
+
+The very high voltage actually makes this much easier
+
+means that low-sensitivity diagnostics, like lithium niobate optical probes.
+Not having a suitable optical bench, an electron-beam probe, similar to a streak camera, itself similar in principle to scan-conversion digitizer tubes in Tek SCD and 7912 series transient digitizers.
+
+If a low voltage sensitivity is required, and because modern high-pixel-density CMOS sensors allow the required deflection (and therefore the entire structure) to be minimized, these are simple to design and inexpensive (much of the complexity is in the slow-wave or travelling-wave structure which is usually required to match the signal velocity to the - slowing down light without affecting its properties or drawing power is an extremely difficult problem) and can offer sample rates in the terasamples/s and analog bandwidths of many dozens of GHz, albeit with very low vertical resolution.
+
+original von Ardenne
+
+\begin{fquote}[Livermore Operations][\cite{Scan2008}]
+An internal CCD recorder would provide high sensitivity to the swept electron beam, but a CCD in a sealed vacuum tube has never been attempted or demonstrated in the phototube facility at Livermore Operations (LO).
+A prototype tube would most likely be built with a phosphor screen.
+\end{fquote}
 
@@
 
-A digital oscilloscope capable of real-time sampling such a transient is no small feat, and it was deemed unlikely that we would be 
-able to obtain access, There is also the concern that, when working with a system producing kilovolt 
-pulses and an input of 5v, some harm might come to a machine worth more than the experimenter.
-
 Possibly some optical method.
@@
 
-$$ \frac{\sin(\frac{2\pi F \tau}{2})}{(2\pi F)/2} $$
+$$ \frac{\sin(\frac{2\pi F \tau}{2})}{(2\pi F \tau)/2} $$
 
-where \tau is the transit time of the electron through the deflection region
+where $\tau$ is the transit time of the electron through the deflection region
+
+Image intensifier microchannel plates where angled holes cause secondary electron
+
+\end{document}

### 2021-02-08 documents/supplemental.tex
words

@@
 %tonsil
+
+\section{Sensing}
+
+There is little discussion on microwave virus detection, with the notable exception of [Mehrotra 2019].
+
+However, \cite{Microwave2012} find that - in controlled conditions - they can detect a single E. Coli bacterium in 50 uL of broth via a microwave cavity.
+
+Havelka \cite{Highfrequency2011} discuss microtubules.
+
+With an extremely high power excitation pulse, the problem may become somewhat easier; especially if the virus has a ring-down that can be subjected to autocorrelation.
+
+However, the dipole radiation power expected in even the most implausibly optimistic case would be about as follows:
+
+$$P={\frac {\mu _{0}(2 \pi \cdot 20 GHz) ^{4}(0.5 \text{nm} * 10^6 e^-)^{2}}{12\pi c}} = 7.1 \times10^{-16} \text{W} $$
+
+which for most reasonable conditions would $\approx 0.5 Janskies$, meaning that the power radiated from the virus would be considerably overpowered by the milky way.
+
+% (magneticConstant*(2 pi * 20 GHz)^4 * (0.1 nm * 1000 * electronCharge)^2)/(12*pi * c) -> W
 

### 2021-02-08 math/update_mma.sh

@@ -1,0 +1,8 @@
+
+#run save_all_files
+rm -r mathematica/
+wget https://www.wolframcloud.com/obj/therobotist/down.zip 
+unzip down.zip "*/*" -d mathematica/
+mv mathematica/all/* mathematica/
+rm -r mathematica/all
+rm down.zip

### 2021-02-09 documents/background.tex
Text and prop improvements

@@
 
+After the relaxation time, the energy is a distant memory; only the mechanical effects that were induced during that time can remain. Since the energy is too small to
+
 \footnote{A note on units, from ICNIRP: ``{[B]elow about 6 GHz, where EMFs penetrate deep into tissue (and thus require depth to be considered), it is useful to describe this in terms of “specific energy absorption rate” (SAR), which is the power absorbed per unit mass $(W/kg)$.
@@
 %3 MV/m * 10000 electronCharge * 0.1 angstrom / (boltzmannConstant * 310 K) = 11 kT per cycle
-From an energetics perspective, we can obtain the spring constant $k = \omega_{res}^2 m^*$ from the resonant frequency, where $m^*$ is the reduced mass.
+From an energetics perspective, we can obtain the spring constant $k = \omega_{res}^2 m^*$ from the resonant frequency and therefore from the speed of sound and $m^*$, the reduced mass.
 With relatively sane choices of screened charge and resonant frequency, the energy per monocycle at 5 MV/m varies from 0.01 to 20 times the thermal energy $k_b T$.
 
-Compare to ~5 $k_b T$ per protein for capsid binding \cite{Energies2012} \cite{Weak2002} and $ (\text{17 to 78 kJ/mol})  / (310 \text{ K}\ k_b) = $ 6 to 30 $k_b T$ for lipid bilayer pore formation \cite{Atomistic2014a}.
+Compare to ~5 $k_b T$ per protein for 1 capsid segment binding energy \cite{Energies2012} \cite{Weak2002} and $ (\text{17 to 78 kJ/mol})  / (310 \text{ K}\ k_b) = $ 6 to 30 $k_b T$ to form a single pore in a lipid bilayer \cite{Atomistic2014a}.
 %17 or 78 kJ/mol / (boltzmannConstant * 310 K) / avogadroConstant = 6.5 to 30.3 kT
+
+On the other hand, 0.5 angstroms is only a 0.04\% deflection of the capsid, whereas a general value for host cells is about 3\% deflection.
+
+Certainly the virus will be destroyed at some finite electric field. It remains to be seen whether a practical limit
+
+ \cite{Resonance1996}
 
@@
 
-\begin{autem}
-Extreme care must be taken in interpreting the results of any one study in isolation, especially in this field.
+While this result would seem to perfectly align with our hypothesis, extreme care must be taken in interpreting the results of any one study in isolation, especially in this field.
 
-Though the temperature was monitored, In this observation, the thermal artifact cannot necessarily be completely discounted.
-The energy dissipated was sufficient to cause a significant temperature rise if localized hot-spots appeared \footnote{(43 cal/cc * (3 microliters)) / (3 milligrams * 4.2 J/(g K)) = ~50 $\Delta$C, whereas melting temperatures are typically about 90 C for capsids \cite{Thermal1999} and 50 C for envelopes\cite{Stability1985}}.
-\\ The electrodes were not insulated, so electrochemical effects are possible but unlikely given the short duration of the pulses.
-\end{autem}
+See the section on pulse artifacts.
+Electrode insulation is not mentioned, so electrochemical effects are possible but unlikely given the short duration of the pulses.
+The observed RNA damage is unexpected from a mechanical standpoint but is somewhat like the damage due to copper ions found by \cite{Microwave1987}; therefore electrochemical interaction may have been a confounding factor.
 
-Madiyar \cite{Manipulation2013} observe rapid permeabilization (likely through the slow, conventional electroporation mechanism) at a field of poorly-defined intensity up to about 10 MV/m, in the Vaccinia poxvirus (a 300 nm enveloped dsDNA virus).
+Also, although the temperature was monitored, the thermal artifact cannot necessarily be completely discounted in this experiment.
+The energy dissipated was sufficient to cause a significant temperature rise if localized hot-spots were to appear \footnote{(43 cal/cc * (3 microliters)) / (3 milligrams * 4.2 J/(g K)) = ~50 $\Delta$C, whereas melting temperatures are typically about 90 C for capsids \cite{Thermal1999} and 50 C for envelopes\cite{Stability1985}}.
+
+Madiyar \cite{Manipulation2013} observe rapid permeabilization (perhaps through the slow, conventional charge electroporation mechanism) at a field of poorly-defined intensity up to about 10 MV/m, in the Vaccinia poxvirus (a 300 nm enveloped dsDNA virus).
 \cite{AC2017}.
@@
 Both AFM data and surmised from osmotic pressure, the force scale required to crack the viral envelopes and capsids is about 1 nanonewton.
+
+Schnelle\cite{Trapping1996}
+
+\subsection{Electrorotation}
+
+and Fuhr\cite{Radiofrequency1994} and Grom \cite{Accumulation2006} report on a modification of so-called dielectrophoresis techniques called electrorotation, in a so-called field cage.
+
+Rotation is sub-synchronous at a few Hz, whereas the field rotates at between 0.1 MHz to over 50 MHz; in all cases the frequency is made high enough that
+
+In the virus tests by Schnelle, a field of 0.3 MV/m was used, without apparent damage to the virus, though their
+
+Gimsa \cite{New1999} use a four-electrode cage at 25 kV/m
 
@@
 
-Man \cite{Picosecond2016b} perform a trustworthy all-atom molecular dynamics simulation of .
-As with most molecular dynamics simulations, the applied field was enhanced by several orders of magnitude to an unrealistic 2 gigavolts per meter to make the reaction proceed fast enough to be captured without excessive computation time.
+Man \cite{Picosecond2016b} perform a trustworthy all-atom molecular dynamics simulation of a laser pulse tuned to provoke dissociation of a viral capsid.
+In this case the large-scale structual modes are not involved.
+As with many molecular dynamics simulations using applied fields, the field was enhanced by several orders of magnitude to an unrealistic 2 gigavolts per meter to make the reaction proceed fast enough to be captured without excessive computation time.
 
@@
 
-A group of literature exists concerning the excitation of these modes with picosecond or femtosecond lasers.
-A pulse some 300 fs long and with a carrier of around 600 nm.
+A group of literature exists concerning the excitation of these structural modes with picosecond or femtosecond lasers.
+A pulse some 300 fs long with a carrier of around 600 nm.
 Impulsive stimulated Raman scattering.
-We confess to not having studied these mechanisms in great detail.
+We confess to not having studied this mechanism in great detail.
 The pulse does not directly act on the vibrational mode; the optimal pulse duration is some small fraction of the period of the mode in question.
@@
 It is common for.
-However, non-zero resonant frequency requires the ratio of the the loss in energy to the surroundings to the mass, to be greater than $b/(2m) < \omega_{res} \sqrt{2}$ \cite{Driven}; the solution to the harmonic oscillator equation is piecewise around this value.
+However, in the classical case, a non-zero resonant frequency requires the ratio of the loss in energy to the surroundings to the oscillating mass to obey $b/(2m) < \omega_{res} \sqrt{2}$ \cite{Driven}; the solution to the harmonic oscillator equation is piecewise around this value.
+
+(unless the various small-scale quantum mechanical oscillators are considered, which in our case appear to require fields in excess of 1 TW to access).
 
@@
 We are adamant that, in all cases cited, we believe their studies were well designed and conducted: the authors went to considerable and sufficient lengths to demonstrate its validity.
+It is easy to say what could have happened, but much harder to say what did happen.
 \end{toolchain}
@@
 \begin{multicols}{1}
+
+Vijayalaxmi \cite{Biological2016} \cite{Comprehensive2018} \cite{Funding2019} already offer a number of excellent guidelines on best practices in this field; as do Chou \cite{chou1996radio}.
+We only offer a few issues which we were particularly concerned about when designing our experiments and searching literature.
 
@@
 
+\subsection{Raman spectroscopy}
+
+Very recently, Burkhartsmeyer \cite{Optical2020} have published data replicating the findings on bacteriophage PhiX174 using a single-particle Raman spectroscopy technique.
+We have not examined these claims in any detail, but believe that they are excellent evidence.
+
+Perhaps these results cannot be trusted implicitly, however, because non-photothermal optical Raman methods can also apparently synthesize artifacts - see unpublished, personal communication with Taylor \cite{mechanisms1981}.
+As this is an unpublished negative result, we know nothing about the experimental details that led to this error.
+
 \subsection{Thermal controls}
@@
 As any researchers who have scalded their mouths on a cheap dinner may know, microwave irradiation can produce unintuitive temperature gradients, with local hot-spots that can be difficult to measure directly.
+
+An electric field necessarily dissipates energy in the surrounding solvent, and
+
+In inevitable temperature rise as a confounding factor.
+
+mouse was heating
+
+A few reports in the 1940s suggested that bacteria might be non-thermally inactivated.
+However, Burton\cite{Effects1950} described an experiment using thermochromic pigments to examine heating profiles throughout the sample.
+With a half-second pulse of an exposure frequency of only 30 MHz, they observe highly localized regions that exceed 50 C even while the maximum temperature measured by thermocouple never exceeds 36-40 C.
+This is despite the use of a tube only 9 mm across, where it might be thought that thermal conduction would dissipate any .
+
+With the shorter wavelengths of microwave frequencies, it seems likely that such effects will be far more pronounced.
+
+This is highlighted by the experiments of Kozempel \cite{Preliminary1997} and \cite{Inactivationa}, discussing the performance of an RF fluid sterilization unit.
+They take great pains to map the temperature profile using a fiber-optic thermometer; use thermographic indicators; and yet find substantial inactivation of {\it Pediococcus sp.} with a maximum measured temperature of only 40 C.
+
+This is a fascinating result, and one which should be compared to the existing literature and very carefully replicated to isolate the mechanism.
+However, unless it is suggested that {\it Pediococcus sp.} also exhibits a confined microwave resonance of the same nature as the virus, it appears that temperature measurements within the physiological range are not necessarily a sufficiently stringent control to definitively {\it isolate} resonant effects from other mechanisms.
+
+The temperature rise after 15 minutes radiation was 27.5°C up to 34.5°C.
 
@@
 
-A previous report of microwave resonance, Grundler \cite{Sharp1983}, use a calorimeter, a stream of cooling water controlled to within 0.1 C, an interferometric thermometer, and can state definitively that at no point does the temperature inhomogeneity exceed 0.02 C.
+A previous report of microwave resonance, Grundler \cite{Sharp1983} use a calorimeter, a stream of cooling water controlled to within 0.1 C, an interferometric thermometer, and can state definitively that at no point does the temperature inhomogeneity exceed 0.02 C.
 
@@
 
-An electric field necessarily dissipates energy in the surrounding solvent, and
-
-In inevitable temperature rise as a confounding factor.
-
-Kozempel \cite{Preliminary1997} and \cite{Inactivationa}.
-They take great pains to map the temperature profile using a fiber-optic thermometer; use thermographic indicators; and find substantial, almost complete inactivation of {\it Pediococcus sp.} with a measured discharge temperature of only 40 C.
-
-This is a fascinating result, and one which should be compared to the existing literature and very carefully replicated to isolate the mechanism.
-However, unless it is suggested that {\it Pediococcus sp.} also exhibits a confined microwave resonance of the same nature, it appears that periodic temperature measurements within the physiological range are not necessarily a sufficiently stringent control to definitively {\it isolate} resonant effects from other mechanisms.
-
-Conversely, if temperature control is not possible, the temperature can be allowed to rise so long as a positive control is present in which
+Conversely, if temperature control is not practical, the temperature can be allowed to rise - so long as a positive control is present which can be
 
 In Gandhi \cite{Basic1983}, nichrome heaters and copper-constantan thermocouples are used to generate the same temperature-time profile in both the treatment and this positive control to within 0.02 C, finding no effect.
-
-Burton\cite{Effects1950} describe the use of thermochromic pigments to examine heating profiles. Using low-frequency exposure, they are able to produce localized regions in excess of 50 C.
 
@@
 \begin{quote}
-
 	To confirm that our observation is not due to the microwave thermal heating effect, we had monitored the sample temperature change during the microwave illumination experiments with a radiated power density of 486W/m2 at a frequency of 6GHz by using an infrared thermal imaging camera with a temperature accuracy of 0.05°C (CHCT, P384-20).
-The temperature rise after 15 minutes radiation was 7°C, from 27.5°C up to 34.5°C.
 We thus exclude the possible contribution of microwave thermal heating effect to inactivation H3N2 viruses under our experimental condition.
-
 \end{quote}
@@
 
-\subsection{Other artifacts}
+\subsection{Even weirder artifacts}
 
@@
 
-\subsection{Raman spectroscopy}
-
-Very recently, Burkhartsmeyer \cite{Optical2020} have published data replicating the findings using a single-particle Raman spectroscopy technique.
-We have not examined these claims in detail, but they are good evidence.
-
-Non-photothermal optical Raman methods can also apparently synthesize artifacts - see unpublished, personal communication with Taylor \cite{mechanisms1981}.
-
  $<< 20 \text{ ps}$ \footnotemark measured in the structures of human tissue.\\
@@
 
-This technique appears to be unique in that it is selective, save for Far UV or cold-plasma sterilization.
-Its advantages over those is that it operates over large volumes with inexpensive emitters, but, most critically, can be made to penetrate tissue without harm.
-
 \end{multicols}

### 2021-02-09 documents/experiment_1.tex
Text and prop improvements

@@
 
-\section{Experiment 1: Attempts at microwave absorption spectroscopy and
+\section{Experiment 1: Attempts at microwave absorption spectroscopy and inactivation in the microsecond pulsed 100 V/m regime}
 
-\section{Microwave lysis feedback}
+\subsection{Microwave lysis feedback}
 
@@
 
-At the time, this seemed important to establish, as it would allow the inactivation threshold to be determined without a time-intensive and potentially dangerous infectivity assay step (making it more plausible that we would get biosafety approval on NCoV).
+At the time, this seemed important to establish, as it would allow the inactivation threshold to be determined without a time-intensive and potentially dangerous infectivity assay step (making it more plausible that we would get biosafety approval to obtain the microwave spectrum of NCoV).
 
@@
 For instance, the lysis that occurs after phage infection of bacteria does little harm to the cell; only the permeability of the membrane is damaged\cite{GROWTH}.
-Similarly, the results of the previous studies could perhaps have been obtained without necessarily breaking the virus' envelope.
+Similarly, the results of the previous studies could perhaps have been obtained without necessarily destroying the virus' envelope.
 

### 2021-02-09 documents/pulse_generator.tex
Text and prop improvements

@@
 
+Spark gaps
+
+\cite{kHz1995} uses an interesting construction of a pressurized spark gap.
+
+The ZTX417 parts are expensive (\$15 apiece, as of this writing).
+
+[] mention triggering parameters
+
+There seem to be two main designs:
+
+drivers Pockels cells for Q switching.
+
+Schaal patent  which can produce 70 ps edges using less expensive ZTX415 (although the all-important RF "second schematic", the ).
+
+marx or marx-free
+
+Almost   Diagnostics of such pulses are difficult.
+
+Attenuators that are rated for such high peak powers are hard to find.
+
+Oak \cite{fast1991} Figure 1 offers a circuit to evaluate avalanche behavior of transistors. Using this, the
+
 Impedance matching to appears to be a solved problem.
@@
 Attenuator for diagnostics are also built in.
-
-Almost   Diagnostics of such pulses are difficult.
-
- Attenuators with such high peak powers are difficult to obtain.
-
+This cell should be used rather than our design.
 \cite{Characterization2012}

### 2021-02-09 electronics/propagation/propagation_numerical_optimize.py

@@ -11,7 +11,7 @@ from scipy.optimize import minimize, basinhopping
 from fdtd_PCB_extensions.tissue import cole_cole_4, get_tissue_cole_cole_coefficients
 import pickle
 import dill
-
+import sys
 
 
 omega_res = 2.0*pi*30e9
@@ -89,6 +89,9 @@ def cost_function(F, n, omega, z):
     return abs(-np.max(propagate(F, n, omega, z))/picometer) + np.max(F**2.0)
 
 
+if(not __name__ == "__main__"):
+    sys.exit()
+    #using as a library, get out
 
 
 duration = 30e-10
@@ -106,6 +109,8 @@ n[omega == 0] = 1
 # F = np.sin(times*omega_res)
 
 # output = propagate(F, omega, z)
+
+
 
 try:
     f = open("output.pkl",'rb')

### 2021-02-10 documents/background.tex
Oh hey the brilluoin just had a bug

@@
 See the section on pulse artifacts.
-Electrode insulation is not mentioned, so electrochemical effects are possible but unlikely given the short duration of the pulses.
+Electrode insulation is not mentioned, so electrochemical effects are possible.
 The observed RNA damage is unexpected from a mechanical standpoint but is somewhat like the damage due to copper ions found by \cite{Microwave1987}; therefore electrochemical interaction may have been a confounding factor.
@@
 
-\subsection{Electrorotation}
+\subsection{Dielectrophoresis and electrorotation}
 
@@
 
-Rotation is sub-synchronous at a few Hz, whereas the field rotates at between 0.1 MHz to over 50 MHz; in all cases the frequency is made high enough that
+Rotation is sub-synchronous at a few dozen Hz, whereas the field rotates at between 0.1 MHz to over 50 MHz; in most cases the frequency is made high enough that ion does not occur.
 

### 2021-02-10 documents/brillouin_pulse_math.tex
words
Oh hey the brilluoin just had a bug

@@
 could be constructed that would be an effective driver for the normal modes in question.
-Oughston ; if the pulses are too close together, they interfere as they propagate and distort the precursor thus formed.
 
-For instance, despite the waveform from nonlinear transmission lines producing strong wideband components, in cursory simulations they did not appear to satisfy the requirements for Brillouin pulses\wikinote{dubious-discuss}\wikinote{citation-needed}.
+First, Oughston ; if the pulses are too close together, they interfere as they propagate and distort the precursor thus formed.
+
+As an example, despite the waveform from nonlinear transmission lines producing strong wideband components, in cursory simulations they did not appear to satisfy the requirements for Brillouin pulses\wikinote{dubious-discuss}\wikinote{citation-needed}.
 Our working hypothesis is that this is because of destructive interference from the falling edge that immediately follows; but this is mere speculation.\wikinote{dubious-discuss}
+
+Second, while the pulse amplitude decays slowly, the total energy contained in such a precursor decays very quickly.
+The biological ramfications of discussed in detail by Adair in \cite{Biophysics2000}.
 
@@
 
-However, the energy contained in such a standard pulsed-sine or gaussian train decays very quickly,
-
 %http://web.physics.ucsb.edu/~fratus/phys103/LN/DHM.pdf
@@
 \pagebreak
-A qualitative statement of the problem we were trying to solve (which may not be correct, especially if Q turns out to be < 1):
+A qualitative statement of the problem we were trying to solve (which may not a useful formulation, especially if Q turns out to be < 1 and the virus exhibits only relaxational and non-resonant behavior):
 
@@
 
-Of course, 10x attenuation at 1 MV/m still takes us outside.
+\begin{figure}[H]
+	%	\makebox[\textwidth][c]{
+	\includesvg[width=\textwidth]{propagated_waveforms}
+	\caption{}
+\end{figure}
+
+Of course, 10x attenuation at 1 MV/m still takes us beyond safe levels at the skin.
 However, the loss that makes phased-array near-field focusing systems impractical at baseband is no longer a concern.

### 2021-02-10 documents/detection.tex
Oh hey the brilluoin just had a bug

@@
 \begin{autem}
-	I hasten to note that quantifying viral titer is a completely solved problem, and is a procedure often done in kindergarten labs.
+	I hasten to note that culturing and quantifying viral titer is a completely solved problem, and is a procedure often done in kindergarten labs.
 The amount of time and effort we spent on this problem was completely unjustifiable.
@@
 
-Two
+Most of our results are tainted by two factors:
+
+First, the fridge froze. A small "three-way"
 
 T4r+,
+
+Two
 
@@
 
-A lot of the basic facts of phage were determined in the 1930s;
+A lot of the basic facts of phage, and most of the useful techniques were determined in the 1930s.
 
@@
 
+Otherwise, GFP-flouresecent strains of E. coli, or phage which has been labeled with a
+
 \subsection{Detect the release of intracellular material due to the lysis of the host}
@@
 X-gal \cite{Improved}
+
+X-gal is only soluble in DMF and DMSO. We choose DMSO due to DMF's toxicity. DMSO is miscible with water, so that works out nicely. Solutions of < 0.75\% DMSO seem to not be cytotoxic.
 
@@
 
+Phages release several small compounds like putrescine and spermadine when broken (Minagawa\cite{characteristics1961}).
+These can be indicated colorimetrically at ppm scales with ninhydrin, or at nanogram scales via fluorescamine.
+
+Biotium Gelgreen has a very specific advantage: to increase the safety of the dye, the flurophore is tied to some huge proprietary molecule, preventing it from diffusing through membranes or capsids.
+This has the side effect of making the fluorescence intensity strictly related to the quantity of genomic material dispersed in the solvent, rather than
+
 \subsubsection{Nucleic acid UV extinction }
@@
 
-Phages release several small compounds like putrescine and spermadine when broken (Minagawa\cite{characteristics1961}).
-These can be indicated colorimetrically at ppm scales with ninhydrin, or at nanogram scales via fluorescamine.
-
-Otherwise, GFP-flouresecent strains of E. coli, or phage which has been labelled with a
-
 PEG apparently concentrates to $10^{12}$ or 13 no matter what the starting concentration is (huh?), very convenient.
 
-Concentrated can be put into the microgram range of many standard protein assays like BCA, but that requires propagation and PEG precipitation, plus many such assays pose disposal hazards and stain labware.
+Early workers on phage mention\cite{ADSORPTION1940}  that cultures with a titer above about $10^10$ have an opalescent blue tint due to Tyndall scattering.
+Schlesinger in 1933 \cite{Beobachtung1933} (paper is in German).
+This technique appears to have been forgotten?
 
-Biotium Gelgreen has a very specific advantage: to increase the safety of the dye, the flurophore is tied to some huge proprietary molecule, preventing it from diffusing through membranes or capsids.
-This has the side effect of making the fluorescence intensity strictly related to the quantity of genomic material dispersed in the solvent, rather than
+Concentrated can be put into the microgram range of high-sensitivity protein assays like BCA or Bradford, but that requires propagation and PEG precipitation, plus many such assays pose disposal hazards and stain labware.
 

### 2021-02-10 electronics/propagation/propagation_numerical_optimize.py

@@ -89,14 +89,13 @@ def cost_function(F, n, omega, z):
     return abs(-np.max(propagate(F, n, omega, z))/picometer) + np.max(F**2.0)
 
 
-if(not __name__ == "__main__"):
-    sys.exit()
-    #using as a library, get out
-
-
 duration = 30e-10
 samples = int(np.ceil(duration * omega_res * 2.0 * 5.0))
 times = np.linspace(-duration,duration,samples)
+
+print("Sample time: ",times[1]-times[0])
+print("Window duration: ",times[-1]-times[0])
+
 
 F=np.ones(samples)
 omega = 2*pi*np.fft.fftfreq(samples)*(samples/(duration*2))

### 2021-02-11 electronics/propagation/propagation_simple_sawtooth.py
log colorbar

@@ -25,7 +25,7 @@ import store
 muscle_id = 48
 lung_id = 41
 #cole-cole refractive index
-ef, sigma, deltas, alphas, taus = get_tissue_cole_cole_coefficients(lung_id)
+ef, sigma, deltas, alphas, taus = get_tissue_cole_cole_coefficients(muscle_id)
 c0 = 3e8
 
 
@@ -46,7 +46,7 @@ def propagate(F, n, omega, z, oscillator=True):
 
     #filter
     # frequency_domain[(omega/(2.0*pi)) < 1e9] = 0
-    # frequency_domain[(omega/(2.0*pi)) > 40e9] = 0
+    frequency_domain[(omega/(2.0*pi)) > 200e9] = 0
 
 
     propagated = frequency_domain * np.exp(-1j*(omega/c0)*n*z)
@@ -56,7 +56,7 @@ def propagate(F, n, omega, z, oscillator=True):
 
 
 
-sf = 10e9 * 2 * pi
+sf = 30e9 * 2 * pi
 
 duration = 30e-10
 samples = int(np.ceil(duration * sf * 2.0 * 5.0))
@@ -95,17 +95,21 @@ snippet_samples = end_samples - beginning_samples
 
 bigtable = np.zeros(((depths*snippet_samples), 3))
 
-plot_indexes = [0, 29]
+plot_indexes = [29]
 
 
-f = 10e9 * 2 * pi
+angular_f = 10e9 * 2 * pi
 
 # F = np.sin(times*f)
-F = normalized_gaussian_pulse(times,1/(10e9))
+F = normalized_gaussian_pulse(times,1/(2*pi*10e9))
 for idx,z in enumerate(np.linspace(0, max_depth, depths)):
     output = propagate(F, n, omega, z)
+    if(idx == 0):
+        plt.subplot(2,4,1)
+        plt.plot(times, output,'r')
     if(idx in plot_indexes):
-        plt.subplot(2,2,1)
+        plt.subplot(2,4,2)
+        plt.ylim((-0.05,0.05))
         plt.plot(times, output,'r')
     bigtable[(idx*snippet_samples):((idx+1)*snippet_samples),0] = times[beginning_samples:end_samples]
     bigtable[(idx*snippet_samples):((idx+1)*snippet_samples),1] = z
@@ -115,11 +119,15 @@ for idx,z in enumerate(np.linspace(0, max_depth, depths)):
[…]

### 2021-02-11 documents/background.tex
Rotation

@@
 
- (of course, it turns out )
+\footnote{"nsPEFs"}
+
+We were inspired to undertake this project by a set of publications by Yang et al, Hung et al, Sun et al.
+
+These reports attempt to establish that, ostensibly unlike human cellular structures, the studied species of viruses coincidentally about the right size, shape, stiffness, and net charge distribution to form a weak (Q=2) spherical dipole resonance mode which couples well to the microwave spectrum at approximately 8 GHz.
+
+They theoretically model and then experimentally demonstrate in various strains of Influenza A that - supposedly due to this acoustic-resonance effect - the power density levels required to crack the lipid envelope are near the safety limits for continuous exposure to humans.
+
+The experiments are competently designed and many orthogonal measurements are made to confirm the effect.
+
+There are a few minor issues with the experimental technique
+
+These very striking results have attracted some recent attention. \cite{Burkhartsmeier} have observed a resonance of the same nature (see below), and work is proceeding by their team.
+
+Such a non-thermal mechanism is quite unprecedented and extremely dubious, oft-posited but never substantiated; so it has taken some convincing that this is not a particularly abstruse artifact, especially when considered in the context of the broader non-thermal effects literature.
+
+For even the RF power limits set by standards organizations like \cite{ICNIRP2020} \cite{IEEE2006} appear to be based on the observation that any resonance modes which might exist in biological tissues are far too overdamped due to viscous from the surrounding solvent to be of any importance \cite{Vibrational2002}; this is grounded in very solid {\it in vitro}, {\it in vivo} and theoretical evidence.
+
+On the other hand, under clinical and laboratory circumstances, a few well-established non-resonant non-thermal effects have already been put to practical use.
+An example, electroporation is now a common laboratory procedure, in which an enormous electric field causes ions in solution to migrate across a host cell's membrane.
+A variant, irreversible electroporation, has been used in the clinic for tumor ablation.
+In vitro there is evidence to suggest that sub-cellular effects take place under truly tremendous fields.
+
+\lettrine{U}nfortunately, we later realized that for both the absorption cross section and the inactivation mechanism to align as suggested requires the virus, a structure with not more than $6 \times 10^8$ atoms, to have an effective charge of $q=10^7$.
+It is very difficult to account for such a charge.
+
+% 300 MDa of hydrogen has 3e8 H atoms
+% ((100 nm)^3 * (1000 kg/m^3))/((18.15 g/mol) / avogadroConstant)
+% 600 MDa
+
+While induced polarization is not expected to occur on GHz time scales, especially where solvent ions are the charge carriers, (see ICNIRP arguments), it is possible that some subtle, extremely fast polarization effect regarding electrons could be used to explain this \cite{nature1986}.
+We have not investigated this in any depth.
+
+On the other hand, Uzunoglu have produced a formulation of the theoretical analysis which requires a very plausible charge of only $q=10^4$.
+
+In another attempt to explain non-thermally, it is possible that this result could be explained by a sort of lipid membrane leakage, attributed to oxidation, which has been observed in strikingly similar regime in liposomes; but this would not necessarily explain the frequency-dependent inactivation seen in Figure 4b of \cite{Efficient2015}.
+
+We are thoroughly mystified by the data presented.
+For the purposes of this paper, we adopt a working hypothesis that this does not represent a clinically useful effect - especially as the exposures required are close to - or greatly exceed - the thermal limit for safety.
+
+In any case, this is a very interesting result, and should be replicated with better controls.
+Gordon Reuben's team appear to be on the case, so we will not address this regime, 100 V/m, 15 minute, 8 GHz, any further.
+
+Were such a mechanism to exist, it would seem to provide significant advantages over existing UV or cold-plasma sterilization;
+
+We leave this section here because it will be useful to inform us in the next section.
 
@@
 
-\footnote{"nsPEFs"}
-
-We were inspired to undertake this project by a set of publications by Yang et al, Hung et al, Sun et al.
-
-We put some
-
-which establishes that - unique to certain viruses, and apparently unlike human cellular structures, as we shall see - coincidentally have just the right size, shape, stiffness, and net charge distribution to form a weak (Q=2) spherical dipole resonance mode which couples well to the microwave spectrum at approximately 8 GHz.
-
-More critically, [] (and, in parallel, [Hung 2014]) theoretically model and then experimentally validate in various strains of Influenza A that - due to this acoustic-resonance effect - the power density levels required to crack the lipid envelope are near the safety limits for continuous exposure to humans.
-
-The experiments are competently designed and many orthogonal measurements are made to confirm the effect.
-
-There are a few minor issues with the experimental technique; sham, blinding, and dosimetry demanded by Vjl. are not mentioned.
-
-\lettrine{U}nfortunately, we later realized that for both the absorption cross section and the requires the virus, a structure with not more than $6 \times 10^8$ atoms, to have an effective charge of $q=10^7$.
-It is very difficult to account for such a charge by any known mechanisms.
-
-% 300 MDa of hydrogen has 3e8 H atoms
-% ((100 nm)^3 * (1000 kg/m^3))/((18.15 g/mol) / avogadroConstant)
-% 600 MDa
-
-While induced polarization is not expected to occur on GHz time scales, especially where solvent ions are the charge carriers, (see ICNIRP arguments), it is possible that some subtle, extremely fast polarization effect regarding electrons could be used to explain this \cite{nature1986}.
-We have not investigated this in any depth.
-
-In another attempt to explain non-thermally, it is possible that this result could be explained by lipid membrane leakage, attributed to oxidation, which has been observed in strikingly similar regime in liposomes; but this would not necessarily explain the frequency-dependent inactivation seen in Figure 4b of \cite{Efficient2015}.
-
-We are thoroughly mystified by the data presented.
-For the purposes of this paper, we accept a working hypothesis that this does not represent a clinically useful effect - especially as the exposures required are close to - or greatly exceed - the thermal limit for safety.
-
-In any case, this is a very interesting result, and should be replicated with better controls.
-Gordon Reuben's team appear to be on the case, so we will not address this regime, 100 V/m, 15 minute, 8 GHz, any further.
-
-We leave this section here because it will be useful to inform us in the next section.
-
 First, free-space techniques are easily implemented to prevent respiratory transmission. A \$10 emitter appears to suffice on a personal level, and \$100 systems for room-scale.\\
@@
 
-One might be tempted to cite long wavelength of microwaves as an advantage. A UV photon is approximately the same wavelength as the virus itself;  In the case of, the wavelength is >> diameter, d
+One might be tempted to cite long wavelength of microwaves as an advantage.
+A UV photon is approximately the same wavelength as the virus itself;  In the case of, the wavelength is >> diameter, meaning that
 
@@
 
-If this mechanism exists, it would seem to provide significant advantages over existing UV or cold-plasma sterilization.
+It is common for.
+However, in the classical case, a non-zero resonant frequency requires the ratio of the loss in energy to the surroundings to the oscillating mass to obey $b/(2m) < \omega_{res} \sqrt{2}$ \cite{Driven}; the solution to the harmonic oscillator equation is piecewise around this value.
 
-If the extensions made in our paper are valid, this is a non-ionizing, non-thermal
+(unless the various small-scale quantum mechanical oscillators are considered, which in our case appear to require fields in excess of 1 TW to access).
 
-, non-chemical technique, harmless for continuous exposure to tissue, which can sterilize air and surfaces alike, including skin, eyes, and within hair; it evolves no ozone, can readily be generated with \$1 USD - scale devices, acts instantaneously, and - perhaps most critically - could be made to act {\bf within infected tissues}.
+Most things with a stiffness matrix has some resonant frequency\citationneeded. As far as we can tell, two justifications underpin the categorical implausibility of resonance-like behavior in
+
+Indeed, relatively trustworthy time-domain spectroscopy of proteins \cite{Microwave1994} has found that the relaxation time is proportional to the molecular weight of the structure (of which viruses are perhaps the ultimate example), and can be as slow as 100 MHz in some cases.
+
+\begin{itemize}
+	\item Viscous damping from biological solvents is so strong that the relaxation time is 
+\end{itemize}
+
+To a first order, this simply doesn't seem to be true in the case of the virion.
+
+\begin{itemize}
+	\item The charge 
+\end{itemize}
 
@@
 So far as we are aware, there are no fundamental physical obstacles to non-thermal effects in biological systems.
-As an example, electroporation is a well-established - now a common laboratory procedure, in which an enormous electric field causes ions in solution to migrate across the membrane,
-
-Such a non-thermal mechanism is quite unprecedented and extremely dubious, oft-posited but never substantiated; so it has taken some convincing that this is not a particularly abstruse artifact, especially when considered in the context of the broader non-thermal effects literature.
-For instance, the very paper (Edwards) which spurred development of the hydration-layer damping hypothesis used to explain these results, is has been quite\cite{Resonances1987} definitively\cite{Microwave1993a} shown to be an artifact, one which we unfortunately have not excluded in our study.\ In fact, even in light of the fine evidence that the other groups have collected, and the poor-quality data we have collected, we are still not entirely convinced that this effect exists - but perhaps this skepticism is unjustified.\\
-
-\lettrine{It} cannot be overstated how unexpected and positively dubious this finding appears to be - that is, based on our limited research and inexperience to date.
-
-For even the RF power limits set by standards organizations like \cite{ICNIRP2020} \cite{IEEE2006} appear to be based on the observation that no significant resonance modes exist in biological tissues due to damping forces from the surrounding tissue \cite{Vibrational2002}.
-As we shall see, this is grounded in solid {\it in vitro} (albeit more limited {\it in vivo}) evidence.
 
@@
 Additionally, other sterilization techniques may produce superior results with less faffing about and should be evaluated in the same context.
-For instance, data on far UV [Buonanno 2017] indicates safety.\\
+For instance, data on far UV\cite{Germicidal2017} indicates safety.\\
 
@@
 
-It is common for.
-However, in the classical case, a non-zero resonant frequency requires the ratio of the loss in energy to the surroundings to the oscillating mass to obey $b/(2m) < \omega_{res} \sqrt{2}$ \cite{Driven}; the solution to the harmonic oscillator equation is piecewise around this value.
-
-(unless the various small-scale quantum mechanical oscillators are considered, which in our case appear to require fields in excess of 1 TW to access).
-
-Most things with a stiffness matrix has some resonant frequency\citationneeded. As far as we can tell, two justifications underpin the categorical implausibility of resonance-like behavior in
-
-Indeed, relatively trustworthy time-domain spectroscopy of proteins \cite{Microwave1994} has found that the relaxation time is proportional to the molecular weight of the structure (of which viruses are perhaps the ultimate example), and can be as slow as 100 MHz in some cases.
-
-\begin{itemize}
-		\item Viscous damping from biological solvents is so strong that the relaxation time is 
-\end{itemize}
-
-To a first order, this simply doesn't seem to be true in the case of the virion.
-
-\begin{itemize}
-		\item The charge 
-\end{itemize}
-
 involving Schnelle
@@
 We only offer a few issues which we were particularly concerned about when designing our experiments and searching literature.
+
+; sham, blinding, and dosimetry demanded by Vjl. are not mentioned.
 

### 2021-02-11 documents/brillouin_pulse_math.tex
log colorbar
Rotation

@@
 	\includesvg[width=\textwidth]{muscle_pulse_8cm_minimize_test2}
-	\caption{Second.}
+	\caption{}
+\end{figure}
+
+\begin{figure}[H]
+	%	\makebox[\textwidth][c]{
+	\includesvg[width=\textwidth]{propagated_waveforms_detail}
+	\caption{\\
+		Some input (left) and output (right) waves (without considering oscillator coupling) transmitted through 6 cm of muscle.\\
+		X axis is time; Y axis is amplitude.
+		(a) Gaussian monopulse with 16 ps FWHM.\\
+		(b) Optimized 10 GHz sawtooth wave. Note the slight high-frequency ripple.\\ This has a frequency of approximately 1.5 GHz.\\
+		(c) Prototypical precursor 10 GHz sine burst.\\
+		(d) Continuous 10 GHz sine tone.
+}
 \end{figure}
@@
 	\includesvg[width=\textwidth]{propagated_waveforms}
-	\caption{}
+	\caption{The same four pulses plotted against depth (Y axis) and amplitude (Z axis)}
 \end{figure}

### 2021-02-11 documents/experiment_1.tex
Oh hey the brilluoin just had a bug
Rotation

@@
 We postulate the following. When the virus is lysed, the resonator is destroyed. This should be reflected in the impedance spectrum.
-We expect a non-reversible decrease in the resonance peak after the application of power.
+We would expect a non-reversible decrease in the resonance peak after the application of power.
 This should also appear in the time-domain pulse envelope; we expect a "notch" on the rising edge, with a slow taper upwards, which does not repeat on the next pulse.
@@
 One could imagine it to be otherwise.
-For instance, the lysis that occurs after phage infection of bacteria does little harm to the cell; only the permeability of the membrane is damaged\cite{GROWTH}.
+For instance, the lysis that occurs after phage infection of bacteria does little harm to the host cell; only the permeability of the membrane is damaged\cite{GROWTH}.
 Similarly, the results of the previous studies could perhaps have been obtained without necessarily destroying the virus' envelope.

### 2021-02-11 documents/lessons_learned.tex
Rotation

@@
 
-It is interesting to think about the meta-issues surrounding this project. Beta-glo assay, not a few kilometers away the food bank ran out of food and people were not able.
+It is interesting to think about the meta-issues surrounding this project.
+While an unusable \$600 Beta-Glo assay went flat, not a few kilometers away the food bank ran out of supplies and people were not able to feed their families.
+That is unjust.
 
-We have seen time and again that investment in science and technology - even basic research, so distant from the mechanics of society - can produce outsized effects on quality-of-life.
-Both NASA and CERN, neither of which do much related to people, produce a 7-to-1 and 3-to-1 return on investment.
+On the other hand, we have seen time and again that investment in science and technology - even basic research, so distant from the mechanics of society - can produce outsized effects on quality-of-life.
+Both NASA and CERN, neither of which do much related to people, produce 7-to-1 and 3-to-1 returns on investment.
 
@@
 
-You could fit a pandemic through a good-sized breakthrough. The vaccines are an excellent example, really. Moreover you learn more to be more useful in the future. Phage display  -
+You could fit a pandemic through a good-sized breakthrough.
+The vaccines are an excellent example.
+Moreover, on a personal level you learn new skills and techniques, to be more useful to others in the future.
 
@@
 
-Is it the avenue of investigation? Perhaps a lack of peer input. Maybe there were too few people involved - now that science is "bigger", we need bigger groups to efficiently manage it?
+Is it the avenue of investigation?
+An arrogance in decision making?
+Perhaps a lack of peer input.
+Maybe there were too few people involved - now that science is "bigger", we need bigger groups to efficiently manage it?
 
-Maybe if you don't have sufficient resources (knowledge, equipment, peers) to persue something efficiently, maybe it's not worth you pursuing it at all.
+Maybe if you don't have sufficient resources, equipment, knowledge, experience, or peers to persue something efficiently, or competently, and developing it slowly would not aid greatly in diffusing or disseminating knowledge, maybe it's not worth you pursuing it at all.
 

### 2021-02-11 documents/paper.tex
Text and prop improvements
Oh hey the brilluoin just had a bug
Rotation

@@
 \subfile{title}
-
-\begin{table}[h!]
-	\centering
-	\begin{tabular}{ |c|c|c|c| } 
-		\hline
-		col1 & col2 & col3 \\
-		\hline
-		& cell2 & cell3 \\ 
-		& cell5 & cell6 \\ 
-		& Negative & 5 \\ 
-		\hline
-	\end{tabular}
-
-	\caption{Data from testing on bacteriophage. Data rounded to the nearest thousand photon counts. Not thoroughly characterized. Repeatability between test conditions   Background was no. 
-	The flurometer printed a constant stream of the integration, all within the random error between capture windows $\sigma=0.5$ kcounts. }
-\end{table}
 
@@
 
+such a waveform may seem implausible but can probably be produced by e.g. an Auston switch feeding a pulse shaping line.
+
 \clearpage
@@
 
+\subfile{experiment_1}
+
+\subfile{experiment_2}
+
 \subfile{molecular_dynamics}
@@
 
+\subfile{acknowledgement}
+
 \nocite{*}
 
-%\printbibliography[]
-%\printbibliography[title={All references}]
+% LC_ALL=C tr -dc '\0-\177' <references.bib >newfile && mv newfile references.bib
+
+%\printbibliography[title={General fluidics resources}]
 

### 2021-02-17 documents/acknowledgement.tex
Text and prop improvements
Oh hey the brilluoin just had a bug
Tersenating

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Acknowledgements}\
+\section{Acknowledgments}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-Sci-Hub
+Sci-Hub - a very important thought
 
@@
 
-Profs H. Kassiri, C. David and W. Taylor (among others) at YorkU for encouragement, and H.P. and ice9 for tolerating midnight ramblings.
+Profs H. Kassiri, C. David and W. Taylor (among others) at YorkU for encouragement, and friends on twitter for tolerating midnight ramblings.
 
 Thanks to L.H. for wisdom regarding this project, and to my friend Eric, and friends at SimCoLab.
-
-Special thanks to all the people - all equally capable of writing this paper if provided the opportunity - who circumstance led to work menial shifts at the component suppliers that remained open that were so critical.
+%
+%Special thanks to all the people - all equally capable of writing this paper if provided the opportunity - who circumstance led to work menial shifts at the component suppliers that remained open that were so critical.
 Hopfstader be damned; despite the name below the abstract, this paper is of course entirely the result of circumstance and luck.
@@
 
-{\Large {\verbatim <3}}
+{\Large 
+	{
+\begin{verbatim}
+		<3 <3 <3
+\end{verbatim}
+}}
 

### 2021-02-17 documents/background.tex
Tersenating

@@
 
-\footnote{"nsPEFs"}
+We were inspired to undertake this project by a set of publications by a certain Sun group, (primarily Liu et al \cite{Microwave2009} and Yang et al \cite{Efficient2015}, simultaneously demonstrated by Hung et al \cite{focusing2014}).
 
-We were inspired to undertake this project by a set of publications by Yang et al, Hung et al, Sun et al.
+These reports attempt to establish that, ostensibly unlike human cellular structures, the studied species of viruses have about the right size, shape, stiffness, and net charge distribution such that the lowest normal mode is slightly underdamped and can be driven by intense electric fields.
 
-These reports attempt to establish that, ostensibly unlike human cellular structures, the studied species of viruses coincidentally about the right size, shape, stiffness, and net charge distribution to form a weak (Q=2) spherical dipole resonance mode which couples well to the microwave spectrum at approximately 8 GHz.
+The group theoretically model and then experimentally demonstrate in various strains of Influenza A that - supposedly due to this acoustic, normal-mode effect - the field intensity required to crack the lipid envelope is near the safety limits for continuous exposure to humans.
 
-They theoretically model and then experimentally demonstrate in various strains of Influenza A that - supposedly due to this acoustic-resonance effect - the power density levels required to crack the lipid envelope are near the safety limits for continuous exposure to humans.
+The experiments are competently designed and many orthogonal measurements are made to suggest that such an effect exists.
 
-The experiments are competently designed and many orthogonal measurements are made to confirm the effect.
+There are a few minor issues with the experimental technique (see discussion below).
 
-There are a few minor issues with the experimental technique
+These results have attracted some recent attention. \cite{Optical2020} have observed a normal mode of the same nature optically, and work is proceeding by their team.
 
-These very striking results have attracted some recent attention. \cite{Burkhartsmeier} have observed a resonance of the same nature (see below), and work is proceeding by their team.
+However, such a non-thermal mechanism is quite unprecedented and extremely dubious, oft-posited but never substantiated; so it has taken some convincing that this is not a particularly abstruse artifact, especially when considered in the context of the broader non-thermal effects literature.
 
-Such a non-thermal mechanism is quite unprecedented and extremely dubious, oft-posited but never substantiated; so it has taken some convincing that this is not a particularly abstruse artifact, especially when considered in the context of the broader non-thermal effects literature.
-
-For even the RF power limits set by standards organizations like \cite{ICNIRP2020} \cite{IEEE2006} appear to be based on the observation that any resonance modes which might exist in biological tissues are far too overdamped due to viscous from the surrounding solvent to be of any importance \cite{Vibrational2002}; this is grounded in very solid {\it in vitro}, {\it in vivo} and theoretical evidence.
+For even the RF power limits set by standards organizations like \cite{ICNIRP2020} \cite{IEEE2006} appear to be based on the observation that any resonance modes which might exist in biological tissues are categorically overdamped due to viscous from the surrounding solvent to be of any importance \cite{Vibrational2002}, and such charge distributions do not lend themselves to sufficiently strong coupling to external fields.
+This is grounded in very solid {\it in vitro}, {\it in vivo} evidence and theoretical modelling.
 
 On the other hand, under clinical and laboratory circumstances, a few well-established non-resonant non-thermal effects have already been put to practical use.
-An example, electroporation is now a common laboratory procedure, in which an enormous electric field causes ions in solution to migrate across a host cell's membrane.
-A variant, irreversible electroporation, has been used in the clinic for tumor ablation.
-In vitro there is evidence to suggest that sub-cellular effects take place under truly tremendous fields.
 
-\lettrine{U}nfortunately, we later realized that for both the absorption cross section and the inactivation mechanism to align as suggested requires the virus, a structure with not more than $6 \times 10^8$ atoms, to have an effective charge of $q=10^7$.
-It is very difficult to account for such a charge.
+As an example, electroporation is now a common laboratory procedure in which an enormous electric field causes ions in solution to diffuse across a host cell's membrane, reversibly rendering it permeable (among other, more subtle mechanisms; the minutia of poration are extraordinarily complex and beyond the author's understanding\cite{Theoretical2007}).
+
+A variant using irreversible electroporation\cite{Irreversible2013} has recently been used in the clinic\cite{Nonthermal2013} for tumor ablation.% In vitro there is evidence to suggest that sub-cellular effects take place under truly tremendous fields.
+
+\lettrine{U}nfortunately, it appears that, in order to fit Yang et al's observed data on absorption cross section, and to explain the suggested inactivation mechanism, requires that the virus, a structure with not more than $6 \times 10^8$ atoms and not more than $1 \times 10^8$ solvent molecules, to have an effective charge of $q=10^7$.
+It is difficult to account for such a charge.
+
+On the other hand, Uzunoglu have produced a formulation of the theoretical analysis which requires a more plausible charge of only $q=10^4$.
+However, whether even this charge is reasonable given solvent screening is not yet known to us.\footnotemark
 
@@
 
-While induced polarization is not expected to occur on GHz time scales, especially where solvent ions are the charge carriers, (see ICNIRP arguments), it is possible that some subtle, extremely fast polarization effect regarding electrons could be used to explain this \cite{nature1986}.
-We have not investigated this in any depth.
+\footnotetext{While induced polarization is not expected to occur on GHz time scales, especially where solvent ions are the charge carriers, (see ICNIRP arguments), it is possible that some subtle, extremely fast polarization effect regarding electrons could be used to explain this \cite{nature1986}.
+We have not investigated this in any depth.}
 
-On the other hand, Uzunoglu have produced a formulation of the theoretical analysis which requires a very plausible charge of only $q=10^4$.
-
-In another attempt to explain non-thermally, it is possible that this result could be explained by a sort of lipid membrane leakage, attributed to oxidation, which has been observed in strikingly similar regime in liposomes; but this would not necessarily explain the frequency-dependent inactivation seen in Figure 4b of \cite{Efficient2015}.
+It is possible that this result could be due to a specific sort of lipid membrane leakage, attributed to oxidation, which has been observed in strikingly similar regime in liposomes (\hyperref[sec:liburdy]{c.f.}); but this would not easily explain the frequency-dependent inactivation seen in Figure 4b of \cite{Efficient2015}.
 
@@
 In any case, this is a very interesting result, and should be replicated with better controls.
-Gordon Reuben's team appear to be on the case, so we will not address this regime, 100 V/m, 15 minute, 8 GHz, any further.
+Reuben's team appear to be on the case, so we will not address this regime, a 15 minute, 100 V/m, 8 GHz, exposure, in much detail.\\
 
-Were such a mechanism to exist, it would seem to provide significant advantages over existing UV or cold-plasma sterilization;
+Were such a mechanism to exist, it would seem to provide significant advantages over existing Far UV or cold-plasma sterilization.
 
-We leave this section here because it will be useful to inform us in the next section.
+%We leave this section here because it will be useful to inform us in the next section.
 
-There are some 20,000 papers on the topic of RF safety, with solid mechanistic, in vitro, in vivo and epidemiological evidence of safety in the 2.4 GHz and 5.8 GHz bands.
-
-However, "There are limited experimental human data upon which to set limits on exposures above 6 GHz" [Chan 2019]. Only 2\% of the above papers are on frequencies $>6$ GHz [Vijayalaxmi 2018].
-
-In addition, what data remains in this category is of varying quality.
-
-As has been starkly demonstrated in the recent hydroxychloroquine contradictions [Gautret 2020] [Geleris 2020], biological research must be essentially perfectly conducted to offer any meaningful results.
-
-So, turning to, we find an entirely new set of problems.
+%
+%
+%There are some 20,000 papers on the topic of RF safety, with solid mechanistic, in vitro, in vivo and epidemiological evidence of safety in the 2.4 GHz and 5.8 GHz bands.
+%
+%However, "There are limited experimental human data upon which to set limits on exposures above 6 GHz" [Chan 2019]. Only 2\% of the above papers are on frequencies $>6$ GHz [Vijayalaxmi 2018]. 
+%
+%In addition, what data remains in this category is of varying quality. 
+%
+%
+%
+%As has been starkly demonstrated in the recent hydroxychloroquine contradictions [Gautret 2020] [Geleris 2020], biological research must be essentially perfectly conducted to offer any meaningful results.
+%
+%So, turning to, we find an entirely new set of problems.
 This effect is presumed to depend on mechanical forces of the entire virus.
@@
 The kind which can only be obtained through extensive hard-wrought expertise (which the author does not possess) and careful verification,
-
-Multiscale or hybrid techniques would seem to offer one route out of this pickle. Simulating a small patch of lipid in explicit solvent, with the pressure provided by
-
-The stymied writer turns to writing inconclusive high-level summaries which lack sufficient detail to be of true use.
-
-First, free-space techniques are easily implemented to prevent respiratory transmission. A \$10 emitter appears to suffice on a personal level, and \$100 systems for room-scale.\\
-
-Second, via cursory FDTD simulations, using off-the-shelf equipment and modified non-invasive microwave diathermy techniques, it appears to be possible to inactivate all virions in the outer 2 cm of the lungs and inner 1 cm of the bronchi without any effect on the surrounding tissue.
-
-One might be tempted to cite long wavelength of microwaves as an advantage.
+%
+%Multiscale or hybrid techniques would seem to offer one route out of this pickle. Simulating a small patch of lipid in explicit solvent, with the pressure provided by
+%
+%The stymied writer turns to writing inconclusive high-level summaries which lack sufficient detail to be of true use.
+%
+%
+%
+%
+%
+%First, free-space techniques are easily implemented to prevent respiratory transmission. A \$10 emitter appears to suffice on a personal level, and \$100 systems for room-scale.\\
+%
+%
+%Second, via cursory FDTD simulations, using off-the-shelf equipment and modified non-invasive microwave diathermy techniques, it appears to be possible to inactivate all virions in the outer 2 cm of the lungs and inner 1 cm of the bronchi without any effect on the surrounding tissue.
+%
+%
+%
+%
+%One might be tempted to cite long wavelength of microwaves as an advantage.
 A UV photon is approximately the same wavelength as the virus itself;  In the case of, the wavelength is >> diameter, meaning that
-
-Like pumping a swing, this effect allows an otherwise inconsequential field magnitude to store energy over a small number of cycles until the virus is destroyed. \\
-\\\\
-
-It is common for.
+%
+%
+%
+%
+%Like pumping a swing, this effect allows an otherwise inconsequential field magnitude to store energy over a small number of cycles until the virus is destroyed. \\
+%\\\\
+%
+%
+%It is common for.
 However, in the classical case, a non-zero resonant frequency requires the ratio of the loss in energy to the surroundings to the oscillating mass to obey $b/(2m) < \omega_{res} \sqrt{2}$ \cite{Driven}; the solution to the harmonic oscillator equation is piecewise around this value.
-
-(unless the various small-scale quantum mechanical oscillators are considered, which in our case appear to require fields in excess of 1 TW to access).
-
-Most things with a stiffness matrix has some resonant frequency\citationneeded. As far as we can tell, two justifications underpin the categorical implausibility of resonance-like behavior in
+%
+%(unless the various small-scale quantum mechanical oscillators are considered, which in our case appear to require fields in excess of 1 TW to access).
+%
+%
+%Most things with a stiffness matrix has some resonant frequency\citationneeded. As far as we can tell, two justifications underpin the categorical implausibility of resonance-like behavior in 
+%
 
@@
 
-\begin{itemize}
-	\item Viscous damping from biological solvents is so strong that the relaxation time is 
-\end{itemize}
-
-To a first order, this simply doesn't seem to be true in the case of the virion.
-
-\begin{itemize}
-	\item The charge 
-\end{itemize}
-
-\footnote{It should be noted that this {\it confined} acoustic resonance is subtly distinct from common-and-garden pipe-organ acoustic resonance; this is apparently not a strictly classical phenomenon.
+%
+%\begin{itemize}
+%	\item Viscous damping from biological solvents is so strong that the relaxation time is 
+%\end{itemize}
+%
+%To a first order, this simply doesn't seem to be true in the case of the virion.
+%
+%
+%
+%
+%
+%\begin{itemize}
+%	\item The charge 
+%\end{itemize}
+%
+%\footnote{It should be noted that this {\it confined} acoustic resonance is subtly distinct from common-and-garden pipe-organ acoustic resonance; this is apparently not a strictly classical phenomenon.
 Besides standard Coulomb-like and Lennard-Jones-like interactions between constituent particles, if Fr\"{o}hlich is to be believed at these nanoscopic scales there are also wave-function interactions among the particles of the virus which can shift storage to modes not otherwise expected.
-
-	We confess to not yet understanding this phenomenon; fortunately, while helpful, the details of how this mode appears are not critical to implementing this technique.}
+%	
+%	We confess to not yet understanding this phenomenon; fortunately, while helpful, the details of how this mode appears are not critical to implementing this technique.}
 
@@
 
-the only analagous non-thermal mechansism we are aware of is electroporation; and that requires the diffusion of ionized sodium and potassium charge carriers through the membrane, which would seem to necessarily require a non-
-
-So far as we are aware, there are no fundamental physical obstacles to non-thermal effects in biological systems.
-
-This may account for why this paper has been largely ignored.
-
-The precise structure and charge of the virion appears to be a singular anomaly in this otherwise categorical non-existence.
-
-Any technique that requires background subtraction (see).
-
-We distinct regimes, which overlap in physical mechanisms (both involve the charge distribution and relaxation time) but which cite different bodies of literature. Vestiges
-
-frequency-dependent inactivation
-
-(gordon reuben following up)
-
-After the relaxation time, the energy is a distant memory; only the mechanical effects that were induced during that time can remain. Since the energy is too small to
+%
+%So far as we are aware, there are no fundamental physical obstacles to non-thermal effects in biological systems. 
+%
+%
+%This may account for why this paper has been largely ignored.
+%
+%The precise structure and charge of the virion appears to be a singular anomaly in this otherwise categorical non-existence.
+%
+%
+%
+%
+%
+%Any technique that requires background subtraction (see).
+%
+%
+%We distinct regimes, which overlap in physical mechanisms (both involve the charge distribution and relaxation time) but which cite different bodies of literature. Vestiges
 
@@
 }
-
-I was hoping I would have a definitive demonstration, so as to not redirect resources from more promising avenues.
-
-Note that it is possible that this has already been worked on. The last review was several months ago, and the literature is changing very rapidly. Reuben
-
-Much of the work in this paper was concerned with this paper
 
@@
 
-On the other hand, 0.5 angstroms is only a 0.04\% deflection of the capsid, whereas a general value for host cells is about 3\% deflection.
+On the other hand, a 0.5 angstrom movement is only a 0.04\% deflection of the capsid, whereas a general value for host cells is about 3\% deflection.
+In addition, with a relaxation time on the order of 500 ps, it is difficult to imagine that the energy will be sufficiently concentrated to be destructive, as after the relaxation time the energy is a distant memory; only the mechanical effects that were induced during that time can remain.
 
-Certainly the virus will be destroyed at some finite electric field. It remains to be seen whether a practical limit
+At least we do not have to justify observing an effect at an exposure of $10^{-17} W/m^2$ \cite{Resonance1996}.
 
- \cite{Resonance1996}
+Certainly the virus will be destroyed at some finite electric field.
 
@@
 
-suggestive, especially because a model organism
+%
+%suggestive, especially because a model organism
+\clearpage
 
@@
 
-On the other hand, the maximum amplitude of oscillation is only expected to be on the order of 50 picometers.
+%
+%On the other hand, the maximum amplitude of oscillation is only expected to be on the order of 50 picometers. 
+%
 
@@
 
-for which our working hypothesis is that there are no clinically useful mechanisms,
+%for which our working hypothesis is that there are no clinically useful mechanisms,
 
-It stands to reason, then, that any pulse longer than the relaxation time is not efficiently.
-
-vestiges
+It stands to reason, then, that any pulse longer than the relaxation time is not efficiently using the non-thermal nature of the effect.
 
@@
 
-as dt decreases, there's lots of room to add more zeros. a pulse 4 orders of magnitude higher than the maximum field used by practically any existing system.
+%as dt decreases, there's lots of room to add more zeros. a pulse 4 orders of magnitude higher than the maximum field used by practically any existing system.
 
@@
 
-The effects that we are concerned with occur 4 orders of magnitude above
+%The effects that we are concerned with occur 4 orders of magnitude above
 
-Windows between caused by structural or
+%Windows between caused by structural or
 
-Additionally, other sterilization techniques may produce superior results with less faffing about and should be evaluated in the same context.
+%Additionally, other sterilization techniques may produce superior results with less faffing about and should be evaluated in the same context.
 For instance, data on far UV\cite{Germicidal2017} indicates safety.\\
+%
+%"Windows" of the same sort have been found, both in thermal and pulsed ultra-high-power UV Prodouz \cite{Use1987a}.
+%
+%(more data exists for influenza A; it is sufficiently structurally similar that ).
+%
+%Excellent theoretical arguments against the possibility of non-thermal effects can be found Adair \cite{Vibrational2002}, Adair \cite{Biological2002}, and Foster \cite{Viscous2000} on microtubules. 
+%
+%
+%
+%Adair \cite{Biophysics2000} on Brillouin.
+%
+%\nameref{sec:viscousdamping}
+%
+%Owrutsky
+%
+%We don't want a purely membrane-electroporative effect since the lipid membrane of the virus is similar to (derived from) the host cell and little selectivity can be expected.
+Unless the virus has a lower capacitance and charges faster than the cell.
+%
+%Also, the pore must stay open for long enough that damage is dealt to the virus. 
+%
 
-"Windows" of the same sort have been found, both in thermal and pulsed ultra-high-power UV Prodouz \cite{Use1987a}.
+%Scope for clinical utility for this effect can be seen in the following contrast.
 
-(more data exists for influenza A; it is sufficiently structurally similar that ).
+Pakhomov \cite{Comparative} find no non-thermal effects on functioning frog heart pacemaker cells at 0.9 MV/m (although the field inside the tissue was not measured and could have been lower).
 
-Excellent theoretical arguments against the possibility of non-thermal effects can be found Adair \cite{Vibrational2002}, Adair \cite{Biological2002}, and Foster \cite{Viscous2000} on microtubules.
+Recent data by de Seze following continuous exposure to nanosecond fields at an external field of 3 MV/m \cite{Repeated2020} notes no acute effects, but
 
-Adair \cite{Biophysics2000} on Brillouin.
-
-\nameref{sec:viscousdamping}
-
-Data cannot be trusted implicitly. By time-domain spectrometry (a reasonably trustworthy technique), Miura \cite{Microwave1994} find
-
-Owrutsky Vibrational1994
-
-We don't want a purely membrane-electroporative effect since the lipid membrane of the virus is similar to (derived from) the host cell and little selectivity can be expected.
-Unless the virus has a lower capacitance and charges faster than the cell.
-
-Also, the pore must stay open for long enough that damage is dealt to the virus.
-
-Scope for this effect can be seen in the following contrast. The statement which echos the concensus of a number of literature reviews by standards organizations:
+The following statement echos the concensus of a number of literature reviews by standards organizations:
 
@@
 
-Schnelle\cite{Trapping1996}
-
 \subsection{Dielectrophoresis and electrorotation}
 
-and Fuhr\cite{Radiofrequency1994} and Grom \cite{Accumulation2006} report on a modification of so-called dielectrophoresis techniques called electrorotation, in a so-called field cage.
+Schnelle\cite{Trapping1996} and Fuhr\cite{Radiofrequency1994} and Grom \cite{Accumulation2006} and Gimsa \cite{New1999} report on using a modification of so-called dielectrophoresis techniques called electrorotation, in a so-called field cage.
 
-Rotation is sub-synchronous at a few dozen Hz, whereas the field rotates at between 0.1 MHz to over 50 MHz; in most cases the frequency is made high enough that ion does not occur.
+Such electrorotation is always sub-synchronous (unlike optical centrifuge techniques) at a few dozen Hz, whereas the field rotates at between 0.1 MHz to over 50 MHz; in most cases the frequency is made high enough that ion does not occur.
 
-In the virus tests by Schnelle, a field of 0.3 MV/m was used, without apparent damage to the virus, though their
+In the virus tests by Schnelle, a field of 0.3 MV/m was used, without apparent damage to the virus.
 
-Gimsa \cite{New1999} use a four-electrode cage at 25 kV/m
+Gimsa \cite{New1999} use a four-electrode cage at 25 kV/m to trap influenza.
 
@@
 
-Pakhomov \cite{Comparative} find no non-thermal effects on functioning frog heart pacemaker cells at 0.9 MV/m (although the field inside the tissue was not measured and could have been lower).
-
 Is this resonance of Q=2 really of any practical use?
@@
 \subsection{Liburdy's oxygen-dependent lipid leakage}
+\label{sec:liburdy}
 
@@
 
-Vijayalaxmi \cite{Biological2016} \cite{Comprehensive2018} \cite{Funding2019} already offer a number of excellent guidelines on best practices in this field; as do Chou \cite{chou1996radio}.
+Vijayalaxmi \cite{Biological2016} \cite{Comprehensive2018} \cite{Funding2019} already offer a number of excellent guidelines on best practices in this field; as do Chou \cite{chou1996radio} and \cite{Effects2016} .
 We only offer a few issues which we were particularly concerned about when designing our experiments and searching literature.

### 2021-02-17 documents/brillouin_pulse_math.tex
Tersenating

@@
 		Some input (left) and output (right) waves (without considering oscillator coupling) transmitted through 6 cm of muscle.\\
-		X axis is time; Y axis is amplitude.
+		X axis is time; Y axis is amplitude.\\
 		(a) Gaussian monopulse with 16 ps FWHM.\\
@@
 
+Producing such arbitrary electrical impulses may seem implausible; but in fact, if is a sufficiently sharp and only a few cycles are required,
+
+can probably be produced by e.g. an Auston switch feeding a pulse shaping line.
+
 Arbitrary pulses can be formed by

### 2021-02-17 documents/experiment_1.tex
Tersenating

@@
 \section{Experiment 1: Attempts at microwave absorption spectroscopy and inactivation in the microsecond pulsed 100 V/m regime}
+
+\cite{Osmotic2003} 30 atmospheres, and breaks at a pressure differential of 100 atm.
+T4 stress
+
+by $\sigma = pr / 2t $,
+t = 7 nm, r = 60 nm, and p =
+
+\subsection{Introduction}
+
+Rationale for using T4
+
+\begin{autem}
+As noted, this field reached a reasonable level of quality. 1951. Some standards.
+By using yet another design, with a new set of unknown artifacts, we are actually hampering this field;
+and so we encourage anyone who may wish to replicate this result not to use this system.
+In this case, we are limited by budget - primarily the power amplifiers we have access to.
+\end{autem}
+
+Positions of the three quantities on the slide are randomized\cite{first2000}.
+
+We have tried to comply with the guidelines
+
+Our aims with this experiment were to perform the following:
+
+\begin{itemize}
+	\item Convince ourselves that our skepticsm is unjustified.
+	\item Crudely demonstrate the pulse hypothesis.
+	\item Simulataneously, avoid any ambiguity related to the 7 C temperature rise seen in the previous paper.
+	\item Test the microwave lysis feedback
+	\item Verify the damage feedback mechanism.
+	\item Demonstrate a cheap microwave spectrometer that could be used on NCoV.
+\end{itemize}
+
+This was very dumb.
+
+Demonstrate the effect in a pulsed manner.
+
+A pulse appears to be more easily applicable in the clinic. \cite{Efficient2015}'s use of a 15 minute exposure caused us some consternation
+- had we missed something; was it possible that inactivation could take so long?
+
+second, it mitigates any possible thermal effect that could have lead to the previous results.
+
+Our justification for wanting a pulse dataset is as follows:
+
+A temperature rise of 7 deg C was found at 6 GHz.
+
+[] found detectable mutagenicity at a mere 2 C temperature rise.
+Of course, a few SNPs here and there is not complete cell lysis; it is extremely implausible that
+the results were the result of the temperature rise. But we nonetheless wanted to control this factor if possible.
+
+The antenna gain increases with frequency (naturally - it goes as aperture size / lambda).
+The gain flatness of the amplifier used is specified at [].
+If the exposure power was measured at the input to the amplifier (the method of power measurement does not appear to be mentioned), is it not
+unreasonable to expect that perhaps, at 9 GHz, the temperature rise, at some point in the 15 minute test, reached 15 C?
+
+This is all post-hoc reasoning. It strains plausibility. If we consider how many negative results went unpublished;
+if we presume that 50 other teams found no effect, is it possible that this is a 1 in 50 fluke?
+
+Because the diode detectors are in an extremely noisy environment, it was found useful to immediately digitize the signal within a mm of the output. Care in shielding may alleviate this issue.
+
+In the end, performing this was probably a mistake and unecessary, but by the time we realized this we had already put in the bulk of the time.
+
+Inspired by \cite{Biocoder2010}, we originally planned on writing the microbiology protocol directly into the {\it Eppenwolf} firmware using \cite{Noweb}.
+However, because the device was planned to run headless in a BSL, this was abandoned.
+
+The method we use is terrible. Such small volumes pose incredible headaches and low SNR for little reason.
+Ideally, we should have used a technique orthogonal to previous studies.
+
+We later found the following paper on phase fluctuation optical heterodyne spectroscopy \cite{Broadband1988}, which solves essentially all issues surrounding.
+Arguably no biological-resonance studies should ever be conducted on any less than such a setup.
+it "[requires] that only perfunctory attention be paid to the sample geometry.", and "allows very straightforward determination of the free-space absorption
+coefficient of the sample based on the photothermal signals measured as a function of distance along the transmission line."
+
+"This spectroscopic technique stands in contrast to the time-domain reflectometer and network-analyzer techniques-not
+zero-background methods-that require the measurement of small changes in large signals."
+
+It uses a phase-sensing, providing a 1 microdegree temperature measurement.
+
+This requires no special equipment beyond standard optical lab supplies - mirrors, servoing piezo stages.
+
+Microwave dielectric spectrometry ("impedance spectroscopy", "absorption spectroscopy")
+
+The notable Feldman biological spectroscopy group recommends a time-domain spectroscopy method\cite{Time2003a}, a modification of beloved TDR techniques.
+They cite several advantages, including easy subtraction of test jig artifacts.
+Generating a sharp-edged impulse with 10+ GHz spectral components is far easier and cheaper than an equivalent CW oscillator; but then we could not simultaneously expose the virus to the pulsed CW tone to verify the inactivation field thresholds.
+A 10+ GHz oscilloscope is generally required for this method, but sampling\footnotemark oscilloscopes may suffice.
+\cite{16psresolution2003} offer a simple way to do away with the delay lines that are usually required.
+
+\footnotetext{Confusing name - a 'sampling oscilloscope' builds up the waveform over a large number of cycles.}
+
+On the other hand, putting the sample into a microwave cavity resonator can often provide a much higher sensitivity.
+The sensitivity can (in some cases - there are tradeoffs - see \cite{FabryPerot1982}) be made proportional to the Q, and even a crude microwave cavity can easily have a Q > 500.
+As an example, EPR spectrometers use cavities in their microwave bridges.
+
+Cavities designed for wide-band use are generally mechanically tuned with a shorting plunger; the plunger itself presents difficulty in design\cite{Contactless2019}.
+However, conventional waveguide cavities run into overlapping modes beyond half an octave, beyond which more than one dimension must usually be altered.
+We desired a spectrum across the entire 6 - 12 GHz octave.
+
+Open-ended coaxial resonators can offer the required tuning range\cite{Wideband1981}\cite{Study2014a}. Microwave Fabry-Perot etalons are also satisfactory.\cite{FabryPerot1982}
+
+The status quou for measuring the dielectric properties of liquid is an open-ended coax dipped in the solution\cite{Coaxial1980}.
+However, these appear to be particularly prone to generating resonance-like artifacts - not that the coplanar method is necessarily any better.
+
+We end up using the coplanar waveguide setup, essentially exactly like \cite{Efficient2015}.
+Rather than expose the sample separately in a horn antenna, the entirety of the sample is held in the fringe field of the coplanar waveguide.
+This was done because of our lack of access to power amplifiers with sufficient power output to expose a large volume simultaneously; however, it ends up an andvantage, because the spectra of the sample can be obtained immediately before and after exposure without disturbance.
+
+Rather than the very professional gold and SiO2-coated sensing structure, we use a basic $50\pm20$ ohm coplanar waveguide, like \cite{Sun}.
+
+An FDTD simulation was performed of the cuvette-waveguide assembly\footnotemark.
+The bottom tape was made 0.5 mm thick in the simulation dielectric\_constant, and non-conductive\footnotemark.
+Amplitude values were obtained with a soft 50 ohm source with a 1 V peak (2v p-p) (which would produce a value of 0.5 V minus the (Shottky drop and a small frequency-dependent loss) on the detectors).
+
+The fringe field in the bottom 40\% (0.4 mm) of the fluid-filled well averaged 160 V/m per volt of uncorrected detector input amplitude, with a peak of 200 $\frac{V/m}{V}$ and two hot-spots at the interfaces of < 0.1 mm each.
+The remaining 60\% (0.6 mm) decreased from 120 $\frac{V/m}{V}$ to 60 $\frac{V/m}{V}$.
+
+\footnotetext{TODO: Update sim to new cuvette dimensions}
+
+\footnotetext{TODO: Update sim real phage fluid conductivity}
+
+[cpwg sim here]
+
+The sample is held against the waveguide in a cylindrical well 1 mm in diameter and approx.
+1 mm high, in a 3 mm high machined polycarbonate slide, 8 wells per slide.\footnotemark This is aligned on the spectrometer with plastic dowel pins.
+0.8 uL of sample are added to each well using a micropipette.
+A 0.06 mm silicone-adhesive Kapton tape insulates the fluid from the waveguide ()
+Evaporation was very significant even if the top of the well was sealed with tape, so the cuvette is capped with a layer of silicone oil in a 2.3 mm opening; this worked very effectively.
+
+[detail of slide]
+
+\footnotetext{Off-the-shelf 1536-well plates have similar dimensions and could be substituted in the future.}
+
+Such small volumes caused us no end of difficulty.
+It is very difficult to obtain a log-phase culture required; but, conversely, it is impossible to consistently add reagents or retrieve the sample after the silicone cap is added, so all the ingredients for the assay must be added before.
+
+Needless to say, this is definitely not the correct way to go about this. However, it seems provide acceptable data for these purposes.
+
+Conventional microstrip produces a considerably larger fringe field.
+However, the ground plane in microstrip is on the bottom layer.
+The sensitive QFN device ground pins would need to be stitched from the top to the bottom, inevitably adding all sorts of weird and wonderful resonators.
+We were not able to prototype with vias with sufficiently low inductance to negate thise issues; so a single-layer, top-side-only stackup is used.
+The difference in performance and in ease of layout and routing is tremendous.
+
+Coplanar waveguides are usually designed with a ground plane and via stitching on either side (GCPW), which both improves isolation and noise, but also helps to avoid parallel-plate propagation modes(\cite{Microwaves101c}, \cite{Propagation1990}, \cite{Characteristics1997}).
+Not including a ground plane avoids these modes, but decreases the available fringe field slightly.
+We did not add a ground plane.
+
+The well is covered
+
+We have tried to follow the study design best practices of \cite{Biological2016}:
+
+\section{Blinding}
+
+\section{Dosimetry}
+
+Here we are slightly deficient. Other
+
+\section{Positive control}
+
+\cite{Efficient2015} use freeze-thaw cycles to crack the viral capsid as a positive control.
+T4 appeared to be more resistant to freezing; therefore, our positive control is the aforementioned autoclaved phage.
+
+Not having a sonication probe or Electroporator
+
+\section{Sham controls}
+
+Properties:
+
+active phage/sterile broth/autoclaved phage/dilute phage in saliva
+e. coli / no e. coli (sterile broth)
+300 exposed / 200 exposed / 100 exposed / un- or sham-exposed
+1 unit time pulse-exposed / 10 unit time pulse-exposed / continuous-exposed
+on-resonance exposed / off-resonance exposed
+
+Of these, the following combinations make sense:
+
+"negative control": Active phage \& e. coli \& sham-exposed
+"e.coli control": Sterile broth \& e. coli \& sham-exposed
+"sterility control": Sterile broth \& no e. coli \& sham-exposed
+"positive control": Autoclaved phage \& e. coli \& sham-exposed
+"continuous trial": Autoclaved phage \& e. coli \& sham-exposed
+
+Each on two plates.
+
+The signal used was spectrally impure; phase noise was very high. However, all spurs are at about 3 dB down.
+
+VCO voltages were calibrated to frequencies using a HackRF One and an HMC /8 frequency divider.
+
+(A downconverter using an HMB and a custom 6.4 GHz LO was tried, but it was found that this was much less informative and more confusing
+due to a lack of effective mixer image and LO spur rejection.)
+
+It is possible to subtract the diode drop using [], but because of design flaws in the AC coupling of the detectors, this was not done.
+A Shottky drop of 0.25 V is assumed in all cases.
+
+- Un-exposed phage-only control:
+
+Add 1 unit phage to cuvette. Monitor turbidity.
+
+- Un-exposed e. coli control.
+- Exposed e. coli control.
+- Exposed phage control.
+- Un-exposed e. coli + phage control
+- Un-exposed e. coli + positive autoclaved phage control
+- 1 - minute exposed
+
+To preclude the possibility of damage to the sample while the spectrum is recorded.
+
+0.3 V on a 50-ohm line is
+
+%0.4 mW × 10 s / ((4 J / (g × K)) × 0.2 µL × (1 g / mL)) ➞ K
+
+5 K
 
@@
 
+\begin{center}
+	\begin{tabular}{ |c|c|c|c| } 
+		\hline
+		col1 & col2 & col3 \\
+		\hline
+		\multirow{3}{4em}{Multiple row} 
+		& cell2 & cell3 \\ 
+		& cell5 & cell6 \\ 
+		& cell8 & cell9 \\ 
+		\hline
+	\end{tabular}
+\end{center}
+
+All biasing and power supplies were programmable and sequenced via an arrangement of DACs and amplifiers.
+
+The sample rate of the delta-sigma ADCs was not sufficient to capture the amplitude of the short pulses; therefore
+
+\begin{figure}[H]
+	\centering
+
+	\includegraphics[width=\textwidth]{{screenshot_192.168.0.38_2020-11-26_13:38:24}.png}
+
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+
+	\includegraphics[width=\textwidth]{{pulse_detail}.png}
+
+\end{figure}
+
+\subsection{Weakened phage capsid testing}
+
+Ishii and Yanagida \cite{two1977} and Qin \cite{Structure2010} find at a pH of 10.6, about 0.3x inactivation after a few minutes of incubation at 37 C, slowly increasing to.
+The capsid is weakened greatly by the base, relying on the "clamp proteins" hoc and soc.
+
+\section{Saturated salt solution}
+
+100 g NaCl was added to 0.25 mL of PG1.
+
+counts only 5000.
+
+pulse\_VCO(10000); and 0.20 deadly current. a consistent 2.96 V maximum was observed.
+
+3200 counts on 0, exposed
+
+ran a sham:
+
+3200 counts.
+
+darnit!
+
+blank counts, with 1 ml water, are about 500.
+
 \end{document}

### 2021-02-17 documents/experiment_1_data.tex
Tersenating

--- 2021-02-09 documents/experiment_1.tex
@@
-%!TeX root = experiment_1
+%!TeX root = experiment_1_data
 \documentclass[paper.tex]{subfiles}
@@
 
-\section{Experiment 1: Attempts at microwave absorption spectroscopy and inactivation in the microsecond pulsed 100 V/m regime}
-
-\subsection{Microwave lysis feedback}
-
-We postulate the following. When the virus is lysed, the resonator is destroyed. This should be reflected in the impedance spectrum.
-We expect a non-reversible decrease in the resonance peak after the application of power.
-This should also appear in the time-domain pulse envelope; we expect a "notch" on the rising edge, with a slow taper upwards, which does not repeat on the next pulse.
-
-If this exists, it would provide a great deal of feedback.
-Not only would the virus be destroyed, but we would have an instant, quantitative determination of of how effective each treatment was.
-In practice, this could be done by applying two pulses in quick succession and monitoring the change in the reflected power; or perhaps by a time-domain pulse-shape method.
-Whether such a signature can be discriminated from background in a clinical setting remains to be seen.
-
-At the time, this seemed important to establish, as it would allow the inactivation threshold to be determined without a time-intensive and potentially dangerous infectivity assay step (making it more plausible that we would get biosafety approval to obtain the microwave spectrum of NCoV).
-
-One could imagine it to be otherwise.
-For instance, the lysis that occurs after phage infection of bacteria does little harm to the cell; only the permeability of the membrane is damaged\cite{GROWTH}.
-Similarly, the results of the previous studies could perhaps have been obtained without necessarily destroying the virus' envelope.
+\begin{center}
+	\begin{tabular}{ |c|c|c| } 
+		\hline
+		 & col2 & col3 \\
+		\hline
+		\multirow{3}{4em}{Multiple row} 
+		& cell2 & cell3 \\ 
+		& cell5 & cell6 \\ 
+		& cell8 & cell9 \\ 
+		\hline
+	\end{tabular}
+\end{center}
 

### 2021-02-17 documents/paper.tex
Tersenating

@@
 
-\section{Figures which have nothing to do with our conclusion but are pretty nonetheless}
+\section{Figures which have little to do with our conclusion but are pretty nonetheless}
 
@@
 	\includegraphics[width=\textwidth]{pulse_exposure_setup.JPG}
-	\caption{\\ \textit{Chengxiang} pulse exposure jig.
-pulser seen off the left.
-Autosampler Pulse shaping plate not shown.
+	\caption{\\ \textit{Chengxiang} nanosecond pulse exposure jig.
+Pulser seen off the left.
+Pulse shaping plate not shown.
 Aluminum disc belongs to the scan-conversion digitizer, not used in this study.}
@@
 	\includegraphics[width=\textwidth]{eppenwolf_2.jpg}
-	\caption{\\ \textit{Eppenwolf} misguided pulsed X-Band microwave spectrometer used in this study, pictured with the near-field cuvette installed.}
+	\caption{\\ \textit{Eppenwolf} misguided pulsed X-Band microwave spectrometer used in this study. (cuvette shown was replaced by the same )}
 \end{figure}
@@
 	\includegraphics[width=\textwidth]{bronch_9GHz_500W_2_transparent.png}
-	\caption{\\ \textit{Eppenwolf} misguided pulsed X-Band microwave spectrometer used in this study, pictured with the near-field cuvette installed.}
+	\caption{Simulation of a (largely ineffective) bronchoscopic method.}
 \end{figure}
 
-\begin{figure}[H]
-	\makebox[\textwidth][c]{
-		\includegraphics[width=\textwidth*2]{chunk_4_line_2_1.png}
-	}%
-	\caption{Chunk 4, it.is Founda}
-\end{figure}
+%
+%\begin{figure}[H]
+%	\makebox[\textwidth][c]{
+%		\includegraphics[width=\textwidth*2]{chunk_4_line_2_1.png}
+%	}%
+%	\caption{Chunk 4, it.is Founda}
+%\end{figure}
 
-\clearpage
+%\clearpage
 
@@
 \begin{figure}[H]
-	\captionsetup{singlelinecheck = false, justification=justified}
-	\centering
-	\includesvg[width=\textwidth]{compChargePlot}
-	\caption{
-		\light{
-			\\
-			We've got a thing\\
-			that's called\\
-			{\it Radar Love}\\}
-		We've got a wave\\
-		in the air}
+	%	\makebox[\textwidth][c]{
+	\includesvg[width=\textwidth]{propagated_waveforms}
+	\caption{Brillouin precursor propagation through tissue (reproduced from section 6).\\
+	(a) Gaussian monopulse with 16 ps FWHM.\\
+	(b) Optimized 10 GHz sawtooth wave. Note the slight high-frequency ripple.\\ This has a frequency of approximately 1.5 GHz.\\
+	(c) Prototypical precursor 10 GHz sine burst.\\
+	(d) Continuous 10 GHz sine tone.}
+
 \end{figure}
 
-such a waveform may seem implausible but can probably be produced by e.g. an Auston switch feeding a pulse shaping line.
+%\begin{figure}[H]
+%	\captionsetup{singlelinecheck = false, justification=justified}
+%	\centering
+%	\includesvg[width=\textwidth]{compChargePlot}
+%	\caption{Charge distribution using Poisson Boltzmann}
+%\end{figure}
+%
 
@@
 
+\subfile{personal_device}
+
 \section{Appendix on microbiology}
@@
 
-%\printbibliography[title={General fluidics resources}]
+\printbibliography[title={All references}]
 

### 2021-02-17 documents/summary.tex
Tersenating

%!TeX root = summary
\documentclass[paper.tex]{subfiles}
\begin{document}

\section{Terse? I can be terse. Once, in flight school, I was laconic.}

There might be some large-scale structural difference between viruses and all host cellular structures that might used as leverage to inactivate the virus by some physical means. Such an inactivation "window" between host cell and virion damage has been found in certain far wavelengths of UV\cite{Germicidal2017} - but also \cite{Use1987a}\cite{Can1993}; in fact

More specifically, the idea of driving the virus as a harmonic oscillator has been considered very little \cite{Comment2004}, perhaps first because in almost all cases structures in tissue are so over-damped by the surrounding solvent\cite{Vibrational2002}\cite{Biological2002}\cite{Biophysics2000}\cite{Viscous2000} as to have no non-zero resonant frequency at all \cite{dielectric1996}\cite{gabriel1996compilation}\wikinote{not in citation}\wikinote{discuss}; and second, because the charge distribution on biological cells is too. On the other hand, the possibility of a slightly underdamped virion does not appear to be entirely unexpected; classical viscous Stokes drag predicts such behaviour\cite{nature1986}, and large proteins have been found with similar properties\cite{Microwave1994}; and while MHz transverse resonances in microtubules are ruled out\cite{Viscous2000}, the same arguments suggest that GHz longitudinal modes may exist.

Whether the small difference in driven amplitude between, for example, a $Q\approx0.5$ host structure normal mode and a $Q\approx6$ virion mode can be of any clinical value is unknown to us.

Originally these were borne from work by Frolich on the formation of large-scale bose-like QM condensates, then to many more subtle lines of inquiry; but, to our knowledge, no non-classical effects have ever been substantiated; in fact, consensus appears to be that, not only are oscillatory effects very unlikely, no relevant non-diffusion-like non-thermal effects have ever been substantiated.

Pulses beyond 1 ns in length \cite{Effect2008}

In our cursory testing, Bacteriophage T4 did not appear to be lysed by microsecond pulses between 6 and 12 GHz at about 70 V/m, nor did nanosecond pulses up to 1 MV/m appear to have any effect.

Capsid and envelope breakage at 100 pulses, 500 ns at 3 MV/m, has been previously observed\cite{Inactivation1990} but the RNA damage suggests that this is an electrochemical artifact \cite{Formation1996} (and \cite{Microwave1987}). Long pulses electroporate enveloped viruses similarly to host cells\cite{AC2017} but do not necessarily affect T4\cite{Manipulation2013}.

Pakhomov \cite{Comparative} find no non-thermal effects on functioning frog heart pacemaker cells at 0.9 MV/m (although the field inside the tissue was not measured and could have been lower).

Recent data by de Seze following continuous exposure to nanosecond fields at an external field of 3 MV/m \cite{Repeated2020} notes no acute effects, but

Almost all biological spectroscopy techniques have produced resonance-like artifacts at some point in the literature, and even the most striking and competently-obtained absorption data should not necessarily be trusted implicitly. In order of highest to lowest apparent reliability for resonance measurement:

Background-free photothermal optical \cite{Microwave1993a}\cite{Broadband1988} >\\ time-domain spectroscopy\cite{Time2003}\cite{Dielectric2004}\cite{Microwave1994} >\\ Raman or other non-photothermal optical (\cite{optical1983} $\neq$ [\cite{Resonances1987} \cite{Dielectric1989}]) and also \footnote{see Taylor \cite{mechanisms1981} citing unpublished, personal communication} (but we have no understanding of how such artifacts could form) >\\ VNA CW absorption or reflection ( \cite{Microwave1982} $\neq$ [\cite{Resonances1987} \cite{Dielectric1989}]) \footnote{Anywhere we liked}; but trustworthiness probably depends most significantly on the quality of error analysis; many have made good use of otherwise unreliable techniques \cite{Substitution1982} \cite{Millimeter1980}.

Positive artifacts are very common in this field, and extreme care in experimental design appears to be required to produce any meaningful result. Excellent best-practices guidelines and meta-analyses are available in \cite{Biological2016} \cite{Comprehensive2018} \cite{Funding2019}, \cite{chou1996radio} and \cite{Effects2016}.

Thermal effects appear to be most common. Most critically, the localized hotspots created by microwave exposure are often almost impossible to measure. Ideally, experimental design should guarantee that even slight temperature rise, more than about 3 C, cannot occur \cite{DNA2004}, or use thermally-matched shams.

FDTD simulation of exposure geometry and sample heating is now usually possible with free, open-source software\footnote{PyTorch FDTD library from \cite{Highly2019} was used in our study with some modification, but \cite{CUDAbased2019} and \cite{openEMS} are also excellent} and should be performed. Metal ions from electrodes, UV exposure, and polymer surface effects must be ruled out by experimental design. The only artifact-free appear to be 1. Remote exposure, actively cooled OR pulsed exposure with sufficiently short pulses to rule out heating, with.

Coherent control targeting small proteins seems to require very large fields. Coherent control of large-scale structural modes using ; however these results have failed replication.

If the effect exists, it appears to be impossible at any input power to externally drive a 10 GHz resonator in the lungs because of the layer of conductive muscle that shields the chest cavity. There is precedent for bronchoscopic \cite{Flexible2019}\cite{Antenna2018} or more invasive methods. Dispersion and Brillouin precursors do offer a significant improvement in loss through tissue, and the required electrical waveforms appear to be synthesizeable by variable-impedance or stub transmission-line pulse shaping\cite{Arbitrarya} . A sawtooth might be the optimal waveform. However, obtaining 10 GHz tones deep in the body is still very hard.

Although not sensitive to infectivity, as suggested by \cite{Quantification2020}, amplification-free fluorescence dsDNA detection using photon-counting plate readers using a 1:1 mix of viral solution with 1/4000 Biotium GelGreen is a very convenient (stable over long periods of time, requires no host culture) and sufficiently sensitive (titers down to $10^9$ of T4 (170 kbp dsDNA)) assay both for capsid damage and, by melting the capsid with an autoclave, for general virus titer estimation, far faster than even high-throughput plaque assays. More useful enveloped viral surrogates like Pseudomonas phage Phi 6 are RNA and a lower sensitivity can be expected.

While their bandwidth is narrow, very cheap 0.5" laser line thin-film filters still work great for both excitation and emission for fluorescence techniques. Blue LEDs like are then sufficient for excitation (though high CRI white LEDs emit more blue, green leakage is too high). Dichroic mirrors are unnecessary. Use a plastic fiber optic at right angles to decrease excitation light scattering. Beware material autofluorescence - custom Lexan cuvettes unexpectedly overwhelmed the DNA signal. (final set: [ in series with Thorlabs FL05532, 532nm, 10 nm FWHM] [Edmund 28432, 486 nm])

In both of our final experimental setups, non-grounded, single-sided coplanar waveguides were used as exposure chambers. A programmable syringe pumped 50 uL of viral fluid through one of the coplanar channels. Simulations showed a significant decrease in field. \cite{Microchamber2011} and \cite{Characterization2012} provide a good review of pulse exposure cells and a design which is much better than ours and should be used instead. Such cells should be used rather than our crude design. \footnote{the utility wcalc was used extensively}.

Electrorotation of viruses has been reported\cite{Analysis2004}\cite{New1999}\cite{comprehensive2001}, but as yet only in a non-destructive low-speed sub-synchronous regime for sensing with optical. Dielectrophoresis and electrostatic trapping of viruses has also been reported.

Data on the charge distribution of the virion can be obtained by and 2D-PAGE relative protein composition or perhaps directly via extraction from CryoEM maps.

Avalanche transistors are sufficient and perhaps the easiest way to produce high power sub 100 ps pulses. We stole an avalanche Marx design verbatim from Li (\cite{Development2016b} \cite{Design2018c}), which allows large pulses from lower voltage supplies (albeit requiring somewhat costly capacitors); but  If a fast laser is available, Auston switches appear to be equally effective. It is difficult to make spark gaps run than 200 ps without the Marx overvoltage.

We are particularly excited by the prospect of using picosecond time-domain measurements not only to perform steady state dielectric measurements or monitor the input pulse, as is now common practice, but to resolve the internal effects of a single high-voltage pulse on the virus in real time - a technique which has not, to our knowledge, previously been demonstrated. Scan-converter based transient digitizers, such as the Tektronix SCD-5000 series, appear to be the lowest-cost method of obtaining such THz sampling bandwidths. When high voltage pulses are available, miniaturized \ntilde 2 mm internal diameter pumped scan converter tubes like Fecher micro-oscillographs using direct-electron-detection in-vacuum CMOS image sensors appear to be an easy way to digitize 20+ GHz transients. The main bandwidth limitation appears to be the length of the Y deflection plate and the sensitivity of the recording medium.

Using Eppendorf tubes as. Impedimetric

\end{document}

### 2021-02-17 documents/supplemental.tex
Tersenating

@@
 %
-However, a third element is also required:
+However, in practice a third element is also required:
 %
@@
 
-With large feedback-loop structures, such as long PiN-switched phasing lines, proximity effects from nearby flesh would detune the oscillator significantly.
+With large feedback-loop structures, such as long PiN-switched phasing lines, proximity effects from nearby flesh were found to detune the oscillator significantly.
 
@@
 
+FIX THIS IT'S WRONG
+
 Naturally, if one is competent, this discrepancy will be immediately obvious.
@@
 \clearpage
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-{\Large Microwave Musings}\\
-
-	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-	\noindent\fbox{\parbox{\linewidth}{
-			Toolchain:
-			\begin{itemize}
-				\item Failed oscillator feedback-loop optimization toolchain: QUCS 0.0.20 + python-qucs + scipy's 'basinhopper'
-				\item Successful A slightly modified ngspice + ngspyce + pyEVTK
-				\item gprMax for FDTD EM simulation
-				\item KiCAD, wcalc, scikit-rf, ngspice
-			\end{itemize}
-	}}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%{\Large Microwave Musings}\\
 %
-
-	Microwave design has a reputation for being the purview of wizards. Modern RF software packages like HFSS, Microwave Office, Agilent's ADS, and Mathworks' RF toolbox, for which; component models
-
-	Luckily, this project falls perfectly within the subset of microwave technologies that do not require a goatee.
+%	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%	
+%	\noindent\fbox{\parbox{\linewidth}{
+%			Toolchain:
+%			\begin{itemize}
+%				\item Failed oscillator feedback-loop optimization toolchain: QUCS 0.0.20 + python-qucs + scipy's 'basinhopper'
+%				\item Successful A slightly modified ngspice + ngspyce + pyEVTK
+%				\item gprMax for FDTD EM simulation
+%				\item KiCAD, wcalc, scikit-rf, ngspice
+%			\end{itemize}
+%	}}
+%	%
+%	
+%	
+%	Microwave design has a reputation for being the purview of wizards. Modern RF software packages like HFSS, Microwave Office, Agilent's ADS, and Mathworks' RF toolbox, for which; component models 
+%	
+%	Luckily, this project falls perfectly within the subset of microwave technologies that do not require a goatee.
 The vast majority of the behavior of most circuits can be accurately modelled with the very same SPICE tools as one would use at low frequencies.
 With judicious application of reference designs, it seems to be possible to design
-
-	Before about 2005, however, it seems to have been somewhat the norm to write a simple numerical code to solve the problem at hand based on underlying principles.
-
-	We are also aided by the fact that what took a \$150,000 computing cluster a single decade ago can now be done in a few minutes by a single budget GPU.
-
+%	
+%	Before about 2005, however, it seems to have been somewhat the norm to write a simple numerical code to solve the problem at hand based on underlying principles.
+%	
+%	We are also aided by the fact that what took a \$150,000 computing cluster a single decade ago can now be done in a few minutes by a single budget GPU.
+%
+%
+%
 many programs try to implement their own command scripting language
-if the api doesn't expose access to the data on each timestep, then you're limited to the features that have already been implemented
+if the api doesn't expose fast access to the data on each timestep, then you're limited to the features that have already been implemented
 

### 2021-02-17 electronics/simple_fdtd/fdtd_PCB_extensions/fdtd_PCB_extensions/sources.py

@@ -82,6 +82,9 @@ class Port:
         return (pcb.grid.E[self.N_x,self.N_y,z_slice,Z]/sqrt(epsilon_0))*(pcb.cell_size)
 
 
+# see http://www.cse.yorku.ca/~kosta/CompVis_Notes/fourier_transform_Gaussian.pdf
+# http://www.sci.utah.edu/~gerig/CS7960-S2010/handouts/04%20Gaussian%20derivatives.pdf
+
 def normalized_gaussian_pulse(pcb,fwhm):
     t = pcb.time
     sigma = fwhm/2.355
@@ -92,6 +95,7 @@ def normalized_gaussian_derivative_pulse(pcb,fwhm):
     sigma = fwhm/2.355
     return (exp((1.0/2.0) - (t**2.0)/(2.0*sigma**2.0))*t)/sigma
 
+###############################################################################
 
 def gaussian_derivative_pulse(pcb, dt, beta):
     #have to normalize
@@ -103,10 +107,7 @@ def gaussian_derivative_pulse(pcb, dt, beta):
     part_two = -2.0*(s**2.0)*b
     return part_one * part_two
 
-
 #scipy.stats.norm.pdf(x, mu, sigma)*(mu - x)/sigma**2
-
-
 
 def compute_all_voltages(pcb):
     for port in pcb.component_ports:

### 2021-02-17 documents/summary.tex
whatever

@@
 
-\section{Terse? I can be terse. Once, in flight school, I was laconic.}
+\subfile{title}
 
-There might be some large-scale structural difference between viruses and all host cellular structures that might used as leverage to inactivate the virus by some physical means.
-Such an inactivation "window" between host cell and virion damage has been found in certain far wavelengths of UV\cite{Germicidal2017} - but also \cite{Use1987a}\cite{Can1993}; in fact
+\begin{figure}[H]
+%\captionsetup{singlelinecheck = false, justification=justified}
+	\centering
 
-More specifically, the idea of driving the virus as a harmonic oscillator has been considered very little \cite{Comment2004}, perhaps first because in almost all cases structures in tissue are so over-damped by the surrounding solvent\cite{Vibrational2002}\cite{Biological2002}\cite{Biophysics2000}\cite{Viscous2000} as to have no non-zero resonant frequency at all \cite{dielectric1996}\cite{gabriel1996compilation}\wikinote{not in citation}\wikinote{discuss}; and second, because the charge distribution on biological cells is too.
-On the other hand, the possibility of a slightly underdamped virion does not appear to be entirely unexpected; classical viscous Stokes drag predicts such behaviour\cite{nature1986}, and large proteins have been found with similar properties\cite{Microwave1994}; and while MHz transverse resonances in microtubules are ruled out\cite{Viscous2000}, the same arguments suggest that GHz longitudinal modes may exist.
+	\subfloat[]{
+		\includegraphics*[width=0.5\textwidth]{pulse_exposure_setup.JPG}
+	}
+	\subfloat[]{
+		\includegraphics*[width=0.5\textwidth]{eppenwolf_2.jpg}
+	}
+    \hfill
+	\subfloat[]{
+		\includegraphics*[width=0.5\textwidth]{bronch_9GHz_500W_2_transparent.png}
+	}
+	\subfloat[]{
+		\includegraphics*[width=0.5\textwidth]{CPWG_sim_pretty_2}
+	}
+    \hfill
 
-Whether the small difference in driven amplitude between, for example, a $Q\approx0.5$ host structure normal mode and a $Q\approx6$ virion mode can be of any clinical value is unknown to us.
+	\subfloat[]{
+		\includegraphics[width=0.3\textwidth]{x_gal.jpg}
+	}
+	\subfloat[]{
+		\includegraphics[width=0.5\textwidth]{fluro_1}
+	}
+%	\caption{Simulation of a (largely ineffective) bronchoscopic method.}
+%	\caption{\\ \textit{Chengxiang} nanosecond pulse exposure jig.
+Pulser seen off the left.
+Pulse shaping plate not shown.
+Aluminum disc belongs to the scan-conversion digitizer, not used in this study.}
+%		\caption{\\ \textit{Eppenwolf} misguided pulsed X-Band microwave spectrometer used in this study. (cuvette shown was replaced by the same )}
+%	\caption{Brillouin precursor propagation through tissue (reproduced from section 6).\\
+%		(a) Gaussian monopulse with 16 ps FWHM.\\
+%		(b) Optimized 10 GHz sawtooth wave. Note the slight high-frequency ripple.\\ This has a frequency of approximately 1.5 GHz.\\
+%		(c) Prototypical precursor 10 GHz sine burst.\\
+%		(d) Continuous 10 GHz sine tone.}
+\end{figure}
+\clearpage
 
-Originally these were borne from work by Frolich on the formation of large-scale bose-like QM condensates, then to many more subtle lines of inquiry; but, to our knowledge, no non-classical effects have ever been substantiated; in fact, consensus appears to be that, not only are oscillatory effects very unlikely, no relevant non-diffusion-like non-thermal effects have ever been substantiated.
+%	\caption{FDTD simulation geometry of the 0.3 mm coplanar waveguide exposure cell. Red object is the fluid channel. Visualized with Paraview.
+%	\ghfile{covidinator/electronics/simple_fdtd/run/microfluidic_coplanar.py}}
+%
 
-Pulses beyond 1 ns in length \cite{Effect2008}
+%
+%\begin{figure}[H]
+%	\makebox[\textwidth][c]{
+%		\includegraphics[width=\textwidth*2]{chunk_4_line_2_1.png}
+%	}%
+%	\caption{Chunk 4, it.is Founda}
+%\end{figure}
 
-In our cursory testing, Bacteriophage T4 did not appear to be lysed by microsecond pulses between 6 and 12 GHz at about 70 V/m, nor did nanosecond pulses up to 1 MV/m appear to have any effect.
+%\clearpage
 
-Capsid and envelope breakage at 100 pulses, 500 ns at 3 MV/m, has been previously observed\cite{Inactivation1990} but the RNA damage suggests that this is an electrochemical artifact \cite{Formation1996} (and \cite{Microwave1987}).
-Long pulses electroporate enveloped viruses similarly to host cells\cite{AC2017} but do not necessarily affect T4\cite{Manipulation2013}.
+%\section{Terse? I can be terse. Once, in flight school, I was laconic.}
 
-Pakhomov \cite{Comparative} find no non-thermal effects on functioning frog heart pacemaker cells at 0.9 MV/m (although the field inside the tissue was not measured and could have been lower).
+We were inspired to undertake this project by a set of publications by a certain Sun group, (primarily Liu et al \cite{Microwave2009} and Yang et al \cite{Efficient2015}, simultaneously demonstrated by Hung et al \cite{focusing2014}), and \cite{Optical2020} \cite{Theoretical2020}.
 
-Recent data by de Seze following continuous exposure to nanosecond fields at an external field of 3 MV/m \cite{Repeated2020} notes no acute effects, but
+We have some minor questions regarding experimental technique\footnote{The use of absorption spectroscopy methods without an error analysis is concerning (see below); an effective charge of $q=10^7 e^-$ was found, which is very hard to explain; a lack of free-space dosimetry or simulation means frequency-selective inactivation could have been due to instrument response, infrared thermography only determines surface temperature.} in the original papers that can only be addressed by more extensive replication studies, and luckily are due to be answered by other groups\cite{Generating}, so we do not defer greatly to their observations.
+
+These studies are all founded on the idea that there might be some large-scale structural difference between viruses and all host cellular structures that might usable as leverage to selectively inactivate the virus by some physical - rather than biological - means.
+Such an inactivation "window" between host cell and virion damage has been found in certain wavelengths of CW Far UV\cite{Germicidal2017} - but also apparently in certain modulated UV pulses\cite{Use1987a}\cite{Can1993}, and also sporadically reported for simple thermal treatment\cite{Summary}.
+
+More specifically, the concept of driving a virus as a harmonic oscillator has been previously considered only briefly \cite{MECHANICAL1968}\cite{Comment2004}, perhaps first because in almost all cases structures in tissue are so over-damped by the surrounding solvent\cite{Vibrational2002}\cite{Biological2002}\cite{Biophysics2000}\cite{Viscous2000} as to have no non-zero resonant frequency at all \cite{dielectric1996}\cite{gabriel1996compilation}\wikinote{not in citation}\wikinote{discuss}; and second, because the charge distributions in biology are too small for energies significantly above the thermal background to be absorbed via applied fields.
+
+On the other hand, the possibility of a slightly underdamped virion does not appear to be entirely unexpected; classical viscous Stokes drag predicts such behavior\cite{nature1986} (see supplemental), and large proteins have been found with similar properties\cite{Microwave1994}; and while MHz transverse resonances in microtubules are ruled out\cite{Viscous2000}, the same arguments suggest that very weak GHz longitudinal modes may exist.
+
+Whether the small difference in driven amplitude between, for example, a $Q\approx0.5$ host structure normal mode and a $	Q\lessapprox6$ virion mode could possibly be of any clinical value is unknown to us.
+
+These ideas appear to have originated from work by Frolich on the possibility of large-scale QM Bose-Einstein condensates, and then many more subtle lines of inquiry\cite{Mechanisms1992}\cite{mechanisms1981}; but, to our knowledge, no such large-scale non-classical effects have ever been substantiated; suggestions of non-classical damping due to hydration layer effects have not been observed.
+In fact, consensus\cite{Exposure2009}\cite{ICNIRP2020}\cite{C95} appears to agree that, not only are oscillatory effects implausible, there are no relevant, substantiated, non-diffusion-like non-thermal mechanisms.
+
+In our cursory testing, Bacteriophage T4 did not appear to be lysed by microsecond pulses between 6 and 12 GHz at about 70 V/m, nor, exploring non-resonant inactivation, did nanosecond pulses up to 1 MV/m appear to have any effect.
+Note than neither of these regimes overlap with the results of the previous studies.
+
+ Non-resonant capsid and envelope breakage at 100 pulses, 500 ns at 3 MV/m, has been previously observed\cite{Inactivation1990} but the RNA damage suggests that this is an electrochemical artifact \cite{Formation1996} (and \cite{Microwave1987}).
+Long pulses at $10$ MV/m electroporate enveloped viruses similarly to host cells\cite{AC2017} but do not necessarily affect T4\cite{Manipulation2013}.
+
+In terms of host safety, Pakhomov \cite{Comparative} find no non-thermal effects on functioning frog heart pacemaker cells at 0.9 MV/m (although the field inside the tissue was not measured and could have been lower).
+Excellent recent \textit{in vivo} data by de Seze following continuous exposure to nanosecond pulse trains at an external field up to 3 MV/m \cite{Repeated2020} notes little acute effects, but a massive rate of long-term carcinogenicity.
+
+In almost all recently updated standards, the precautionary 100 kV/m instantaneous field limits established by ANSI have been abolished due to a lack of evidence of harm; an excellent review in this regime is \footnote{\cite{treatyelectromagnetic}, as cited by \textit{C95.1-2019, B.4.3 Rationale for pulsed RF field limits}}.
+Field limits are now set only by integrated pulse energy.
+
+Electrorotation\cite{Electrorotation1988}\cite{Electrorotation1997} of viruses has been reported\cite{Analysis2004}\cite{New1999}\cite{comprehensive2001}, but as yet only in a non-destructive low-speed sub-synchronous regime for sensing, using optical means to detect rotation rate.
+Dielectrophoresis and electrostatic trapping of viruses has also been reported.
+
+Data on the charge distribution of the virion can be obtained by and 2D-PAGE relative protein composition or perhaps directly via extraction from CryoEM maps.
+
+Tsen
+
+Liburdy
 
 Almost all biological spectroscopy techniques have produced resonance-like artifacts at some point in the literature, and even the most striking and competently-obtained absorption data should not necessarily be trusted implicitly.
+Trustworthiness probably depends most significantly on the quality of error analysis; many have made good use of otherwise unreliable techniques.
 In order of highest to lowest apparent reliability for resonance measurement:
 
-Background-free photothermal optical \cite{Microwave1993a}\cite{Broadband1988} >\\ time-domain spectroscopy\cite{Time2003}\cite{Dielectric2004}\cite{Microwave1994} >\\ Raman or other non-photothermal optical (\cite{optical1983} $\neq$ [\cite{Resonances1987} \cite{Dielectric1989}]) and also \footnote{see Taylor \cite{mechanisms1981} citing unpublished, personal communication} (but we have no understanding of how such artifacts could form) >\\ VNA CW absorption or reflection ( \cite{Microwave1982} $\neq$ [\cite{Resonances1987} \cite{Dielectric1989}]) \footnote{Anywhere we liked}; but trustworthiness probably depends most significantly on the quality of error analysis; many have made good use of otherwise unreliable techniques \cite{Substitution1982} \cite{Millimeter1980}.
+Background-free photothermal optical \cite{Microwave1993a}\cite{Broadband1988} >\\ time-domain spectroscopy\cite{Time2003}\cite{Dielectric2004}\cite{Microwave1994} >\\ Raman or other non-photothermal optical (\cite{optical1983} $\neq$ [\cite{Resonances1987} \cite{Dielectric1989}]) and also \footnote{see Taylor \cite{mechanisms1981} citing unpublished, personal communication} (but we have no understanding of how such artifacts could form) >\\ VNA CW absorption or reflection (\cite{Microwave1982} $\neq$ [\cite{Resonances1987} \cite{Dielectric1989}]) \cite{Substitution1982} \cite{Millimeter1980} \footnote{Anywhere we liked};
 
@@
 Most critically, the localized hotspots created by microwave exposure are often almost impossible to measure.
-Ideally, experimental design should guarantee that even slight temperature rise, more than about 3 C, cannot occur \cite{DNA2004}, or use thermally-matched shams.
+Ideally, experimental design should guarantee that even slight localized temperature rise, any more than about 3 C, cannot occur \cite{DNA2004}, or use thermally-matched shams.
 
@@
 
-If the effect exists, it appears to be impossible at any input power to externally drive a 10 GHz resonator in the lungs because of the layer of conductive muscle that shields the chest cavity.
+If the effect exists, it appears to be impossible at any input power to externally drive a 10 GHz resonator in the lungs because of the layer of conductive muscle that shields the chest cavity (see supplemental).
 There is precedent for bronchoscopic \cite{Flexible2019}\cite{Antenna2018} or more invasive methods.
 Dispersion and Brillouin precursors do offer a significant improvement in loss through tissue, and the required electrical waveforms appear to be synthesizeable by variable-impedance or stub transmission-line pulse shaping\cite{Arbitrarya} .
-A sawtooth might be the optimal waveform.
+A sawtooth might be the optimal waveform (see supplemental).
 However, obtaining 10 GHz tones deep in the body is still very hard.
 
-Although not sensitive to infectivity, as suggested by \cite{Quantification2020}, amplification-free fluorescence dsDNA detection using photon-counting plate readers using a 1:1 mix of viral solution with 1/4000 Biotium GelGreen is a very convenient (stable over long periods of time, requires no host culture) and sufficiently sensitive (titers down to $10^9$ of T4 (170 kbp dsDNA)) assay both for capsid damage and, by melting the capsid with an autoclave, for general virus titer estimation, far faster than even high-throughput plaque assays.
+Although not sensitive to infectivity, as suggested by \cite{Quantification2020}, amplification-free fluorescence dsDNA detection using photon-counting plate readers using a 1:1 mix of viral solution with 1/4000 Biotium GelGreen (a safe Acridine Orange (N-alkylacridinium) based flurophore) is a very convenient (stable over long periods of time, requires no host culture) and sufficiently sensitive (titers down to $10^8$ of T4 (170 kbp dsDNA)) assay both for capsid damage and, by melting the capsid with an autoclave, for general virus titer estimation, far faster than even high-throughput plaque assays.
 More useful enveloped viral surrogates like Pseudomonas phage Phi 6 are RNA and a lower sensitivity can be expected.
@@
 While their bandwidth is narrow, very cheap 0.5" laser line thin-film filters still work great for both excitation and emission for fluorescence techniques.
-Blue LEDs like are then sufficient for excitation (though high CRI white LEDs emit more blue, green leakage is too high).
+Blue LEDs [Cree XLamp XP-E2 Blue Starboard] are then sufficient for excitation (though high CRI white LEDs emit more blue, green leakage is too high).
 Dichroic mirrors are unnecessary.
-Use a plastic fiber optic at right angles to decrease excitation light scattering.
+Use a 1 mm plastic fiber optic at right angles to decrease excitation light scattering.
 Beware material autofluorescence - custom Lexan cuvettes unexpectedly overwhelmed the DNA signal.
-(final set: [ in series with Thorlabs FL05532, 532nm, 10 nm FWHM] [Edmund 28432, 486 nm])
+(final set: [emission: Tiffen Orange 16 gel in series with Thorlabs FL05532, 532nm, 10 nm FWHM] [Edmund 28432, 486 nm])
 
-In both of our final experimental setups, non-grounded, single-sided coplanar waveguides were used as exposure chambers.
-A programmable syringe pumped 50 uL of viral fluid through one of the coplanar channels.
+ImageJ
+
+In both of our final experimental setups, non-grounded, single-sided coplanar waveguides were used as exposure chambers, inspired by \cite{Microwave2007}.
+A programmable syringe pumped 50 uL of fluid at a constant rate through one of the coplanar channels.
 Simulations showed a significant decrease in field.
@@
 \footnote{the utility wcalc was used extensively}.
-
-Electrorotation of viruses has been reported\cite{Analysis2004}\cite{New1999}\cite{comprehensive2001}, but as yet only in a non-destructive low-speed sub-synchronous regime for sensing with optical.
-Dielectrophoresis and electrostatic trapping of viruses has also been reported.
-
-Data on the charge distribution of the virion can be obtained by and 2D-PAGE relative protein composition or perhaps directly via extraction from CryoEM maps.
 
@@
 Scan-converter based transient digitizers, such as the Tektronix SCD-5000 series, appear to be the lowest-cost method of obtaining such THz sampling bandwidths.
-When high voltage pulses are available, miniaturized \ntilde 2 mm internal diameter pumped scan converter tubes like Fecher micro-oscillographs using direct-electron-detection in-vacuum CMOS image sensors appear to be an easy way to digitize 20+ GHz transients.
+When high voltage pulses are available, miniaturized \ntilde 2 mm internal diameter continuously pumped scan converter tubes like Fecher micro-oscillographs using in-vacuum CMOS image sensors for direct-electron-detection appear to be an easy way to digitize 20+ GHz transients.
 The main bandwidth limitation appears to be the length of the Y deflection plate and the sensitivity of the recording medium.
+
+\begin{figure}[H]
+	%	\makebox[\textwidth][c]{
+	\centering
+	\subfloat[Direct electron beam detection]{
+		\includegraphics[width=0.3\textwidth]{direct_electron_beam}
+	}
+	\subfloat[Damage to the sensor, believed to be due to. ]{
+		\includegraphics[width=0.3\textwidth]{e_beam_damage_2}
+
+	}
+	\subfloat[]{
+		\includegraphics[width=0.3\textwidth]{e_beam_damage}
+
+	}
+
+	\caption{Second.}
+	\hfill
+
+\end{figure}
 

### 2021-02-18 documents/lessons_learned.tex
More progress on summary

@@
 
-Rather than focus effort on making marginal improvements to avoid errors in a certain technique, it may be better to find an experimental technique that is totally immune to these problems.
+This was written in 4 parts: first, rough lab notes were made, then this was cleaned up into a long thesis-like document, and then this was compressed into the final paper.
+However, in that final compression step, a lot of "texture" and pedagogy was lost.
+
+\rule{\linewidth}{0.2pt}
+
+Rather than focus effort on making marginal improvements to avoid errors in a certain technique, it may be better to put more effort to find a better experimental technique that is totally immune to these problems.
 Obviously this isn't always possible or practical.

### 2021-02-18 documents/summary.tex
More progress on summary

@@
 
-Whether the small difference in driven amplitude between, for example, a $Q\approx0.5$ host structure normal mode and a $	Q\lessapprox6$ virion mode could possibly be of any clinical value is unknown to us.
+However, whether the small difference in driven amplitude between, for example, a $Q\approx0.5$ host structure normal mode and a $Q\lessapprox6$ virion mode could possibly be of any clinical value is unknown to us.
 
@@
 In our cursory testing, Bacteriophage T4 did not appear to be lysed by microsecond pulses between 6 and 12 GHz at about 70 V/m, nor, exploring non-resonant inactivation, did nanosecond pulses up to 1 MV/m appear to have any effect.
-Note than neither of these regimes overlap with the results of the previous studies.
+Note that neither of these regimes overlap with the results of the previous studies.
 
@@
 
-Electrorotation\cite{Electrorotation1988}\cite{Electrorotation1997} of viruses has been reported\cite{Analysis2004}\cite{New1999}\cite{comprehensive2001}, but as yet only in a non-destructive low-speed sub-synchronous regime for sensing, using optical means to detect rotation rate.
+Electrorotation\cite{Electrorotation1988}\cite{Electrorotation1997} of viruses has been reported\cite{Analysis2004}\cite{New1999}\cite{comprehensive2001}, but as yet only in a non-destructive low-speed sub-synchronous regime for sensing, using optical means to detect rotation.
 Dielectrophoresis and electrostatic trapping of viruses has also been reported.
 
-Data on the charge distribution of the virion can be obtained by and 2D-PAGE relative protein composition or perhaps directly via extraction from CryoEM maps.
-
-Tsen
+Data on the charge distribution of the virion can be obtained by and 2D-PAGE relative protein composition or, interestingly, perhaps directly via extraction from CryoEM maps.
 
@@
 Most critically, the localized hotspots created by microwave exposure are often almost impossible to measure.
-Ideally, experimental design should guarantee that even slight localized temperature rise, any more than about 3 C, cannot occur \cite{DNA2004}, or use thermally-matched shams.
+Ideally, experimental design should guarantee that even slight localized temperature rise, any more than about 3 C, cannot occur \cite{Sharp1983}\cite{DNA2004}, or use thermally-matched shams\cite{Basic1983}.
+\cite{Effects1951}
 
 FDTD simulation of exposure geometry and sample heating is now usually possible with free, open-source software\footnote{PyTorch FDTD library from \cite{Highly2019} was used in our study with some modification, but \cite{CUDAbased2019} and \cite{openEMS} are also excellent} and should be performed.
-Metal ions from electrodes, UV exposure, and polymer surface effects must be ruled out by experimental design.
+As above, metal ions from electrodes, UV exposure, and polymer surface effects\cite{Effect1994a} must be ruled out by experimental design.
 The only artifact-free appear to be 1.
@@
 
-Coherent control targeting small proteins seems to require very large fields. Coherent control of large-scale structural modes using ; however these results have failed replication.
+ There is a body of work on coherent control of viral inactivation using picosecond laser exposure \cite{Maximum2010}; targeting small proteins seems to require very large fields\cite{Picosecond2016b}, but driving using Raman scattering \cite{Inactivation2007} \cite{Prospects2012}\cite{Studies2014} and molecular dynamics \cite{Maximum2010} (but without considering heat-bath damping).
+however these results have failed replication\cite{No2011}.
+Interestingly, if the well-established 1 TW power density\cite{Targeted2002} for mammalian cell laser damage is scaled linearly with time to the nanosecond regime ($1\ \text{TW/m}^2 / (100\ \text{ps} / 0.3\ \text{ps}) = 3\ \text{GW/m}^2$),
 
@@
 
-Although not sensitive to infectivity, as suggested by \cite{Quantification2020}, amplification-free fluorescence dsDNA detection using photon-counting plate readers using a 1:1 mix of viral solution with 1/4000 Biotium GelGreen (a safe Acridine Orange (N-alkylacridinium) based flurophore) is a very convenient (stable over long periods of time, requires no host culture) and sufficiently sensitive (titers down to $10^8$ of T4 (170 kbp dsDNA)) assay both for capsid damage and, by melting the capsid with an autoclave, for general virus titer estimation, far faster than even high-throughput plaque assays.
+Although not sensitive to changes in infectivity, as suggested by \cite{Quantification2020}, amplification-free fluorescence dsDNA detection using photon-counting plate readers using a 1:1 mix of viral solution with 1/4000 Biotium GelGreen (a safe Acridine Orange (N-alkylacridinium) based flurophore) is a very convenient (stable over long periods of time, requires no host culture) and sufficiently sensitive (titers down to $10^8$ of T4 (170 kbp dsDNA)) assay both for capsid damage and, by melting the capsid with an autoclave, for general virus titer estimation, far faster than even high-throughput plaque assays.
 More useful enveloped viral surrogates like Pseudomonas phage Phi 6 are RNA and a lower sensitivity can be expected.
@@
 
-ImageJ
+If CCD sensors with a, ImageJ \cite{Image2012} A silicon photomultiplier may be sufficient in some cases.
+
+However, these initial tests were marred by use of a domestic fridge to store phage, which unexpectedly froze regularly overnight, apparently reducing phage titer, along with our accidental use of T4r+, which is not an "improved" T4r, as we believed, but rather a mutation away from rapid-lysis, meaning that the lysis behavior is far slower (see \cite{Spontaneous1946}) and, in our testing, lysis of T4r+ only occurred on plaque assay plates (where culture growth and log stage infectivity is maintained for many days).
+
+Nephelometry (right-angle light scattering measurement) and turbidimetric (transmission) using CdS and LtoF sensors; despite being visible to the naked eye "clean" 2 hour E.
+coli cultures do not .
+Turbidimetry Impedimietric In addition, removing the necessitating
+$\beta$-galactosidase luciferase Promega Beta-Glo\cite{rapid2014}.
+While undoubtedly useful for quantifying $\beta$-galactosidase, because of ambiguities in the rise and decay of the luminescence signal, short shelf life when components are mixed, storage and reagent mixing requirements, and relatively high cost, Beta-Glo assaying compared unfavorably to direct fluorescence for this application, but this may have been user error.
+
+It is difficult to make spark gaps run faster than 200 ps without high-pressure or Marx overvoltage.
+Avalanche transistors appear to be the easiest way to produce high power sub 100 picosecond pulses.
+We stole an avalanche Marx design verbatim from Li (\cite{Development2016b} \cite{Design2018c}), which allows large pulses from safer lower voltage supplies (albeit requiring somewhat costly capacitors); but
 
@@
 Such cells should be used rather than our crude design.
-\footnote{the utility wcalc was used extensively}.
+\footnote{The utility wcalc was used extensively}.
 
-Avalanche transistors are sufficient and perhaps the easiest way to produce high power sub 100 ps pulses.
-We stole an avalanche Marx design verbatim from Li (\cite{Development2016b} \cite{Design2018c}), which allows large pulses from lower voltage supplies (albeit requiring somewhat costly capacitors); but  If a fast laser is available, Auston switches appear to be equally effective.
-It is difficult to make spark gaps run than 200 ps without the Marx overvoltage.
+If a fast laser is available, Auston switches appear to be equally effective.
 
-We are particularly excited by the prospect of using picosecond time-domain measurements not only to perform steady state dielectric measurements or monitor the input pulse, as is now common practice, but to resolve the internal effects of a single high-voltage pulse on the virus in real time - a technique which has not, to our knowledge, previously been demonstrated.
+We are particularly excited by the prospect of using picosecond time-domain measurements not only to perform steady state dielectric measurements or monitor the input pulse, as is now common practice, but to resolve the internal effects of a single high-voltage pulse on the virus in real time.
 Scan-converter based transient digitizers, such as the Tektronix SCD-5000 series, appear to be the lowest-cost method of obtaining such THz sampling bandwidths.

### 2021-02-19 documents/background.tex
readme

@@
 
-%3 MV/m * 10000 electronCharge * 0.1 angstrom / (boltzmannConstant * 310 K) = 11 kT per cycle
-%3 MV/m * 10000 electronCharge * 0.1 angstrom / (boltzmannConstant * 310 K) = 11 kT per cycle
 From an energetics perspective, we can obtain the spring constant $k = \omega_{res}^2 m^*$ from the resonant frequency and therefore from the speed of sound and $m^*$, the reduced mass.
@@
 
-Compare to ~5 $k_b T$ per protein for 1 capsid segment binding energy \cite{Energies2012} \cite{Weak2002} and $ (\text{17 to 78 kJ/mol})  / (310 \text{ K}\ k_b) = $ 6 to 30 $k_b T$ to form a single pore in a lipid bilayer \cite{Atomistic2014a}.
+Compare to ~5 $k_b T$ per protein for 1 capsid segment binding energy \cite{Energies2012} \cite{Weak2002} and 6 to 30 $k_b T$ to form a single pore in a lipid bilayer \cite{Atomistic2014a}.
 %17 or 78 kJ/mol / (boltzmannConstant * 310 K) / avogadroConstant = 6.5 to 30.3 kT
@@
 
-%(2*pi*(20 GHz))^2 * 100 MDa to N/m \approx 3000 N/m
-% 1 nanonewton / (3000 N/m) = 3e-13 m
+% google
+% ((5 megavolts/meter * 100 electron charge)^2 / ((2*pi*(30 GHz))^2 * 60 MDa)) / (boltzmann constant * 310 Kelvin) = 0.00042 kb
+% ((5 megavolts/meter * 10000 electron charge)^2 / ((2*pi*(5 GHz))^2 * 60 MDa)) / (boltzmann constant * 310 Kelvin) = 152.48 kb
+% ((40 megavolts/meter * 100 electron charge)^2 / ((2*pi*(15 GHz))^2 * 100 MDa)) / (boltzmann constant * 310 Kelvin)
 
-% (2*pi*(5 GHz))^2 * 60 MDa to N/m = 100 N/m
-% 0.1 angstroms
-
-% 1000 N/m = 0.01 Angstroms
-
-%
-%suggestive, especially because a model organism
 \clearpage

### 2021-02-19 documents/summary.tex
readme

@@
 
-These ideas appear to have originated from work by Frolich on the possibility of large-scale QM Bose-Einstein condensates, and then many more subtle lines of inquiry\cite{Mechanisms1992}\cite{mechanisms1981}; but, to our knowledge, no such large-scale non-classical effects have ever been substantiated; suggestions of non-classical damping due to hydration layer effects have not been observed.
+These ideas appear to have originated from work by Frolich\cite{Longrange1968}\cite{Evidence1983}\cite{Biological1980}\cite{Coherence1983} on the possibility of large-scale coherent QM Bose-Einstein condensates, and then many more subtle lines of inquiry\cite{Mechanisms1992}\cite{mechanisms1981}; but, to our knowledge, no such large-scale non-classical effects have ever been substantiated; suggestions of non-classical damping due to hydration layer effects have not been observed.
 In fact, consensus\cite{Exposure2009}\cite{ICNIRP2020}\cite{C95} appears to agree that, not only are oscillatory effects implausible, there are no relevant, substantiated, non-diffusion-like non-thermal mechanisms.
+
+The genome charge is almost entirely neutralized  From an energetics perspective, \footnote{we can obtain the spring constant $k = \omega_{res}^2 m^*$ from the resonant frequency and therefore from the speed of sound and $m^*$, the reduced mass.} With relatively sane choices of charge screening and resonant frequency, the energy absorbed per monocycle at 5 MV/m varies from 0.0001 to 200 times the thermal energy $k_b T$, so the maximum energy
+
+Compare to ~5 $k_b T$ per protein for 1 capsid segment binding energy \cite{Energies2012} \cite{Weak2002} and 6 to 30 $k_b T$ to form a single pore in a lipid bilayer \cite{Atomistic2014a}.
+%17 or 78 kJ/mol / (boltzmannConstant * 310 K) / avogadroConstant = 6.5 to 30.3 kT
+
+On the other hand, a 0.5 angstrom movement is only a 0.04\% deflection of the capsid, whereas a general value for host cells is about 3\% deflection.
+In addition, with a relaxation time on the order of 500 ps, it is difficult to imagine that the energy will be sufficiently concentrated to be destructive, as after the relaxation time the energy is a distant memory; only the mechanical effects that were induced during that time can remain.
+
+Data on the charge distribution of the virion can be obtained by and 2D-PAGE relative protein composition or, interestingly, perhaps directly via extraction from CryoEM maps.
+
+Modelling this sort of large-scale inactivation mechanism involving the collective motion of some $10^9$ atoms poses a significant computational and theoretical hassle, which has far exceeded our capabilities.
+Poisson-Boltzmann implicit ionized solvents.
+
+note clinical irrev electroporation
 
@@
 Dielectrophoresis and electrostatic trapping of viruses has also been reported.
-
-Data on the charge distribution of the virion can be obtained by and 2D-PAGE relative protein composition or, interestingly, perhaps directly via extraction from CryoEM maps.
 
@@
 
+Before the HMC732 was used, a misguided effort was spent in trying to develop an inexpensive wideband tunable oscillator.
+
 \end{document}

### 2021-02-20 documents/experiment_1_data.tex
whatever
test

@@
 
-\begin{center}
+\begin{table}[h!]
+	\centering
 	\begin{tabular}{ |c|c|c| } 
 		\hline
-		 & col2 & col3 \\
+		col1 & kilocounts per 10s integration \\
 		\hline
-		\multirow{3}{4em}{Multiple row} 
-		& cell2 & cell3 \\ 
-		& cell5 & cell6 \\ 
-		& cell8 & cell9 \\ 
+		Autoclaved (0.2 mL) & 32 \\ 
+		Autoclaved (50 uL, sham) & 30 \\ 
+		Autoclaved (0.2 mL) & 29 \\ 
+		PG1 'blank' & 8 \\ 
+		Dist. water & 0.5 \\
+		\hline
+		\multicolumn{2}{|c|}{\ntilde 0.25 MV/m, 0.2 uL/s at 500 Hz  } \\
+		\hline
+
+		& cell5  \\ 
+		& Negative  \\ 
 		\hline
 	\end{tabular}
-\end{center}
+
+\end{table}
+
+Data from testing on bacteriophage. Data rounded to the nearest thousand photon counts per 10 seconds. Not thoroughly characterized.
+
+Field strengths are very approximate.
+
+Background ('blank', in notes) readings measure the amount of DNA present in the phage culture tube before any treatment.
+
+Repeatability between test conditions was not excellent. The source of the ~7000 count variation between backgrounds is not known.
+
+The flurometer printed a constant stream of results, all within the random error between capture windows $\sigma=0.5$ kcounts. Only after most of the data was taken was it realized how dumb this was.
 

### 2021-02-20 documents/summary.tex
test

@@
 
-We have some minor questions regarding experimental technique\footnote{The use of absorption spectroscopy methods without an error analysis is concerning (see below); an effective charge of $q=10^7 e^-$ was found, which is very hard to explain; a lack of free-space dosimetry or simulation means frequency-selective inactivation could have been due to instrument response, infrared thermography only determines surface temperature.} in the original papers that can only be addressed by more extensive replication studies, and luckily are due to be answered by other groups\cite{Generating}, so we do not defer greatly to their observations.
+We have some minor questions regarding experimental technique in the original papers that can only be addressed by more extensive replication studies, and luckily are due to be answered by other groups\cite{Generating}, so we do not defer greatly to their observations.
 
@@
 
-The genome charge is almost entirely neutralized  From an energetics perspective, \footnote{we can obtain the spring constant $k = \omega_{res}^2 m^*$ from the resonant frequency and therefore from the speed of sound and $m^*$, the reduced mass.} With relatively sane choices of charge screening and resonant frequency, the energy absorbed per monocycle at 5 MV/m varies from 0.0001 to 200 times the thermal energy $k_b T$, so the maximum energy
+Because the effect is so remarkable, we have tried to come up with ways of explaining the observed results without invoking a non-thermal effect:
+\begin{itemize}
+	\item The use of microwave absorption spectroscopy techniques that have previously shown resonance-like artifacts\cite{Resonances1987}.
+An effective charge of $q=10^7 e^-$ was found, which is very large for a $10^9$ atom structure; genome and protein charge can hardly explain $10^5 e^-$, which would be reduced further by ionic screening.
+The potential energy of such a sphere of charge exceeds the metabolic burden to build a virus by a factor of 10.
+	\item Infrared thermography only determines the surface temperature.
+Based on heating patterns seen in other experiments\cite{Effects1950}, the observed 7 C temperature rise does not seem to conclusively rule out a thermal effect.
+	\item A lack of free-space dosimetry or simulation of power density means that the frequency-selective inactivation could have been due to the frequency response of the power amplifier, antenna gain, and absorption of the cuvette.
+\end{itemize}
 
-Compare to ~5 $k_b T$ per protein for 1 capsid segment binding energy \cite{Energies2012} \cite{Weak2002} and 6 to 30 $k_b T$ to form a single pore in a lipid bilayer \cite{Atomistic2014a}.
+A few well-established non-resonant non-thermal effects have already been put to practical use.
+Electroporation is a common laboratory procedure where an enormous electric field causes ions in solution to diffuse across a host cell's membrane, reversibly rendering it permeable (among other, more subtle mechanisms; the minutia of poration are extraordinarily complex and beyond the author's understanding\cite{Theoretical2007}).
+Irreversible electroporation\cite{Irreversible2013} has recently been used in the clinic\cite{Nonthermal2013} for tumor ablation.% In vitro there is evidence to suggest that sub-cellular effects take place under truly tremendous fields.
+
+The genome charge is almost entirely neutralized by the nucleocapsid.
+From an energetics perspective, \footnote{we can obtain the spring constant $k = \omega_{res}^2 m^*$ from the resonant frequency and therefore from the speed of sound and $m^*$, the reduced mass.} With relatively sane choices of charge screening and resonant frequency, the energy absorbed by the whole virus per cycle at 5 MV/m might vary from $10^{-5}$ to 100 times the thermal energy $k_b T$.
+
+Compare to $~5 k_b T$ per protein for 1 capsid segment binding energy \cite{Energies2012} \cite{Weak2002} and 6 to 30 $k_b T$ to form a single pore in a lipid bilayer \cite{Atomistic2014}.
 %17 or 78 kJ/mol / (boltzmannConstant * 310 K) / avogadroConstant = 6.5 to 30.3 kT
 
-On the other hand, a 0.5 angstrom movement is only a 0.04\% deflection of the capsid, whereas a general value for host cells is about 3\% deflection.
+On the other hand, such a sub-angstrom movement only produces approx.
+0.05\% deflection of the capsid, whereas a general value for host cells is about 3\% deflection.
 In addition, with a relaxation time on the order of 500 ps, it is difficult to imagine that the energy will be sufficiently concentrated to be destructive, as after the relaxation time the energy is a distant memory; only the mechanical effects that were induced during that time can remain.
@@
 Poisson-Boltzmann implicit ionized solvents.
-
-note clinical irrev electroporation
 
@@
 Excellent recent \textit{in vivo} data by de Seze following continuous exposure to nanosecond pulse trains at an external field up to 3 MV/m \cite{Repeated2020} notes little acute effects, but a massive rate of long-term carcinogenicity.
+Reviews \cite{Penetration2016c} \cite{Effects2016}.
 
@@
 Field limits are now set only by integrated pulse energy.
+
+There is a body of work on coherent control of viral inactivation using picosecond laser exposure \cite{Maximum2010}; targeting small proteins seems to require very large fields\cite{Picosecond2016b}, but driving using Raman scattering \cite{Inactivation2007} \cite{Prospects2012}\cite{Studies2014} and molecular dynamics \cite{Maximum2010} (but without considering heat-bath damping).
+however these results have failed replication\cite{No2011}.
+Interestingly, if the well-established 1 TW power density\cite{Targeted2002} for mammalian cell laser damage is scaled linearly with time to the nanosecond regime ($1\ \text{TW/m}^2 / (100\ \text{ps} / 0.3\ \text{ps}) = 3\ \text{GW/m}^2$),
 
@@
 Remote exposure, actively cooled OR pulsed exposure with sufficiently short pulses to rule out heating, with.
-
- There is a body of work on coherent control of viral inactivation using picosecond laser exposure \cite{Maximum2010}; targeting small proteins seems to require very large fields\cite{Picosecond2016b}, but driving using Raman scattering \cite{Inactivation2007} \cite{Prospects2012}\cite{Studies2014} and molecular dynamics \cite{Maximum2010} (but without considering heat-bath damping).
-however these results have failed replication\cite{No2011}.
-Interestingly, if the well-established 1 TW power density\cite{Targeted2002} for mammalian cell laser damage is scaled linearly with time to the nanosecond regime ($1\ \text{TW/m}^2 / (100\ \text{ps} / 0.3\ \text{ps}) = 3\ \text{GW/m}^2$),
 
@@
 
-It is difficult to make spark gaps run faster than 200 ps without high-pressure or Marx overvoltage.
-Avalanche transistors appear to be the easiest way to produce high power sub 100 picosecond pulses.
+We hoped to shape the nanosecond pulse into a high-voltage 10 GHz tone to drive the virus.
+This requires an edge faster than ~100 ps.
+It is difficult, but not impossible\cite{Fundamental1998} to make spark gaps produce such fast edges without high-pressure\cite{Design2007d}\cite{Picosecond1993} or building the gap into a Marx\cite{Simple1991} pulse-forming line.
+
+Avalanche transistors appear to be the easiest way to produce high power sub-100 picosecond pulses.
 We stole an avalanche Marx design verbatim from Li (\cite{Development2016b} \cite{Design2018c}), which allows large pulses from safer lower voltage supplies (albeit requiring somewhat costly capacitors); but
@@
 Scan-converter based transient digitizers, such as the Tektronix SCD-5000 series, appear to be the lowest-cost method of obtaining such THz sampling bandwidths.
-When high voltage pulses are available, miniaturized \ntilde 2 mm internal diameter continuously pumped scan converter tubes like Fecher micro-oscillographs using in-vacuum CMOS image sensors for direct-electron-detection appear to be an easy way to digitize 20+ GHz transients.
+
+%When high voltage pulses are available, miniaturized \ntilde 2 mm internal diameter continuously pumped scan converter tubes like Fecher\cite{Production1949} micro-oscillographs using in-vacuum CMOS image sensors for direct-electron-detection appear to be an easy way to digitize 20+ GHz transients.
 The main bandwidth limitation appears to be the length of the Y deflection plate and the sensitivity of the recording medium.

### 2021-02-20 documents/experiment_1_data.tex
edits

--- 2021-02-17 documents/experiment_1_data.tex
@@
 
-\begin{center}
+\begin{table}[h!]
+	\centering
 	\begin{tabular}{ |c|c|c| } 
 		\hline
-		 & col2 & col3 \\
+		Exposure & kilocounts per 10s integration & Note \# \\
 		\hline
-		\multirow{3}{4em}{Multiple row} 
-		& cell2 & cell3 \\ 
-		& cell5 & cell6 \\ 
-		& cell8 & cell9 \\ 
+		Autoclaved phage & 30 & \\ 
+		Autoclaved p. (50 uL) & 32 & Run 8\\ 
+		\hline
+		Phage culture 'blank' & 8 & \\ 
+		Dist. water & 0.5 \\
+		\hline
+		\multicolumn{3}{|c|}{\ntilde 10 or 20 us  } \\
+		\hline
+		 & \\ 
+		\hline
+		\multicolumn{3}{|c|}{\ntilde 10 or 20 us, pH 10.6} \\
+		\hline
+		\multicolumn{3}{|c|}{\ntilde 0.2 mm \ntilde 0.25 MV/m, 0.2 uL/s, various pulse counts  } \\
+		\hline 
+		 Blank & 8 & Li test 1\\
+		 + & 8 & Li test 1\\
+ 		 + & 7 & Li test 1\\
+ 		 + & 7 & Li test 1\\
+ 		 \hline
+		\multicolumn{3}{|c|}{\ntilde 0.05 mm \ntilde 1 MV/m, 0.2 uL/s, various pulse counts  } \\
+		\hline
+		Sham & 5 & Sma. co. \\
+		+ & 6 & Sma. co.  \\ 
+		+ & 6 & Sma. co.  \\ 
 		\hline
 	\end{tabular}
-\end{center}
+\end{table}
+
+Data from testing on bacteriophage. Data rounded to the nearest thousand photon counts per 10 seconds. thoroughly characterized.
+
+Field strengths are very approximate.
+
+Background ('blank', in notes) readings measure the amount of DNA present in the phage culture tube before any treatment.
+
+Repeatability between test conditions was not terrific.
+The source of the \ntilde 5000 count variation between some equivalent samples is not known.
+However, in no case did any tube approach the 22 to 30 kcounts of the autoclave.
+
+Stock culture had titer $3\times 10^9$ T4r.
+
+The fluor-meter printed a constant stream of results, all within the random error between capture windows $\sigma=0.5$ kcounts. Only after most of the data was taken was it realized how dumb this was.
+
+Results aggregated over the course of several months.
+
+In all cases, thermal artifact was completely di
+
+The firmware and data analysis scripts originally randomly generated blinded sham and autoclave assignments and automatically treated the samples accordingly.
+It also printed blinded templates for pipetting.
+This was done partly in the hopes that massively oversampling the microwave absorption spectrometer across the physical tolerances would highlight any resonances and changes in the resonances.
+
+However, as the spectrometer was abandoned, this non-deterministic property caused significant issues while troubleshooting the fluorescence detection system, and \st{expedience} \textit{laziness} prompted us to disable this system.
+This violates best practices.
+
+A layer of silicone conformal coating was applied to the 0.2 mm
 

### 2021-02-20 documents/summary.tex
edits

@@
 Turbidimetry Impedimietric In addition, removing the necessitating
-$\beta$-galactosidase luciferase Promega Beta-Glo\cite{rapid2014}.
-While undoubtedly useful for quantifying $\beta$-galactosidase, because of ambiguities in the rise and decay of the luminescence signal, short shelf life when components are mixed, storage and reagent mixing requirements, and relatively high cost, Beta-Glo assaying compared unfavorably to direct fluorescence for this application, but this may have been user error.
+E.
+coli produces the enzyme $\beta$-galactosidase to break lactose into glucose for metabolism.
+luciferase Promega Beta-Glo\cite{rapid2014}.
+However, the one part contains a proprietary detergent to lyse cells.
+
+While undoubtedly useful for quantifying $\beta$-galactosidase, because of ambiguities in the rise and decay of the luminescence signal, short shelf life when two components are mixed, storage and reagent mixing requirements, and relatively high cost, Beta-Glo compared unfavorably to direct fluorescence for this application.
 
@@
 		\includegraphics[width=0.3\textwidth]{e_beam_damage_2}
-
 	}
@@
 		\includegraphics[width=0.3\textwidth]{e_beam_damage}
-
 	}
-
 	\caption{Second.}
@@
 
+Thanks to Oughston and Sarris for information on dispersion;
+
 \end{document}

### 2021-02-22 documents/experiment_1.tex
More edits

@@
 \section{Experiment 1: Attempts at microwave absorption spectroscopy and inactivation in the microsecond pulsed 100 V/m regime}
-
-\cite{Osmotic2003} 30 atmospheres, and breaks at a pressure differential of 100 atm.
-T4 stress
-
-by $\sigma = pr / 2t $,
-t = 7 nm, r = 60 nm, and p =
 
@@
 By using yet another design, with a new set of unknown artifacts, we are actually hampering this field;
-and so we encourage anyone who may wish to replicate this result not to use this system.
+and so we encourage anyone who may wish to replicate this result not to use this system, but one of the better-characterized systems mentioned below.
 In this case, we are limited by budget - primarily the power amplifiers we have access to.

### 2021-02-22 documents/experiment_1_data.tex
More edits

--- 2021-02-17 documents/experiment_1_data.tex
@@
 
-\begin{center}
+\begin{table}[h!]
+	\centering
 	\begin{tabular}{ |c|c|c| } 
 		\hline
-		 & col2 & col3 \\
+		Exposure & kilocounts per 10s integration & Note \# \\
 		\hline
-		\multirow{3}{4em}{Multiple row} 
-		& cell2 & cell3 \\ 
-		& cell5 & cell6 \\ 
-		& cell8 & cell9 \\ 
+		Autoclaved phage (0.2 mL) & 30 & \\ 
+		Autoclaved p. (50 uL) & 32 & Run 8\\ 
+		\hline
+		Phage culture 'blank' & 8 & \\ 
+		Water & 1 & \\
+		\hline
+		\multicolumn{3}{|c|}{\ntilde 10 or 20 us  } \\
+		\hline
+		 & \\ 
+		\hline
+		\multicolumn{3}{|c|}{Sweep from 6 to 12 GHz, average approximately 150 V/m, 10 or 20 us CW pulses} \\
+		\hline
+		\multicolumn{3}{|c|}{\ntilde 0.05 mm, \ntilde } \\
+		\hline
+		\multicolumn{3}{|c|}{\ntilde 0.2 mm channel, 0.2 uL/s, various pulse counts and termination} \\
+		\hline 
+		 Blank    & 8 & Li test 1\\
+		 +           & 8 & Li test 1\\
+ 		 +           & 7 & Li test 1\\
+ 		 +           & 7 & Li test 1\\
+ 		 + \& shaper & 7 & Li test 1\\
+ 		 \hline
+		\multicolumn{3}{|c|}{\ntilde 0.05 mm channel, \ntilde 0.75 MV/m, 0.2 uL/s, various pulse counts and termination} \\
+		\hline
+		Sham & 5 & Smaller \\
+		+ & 6 & Smaller \\ 
+		+ & 6 & Smaller  \\ 
+		\hline
+		\multicolumn{3}{|c|}{\ntilde 0.05 mm channel, \ntilde 0.75 MV/m, 0.2 uL/s, basic buffer, but pH may not have been 10.6} \\
+		\hline
+		+ & 11 & Weakened \\
+		+ (no term) & 11 & Weakened \\ 
+		Sham & 12 & Weakened  \\ 
 		\hline
 	\end{tabular}
-\end{center}
+\end{table}
+
+Data from testing on bacteriophage. Data rounded (0.5 and above up) to the nearest thousand photon counts per 10 seconds. %thoroughly characterized.
+
+Background ('blank', in notes) readings measure the amount of DNA present in the phage culture tube before any treatment.
+
+Repeatability between test conditions was not terrific.
+The source of the \ntilde 5000 count variation between some equivalent samples is not known.
+However, in no case did any tube approach the 22 to 30 kcounts of the autoclave.
+
+Stock culture had titer $3\times 10^9$ T4r.
+
+The fluor-meter printed a constant stream of results, all within the random error between capture windows $\sigma=0.5$ kcounts. Only after most of the data was taken was it realized how dumb this was.
+
+Results aggregated over the course of several months.
+
+In all cases, a thermal effect was implausible; the total energy in the pulse train precluded heating above the capsid melting temperature.\cite{Effects1951}
+
+In an early iteration of the experiment, the firmware and data analysis scripts randomly generated blinded sham and autoclave assignments and automatically treated the samples accordingly.
+It also printed blinded templates for pipetting.
+This was done partly in the hopes that massively oversampling the microwave absorption spectrometer across the range of physical tolerances would highlight any resonances.\cite{first2000}
+
+However, as spectrometry was abandoned, this non-deterministic property caused significant issues while troubleshooting the fluorescence detection system, and \st{expedience} \st{\textit{laziness}} prompted us to disable this system, violating best practices.
+
+A thin layer of silicone conformal coating was applied to the 0.2 mm waveguide to avoid the copper ion artifact, but this could not be done on the 0.05 mm waveguide.
 

### 2021-02-22 documents/summary.tex
More edits

@@
 	\item The use of microwave absorption spectroscopy techniques that have previously shown resonance-like artifacts\cite{Resonances1987}.
-An effective charge of $q=10^7 e^-$ was found, which is very large for a $10^9$ atom structure; genome and protein charge can hardly explain $10^5 e^-$, which would be reduced further by ionic screening.
-The potential energy of such a sphere of charge exceeds the metabolic burden to build a virus by a factor of 10.
+An effective charge of $q=10^7 e^-$ was found, which is very large for a $10^9$ atom structure.
+Genome and protein charge can hardly explain $10^5 e^-$, which would be reduced further by ionic screening.
+The potential energy of such a sphere of charge would exceed the metabolic burden to build a virus by a factor of 10.
 	\item Infrared thermography only determines the surface temperature.
@@
 A few well-established non-resonant non-thermal effects have already been put to practical use.
-Electroporation is a common laboratory procedure where an enormous electric field causes ions in solution to diffuse across a host cell's membrane, reversibly rendering it permeable (among other, more subtle mechanisms; the minutia of poration are extraordinarily complex and beyond the author's understanding\cite{Theoretical2007}).
+Electroporation is a common laboratory procedure where an enormous electric field causes ions in solution to diffuse across a host cell's membrane, capacitively charging it, causing a change in lipid conformation, reversibly rendering it permeable (among other, more subtle mechanisms; the minutia of poration are extraordinarily complex and beyond the author's understanding\cite{Theoretical2007}).
 Irreversible electroporation\cite{Irreversible2013} has recently been used in the clinic\cite{Nonthermal2013} for tumor ablation.% In vitro there is evidence to suggest that sub-cellular effects take place under truly tremendous fields.
@@
 
-In our cursory testing, Bacteriophage T4 did not appear to be lysed by microsecond pulses between 6 and 12 GHz at about 70 V/m, nor, exploring non-resonant inactivation, did nanosecond pulses up to 1 MV/m appear to have any effect.
+Parametrizing based on all-atom simulations of small capsid segments or proteins \cite{Elucidating2009}.
+DNA with beads restrained by Lennard-Jones forces \cite{Communication2013}.
+Finite-element analysis \cite{Finite2008}; some Poisson-Boltzmann solvers
+
+GROMACS simulations of liposomes, trajectories fourier transformed with \cite{TRAVIS2011}
+
+In our cursory testing, Bacteriophage T4 did not appear to be lysed by 10 microsecond pulses between 6 and 12 GHz at about 70 V/m, nor, exploring non-resonant inactivation, did nanosecond pulses up to 1 MV/m appear to have any effect.
 Note that neither of these regimes overlap with the results of the previous studies.
@@
 
+\cite{MICROWAVEINDUCED1975}
+
 There is a body of work on coherent control of viral inactivation using picosecond laser exposure \cite{Maximum2010}; targeting small proteins seems to require very large fields\cite{Picosecond2016b}, but driving using Raman scattering \cite{Inactivation2007} \cite{Prospects2012}\cite{Studies2014} and molecular dynamics \cite{Maximum2010} (but without considering heat-bath damping).
@@
 
-Electrorotation\cite{Electrorotation1988}\cite{Electrorotation1997} of viruses has been reported\cite{Analysis2004}\cite{New1999}\cite{comprehensive2001}, but as yet only in a non-destructive low-speed sub-synchronous regime for sensing, using optical means to detect rotation.
+\cite{Forced2000} Electrorotation\cite{RotatingFieldInduced1982}\cite{Electrorotation1988}\cite{Electrorotation1997} of viruses has been reported\cite{Analysis2004}\cite{New1999}\cite{comprehensive2001}, but as yet only in a non-destructive low-speed sub-synchronous regime for sensing, using optical means to detect rotation.
 Dielectrophoresis and electrostatic trapping of viruses has also been reported.
+
+Rotational drag force can be found from MD simulation\cite{Evaluating2017}.
+A 30 nm lipid liposome using GROMACS' torque measurement feature, kindly implemented by Kutzner \cite{Keep2011}, yielded a , whereas rupture From \cite{Spinning2008}, the upper bound on the limiting angular frequency for a homegenous elastic sphere is at most $2.236 \ \bar \omega$, $$\bar \omega = \sqrt{3}\sqrt{\frac{Y}{\rho a^2}}$$ with radius a, mass density $\rho$, yield stress Y.
 
@@
 
-Background-free photothermal optical \cite{Microwave1993a}\cite{Broadband1988} >\\ time-domain spectroscopy\cite{Time2003}\cite{Dielectric2004}\cite{Microwave1994} >\\ Raman or other non-photothermal optical (\cite{optical1983} $\neq$ [\cite{Resonances1987} \cite{Dielectric1989}]) and also \footnote{see Taylor \cite{mechanisms1981} citing unpublished, personal communication} (but we have no understanding of how such artifacts could form) >\\ VNA CW absorption or reflection (\cite{Microwave1982} $\neq$ [\cite{Resonances1987} \cite{Dielectric1989}]) \cite{Substitution1982} \cite{Millimeter1980} \footnote{Anywhere we liked};
+Background-free photothermal optical \cite{Microwave1993a}\cite{Broadband1988} >\\ time-domain spectroscopy\cite{Time2003}\cite{Dielectric2004}\cite{Microwave1994} >\\ Raman or other non-photothermal optical (\cite{optical1983} $\neq$ [\cite{Resonances1987} \cite{Dielectric1989}]) and also \footnote{see Taylor \cite{mechanisms1981} citing unpublished, personal communication}, but we have no understanding of how such artifacts could form >\\ VNA CW absorption or reflection (\cite{Microwave1982} $\neq$ [\cite{Resonances1987} \cite{Dielectric1989}]) \cite{Substitution1982} \cite{Millimeter1980}.
+
+In our experiments with our (admittedly unstable) we were able to produce many candidate resonances with perfectly justifiable modifications to post-processing.
+\cite{Reanalysis2020}\cite{statistical2020}.
+which raises interesting questions regarding software quality in research.
+Synthetic data
 
@@
 
-FDTD simulation of exposure geometry and sample heating is now usually possible with free, open-source software\footnote{PyTorch FDTD library from \cite{Highly2019} was used in our study with some modification, but \cite{CUDAbased2019} and \cite{openEMS} are also excellent} and should be performed.
+FDTD simulation of exposure geometry and sample heating is now usually possible with free, open-source software and should be performed.
+PyTorch FDTD library from \cite{Highly2019} was used in our study with some modification, but \cite{CUDAbased2019} and \cite{openEMS} are also excellent.
 As above, metal ions from electrodes, UV exposure, and polymer surface effects\cite{Effect1994a} must be ruled out by experimental design.
@@
 
-If the effect exists, it appears to be impossible at any input power to externally drive a 10 GHz resonator in the lungs because of the layer of conductive muscle that shields the chest cavity (see supplemental).
+If the effect exists, it appears to be impossible at any input power to externally drive a 10 GHz resonator in the lungs, partly because of the layer of conductive muscle that shields the chest cavity (see supplemental).
+Open-ended waveguides\cite{142018} or water bolus allow efficient coupling to the body.
 There is precedent for bronchoscopic \cite{Flexible2019}\cite{Antenna2018} or more invasive methods.
@@
 
-Although not sensitive to changes in infectivity, as suggested by \cite{Quantification2020}, amplification-free fluorescence dsDNA detection using photon-counting plate readers using a 1:1 mix of viral solution with 1/4000 Biotium GelGreen (a safe Acridine Orange (N-alkylacridinium) based flurophore) is a very convenient (stable over long periods of time, requires no host culture) and sufficiently sensitive (titers down to $10^8$ of T4 (170 kbp dsDNA)) assay both for capsid damage and, by melting the capsid with an autoclave, for general virus titer estimation, far faster than even high-throughput plaque assays.
-More useful enveloped viral surrogates like Pseudomonas phage Phi 6 are RNA and a lower sensitivity can be expected.
+What quantity is referred to; induced dipole due to polarization or ionic.
+
+T4 was selected because of large amount of history. T4 does not have a nucleocapsid; the charge distribution is likely stronger than. 
+Phi6 \footnote{An interesting}
+
+30 atmospheres.
+When phage is rapidly immersed in solution of high osmotic strength, the active system that maintains osmotic equilibrium is overwhelmed, and the resulting force ruptures the capsid.
+\cite{Osmotic2003}, and breaks at a pressure differential of 100 atm.
+By $\sigma = pr / 2t $ t = 5.7 nm\cite{Head1988} and r=60 nm, capsid strength should be about 53 MPa, less than the 100 to 300 MPa cited by \cite{Bacteriophage2004}.
+%((100 atm * 60 nanometers) / (2*(5.7 nanometers))) to MPa
+
+The original Yang paper used plaque assays and RT-PCR to measure envelope damage; the quantification of viral titer is a solved problem.
+
+Although not sensitive to changes in infectivity, we used an amplification-free fluorescent dsDNA detection method, as suggested by \cite{Quantification2020}, using a custom photon-counting plate reader and a 1:1 mix of viral solution with 1/4000 Biotium GelGreen (a safe Acridine Orange (N-alkylacridinium) based flurophore).
+
+This was a very convenient (stable over long periods of time, requires no host culture) and sufficiently sensitive (titers down to $10^8$ of T4 (170 kbp dsDNA)) assay both for capsid damage and, by melting the capsid with an autoclave, for general virus titer estimation, far faster and less laborious than high-throughput plaque assays evaluated\cite{Simple2018}\cite{Streamlining2018}.
+More useful enveloped viral surrogates like Phi6 are RNA and a lower sensitivity can be expected.\cite{Selected}
 
@@
 
-If CCD sensors with a, ImageJ \cite{Image2012} A silicon photomultiplier may be sufficient in some cases.
+PMT dark counts and ambient light were removed by synchronous photon counting - add when light is on, subtract when light is off.
+This cannot be done with luminescence.
+Further filtering could be done by fluorescence lifetime discrimination.
 
-However, these initial tests were marred by use of a domestic fridge to store phage, which unexpectedly froze regularly overnight, apparently reducing phage titer, along with our accidental use of T4r+, which is not an "improved" T4r, as we believed, but rather a mutation away from rapid-lysis, meaning that the lysis behavior is far slower (see \cite{Spontaneous1946}) and, in our testing, lysis of T4r+ only occurred on plaque assay plates (where culture growth and log stage infectivity is maintained for many days).
+If CCD sensors with a, ImageJ \cite{Image2012}. A silicon photomultiplier will probably be sufficient in most cases.
 
-Nephelometry (right-angle light scattering measurement) and turbidimetric (transmission) using CdS and LtoF sensors; despite being visible to the naked eye "clean" 2 hour E.
-coli cultures do not .
+A number of other assays were evaluated.
+However, these initial tests were marred by use of a domestic fridge to store phage, which unexpectedly froze regularly overnight, apparently reducing phage titer, along with our accidental use of T4r+, which is not an "improved" T4r, as we believed, but rather a mutation away from rapid-lysis, meaning that the lysis behavior is far slower (see \cite{Spontaneous1946}).
+In our testing, lysis of T4r+ only occurred on plaque plates (where culture growth and log stage infectivity is maintained for many days).
+
+Nephelometry (right-angle light scatter detection) and turbidimetry (transmission) using CdS and LtoF sensors; despite being visible to the naked eye "clean" 2 hour E.
+coli cultures 1.5 mL.
 Turbidimetry Impedimietric In addition, removing the necessitating
@@
 luciferase Promega Beta-Glo\cite{rapid2014}.
-However, the one part contains a proprietary detergent to lyse cells.
+However, one component contains a proprietary detergent designed to lyse cells and expose the galactosidase, counterproductive for phage use.
+Perhaps the detergent is not effective on bacteria, or the paper substrate that was used is sufficient.
+The detergent could perhaps be removed with BioBeads if this is desired.
 
-While undoubtedly useful for quantifying $\beta$-galactosidase, because of ambiguities in the rise and decay of the luminescence signal, short shelf life when two components are mixed, storage and reagent mixing requirements, and relatively high cost, Beta-Glo compared unfavorably to direct fluorescence for this application.
+While undoubtedly essential and very effective for its intended purpose (quantifying lac operon activity), because of ambiguities in the rise and decay of the luminescence signal, short shelf life when the two components are mixed, concerns regarding the detergent, and cost, Beta-Glo compared unfavorably to direct fluorescence or X-Gal for this application.
 
@@
 
-In both of our final experimental setups, non-grounded, single-sided coplanar waveguides were used as exposure chambers, inspired by \cite{Microwave2007}.
+In both of our final experimental setups, non-grounded, single-sided coplanar waveguides were used as exposure chambers, inspired by the CPWG heater of \cite{Microwave2007}.
+\cite{Nanosecond2006} describe a very similar arrangement.
 A programmable syringe pumped 50 uL of fluid at a constant rate through one of the coplanar channels.
-Simulations showed a significant decrease in field.
+FDTD simulations showed a significant decrease in field.
 \cite{Microchamber2011} and \cite{Characterization2012} provide a good review of pulse exposure cells and a design which is much better than ours and should be used instead.
-Such cells should be used rather than our crude design.
-\footnote{The utility wcalc was used extensively}.
+\cite{Electromagnetic1989} \footnote{The utility wcalc was used extensively}.
 
@@
 We are particularly excited by the prospect of using picosecond time-domain measurements not only to perform steady state dielectric measurements or monitor the input pulse, as is now common practice, but to resolve the internal effects of a single high-voltage pulse on the virus in real time.
-Scan-converter based transient digitizers, such as the Tektronix SCD-5000 series, appear to be the lowest-cost method of obtaining such THz sampling bandwidths.
+Scan-converter based transient digitizers, such as the Tektronix SCD-5000 series, appear to be the lowest-cost method of obtaining the >0.5 THz sampling bandwidths required, when the tube bandwidth is deconvolved.
 

### 2021-02-26 documents/experiment_1_data.tex
Ruler

@@
 
+\subsection{Data from testing on bacteriophage T4}
 \begin{table}[h!]
@@
 		Water & 1 & \\
+
 		\hline
-		\multicolumn{3}{|c|}{\ntilde 10 or 20 us  } \\
+		\multicolumn{3}{|c|}{NF capillary, 6 to 12 GHz, average approximately 150 V/m, 10 or 20 us CW pulses} \\
 		\hline
-		 & \\ 
+		Sham   & 12 & Run 8 t4,5...\\
+		+ & 11 & Run 8 t4,5...\\
+		+  & 12 & Run 8 t4,5...\\
+		+  & 12 & Run 8 t4,5...\\
 		\hline
-		\multicolumn{3}{|c|}{Sweep from 6 to 12 GHz, average approximately 150 V/m, 10 or 20 us CW pulses} \\
+		\multicolumn{3}{|c|}{NF capillary, 6 to 12 GHz, phage degraded with basic buffer} \\
 		\hline
+		Blank (0 min) & 14 & Run 9\\
+		Blank (\ntilde 15 min) & 17 & Run 9\\
+		Sham (\ntilde 15 min) & 5 & Run 9\\
+		Blank (\ntilde 4 hr) & 24 & Run 9\\
+		\hline
+		+  & 14 & Run 11\\
+		Sham & 17 & Run 11\\
+		\hline
+		\multicolumn{3}{|c|}{NF capillary, 6 to 12 GHz, average approximately 150 V/m, 10 or 20 us CW pulses} \\
+		\hline
+		Sham & 12 & Run 12\\
+		+    & 10 & Run 12\\
+		\hline
+		\multicolumn{3}{|c|}{0.2 mm channel, 6 to 12 GHz, average approximately 150 V/m, 10 or 20 us CW pulses} \\
+		\hline
+		 Sham & 12 & CPWG micro-\\
+ 		 +    & 10 & CPWG micro-\\
+ 		\hline
+
 		\multicolumn{3}{|c|}{\ntilde 0.05 mm, \ntilde } \\
 		\hline
+
 		\multicolumn{3}{|c|}{\ntilde 0.2 mm channel, 0.2 uL/s, various pulse counts and termination} \\
@@
  		 \hline
-		\multicolumn{3}{|c|}{\ntilde 0.05 mm channel, \ntilde 0.75 MV/m, 0.2 uL/s, various pulse counts and termination} \\
+
+		\multicolumn{3}{|c|}{\ntilde 0.05 mm channel, 0.2 uL/s, various pulse counts and termination} \\
 		\hline
@@
 		\hline
-		\multicolumn{3}{|c|}{\ntilde 0.05 mm channel, \ntilde 0.75 MV/m, 0.2 uL/s, basic buffer, but pH may not have been 10.6} \\
+
+		\multicolumn{3}{|c|}{\ntilde 0.05 mm channel, 0.2 uL/s, basic buffer, tainted as pH may not have been 10.6} \\
 		\hline
+		Sham & 12 & Weakened \\ 
+		Blank & 11 & Weakened  \\ 
+		Blank & 12 & Weakened  \\ 
+		Blank & 9 & Weakened  \\ 
 		+ & 11 & Weakened \\
 		+ (no term) & 11 & Weakened \\ 
-		Sham & 12 & Weakened  \\ 
+		+ & 9 & Weakened \\ 
 		\hline
@@
 
-Data from testing on bacteriophage. Data rounded (0.5 and above up) to the nearest thousand photon counts per 10 seconds. %thoroughly characterized.
+As noted, this field reached a reasonable level of quality many decades ago, and many of the most troubling issues had already been encountered and addressed satisfactorily in experimental designs\cite{Biological1984}.
+In some cases, these are thoroughly characterized and described.
+UWB rat paper.
+But it seems to me that each worker (myself included!) is using their own test arrangement; and yet the studies are not so different as to require such customization.
+analysis anew to ascertain the very details of how the study was conducted, rather than simply its results.
 
-Background ('blank', in notes) readings measure the amount of DNA present in the phage culture tube before any treatment.
+By using yet another exposure cell, introducing an new set of unknown artifacts, we are actually hampering this field; and so we encourage anyone who may wish to replicate this result not to use this system, but one of the existing, well-characterized systems mentioned below or in the literature.
+
+For in-vitro research, it seems to me that perhaps this field is running into the issues Feynman's rat-races \cite{Cargo}. There are a large number of very tricky variables.
+
+ In this case, we were limited by budget - primarily the power amplifiers we have access to.
+
+It occurs to me that perhaps a set of exquisitely characterized standardized test cells and procedures would be helpful; and a requirement that any papers on the topic either use such a cell, or if their study requires some exceptional treatment, to follow an established procedure to add a new cell to the standard.
+
+ Data rounded to the nearest thousand photon counts per 10 seconds. %thoroughly characterized.
+
+Background ('blank', in notes) readings measure the amount of DNA present in the phage culture tube before any treatment. 'sham' indicates
 
 Repeatability between test conditions was not terrific.
-The source of the \ntilde 5000 count variation between some equivalent samples is not known.
-However, in no case did any tube approach the 22 to 30 kcounts of the autoclave.
+The source of the \ntilde 5000 count variation between some equivalent samples, and between "blank" and "sham", is not known.
+However, in no case did any sample\wikinote{verify} approach the 22 to 30 kcounts of the autoclave.
 
 Stock culture had titer $3\times 10^9$ T4r.
+
+The electrodes are only 1 oz copper thick (35 micrometers); but the engraved channel is significantly deeper.
+\cite{Nanosecond2006} and simulations seem to suggest that this is not a serious problem, but it is possible that the field in much of the channel was much lower than predicted.
 
@@
 
-In all cases, a thermal effect was implausible; the total energy in the pulse train precluded heating above the capsid melting temperature.\cite{Effects1951}
+In all cases, a thermal effect was made implausible; the total energy in the pulse train precluded heating above the capsid melting temperature\cite{Effects1951}.
+
+Only tubes 4 onwards are shown from Run 8 data because the capillary purging protocol was changed.
+In the final iteration, the autosampler was disconnected.
+The capillary was flushed with water; then the leuer lock was disconnected, air withdrawn into the syringe, and then purged through the capillary and fluidic channel.
 
@@
 
-However, as spectrometry was abandoned, this non-deterministic property caused significant issues while troubleshooting the fluorescence detection system, and \st{expedience} \st{\textit{laziness}} prompted us to disable this system, violating best practices.
+However, as spectrometry was abandoned, this non-deterministic property caused considerable issues while troubleshooting the fluorescence detection system, and \st{expedience} \footnote{laziness} prompted us to disable this system at run 9, defying best practices on blinded trials.
 
@@
 
+\clearpage
+
 \end{document}

### 2021-02-26 documents/lessons_learned.tex
Ruler

@@
 This was written in 4 parts: first, rough lab notes were made, then this was cleaned up into a long thesis-like document, and then this was compressed into the final paper.
-However, in that final compression step, a lot of "texture" and pedagogy was lost.
+However, in that final compression step, a lot of "texture" and pedagogy was lost on the first draft, when writing as terse as possible.
+
+Don't worry about repeating yourself; duplicating sections in different contexts is fine.
 

### 2021-02-26 documents/summary.tex
Ruler

@@
 
+\subfile{experiment_1_data}
+\begin{figure}[H]
+	%	\makebox[\textwidth][c]{
+	\includesvg[width=\textwidth]{propagated_waveforms}
+	\caption{Brillouin precursor propagation through tissue (reproduced from section 6).\\
+		(a) Gaussian monopulse with 16 ps FWHM.\\
+		(b) Optimized 10 GHz sawtooth wave. Note the slight high-frequency ripple.\\ This has a frequency of approximately 1.5 GHz.\\
+		(c) Prototypical precursor 10 GHz sine burst.\\
+		(d) Continuous 10 GHz sine tone.}
+
+\end{figure}
+\clearpage
 %
@@
 
-We were inspired to undertake this project by a set of publications by a certain Sun group, (primarily Liu et al \cite{Microwave2009} and Yang et al \cite{Efficient2015}, simultaneously demonstrated by Hung et al \cite{focusing2014}), and \cite{Optical2020} \cite{Theoretical2020}.
+\lettrine{W}e were inspired to undertake this project by a set of publications by a certain Sun group, (primarily Liu et al \cite{Microwave2009} and Yang et al \cite{Efficient2015}, simultaneously demonstrated by Hung et al \cite{focusing2014}), partially replicated by \cite{Optical2020} and discussed by \cite{Theoretical2020}.
 
@@
 
-These studies are all founded on the idea that there might be some large-scale structural difference between viruses and all host cellular structures that might usable as leverage to selectively inactivate the virus by some physical - rather than biological - means.
-Such an inactivation "window" between host cell and virion damage has been found in certain wavelengths of CW Far UV\cite{Germicidal2017} - but also apparently in certain modulated UV pulses\cite{Use1987a}\cite{Can1993}, and also sporadically reported for simple thermal treatment\cite{Summary}.
+These studies are all founded on the idea that some large-scale structural difference between viruses and all host cellular structures might usable as leverage to selectively inactivate the virus by some physical - rather than biological - means.
+For example, such an inactivation "window" between host cell and virion damage has been found in certain wavelengths of CW Far UV\cite{Germicidal2017} - but also apparently in certain modulated UV pulses\cite{Use1987a}\cite{Can1993}, and also sporadically reported for simple thermal treatment\cite{Summary}; however, the differential inactivation modes found so far do not appear to be of much use in the clinic.
 
-More specifically, the concept of driving a virus as a harmonic oscillator has been previously considered only briefly \cite{MECHANICAL1968}\cite{Comment2004}, perhaps first because in almost all cases structures in tissue are so over-damped by the surrounding solvent\cite{Vibrational2002}\cite{Biological2002}\cite{Biophysics2000}\cite{Viscous2000} as to have no non-zero resonant frequency at all \cite{dielectric1996}\cite{gabriel1996compilation}\wikinote{not in citation}\wikinote{discuss}; and second, because the charge distributions in biology are too small for energies significantly above the thermal background to be absorbed via applied fields.
+More specifically, the concept of driving a virus as a harmonic oscillator has been previously considered only briefly \cite{MECHANICAL1968}\cite{Comment2004}\cite{Vibrational2009}\cite{Maximum2010}, perhaps first because in almost all cases structures in tissue are so over-damped by the surrounding solvent\cite{Vibrational2002}\cite{Biological2002}\cite{Biophysics2000}\cite{Viscous2000} as to have no non-zero resonant frequency at all \cite{dielectric1996}\cite{gabriel1996compilation}\wikinote{not in citation}\wikinote{discuss}; and second, because the charge distributions found in biology are too small for energies significantly above the thermal background to be absorbed via applied fields.
 
@@
 
-However, whether the small difference in driven amplitude between, for example, a $Q\approx0.5$ host structure normal mode and a $Q\lessapprox6$ virion mode could possibly be of any clinical value is unknown to us.
+However, whether the small difference in driven amplitude between, for example, a $Q\approx0.5$ host structure normal mode and a $Q\lessapprox6$ virion mode could possibly be of any clinical value is not clear to us.
 
-These ideas appear to have originated from work by Frolich\cite{Longrange1968}\cite{Evidence1983}\cite{Biological1980}\cite{Coherence1983} on the possibility of large-scale coherent QM Bose-Einstein condensates, and then many more subtle lines of inquiry\cite{Mechanisms1992}\cite{mechanisms1981}; but, to our knowledge, no such large-scale non-classical effects have ever been substantiated; suggestions of non-classical damping due to hydration layer effects have not been observed.
+A few well-established non-resonant non-thermal effects have already been put to practical use.
+Electroporation\cite{Electroporation1988} is a common laboratory procedure where an enormous electric field causes ions in solution to diffuse across a host cell's membrane, capacitively charging it, causing a change in lipid conformation, reversibly rendering it permeable (among other, more subtle mechanisms; the minutia of poration are extraordinarily complex and beyond the author's understanding\cite{Theoretical2007}).
+
+Therapies based on irreversible electroporation\cite{Nonthermal2013}\cite{Lipid2017} have recently been used in the clinic\cite{Irreversible2013} for tumor ablation.
+There is much discussion on electroporation as an alternative to viral vectors, but we have not found any discussion of clinical treatment of viral infection with these conventional electroporation therapies.% In vitro there is evidence to suggest that sub-cellular effects take place under truly tremendous fields.
+
+The idea of driven oscillation in biological systems appears to have originated from work by Frohlich\cite{Longrange1968}\cite{Evidence1983}\cite{Biological1980}\cite{Coherence1983} on the possibility of large-scale coherent QM Bose-Einstein condensates, and then many more subtle lines of inquiry\cite{Mechanisms1992}\cite{mechanisms1981}; but, to our knowledge, no such large-scale non-classical effects have ever been substantiated; specifically, suggestions of non-classical damping due to hydration layer effects have not been observed.
 In fact, consensus\cite{Exposure2009}\cite{ICNIRP2020}\cite{C95} appears to agree that, not only are oscillatory effects implausible, there are no relevant, substantiated, non-diffusion-like non-thermal mechanisms.
 
-Because the effect is so remarkable, we have tried to come up with ways of explaining the observed results without invoking a non-thermal effect:
+Because the effect seen by Yang et al \cite{Efficient2015} is so remarkable, we have tried to come up with ways of explaining the observed results without invoking a non-thermal effect:
 \begin{itemize}
@@
 Genome and protein charge can hardly explain $10^5 e^-$, which would be reduced further by ionic screening.
-The potential energy of such a sphere of charge would exceed the metabolic burden to build a virus by a factor of 10.
+It appears that the  potential energy of such a sphere of charge would exceed the metabolic burden to build a virus by a significant factor\footnotetext.
 	\item Infrared thermography only determines the surface temperature.
-Based on heating patterns seen in other experiments\cite{Effects1950}, the observed 7 C temperature rise does not seem to conclusively rule out a thermal effect.
-	\item A lack of free-space dosimetry or simulation of power density means that the frequency-selective inactivation could have been due to the frequency response of the power amplifier, antenna gain, and absorption of the cuvette.
+Based on heating patterns seen in other experiments\cite{Effects1950}, the observed surface temperature rise does not seem to conclusively rule out a very localized thermal effect.
+	\item Therefore, without free-space dosimetry or simulation of power density to demonstrate otherwise, the frequency-selective inactivation could be explained by the frequency response of the power amplifier, antenna gain, and absorption of the cuvette.
 \end{itemize}
 
-A few well-established non-resonant non-thermal effects have already been put to practical use.
-Electroporation is a common laboratory procedure where an enormous electric field causes ions in solution to diffuse across a host cell's membrane, capacitively charging it, causing a change in lipid conformation, reversibly rendering it permeable (among other, more subtle mechanisms; the minutia of poration are extraordinarily complex and beyond the author's understanding\cite{Theoretical2007}).
-Irreversible electroporation\cite{Irreversible2013} has recently been used in the clinic\cite{Nonthermal2013} for tumor ablation.% In vitro there is evidence to suggest that sub-cellular effects take place under truly tremendous fields.
+It seems reasonable that a field with a strong positive publication bias\cite{Comprehensive2018}, in the presence of strong peer review, might tend towards only the most abstruse and difficult to explain false-positive results.
+
+However, if this is a thermal artifact, the fact that the spectrometry and inactivation data shown align perfectly is very difficult to explain. We are forced to be satisfied with mystification.
+
+\footnotetext{
+$$ U = \frac{3}{5}  \frac{1}{4 \pi \epsilon_0} \frac{Q^2}{R} \approx 2.3\text{e}^{-7} \text{ J} \approx 6 \times 10^{11}\  \text{ATP-equivalent} $$
+%U = (3/5) * 1/(4*pi*electricConstant) *((1e7 electricCharge)^2 / 60 nanometers) = 2.30708e-7 J
+
+%50 kJ per mole, 6.022*10^23 = 9.9634673e-13 * 50 kj = 5e-8 J
+
+Mahmoudabadi\cite{Energetic2017} provide a total per-virion energetic cost of $10^8 $ ATP-equivalent , so this appears to be 3 orders of magnitude too large.
+
+Of course, much of the potential energy may have already existed in the host cell, so this is probably an invalid comparison.
+And if most of the charge is contributed by osmotic, ion, this potential energy may not be considered in the above.
+Autem: is it possible for the charged core to compensate for the potential energy of the charged shell?}
 
 The genome charge is almost entirely neutralized by the nucleocapsid.
-From an energetics perspective, \footnote{we can obtain the spring constant $k = \omega_{res}^2 m^*$ from the resonant frequency and therefore from the speed of sound and $m^*$, the reduced mass.} With relatively sane choices of charge screening and resonant frequency, the energy absorbed by the whole virus per cycle at 5 MV/m might vary from $10^{-5}$ to 100 times the thermal energy $k_b T$.
+
+From an energetics perspective, \footnote{The dipole spring constant can be extracted from the resonant frequency and therefore from the speed of sound and $m^*$, the reduced mass ($k = \omega_{res}^2 m^2$).
+} With relatively sane choices of charge screening and resonant frequency, the energy absorbed by the whole virus per cycle at 5 MV/m might vary from $10^{-5}$ to 100 times the thermal energy $k_b T$.
+%TODO check effect of damping on hookes law energy.
 
@@
 On the other hand, such a sub-angstrom movement only produces approx.
-0.05\% deflection of the capsid, whereas a general value for host cells is about 3\% deflection.
-In addition, with a relaxation time on the order of 500 ps, it is difficult to imagine that the energy will be sufficiently concentrated to be destructive, as after the relaxation time the energy is a distant memory; only the mechanical effects that were induced during that time can remain.
+0.05\% deflection of the capsid, whereas a general value for the rupture of host cells is about 3\% deflection.
+The stiffness of the genome may explain this.
+In addition, with a relaxation time on the order of 500 ps, it is difficult to imagine that the energy will be sufficiently concentrated in the capsid to be destructive.
+After the relaxation time, the energy is a distant memory; only the mechanical effects that were induced during that time can remain.
 
-Data on the charge distribution of the virion can be obtained by and 2D-PAGE relative protein composition or, interestingly, perhaps directly via extraction from CryoEM maps.
+Data on the charge distribution of the virion can be obtained by and 2D-PAGE relative protein composition or perhaps directly via extraction from whole-virion CryoEM maps because of the charge-sensitive nature of electrons over X-ray diffraction \cite{Identification2018}\cite{Electrostatic2020}; but this has not yet been implemented.
 
@@
 Excellent recent \textit{in vivo} data by de Seze following continuous exposure to nanosecond pulse trains at an external field up to 3 MV/m \cite{Repeated2020} notes little acute effects, but a massive rate of long-term carcinogenicity.
-Reviews \cite{Penetration2016c} \cite{Effects2016}.
 
-In almost all recently updated standards, the precautionary 100 kV/m instantaneous field limits established by ANSI have been abolished due to a lack of evidence of harm; an excellent review in this regime is \footnote{\cite{treatyelectromagnetic}, as cited by \textit{C95.1-2019, B.4.3 Rationale for pulsed RF field limits}}.
-Field limits are now set only by integrated pulse energy.
+In-vitro, there appears to be a consistent set of effects of nanosecond pulses, or nsPEF, distinct from membrane effects, that occur on small intracellular organelles (see reviews \cite{Penetration2016c} \cite{Effects2016} ), \cite{Bioeffects},
 
-\cite{MICROWAVEINDUCED1975}
+In almost all recently updated standards, the precautionary 100 kV/m instantaneous field limits established by ANSI have been abolished due to a lack of evidence of harm; an excellent review in this regime is \footnote{\cite{treatyelectromagnetic}, as cited by \textit{C95.1-2019, B.4.3 Rationale for pulsed RF field limits}.\footnote{That same review also contains the following, which highlights the incredible difficulty of obtaining reliable results in this field: "Dr.
+de Seze also described an experiment in which two sham groups were mistakenly run and a significant difference was found.
+Dr.
+Klauenberg noted another series of experiments he reviewed where experimental treatment groups did not vary while the sham groups compared to each other did resulting in a significant difference that was otherwise meaningless."}}.
+Field limits are now generally set only by integrated pulse energy.
 
-There is a body of work on coherent control of viral inactivation using picosecond laser exposure \cite{Maximum2010}; targeting small proteins seems to require very large fields\cite{Picosecond2016b}, but driving using Raman scattering \cite{Inactivation2007} \cite{Prospects2012}\cite{Studies2014} and molecular dynamics \cite{Maximum2010} (but without considering heat-bath damping).
-however these results have failed replication\cite{No2011}.
+Previous field limits were set by the microwave hearing effect, a primarily thermoelastic mechanical \cite{MICROWAVEINDUCED1975}.
+Thermoelastic effects can cause damage, but primarily when \cite{Thermoacoustic2017}\cite{MECHANICAL1968}.
+\cite{Radiation1996}
+
+There is a body of work on coherent control of viral inactivation using picosecond laser exposure \cite{Maximum2010}; targeting small proteins seems to require very large fields\cite{Picosecond2016b}, but breaking viral capsids by exciting long-wavelength vibrations using Raman scattering has been reported experimentally \cite{Inactivation2007}\cite{Prospects2012}\cite{Studies2014}, however these results have failed replication\cite{No2011}.
+The author has not investigated this mechanism in any detail.
+Molecular dynamics of ISRU has been considered \cite{Maximum2010}, (\cite{Vibrational2009} but without considering heat-bath damping).
 Interestingly, if the well-established 1 TW power density\cite{Targeted2002} for mammalian cell laser damage is scaled linearly with time to the nanosecond regime ($1\ \text{TW/m}^2 / (100\ \text{ps} / 0.3\ \text{ps}) = 3\ \text{GW/m}^2$),
 
-\cite{Forced2000} Electrorotation\cite{RotatingFieldInduced1982}\cite{Electrorotation1988}\cite{Electrorotation1997} of viruses has been reported\cite{Analysis2004}\cite{New1999}\cite{comprehensive2001}, but as yet only in a non-destructive low-speed sub-synchronous regime for sensing, using optical means to detect rotation.
-Dielectrophoresis and electrostatic trapping of viruses has also been reported.
+Optical centrifuges use a rotating polarization to induce a dipole moment and spin up small molecules \cite{Forced2000}\cite{Spinning2000}.
+Electrorotation\cite{RotatingFieldInduced1982}\cite{Electrorotation1988}\cite{Electrorotation1997}\cite{Dielectric1988} of viruses has been reported\cite{Analysis2004}\cite{New1999}\cite{comprehensive2001}, but as yet only in a non-destructive low-speed sub-synchronous regime for sensing, using optical means to detect rotation - using the virion as a kind of electrostatic induction motor.
+High-frequency dielectrophoresis and electrostatic trapping of viruses has also been reported\cite{Accumulation2006}, without suggestions of electrostatic damage, implying that conventional irreversible electroporation of viruses should require longer than 10 microseconds.
 
-Rotational drag force can be found from MD simulation\cite{Evaluating2017}.
-A 30 nm lipid liposome using GROMACS' torque measurement feature, kindly implemented by Kutzner \cite{Keep2011}, yielded a , whereas rupture From \cite{Spinning2008}, the upper bound on the limiting angular frequency for a homegenous elastic sphere is at most $2.236 \ \bar \omega$, $$\bar \omega = \sqrt{3}\sqrt{\frac{Y}{\rho a^2}}$$ with radius a, mass density $\rho$, yield stress Y.
+A rotational drag coefficient can extracted from MD simulation\cite{Evaluating2017}.
+Simulating a 30 nm lipid liposome using the MARTINI coarse-grained \cite{MARTINI2007} lipid force fields with GROMACS\cite{GROMACS2005}' torque measurement feature, kindly implemented by Kutzner \cite{Keep2011}.
+This suggests a maximum rotation frequency $10^7$ on the order of $10^3$, but this value requires so many assumptions that it's hardly worth mentioning.
+From \cite{Spinning2008}, the upper bound of a homogenous spherical virus with 10 MPa overall tensile strength appears to be about $10^9$ Hz.
+\footnote{\ghfile{documents/optical_centrifuge.ipynb}}
 
-Liburdy
+which are similar in size to the viral membrane \cite{MicrowaveStimulated1985}\cite{Influence}\cite{Correlation1994}\cite{contribution2019}.
+These results are of excellent quality, with good thermal controls.
+\footnote{One founding researcher has been implicated in a scandal; however, the Livermore report on the topic does not appear to be public, so we cannot evaluate the basis for these claims.} This effect appears to depend on dissolved oxygen, seemingly evidence against a mechanical effect.
+lipid "transition temperature" - the point at which pores reseal.
+\cite{Effect1994a}.
 
-Almost all biological spectroscopy techniques have produced resonance-like artifacts at some point in the literature, and even the most striking and competently-obtained absorption data should not necessarily be trusted implicitly.
+Custom single-lipid liposome surrogates appear to be relatively easy to produce and fill with a DNA tracer by sonication and dehydration\cite{Encapsulation1982}\cite{OPTIMIZATION2017}.
+The only problem expected was removing unencapsulated DNA, which typically requires ultracentrifugiation as precipitation is not as easy as with phage.
+However, \cite{novela} appear to demonstrate that ethanol is satisfactory, and likely does not lead to DNA precipitation because of the lack of salt.
+\cite{Liposome2014}
+
+Almost all biological spectroscopy techniques have produced resonance-like artifacts at some point in the literature, and we suggest that even the most striking and competently-obtained absorption data should not necessarily be trusted implicitly.
 Trustworthiness probably depends most significantly on the quality of error analysis; many have made good use of otherwise unreliable techniques.
-In order of highest to lowest apparent reliability for resonance measurement:
+However, particularly in a field with a high positive publication bias, it seems most productive to use the most advanced techniques, those that are foolproof by their very nature.
+Based only on our experience of the literature, in order of decreasing reliability for resonance measurement:
 
-Background-free photothermal optical \cite{Microwave1993a}\cite{Broadband1988} >\\ time-domain spectroscopy\cite{Time2003}\cite{Dielectric2004}\cite{Microwave1994} >\\ Raman or other non-photothermal optical (\cite{optical1983} $\neq$ [\cite{Resonances1987} \cite{Dielectric1989}]) and also \footnote{see Taylor \cite{mechanisms1981} citing unpublished, personal communication}, but we have no understanding of how such artifacts could form >\\ VNA CW absorption or reflection (\cite{Microwave1982} $\neq$ [\cite{Resonances1987} \cite{Dielectric1989}]) \cite{Substitution1982} \cite{Millimeter1980}.
+\begin{itemize}
+\item Background-free photothermal optical \cite{Microwave1993a}\cite{Broadband1988}
+\item Time-domain spectroscopy (many advantages cited by \cite{Time2003}, including instant, drift-free capture of all frequencies and limited instrumentation artifacts), \cite{Dielectric2004}\cite{Microwave1994}
+\item Raman or other non-photothermal optical (\cite{optical1983} $\neq$ [\cite{Resonances1987} \cite{Dielectric1989}]) and also \footnote{see Taylor \cite{mechanisms1981} citing unpublished, personal communication}, but we have no understanding of how such artifacts could form
+\item Frequency-domain CW VNA absorption or reflection (\cite{Microwave1982} $\neq$ [\cite{Resonances1987} \cite{Dielectric1989}]) \cite{Substitution1982} \cite{Millimeter1980}.
+\end{itemize}
 
-In our experiments with our (admittedly unstable) we were able to produce many candidate resonances with perfectly justifiable modifications to post-processing.
-\cite{Reanalysis2020}\cite{statistical2020}.
-which raises interesting questions regarding software quality in research.
-Synthetic data
+In our experiments with our (admittedly very unstable) spectrometer, we were able to produce many candidate resonances with perfectly justifiable modifications to post-processing, which raises interesting (but not novel) questions regarding software quality in research.
+Unit testing
+
+Synthetic data \cite{Reanalysis2020}\cite{statistical2020}.
 
@@
 Thermal effects appear to be most common.
+For instance, Manikowska\cite{Effects1985a} showed a "highly significant (P > 0.001)" result, and state that "...under our experimental conditions, effects of heat stress and local heating are unlikely".
+This result was promptly refuted by \cite{Cytogenetic1986}, who suggest a thermal artifact.
 Most critically, the localized hotspots created by microwave exposure are often almost impossible to measure.
-Ideally, experimental design should guarantee that even slight localized temperature rise, any more than about 3 C, cannot occur \cite{Sharp1983}\cite{DNA2004}, or use thermally-matched shams\cite{Basic1983}.
-\cite{Effects1951}
+Ideally, experimental design should guarantee that even slight localized temperature rise above 3 C cannot occur \cite{Sharp1983}\cite{Effects1951}\cite{DNA2004}, or use thermally-matched shams\cite{Basic1983}.
 
 FDTD simulation of exposure geometry and sample heating is now usually possible with free, open-source software and should be performed.
-PyTorch FDTD library from \cite{Highly2019} was used in our study with some modification, but \cite{CUDAbased2019} and \cite{openEMS} are also excellent.
-As above, metal ions from electrodes, UV exposure, and polymer surface effects\cite{Effect1994a} must be ruled out by experimental design.
-The only artifact-free appear to be 1.
-Remote exposure, actively cooled OR pulsed exposure with sufficiently short pulses to rule out heating, with.
+A PyTorch-based FDTD library from \cite{Highly2019} was used in our study with some modification, but \cite{CUDAbased2019} and \cite{openEMS} are also excellent.
 
-If the effect exists, it appears to be impossible at any input power to externally drive a 10 GHz resonator in the lungs, partly because of the layer of conductive muscle that shields the chest cavity (see supplemental).
-Open-ended waveguides\cite{142018} or water bolus allow efficient coupling to the body.
-There is precedent for bronchoscopic \cite{Flexible2019}\cite{Antenna2018} or more invasive methods.
-Dispersion and Brillouin precursors do offer a significant improvement in loss through tissue, and the required electrical waveforms appear to be synthesizeable by variable-impedance or stub transmission-line pulse shaping\cite{Arbitrarya} .
+Next appear to be electrochemical\cite{Comparative2003} effects; as noted above, metal ions from electrodes can wreak havoc.
+Even more obscure differences between positive and sham, such as very strange polymer surface effects observed by\cite{Effect1994a}, must be ruled out by experimental design.
+
+If the effect exists, efficient use of the lower damping would seem to require more than one cycle of oscillation.
+It appears to be impossible at any input power to effectively drive a 10 GHz resonator in the lungs from outside the torso, partly because of the layer of conductive muscle that shields the chest cavity (see supplemental).
+Open-ended waveguides\cite{OpenEnded1982}\cite{Analysis1989}\cite{142018} or water bolus allow efficient coupling to the body.
+There is precedent for bronchoscopic \cite{Flexible2019}\cite{Antenna2018} or more invasive methods\cite{Implantable1980}\cite{Implantable1982}\cite{Electromagnetic1983}.
+
+Dispersion and Brillouin precursors do offer a significant improvement in loss through tissue, and the required electrical waveforms appear to be synthesizeable by variable-impedance or stub transmission-line pulse shaping\cite{Coaxial1985}\cite{Arbitrarya}.
+
 A sawtooth might be the optimal waveform (see supplemental).
-However, obtaining 10 GHz tones deep in the body is still very hard.
+However, obtaining 10 GHz tones deep in the body is still very hard, and may require very complicated dispersive phased arrays\cite{Microwave1982a}.
+
+Early albanese with mm used vircator diodes.
 
@@
 
-T4 was selected because of large amount of history. T4 does not have a nucleocapsid; the charge distribution is likely stronger than. 
-Phi6 \footnote{An interesting}
+T4 was selected because of large amount of history and safety of the host.
+T4 does not have a nucleocapsid; the charge distribution is likely stronger than.
+Phi6 \footnote{An interesting}.
+Some other surrogates may include PMD1,
 
@@
 
-The original Yang paper used plaque assays and RT-PCR to measure envelope damage; the quantification of viral titer is a solved problem.
+The original Yang paper used plaque assays and RT-PCR to measure envelope damage; the quantification of viral titer is a solved problem. Not having equipment or experience
 
@@
 
-This was a very convenient (stable over long periods of time, requires no host culture) and sufficiently sensitive (titers down to $10^8$ of T4 (170 kbp dsDNA)) assay both for capsid damage and, by melting the capsid with an autoclave, for general virus titer estimation, far faster and less laborious than high-throughput plaque assays evaluated\cite{Simple2018}\cite{Streamlining2018}.
+This was a very convenient (stable over long periods of time, requires no host culture) and sufficiently sensitive (titers down to $10^8$ of T4 (170 kbp dsDNA)) assay both for capsid damage and, by melting the capsid with an autoclave, for general virus titer estimation, far faster and less laborious\footnote{"Fast turnaround time has always been important to me.
+Mistakes are unavoidable, so I always wanted an apparatus that would allow mistakes to be corrected as rapidly as possible." \cite{manipulation1998}} than high-throughput plaque assays evaluated\cite{Simple2018}\cite{Streamlining2018}.
 More useful enveloped viral surrogates like Phi6 are RNA and a lower sensitivity can be expected.\cite{Selected}
@@
 While their bandwidth is narrow, very cheap 0.5" laser line thin-film filters still work great for both excitation and emission for fluorescence techniques.
-Blue LEDs [Cree XLamp XP-E2 Blue Starboard] are then sufficient for excitation (though high CRI white LEDs emit more blue, green leakage is too high).
-Dichroic mirrors are unnecessary.
+Blue LEDs [Cree XLamp XP-E2 Blue Starboard] are then sufficient for excitation (though high CRI white LEDs emit more 480 nm blue, green leakage is too high).
+Dichroic mirrors are unnecessary for this application.
 Use a 1 mm plastic fiber optic at right angles to decrease excitation light scattering.
@@
 coli cultures 1.5 mL.
-Turbidimetry Impedimietric In addition, removing the necessitating
+Turbidimetry\cite{Fast2019} Impedimietric In addition, removing the necessitating
+
 E.
@@
 This requires an edge faster than ~100 ps.
-It is difficult, but not impossible\cite{Fundamental1998} to make spark gaps produce such fast edges without high-pressure\cite{Design2007d}\cite{Picosecond1993} or building the gap into a Marx\cite{Simple1991} pulse-forming line.
+It appears to be difficult, but not impossible\cite{Fundamental1998}to make spark gaps produce such fast edges without high-pressure\cite{kHz1995} \cite{Design2007d}\cite{Picosecond1993} or building the gap into a Marx\cite{Simple1991} pulse-forming line.
 
 Avalanche transistors appear to be the easiest way to produce high power sub-100 picosecond pulses.
-We stole an avalanche Marx design verbatim from Li (\cite{Development2016b} \cite{Design2018c}), which allows large pulses from safer lower voltage supplies (albeit requiring somewhat costly capacitors); but
+We stole an avalanche Marx design verbatim from Li (\cite{Development2016b} \cite{Design2018c}), which allows large pulses from safer lower voltage supplies (albeit requiring somewhat costly capacitors).
 
@@
 \cite{Nanosecond2006} describe a very similar arrangement.
-A programmable syringe pumped 50 uL of fluid at a constant rate through one of the coplanar channels.
+
+A programmable syringe withdrew and pumped 50 uL of fluid at a constant rate through one of the coplanar channels, via a 4 cm long silicone capillary (McMaster-Carr \#51845K65) immersed in a 1.5 mL centrifuge tube using a 26 Ga Luer-lock (\#6710A76).
+Forcing phage through the capillary is similar to lysis with a French pressure cell press, but no such effects were seen.
+
  FDTD simulations showed a significant decrease in field.
@@
 
-Thanks to Oughston and Sarris for information on dispersion;
+Funded in part by the author's company, SafeSump Inc., and Ideal Consulting Inc., and the author's parents.
+
+Special thanks to my parents, Doris and Brian, without whom this work would have been accomplished by someone else, and whose extraordinary support made this paper possible.
+
+Thanks to a group with Chengxiang Li for the Marx generator design we use in this paper.
+It is an excellent, very high performance design!
+Professor Shahramian's video blog informed this work, as did Dr.
+Dainis' on microbiology.
+Thanks to legend of dispersion himself, Professor Oughstun at Vermont, Prof.
+Sarris at U of Toronto, both for excellent information on optimal dispersive pulses; Professor Voinigescu at UofT for a tip on experiment engineering; Sandra and colleagues at York library for spending an hour looking for the Gray paper; Prof.
+Griffiths and Dr.
+Brovko at UGuelph and Dr.
+Anany at the GRDC for useful tips on the Beta-Glo assay; Professor Z-G Wang at Caltech for a note on viral electrostatics; Dr.
+James Hawthorne for the Autoleveller utility; Yuriy at Indiana; Barfuss for reviewing an early draft; Greenland Engineering for patience; and lots of friends - a few at York and many beyond.
+
+This paper would have been absolutely impossible without the support of thousands of open-source software packages, ranging from monolithic state-supported tools like Paraview to poorly-compensated but equally invaluable scripts like zonca.
+A special thanks to the dedicated authors that develop and maintain these tools, and especially to those who choose not to put them behind a paywall.
+
+ Hamming be damned; despite the name below the abstract, this paper is of course entirely the result of circumstance, luck, and awesome friends.
+
+\rule{\linewidth}{0.2pt}
+
+The authors gratefully acknowledge the IT.IS foundation
+
+and also compiling the tissue property databases.
+
+\rule{\linewidth}{0.2pt}
+
+Thanks to
+
+\rule{\linewidth}{0.2pt}
+
+One Very Important Thought
 

### 2021-03-01 documents/brillouin_pulse_math.tex
Tersenating again

@@
 
-The extremely high losses from such thin coaxial cables should be considered.
-
-\pagebreak
 \section{Dispersion Timothy and the Brillouin Precursors}
 
-Uzunoglu \cite{Theoretical2020} mention a handy way to circumvent this lossy-flesh problem: the Brillouin and Sommerfeld precursors\footnotemark, and pulse or wavepacket dispersion in tissues in general.\footnotemark
-
-\footnotetext{
-	Sincere thanks go to the legendary Kurt Oughstun for taking the time to reply to our emails.
-}
+Uzunoglu \cite{Theoretical2020} mention a handy way to circumvent the lossy-flesh problem: the Brillouin and Sommerfeld precursors\footnotemark, and pulse or wavepacket dispersion in tissues in general.
+The original text of these papers are in German; translations can be found in Léon Brillouin's 1960 book\cite{Wave1960} on the topic.
 
 \footnotetext{"precursor" is perhaps a misnomer when single pulses are used rather than trapezoidally-modulated tones - Oughston and Najafabadi both call these \textit{Brillouin pulses}.\\ \cite{Optimal2015} \cite{Optimal2017} \cite{Heat2010}.}
-
-The original text of these papers are in German; translations can be found in Léon Brillouin's 1960 
-book\cite{Wave1960} on the topic. \footnotemark
 
@@
 \begin{itemize}
-	\item The highly dispersive nature of tissue, which causes a peculiar distortion of pulses with broadband spectral content,
+	\item The highly dispersive nature of tissue (the variation in speed of light with frequency), which causes a peculiar distortion of short pulses (which necessarily have a broadband spectral content).
 	\item The variation in loss (the imaginary part of the complex permittivity and the penetration depth) versus frequency. \wikinote{add image from that mathematica code}
@@
 A third aspect leads to the formation of the prototypical Brillouin precursor specifically: any sharp 
-beginning or end of a tone, or other sharply defined structure in a waveform, includes harmonics beyond the tone's carrier wave up to the rise time \footnotemark. \wikinote{add image}
+beginning or end of a tone, or other sharply defined structure in a waveform, includes harmonics beyond the tone's carrier wave up to the rise time\wikinote{add image}.
 
@@
 
-Precursors have been used in practice, by Ong \cite{Detection2003} using simple square waves to detect respiration\footnotemark, Ossberger \cite{Noninvasive2004} for the same purpose; and various techniques for breast cancer detection.
+Based on Yang's inactivation thresholds, for instance, at 9 GHz, assuming that a torso is about 10 penetration depths in radius and the hypothetical Brillouin train drives the virus equally effectively as, implementing a precursor would decrease the field required at the skin to a perfectly practicable 1 kV/m, rather than an air-ionizing 6.6 MV/m ($\frac{1}{\sqrt{10}}=0.316$ versus $e^{-10}=4.5e^{-5}$).
 
-Also another really good paper that I can't find.
+Precursors have been used in practice, by Ong \cite{Detection2003}\footnote{Well, Ong don't really observe the precursor itself directly, it seems.} using simple square waves to detect respiration\footnotemark, Ossberger \cite{Noninvasive2004} for the same purpose; and various techniques for tumor detection.\footnote{TODO: Also another really good paper that I can't find}
 
-\footnotetext{Well, Ong don't really observe the precursor itself, it seems.}
+While it is clearly possible to produce this abnormal penetration (any sharp edge sufficiently distant from suffices to provoke dispersive distortion), it was not obvious to us that a waveform could be constructed that would be an effective driver for the 10 GHz normal modes in question.
 
-By putting more power in higher frequencies,
+First, if dispersive pulses are too close together, they interfere as they propagate and diminish the precursor thus formed \cite{Dynamical2005}.
 
-While it is clearly possible to produce this abnormal penetration (any sharp edge sufficiently distant from  suffices to produce a dispersive pulse), it was not obvious to us that a waveform 
-could be constructed that would be an effective driver for the normal modes in question.
-
-First, Oughston ; if the pulses are too close together, they interfere as they propagate and distort the precursor thus formed.
-
-As an example, despite the waveform from nonlinear transmission lines producing strong wideband components, in cursory simulations they did not appear to satisfy the requirements for Brillouin pulses\wikinote{dubious-discuss}\wikinote{citation-needed}.
+As an example, despite the waveform from nonlinear transmission lines\cite{NLTL6275} producing strong wideband components, in cursory simulations they did not appear to satisfy the requirements for usable Brillouin pulses\wikinote{dubious-discuss}\wikinote{citation-needed}.
 Our working hypothesis is that this is because of destructive interference from the falling edge that immediately follows; but this is mere speculation.\wikinote{dubious-discuss}
 
-Second, while the pulse amplitude decays slowly, the total energy contained in such a precursor decays very quickly.
-The biological ramfications of discussed in detail by Adair in \cite{Biophysics2000}.
+Second, and most critically, while the pulse amplitude decays slowly, the total energy contained in such a precursor decays very quickly.
+The biological ramifications of this are discussed in detail by Adair in \cite{Biophysics2000}.
 
-temporal Soliton-producing nonlinear transmission lines, and NLTL oscillators constructed therefrom, particularly well suited
-
-\footnotetext{it is interesting to note that a similar - if not equivalent - effect leads to the Heisenberg uncertainty principle. The more localized a }
-
-At a depth of 8 cm in Cole-Cole muscle, an 8 GHz resonance, attack pattern alpha appears to achieve 4 picometers of oscillation amplitude, rather than 0.01 picometers with $\sin(t\ \omega_{resonance})$.
+%temporal Soliton-producing nonlinear transmission lines, and NLTL oscillators constructed therefrom, particularly well suited 
+%
+%At a depth of 8 cm in Cole-Cole muscle, an 8 GHz resonance, attack pattern alpha appears to achieve 4 picometers of oscillation amplitude, rather than 0.01 picometers with $\sin(t\ \omega_{resonance})$.
 The sharp edges are at approx.
@@
 
-At 9 GHz, assuming that a torso is about 10 penetration depths in radius and the Brillouin train 
-drives the virus with an equally, implementing this would decrease the field at the skin required 
-for complete eradication of the virus from the body to a perfectly practicable 1 kV/m, rather than 
-an air-ionizing 6.6 MV/m ($\frac{1}{\sqrt{10}}=0.316$ versus $e^{-10}=4.5e^{-5}$).
+Dispersive pulse propagation is easily modelled by a Fourier transform, propagation, and an inverse fourier transform (see Franzen \cite{Wideband1999}, see also \cite{Comments1993} and \cite{Shortrisetime1989}).
+\footnote{This isn't truly a transient process, of course - the fourier integral is still periodic, wrapping around the window; it's just more transient than a steady-state}.
+
+The loss and refractive index can be obtained from a four term Cole-Cole model\cite{dielectric1996}\cite{gabriel1996compilation}. We used parameters from the it.is tissue database \cite{Tissue2018a}.
 
@@
 % https://www.int.washington.edu/users/dbkaplan/228_01/green.pdf
-
-Note: this isn't truly transient - the fourier integral is still periodic, wrapping around every x cycles. It's just more transient than the steady-state.
-
-attack pattern alpha
-
-Transient solution
 
@@
 
-\paragraph{\textbf{Subharmonics}}\
-
 \begin{fquote}[Wait][ \cite{Propagation1965}]
@@
 \begin{autem}
+	autem: 
 Reflection from tissue interfaces?
@@
 
-Progress was hindered by the ~6 conventions for Fourier normalization, the sign or handedness of the imaginary number.
-What self-respecting field has completely antipodal definitions of the same concept.
-
-oh, on the same topic, can we finally settle the i / j convention. Also, everyone that doesn't explicitly note
+\footnote{Progress was hindered by the number of conventions for Fourier normalization.
+It's all well and good for the signal processing specialists to make all sorts of excuses about brevity, but when crossing fields it's pretty annoying for such a fundamental concept to be so loosely defined.
+On the same topic, can we finally settle the i vs.
+j convention, and the choice of reduced units in molecular dynamics?}
 
@@
 
-The most promising analytical technique that we explored was a slight modification of a formulation for optimal-energy pulses, largely supplied by Prof.
+We apologize in advance for the desecration of mathematics in this section.
+
+The most promising analytical technique explored was a slight modification of a formulation for optimal-energy pulses, largely supplied by Prof.
 Costas Sarris in a yet-unpublished personal communication, based on Zhu, Hum, Costas formulation in \cite{Microwave2012b}, previously discussed by Pozar \cite{Waveform2003}.
@@
 
-Here, rather than taking the derivative with respect to a small change in a variable, we take the derivative with respect to a small change in the function itself - a very useful technique (that the author was not aware of) which imposes little to no limitation on the form of the solution.
-For some intuition, the definition of the first variation and the Gateaux derivative may be of some use.
+Here, rather than taking the derivative with respect to a small change in a variable, we take the derivative with respect to a small change in the function itself - a very useful technique \footnote{that the author was not aware of!} which imposes little to no limitation on the form of the solution.
+For some intuition, the definition of the first variation and the Gateaux derivative may be of some use.\footnote{The complex conjugate in Sarris' formulation, $\nabla H() = H()^\star$, seems to come from \cite{Signal1969}, page 140 onwards; I cannot make heads or tails of his formulation.
+Pozar note that this complex conjugate arises from the concept of "adjointness".}
 
 A common setup for such a problem is to use the Euler-Lagrange equation; this is usually brought up in the case of the Brachistochrone problem, or the Principle of Least Action \footnote{For background, see The Feynman Lectures, vol II chapter 19}.
-In these types of problems, it appears that the path of integration through space from endpoints a to b is instead replaced by the whole frequency domain from -$\infty$ to +$\infty$.
+In these types of problems, it appears that the path of integration through space from endpoints a to b can be replaced by the whole frequency domain from -$\infty$ to +$\infty$.
 
@@
 where $\int e^{j \omega t} d\omega$ is the inverse fourier transform.
+At this point, you could choose to perform a second integral over the time-domain Greens function solution to the harmonic oscillator\cite{Complex2020}, or substitute
 
-$$W = \frac{1}{\eta_0} \int_{-\infty}^{+\infty}{(n_r(\omega))\ |F(\omega)|^2}\ d\omega$$\\
+\footnote{Many symbolic math tools have support for functional calculus.
+However, neither Maxima, SageMath, Mathematica's VariationalD, Matlab's Fundiff, nor Maple's functionalDerivative seem to yield any meaningful result for grad xi.}\\
 
-Where $n(\omega)$ is a complex refractive index per Debye relaxation equation, $n_r()$ is the real part of the same, everything else is a real constant.
+%$$W = \frac{1}{\eta_0} \int_{-\infty}^{+\infty}{(n_r(\omega))\ |F(\omega)|^2}\ d\omega$$\\
+%
+%Where $n(\omega)$ is a complex refractive index per Debye relaxation equation, $n_r()$ is the real part of the same, everything else is a real constant.
 Set up a functional with a lagrange multiplier\\
+%
+%$$\xi = -e_x(z,t) + \lambda W$$\\
+%
+%Take the functional ("variational") gradient with respect to $F(\omega)$.
+%
+%$$ \nabla \xi = -\frac{1}{\sqrt{2\pi}} \left(e^{- j (\omega/c_0)n(\omega)z}\right)^\star \  e^{-j\omega T} + \lambda...$$
+%
+%At this point, you could choose to perform a second integral over the time-domain Greens function solution to the harmonic oscillator\cite{Complex2020}, eq. 4 and 15, 
+%
+%$$x(t) = \int_{-\infty}^{+\infty}{G(t,t')\ \frac{q\cdot e_x(z,t'))}{m}\ } dt'$$\\
+%
+%(eq. 15, for the underdamped case)
+%
+%$$G(t,t') = UnitStep(t-t') \frac{1}{\sqrt{\gamma^2-\omega_0^2}  }\sinh\left({\sqrt{\gamma^2-\omega_0^2}}\ (t-t')\right)$$
+%
+%But a much more straightforward 
+%
+%Where * is the complex conjugate.\\
 
-$$\xi = -e_x(z,t) + \lambda W$$\\
+%
+%Then set
+%
+%$$x(t) = \int_{-\infty}^{+\infty}{G(t,t')\ \frac{q\cdot e_x(z,t'))}{m}\ } dt'$$\\
+%
+%Anyhow, then modify the lagrange multiplier,
+%
+%$$\xi = -x(t) + \lambda W$$\\
+%
+%And now,
+%
+%$$\nabla \xi = 0$$
 
-Take the functional ("variational") gradient with respect to $F(\omega)$.
-
-$$ \nabla \xi = -\frac{1}{\sqrt{2\pi}} \left(e^{- j (\omega/c_0)n(\omega)z}\right)^\star \  e^{-j\omega T} + \lambda...$$
-
-At this point, you could choose to perform a second integral over the time-domain Greens function solution to the harmonic oscillator\cite{Complex2020}, eq. 4 and 15,
-
-$$x(t) = \int_{-\infty}^{+\infty}{G(t,t')\ \frac{q\cdot e_x(z,t'))}{m}\ } dt'$$\\
-
-(eq. 15, for the underdamped case)
-
-$$G(t,t') = UnitStep(t-t') \frac{1}{\sqrt{\gamma^2-\omega_0^2}  }\sinh\left({\sqrt{\gamma^2-\omega_0^2}}\ (t-t')\right)$$
-
-But a much more straightforward
-
-Where * is the complex conjugate.\\
-
-The $\nabla H() = H()^\star$ thing seems to come from Franks, Signal Theory, 1969, page 140 onwards; I cannot make heads or tails of his formulation.
-
-Neither Maxima, SageMath, Mathematica's VariationalD, Matlab's Fundiff, nor Maple's 
-functionalDerivative seem to yield any meaningful result for grad xi.\\
-
-Then set
-
-$$x(t) = \int_{-\infty}^{+\infty}{G(t,t')\ \frac{q\cdot e_x(z,t'))}{m}\ } dt'$$\\
-
-Anyhow, then modify the lagrange multiplier,
-
-$$\xi = -x(t) + \lambda W$$\\
-
-And now,
-
-$$\nabla \xi = 0$$
-
-This lagrange multiplier technique has, however, a fundamental limitation (noted by Tufts \cite{Optimum1964}): for reasons that the author does not comprehend, only the pulse energy can be used as a constraint, rather than the value of the peak field.
+This lagrange multiplier technique has, however, a fundamental limitation (noted by Tufts \cite{Optimum1964}): for reasons that the author does not yet comprehend, only the pulse energy can be used as a constraint, rather than the value of the peak field.
 This seems to turn out to be of some importance.
-
-As noted by Pozar, the complex conjugate arises from the concept of "adjointness". Franks.
 

### 2021-03-01 documents/experiment_1_data.tex
Tersenating again

--- 2021-02-22 documents/experiment_1_data.tex
@@
 	\begin{tabular}{ |c|c|c| } 
+				\hline
+		\multicolumn{3}{|c|}{\textbf{Calibration trials} } \\
+		\hline
 		\hline
@@
 		Water & 1 & \\
+
 		\hline
-		\multicolumn{3}{|c|}{\ntilde 10 or 20 us  } \\
+\multicolumn{3}{|c|}{\textbf{Pulsed CW trials}} \\
 \hline
-		 & \\ 
+
 		\hline
-		\multicolumn{3}{|c|}{Sweep from 6 to 12 GHz, average approximately 150 V/m, 10 or 20 us CW pulses} \\
+		\multicolumn{3}{|c|}{\textbf{NF capillary}, 6 to 12 GHz, 10 or 20 us CW pulses} \\
 		\hline
-		\multicolumn{3}{|c|}{\ntilde 0.05 mm, \ntilde } \\
+		Sham   & 12 & Run 8 t4,5...\\
+		+ & 11 & Run 8 t4,5...\\
+		+  & 12 & Run 8 t4,5...\\
+		+  & 12 & Run 8 t4,5...\\
+		\hline
+		\multicolumn{3}{|c|}{\textbf{NF capillary}, 6 to 12 GHz, phage degraded with basic buffer} \\
+		\hline
+		Blank (0 min) & 14 & Run 9\\
+		Blank (\ntilde 15 min) & 17 & Run 9\\
+		Sham (\ntilde 15 min) & 5 & Run 9\\
+		Blank (\ntilde 4 hr) & 24 & Run 9\\
+		\hline
+		+  & 14 & Run 11\\
+		Sham & 17 & Run 11\\
+		\hline
+		\multicolumn{3}{|c|}{\textbf{NF capillary}, 6 to 12 GHz, 10 or 20 us CW pulses} \\
+		\hline
+		Sham & 12 & Run 12\\
+		+    & 10 & Run 12\\
+		\hline
+		\multicolumn{3}{|c|}{\textbf{0.2 mm channel}, 6 to 12 GHz, 10 or 20 us CW pulses} \\
+		\hline
+		 Sham & 12 & CPWG micro-\\
+ 		 +    & 10 & CPWG micro-\\
+
+		\hline
+		\multicolumn{3}{|c|}{\textbf{Nanosecond pulsed trials} } \\
+		\hline
+
  		\hline
@@
 
-Data from testing on bacteriophage. Data rounded (0.5 and above up) to the nearest thousand photon counts per 10 seconds. %thoroughly characterized.
+Original data for this table can be inspected at \ghfile{firmware/eppenwolf/pulse_1.pnw}.
 
-Background ('blank', in notes) readings measure the amount of DNA present in the phage culture tube before any treatment.
-
-Repeatability between test conditions was not terrific.
-The source of the \ntilde 5000 count variation between some equivalent samples is not known.
-However, in no case did any tube approach the 22 to 30 kcounts of the autoclave.
-
-Stock culture had titer $3\times 10^9$ T4r.
-
-The fluor-meter printed a constant stream of results, all within the random error between capture windows $\sigma=0.5$ kcounts. Only after most of the data was taken was it realized how dumb this was.
-
-Results aggregated over the course of several months.
-
-In all cases, a thermal effect was implausible; the total energy in the pulse train precluded heating above the capsid melting temperature.\cite{Effects1951}
-
-In an early iteration of the experiment, the firmware and data analysis scripts randomly generated blinded sham and autoclave assignments and automatically treated the samples accordingly.
-It also printed blinded templates for pipetting.
-This was done partly in the hopes that massively oversampling the microwave absorption spectrometer across the range of physical tolerances would highlight any resonances.\cite{first2000}
-
-However, as spectrometry was abandoned, this non-deterministic property caused significant issues while troubleshooting the fluorescence detection system, and \st{expedience} \st{\textit{laziness}} prompted us to disable this system, violating best practices.
-
-A thin layer of silicone conformal coating was applied to the 0.2 mm waveguide to avoid the copper ion artifact, but this could not be done on the 0.05 mm waveguide.
+See notes on data collection in main body.
 

### 2021-03-01 documents/summary.tex
Tersenating again

@@
 
+\begin{multicols}{1}
 \lettrine{W}e were inspired to undertake this project by a set of publications by a certain Sun group, (primarily Liu et al \cite{Microwave2009} and Yang et al \cite{Efficient2015}, simultaneously demonstrated by Hung et al \cite{focusing2014}), partially replicated by \cite{Optical2020} and discussed by \cite{Theoretical2020}.
@@
 
-More specifically, the concept of driving a virus as a harmonic oscillator has been previously considered only briefly \cite{MECHANICAL1968}\cite{Comment2004}\cite{Vibrational2009}\cite{Maximum2010}, perhaps first because in almost all cases structures in tissue are so over-damped by the surrounding solvent\cite{Vibrational2002}\cite{Biological2002}\cite{Biophysics2000}\cite{Viscous2000} as to have no non-zero resonant frequency at all \cite{dielectric1996}\cite{gabriel1996compilation}\wikinote{not in citation}\wikinote{discuss}; and second, because the charge distributions found in biology are too small for energies significantly above the thermal background to be absorbed via applied fields.
+A few well-established non-resonant non-thermal effects caused by extreme electric fields have already been put to practical use.
+Electroporation\cite{Electroporation1988} is a common laboratory procedure in which an enormous electric field causes ions in solution to diffuse across a host cell's membrane, capacitively charging it.
+This leads to a change in lipid conformation, reversibly rendering the membrane permeable (among other, more subtle mechanisms; the minutia of poration are extraordinarily complex and beyond the author's understanding\cite{Theoretical2007}).
+
+Therapies based on irreversible electroporation\cite{Nonthermal2013}\cite{Lipid2017} have recently been used in the clinic\cite{Irreversible2013} for tumor ablation.
+There is much discussion on electroporation as an alternative to viral vectors, but we have not yet found any discussion of clinical treatment of viral infection with these conventional electroporation therapies.% In vitro there is evidence to suggest that sub-cellular effects take place under truly tremendous fields.
+
+More specifically, the concept of driving a virus as a harmonic oscillator, as suggested by has been previously considered only briefly \cite{MECHANICAL1968}\cite{Comment2004}\cite{Vibrational2009}\cite{Maximum2010}, perhaps first because in almost all cases structures in tissue are so over-damped by the surrounding solvent\cite{Vibrational2002}\cite{Biological2002}\cite{Biophysics2000}\cite{Viscous2000} as to have no non-zero resonant frequency at all \cite{dielectric1996}\cite{gabriel1996compilation}\wikinote{not in citation}\wikinote{discuss}; and second, because the charge distributions found in biology are too small for energies significantly above the thermal background to be absorbed via applied fields.
 
@@
 
-A few well-established non-resonant non-thermal effects have already been put to practical use.
-Electroporation\cite{Electroporation1988} is a common laboratory procedure where an enormous electric field causes ions in solution to diffuse across a host cell's membrane, capacitively charging it, causing a change in lipid conformation, reversibly rendering it permeable (among other, more subtle mechanisms; the minutia of poration are extraordinarily complex and beyond the author's understanding\cite{Theoretical2007}).
-
-Therapies based on irreversible electroporation\cite{Nonthermal2013}\cite{Lipid2017} have recently been used in the clinic\cite{Irreversible2013} for tumor ablation.
-There is much discussion on electroporation as an alternative to viral vectors, but we have not found any discussion of clinical treatment of viral infection with these conventional electroporation therapies.% In vitro there is evidence to suggest that sub-cellular effects take place under truly tremendous fields.
-
 The idea of driven oscillation in biological systems appears to have originated from work by Frohlich\cite{Longrange1968}\cite{Evidence1983}\cite{Biological1980}\cite{Coherence1983} on the possibility of large-scale coherent QM Bose-Einstein condensates, and then many more subtle lines of inquiry\cite{Mechanisms1992}\cite{mechanisms1981}; but, to our knowledge, no such large-scale non-classical effects have ever been substantiated; specifically, suggestions of non-classical damping due to hydration layer effects have not been observed.
@@
 
-Because the effect seen by Yang et al \cite{Efficient2015} is so remarkable, we have tried to come up with ways of explaining the observed results without invoking a non-thermal effect:
+Because the effect seen by Yang et al \cite{Efficient2015} is so striking compared to previous work in the non-thermal literature, we have tried to invent with ways of explaining the observed results without invoking a non-thermal effect.
+Sufficient orthogonal measurements were made so that this is quite difficult.
+The most plausible timeline was:
 \begin{itemize}
-	\item The use of microwave absorption spectroscopy techniques that have previously shown resonance-like artifacts\cite{Resonances1987}.
+	\item The use of microwave absorption spectroscopy techniques somewhat similar to those which have previously shown resonance-like artifacts\cite{Resonances1987}.
 An effective charge of $q=10^7 e^-$ was found, which is very large for a $10^9$ atom structure.
 Genome and protein charge can hardly explain $10^5 e^-$, which would be reduced further by ionic screening.
-It appears that the  potential energy of such a sphere of charge would exceed the metabolic burden to build a virus by a significant factor\footnotetext.
-	\item Infrared thermography only determines the surface temperature.
-Based on heating patterns seen in other experiments\cite{Effects1950}, the observed surface temperature rise does not seem to conclusively rule out a very localized thermal effect.
-	\item Therefore, without free-space dosimetry or simulation of power density to demonstrate otherwise, the frequency-selective inactivation could be explained by the frequency response of the power amplifier, antenna gain, and absorption of the cuvette.
-\end{itemize}
-
-It seems reasonable that a field with a strong positive publication bias\cite{Comprehensive2018}, in the presence of strong peer review, might tend towards only the most abstruse and difficult to explain false-positive results.
-
-However, if this is a thermal artifact, the fact that the spectrometry and inactivation data shown align perfectly is very difficult to explain. We are forced to be satisfied with mystification.
+It appears that the potential energy of such a sphere of charge would exceed the observed metabolic burden to build a virus by a significant factor\footnotemark.
 
@@
 
-Of course, much of the potential energy may have already existed in the host cell, so this is probably an invalid comparison.
-And if most of the charge is contributed by osmotic, ion, this potential energy may not be considered in the above.
+		Of course, much of the potential energy may have already existed in the host cell, so this is possibly a flawed comparison.
+If most of the charge is contributed by osmotic, ion, this potential energy may not be considered in the above.
 Autem: is it possible for the charged core to compensate for the potential energy of the charged shell?}
+
+	\item Infrared thermography only determines the surface temperature.
+Based on heating patterns seen in other experiments\cite{Effects1950}, the observed surface temperature rise does not seem to conclusively rule out a very localized thermal effect.
+	\item Therefore, without free-space dosimetry or simulation of power density to demonstrate otherwise, the frequency-selective inactivation could be explained by the frequency response of the power amplifier, antenna gain, and absorption of the cuvette.
+\end{itemize}
+
+It seems reasonable that a field with a strong positive publication bias\cite{Comprehensive2018}, in the presence of strong peer review, might tend towards only the most abstruse and difficult to explain false-positive results.
+
+However, if this is a thermal artifact, the fact that the spectrometry and inactivation data shown align perfectly is very difficult to explain; and so this chain of events seems unlikely.
+We are forced to be satisfied with mystification.
 
@@
 From an energetics perspective, \footnote{The dipole spring constant can be extracted from the resonant frequency and therefore from the speed of sound and $m^*$, the reduced mass ($k = \omega_{res}^2 m^2$).
-} With relatively sane choices of charge screening and resonant frequency, the energy absorbed by the whole virus per cycle at 5 MV/m might vary from $10^{-5}$ to 100 times the thermal energy $k_b T$.
+} With relatively sane choices of solvent charge screening and resonant frequency, the energy absorbed by the whole virus per cycle at 5 MV/m might vary from $10^{-5}$ to 100 times the thermal energy $k_b T$.
 %TODO check effect of damping on hookes law energy.
@@
 
-Data on the charge distribution of the virion can be obtained by and 2D-PAGE relative protein composition or perhaps directly via extraction from whole-virion CryoEM maps because of the charge-sensitive nature of electrons over X-ray diffraction \cite{Identification2018}\cite{Electrostatic2020}; but this has not yet been implemented.
+Data on the charge distribution of the virion can be obtained by and 2D-PAGE relative protein composition or perhaps directly via extraction from whole-virion CryoEM maps, because of the charge-sensitive nature of electrons over X-ray diffraction \cite{Identification2018}\cite{Electrostatic2020}; but this has not yet been implemented.
 
-Modelling this sort of large-scale inactivation mechanism involving the collective motion of some $10^9$ atoms poses a significant computational and theoretical hassle, which has far exceeded our capabilities.
+Modelling this sort of multi-scale inactivation mechanism involving the collective motion of some $10^9$ atoms poses a significant computational and theoretical hassle, which has far exceeded our capabilities.
 Poisson-Boltzmann implicit ionized solvents.
@@
 Parametrizing based on all-atom simulations of small capsid segments or proteins \cite{Elucidating2009}.
+Mechanically reasonable coarse-grained models have recently been published for SARS-NCoV-2.
 DNA with beads restrained by Lennard-Jones forces \cite{Communication2013}.
@@
 
-Non-resonant capsid and envelope breakage at 100 pulses, 500 ns at 3 MV/m, has been previously observed\cite{Inactivation1990} but the RNA damage suggests that this is an electrochemical artifact \cite{Formation1996} (and \cite{Microwave1987}).
+Non-resonant capsid and envelope breakage with 120 pulses, 500 ns each, at 3 MV/m, has been previously observed\cite{Inactivation1990} but the RNA damage suggests that this is an electrochemical artifact \cite{Formation1996} (and \cite{Microwave1987}).
 Long pulses at $10$ MV/m electroporate enveloped viruses similarly to host cells\cite{AC2017} but do not necessarily affect T4\cite{Manipulation2013}.
@@
 
-which are similar in size to the viral membrane \cite{MicrowaveStimulated1985}\cite{Influence}\cite{Correlation1994}\cite{contribution2019}.
+An effect \cite{MicrowaveStimulated1985}\cite{Influence}\cite{Correlation1994}\cite{contribution2019}.
 These results are of excellent quality, with good thermal controls.
-\footnote{One founding researcher has been implicated in a scandal; however, the Livermore report on the topic does not appear to be public, so we cannot evaluate the basis for these claims.} This effect appears to depend on dissolved oxygen, seemingly evidence against a mechanical effect.
-lipid "transition temperature" - the point at which pores reseal.
-\cite{Effect1994a}.
+\footnote{One founding researcher has been implicated in a research scandal; however, the Livermore report on the topic does not appear to be public, so we cannot evaluate the basis for these claims.} This effect appears to depend on dissolved oxygen\cite{Microwaves1987}\cite{Microwaves1988}, evidence against a mechanical effect.
+The lipid "transition temperature" - the point at which pores reseal - is also relevant.
+One report has been found to be a very strange artifact\cite{Effect1994a}.
 
-Custom single-lipid liposome surrogates appear to be relatively easy to produce and fill with a DNA tracer by sonication and dehydration\cite{Encapsulation1982}\cite{OPTIMIZATION2017}.
-The only problem expected was removing unencapsulated DNA, which typically requires ultracentrifugiation as precipitation is not as easy as with phage.
+Custom single-lipid liposome surrogates appear to be relatively easy to produce and fill with a DNA tracer by sonication and dehydration\cite{Encapsulation1982}\cite{OPTIMIZATION2017}\cite{Liposome2014}.
+One problem encountered removing unencapsulated DNA, which typically requires ultracentrifugiation as precipitation of liposomes is more difficult.
 However, \cite{novela} appear to demonstrate that ethanol is satisfactory, and likely does not lead to DNA precipitation because of the lack of salt.
-\cite{Liposome2014}
 
@@
 
-In our experiments with our (admittedly very unstable) spectrometer, we were able to produce many candidate resonances with perfectly justifiable modifications to post-processing, which raises interesting (but not novel) questions regarding software quality in research.
-Unit testing
+In our experiments with our homebrew spectrometer, we were able to produce many candidate resonances with perfectly justifiable modifications to post-processing, which raises interesting (but not novel\cite{Reanalysis2020}\cite{statistical2020}) questions regarding software quality in such research.
+\footnote{Perhaps developing the analysis software only on some sort of blind, synthetic data would offer a }
 
-Synthetic data \cite{Reanalysis2020}\cite{statistical2020}.
+\begin{figure}[H]
+	%	\makebox[\textwidth][c]{
+	\includesvg[width=\textwidth]{propagated_waveforms}
+	\caption{Brillouin precursor propagation through tissue (reproduced from section 6).\\
+		(a) Gaussian monopulse with 16 ps FWHM.\\
+		(b) Optimized 10 GHz sawtooth wave. Note the slight high-frequency ripple.\\ This has a frequency of approximately 1.5 GHz.\\
+		(c) Prototypical precursor 10 GHz sine burst.\\
+		(d) Continuous 10 GHz sine tone.}
+
+\end{figure}
 
@@
 
-A sawtooth might be the optimal waveform (see supplemental).
+A sawtooth might be the optimal waveform (see below).
 However, obtaining 10 GHz tones deep in the body is still very hard, and may require very complicated dispersive phased arrays\cite{Microwave1982a}.
@@
 Phi6 \footnote{An interesting}.
-Some other surrogates may include PMD1,
+Some more useful surrogates may include Pseudomonas Phi 6\cite{Selection2017}, PM2,
+
+Viradel
 
@@
 
-The original Yang paper used plaque assays and RT-PCR to measure envelope damage; the quantification of viral titer is a solved problem. Not having equipment or experience
+The original paper by Yang et al used plaque assays and RT-PCR to measure envelope damage.
+Quantification of viral titer is a thoroughly solved problem, which did not justify the amount of time we spent developing the below procedures.
 
-Although not sensitive to changes in infectivity, we used an amplification-free fluorescent dsDNA detection method, as suggested by \cite{Quantification2020}, using a custom photon-counting plate reader and a 1:1 mix of viral solution with 1/4000 Biotium GelGreen (a safe Acridine Orange (N-alkylacridinium) based flurophore).
+Although not sensitive to changes in infectivity, we used an amplification-free fluorescent dsDNA detection method, exactly as suggested by \cite{Quantification2020}, using a custom photon-counting reader and a 1:1 mix of viral solution with 1/4000 Biotium GelGreen (a safe Acridine Orange (N-alkylacridinium) based flurophore).
 
@@
 
+This assay works because the flurophore drastically changes fluorescence intensity and lifetime when in complex with DNA\cite{SYBR2012}\cite{Characterization2010}, and the large size of the GelGreen molecule prevents diffusion through intact membranes.
+
 While their bandwidth is narrow, very cheap 0.5" laser line thin-film filters still work great for both excitation and emission for fluorescence techniques.
@@
 Use a 1 mm plastic fiber optic at right angles to decrease excitation light scattering.
-Beware material autofluorescence - custom Lexan cuvettes unexpectedly overwhelmed the DNA signal.
-(final set: [emission: Tiffen Orange 16 gel in series with Thorlabs FL05532, 532nm, 10 nm FWHM] [Edmund 28432, 486 nm])
+Beware material autofluorescence - custom Lexan cuvettes unexpectedly overwhelmed the DNA signal (final set: [emission: Tiffen Orange 16 gel\cite{lide2004crc} in series with Thorlabs FL05532, 532nm, 10 nm FWHM] [Edmund 28432, 486 nm]).
+A surplus Hammamatsu R4220 with HC123 current-limiting base at maximum sensitivity was used.
+A low-voltage silicon photomultiplier will probably be sufficient in most cases.
 
@@
 
-If CCD sensors with a, ImageJ \cite{Image2012}. A silicon photomultiplier will probably be sufficient in most cases.
+Many luminescent assays require high-performance DSLR CCDs capable of several minute exposures.
+\cite{Image2012} use ImageJ\cite{NIH2012} to stack frames from standard CMOS video cameras.
+In our testing, this was ineffective with expensive, high-quality industrial CMOS cameras, but extremely effective with webcams and ELP-brand cameras.
+Performance of such a stacked video approached that of the photomultiplier.
 
-A number of other assays were evaluated.
-However, these initial tests were marred by use of a domestic fridge to store phage, which unexpectedly froze regularly overnight, apparently reducing phage titer, along with our accidental use of T4r+, which is not an "improved" T4r, as we believed, but rather a mutation away from rapid-lysis, meaning that the lysis behavior is far slower (see \cite{Spontaneous1946}).
-In our testing, lysis of T4r+ only occurred on plaque plates (where culture growth and log stage infectivity is maintained for many days).
+A number of other capsid damage assays were evaluated.
+However, these initial tests were marred by the 1 uL sample volume in our initial cuvette attempts, our use of a domestic fridge to store phage, which unexpectedly froze regularly overnight, apparently reducing phage titer, along with our accidental use of T4r+ (not an "improved" T4r, as we believed, but rather a mutation away from rapid-lysis, meaning that the lysis behavior is far slower (see \cite{Spontaneous1946}).
+In our testing, lysis of T4r+ only occurred on plaque plates (where culture growth and log stage infectivity is maintained for many days)).
 
@@
 We stole an avalanche Marx design verbatim from Li (\cite{Development2016b} \cite{Design2018c}), which allows large pulses from safer lower voltage supplies (albeit requiring somewhat costly capacitors).
+2N5551 transistors used to be common \cite{Avalanche1991}\cite{high1994}\cite{High1998}; our testing with Raj's FMMT417
 
@@
 If a fast laser is available, Auston switches appear to be equally effective.
+
+\subsection{Notes}
+
+%
+%For in-vitro research, it seems to me that perhaps this field is running into the issues Feynman's rat-races \cite{Cargo}. There are a large number of very tricky variables.
+
+Data rounded to the nearest thousand photon counts per 10 seconds. %thoroughly characterized.
+
+Background ('blank', in notes) readings measure the amount of DNA present in the phage culture tube before any treatment.
+'sham' indicates a blank sample that was injected through the capillary identically to the treatment samples, except with either the VCO or Marx pulser disabled.
+
+Repeatability between test conditions was not terrific. The source of the \ntilde 5000 count variation between some equivalent samples, and between "blank" and "sham", is not known.
+
+Ishii and Yanagida \cite{two1977}, (Qin \cite{Structure2010}), find at a pH of 10.6, about 0.3x inactivation after a few minutes of incubation at 37 C, and almost complete loss after a few hours.
+The capsid is weakened greatly by the base, relying on the "clamp proteins" hoc and soc.
+
+Note the difference in base inactivation timeline between Run 9 and Weakened.
+In one case, base inactivation is found exactly as predicted; little inactivation is found in the other.
+We cannot explain this result.
+
+In no case did any field-exposed sample\wikinote{verify in notes} approach the 30 kcounts of the autoclave; therefore, we do not consider this a positive result.
+
+Stock culture had titer $3\times 10^9$ T4r.
+
+The electrodes were only 1 oz copper thick (35 micrometers), but the engraved channel is significantly deeper. 
+\cite{Nanosecond2006} and simulations seem to suggest that this is not a serious problem, but it is possible that the field in much of the channel was much lower than predicted.
+
+The fluor-meter printed a constant stream of results, all within the random error between capture windows $\sigma=0.5$ kcounts. Only after most of the data was taken was it realized how dumb this was.
+
+Results aggregated over the course of several months.
+
+In all cases, a thermal effect was made implausible; the total energy in the pulse train precluded heating above the capsid melting temperature\cite{Effects1951}.
+
+Only tubes 4 onwards are shown from Run 8 data because the capillary purging protocol was changed.
+In the final iteration, the autosampler was disconnected.
+The capillary was flushed with water; then the leuer lock was disconnected, air withdrawn into the syringe, and then purged through the capillary and fluidic channel.
+
+In an early iteration of the experiment, the firmware and data analysis scripts randomly generated blinded sham and autoclave assignments and automatically treated the samples accordingly.
+It also printed blinded templates for pipetting.
+This was done partly in the hopes that massively oversampling the microwave absorption spectrometer across the range of physical tolerances would highlight any resonances.\cite{first2000}
+
+However, as spectrometry was abandoned, this non-deterministic property caused considerable issues while troubleshooting the fluorescence detection system, and \st{expedience} \footnote{laziness} prompted us to disable this system at run 9, defying best practices on blinded trials.
+
+A thin layer of silicone conformal coating was applied to the 0.2 mm waveguide to avoid the copper ion artifact, but this could not be done on the 0.05 mm waveguide.
+
+\begin{tcolorbox}
+
+	The following is probably self-evident to all good scientists, and will ring worthy and overripe to those experienced; unfortunately, we only learned it during this project, so it seems worthwhile to make explicit.\\
+
+	As noted later, this field reached a reasonable level of quality many decades ago, and many of the most troubling issues had already been encountered and addressed satisfactorily in published experimental designs\cite{Biological1984}.
+
+	In some cases, these are thoroughly characterized and described; field intensities are mapped, thermal profiles taken; even the dielectric properties of the media must be considered.
+But it seems that some workers continue to develop their own test arrangements; yet the studies are sometimes not so different as to require such customization.
+\\
+
+	This demands that the reader perform analysis anew to verify details of how the study was conducted, rather than simply evaluate its results; a waste of time on all counts.\\
+
+	By using yet another exposure cell, introducing an new set of unknown artifacts, we hamper this field; and so we encourage anyone who may wish to persue similar results to not use this arrangement, but instead one of the existing, well-characterized exposure systems mentioned below or in the literature.
+
+	In this case, we were limited by budget - primarily the power amplifiers we have access to.
+
+	%\blfootnote{It occurs to me that perhaps a set of standardized test cells and procedures would be helpful; along with a requirement that any papers on the topic either use such a cell, or, if their study requires some exceptional treatment, to follow some established step-by-step procedure to add a new cell to the standard.}
+\end{tcolorbox}
 
@@
 
-The authors gratefully acknowledge the IT.IS foundation
-
-and also compiling the tissue property databases.
-
-\rule{\linewidth}{0.2pt}
-
 Thanks to
@@
 
+\end{multicols}
+
 One Very Important Thought
 
+\subfile{brillouin_pulse_math}
+
 \end{document}

### 2021-03-04 documents/brillouin_pulse_math.tex
Fields put in data table

@@
 
-Dispersive pulse propagation is easily modelled by a Fourier transform, propagation, and an inverse fourier transform (see Franzen \cite{Wideband1999}, see also \cite{Comments1993} and \cite{Shortrisetime1989}).
-\footnote{This isn't truly a transient process, of course - the fourier integral is still periodic, wrapping around the window; it's just more transient than a steady-state}.
+Dispersive pulse propagation is easily modelled by a Fourier transform, propagation, and an inverse fourier transform (see Franzen \cite{Wideband1999}, see also \cite{Comments1993} and \cite{Shortrisetime1989})\footnote{implemented in\ghfile{/home/arthurdent/Projects/covidinator/electronics/propagation/propagation_numerical_optimize.py}} \footnote{This isn't truly a transient process, of course - the fourier integral is still periodic, wrapping around the window; it's just more transient than a steady-state}.
 
-The loss and refractive index can be obtained from a four term Cole-Cole model\cite{dielectric1996}\cite{gabriel1996compilation}. We used parameters from the it.is tissue database \cite{Tissue2018a}.
+The loss and refractive index can be obtained from a four term Cole-Cole model\cite{gabriel1996compilation}\footnote{implemented in\ghfile{/electronics/simple_fdtd/fdtd_PCB_extensions/fdtd_PCB_extensions/tissue.py}}.
+We used parameters from the IT.IS Foundation tissue database\cite{Tissue2018a}.
 
@@
 Of course, 10x attenuation at 1 MV/m still takes us beyond safe levels at the skin.
-However, the loss that makes phased-array near-field focusing systems impractical at baseband is no longer a concern.
-A dispersive phased array with more than 10 elements may allow the complete elimination of attenuation without exceeding the limit field at any point in the body.
-
-\section{Pulse shaping}
-
-Producing such arbitrary electrical impulses may seem implausible; but in fact, if is a sufficiently sharp and only a few cycles are required,
-
-can probably be produced by e.g. an Auston switch feeding a pulse shaping line.
-
-Arbitrary pulses can be formed by
+However, the loss that makes phased-array near-field focusing systems impractical at baseband is no longer as significant of a concern.
+A dispersive phased array with more than 10 elements may improve penetration further.
 

### 2021-03-04 documents/experiment_1_data.tex
Fields put in data table

@@
 	\centering
-	\begin{tabular}{ |c|c|c| } 
+	\begin{tabular}{ |c|c|c|c| } 
 				\hline
@@
 		\hline
-		\multicolumn{3}{|c|}{\textbf{NF capillary}, 6 to 12 GHz, 10 or 20 us CW pulses} \\
+		\multicolumn{3}{|c|}{\textbf{NF capillary}, 6 to 12 GHz, 10 or 20 us CW pulses 84.8 V/m pessimistic to 339 V/m optimistic} \\
 		\hline
@@
 		\hline
-		\multicolumn{3}{|c|}{\textbf{NF capillary}, 6 to 12 GHz, phage degraded with basic buffer} \\
+		\multicolumn{3}{|c|}{\textbf{NF capillary}, 6 to 12 GHz, phage degraded with basic buffer, 84.8 V/m pessimistic to 339 V/m optimistic} \\
 		\hline
-		Blank (0 min) & 14 & Run 9\\
+		Blank (0 min) & 14 & Run 9 \\
 		Blank (\ntilde 15 min) & 17 & Run 9\\
@@
 		\hline
-		\multicolumn{3}{|c|}{\textbf{NF capillary}, 6 to 12 GHz, 10 or 20 us CW pulses} \\
+		\multicolumn{3}{|c|}{\textbf{NF capillary}, 6 to 12 GHz, 10 or 20 us CW pulses, 84.8 V/m pessimistic to 339 V/m optimistic} \\
 		\hline
@@
 		\hline
-		\multicolumn{3}{|c|}{\textbf{0.2 mm channel}, 6 to 12 GHz, 10 or 20 us CW pulses} \\
+		\multicolumn{3}{|c|}{\textbf{0.2 mm channel}, 6 to 12 GHz, 10 or 20 us CW pulses, 200 V/m pes. and 10.6 kV/m opt.} \\
 		\hline
@@
  		\hline
-		\multicolumn{3}{|c|}{\ntilde 0.2 mm channel, 0.2 uL/s, various pulse counts and termination} \\
+		\multicolumn{3}{|c|}{\ntilde 0.2 mm channel, various pulse counts and termination, 0.155 MV/m to 5.6 MV/m} \\
 		\hline 
@@
 
-		\multicolumn{3}{|c|}{\ntilde 0.05 mm channel, 0.2 uL/s, various pulse counts and termination} \\
+		\multicolumn{3}{|c|}{\ntilde 0.03 mm channel, 0.2 uL/s, various pulse counts and termination, 1 MV/m to 38 MV/m} \\
 		\hline
@@
 
-		\multicolumn{3}{|c|}{\ntilde 0.05 mm channel, 0.2 uL/s, basic buffer, tainted as pH may not have been 10.6} \\
+		\multicolumn{3}{|c|}{\ntilde 0.03 mm channel, basic buffer, tainted as pH may not have been 10.6, 1 MV/m to 38 MV/m} \\
 		\hline
@@
 
-Original data for this table can be inspected at \ghfile{firmware/eppenwolf/pulse_1.pnw}.
+Original notes for this table can be inspected at \ghfile{firmware/eppenwolf/pulse_1.pnw}.
+Data rounded to the nearest thousand fluorescence photon counts per 10 seconds.
+Larger numbers are presumed to correlate with greater capsid damage.
 
-See notes on data collection in main body.
+See notes on experiment design and data collection in main body.
 

### 2021-03-04 documents/summary.tex
Fields put in data table

@@
 \subfile{experiment_1_data}
-\begin{figure}[H]
-	%	\makebox[\textwidth][c]{
-	\includesvg[width=\textwidth]{propagated_waveforms}
-	\caption{Brillouin precursor propagation through tissue (reproduced from section 6).\\
-		(a) Gaussian monopulse with 16 ps FWHM.\\
-		(b) Optimized 10 GHz sawtooth wave. Note the slight high-frequency ripple.\\ This has a frequency of approximately 1.5 GHz.\\
-		(c) Prototypical precursor 10 GHz sine burst.\\
-		(d) Continuous 10 GHz sine tone.}
 
-\end{figure}
 \clearpage
@@
 \begin{multicols}{1}
+
+%\begin{refsection}
 \lettrine{W}e were inspired to undertake this project by a set of publications by a certain Sun group, (primarily Liu et al \cite{Microwave2009} and Yang et al \cite{Efficient2015}, simultaneously demonstrated by Hung et al \cite{focusing2014}), partially replicated by \cite{Optical2020} and discussed by \cite{Theoretical2020}.
 
-We have some minor questions regarding experimental technique in the original papers that can only be addressed by more extensive replication studies, and luckily are due to be answered by other groups\cite{Generating}, so we do not defer greatly to their observations.
+We have some minor questions regarding experimental technique in the original papers that can only be addressed by more extensive replication studies, and luckily are due to be answered by other groups\cite{Generating}, so we try not to defer greatly to their observations.
 
@@
 
-More specifically, the concept of driving a virus as a harmonic oscillator, as suggested by has been previously considered only briefly \cite{MECHANICAL1968}\cite{Comment2004}\cite{Vibrational2009}\cite{Maximum2010}, perhaps first because in almost all cases structures in tissue are so over-damped by the surrounding solvent\cite{Vibrational2002}\cite{Biological2002}\cite{Biophysics2000}\cite{Viscous2000} as to have no non-zero resonant frequency at all \cite{dielectric1996}\cite{gabriel1996compilation}\wikinote{not in citation}\wikinote{discuss}; and second, because the charge distributions found in biology are too small for energies significantly above the thermal background to be absorbed via applied fields.
+If the duration of exposure is sufficiently short that thermal and membrane breakdown effects can be neglected, tissue appears to withstand peak electric fields of great magnitude - above 1 nanosecond megavolt/meter, even in in-vivo studies - without severe acute effects(\cite{Repeated2020}\cite{Review2011} and below).
+
+More specifically, the concept of driving a virus as a harmonic oscillator, as suggested by \cite{Efficient2015} has been previously considered only briefly \cite{MECHANICAL1968}\cite{Comment2004}\cite{Vibrational2009}\cite{Maximum2010}, perhaps first because in almost all cases structures in tissue are so over-damped by the surrounding solvent\cite{Vibrational2002}\cite{Biological2002}\cite{Biophysics2000}\cite{Viscous2000} as to have no non-zero resonant frequency at all \cite{dielectric1996}\cite{gabriel1996compilation}\wikinote{not in citation}\wikinote{discuss}; and second, because the charge distributions found in biology are too small for energies significantly above the thermal background to be absorbed via applied fields.
 
@@
 
+%
+%\printbibliography[heading=subbibliography]
+%\end{refsection}
+
 The idea of driven oscillation in biological systems appears to have originated from work by Frohlich\cite{Longrange1968}\cite{Evidence1983}\cite{Biological1980}\cite{Coherence1983} on the possibility of large-scale coherent QM Bose-Einstein condensates, and then many more subtle lines of inquiry\cite{Mechanisms1992}\cite{mechanisms1981}; but, to our knowledge, no such large-scale non-classical effects have ever been substantiated; specifically, suggestions of non-classical damping due to hydration layer effects have not been observed.
-In fact, consensus\cite{Exposure2009}\cite{ICNIRP2020}\cite{C95} appears to agree that, not only are oscillatory effects implausible, there are no relevant, substantiated, non-diffusion-like non-thermal mechanisms.
+In fact, evidence to date\cite{Exposure2009}\cite{ICNIRP2020}\cite{C95} appears to agree that, not only are oscillatory effects implausible, there are no relevant, substantiated, non-diffusion-like non-thermal mechanisms.
 
-Because the effect seen by Yang et al \cite{Efficient2015} is so striking compared to previous work in the non-thermal literature, we have tried to invent with ways of explaining the observed results without invoking a non-thermal effect.
-Sufficient orthogonal measurements were made so that this is quite difficult.
+Because the effect seen by\cite{Efficient2015} is so striking compared to previous work in the non-thermal literature, we have tried to invent ways of explaining the observed results without invoking a non-thermal effect.
+Sufficient orthogonal measurements were made, so this is quite difficult.
 The most plausible timeline was:
@@
 	\item The use of microwave absorption spectroscopy techniques somewhat similar to those which have previously shown resonance-like artifacts\cite{Resonances1987}.
-An effective charge of $q=10^7 e^-$ was found, which is very large for a $10^9$ atom structure.
-Genome and protein charge can hardly explain $10^5 e^-$, which would be reduced further by ionic screening.
-It appears that the potential energy of such a sphere of charge would exceed the observed metabolic burden to build a virus by a significant factor\footnotemark.
-
-	\footnotetext{
+In particular, an effective charge of $q=10^7 e^-$ was found via this method, which is very large for a $10^9$ atom structure.
+Genome and protein charge can hardly explain $10^5 e^-$ (see below), which would be reduced further by ionic screening.
+It appears that the potential energy of such a sphere of charge would exceed the observed metabolic burden to build a virus by a significant factor \footnote{
 		$$ U = \frac{3}{5}  \frac{1}{4 \pi \epsilon_0} \frac{Q^2}{R} \approx 2.3\text{e}^{-7} \text{ J} \approx 6 \times 10^{11}\  \text{ATP-equivalent} $$
@@
 If most of the charge is contributed by osmotic, ion, this potential energy may not be considered in the above.
-Autem: is it possible for the charged core to compensate for the potential energy of the charged shell?}
+Autem: is it possible for the charged core to compensate for the potential energy of the charged shell?}.
+Ion polarization effects are generally not indicated at these timescales\cite{ICNIRP2020}, but faster electron polarization might occur to some small degree.
 
@@
 
-It seems reasonable that a field with a strong positive publication bias\cite{Comprehensive2018}, in the presence of strong peer review, might tend towards only the most abstruse and difficult to explain false-positive results.
+It seems reasonable that a field with a strong positive publication bias\cite{Comprehensive2018}, in the presence of stringent peer review, might tend towards only the most abstruse and difficult to explain false-positive results.
 
 However, if this is a thermal artifact, the fact that the spectrometry and inactivation data shown align perfectly is very difficult to explain; and so this chain of events seems unlikely.
-We are forced to be satisfied with mystification.
 
-The genome charge is almost entirely neutralized by the nucleocapsid.
+An interesting effect, superficially similar to the leakage found by Yang et al, has been observed on lipid liposomes similar to viral envelopes\cite{MicrowaveStimulated1985}\cite{Influence}\cite{Correlation1994}\cite{contribution2019}.
+These results are of excellent quality, with good thermal controls.
+\footnote{One founding researcher has been implicated in a research scandal; however, the Livermore report on the topic does not appear to be public, so we cannot evaluate the basis for these claims.} This effect appears to depend on dissolved oxygen\cite{Microwaves1987}\cite{Microwaves1988}, somewhat contrary to a mechanical effect.
+The phase transition temperature of the lipids used (the point at which pores reseal) is also a relevant quantity.
 
-From an energetics perspective, \footnote{The dipole spring constant can be extracted from the resonant frequency and therefore from the speed of sound and $m^*$, the reduced mass ($k = \omega_{res}^2 m^2$).
-} With relatively sane choices of solvent charge screening and resonant frequency, the energy absorbed by the whole virus per cycle at 5 MV/m might vary from $10^{-5}$ to 100 times the thermal energy $k_b T$.
+One such report has been found to be a very strange artifact caused by the Teflon dish used for microwave trials\cite{Effect1994a}, highlighting the need for exactly identical sham trials.
+
+Custom single-lipid liposome surrogates appear to be relatively easy to produce and fill with a DNA tracer by sonication and dehydration\cite{Encapsulation1982}\cite{OPTIMIZATION2017}\cite{Liposome2014}.
+We encountered one problem removing unencapsulated DNA, which typically requires ultracentrifugation as precipitation of liposomes is difficult.
+However, \cite{novela} appear to demonstrate that ethanol extraction is satisfactory.
+This likely does not lead to DNA precipitation because of the lack of salt.
+
+With\footnote{The dipole spring constant can be extracted from the resonant frequency and therefore from the speed of sound and $m^*$, the reduced mass ($k = \omega_{res}^2 m^2$).
+} relatively sane choices of solvent charge screening and resonant frequency, the energy absorbed by the whole virus per cycle at 5 MV/m might vary from $10^{-5}$ to 100 times the thermal energy $k_b T$.
 %TODO check effect of damping on hookes law energy.
@@
 
-On the other hand, such a sub-angstrom movement only produces approx.
-0.05\% deflection of the capsid, whereas a general value for the rupture of host cells is about 3\% deflection.
-The stiffness of the genome may explain this.
-In addition, with a relaxation time on the order of 500 ps, it is difficult to imagine that the energy will be sufficiently concentrated in the capsid to be destructive.
-After the relaxation time, the energy is a distant memory; only the mechanical effects that were induced during that time can remain.
-
-Data on the charge distribution of the virion can be obtained by and 2D-PAGE relative protein composition or perhaps directly via extraction from whole-virion CryoEM maps, because of the charge-sensitive nature of electrons over X-ray diffraction \cite{Identification2018}\cite{Electrostatic2020}; but this has not yet been implemented.
+On the other hand, such a sub-angstrom movement can only induce approx.
+0.05\% deflection of the capsid, whereas a general value for the rupture of host cells is about 3\% deflection\cite{Electromechanical1989}.
+The stiffness of the genome could be used to explain this.
+With a relaxation time on the order of 500 ps, it is difficult to imagine that this energy will be sufficiently concentrated in the capsid to be destructive.
+After the relaxation time, only the mechanical effects that were induced can remain.
 
 Modelling this sort of multi-scale inactivation mechanism involving the collective motion of some $10^9$ atoms poses a significant computational and theoretical hassle, which has far exceeded our capabilities.
+
+Coarse-graining; but, as with all simulations, the problem must be set up with great care and experience (polarizable water; proper heat-bath damping coefficients and choice of integrator)\cite{Membrane2016}, and with an understanding of possible failure modes; we did not trust our abilities to produce correct results.
+Parametrizing based on all-atom simulations of small capsid segments or proteins \cite{Elucidating2009}.
+Mechanically reasonable coarse-grained models have recently been published for SARS-NCoV-2\cite{Multiscale2020}.
+DNA can be represented by homogeneous beads restrained by Lennard-Jones forces \cite{Communication2013}.
+Finite-element analysis \cite{Finite2008}
+
 Poisson-Boltzmann implicit ionized solvents.
 
-Parametrizing based on all-atom simulations of small capsid segments or proteins \cite{Elucidating2009}.
-Mechanically reasonable coarse-grained models have recently been published for SARS-NCoV-2.
-DNA with beads restrained by Lennard-Jones forces \cite{Communication2013}.
-Finite-element analysis \cite{Finite2008}; some Poisson-Boltzmann solvers
+Data on the charge distribution of the virion can be obtained by and 2D-PAGE relative protein composition - or even perhaps directly, via extraction from whole-virion CryoEM maps, because of the charge-sensitive nature of the technique \cite{Identification2018}\cite{Electrostatic2020}.
+This has not yet been implemented in any software tools and seems quite tricky.
+The genome charge is almost entirely neutralized by the nucleocapsid.
 
-GROMACS simulations of liposomes, trajectories fourier transformed with \cite{TRAVIS2011}
+GROMACS simulations of liposomes, trajectories fourier transformed with \cite{TRAVIS2011}.
 
@@
 Molecular dynamics of ISRU has been considered \cite{Maximum2010}, (\cite{Vibrational2009} but without considering heat-bath damping).
-Interestingly, if the well-established 1 TW power density\cite{Targeted2002} for mammalian cell laser damage is scaled linearly with time to the nanosecond regime ($1\ \text{TW/m}^2 / (100\ \text{ps} / 0.3\ \text{ps}) = 3\ \text{GW/m}^2$),
+Interestingly, if the well-established 1 TW power density\cite{Targeted2002} for mammalian cell damage by femtosecond laser is scaled linearly with time to the nanosecond regime, a power density similar to that of \cite{Repeated2020} is found ($1\ \text{TW/m}^2 / (100\ \text{ps} / 0.3\ \text{ps}) = 3\ \text{GW/m}^2$).
 
@@
 A rotational drag coefficient can extracted from MD simulation\cite{Evaluating2017}.
-Simulating a 30 nm lipid liposome using the MARTINI coarse-grained \cite{MARTINI2007} lipid force fields with GROMACS\cite{GROMACS2005}' torque measurement feature, kindly implemented by Kutzner \cite{Keep2011}.
-This suggests a maximum rotation frequency $10^7$ on the order of $10^3$, but this value requires so many assumptions that it's hardly worth mentioning.
+We simulated a 30 nm lipid liposome using the MARTINI coarse-grained \cite{MARTINI2007} lipid force fields with GROMACS\cite{GROMACS2005}' torque measurement feature, kindly implemented by Kutzner \cite{Keep2011}.
+This suggests a maximum rotation frequency at on the order of $10^3$, but this value requires so many assumptions that it's hardly worth mentioning.
 From \cite{Spinning2008}, the upper bound of a homogenous spherical virus with 10 MPa overall tensile strength appears to be about $10^9$ Hz.
 \footnote{\ghfile{documents/optical_centrifuge.ipynb}}
-
-An effect \cite{MicrowaveStimulated1985}\cite{Influence}\cite{Correlation1994}\cite{contribution2019}.
-These results are of excellent quality, with good thermal controls.
-\footnote{One founding researcher has been implicated in a research scandal; however, the Livermore report on the topic does not appear to be public, so we cannot evaluate the basis for these claims.} This effect appears to depend on dissolved oxygen\cite{Microwaves1987}\cite{Microwaves1988}, evidence against a mechanical effect.
-The lipid "transition temperature" - the point at which pores reseal - is also relevant.
-One report has been found to be a very strange artifact\cite{Effect1994a}.
-
-Custom single-lipid liposome surrogates appear to be relatively easy to produce and fill with a DNA tracer by sonication and dehydration\cite{Encapsulation1982}\cite{OPTIMIZATION2017}\cite{Liposome2014}.
-One problem encountered removing unencapsulated DNA, which typically requires ultracentrifugiation as precipitation of liposomes is more difficult.
-However, \cite{novela} appear to demonstrate that ethanol is satisfactory, and likely does not lead to DNA precipitation because of the lack of salt.
 
@@
 
-In our experiments with our homebrew spectrometer, we were able to produce many candidate resonances with perfectly justifiable modifications to post-processing, which raises interesting (but not novel\cite{Reanalysis2020}\cite{statistical2020}) questions regarding software quality in such research.
-\footnote{Perhaps developing the analysis software only on some sort of blind, synthetic data would offer a }
+Although not representative of careful, well-calibrated VNA testing because of the crudity of our homebrew spectrometer, we were able to produce many candidate resonances in our data with perfectly justifiable modifications to post-processing, which raises interesting (but not novel\cite{Reanalysis2020}\cite{statistical2020}) questions regarding software development in such conditions.
+\footnote{One solution might be to keep all data blinded while developing the analysis software, and use synthetic data to calibrate.
+One objection might be that the data often inform the required calibration; we might retort that if the technique is so sensitive that the calibration procedure cannot be known beforehand, a different technique should be used.}
 
+\end{multicols}
 \begin{figure}[H]
@@
 
+\begin{multicols}{1}
 Positive artifacts are very common in this field, and extreme care in experimental design appears to be required to produce any meaningful result.
@@
 
-T4 was selected because of large amount of history and safety of the host.
-T4 does not have a nucleocapsid; the charge distribution is likely stronger than.
-Phi6 \footnote{An interesting}.
-Some more useful surrogates may include Pseudomonas Phi 6\cite{Selection2017}, PM2,
-
-Viradel
+T4 was selected for biosafety reasons, and because of the large amount of structural data available.
+T4 does not have a nucleocapsid; the charge distribution is likely much stronger than other RNA-like viruses Phi 6\footnote{Naming organisms with greek letters makes literature review somewhat more difficult, because many search engines do not support Unicode.}.
+Some more useful surrogates may include Pseudomonas Phi 6\cite{Selection2017}, the lipid-bearing PM2, PRD1 or PR4\cite{Lipidcontaining1979} if the outer protein capsid is dissolved\cite{Bacteriophage2002}, \cite{Dissociation1993}, or lipid liposomes.
+Certain phages also allow efficient concentration without ultracentrifuge, either by PEG precipitation\cite{Rapid1970} and settling, or via VIRADEL\cite{GROWTH}\cite{Chemical1982}\cite{highly1988}\cite{AdsorptionElution1989}, by altering the zeta potential of a syringe filter.
 
@@
 A surplus Hammamatsu R4220 with HC123 current-limiting base at maximum sensitivity was used.
-A low-voltage silicon photomultiplier will probably be sufficient in most cases.
+A low-voltage silicon photomultiplier like ON Semi's C-Series SiPMs will probably be sufficient in most cases.
 
@@
 The capsid is weakened greatly by the base, relying on the "clamp proteins" hoc and soc.
+It was thought that, if the phage capsid was weakened, it might be easier to destroy electrically.
+A sodium carbonate-bicarbonate buffer was used to raise the pH.
+Run 9 and Weakened show these results.
 
@@
 In one case, base inactivation is found exactly as predicted; little inactivation is found in the other.
-We cannot explain this result.
+We cannot explain this result; it is possible that the buffer degraded somehow between experiments.
 
@@
 
-	The following is probably self-evident to all good scientists, and will ring worthy and overripe to those experienced; unfortunately, we only learned it during this project, so it seems worthwhile to make explicit.\\
+	The following is probably self-evident to all good scientists; unfortunately, we only learned it during this project, so it seems worthwhile to make explicit.\\
 
@@
 
-\begin{figure}[H]
-	%	\makebox[\textwidth][c]{
-	\centering
-	\subfloat[Direct electron beam detection]{
-		\includegraphics[width=0.3\textwidth]{direct_electron_beam}
-	}
-	\subfloat[Damage to the sensor, believed to be due to. ]{
-		\includegraphics[width=0.3\textwidth]{e_beam_damage_2}
-	}
-	\subfloat[]{
-		\includegraphics[width=0.3\textwidth]{e_beam_damage}
-	}
-	\caption{Second.}
-	\hfill
-
-\end{figure}
+%\begin{figure}[H]
+%	%	\makebox[\textwidth][c]{
+%	\centering
+%	\subfloat[Direct electron beam detection]{
+%		\includegraphics[width=0.3\textwidth]{direct_electron_beam}
+%	}
+%	\subfloat[Damage to the sensor, believed to be due to. ]{
+%		\includegraphics[width=0.3\textwidth]{e_beam_damage_2}
+%	}
+%	\subfloat[]{
+%		\includegraphics[width=0.3\textwidth]{e_beam_damage}
+%	}
+%	\caption{Second.}
+%	\hfill
+%	
+%\end{figure}
 

### 2021-03-05 documents/experiment_1_data.tex
More work on writing, need to add pulse counts

@@
 \subsection{Data from testing on bacteriophage T4}
+
 \begin{table}[h!]
@@
 		\hline
-		\multicolumn{3}{|c|}{\textbf{NF capillary}, 6 to 12 GHz, 10 or 20 us CW pulses 84.8 V/m pessimistic to 339 V/m optimistic} \\
+		\multicolumn{3}{|c|}{\textbf{NF capillary}, 6 to 12 GHz, 10 or 20 us CW pulses, 84.8 V/m to 339 V/m} \\
 		\hline
@@
 		\hline
-		\multicolumn{3}{|c|}{\textbf{NF capillary}, 6 to 12 GHz, phage degraded with basic buffer, 84.8 V/m pessimistic to 339 V/m optimistic} \\
+		\multicolumn{3}{|c|}{\textbf{NF capillary}, 6 to 12 GHz, phage degraded with basic buffer, 84.8 V/m to 339 V/m} \\
 		\hline
@@
 		\hline
-		\multicolumn{3}{|c|}{\textbf{NF capillary}, 6 to 12 GHz, 10 or 20 us CW pulses, 84.8 V/m pessimistic to 339 V/m optimistic} \\
+		\multicolumn{3}{|c|}{\textbf{NF capillary}, 6 to 12 GHz, 10 or 20 us CW pulses, 84.8 V/m to 339 V/m} \\
 		\hline
@@
 \end{table}
+%how many counts?
+
+Note the width of the electric field error bars.
+These are not meaningful random or systematic intervals; while we have tried to do our best with the instruments available, we cannot confidently assert that the field was within this range.
 

### 2021-03-05 documents/summary.tex
More work on writing, need to add pulse counts

@@
 \begin{figure}[H]
-%\captionsetup{singlelinecheck = false, justification=justified}
+\captionsetup{singlelinecheck = false, justification=justified}
 	\centering
@@
 		\includegraphics*[width=0.5\textwidth]{pulse_exposure_setup.JPG}
+
 	}
 	\subfloat[]{
-		\includegraphics*[width=0.5\textwidth]{eppenwolf_2.jpg}
+		\includegraphics*[width=0.5\textwidth]{eppenwolf_output_cap.jpg}
 	}
@@
 %	\caption{Simulation of a (largely ineffective) bronchoscopic method.}
-%	\caption{\\ \textit{Chengxiang} nanosecond pulse exposure jig.
-Pulser seen off the left.
-Pulse shaping plate not shown.
-Aluminum disc belongs to the scan-conversion digitizer, not used in this study.}
-%		\caption{\\ \textit{Eppenwolf} misguided pulsed X-Band microwave spectrometer used in this study. (cuvette shown was replaced by the same )}
+
+	\caption*{\small{\textit{Chengxiang} nanosecond pulse exposure jig. Aluminum disc belongs to the scan-conversion digitizer, not used in this study.}}
+		\caption*{\small{Pulsed X-Band microwave spectrometer used in this study.}}
+				\caption*{\small{FDTD simulation geometry of the 0.2 mm coplanar waveguide exposure cell. }}
+						\caption*{\small{The very pretty opalescent blue culture caused by E. coli B and X-gal.}}
+						\caption*{\small{Fluorescence reader used.}} 
 %	\caption{Brillouin precursor propagation through tissue (reproduced from section 6).\\
@@
 
-If the duration of exposure is sufficiently short that thermal and membrane breakdown effects can be neglected, tissue appears to withstand peak electric fields of great magnitude - above 1 nanosecond megavolt/meter, even in in-vivo studies - without severe acute effects(\cite{Repeated2020}\cite{Review2011} and below).
+If the duration of exposure is sufficiently short that thermal and membrane breakdown effects can be neglected, tissue appears to withstand peak electric fields of great magnitude - above 1 nanosecond megavolt/meter, even in in-vivo studies - without severe acute effects (\cite{Repeated2020}\cite{Review2011}\cite{DNA2004} and below).
 
-More specifically, the concept of driving a virus as a harmonic oscillator, as suggested by \cite{Efficient2015} has been previously considered only briefly \cite{MECHANICAL1968}\cite{Comment2004}\cite{Vibrational2009}\cite{Maximum2010}, perhaps first because in almost all cases structures in tissue are so over-damped by the surrounding solvent\cite{Vibrational2002}\cite{Biological2002}\cite{Biophysics2000}\cite{Viscous2000} as to have no non-zero resonant frequency at all \cite{dielectric1996}\cite{gabriel1996compilation}\wikinote{not in citation}\wikinote{discuss}; and second, because the charge distributions found in biology are too small for energies significantly above the thermal background to be absorbed via applied fields.
+The specific concept of driving a virus as a harmonic oscillator suggested by \cite{Efficient2015} has been previously considered only briefly \cite{MECHANICAL1968}\cite{Comment2004}\cite{Vibrational2009}\cite{Maximum2010}\cite{Effects1951}, perhaps first because in almost all cases structures in tissue are so over-damped by the surrounding solvent\cite{Vibrational2002}\cite{Biological2002}\cite{Biophysics2000}\cite{Viscous2000} as to have no non-zero resonant frequency at all \cite{dielectric1996}\cite{gabriel1996compilation}\wikinote{not in citation}\wikinote{discuss}; and second, because the charge distributions found in biology are too small for energies significantly above the thermal background to be absorbed via applied fields.
 
@@
 	\item The use of microwave absorption spectroscopy techniques somewhat similar to those which have previously shown resonance-like artifacts\cite{Resonances1987}.
-In particular, an effective charge of $q=10^7 e^-$ was found via this method, which is very large for a $10^9$ atom structure.
+In particular, an effective charge of $q=10^7 e^-$ was found via this method, which seems quite large for a $10^9$ atom structure.
 Genome and protein charge can hardly explain $10^5 e^-$ (see below), which would be reduced further by ionic screening.
 It appears that the potential energy of such a sphere of charge would exceed the observed metabolic burden to build a virus by a significant factor \footnote{
-		$$ U = \frac{3}{5}  \frac{1}{4 \pi \epsilon_0} \frac{Q^2}{R} \approx 2.3\text{e}^{-7} \text{ J} \approx 6 \times 10^{11}\  \text{ATP-equivalent} $$
+		$$ U = \frac{3}{5}  \frac{1}{4 \pi \epsilon_0} \frac{Q^2}{R} \approx 2.3
+		\times10^{-7} \text{ J} \approx 6 \times 10^{11}\  \text{ATP-equivalent} $$
 		%U = (3/5) * 1/(4*pi*electricConstant) *((1e7 electricCharge)^2 / 60 nanometers) = 2.30708e-7 J
@@
 Based on heating patterns seen in other experiments\cite{Effects1950}, the observed surface temperature rise does not seem to conclusively rule out a very localized thermal effect.
-	\item Therefore, without free-space dosimetry or simulation of power density to demonstrate otherwise, the frequency-selective inactivation could be explained by the frequency response of the power amplifier, antenna gain, and absorption of the cuvette.
+	\item Therefore, without free-space dosimetry or simulation of power density, the frequency-selective inactivation could possibly be explained by the frequency response of the power amplifier, antenna gain, and absorption of the cuvette.
 \end{itemize}
 
-It seems reasonable that a field with a strong positive publication bias\cite{Comprehensive2018}, in the presence of stringent peer review, might tend towards only the most abstruse and difficult to explain false-positive results.
+It seems reasonable that a field with a strong positive publication bias\cite{Comprehensive2018}, in the presence of stringent peer review, could tend towards only the most abstruse and difficult to explain false-positive results.
 
 However, if this is a thermal artifact, the fact that the spectrometry and inactivation data shown align perfectly is very difficult to explain; and so this chain of events seems unlikely.
+
+Permeabilization at high field strengths is not necessarily completely implausible. \cite{182015} observe a similar non-ionic photoporation effect.
 
@@
 
-Custom single-lipid liposome surrogates appear to be relatively easy to produce and fill with a DNA tracer by sonication and dehydration\cite{Encapsulation1982}\cite{OPTIMIZATION2017}\cite{Liposome2014}.
-We encountered one problem removing unencapsulated DNA, which typically requires ultracentrifugation as precipitation of liposomes is difficult.
-However, \cite{novela} appear to demonstrate that ethanol extraction is satisfactory.
-This likely does not lead to DNA precipitation because of the lack of salt.
-
 With\footnote{The dipole spring constant can be extracted from the resonant frequency and therefore from the speed of sound and $m^*$, the reduced mass ($k = \omega_{res}^2 m^2$).
 } relatively sane choices of solvent charge screening and resonant frequency, the energy absorbed by the whole virus per cycle at 5 MV/m might vary from $10^{-5}$ to 100 times the thermal energy $k_b T$.
-%TODO check effect of damping on hookes law energy.
 
 Compare to $~5 k_b T$ per protein for 1 capsid segment binding energy \cite{Energies2012} \cite{Weak2002} and 6 to 30 $k_b T$ to form a single pore in a lipid bilayer \cite{Atomistic2014}.
+\cite{Electrostatic2020a}
 %17 or 78 kJ/mol / (boltzmannConstant * 310 K) / avogadroConstant = 6.5 to 30.3 kT
+
+Brackley \cite{Electrostatic2020} describe various analytic representations of the charge screening about the virion with the Poisson-Boltzmann equation.
+
+From a force perspective, the $10^3$ genome charge easily provides the nanonewton force scale required\cite{Bacteriophage2004} to break capsids or envelopes in 5 MV/m fields; but accurate estimation of the capsid stress will require application of the Maxwell stress tensor \cite{Electrostatic2013}\cite{Deformation1991}
 
@@
 
-Poisson-Boltzmann implicit ionized solvents.
+Coupling FEM \cite{Electrostatic2020a}.
 
@@
 
-\end{multicols}
-\begin{figure}[H]
-	%	\makebox[\textwidth][c]{
-	\includesvg[width=\textwidth]{propagated_waveforms}
-	\caption{Brillouin precursor propagation through tissue (reproduced from section 6).\\
-		(a) Gaussian monopulse with 16 ps FWHM.\\
-		(b) Optimized 10 GHz sawtooth wave. Note the slight high-frequency ripple.\\ This has a frequency of approximately 1.5 GHz.\\
-		(c) Prototypical precursor 10 GHz sine burst.\\
-		(d) Continuous 10 GHz sine tone.}
-
-\end{figure}
-
-\begin{multicols}{1}
 Positive artifacts are very common in this field, and extreme care in experimental design appears to be required to produce any meaningful result.
@@
 Certain phages also allow efficient concentration without ultracentrifuge, either by PEG precipitation\cite{Rapid1970} and settling, or via VIRADEL\cite{GROWTH}\cite{Chemical1982}\cite{highly1988}\cite{AdsorptionElution1989}, by altering the zeta potential of a syringe filter.
+
+Custom single-lipid liposome surrogates appear to be relatively easy to produce and fill with a DNA tracer by sonication and dehydration\cite{Encapsulation1982}\cite{OPTIMIZATION2017}\cite{Liposome2014}.
+We encountered one problem removing unencapsulated DNA, which typically requires ultracentrifugation as precipitation of liposomes is difficult.
+However, \cite{novela} appear to demonstrate that ethanol extraction is satisfactory.
+This likely does not lead to DNA precipitation because of the lack of salt.
 
@@
 However, these initial tests were marred by the 1 uL sample volume in our initial cuvette attempts, our use of a domestic fridge to store phage, which unexpectedly froze regularly overnight, apparently reducing phage titer, along with our accidental use of T4r+ (not an "improved" T4r, as we believed, but rather a mutation away from rapid-lysis, meaning that the lysis behavior is far slower (see \cite{Spontaneous1946}).
-In our testing, lysis of T4r+ only occurred on plaque plates (where culture growth and log stage infectivity is maintained for many days)).
+In our testing, lysis of T4r+ only occurred on plaque plates [where culture growth and log stage infectivity is maintained for many days]).
 
@@
 E.
-coli produces the enzyme $\beta$-galactosidase to break lactose into glucose for metabolism.
-luciferase Promega Beta-Glo\cite{rapid2014}.
-However, one component contains a proprietary detergent designed to lyse cells and expose the galactosidase, counterproductive for phage use.
-Perhaps the detergent is not effective on bacteria, or the paper substrate that was used is sufficient.
+coli produces the enzyme $\beta$-galactosidase to break lactose into glucose for later metabolism.
+A luciferase-based luminescent assay, Promega Beta-Glo, was evaluated.
+One component of the beta-glo contains a proprietary detergent designed to lyse cells\cite{BETAGLO2003} and expose the enzyme, counterproductive for phage use.
+Perhaps the detergent is not effective on bacteria, or the paper substrate that w\cite{rapid2014}as used is sufficient.
 The detergent could perhaps be removed with BioBeads if this is desired.
 
-While undoubtedly essential and very effective for its intended purpose (quantifying lac operon activity), because of ambiguities in the rise and decay of the luminescence signal, short shelf life when the two components are mixed, concerns regarding the detergent, and cost, Beta-Glo compared unfavorably to direct fluorescence or X-Gal for this application.
+While undoubtedly essential and very effective for its intended purpose (accurately quantifying lac operon activity), because of ambiguities in the rise and decay of the luminescence signal, short shelf life after the two components are mixed, oxygen depletion in small cuvettes, concerns regarding the detergent, and cost, Beta-Glo compared unfavorably to direct fluorescence or X-Gal for this application.
+
+Positive control samples were put in a commercial pressure cooker to autoclave for either 6 or 20 minutes in an Eppendorf tube: the pressure was released after the cycle to prevent dilution.
+The flurophore was added after autoclaving.
 
@@
 A programmable syringe withdrew and pumped 50 uL of fluid at a constant rate through one of the coplanar channels, via a 4 cm long silicone capillary (McMaster-Carr \#51845K65) immersed in a 1.5 mL centrifuge tube using a 26 Ga Luer-lock (\#6710A76).
-Forcing phage through the capillary is similar to lysis with a French pressure cell press, but no such effects were seen.
+Forcing phage through the capillary is similar to lysis with a French pressure cell press, but no such effects were obviously seen.
 
@@
 
+For the Eppenwolf, the lower bound is the lowest voltage measured on the diode detector through the sweep (at 12 GHz), (raw unconverted voltage across frequency can be seen at\ghfile{firmware/eppenwolf/runs/phage_experiment_12/screenshot_192.168.0.38_2020-11-26_13:38:24.png} - it is not recorded which detector this was seen at) multiplied by the FDTD results for the coplanar waveguide voltage to channel field scaling factor.
+The upper bound is the maximum voltage seen over the frequency sweep multiplied by the same FDTD factor.
+
+\section{Discussion}
+
+%For the pulser, the lower bound is
+
 \begin{tcolorbox}
@@
 
-	By using yet another exposure cell, introducing an new set of unknown artifacts, we hamper this field; and so we encourage anyone who may wish to persue similar results to not use this arrangement, but instead one of the existing, well-characterized exposure systems mentioned below or in the literature.
+	By using yet another exposure cell, introducing a new set of unknown artifacts, we hamper this field; and so we encourage anyone who may wish to persue similar results to not use this arrangement, but instead one of the existing, well-characterized exposure systems mentioned below or in the literature.
 
@@
 
-Using Eppendorf tubes as. Impedimetric
+Before the HMC732 was used, a misguided effort was spent in trying to develop an inexpensive wideband tunable oscillator for spectrometry. This will be chronicled in the GitHub repository.
 
-Before the HMC732 was used, a misguided effort was spent in trying to develop an inexpensive wideband tunable oscillator.
+\end{multicols}
 
-Funded in part by the author's company, SafeSump Inc., and Ideal Consulting Inc., and the author's parents.
+\section{Acknowledgements}
+
+Funded in part by the author's company, SafeSump Inc., and Ideal Consulting Inc., and the author's parents. The author was at YorkU for the duration of this project.
 
@@
 Dainis' on microbiology.
-Thanks to legend of dispersion himself, Professor Oughstun at Vermont, Prof.
+Thanks to the legend of dispersion himself, Professor Oughstun at Vermont, Prof.
 Sarris at U of Toronto, both for excellent information on optimal dispersive pulses; Professor Voinigescu at UofT for a tip on experiment engineering; Sandra and colleagues at York library for spending an hour looking for the Gray paper; Prof.
@@
 
-Hamming be damned; despite the name below the abstract, this paper is of course entirely the result of circumstance, luck, and awesome friends.
+Hamming was wrong; despite the name above the abstract, this paper is of course entirely the result of circumstance, luck, and awesome friends.
+
+Special thanks to Alexandra Elbakyan and Aaron Swartz.
 
 \rule{\linewidth}{0.2pt}
-
-Thanks to
-
-\rule{\linewidth}{0.2pt}
-
-\end{multicols}
-
-One Very Important Thought
 

### 2021-03-06 documents/charge.tex
words
Text and prop improvements
More progress on summary
More details

@@
 
+\clearpage
 \section{Charge}
@@
 		Persson cite a polarization re-arrangement of electrons as a source of drag. Polarization-like effects are not expected. We have not followed up on this.
-\item 
+\item Donnan equilibrium
 \end{itemize}
@@
 \subsection{Empirical methods}
-
-Bosch \cite{Studies1985}
 
@@
 It is easy to determine an upper limit.
-
-Donnan equilibrium
 
@@
 
-At the largest scale, at a pH of 7 the net charges of the 4 proteins that comprise ~88\% of the protein mass\cite{Quantitative1981} of the virus (of the 11 coded for by the Influenza A genome) only contribute at most  $\approx 1 \times 10^5\  e^-$.
+At the largest scale, at a pH of 7, the net charges of the 4 proteins that comprise ~88\% of the protein mass\cite{Quantitative1981} of the virus (of the 11 coded for by the Influenza A genome) only contribute at most  $\approx 1 \times 10^5\  e^-$.
 
@@
 They also note that
+
+	Bosch \cite{Studies1985}
 

### 2021-03-06 documents/experiment_1_data.tex
More details

--- 2021-03-04 documents/experiment_1_data.tex
@@
 		\hline
-		\multicolumn{3}{|c|}{\textbf{NF capillary}, 6 to 12 GHz, 10 or 20 us CW pulses 84.8 V/m pessimistic to 339 V/m optimistic} \\
+		\multicolumn{3}{|c|}{\textbf{NF capillary}, 6 to 12 GHz, 10 or 20 us CW pulses, 85 V/m to 339 V/m expected} \\
 		\hline
@@
 		\hline
-		\multicolumn{3}{|c|}{\textbf{NF capillary}, 6 to 12 GHz, phage degraded with basic buffer, 84.8 V/m pessimistic to 339 V/m optimistic} \\
+		\multicolumn{3}{|c|}{\textbf{NF capillary}, 6 to 12 GHz, phage degraded with basic buffer, 85 V/m to 339 V/m expected} \\
 		\hline
@@
 		\hline
-		\multicolumn{3}{|c|}{\textbf{NF capillary}, 6 to 12 GHz, 10 or 20 us CW pulses, 84.8 V/m pessimistic to 339 V/m optimistic} \\
+		\multicolumn{3}{|c|}{\textbf{NF capillary}, 6 to 12 GHz, 10 or 20 us CW pulses} \\
 		\hline
@@
 		\hline
-		\multicolumn{3}{|c|}{\textbf{0.2 mm channel}, 6 to 12 GHz, 10 or 20 us CW pulses, 200 V/m pes. and 10.6 kV/m opt.} \\
+		\multicolumn{3}{|c|}{\textbf{0.2 mm channel}, 6 to 12 GHz, 10 or 20 us CW pulses, 200 V/m to 850 V/m exp., 10.6 kV/m pk} \\
 		\hline
@@
  		\hline
-		\multicolumn{3}{|c|}{\ntilde 0.2 mm channel, various pulse counts and termination, 0.155 MV/m to 5.6 MV/m} \\
+		\multicolumn{3}{|c|}{\ntilde 0.2 mm channel, various pulse counts and termination, 0.155 MV/m expected, 5.6 MV/m peak} \\
 		\hline 
@@
 
-		\multicolumn{3}{|c|}{\ntilde 0.03 mm channel, 0.2 uL/s, various pulse counts and termination, 1 MV/m to 38 MV/m} \\
+		\multicolumn{3}{|c|}{\ntilde 0.03 mm channel, 0.2 uL/s, various pulse counts and termination, 1 MV/m expected, 38 MV/m peak} \\
 		\hline
@@
 
-		\multicolumn{3}{|c|}{\ntilde 0.03 mm channel, basic buffer, tainted as pH may not have been 10.6, 1 MV/m to 38 MV/m} \\
+		\multicolumn{3}{|c|}{\ntilde 0.03 mm channel, basic buffer, tainted as pH may not have been 10.6, 1 MV/m exp., 38 MV/m pk} \\
 		\hline
@@
 \end{table}
+%how many pulses?
 
@@
 Data rounded to the nearest thousand fluorescence photon counts per 10 seconds.
-Larger numbers are presumed to correlate with greater capsid damage.
+Larger numbers are presumed to correlate with greater capsid damage (see Autoclaved).
 
-See notes on experiment design and data collection in main body.
+Note the width of the electric field bounds.
+These are not meaningful random or systematic intervals; we can only confidently assert that the field did not exceed the peak value at any point within the channel.
+Expected values based on FDTD simulation and voltage; peak based on channel width and voltage.
+
+See notes on experiment design and data collection in main body and GitHub supplemental.
 

### 2021-03-06 documents/summary.tex
More details

@@
 
-	\caption*{\small{\textit{Chengxiang} nanosecond pulse exposure jig. Aluminum disc belongs to the scan-conversion digitizer, not used in this study.}}
-		\caption*{\small{Pulsed X-Band microwave spectrometer used in this study.}}
-				\caption*{\small{FDTD simulation geometry of the 0.2 mm coplanar waveguide exposure cell. }}
-						\caption*{\small{The very pretty opalescent blue culture caused by E. coli B and X-gal.}}
-						\caption*{\small{Fluorescence reader used.}} 
+	\caption*{\small{\\
+	(a) \textit{Chengxiang} nanosecond pulse exposure jig. Aluminum disc belongs to the scan-conversion digitizer, not used in this study.\\
+	(b) Pulsed X-Band microwave spectrometer used.\\
+	(c) Simulation of a (largely ineffective) bronchoscopic method.\\
+	(d) FDTD simulation geometry of the 0.2 mm coplanar waveguide exposure cell.\\
+	(e)	The very pretty opalescent blue culture caused by E. coli B uptake of X-Gal.\\
+	(f) Fluorescence reader used.\\
+}}
+%		\caption*{\small{}}
+%				\caption*{\small{FDTD simulation geometry of the 0.2 mm coplanar waveguide exposure cell. }}
+%						\caption*{\small{The very pretty opalescent blue culture caused by E. coli B and X-gal.}}
+%						\caption*{\small{Fluorescence reader used.}} 
 %	\caption{Brillouin precursor propagation through tissue (reproduced from section 6).\\
@@
 
-We have some minor questions regarding experimental technique in the original papers that can only be addressed by more extensive replication studies, and luckily are due to be answered by other groups\cite{Generating}, so we try not to defer greatly to their observations.
+%We have some minor reservations regarding experimental technique in the original papers that can only be addressed by more extensive replication studies, and luckily are due to be answered by other groups\cite{Generating}, so we try not to defer greatly to their observations.
 
 These studies are all founded on the idea that some large-scale structural difference between viruses and all host cellular structures might usable as leverage to selectively inactivate the virus by some physical - rather than biological - means.
-For example, such an inactivation "window" between host cell and virion damage has been found in certain wavelengths of CW Far UV\cite{Germicidal2017} - but also apparently in certain modulated UV pulses\cite{Use1987a}\cite{Can1993}, and also sporadically reported for simple thermal treatment\cite{Summary}; however, the differential inactivation modes found so far do not appear to be of much use in the clinic.
+For example, such an inactivation "window" between host cell and virion damage has been found in certain wavelengths of CW Far UV\cite{Germicidal2017} - but also apparently in certain modulated UV pulses\cite{Use1987a}\cite{Can1993}, and also sporadically reported for simple thermal treatment\cite{Summary}; however, the modes exhibiting differential inactivation that have been found so far do not appear to be of particular use in the clinic.
+
+Some possible minor shortcomings of the original experiments are due to be addressed by other groups\cite{Generating}, so we try not to defer greatly to those observations.
 
 A few well-established non-resonant non-thermal effects caused by extreme electric fields have already been put to practical use.
-Electroporation\cite{Electroporation1988} is a common laboratory procedure in which an enormous electric field causes ions in solution to diffuse across a host cell's membrane, capacitively charging it.
+Electroporation\cite{Electroporation1988}, now a common laboratory procedure, occurs when an enormous electric field causes ions in solution to diffuse across a cell membrane, capacitively charging it.
 This leads to a change in lipid conformation, reversibly rendering the membrane permeable (among other, more subtle mechanisms; the minutia of poration are extraordinarily complex and beyond the author's understanding\cite{Theoretical2007}).
@@
 Compare to $~5 k_b T$ per protein for 1 capsid segment binding energy \cite{Energies2012} \cite{Weak2002} and 6 to 30 $k_b T$ to form a single pore in a lipid bilayer \cite{Atomistic2014}. 
-\cite{Electrostatic2020a}
 %17 or 78 kJ/mol / (boltzmannConstant * 310 K) / avogadroConstant = 6.5 to 30.3 kT
 
-Brackley \cite{Electrostatic2020} describe various analytic representations of the charge screening about the virion with the Poisson-Boltzmann equation.
+With a relaxation time on the order of 500 ps, it is somewhat difficult to imagine that this energy will be sufficiently concentrated in the capsid to be destructive.
+After the relaxation time, only the mechanical effects that were induced can remain, unless some progressive chemical or fatigue-like degradation occurs.
 
-From a force perspective, the $10^3$ genome charge easily provides the nanonewton force scale required\cite{Bacteriophage2004} to break capsids or envelopes in 5 MV/m fields; but accurate estimation of the capsid stress will require application of the Maxwell stress tensor \cite{Electrostatic2013}\cite{Deformation1991}
+Brackley \cite{Electrostatic2020} describe various analytic representations of the charge screening about the virion with the Poisson-Boltzmann equation; by translating the obtained charge into a steady-state Poisson simulation (ions will not migrate in nanosecond pulse timescales), a relatively representative simulation may be obtained\footnote{implementation attempted at \ghfile{/math/mathematica/analytic_force.nb}}.
 
-On the other hand, such a sub-angstrom movement can only induce approx.
-0.05\% deflection of the capsid, whereas a general value for the rupture of host cells is about 3\% deflection\cite{Electromechanical1989}.
+\end{multicols}
+\begin{autem}
+	autem, discuss\\
+	At the risk of seeming a fool, what is the correct metric for the charge quantity being discussed?
+We are interested in the stress produced by a certain arbitrary distribution of charge.
+Assuming a spherically symmetric virus composed of two charged shells, there is no intrinsic dipole moment.
+Polarizability or induced dipole moment are not obviously relevant; stress could be produced in an extremely stiff structure with no electron mobility.
+The virion has little net charge.
+Multipole expansions are not clearly relevant.
+\end{autem}
+\begin{multicols}{1}
+From a force perspective, the $10^3$ genome charge easily provides the nanonewton force scale required\cite{Bacteriophage2004} to break capsids or envelopes in 5 MV/m fields; but accurate estimation of the capsid stress will likely require application of the Maxwell stress tensor \cite{Electrostatic2013}\cite{Deformation1991}.
+
+On the other hand, such a sub-angstrom movement can only induce approximately a 0.05\% deflection of the capsid, whereas a general value for the rupture of host cells is about 3\% deflection\cite{Electromechanical1989}.
 The stiffness of the genome could be used to explain this.
-With a relaxation time on the order of 500 ps, it is difficult to imagine that this energy will be sufficiently concentrated in the capsid to be destructive.
-After the relaxation time, only the mechanical effects that were induced can remain.
 
-Modelling this sort of multi-scale inactivation mechanism involving the collective motion of some $10^9$ atoms poses a significant computational and theoretical hassle, which has far exceeded our capabilities.
+Accurately modelling this sort of multi-scale inactivation mechanism involving the collective motion of some $10^9$ atoms simultaneously with fatigue from atomic dislocations\cite{Physical2010} and reactive oxidation effects poses a significant computational and theoretical hassle, which has far exceeded our capabilities.
 
-Coarse-graining; but, as with all simulations, the problem must be set up with great care and experience (polarizable water; proper heat-bath damping coefficients and choice of integrator)\cite{Membrane2016}, and with an understanding of possible failure modes; we did not trust our abilities to produce correct results.
-Parametrizing based on all-atom simulations of small capsid segments or proteins \cite{Elucidating2009}.
+All-atom simulations of whole capsids are now possible, but existing pipelines tend to lack genome or nucleocapsid\cite{Mesoscale2020}\cite{Physical2017} and are extremely computationally demanding.
+
+Coarse-graining is one route out; but, as with all abstractions in simulations, the problem must be set up with great care and experience (polarizable water; proper heat-bath damping coefficients and choice of integrator)\cite{Membrane2016}\cite{Determining2014}, and with an understanding of possible failure modes; we did not trust our abilities to produce correct results.
+An illustrative GROMACS simulation of a liposome, trajectories fourier transformed with \cite{TRAVIS2011}, was used to determine some parameters\footnote{implemented at \ghfile{/biology/simulation/GROMACS/BUMPy_bilayer/}, see supplemental}.
+
+Parameterizing coarse bead-spring models based on all-atom simulations of small capsid segments or proteins \cite{Elucidating2009} is another technique.
+In this case, DNA/RNA can be represented by homogeneous beads restrained by Lennard-Jones forces \cite{Communication2013}.
 Mechanically reasonable coarse-grained models have recently been published for SARS-NCoV-2\cite{Multiscale2020}.
-DNA can be represented by homogeneous beads restrained by Lennard-Jones forces \cite{Communication2013}.
 Finite-element analysis \cite{Finite2008}
 
-Coupling FEM \cite{Electrostatic2020a}.
+Coupling finite-element and Poisson-Boltzmann\cite{Electrostatic2020a}.
 
-Data on the charge distribution of the virion can be obtained by and 2D-PAGE relative protein composition - or even perhaps directly, via extraction from whole-virion CryoEM maps, because of the charge-sensitive nature of the technique \cite{Identification2018}\cite{Electrostatic2020}.
+An approximate charge distribution of the proteins of the virion can be obtained by multiplying primary structure charges (in our case, extracted \cite{CIDER2017}, or (\cite{complete2003})) by observed protein contribution to total MW\cite{Quantitative1981}, old 2D-PAGE gels \cite{Influenza1978}\cite{Structurea} (which also provides an estimate of the variation in the charge, important for accurate spectroscopy, see supplemental) - or perhaps directly via extraction from whole-virion CryoEM maps, enabled by the charge-sensitive nature of the technique \cite{Identification2018}\cite{Electrostatic2020}.
 This has not yet been implemented in any software tools and seems quite tricky.
+
 The genome charge is almost entirely neutralized by the nucleocapsid.
 
-GROMACS simulations of liposomes, trajectories fourier transformed with \cite{TRAVIS2011}.
-
-In our cursory testing, Bacteriophage T4 did not appear to be lysed by 10 microsecond pulses between 6 and 12 GHz at about 70 V/m, nor, exploring non-resonant inactivation, did nanosecond pulses up to 1 MV/m appear to have any effect.
+In our cursory testing, Bacteriophage T4 did not appear to be lysed by 10 microsecond pulses between 6 and 12 GHz at about $10^2$ to $10^3$ V/m, nor, exploring non-resonant inactivation, did nanosecond pulses up to a few MV/m appear to have any effect.
 Note that neither of these regimes overlap with the results of the previous studies.
@@
 A rotational drag coefficient can extracted from MD simulation\cite{Evaluating2017}.
-We simulated a 30 nm lipid liposome using the MARTINI coarse-grained \cite{MARTINI2007} lipid force fields with GROMACS\cite{GROMACS2005}' torque measurement feature, kindly implemented by Kutzner \cite{Keep2011}.
-This suggests a maximum rotation frequency at on the order of $10^3$, but this value requires so many assumptions that it's hardly worth mentioning.
+We simulated a 30 nm lipid liposome using the MARTINI coarse-grained \cite{MARTINI2007}\cite{BUMPy2018}\cite{Tsjerk2020} lipid force fields with GROMACS\cite{GROMACS2005}' torque measurement feature, kindly implemented by Kutzner \cite{Keep2011}.
+This suggests a maximum rotation frequency on the order of $10^3$, but this value requires so many assumptions that it's hardly worth mentioning.
 From \cite{Spinning2008}, the upper bound of a homogenous spherical virus with 10 MPa overall tensile strength appears to be about $10^9$ Hz.
@@
 
-Dispersion and Brillouin precursors do offer a significant improvement in loss through tissue, and the required electrical waveforms appear to be synthesizeable by variable-impedance or stub transmission-line pulse shaping\cite{Coaxial1985}\cite{Arbitrarya}.
+Dispersion and Brillouin precursors do offer a means to produce a significant improvement in loss through tissue, and the required electrical waveforms appear to be synthesizeable by variable-impedance or stub transmission-line pulse shaping\cite{Coaxial1985}\cite{Arbitrarya}.
 
@@
 
-T4 was selected for biosafety reasons, and because of the large amount of structural data available.
-T4 does not have a nucleocapsid; the charge distribution is likely much stronger than other RNA-like viruses Phi 6\footnote{Naming organisms with greek letters makes literature review somewhat more difficult, because many search engines do not support Unicode.}.
+T4r was selected for biosafety reasons, and because of the large amount of structural data available.
+T4\cite{History1995} does not have a nucleocapsid; the charge distribution is likely much stronger than other RNA-like viruses Phi 6\footnote{Naming organisms with greek letters makes literature review somewhat more difficult, because many search engines do not support Unicode.}.
 Some more useful surrogates may include Pseudomonas Phi 6\cite{Selection2017}, the lipid-bearing PM2, PRD1 or PR4\cite{Lipidcontaining1979} if the outer protein capsid is dissolved\cite{Bacteriophage2002}, \cite{Dissociation1993}, or lipid liposomes.
@@
 
-30 atmospheres.
-When phage is rapidly immersed in solution of high osmotic strength, the active system that maintains osmotic equilibrium is overwhelmed, and the resulting force ruptures the capsid.
-\cite{Osmotic2003}, and breaks at a pressure differential of 100 atm.
+When phage is rapidly immersed in solution of high osmotic strength, the active system that maintains osmotic equilibrium is overwhelmed, and the resulting pressure ruptures the capsid when it exceeds 100 atm \cite{Osmotic2003}.
 By $\sigma = pr / 2t $ t = 5.7 nm\cite{Head1988} and r=60 nm, capsid strength should be about 53 MPa, less than the 100 to 300 MPa cited by \cite{Bacteriophage2004}.
 %((100 atm * 60 nanometers) / (2*(5.7 nanometers))) to MPa
+
+\subsection{Experiment methods}
 
@@
 coli produces the enzyme $\beta$-galactosidase to break lactose into glucose for later metabolism.
-A luciferase-based luminescent assay, Promega Beta-Glo, was evaluated.
+A luciferase-based luminescent assay, Promega Beta-Glo, was evaluated, as described in\cite{rapid2014}.
 One component of the beta-glo contains a proprietary detergent designed to lyse cells\cite{BETAGLO2003} and expose the enzyme, counterproductive for phage use.
-Perhaps the detergent is not effective on bacteria, or the paper substrate that w\cite{rapid2014}as used is sufficient.
+Perhaps the detergent is not effective on bacteria, or the paper substrate that was used is sufficient.
 The detergent could perhaps be removed with BioBeads if this is desired.
 
-While undoubtedly essential and very effective for its intended purpose (accurately quantifying lac operon activity), because of ambiguities in the rise and decay of the luminescence signal, short shelf life after the two components are mixed, oxygen depletion in small cuvettes, concerns regarding the detergent, and cost, Beta-Glo compared unfavorably to direct fluorescence or X-Gal for this application.
+While undoubtedly essential and very effective for its intended purpose (accurately quantifying lac operon activity), because of ambiguities in the rise and decay of the luminescence signal, short shelf life after the two components are mixed, oxygen depletion in small cuvettes, concerns regarding the detergent, and cost, Beta-Glo compared unfavorably to direct fluorescence or X-Gal for this specific application.
 
@@
 
-If a fast laser is available, Auston switches appear to be equally effective.
-
-\subsection{Notes}
-
 %
@@
 
+The fluor-meter printed a constant stream of results, all within the random error between capture windows $\sigma=0.5$ kcounts. Only after most of the data was taken was it realized how dumb this was.
+
 Data rounded to the nearest thousand photon counts per 10 seconds. %thoroughly characterized.
+
+If a fast laser is available, Auston switches appear to be equally effective.
+
+Repeatability between test conditions was not terrific. The source of the \ntilde 5000 count variation between some equivalent samples, and between "blank" and "sham", is not known.
 
@@
 'sham' indicates a blank sample that was injected through the capillary identically to the treatment samples, except with either the VCO or Marx pulser disabled.
-
-Repeatability between test conditions was not terrific. The source of the \ntilde 5000 count variation between some equivalent samples, and between "blank" and "sham", is not known.
 
@@
 \cite{Nanosecond2006} and simulations seem to suggest that this is not a serious problem, but it is possible that the field in much of the channel was much lower than predicted.
-
-The fluor-meter printed a constant stream of results, all within the random error between capture windows $\sigma=0.5$ kcounts. Only after most of the data was taken was it realized how dumb this was.
 
@@
 The upper bound is the maximum voltage seen over the frequency sweep multiplied by the same FDTD factor.
-
-\section{Discussion}
 

### 2021-03-06 documents/brillouin_pulse_math.tex
More work on writing, need to add pulse counts
Removed README disclaimer

@@
 We used parameters from the IT.IS Foundation tissue database\cite{Tissue2018a}.
+IT.IS Foundation computational phantom 'duke V3.0' was used, \cite{Duke2014}.
 
@@
 where $\int e^{j \omega t} d\omega$ is the inverse fourier transform.
-At this point, you could choose to perform a second integral over the time-domain Greens function solution to the harmonic oscillator\cite{Complex2020}, or substitute
+At this point, you could choose to perform a second integral over the time-domain Greens function solution to the harmonic oscillator\cite{Complex2020} - or straightforwardly integrate over the frequency-domain Greens function.
 
@@
 
-Note the ni specifically in the complex conjugate!
+\footnote{Note the ni specifically in the complex conjugate!}
 
@@
 
-However, a maximum absolute value constraint produces fantastic results.
+However, a maximum absolute value constraint appears to produce fantastic results.
 

### 2021-03-06 documents/summary.tex
Removed README disclaimer

@@
 
-It seems reasonable that a field with a strong positive publication bias\cite{Comprehensive2018}, in the presence of stringent peer review, could tend towards only the most abstruse and difficult to explain false-positive results.
+\footnote{It is interesting to consider that a field with a strong positive publication bias\cite{Comprehensive2018}, in the presence of stringent peer review, could unintentionally tend towards a literature populated with only the most abstruse and difficult to explain false-positive results.}
 
@@
 	autem, discuss\\
-	At the risk of seeming a fool, what is the correct metric for the charge quantity being discussed?
+	At the risk of seeming a fool, what is the most useful metric for the charge quantity being discussed?
 We are interested in the stress produced by a certain arbitrary distribution of charge.
@@
 
-Accurately modelling this sort of multi-scale inactivation mechanism involving the collective motion of some $10^9$ atoms simultaneously with fatigue from atomic dislocations\cite{Physical2010} and reactive oxidation effects poses a significant computational and theoretical hassle, which has far exceeded our capabilities.
+Accurately modelling this sort of multi-scale inactivation mechanism involving the collective motion of some $10^9$ atoms, possibly simultaneously with fatigue from atomic dislocations\cite{Physical2010} and reactive oxidation effects, poses a significant computational and theoretical hassle, which has far exceeded our capabilities.
 
@@
 Mechanically reasonable coarse-grained models have recently been published for SARS-NCoV-2\cite{Multiscale2020}.
-Finite-element analysis \cite{Finite2008}
-
-Coupling finite-element and Poisson-Boltzmann\cite{Electrostatic2020a}.
+Finite-element analysis in biology is also somewhat common \cite{Finite2007}; coupled finite-element and Poisson-Boltzmann\cite{Electrostatic2020a} seems particularly effective.
 
@@
 
-Early albanese with mm used vircator diodes.
+%Early albanese with mm used vircator diodes.
 
-What quantity is referred to; induced dipole due to polarization or ionic.
-
-T4r was selected for biosafety reasons, and because of the large amount of structural data available.
-T4\cite{History1995} does not have a nucleocapsid; the charge distribution is likely much stronger than other RNA-like viruses Phi 6\footnote{Naming organisms with greek letters makes literature review somewhat more difficult, because many search engines do not support Unicode.}.
-Some more useful surrogates may include Pseudomonas Phi 6\cite{Selection2017}, the lipid-bearing PM2, PRD1 or PR4\cite{Lipidcontaining1979} if the outer protein capsid is dissolved\cite{Bacteriophage2002}, \cite{Dissociation1993}, or lipid liposomes.
+E.
+coli phage T4r was selected for biosafety reasons, and because of the large amount of experience\cite{History1995} and structural data available.
+T4 does not have a nucleocapsid; the charge distribution is likely much stronger than other RNA-like viruses Phi 6\footnote{Naming organisms with greek letters makes literature review somewhat more difficult, because many search engines do not support Unicode.}.
+Some more useful surrogates may include Pseudomonas Phi 6\cite{Selection2017}, the lipid-bearing PM2, PRD1 or PR4\cite{Lipidcontaining1979} if the outer protein capsid is dissolved\cite{Bacteriophage2002}, \cite{Dissociation1993}; or synthetic lipid liposomes.
 Certain phages also allow efficient concentration without ultracentrifuge, either by PEG precipitation\cite{Rapid1970} and settling, or via VIRADEL\cite{GROWTH}\cite{Chemical1982}\cite{highly1988}\cite{AdsorptionElution1989}, by altering the zeta potential of a syringe filter.
@@
 Custom single-lipid liposome surrogates appear to be relatively easy to produce and fill with a DNA tracer by sonication and dehydration\cite{Encapsulation1982}\cite{OPTIMIZATION2017}\cite{Liposome2014}.
-We encountered one problem removing unencapsulated DNA, which typically requires ultracentrifugation as precipitation of liposomes is difficult.
-However, \cite{novela} appear to demonstrate that ethanol extraction is satisfactory.
+We encountered one problem in removing unencapsulated DNA, which typically requires ultracentrifugation as precipitation of liposomes is difficult.
+However, \cite{novela} appear to demonstrate that ethanol extraction is satisfactory - we have not tested this.
 This likely does not lead to DNA precipitation because of the lack of salt.
 
-When phage is rapidly immersed in solution of high osmotic strength, the active system that maintains osmotic equilibrium is overwhelmed, and the resulting pressure ruptures the capsid when it exceeds 100 atm \cite{Osmotic2003}.
+When phage is rapidly immersed in solution of high osmotic strength, the active system that maintains osmotic equilibrium is overwhelmed, and the resulting pressure ruptures the capsid when it exceeds about 100 atm \cite{Osmotic2003}.
 By $\sigma = pr / 2t $ t = 5.7 nm\cite{Head1988} and r=60 nm, capsid strength should be about 53 MPa, less than the 100 to 300 MPa cited by \cite{Bacteriophage2004}.
@@
 
-PMT dark counts and ambient light were removed by synchronous photon counting - add when light is on, subtract when light is off.
+PMT dark counts and ambient light were removed by synchronous photon counting\cite{Measurement1966} - add when light is on, subtract when light is off.
 This cannot be done with luminescence.
@@
 
-Nephelometry (right-angle light scatter detection) and turbidimetry (transmission) using CdS and LtoF sensors; despite being visible to the naked eye "clean" 2 hour E.
+%Nephelometry (right-angle light scatter detection) and turbidimetry (transmission) using CdS and LtoF sensors; despite being visible to the naked eye "clean" 2 hour E.
 coli cultures 1.5 mL.
@@
 One component of the beta-glo contains a proprietary detergent designed to lyse cells\cite{BETAGLO2003} and expose the enzyme, counterproductive for phage use.
-Perhaps the detergent is not effective on bacteria, or the paper substrate that was used is sufficient.
+Perhaps the detergent is not effective on bacteria, or the paper substrate that was used in the previous work was sufficient to bind the detergent.
 The detergent could perhaps be removed with BioBeads if this is desired.
@@
 
-A thin layer of silicone conformal coating was applied to the 0.2 mm waveguide to avoid the copper ion artifact, but this could not be done on the 0.05 mm waveguide.
+A thin layer of silicone conformal coating was applied to the 0.2 mm waveguide to avoid the copper ion artifact, but this could not be done on the 0.03 mm waveguide.
 
@@
 
-This paper would have been absolutely impossible without the support of thousands of open-source software packages, ranging from monolithic state-supported tools like Paraview to poorly-compensated but equally invaluable scripts like zonca.
+This paper would have been absolutely impossible without the support of thousands of open-source software packages, ranging from monolithic state-supported tools like Paraview to poorly-compensated but equally invaluable scripts like zonca/qucs\cite{Modeling2010}.
 A special thanks to the dedicated authors that develop and maintain these tools, and especially to those who choose not to put them behind a paywall.

### 2021-03-08 documents/brillouin_pulse_math.tex
Adding supplemental

@@
 
-Based on Yang's inactivation thresholds, for instance, at 9 GHz, assuming that a torso is about 10 penetration depths in radius and the hypothetical Brillouin train drives the virus equally effectively as, implementing a precursor would decrease the field required at the skin to a perfectly practicable 1 kV/m, rather than an air-ionizing 6.6 MV/m ($\frac{1}{\sqrt{10}}=0.316$ versus $e^{-10}=4.5e^{-5}$).
+Based on Yang's inactivation thresholds, for instance, at 9 GHz, assuming that a torso is about 10 penetration depths in radius and the hypothetical Brillouin train drives the virus equally effectively as a pure sine, implementing a precursor would decrease the field required at the skin to a perfectly practicable 1 kV/m, rather than an air-ionizing 6.6 MV/m ($\frac{1}{\sqrt{10}}=0.316$ versus $e^{-10}=4.5e^{-5}$).
 
@@
 
-\begin{figure}[H]
-	%	\makebox[\textwidth][c]{
-	\includesvg[width=\textwidth]{muscle_pulse_8cm_minimize_test2}
-	\caption{}
-\end{figure}
+%\begin{figure}[H]
+%	%	\makebox[\textwidth][c]{
+%	\includesvg[width=\textwidth]{muscle_pulse_8cm_minimize_test2}
+%	\caption{}
+%\end{figure}
 

### 2021-03-08 documents/summary.tex
Adding supplemental

@@
 
-When phage is rapidly immersed in solution of high osmotic strength, the active system that maintains osmotic equilibrium is overwhelmed, and the resulting pressure ruptures the capsid when it exceeds about 100 atm \cite{Osmotic2003}.
+When phage is rapidly immersed in solution of differing osmotic strength, the active system that maintains osmotic equilibrium is overwhelmed, and the resulting pressure ruptures the capsid when it exceeds about 100 atm \cite{Osmotic2003}.
 By $\sigma = pr / 2t $ t = 5.7 nm\cite{Head1988} and r=60 nm, capsid strength should be about 53 MPa, less than the 100 to 300 MPa cited by \cite{Bacteriophage2004}.
@@
 PMT dark counts and ambient light were removed by synchronous photon counting\cite{Measurement1966} - add when light is on, subtract when light is off.
+The fluorescence excitation light was 50\% square-wave modulated at 100 khz.
 This cannot be done with luminescence.
@@
 
-For the Eppenwolf, the lower bound is the lowest voltage measured on the diode detector through the sweep (at 12 GHz), (raw unconverted voltage across frequency can be seen at\ghfile{firmware/eppenwolf/runs/phage_experiment_12/screenshot_192.168.0.38_2020-11-26_13:38:24.png} - it is not recorded which detector this was seen at) multiplied by the FDTD results for the coplanar waveguide voltage to channel field scaling factor.
+For the Eppenwolf, the lower bound is the lowest voltage measured on the diode detector through the sweep (at 12 GHz), (raw unconverted voltage across frequency can be seen at\ghfile{/firmware/eppenwolf/runs/phage_experiment_12/screenshot_192.168.0.38_2020-11-26_13:38:24.png} - it is not recorded which detector this was seen at) multiplied by the FDTD results for the coplanar waveguide voltage to channel field scaling factor.
 The upper bound is the maximum voltage seen over the frequency sweep multiplied by the same FDTD factor.
@@
 
-Funded in part by the author's company, SafeSump Inc., and Ideal Consulting Inc., and the author's parents. The author was at YorkU for the duration of this project.
+Funded in part by the author's company, SafeSump Inc., and Ideal Consulting Ltd., and the author's parents. The author was at YorkU for the duration of this project.
 

### 2021-03-08 documents/supplemental.tex
Adding supplemental

@@
 \clearpage
-\rule{\linewidth}{0.2pt}
+%\rule{\linewidth}{0.2pt}
+%
+%
+%There seems to be a discrepancy between \cite{Efficient2015} and our reading of [C95.1-2005].
+%
+%They use a threshold in open public space of $100(f/3)^{1/5} \text{ W/m}^2$. The 115 W @ 6 GHz figure they provide corresponds to this equation with a coefficient of 100.
+%
+%For Table 9, general public, the equation is $18.56 (f)^{0.699} \text{ W/m}^2$, or $64.93 \text{ W}/\text{m}^2$ @ 6 GHz. 
+%
+%Different versions of the IEEE standard have used equations of equivalent form but with different coefficients [Wu 2015]; it is entirely possible that we have retrieved the wrong standard.
+%
+%\rule{\linewidth}{0.2pt}
 
-There seems to be a discrepancy between \cite{Efficient2015} and our reading of [C95.1-2005].
+\section{Wherein a wideband oscillator is designed}
 
-They use a threshold in open public space of $100(f/3)^{1/5} \text{ W/m}^2$. The 115 W @ 6 GHz figure they provide corresponds to this equation with a coefficient of 100.
-
-For Table 9, general public, the equation is $18.56 (f)^{0.699} \text{ W/m}^2$, or $64.93 \text{ W}/\text{m}^2$ @ 6 GHz.
-
-Different versions of the IEEE standard have used equations of equivalent form but with different coefficients [Wu 2015]; it is entirely possible that we have retrieved the wrong standard.
-
-\rule{\linewidth}{0.2pt}
-
-\PRLsep{{\itshape Wherein an oscillator is designed }}
-
-Many
-
-Three incorrect pieces of information conspired to lead us to try to develop an inexpensive ultrawideband oscillator.
+Several incorrect pieces of information conspired to lead us to try to develop an inexpensive ultrawideband oscillator.
 
 \begin{itemize}
+	\item The
 	\item The assumption that a broadband frequency sweep would drastically improve the inactivation threshold, and moreover that 
@@
 \end{itemize}
+
+Besides the AD (formerly Hittite) HMC732 device, ADF5355 and lmx2615
 

### 2021-03-12 documents/fluorescence.tex
fucker
I keep re-writing things but they don't get any better!
Text and prop improvements
Tersenating
Rewording text slightly in case biorxiv is a good idea

@@
 
+the base had integral overcurrent protection, which was triggered a few times during development - a very useful
+
 For one thing, GelGreen appears to be eminiently stable - samples can be stored for long periods of time; pre-mixed batches.
 
-\subsection{Light source}
+Unlike luminescence techniques,
+
+%\subsubsection{Light source}
 
@@
 
+it has been noted that water is a good fluorescence quencher and that this might be how
+
 If time-domain filtering is sufficient,
@@
 
+The fiber optic \cite{vurek1982nanoliter}
+
 You might be wondering why the filters are even required - why not just subtract the excitation bleed-through with a control?
@@
 
-Silicon photomultipliers like ON's C-Series are almost certainly sufficient for this application, eliminating the HV requirements of PMTs at the cost of a higher dark count and slightly smaller active area.
+Silicon photomultipliers like ON's C-Series are almost certainly sufficient for this application, eliminating the HV requirements of PMTs at the cost of a smaller active area.
 
@@
 
-Another neat technique is to add
+Another neat technique is to add I/Q
 

### 2021-03-12 documents/summary.tex
Rewording text slightly in case biorxiv is a good idea

@@
 Electroporation\cite{Electroporation1988}, now a common laboratory procedure, occurs when an enormous electric field causes ions in solution to diffuse across a cell membrane, capacitively charging it.
-This leads to a change in lipid conformation, reversibly rendering the membrane permeable (among other, more subtle mechanisms; the minutia of poration are extraordinarily complex and beyond the author's understanding\cite{Theoretical2007}).
+This leads to a change in lipid conformation, reversibly rendering the membrane permeable.
+This is one among other, more subtle mechanisms; the minutia of poration are extraordinarily complex and beyond the author's current understanding\cite{Theoretical2007}.
 
 Therapies based on irreversible electroporation\cite{Nonthermal2013}\cite{Lipid2017} have recently been used in the clinic\cite{Irreversible2013} for tumor ablation.
-There is much discussion on electroporation as an alternative to viral vectors, but we have not yet found any discussion of clinical treatment of viral infection with these conventional electroporation therapies.% In vitro there is evidence to suggest that sub-cellular effects take place under truly tremendous fields.
+There is much discussion on electroporation as an alternative to viral vectors, but we have found surprisingly little discussion on clinical treatment of viral infection with these conventional electroporation therapies.% In vitro there is evidence to suggest that sub-cellular effects take place under truly tremendous fields.
+
+Long pulses at $\approx10$ MV/m appear to electroporate enveloped viruses similarly to host cells\cite{AC2017}, which we believe might hint that a regime of intensity, duration, and pulse count may exist to target the viral envelope.
+The same field intensity does not appear to damage phages with protein capsids\cite{Manipulation2013}.
+
+Non-resonant capsid and envelope breakage with 120 pulses, 500 ns each, at 3 MV/m, has been previously observed\cite{Inactivation1990}, but the RNA damage suggests that this is an electrochemical artifact \cite{Formation1996} (c.f.
+\cite{Microwave1987}).
 
 If the duration of exposure is sufficiently short that thermal and membrane breakdown effects can be neglected, tissue appears to withstand peak electric fields of great magnitude - above 1 nanosecond megavolt/meter, even in in-vivo studies - without severe acute effects (\cite{Repeated2020}\cite{Review2011}\cite{DNA2004} and below).
+
+However, perhaps regrettably, the experiments reported here were not designed to address the question of whether conventional ion- and bilayer- driven electroporation can be harnessed, but rather to test whether purely mechanical damage from $qE$ forces can be easily observed.
 
@@
 	\item Infrared thermography only determines the surface temperature.
-Based on heating patterns seen in other experiments\cite{Effects1950}, the observed surface temperature rise does not seem to conclusively rule out a very localized thermal effect.
+Based on heating patterns seen in other experiments\cite{Effects1950}, the observed surface temperature rise does not perhaps conclusively rule out a very localized thermal effect.
 	\item Therefore, without free-space dosimetry or simulation of power density, the frequency-selective inactivation could possibly be explained by the frequency response of the power amplifier, antenna gain, and absorption of the cuvette.
@@
 
-\footnote{It is interesting to consider that a field with a strong positive publication bias\cite{Comprehensive2018}, in the presence of stringent peer review, could unintentionally tend towards a literature populated with only the most abstruse and difficult to explain false-positive results.}
+\footnote{It is interesting to consider that a field with a strong positive publication bias\cite{Comprehensive2018}, in the presence of stringent peer review, could unintentionally tend towards a literature populated with only the most abstruse and difficult to explain false-positive results.
+We do not suggest that this is relevant in this case; but a cursory review of the papers cited in that excellent meta-analysis leads both very difficult to find fault in, and entirely disproved by later research.}
 
@@
 
-An approximate charge distribution of the proteins of the virion can be obtained by multiplying primary structure charges (in our case, extracted \cite{CIDER2017}, or (\cite{complete2003})) by observed protein contribution to total MW\cite{Quantitative1981}, old 2D-PAGE gels \cite{Influenza1978}\cite{Structurea} (which also provides an estimate of the variation in the charge, important for accurate spectroscopy, see supplemental) - or perhaps directly via extraction from whole-virion CryoEM maps, enabled by the charge-sensitive nature of the technique \cite{Identification2018}\cite{Electrostatic2020}.
+An approximate upper bound on the charge distribution due to the proteins of the virion can be obtained by multiplying primary structure charges (in our case, extracted \cite{CIDER2017}, or (\cite{complete2003})) by observed protein contribution to total MW\cite{Quantitative1981}, old 2D-PAGE gels \cite{Influenza1978}\cite{Structurea} (which also provides an estimate of the variation in the charge, important for accurate spectroscopy).
+See supplemental data.
+It appears that the genome charge is largely neutralized by the nucleocapsid.
+
+It might be possible to extract the charge directly from whole-virion CryoEM maps, enabled by the charge-sensitive nature of the technique \cite{Identification2018}\cite{Electrostatic2020}.
 This has not yet been implemented in any software tools and seems quite tricky.
-
-The genome charge is almost entirely neutralized by the nucleocapsid.
 
@@
 Note that neither of these regimes overlap with the results of the previous studies.
-
-Non-resonant capsid and envelope breakage with 120 pulses, 500 ns each, at 3 MV/m, has been previously observed\cite{Inactivation1990} but the RNA damage suggests that this is an electrochemical artifact \cite{Formation1996} (and \cite{Microwave1987}).
-Long pulses at $10$ MV/m electroporate enveloped viruses similarly to host cells\cite{AC2017} but do not necessarily affect T4\cite{Manipulation2013}.
 
@@
 
-Previous field limits were set by the microwave hearing effect, a primarily thermoelastic mechanical \cite{MICROWAVEINDUCED1975}.
-Thermoelastic effects can cause damage, but primarily when \cite{Thermoacoustic2017}\cite{MECHANICAL1968}.
-\cite{Radiation1996}
+Previous field limits were generally set by the microwave hearing effect, a primarily thermoelastic mechanical \cite{MICROWAVEINDUCED1975}.
+Thermoelastic effects can cause damage\cite{MECHANICAL1968}, particularly when susceptors are implanted\cite{Thermoacoustic2017}, but do not seem to be a significant concern in most cases \cite{Radiation1996}.
 
-There is a body of work on coherent control of viral inactivation using picosecond laser exposure \cite{Maximum2010}; targeting small proteins seems to require very large fields\cite{Picosecond2016b}, but breaking viral capsids by exciting long-wavelength vibrations using Raman scattering has been reported experimentally \cite{Inactivation2007}\cite{Prospects2012}\cite{Studies2014}, however these results have failed replication\cite{No2011}.
+In general, methods targeting small proteins seem to require impractical fields\cite{Picosecond2016b}.
+Very recently, a region of the SARS-NCoV-2 spike protein has been reported to be susceptible to electric fields\cite{Receptor2021}; however the field intensity required appears to be on the order of 3 GV/m.
+
+There is a body of work on coherent control of viral inactivation using picosecond laser exposure \cite{Maximum2010}.
+Breaking viral capsids by exciting long-wavelength vibrations using Raman scattering has been reported experimentally \cite{Inactivation2007}\cite{Prospects2012}\cite{Studies2014}, however these results have failed replication\cite{No2011}.
 The author has not investigated this mechanism in any detail.
@@
 
-Positive artifacts are very common in this field, and extreme care in experimental design appears to be required to produce any meaningful result.
+Positive artifacts are very common when exposing organisms to electric fields, and extreme care in experimental design appears to be required to produce any meaningful result.
 Excellent best-practices guidelines and meta-analyses are available in \cite{Biological2016} \cite{Comprehensive2018} \cite{Funding2019}, \cite{chou1996radio} and \cite{Effects2016}.
@@
 
-\subsection{Experiment methods}
+\subsection{Materials and methods}
 

### 2021-03-14 documents/summary.tex
Screw it, let's try liposomes

@@
 %\begin{refsection}
+
+A few well-established non-resonant non-thermal phenomena caused by extreme electric fields have been put to practical use.
+
+Electroporation\cite{Electroporation1988}, now a common laboratory procedure, occurs when an enormous electric field causes ions in solution to diffuse across a cell membrane, capacitively charging it, provoking a change in lipid bilayer conformation\cite{Membrane2016}, reversibly rendering the membrane permeable.
+This is one among many other, more subtle mechanisms; the minutia of poration can become extraordinarily complex in certain circumstances and are beyond the author's current understanding\cite{Theoretical2007}.
+
+Therapies based on irreversible electroporation\cite{Nonthermal2013}\cite{Lipid2017} have recently been used in the clinic\cite{Irreversible2013} for tumor ablation.
+There is much discussion on electroporation as an alternative to viral vectors, but we have found surprisingly little discussion on clinical treatment of viral infection with these conventional electroporation therapies.
+
+However, long pulses at $\approx10$ MV/m appear to electroporate large enveloped viruses, similarly to host cells\cite{AC2017}, which we believe might hint that a regime of intensity, duration, and pulse count may exist to target the viral envelope.
+In fact, despite considering the somewhat harder problem of electroporating while inside the cell, rather than in extracellular fluid, \cite{Electroporation2013} report selective electroporation of 250 nm liposomes with 4 ns pulses up to 10 MV/m without inducing damage to the host cell - which seems a very important result.
+Despite the number of free parameters in pulse exposure, it is possible that scaling laws might conceivably preclude the formation of destructive transmembrane potentials in 100 nm-scale viruses.
+
+The same field intensities do not appear to damage phages with protein capsids\cite{Manipulation2013}, in line with our negative results on T4.
+
+Non-resonant capsid and envelope breakage with 120 pulses, 500 ns each, at 3 MV/m, has been previously observed\cite{Inactivation1990}, but the RNA damage suggests that this is an electrochemical artifact \cite{Formation1996} (c.f.
+\cite{Microwave1987}).
+
+However, perhaps regrettably, the experiments reported in this study were not designed to address the question of whether conventional ion- and bilayer- driven electroporation can be harnessed, but rather to test whether purely mechanical damage from $qE$ forces can be easily observed in viruses.
+
 \lettrine{W}e were inspired to undertake this project by a set of publications by a certain Sun group, (primarily Liu et al \cite{Microwave2009} and Yang et al \cite{Efficient2015}, simultaneously demonstrated by Hung et al \cite{focusing2014}), partially replicated by \cite{Optical2020} and discussed by \cite{Theoretical2020}.
@@
 
-A few well-established non-resonant non-thermal effects caused by extreme electric fields have already been put to practical use.
-Electroporation\cite{Electroporation1988}, now a common laboratory procedure, occurs when an enormous electric field causes ions in solution to diffuse across a cell membrane, capacitively charging it.
-This leads to a change in lipid conformation, reversibly rendering the membrane permeable.
-This is one among other, more subtle mechanisms; the minutia of poration are extraordinarily complex and beyond the author's current understanding\cite{Theoretical2007}.
-
-Therapies based on irreversible electroporation\cite{Nonthermal2013}\cite{Lipid2017} have recently been used in the clinic\cite{Irreversible2013} for tumor ablation.
-There is much discussion on electroporation as an alternative to viral vectors, but we have found surprisingly little discussion on clinical treatment of viral infection with these conventional electroporation therapies.% In vitro there is evidence to suggest that sub-cellular effects take place under truly tremendous fields.
-
-Long pulses at $\approx10$ MV/m appear to electroporate enveloped viruses similarly to host cells\cite{AC2017}, which we believe might hint that a regime of intensity, duration, and pulse count may exist to target the viral envelope.
-The same field intensity does not appear to damage phages with protein capsids\cite{Manipulation2013}.
-
-Non-resonant capsid and envelope breakage with 120 pulses, 500 ns each, at 3 MV/m, has been previously observed\cite{Inactivation1990}, but the RNA damage suggests that this is an electrochemical artifact \cite{Formation1996} (c.f.
-\cite{Microwave1987}).
-
 If the duration of exposure is sufficiently short that thermal and membrane breakdown effects can be neglected, tissue appears to withstand peak electric fields of great magnitude - above 1 nanosecond megavolt/meter, even in in-vivo studies - without severe acute effects (\cite{Repeated2020}\cite{Review2011}\cite{DNA2004} and below).
-
-However, perhaps regrettably, the experiments reported here were not designed to address the question of whether conventional ion- and bilayer- driven electroporation can be harnessed, but rather to test whether purely mechanical damage from $qE$ forces can be easily observed.
 
@@
 Trustworthiness probably depends most significantly on the quality of error analysis; many have made good use of otherwise unreliable techniques.
-However, particularly in a field with a high positive publication bias, it seems most productive to use the most advanced techniques, those that are foolproof by their very nature.
+However, particularly in this field, it seems most productive to use the most advanced techniques, those that are foolproof by their very nature.
 Based only on our experience of the literature, in order of decreasing reliability for resonance measurement:
@@
 \item Time-domain spectroscopy (many advantages cited by \cite{Time2003}, including instant, drift-free capture of all frequencies and limited instrumentation artifacts), \cite{Dielectric2004}\cite{Microwave1994}
-\item Raman or other non-photothermal optical (\cite{optical1983} $\neq$ [\cite{Resonances1987} \cite{Dielectric1989}]) and also \footnote{see Taylor \cite{mechanisms1981} citing unpublished, personal communication}, but we have no understanding of how such artifacts could form
+\item Raman or other non-photothermal optical (\cite{optical1983} $\neq$ [\cite{Resonances1987} \cite{Dielectric1989}]) and also \footnote{see Taylor \cite{mechanisms1981} citing unpublished, personal communication - a textbook example of positive publication bias!}, but we have no understanding of how such artifacts could form
 \item Frequency-domain CW VNA absorption or reflection (\cite{Microwave1982} $\neq$ [\cite{Resonances1987} \cite{Dielectric1989}]) \cite{Substitution1982} \cite{Millimeter1980}.
@@
 
-Although not representative of careful, well-calibrated VNA testing because of the crudity of our homebrew spectrometer, we were able to produce many candidate resonances in our data with perfectly justifiable modifications to post-processing, which raises interesting (but not novel\cite{Reanalysis2020}\cite{statistical2020}) questions regarding software development in such conditions.
-\footnote{One solution might be to keep all data blinded while developing the analysis software, and use synthetic data to calibrate.
-One objection might be that the data often inform the required calibration; we might retort that if the technique is so sensitive that the calibration procedure cannot be known beforehand, a different technique should be used.}
+Although not representative of careful, well-calibrated VNA testing because of the crudity of our homebrew spectrometer, we were able to produce many candidate resonances in our data with perfectly justifiable modifications to post-processing, which raises interesting (but not novel\cite{Blindinga}, \cite{Reanalysis2020}\cite{statistical2020}) questions regarding software development in such conditions.
+\footnote{One solution might be to keep all data blind while developing the analysis software, and use synthetic data to calibrate.
+One objection might be that the data often inform the required calibration; we might retort that if the technique is so sensitive that the calibration procedure cannot be known beforehand, a different method with a higher SNR should be used.}
 
@@
 
-\subsection{Materials and methods}
+\subsection{Experiment notes}
 
@@
 
-Positive control samples were put in a commercial pressure cooker to autoclave for either 6 or 20 minutes in an Eppendorf tube: the pressure was released after the cycle to prevent dilution.
+Positive control samples were put in a commercial pressure cooker to autoclave for 20 minutes in an Eppendorf tube: the pressure was released after the cycle to prevent dilution.
 The flurophore was added after autoclaving.
@@
 Avalanche transistors appear to be the easiest way to produce high power sub-100 picosecond pulses.
-We stole an avalanche Marx design verbatim from Li (\cite{Development2016b} \cite{Design2018c}), which allows large pulses from safer lower voltage supplies (albeit requiring somewhat costly capacitors).
-2N5551 transistors used to be common \cite{Avalanche1991}\cite{high1994}\cite{High1998}; our testing with Raj's FMMT417
+We stole an avalanche Marx design verbatim from Li et al (\cite{Development2016b} \cite{Design2018c}), which allows large, fast pulses to be produced from lower voltage supplies (albeit requiring somewhat costly capacitors).
+2N5551 transistors used to be commonly used for this purpose.
+\cite{Avalanche1991}\cite{high1994}\cite{High1998}; Oak's test circuit .
 
@@
 
-A programmable syringe withdrew and pumped 50 uL of fluid at a constant rate through one of the coplanar channels, via a 4 cm long silicone capillary (McMaster-Carr \#51845K65) immersed in a 1.5 mL centrifuge tube using a 26 Ga Luer-lock (\#6710A76).
+A programmable syringe withdrew and pumped approximately 50 uL of fluid at a constant rate through one of the coplanar channels, via a 4 cm long silicone capillary (McMaster-Carr \#51845K65) immersed in a 1.5 mL centrifuge tube using a 26 Ga Luer-lock (\#6710A76).
 Forcing phage through the capillary is similar to lysis with a French pressure cell press, but no such effects were obviously seen.
@@
 
-In all cases, a thermal effect was made implausible; the total energy in the pulse train precluded heating above the capsid melting temperature\cite{Effects1951}.
+In all cases, a thermal effect was made implausible because of the short pulse duration; the total energy in the pulse train precluded heating above the capsid melting temperature, like\cite{Effects1951} - about 90 C for capsids \cite{Thermal1999} and 50 C for envelopes\cite{Stability1985}.
 
@@
 However, as spectrometry was abandoned, this non-deterministic property caused considerable issues while troubleshooting the fluorescence detection system, and \st{expedience} \footnote{laziness} prompted us to disable this system at run 9, defying best practices on blinded trials.
-
-A thin layer of silicone conformal coating was applied to the 0.2 mm waveguide to avoid the copper ion artifact, but this could not be done on the 0.03 mm waveguide.
 
@@
 
-We are particularly excited by the prospect of using picosecond time-domain measurements not only to perform steady state dielectric measurements or monitor the input pulse, as is now common practice, but to resolve the internal effects of a single high-voltage pulse on the virus in real time.
+We are particularly excited by the prospect of using picosecond time-domain measurements not only to perform low-field-intensity steady state dielectric measurements or monitor the input pulse, as is now common practice, but to resolve the internal effects of a single high-voltage pulse on the virus in real time.
 Scan-converter based transient digitizers, such as the Tektronix SCD-5000 series, appear to be the lowest-cost method of obtaining the >0.5 THz sampling bandwidths required, when the tube bandwidth is deconvolved.
+
+Fecher\cite{Production1949} micro-oscillographs
+
+\section{Materials and methods}
+
+\subsubsection{Main sample preparation}
+
+A stock preparation of 1:150 Biotium GelGreen was diluted to 1:4000 in a 15 mL Falcon tube.
+
+With a Kartell 0.2 mL fixed-volume micropipette (McMaster-Carr \#7015T17) connected to an autoclaved and flamed glass pipette,  0.2 mL of Carolina 124330 (early assay tests) or Carolina 124335 (electric field tests), titer $3\times10^9$, was transferred into a 1.5 mL Eppendorf tube.
+Field-tested phage was stored in a 4 C fridge for several months during the experiment.
+
+ stored in an aluminum light-tight bag was pipetted into the same 1.5 mL tube.
+
+\subsubsection{Main sample preparation}
+
+\subsubsection{Nanosecond pulsed trials}
+
+A clone of Li et al's pulse generator was engraved with a 30 degree V-bit cutter onto a 1.6 mm double-sided 1 oz copper FR4 substrate. ATC 100B470JT500XT capacitors and FMMT417 transistors were used.
+
+Two coplanar waveguides, approximately 2.5 cm long, designed with 'wcalc'\cite{Wcalc}, were similarly engraved into a single-sided 0.8 mm 1 oz copper FR4 substrate (MG chemicals).
+One waveguide (referred to as "0.2 mm channel") was 0.4 mm wide with 0.1 mm and 0.15 mm wide slots (asymmetric due to machining tolerances).
+The other was 0.4 mm wide with 0.03 and 0.06 mm slots.
+
+The depth of the channels was not precisely known but considerably exceeded the copper thickness, as is reflected in the simulation.
+
+Two end-launch SMA connectors were soldered to the waveguide; one connector was either terminated with a standard 50-ohm SMA terminator or left open, depending on the trial, and the other connected via semirigid coax (CCSMA-MM-086-12) to the pulse generator.
+
+\conclusiongrad
+
+A thin layer of silicone conformal coating was applied to the 0.2 mm waveguide to avoid the copper ion artifact, but this could not be done on the 0.03 mm waveguide.
+
+HIA4 power supply.
+
+\subsubsection{FDTD tissue modelling}
+
+To determine penetration of waves in tissue, the four term Cole-Cole model\cite{gabriel1996compilation}, \ghfile{/electronics/simple_fdtd/fdtd_PCB_extensions/fdtd_PCB_extensions/tissue.py}, was used with parameters from the IT.IS Foundation tissue database\cite{Tissue2018a}.
+The IT.IS Foundation computational phantom 'duke V3.0' was used, \cite{Duke2014}.
 
@@
 
-Funded in part by the author's company, SafeSump Inc., and Ideal Consulting Ltd., and the author's parents. The author was at YorkU for the duration of this project.
+Funded in part by the author's company, SafeSump Inc., and Ideal Consulting Ltd., and the author's parents.
 
@@
 
-\subfile{brillouin_pulse_math}
+%\subfile{brillouin_pulse_math}
 

### 2021-03-21 documents/EPA_paper.tex
Writing notes
Pure electroporation

@@
 
-There is an interesting citation in the Gray literature \cite{Indexa}, particularly because it seems to have progressed to the clinic:
+\section{Gray literature}
+
+There is an interesting citation in the Gray literature \cite{Index1981}, particularly because it seems to have progressed to the clinic:
 
@@
 
+Thanks to [] at york, and [] on the UWaterloo Discord.
 \end{document}

### 2021-03-21 documents/paper_electrophoresis.tex
Pure electroporation

%!TeX root = paper_electrophoresis
\documentclass[paper.tex]{subfiles}
\begin{document}

\subsection{Paper electrophoresis}

There's a very interesting which has almost completely fallen into antiquity, and yet not obviously for any reason. Filter paper electrophoresis. It requires less work to set up than gel electrophoresis. because I believe it partially relies on a different mechanism. When power is applied to the filter paper baths, the buffer visibly pumps through. \cite{ELECTROPHORESIS1951} Electroosmotic flow 40 to 100 volts works fine, no gel needs to be poured beforehand.

I've heard that this is not effective for DNA et al, only for proteins or amino acids.

\cite{gelelectrophoresis}
\begin{fquote}
	While paper and other solid support materials proved to be an advantage over free solutions for the electrophoretic analysis of biomolecules, gels were adopted later because gels not only minimized diffusion better than paper supports they actually participated in the separation process by interacting with the migrating particles. Gels can be thought of as semi-solid matrices whose pore sizes aid in separation. The semisolid nature of the gel participates through a process known as molecular sieving. The three common media for gel electrophoresis are starch, polyacrylamide, and agarose. Of these, the starch gel medium is the least versatile whereas a wide range of separation effects can be achieved using the other two media. There are limitations to the use of both polyacrylamide and agarose but these are effectively minimized when the material to be analyzed is a nucleic acid. Even very small nucleic acids (i.e., oligonucleotides) are easily separated in an electrical field by one or the other medium. The primary criteria for choosing polyacrylamide or agarose gel electrophoresis are length and whether or not the nucleic acid is single stranded or double stranded. Short, single-stranded DNAs like oligonucleotides require polyacrylamide whereas long (>100bp), double stranded DNAs are best resolved on agarose.
\end{fquote}

The macgyver running buffer\cite{MACGYVER2005}.

\cite{Inexpensive1955}

\end{document}

### 2021-03-21 documents/pure_electroporation.tex
Pure electroporation

%!TeX root = pure_electroporation
\documentclass[paper.tex]{subfiles}
\begin{document}

\title{Selective electroporation of the viral envelope via nanosecond pulses}
\author{\small{Daniel Correia\orcidlink{0000-0002-9353-0216} (therobotist@gmail.com), Ontario, Canada.}}
\date{March 2021}

\flushbottom 
\maketitle
\thispagestyle{empty}

\renewcommand{\abstractname}{Summary}    % clear the title

\begin{abstract}
	Extreme electric fields drive transmembrane potentials, leading to pores in membranes; this phenomenon is commonly harnessed for transfection into the cell in the laboratory, and similar pulses have recently been shown to be effective in the clinic for ablating tumors.

	As pulse duration is reduced from the microsecond to sub-nanosecond regime, and the field is increased to approach the breakdown voltage of tissue, effects on smaller structures are expected and observed.

	As a followup to

	Recently-developed gigawatt pulse systems may offer a possible means of noninvasively propagating such pulses into deep tissues, such as within lungs. 
\end{abstract}

At the risk of spending more time producing underpowered "scientifically useless" results,

As in the previous paper, we must stress that meaningful bioelectrics research hinges very strongly on experimental design and methodology, and very few results can be trusted implicitly.

can determine the conductivity sigma from Brackley's kappa debye length

A danger would be that if a nuclear or organelle membrane were to be porated, viral ssRNA may be admitted to places it shouldn't be, which would be bad news.

Pulse count and timing is another free variable. Joshi et al \cite{Selfconsistent2001} model that a carefully timed second pulse can have much greater effects than a single pulse, in agreement with experiment.

Of course, unlike localized tumors, viral infections are systemic, affecting many of the most favoured organs. However, either blood

Note that, mostly contrary to these observations,

\cite{Nanosecond2006b}

Some scaling laws for membrane charging effects due to short (sub Tc) pulses are given by Schoenbach \cite{Bioelectric2007}.

The membrane charging time constant Cole single-shell model \cite{Ultrashort2004} simplified for the low-density case,

$$\tau_c = \left(1 \frac{\rho_1}{2} + \rho_2\right) C_m (D/2)$$

\cite{Bioelectric2007} eq. 15,

$$\Delta V_M = \frac{3}{2}\frac{E\tau D}{2 \tau_c }$$

substituting,

$$\Delta V_M = \frac{3}{2}\frac{E \tau}{C_m ((\rho_1/2) + \rho_2)}$$

that is, all else being equal, the transmembrane voltage appears to be invariant with raw particle diameter.

The membrane capacitance per unit area, $C_m$, is determined simply by parallel-plate Ermolina \cite{Study2001}; $C_m = (k\epsilon_0) / d$, where d is the membrane thickness. The cell and nucleus membrane have similar capacitance, but greatly differ in conductivity.

The dielectric properties of viruses have been determined by the fascinating technique of electrorotation (and dielectrophoresis). There is considerable variation.

Influenza has a membrane thickness of 4 nm (Harris \cite{Influenza2006}),

Is the effect replicable, or is it simply an electrochemical artifact? Will these nanopores be destructive to viruses - will the pores be open for sufficient time for the ssRNA to be released? Will the nucleocapsid restrain the genome sufficiently and prevent membrane damage from inactivating the virus? Are the apoptosis effects likely to be triggered before these? Are there similar structures in tissue?

\end{document}

### 2021-03-21 documents/summary.tex
Pure electroporation

@@
 However, long pulses at $\approx10$ MV/m appear to electroporate large enveloped viruses, similarly to host cells\cite{AC2017}, which we believe might hint that a regime of intensity, duration, and pulse count may exist to target the viral envelope.
-In fact, despite considering the somewhat harder problem of electroporating while inside the cell, rather than in extracellular fluid, \cite{Electroporation2013} report selective electroporation of 250 nm liposomes with 4 ns pulses up to 10 MV/m without inducing damage to the host cell - which seems a very important result.
-Despite the number of free parameters in pulse exposure, it is possible that scaling laws might conceivably preclude the formation of destructive transmembrane potentials in 100 nm-scale viruses.
+In fact, despite considering the somewhat harder problem of electroporating while inside the cell, rather than in extracellular fluid, \cite{Electroporation2013} report that 250 nm liposomes should be porated without inducing damage to the host cell, and modelling shows that 100 nm liposomes may be porated by 4 ns pulses never exceeding 20 MV/m.
+Despite the number of free parameters in pulse exposure, it is possible that scaling laws might conceivably preclude the safe formation of destructive transmembrane potentials in 100 nm-scale viruses.
 
@@
 
-However, perhaps regrettably, the experiments reported in this study were not designed to address the question of whether conventional ion- and bilayer- driven electroporation can be harnessed, but rather to test whether purely mechanical damage from $qE$ forces can be easily observed in viruses.
+However, perhaps regrettably, the experiments reported in this study were not designed to address the question of whether this conventional ion- and bilayer- driven electroporation can be harnessed, but rather to test whether purely mechanical damage from $qE$ forces can be easily observed in viruses.
 
@@
 
-In-vitro, there appears to be a consistent set of effects of nanosecond pulses, or nsPEF, distinct from membrane effects, that occur on small intracellular organelles (see reviews \cite{Penetration2016c} \cite{Effects2016} ), \cite{Bioeffects},
+In-vitro, there appears to be a consistent set of effects of nanosecond pulses, or nsPEF, distinct from membrane effects, that occur on small intracellular organelles (see reviews \cite{Penetration2016c} \cite{Effects2016} ), \cite{Bioeffects}.
+
+Apoptosis \cite{Effect2008}
 
@@
 This suggests a maximum rotation frequency on the order of $10^3$, but this value requires so many assumptions that it's hardly worth mentioning.
-From \cite{Spinning2008}, the upper bound of a homogenous spherical virus with 10 MPa overall tensile strength appears to be about $10^9$ Hz.
-\footnote{\ghfile{documents/optical_centrifuge.ipynb}}
+
+From \cite{Spinning2008}, the upper bound of a homogenous spherical virus with 10 MPa overall tensile strength appears to be about $10^9$ Hz. \footnote{\ghfile{documents/optical_centrifuge.ipynb}}
 
@@
 If the effect exists, efficient use of the lower damping would seem to require more than one cycle of oscillation.
-It appears to be impossible at any input power to effectively drive a 10 GHz resonator in the lungs from outside the torso, partly because of the layer of conductive muscle that shields the chest cavity (see supplemental).
+It appears to be impossible at any input power to effectively drive a 10 GHz resonator in the lungs from outside the torso, partly because of the layer of conductive muscle that shields the chest cavity.
+
 Open-ended waveguides\cite{OpenEnded1982}\cite{Analysis1989}\cite{142018} or water bolus allow efficient coupling to the body.
@@
 Dispersion and Brillouin precursors do offer a means to produce a significant improvement in loss through tissue, and the required electrical waveforms appear to be synthesizeable by variable-impedance or stub transmission-line pulse shaping\cite{Coaxial1985}\cite{Arbitrarya}.
+
+See supplemental for a cursory treatment of the Brillouin precursors.
 
@@
 
-Fecher\cite{Production1949} micro-oscillographs
+%Fecher\cite{Production1949} micro-oscillographs
+
+Before the HMC732 was used, a misguided effort was spent in trying to develop an inexpensive wideband tunable oscillator for spectrometry. This will be chronicled in the GitHub repository.
 
@@
 
-A clone of Li et al's pulse generator was engraved with a 30 degree V-bit cutter onto a 1.6 mm double-sided 1 oz copper FR4 substrate. ATC 100B470JT500XT capacitors and FMMT417 transistors were used.
+A clone of Li et al's pulse generator was engraved with a 30 degree V-bit cutter onto a 1.6 mm double-sided 1 oz copper FR4 substrate.
+ATC 100B470JT500XT capacitors and FMMT417 transistors were used.
+This was powered by a HIA4 power supply at 330v.
 
@@
 A thin layer of silicone conformal coating was applied to the 0.2 mm waveguide to avoid the copper ion artifact, but this could not be done on the 0.03 mm waveguide.
-
-HIA4 power supply.
 
@@
 %\end{figure}
-
-Before the HMC732 was used, a misguided effort was spent in trying to develop an inexpensive wideband tunable oscillator for spectrometry. This will be chronicled in the GitHub repository.
 

### 2021-03-22 documents/pure_electroporation.tex
Pulse stacking - charge-pulse!!!!!

@@
 %!TeX root = pure_electroporation
-\documentclass[paper.tex]{subfiles}
+\documentclass[fleqn,10pt]{article}
+
+\include{preamble}
 \begin{document}
 
-\title{Selective electroporation of the viral envelope via nanosecond pulses}
+\title{On selective electroporation of the viral envelope}
 \author{\small{Daniel Correia\orcidlink{0000-0002-9353-0216} (therobotist@gmail.com), Ontario, Canada.}}
@@
 \begin{abstract}
-	Extreme electric fields drive transmembrane potentials, leading to pores in membranes; this phenomenon is commonly harnessed for transfection into the cell in the laboratory, and similar pulses have recently been shown to be effective in the clinic for ablating tumors.
+	\noindent Extreme electric fields drive transmembrane potentials, leading to pores through membranes; this phenomenon is commonly harnessed for transfection into the cell in the laboratory, and similar techniques have recently been shown to be effective in the clinic for ablating tumors.\\
 
-	As pulse duration is reduced from the microsecond to sub-nanosecond regime, and the field is increased to approach the breakdown voltage of tissue, effects on smaller structures are expected and observed.
+	\noindent As pulse duration is reduced from the microsecond to nanosecond regime, effects targeting smaller intracellular structures are expected and observed.
+Indeed, pulses shorter than 10 ns have been observed to porate the nuclear envelope while leaving the cell membrane intact.
 
@@
 
-A danger would be that if a nuclear or organelle membrane were to be porated, viral ssRNA may be admitted to places it shouldn't be, which would be bad news.
+A serious danger would be that if a nuclear or organelle membrane were to be porated, viral ssRNA may be admitted to places it shouldn't be.
+The author does not have the biology experience to evaluate this risk.
 
-Pulse count and timing is another free variable.
-Joshi et al \cite{Selfconsistent2001} model that a carefully timed second pulse can have much greater effects than a single pulse, in agreement with experiment.
+Pulse count and inter-pulse timing is another free variable.
+Joshi et al \cite{Selfconsistent2001} model that a carefully timed second pulse can have greater effects than a single pulse, in agreement with experiment.
 
@@
 
+\section*{Basic scaling laws}
+
 Some scaling laws for membrane charging effects due to short (sub Tc) pulses are given by Schoenbach \cite{Bioelectric2007}.
 
-The membrane charging time constant Cole single-shell model \cite{Ultrashort2004} simplified for the low-density case,
+The membrane charging time constant Cole single-shell model \cite{Ultrashort2004} - simplified for the low-density case -
 
-$$\tau_c = \left(1 \frac{\rho_1}{2} + \rho_2\right) C_m (D/2)$$
+$$\tau_c = \left(1 \frac{\rho_{medium}}{2} + \rho_{internal}\right) C_m (D/2)$$
 
-\cite{Bioelectric2007} eq. 15,
+where $\rho_{medium}$ and $\rho_{internal}$ are the resistivities of the medium and internal fluid (the cytoplasm for cells, and assumed to be the 'core' for viruses). \cite{Bioelectric2007} eq. 15,
 
 $$\Delta V_M = \frac{3}{2}\frac{E\tau D}{2 \tau_c }$$
+
+pore size vs time? same size pore in a smal lparticle
 
@@
 
-that is, all else being equal, the transmembrane voltage appears to be invariant with raw particle diameter.
+that is, all else being equal, the induced transmembrane voltage appears to be invariant with raw particle diameter - contrary to Rjif's more detailed analysis.
 
-The membrane capacitance per unit area, $C_m$, is determined simply by parallel-plate Ermolina \cite{Study2001}; $C_m = (k\epsilon_0) / d$, where d is the membrane thickness.
+The viral envelope capacitance per unit area, $C_m$, can be determined simply by parallel-plate (Ermolina \cite{Study2001}); $C_m = (k\epsilon_0) / d$, where d is the membrane thickness.
 The cell and nucleus membrane have similar capacitance, but greatly differ in conductivity.
 
-The dielectric properties of viruses have been determined by the fascinating technique of electrorotation (and dielectrophoresis). There is considerable variation.
+There may be an existing transmembrane potential that must be added - this is neglected in this case.
 
-Influenza has a membrane thickness of 4 nm (Harris \cite{Influenza2006}),
+The dielectric properties of viruses have been determined by the fascinating technique of electrorotation (and dielectrophoresis).
+There is some variation in reported values.
+The internal core permittivity of viruses is often referred to as being about 2 to 3 (Brackley \cite{Electrostatic2020}, SARS-CoV-2; and Schnelle \cite{Trapping1996}, Sendai and Influenza A) - however, Gimsa \cite{New1999}, on influenza, and Hughes\cite{Dielectrophoretic2001} on HSV-1 both suggest an internal $\epsilon_r$ of 30.
+We have not investigated this discrepancy.
+The internal permittivity of impermeable viruses depends on the growth medium's osmotic strength\cite{Osmotic2003}, so results with different media may not be comparable.
 
-Is the effect replicable, or is it simply an electrochemical artifact?
+It is usually agreed that the viral shell has a permittivity of about 60 to 80, similar to the nuclear membrane (60 to 100) but unlike the cell membrane ($\epsilon_r\approx 10$).
+
+Influenza has a membrane thickness of about 4 nm (Harris \cite{Influenza2006}).
+However, Gimsa and Hughes use a shell thickness of 18 and 15 nm, respectively, to account for the membrane proteins and hemaglutinase.
+The $C_{envelope}$ may therefore fall within the range $2.9 \text{ to } 17.7 \text{ uF/cm}^2$.
+
+% >>> (80 * electricConstant) / 4 nanometers -> 17.7 uF/cm^2
+% >>> (60 * electricConstant) / 18 nanometers -> 2.9514 uF/cm^2
+
+Gimsa and Schnelle data on influenza seems to suggest a core conductivity of 0.1 to 1 milliSiemens/m (1000 to 10000 $\Omega \cdot m$), far less conductive than cytoplasm or nucleoplasm, at about 1 S/m (1 $\Omega \cdot m$) \cite{Study2001}.
+
+The viral envelope appears to be slightly less conductive than the cell membrane (0.1 $\micro$S/m \cite{New1999} vs 10 $\micro$S/m \cite{Study2001}), and far less conductive than the nuclear envelope (0.1 $\text{m}$S/m \cite{Study2001}).
+This ratio is the relevant quantity to find the steady state transmembrane voltage for long pulses (before pore conduction becomes relevant).
+
+The time constant of the virus therefore appears to be between 7 and 44 us, compared to about 100 ns for most host cells, the discrepancy mainly contributed by the internal core conductivity and the shell permittivity.
+
+At first glance, this may seem unfortunate: the host will be destroyed far before the virus.
+
+However, if a pulse train with a pulse duration shorter than the cell time constant, an intensity too low for, and a repetition rate of some 3 us, (200 khz),
+
+This is unlike the 'killing blow' described in Schoenberterg where pores have already formed.
+
+% 1 Ohm m / 2 + 5000 ohm meter * 2.9 uF/cm^2 * 50 nm
+
+%Is the effect replicable, or is it simply an electrochemical artifact?
 Will these nanopores be destructive to viruses - will the pores be open for sufficient time for the ssRNA to be released?

### 2021-03-22 documents/pure_electroporation.tex
README

@@
 
-\title{On selective electroporation of the viral envelope}
+\title{Selective electroporation of the viral envelope}
 \author{\small{Daniel Correia\orcidlink{0000-0002-9353-0216} (therobotist@gmail.com), Ontario, Canada.}}
@@
 	\noindent As pulse duration is reduced from the microsecond to nanosecond regime, effects targeting smaller intracellular structures are expected and observed.
-Indeed, pulses shorter than 10 ns have been observed to porate the nuclear envelope while leaving the cell membrane intact.
-
-	As a followup to
+Indeed, pulses shorter than 10 ns have been observed to porate the nuclear envelope and organelle membranes while leaving the cell membrane intact.
 
@@
 
+As a followup to.
+
 At the risk of spending more time producing underpowered "scientifically useless" results,
@@
 As in the previous paper, we must stress that meaningful bioelectrics research hinges very strongly on experimental design and methodology, and very few results can be trusted implicitly.
-
-can determine the conductivity sigma from Brackley's kappa debye length
 
@@
 
-It is usually agreed that the viral shell has a permittivity of about 60 to 80, similar to the nuclear membrane (60 to 100) but unlike the cell membrane ($\epsilon_r\approx 10$).
+In electrorotation, it is usually found that the viral shell has a permittivity of about 60 to 80, similar to the nuclear membrane (60 to 100) but massively unlike the cell membrane ($\epsilon_r\approx 10$).
 

### 2021-03-22 documents/pure_electroporation.tex
electroporation

@@
 \author{\small{Daniel Correia\orcidlink{0000-0002-9353-0216} (therobotist@gmail.com), Ontario, Canada.}}
-\date{March 2021}
+\date{March 21 2021}
 
@@
 \begin{abstract}
-	\noindent Extreme electric fields drive transmembrane potentials, leading to pores through membranes; this phenomenon is commonly harnessed for transfection into the cell in the laboratory, and similar techniques have recently been shown to be effective in the clinic for ablating tumors.\\
+	\noindent The phenomenon of electroporation occurs when extreme applied electric fields in the MV/m range drive transmembrane potentials, leading to pores through membranes; this is commonly harnessed for transfection into the cell in the laboratory, and has recently been shown to be safe and effective in the clinic for ablating tumors.\\
 
 	\noindent As pulse duration is reduced from the microsecond to nanosecond regime, effects targeting smaller intracellular structures are expected and observed.
-Indeed, pulses shorter than 10 ns have been observed to porate the nuclear envelope and organelle membranes while leaving the cell membrane intact.
+Indeed, pulses shorter than 10 ns have been observed to porate the nuclear envelope and organelle membranes while leaving the plasma membrane intact.
+\\
 
-	Recently-developed gigawatt pulse systems may offer a possible means of noninvasively propagating such pulses into deep tissues, such as within lungs. 
+	Dielectric properties apparently due to the
+
+	\noindent Recently-developed gigawatt pulse systems may offer a possible means of noninvasively propagating such pulses into deep tissues, such as within lungs. 
 \end{abstract}
 
-As a followup to.
+As a followup to \cite{notes2021}
+
+The same electrostatic effects on lipid bilayers have been investigated for decades. Many extremely fascinating hydrodynamic and parametric
 
@@
 Pulse count and inter-pulse timing is another free variable.
-Joshi et al \cite{Selfconsistent2001} model that a carefully timed second pulse can have greater effects than a single pulse, in agreement with experiment.
+Joshi et al \cite{Selfconsistent2001} model that a carefully timed second pulse can have greater effects than a single pulse, in agreement with experiment on E.
+coli.
 
@@
 
-\section*{Basic scaling laws}
+This seems too simple.
 
-Some scaling laws for membrane charging effects due to short (sub Tc) pulses are given by Schoenbach \cite{Bioelectric2007}.
+\subsection*{Basic scaling laws}
 
-The membrane charging time constant Cole single-shell model \cite{Ultrashort2004} - simplified for the low-density case -
+Some extremely simplified scaling laws for membrane charging effects due to short (sub Tc) pulses are given by Schoenbach \cite{Bioelectric2007}.
+These are based primarily on an equivalent circuit model.
+
+The membrane charging time constant from a single-shell model \cite{Ultrashort2004} - simplified for the low-density case
 
@@
 
-where $\rho_{medium}$ and $\rho_{internal}$ are the resistivities of the medium and internal fluid (the cytoplasm for cells, and assumed to be the 'core' for viruses). \cite{Bioelectric2007} eq. 15,
+where $\rho_{medium}$ and $\rho_{internal}$ are the resistivities of the medium and internal fluid (the cytoplasm for cells, and assumed to be the 'core' for viruses).
+Electroporation is a highly nonlinear effect, and this .
+\cite{Bioelectric2007} eq.
+15,
 
 $$\Delta V_M = \frac{3}{2}\frac{E\tau D}{2 \tau_c }$$
-
-pore size vs time? same size pore in a smal lparticle
 
@@
 
-that is, all else being equal, the induced transmembrane voltage appears to be invariant with raw particle diameter - contrary to Rjif's more detailed analysis.
+that is, all else being equal, the induced transmembrane voltage appears to be invariant with raw particle diameter - mildly contrary to Rjif's more detailed analysis.
 
@@
 In electrorotation, it is usually found that the viral shell has a permittivity of about 60 to 80, similar to the nuclear membrane (60 to 100) but massively unlike the cell membrane ($\epsilon_r\approx 10$).
+This is very remarkable, since the lipid bilayer itself is somewhat similar in composition to the host cell; envelope, spike and membrane proteins may account.
 
@@
 
-However, if a pulse train with a pulse duration shorter than the cell time constant, an intensity too low for, and a repetition rate of some 3 us, (200 khz),
+However, if a monopolar pulse train with a pulse duration shorter than the cell time constant, an intensity too low for, and a repetition rate of some 3 us, (200 khz),
 

### 2021-03-27 documents/lessons_learned.tex
Pure electroporation
Transmembrane library

@@
 \section{Lessons Learned} \
+
+In general, even though thesis works are generally pretty high quality, I don't find myself citing them very often.
+This might be because are packaged to be relevant when searched - breaking a large project with different components into a series of papers probably makes it more useful for later readers.
+
+\rule{\linewidth}{0.2pt}
+
+Peer review is pretty helpful. external input can dissuade you from the apparently frivolous but essential deviations that seem pretty helpful, but in general
 

### 2021-03-27 documents/pure_electroporation.tex
Transmembrane library

@@
 
-As a followup to \cite{notes2021}
+As a followup to a technical report \cite{notes2021} on inducing
+
+There, the relevant time constants referred to the viscous loss of energy into the surrounding medium and the normal modes of the viral envelope; here the time constants relate to ion diffusion and capacitive charging.
+
+There the relevant damage quantities were mechanical displacement and membrane stress; here we consider transmembrane voltage and pore diameter.
+
+At the risk of self-plagarism, we will restate precedent
 
@@
 
-At the risk of spending more time producing underpowered "scientifically useless" results,
+Electroporation\cite{Electroporation1988}, now a common laboratory procedure, occurs when an enormous electric field causes ions in solution to diffuse across a cell membrane, capacitively charging it, provoking a change in lipid bilayer conformation\cite{Membrane2016}, reversibly rendering the membrane permeable.
+This is one among many other, more subtle mechanisms; the minutia of poration can become extraordinarily complex in certain circumstances and are beyond the author's current understanding\cite{Theoretical2007}.
+Hydrodynamic
+
+Therapies based on irreversible electroporation\cite{Nonthermal2013}\cite{Lipid2017} have recently been used in the clinic\cite{Irreversible2013} for tumor ablation.
+There is much discussion on electroporation as an alternative to viral vectors, but we have found surprisingly little discussion on clinical treatment of viral infection with these conventional electroporation therapies.
+
+However, long pulses at $\approx10$ MV/m appear to electroporate large enveloped viruses, similarly to host cells\cite{AC2017}
+
+There is a single report of the electroporation of HIV in the literature.
+This one of very few reports involving the electroporation of viruses, reporting the ~95\% inactivation of HIV  using a standard commercial Bio-Rad electroporation system at 2.3 MV/m.
+However, the authors appear to commit such an egregious breach of human research ethics that we cannot cite them here.
+
+ which we believe might hint that a regime of intensity, duration, and pulse count may exist to target the viral envelope.
+
+Despite considering the somewhat harder problem of electroporating while inside the cell, rather than in extracellular fluid, \cite{Electroporation2013} report that 250 nm liposomes should be porated without inducing damage to the host cell, and modelling shows that 100 nm liposomes may be porated by 4 ns pulses never exceeding 20 MV/m.
+
+The same field intensities do not appear to damage phages with protein capsids\cite{Manipulation2013}, in line with our negative results on T4.
+
+Non-resonant capsid and envelope breakage with 120 pulses, 500 ns each, at 3 MV/m, has been previously observed\cite{Inactivation1990}, but the RNA damage suggests that this is an electrochemical artifact \cite{Formation1996} (c.f.
+\cite{Microwave1987}).
 
@@
 
-A serious danger would be that if a nuclear or organelle membrane were to be porated, viral ssRNA may be admitted to places it shouldn't be.
-The author does not have the biology experience to evaluate this risk.
+As in the previous paper, bulk dielectric properties of tissues are given by Gabriel.
 
@@
 
+This seems to hint that electroporation occurs at the same order of magnitude field as host cells.
+
 Of course, unlike localized tumors, viral infections are systemic, affecting many of the most favoured organs. However, either blood
 
-Note that, mostly contrary to these observations,
+Note that, mostly contrary to these observations, it is not unambiguously
 
+Note that, despite clear evidence in nanosecond review, microsecond in vivo and clinical treatment, nanosecond in vivo conduction, and, a review of in vivo data has not yet found any evidence demonstrating electroporation via pulsed RF.
+
+This property is 
 \cite{Nanosecond2006b}
@@
 
+Viruses have extraordinary mechanical properties\footnote{Why is this?
+What selection pressures drive this selected pressure?}, so it seems reasonable that their dielectric properties may differ substantially from that of other structures.
+In the case of bacteriophages, the genome is packaged so tightly that the core is best considered an amorphous, glass-like material.
+ssRNA viruses like coronaviridae are perhaps somewhat less .
+On the other hand, the human "structome"
+
+At the risk of spending more time producing underpowered "scientifically useless" results,
+
 \subsection*{Basic scaling laws}
@@
 Some extremely simplified scaling laws for membrane charging effects due to short (sub Tc) pulses are given by Schoenbach \cite{Bioelectric2007}.
-These are based primarily on an equivalent circuit model.
+This is based primarily on an equivalent circuit model, we largely neglect the electrodynamics that apply with short pulses and also the conductivity change due to pore formation.
+Electroporation is a highly nonlinear effect\cite{Letter1974}, and this .
 
-The membrane charging time constant from a single-shell model \cite{Ultrashort2004} - simplified for the low-density case
+The membrane charging time constant from a single-shell model \cite{Ultrashort2004} - simplified for the low-density case.
+As the fraction, and papers citing this usually mention that this may not be representative of charging time in tissue.
 
@@
 where $\rho_{medium}$ and $\rho_{internal}$ are the resistivities of the medium and internal fluid (the cytoplasm for cells, and assumed to be the 'core' for viruses).
-Electroporation is a highly nonlinear effect, and this .
+Note that this time constant is unrelated to the relaxation time constant discussed in the previous paper, which was purely mechanical.
 \cite{Bioelectric2007} eq.
@@
 
-The dielectric properties of viruses have been determined by the fascinating technique of electrorotation (and dielectrophoresis).
-There is some variation in reported values.
-The internal core permittivity of viruses is often referred to as being about 2 to 3 (Brackley \cite{Electrostatic2020}, SARS-CoV-2; and Schnelle \cite{Trapping1996}, Sendai and Influenza A) - however, Gimsa \cite{New1999}, on influenza, and Hughes\cite{Dielectrophoretic2001} on HSV-1 both suggest an internal $\epsilon_r$ of 30.
+The dielectric properties of viruses have been determined by the fascinating technique of electrorotation, dielectrophoresis, and dielectric spectroscopy.
+To prevent fluid heating, these are often conducted in low osmotic strength media.
+Enveloped viruses are permeable to small ions, and so some results may not necessarily representative of conductivities in physiological conditions; \cite{Assessment}.
+
+The internal core permittivity of viruses is often referred to as being about 5 to 3 (Brackley \cite{Electrostatic2020}, SARS-CoV-2; and Schnelle \cite{Trapping1996}, Sendai and Influenza A) - however, Gimsa \cite{New1999}, on influenza report that the internal $\epsilon_r$ is probably closer to 30.
+Hughes on HSV-1 originally suggest 80\cite{Manipulation1998}, then refine to 30\cite{Dielectrophoretic2001}.
 We have not investigated this discrepancy.
-The internal permittivity of impermeable viruses depends on the growth medium's osmotic strength\cite{Osmotic2003}, so results with different media may not be comparable.
+The internal osmotic strength of some viruses depends direclt on the growth medium's osmotic strength\cite{Osmotic2003}, so results with different media may not be comparable.
+Aggregation of viruses may also be a relevant artifact.
 
-In electrorotation, it is usually found that the viral shell has a permittivity of about 60 to 80, similar to the nuclear membrane (60 to 100) but massively unlike the cell membrane ($\epsilon_r\approx 10$).
-This is very remarkable, since the lipid bilayer itself is somewhat similar in composition to the host cell; envelope, spike and membrane proteins may account.
+Via electrorotation, it is usually found that the viral shell has a permittivity of about 60 to 80, similar to the nuclear envelope (60 to 100) but massively unlike the cell membrane ($\epsilon_r\approx 10$).
+This is very remarkable, since the lipid bilayer itself is somewhat similar in composition to the host cell, and the proteins that are stuck into it permittivity is generally assumed to be only about 4.
+Envelope, spike and membrane proteins may perhaps account for the discrepancy?!?
+
+On the other hand, \cite{Electrostatic2020a} use a membrane value of 4.
+
+want to more accurately represent the - most importantly, the core permittivity seems like it should alter the reflection significantly at high frequencies, but isn't usually treated
 
@@
 However, Gimsa and Hughes use a shell thickness of 18 and 15 nm, respectively, to account for the membrane proteins and hemaglutinase.
-The $C_{envelope}$ may therefore fall within the range $2.9 \text{ to } 17.7 \text{ uF/cm}^2$.
+The $C_{envelope}$ may therefore be expected to fall within the range $2.9 \text{ to } 17.7 \text{ uF/cm}^2$.
 
+Basic dry-weight measurements seem to suggest that influenza contains about 60\% water by weight \cite{lauffer1944biophysical}.
+Has diffusion coefficients and maintains a Donnan ion size equilibrium similar to that of lipid bilayers \cite{Effect2015b}.
+
+% should this be noweb python? python isn't really unit aware though
+% maybe sympy or something?
+% ooh we could have the supplemental appendix written right inline with noweb, 
+% also python could print the equation back to latex
+
+% Viral envelope capacitance per area:
 % >>> (80 * electricConstant) / 4 nanometers -> 17.7 uF/cm^2
 % >>> (60 * electricConstant) / 18 nanometers -> 2.9514 uF/cm^2
+% Actual envelope capacitance:
+% >>> 17.7 uF/cm^2 * 4 * pi * (50 nm)^2 -> 5.56 fF
+% >>> 2.95 uF/cm^2 * 4 * pi * (50 nm)^2 -> 0.92 fF
+% Actual envelope resistance:
+%
 
-Gimsa and Schnelle data on influenza seems to suggest a core conductivity of 0.1 to 1 milliSiemens/m (1000 to 10000 $\Omega \cdot m$), far less conductive than cytoplasm or nucleoplasm, at about 1 S/m (1 $\Omega \cdot m$) \cite{Study2001}.
+Critically, Gimsa and Schnelle data, both on influenza, seems to suggest a core conductivity of 0.1 to 1 milliSiemens/m (1000 to 10000 $\Omega \cdot m$).
+This is far less conductive than cytoplasm or nucleoplasm, each on the order of 1 S/m (1 $\Omega \cdot m$) \cite{Study2001}.
+
+However, Hughes suggests 30 mS/m for HSV-1, a significant discrepancy.
+Unlike influenza, HSV-1 has a complete protein capsid rather than a helical nucleocapsid.
+Protein capsids are typically regarded as monolithic and impermeable, whereas enveloped viruses are permeable, and therefore the ionic strength of the medium may be very important.
+No other sources of data on permittivity ion mobility in enveloped viruses were found.
+\footnote{Special thanks to Professor Jan Gimsa for replying to my email!}
 
 The viral envelope appears to be slightly less conductive than the cell membrane (0.1 $\micro$S/m \cite{New1999} vs 10 $\micro$S/m \cite{Study2001}), and far less conductive than the nuclear envelope (0.1 $\text{m}$S/m \cite{Study2001}).
-This ratio is the relevant quantity to find the steady state transmembrane voltage for long pulses (before pore conduction becomes relevant).
+%This ratio is the relevant quantity to find the steady state transmembrane voltage for long pulses (before pore conduction becomes relevant). gotta look into "interfacial / surfaec conductance"
 
-The time constant of the virus therefore appears to be between 7 and 44 us, compared to about 100 ns for most host cells, the discrepancy mainly contributed by the internal core conductivity and the shell permittivity.
+% is the relaxation time quoted in some papers the one we're looking for here? alfalfa is 600 ns, is that a better, more direct value?
 
-At first glance, this may seem unfortunate: the host will be destroyed far before the virus.
+The dielectric properties of viruses do appear to differ considerably from the host, the discrepancy mainly in the internal core conductivity and perhaps the envelope permittivity.
+Despite this, because of the small radius of the virus, the first time constant of the virus transmembrane might plausibly range anywhere between 50 ns and 90 us, compared to between 100 ns and  for the both the plasma membrane and the nucleus.
 
-However, if a monopolar pulse train with a pulse duration shorter than the cell time constant, an intensity too low for, and a repetition rate of some 3 us, (200 khz),
+% Virus time constant:
+% >>> (((1 ohm m) / 2) + (1000 ohm meter)) * 2.9 uF/cm^2 * 50 nanometer -> 1.45 us
+% >>> (((1 ohm m) / 2) + (10000 ohm meter)) * 17.7 uF/cm^2 * 50 nanometer -> 44.25 ns
+% Host time constant:
+% (already given by others, 100 ns)
+% Nucleus time constant:
+% using data from feldman paper,
+% (Must be very careful regarding S/m, mS/m, etc!)
+% >>> (((1 ohm m) / 2) + (1 ohm meter)) * 1.5 uF/cm^2 * 3 um -> 67.5 ns
+% that's interesting, because it conflicts somewhat with shoenbach's suggestion that the nucleus has a longer time constant.
 
-This is unlike the 'killing blow' described in Schoenberterg where pores have already formed.
+%At first glance, this may seem unfortunate: the host will be electroporated far before the virus.
+%However, if a monopolar pulse train with a pulse duration shorter than the cell time constant, an intensity too low for, and a repetition rate of some 3 us, (200 khz),
 
-% 1 Ohm m / 2 + 5000 ohm meter * 2.9 uF/cm^2 * 50 nm
+\subsection{Electrodynamic considerations}
 
-%Is the effect replicable, or is it simply an electrochemical artifact?
+Kotnik note an important fact: all these permittivity and conductivity values will also depend on frequency, which is not included in their model.
+We have not examined how these factors can be extracted from
+
+The necessity for the Laplace transform over the Fourier-based method used for the precursor propagation in the previous report is founded in the requirement for a fully transient solution with a definite t=0.
+
+% Is the effect replicable, or is it simply an electrochemical artifact?
 Will these nanopores be destructive to viruses - will the pores be open for sufficient time for the ssRNA to be released?
@@
 
+% A serious danger would be that if a nuclear or organelle membrane were to be porated, viral ssRNA may be admitted to places it shouldn't be.
+The author does not have the biology experience to evaluate this risk.
+
 \end{document}

### 2021-03-28 biology/transmembrane/transmembrane_lib.py
Transmembrane

@@ -2,10 +2,12 @@ from dataclasses import dataclass
 from math import pi, sqrt, e, log, isclose, exp
 # from scipy.optimize import curve_fit
 # import numpy as np
+from numpy import heaviside
 # import matplotlib.pyplot as plt
 # import h5py
 from scipy.constants import epsilon_0, mu_0
 
+ustep = heaviside
 
 outer_radius_R = 0
 membrane_thickness_d = 0
@@ -27,6 +29,8 @@ Time course of transmembrane voltage induced by time-varying electric fields—a
 Bioelectrochemistry and Bioenergetics 1998;45:3–16.
 https://doi.org/10.1016/S0302-4598(97)00093-7.
 
+Kotnik et al also have number of other papers with minor variations that may be of some use
+
 If a truly arbitrary
 the equivalent of the discrete fourier transform for the Laplace transform appears to be the Z-transform.
 
@@ -42,7 +46,7 @@ def tau_2_f(b_1, b_2, b_3):
 
 
 
-def delta_transmembrane_trapezoidal(t, start_time, a_1, a_2, b_3, R):
+def delta_transmembrane_unit_ramp(t, start_time, R):
 
     l_o = conductivity_extracellular # S/m
     l_i = conductivity_intracellular #S/m
@@ -58,12 +62,20 @@ def delta_transmembrane_trapezoidal(t, start_time, a_1, a_2, b_3, R):
 
     b_1 = 2.0 * R**3.0 * (l_m + 2.0*l_o) * (l_m + 0.5 * l_i) + 2.0 * (R-d)**3.0 * (l_m - l_o) * (l_i - l_m)
 
-    b_2 = 2.0 * R**3.0 * (l_i * (0.5 * e_m + e_o) + l_m * (0.5*e_i + 2.0*e_m + 2*e_0) + l_0 * (e_i + 2.0 * e_m)) + (2.0 * (R - d)**3.0 * (l_i * (e_m - e_0) + l_m * (e_i - 2.0*e_m + e_o) - l_0 * (e_i - e_m))) # is this truly a multiply, or a cross?
[…]

### 2021-03-29 documents/pure_electroporation.tex
Electroporation
Transmembrane
Triangle wave works

@@
 %!TeX root = pure_electroporation
-\documentclass[fleqn,10pt]{article}
+\documentclass[fleqn,10pt]{paper}
+
+\usepackage[left=2cm,right=2cm,
+top=0.5cm,
+bottom=1.5cm,%
+headheight=11pt,%
+letterpaper]{geometry}
 
 \include{preamble}
+
 \begin{document}
@@
 \title{Selective electroporation of the viral envelope}
-\author{\small{Daniel Correia\orcidlink{0000-0002-9353-0216} (therobotist@gmail.com), Ontario, Canada.}}
-\date{March 21 2021}
+\author{\footnotesize{Daniel Correia\orcidlink{0000-0002-9353-0216} \footnote{therobotist@gmail.com, Ontario, Canada.}}}
+\date{\small{March 21 2021}}
 
 \flushbottom 
+%%\maketitle
+%\begingroup
+%\let\center\flushleft
+%\let\endcenter\endflushleft
 \maketitle
+%\endgroup
+
 \thispagestyle{empty}
@@
 As a followup to a technical report \cite{notes2021} on inducing
+
+Electroinsertion of proteins into membranes\cite{Clinical1996}; to provoke a local immune response near affected tissues,
 
@@
 \cite{Microwave1987}).
+
+The trapping experiments we use were conducted at
 
@@
 
-Critically, Gimsa and Schnelle data, both on influenza, seems to suggest a core conductivity of 0.1 to 1 milliSiemens/m (1000 to 10000 $\Omega \cdot m$).
+Critically, Gimsa and Schnelle data, both on influenza, seems to suggest a core conductivity of 0.8 to 0.1 milliSiemens/m (1000 to 10000 $\Omega \cdot m$), using a medium conductivity of 74 mS/m and 3 mS/m, respectively.
 This is far less conductive than cytoplasm or nucleoplasm, each on the order of 1 S/m (1 $\Omega \cdot m$) \cite{Study2001}.
+
+% if this is correct, scaling linearly:
+% like 60 % water in core  * (1 S/m / 0.074) would get us to 1 mS/m.
+
+% absolute pessimistic, using 0.8 mS/m and Schnelle's medium conductivity, would get us 0.008 * 0.6 * (1/0.003) = 1.6 S/m
 
@@
 
+Kotnik-simulchouski
+
+(Helmholz)
+
 % Is the effect replicable, or is it simply an electrochemical artifact?

### 2021-04-04 documents/pure_electroporation.tex
differential

@@
 \title{Selective electroporation of the viral envelope}
-\author{\footnotesize{Daniel Correia\orcidlink{0000-0002-9353-0216} \footnote{therobotist@gmail.com, Ontario, Canada.}}}
+\author{\footnotesize{Daniel Correia\orcidlink{0000-0002-9353-0216}}\footnote{therobotist@gmail.com, Ontario, Canada.}}
 \date{\small{March 21 2021}}
@@
 
-As a followup to a technical report \cite{notes2021} on inducing
+\lettrine{A}{s} a followup to a technical report \cite{notes2021}, presenting experimental data on protein capsid adjacent technique;
+
+There, the relevant time constants referred to the viscous loss of energy into the surrounding medium and the normal modes of the viral envelope; here the time constants relate to ion diffusion and capacitive charging.
+The relevant damage quantities were mechanical displacement and membrane stress, whereas here we consider transmembrane voltage and pore diameter.
 
 Electroinsertion of proteins into membranes\cite{Clinical1996}; to provoke a local immune response near affected tissues,
-
-There, the relevant time constants referred to the viscous loss of energy into the surrounding medium and the normal modes of the viral envelope; here the time constants relate to ion diffusion and capacitive charging.
-
-There the relevant damage quantities were mechanical displacement and membrane stress; here we consider transmembrane voltage and pore diameter.
 
@@
 The same electrostatic effects on lipid bilayers have been investigated for decades. Many extremely fascinating hydrodynamic and parametric
+
+ultracrepidarian
+
+on the other hand, the idea of shocking a virus is so basic that it can scarcely be believed
 

### 2021-04-04 biology/transmembrane/transmembrane_diffeq.py

@@ -1,0 +1,6 @@
+from sympy import *
+x, y, z = symbols('x y z')
+init_printing()
+expr = exp(x*y*z)
+deriv = Derivative(expr, x, y, y, z, 4)
+pprint(deriv)

### 2021-04-06 documents/pure_electroporation.tex
kotnik

@@
 Viruses have extraordinary mechanical properties\footnote{Why is this?
-What selection pressures drive this selected pressure?}, so it seems reasonable that their dielectric properties may differ substantially from that of other structures.
+What selection pressures drive the selected pressure?}, so it seems reasonable that their dielectric properties could differ substantially from that of other structures.
 In the case of bacteriophages, the genome is packaged so tightly that the core is best considered an amorphous, glass-like material.
 ssRNA viruses like coronaviridae are perhaps somewhat less .
-On the other hand, the human "structome"
+On the other hand, the human "structome" also contains countless lipid vesicles that might plausibly
+
+The most obvious difference is scale. Viruses are minute. The classic Schwan equation implies that the transmembrane voltage
 

### 2021-04-06 biology/transmembrane/transmembrane_diffeq.py

@@ -1,6 +1,0 @@
-from sympy import *
-x, y, z = symbols('x y z')
-init_printing()
-expr = exp(x*y*z)
-deriv = Derivative(expr, x, y, y, z, 4)
-pprint(deriv)

### 2021-04-08 documents/pure_electroporation.tex
Fiiine I'll do it numerically

@@
 
-There, the relevant time constants referred to the viscous loss of energy into the surrounding medium and the normal modes of the viral envelope; here the time constants relate to ion diffusion and capacitive charging.
+While both mechanisms time constants, those discussed in the previous paper referred to the viscous loss of energy into the surrounding medium and the normal modes of the viral envelope; here the time constants relate to capacitive charging and ion diffusion.
 The relevant damage quantities were mechanical displacement and membrane stress, whereas here we consider transmembrane voltage and pore diameter.
@@
 Viruses have extraordinary mechanical properties\footnote{Why is this?
-What selection pressures drive the selected pressure?}, so it seems reasonable that their dielectric properties could differ substantially from that of other structures.
-In the case of bacteriophages, the genome is packaged so tightly that the core is best considered an amorphous, glass-like material.
-ssRNA viruses like coronaviridae are perhaps somewhat less .
+What selection pressures drive the selection of this pressure?}, so it seems reasonable that their dielectric properties could differ substantially from that of other structures.
+
+In the extreme case of the bacteriophage, the genome is packaged so tightly into the protein capsid that the core is often described as a glassy crystal of DNA\cite{Conformation2007}.
+ssRNA viruses like coronaviridae are perhaps somewhat less.
+
 On the other hand, the human "structome" also contains countless lipid vesicles that might plausibly
-
-The most obvious difference is scale. Viruses are minute. The classic Schwan equation implies that the transmembrane voltage
 
@@
 \subsection*{Basic scaling laws}
+
+The most obvious difference is scale. Viruses are minute. The classic Schwan equation implies that the transmembrane voltage is proportional to
+
+There are two characteristic time constants; a low and a high-frequency one.
 
@@
 
+\subsection{Optimal pulse}
+
+This bears considerable similarity to e.g. radar waveform design and compressed sensing.
+
+Lagrange multipliers. Unfortunately, while closed-form solutions appear to be readily available for some simplified cases (such as when the membrane is infinitesimally thin),
+
+The impulse response is the derivative of the step response. The convolution integral (or sum, in the discrete case) can be performed
+
 % Is the effect replicable, or is it simply an electrochemical artifact?

### 2021-04-08 documents/pure_electroporation.tex
Convolution working properly

@@
 
+In a continued effort to which make ultracrepidarian physicist such as ourselves feel useful indirectly biological
+
 While both mechanisms time constants, those discussed in the previous paper referred to the viscous loss of energy into the surrounding medium and the normal modes of the viral envelope; here the time constants relate to capacitive charging and ion diffusion.
@@
 The same electrostatic effects on lipid bilayers have been investigated for decades. Many extremely fascinating hydrodynamic and parametric
-
-ultracrepidarian
 
@@
 Kotnik note an important fact: all these permittivity and conductivity values will also depend on frequency, which is not included in their model.
-We have not examined how these factors can be extracted from
+We have not examined how these factors can be extracted from.
+Also disregarded are the Poisson-boltzmann shielding space-charges that proved all-important in the last study.
 
@@
 
-Kotnik-simulchouski
-
-(Helmholz)
+Several groups have discussed optimizing
 
@@
 
-This bears considerable similarity to e.g. radar waveform design and compressed sensing.
+This bears considerable similarity to e.g. radar waveform design and compressed sensing, and also problems of optimal control.
 
-Lagrange multipliers. Unfortunately, while closed-form solutions appear to be readily available for some simplified cases (such as when the membrane is infinitesimally thin),
+Lagrange multipliers.
+Unfortunately, while closed-form solutions appear to be readily available for some simplified cases (such as when the membrane is infinitesimally thin or when permittivity is neglected) [schwan paper],
 
-The impulse response is the derivative of the step response. The convolution integral (or sum, in the discrete case) can be performed
+Kotnik discuss the transmembrane voltage due to several pulse shapes formed from the Laplace Transform of the original differential equation.
+Talele offer their own response due to an arbitrary waveform can be produced by
+
+The impulse response is the derivative of the step response.
+The convolution integral (or sum, in the discrete case) can be performed either with the derivative of the input function and the step response, or the impulse response and the input function as algebraic convenience demands.
+Unfortunately
+
+There exists an alternative convolution technique, due to the Convolution Property of the fourier transform.
+
+The fourier transform of both the impulse response and the step response exist, are analytic and of manageable size.
 

### 2021-04-11 documents/EPA_paper.tex
w

@@
 I can find no reference to such a conference in Annals of the NYAS, but it may be recorded in Transactions.
-It is a shame to see good work fade into the mist of time, especially since research in this field attained an acceptable level of quality even in the 1940s.
+It is a shame to see any work fade into the mist of time, especially since research in this field attained an acceptable level of quality even in the 1940s.
 O.

### 2021-04-12 documents/lessons_learned.tex
Fiiine I'll do it numerically
Using a real optimal control software

@@
 \section{Lessons Learned} \
+
+when you build a project, put aside a certain amount of money and time to justify helping future people
+
+At least with mathematics, it seems to generally be easier to find a starting point closer to your desired one than to work it out yourself.
+If you get stuck trying to massage things into a different representation, look harder for a different formulation.
+
+\rule{\linewidth}{0.2pt}
 

### 2021-04-14 documents/pure_electroporation.tex
relatively consistent convergence!
fft subtratction
Using a real optimal control software
Some work on the paper wording

@@
 
-	Dielectric properties apparently due to the
+	fortuitous Dielectric properties apparently due to the
 
@@
 
-\lettrine{A}{s} a followup to a technical report \cite{notes2021}, presenting experimental data on protein capsid adjacent technique;
+\lettrine{A}{s} an addendum to a technical report \cite{notes2021} by the author presenting experimental data on protein capsid adjacent technique;
 
@@
 
-While both mechanisms time constants, those discussed in the previous paper referred to the viscous loss of energy into the surrounding medium and the normal modes of the viral envelope; here the time constants relate to capacitive charging and ion diffusion.
+While both mechanisms hinge on time constants, those discussed in the previous paper referred to the viscous loss of energy into the surrounding medium and the normal modes of the viral envelope; here the time constants relate to capacitive charging, and Smoluchowski processes.
 The relevant damage quantities were mechanical displacement and membrane stress, whereas here we consider transmembrane voltage and pore diameter.
 
-Electroinsertion of proteins into membranes\cite{Clinical1996}; to provoke a local immune response near affected tissues,
+The breakdown of lipid membranes has proved to be an From initial studies of crude membrane breakdown effects \cite{Reversible1979}
+
+"...hit them [cells] with an electric field strong enough to knock over a horse, and they do enough things to justify international meetings, to fill a sizable book, and to lead one to speak of an entirely new technology for cell manipulation."
+
+It is, in general, something of a singular outlier in that it is one of very few biological mechanisms relevant at practical electric field intensities. It also something like integration, which is
+
+Electroinsertion of proteins into membranes\cite{Clinical1996}; to provoke a local immune response near diseased tissues,
 
@@
 The same electrostatic effects on lipid bilayers have been investigated for decades. Many extremely fascinating hydrodynamic and parametric
+
+The idea of inactivating viruses via electric fields is not new.
+Very recently, Osorio \cite{Receptor2021} have reported on a susceptibility of SARS-CoV-2's spike proteins to intense electric fields; however, in general, techniques targeting proteins appear to require truly extreme; in their study, fields of up to 2.9 GV/m were required.
+Dissocation of capsid proteins has been predicted by Man \cite{Picosecond2016b} at 2 GV/m.
+Similar techniques Tsen \cite{Studies2014}, but these have not been replicated \cite{No2011}.
+These regimes of intensity may possibly be accessible via ultrashort optical techniques.
 
@@
 As in the previous paper, we must stress that meaningful bioelectrics research hinges very strongly on experimental design and methodology, and very few results can be trusted implicitly.
+It appears to be very difficult to unambiguously determine cause and effect on a system as complex as a cell; especially when electrodes are in contact with solution and may release an energy-dependent dose of metal ions.
 
@@
 
-Note that, mostly contrary to these observations, it is not unambiguously
-
-Note that, despite clear evidence in nanosecond review, microsecond in vivo and clinical treatment, nanosecond in vivo conduction, and, a review of in vivo data has not yet found any evidence demonstrating electroporation via pulsed RF.
+Note that, despite clear evidence in nanosecond review, microsecond in vivo and clinical treatment, nanosecond in vivo conduction, and, The NATO review of vivo data regarding non-contact, "electrodeless", even above the thresholds that might otherwise be expected to cause electroporation.
+has not yet found any evidence demonstrating electroporation via pulsed RF.
+de Seze,
 
@@
 
-On the other hand, the human "structome" also contains countless lipid vesicles that might plausibly
+On the other hand, the cellular "structome" also contains countless lipid vesicles that might plausibly be damaged; small pockets of lipid in the endoplasmic reticula, Much like in drug discovery, we do not believe we can meaningfully predict all possible off-target effects.
 
@@
 
-Several groups have discussed optimizing
+The question of optimizing a pulse is not novel, having been discussed by many groups in the past. Retelj use a series of
 
@@
 
-This bears considerable similarity to e.g. radar waveform design and compressed sensing, and also problems of optimal control.
+This bears considerable similarity to e.g. radar waveform design and compressed sensing, and also problems of optimal control. In many cases, the optimal control is equal to the transfer function
+
+The time-domain response can be obtained by the convolution integral with the step or impulse response function, or by manually integrating the differential equation via some integrator.
 

### 2021-04-15 documents/lessons_learned.tex
Convert to differential equation
DoF error

@@
 \section{Lessons Learned} \
+
+the os community has figured out that investment in open work comes back;
+
+is there a way to "sign" gel images (maybe from the gel-doc itself?) so that manipulation is obvious?
+
+an interesting thing is searchability.
+I often don't come back to notes because it's easier and more likely I'll get a relevant result by googling again!
+future lab notebook should have a live and very effective search.
+
+Why do problems keep happening? Why do bugs which other people have hit keep recurring? Why does bad science even happen?
 

### 2021-04-15 documents/pure_electroporation.tex
Whoops, wrong transfer function!

@@
 
-	\noindent As pulse duration is reduced from the microsecond to nanosecond regime, effects targeting smaller intracellular structures are expected and observed.
+	\noindent As pulse duration is reduced from the microsecond to nanosecond regime, effects targeting smaller intracellular structures are expected and observed, and a degree of tunability arises.
 Indeed, pulses shorter than 10 ns have been observed to porate the nuclear envelope and organelle membranes while leaving the plasma membrane intact.

### 2021-04-18 documents/pure_electroporation.tex
got it in one
Integral constraint failing?

@@
 
+400x difference, reflected in the numerical steady state.
+
+However, not field-time product [analytic, ].
+
+Despite the two having nearly identical time constants, the course of the transmembrane voltage is clearly different.
+[transmembrane plot here]
+
+[gaussian pulse results, 1/2.7].
+
 The most obvious difference is scale. Viruses are minute. The classic Schwan equation implies that the transmembrane voltage is proportional to
@@
 
-that is, all else being equal, the induced transmembrane voltage appears to be invariant with raw particle diameter - mildly contrary to Rjif's more detailed analysis.
+that is, all else being equal, the induced transmembrane voltage appears to be invariant with particle diameter - mildly contrary to Rjif's more detailed analysis.
 

### 2021-04-19 documents/pure_electroporation.tex
Apparent success once again?

@@
 
+For use with GEKKO, the transfer function was converted into a system of differential equations:
+
+For PSOPT, a further modification was needed, as the library does not support the derivative of the control during .
+
+Initial guess of 0 produces a trap.
+
+because the problem depends on the second derivative of sub-nanosecond curves, the scaling varies by about 30 orders of magnitude.
+PSOPT [] with IPOPT\cite{implementation2006} solver.
+
 % Is the effect replicable, or is it simply an electrochemical artifact?

### 2021-04-19 documents/lessons_learned.tex
rk4 integrator
PSOPT constants calculation
good lord it's done

@@
 \section{Lessons Learned} \
+
+Made a bonehead mistake while installing lanl-ansi fork of Ipopt.
+While screwing around in the very beginning, I had accidentally added to -L to the LDFLAGS environment variable.
+This completely broke the installation.
+I spent almost 4 hours trying to figure that out.
+I suppose having a list of commands would perhaps improve things...
+
+LLIS
+
+write in the highest-level language first , then translate.
 
@@
 Why do problems keep happening? Why do bugs which other people have hit keep recurring? Why does bad science even happen?
+laser power supply troubles paper
 

### 2021-04-20 documents/pure_electroporation.tex
Using LLNL-ANSI lpopt
Switched from spral to HSL now that I got the email

@@
 
-The time-domain response can be obtained by the convolution integral with the step or impulse response function, or by manually integrating the differential equation via some integrator.
+The time-domain response can be obtained from the step or impulse response function by evaluating the convolution integral, or by manually integrating the differential equation via some integrator.
 
@@
 
-The fourier transform of both the impulse response and the step response exist, are analytic and of manageable size.
+The fourier transform of both the impulse response and the step response exist, are analytic and of manageable size; however, the integral of the cost function is extremely unweildy.
+
+\subsection{Optimal control solvers}
+
+An excellent overview of solutions http://plato.asu.edu/sub/nlounres.html
 
@@
 
-For PSOPT, a further modification was needed, as the library does not support the derivative of the control during .
+For PSOPT, a further modification was needed, as the library does not support the derivative of the control.
 
@@
 because the problem depends on the second derivative of sub-nanosecond curves, the scaling varies by about 30 orders of magnitude.
-PSOPT [] with IPOPT\cite{implementation2006} solver.
+PSOPT [] with IPOPT\cite{implementation2006} solver. PSOPT has the advantage of semi-automatic scaling based on bounds.
+
+Both PSOPT and GEKKO's APMonitor backend use the famous ipopt solver.
+A number of linear solvers can be used.
+LANL's Tasseff's integration with the SPRAL solver, reportedly faster on large problems, was
+
+It was found very useful to test the
+
+A hard-to-detect lack of convergence would often produce a fallacious simulated output from PSOPT.
+To double-check that the solution was actually valid, the output was fed through the convolution integral method.
+
+Considerable difficulty was encountered.
+
+\subsection{Optimal control solvers}
 

### 2021-04-21 documents/pure_electroporation.tex
Big attempt
Very large problem size

@@
 The idea of inactivating viruses via electric fields is not new.
-Very recently, Osorio \cite{Receptor2021} have reported on a susceptibility of SARS-CoV-2's spike proteins to intense electric fields; however, in general, techniques targeting proteins appear to require truly extreme; in their study, fields of up to 2.9 GV/m were required.
+Very recently, Osorio \cite{Receptor2021} have reported on a susceptibility of SARS-CoV-2's spike protein to intense electric fields; however, in general, techniques targeting proteins appear to require truly extreme; in their study, fields of up to 2.9 GV/m were required.
 Dissocation of capsid proteins has been predicted by Man \cite{Picosecond2016b} at 2 GV/m.
-Similar techniques Tsen \cite{Studies2014}, but these have not been replicated \cite{No2011}.
+
 These regimes of intensity may possibly be accessible via ultrashort optical techniques.
+Similarly, Tsen \cite{Studies2014} report a non-electroporative mechanism, but these results have not been replicated at that intensity\cite{No2011}.
 
@@
 
-Of course, unlike localized tumors, viral infections are systemic, affecting many of the most favoured organs. However, either blood
+Of course, unlike localized tumors, viral infections are systemic, affecting many of the most favoured organs.
 
-Note that, despite clear evidence in nanosecond review, microsecond in vivo and clinical treatment, nanosecond in vivo conduction, and, The NATO review of vivo data regarding non-contact, "electrodeless", even above the thresholds that might otherwise be expected to cause electroporation.
+Note that, despite clear evidence in [nanosecond review], microsecond in vivo and clinical treatment, nanosecond in vivo conduction, and, The NATO review of vivo data regarding non-contact, "electrodeless", even above the thresholds that might otherwise be expected to cause electroporation.
 has not yet found any evidence demonstrating electroporation via pulsed RF.
@@
 
-This bears considerable similarity to e.g. radar waveform design and compressed sensing, and also problems of optimal control. In many cases, the optimal control is equal to the transfer function
+This bears considerable similarity to e.g.
+radar waveform design and compressed sensing, and also problems of coherent control in quantum systems.
+In many cases, the optimal control is equal to the transfer function
+
+single input, multiple output
+
+"Underactuated";
 
@@
 
-\subsection{Optimal control solvers}
+\subsection{direct method Pseudospectral solvers}
 
@@
 
-For PSOPT, a further modification was needed, as the library does not support the derivative of the control.
+For PSOPT, a further modification was needed, as the library does not support the derivative of the control; the second derivative was used as the control.
 
-Initial guess of 0 produces a trap.
-
-because the problem depends on the second derivative of sub-nanosecond curves, the scaling varies by about 30 orders of magnitude.
-PSOPT [] with IPOPT\cite{implementation2006} solver. PSOPT has the advantage of semi-automatic scaling based on bounds.
+because the problem depends on the second derivative of sub-nanosecond curves, the scaling varies by about 20 orders of magnitude.
+PSOPT [] with IPOPT\cite{implementation2006} solver. PSOPT has the advantage of semi-automatic scaling based on supplied bounds.
 
@@
 
-It was found very useful to test the
+It was found very useful to test the equation setup by first propagating a test using a standard integrator (PSOPT's rk4 or mode 4).
 
@@
 Considerable difficulty was encountered.
+
+First the objective function with an integral power constraint was used, but this did not yield
 

### 2021-04-26 documents/lessons_learned.tex
Very large problem size
iLQR

@@
 \section{Lessons Learned} \
+
+I've just realized something.
+
+Experience.
+When I run a simulation and it errors out, the root cause of that error is *experience*.
+The plot that I generated and glanced over to inform the next set of parameters is *experience*.
+The way you pipette 0.5 uL of fluid is experience.
+
+maybe we need to digitize the experience of science.
+
+talk about the electroporation book saying that more effort in standardization is needed
+
+%I hope that software should be written in a manner that is easy to support. This means documentation; reproducible builds;
+
+Not a fan of fortran, but it's actually remarkable in its longevity. A fortran code listing from the 1970s actually has a fair chance of running; has no dependencies, fully self-contained, etc.
 

### 2021-04-26 documents/pure_electroporation.tex
iLQR

@@
 \begin{abstract}
-	\noindent The phenomenon of electroporation occurs when extreme applied electric fields in the MV/m range drive transmembrane potentials, leading to pores through membranes; this is commonly harnessed for transfection into the cell in the laboratory, and has recently been shown to be safe and effective in the clinic for ablating tumors.\\
+	\noindent The phenomenon of electroporation occurs when extreme applied electric fields in the MV/m range drive transmembrane potentials, leading to pores in, and perhaps the destruction of, membranes; this is commonly harnessed for transfection into the cell in the laboratory, and has recently been shown to be safe and effective in the clinic for the ablation of tumors.
 
@@
 Indeed, pulses shorter than 10 ns have been observed to porate the nuclear envelope and organelle membranes while leaving the plasma membrane intact.
-\\
 
@@
 
-	\noindent Recently-developed gigawatt pulse systems may offer a possible means of noninvasively propagating such pulses into deep tissues, such as within lungs. 
+	\noindent Recently-developed multi-gigawatt electrical pulse systems may offer a possible means of noninvasively propagating such pulses into deep tissues, such as within lungs. 
 \end{abstract}
 
-\lettrine{A}{s} an addendum to a technical report \cite{notes2021} by the author presenting experimental data on protein capsid adjacent technique;
+\lettrine{A}{s} an addendum to a crude technical report \cite{notes2021} by the author, presenting some experimental results on an adjacent technique
 
-In a continued effort to which make ultracrepidarian physicist such as ourselves feel useful indirectly biological
+At the risk of spending more time producing underpowered "scientifically useless" results,
 
-While both mechanisms hinge on time constants, those discussed in the previous paper referred to the viscous loss of energy into the surrounding medium and the normal modes of the viral envelope; here the time constants relate to capacitive charging, and Smoluchowski processes.
+In a continued effort to make ultracrepidarian physicists such as ourselves feel useful
+
+While both mechanisms hinge on time constants, those discussed in the previous paper referred to the time for viscous loss of energy into the surrounding medium and the normal modes of the viral envelope; here the time constants relate to capacitive charging, and Smoluchowski processes.
 The relevant damage quantities were mechanical displacement and membrane stress, whereas here we consider transmembrane voltage and pore diameter.
 
-The breakdown of lipid membranes has proved to be an From initial studies of crude membrane breakdown effects \cite{Reversible1979}
+At the risk of self-plagarism, we will restate some precedent
 
-"...hit them [cells] with an electric field strong enough to knock over a horse, and they do enough things to justify international meetings, to fill a sizable book, and to lead one to speak of an entirely new technology for cell manipulation."
+The field-induced breakdown of lipid membranes has proved to be a particularly useful property of the cell. From initial studies of crude membrane breakdown effects \cite{Reversible1979}
 
-It is, in general, something of a singular outlier in that it is one of very few biological mechanisms relevant at practical electric field intensities. It also something like integration, which is
+hit "with an electric field strong enough to knock over a horse, and they do enough things to justify international meetings, to fill a sizable book, and to lead one to speak of an entirely new technology for cell manipulation."
+
+It is, in general, something of a singular outlier in that it is one of very few biological mechanisms relevant at practical electric field intensities.
+Along with thermal treatment, it also performs an operation something like integration, distinct from absolute-value.
+It is perhaps this property which provides a small degree of tunability.
+
+\footnote{It is amusing to draw parallels between electroporation and Bialke et al's reports on spacecraft reaction wheels.
+In both cases, destructive process are charging of the external shell (the spacecraft itself), a highly resistive layer (a layer of grease on the ball bearings), and a }
+
+Varactor-like parametric, as the bilayer is squished by the potential;
 
 Electroinsertion of proteins into membranes\cite{Clinical1996}; to provoke a local immune response near diseased tissues,
-
-At the risk of self-plagarism, we will restate precedent
 
@@
 
-There is a single report of the electroporation of HIV in the literature.
+There is a single report of the electroporation of HIV in the gray literature.
 This one of very few reports involving the electroporation of viruses, reporting the ~95\% inactivation of HIV using a standard commercial Bio-Rad electroporation system at 2.3 MV/m.
-However, the authors appear to commit such an egregious breach of human research ethics that we cannot cite them here.
+However, the authors appear to have committed such an egregious breach of research ethics that we cannot cite them here.
 
@@
 
-Note that, despite clear evidence in [nanosecond review], microsecond in vivo and clinical treatment, nanosecond in vivo conduction, and, The NATO review of vivo data regarding non-contact, "electrodeless", even above the thresholds that might otherwise be expected to cause electroporation.
+Note that, despite clear evidence in [nanosecond review], microsecond in vivo and clinical treatment, nanosecond in vivo conduction, and, The NATO review concluded that evidence did not support non-contact, "electrodeless", even above the thresholds that might otherwise be expected to cause electroporation.
 has not yet found any evidence demonstrating electroporation via pulsed RF.
+
 de Seze,
+
+that said, the reviews of the ICNIRP [that 18 GHz  paper]
 
@@
 In the extreme case of the bacteriophage, the genome is packaged so tightly into the protein capsid that the core is often described as a glassy crystal of DNA\cite{Conformation2007}.
-ssRNA viruses like coronaviridae are perhaps somewhat less.
+ssRNA viruses like coronaviridae might be expected to be somewhat more sedate, but this does not seem to be borne out in the core conductivity data.
 
-On the other hand, the cellular "structome" also contains countless lipid vesicles that might plausibly be damaged; small pockets of lipid in the endoplasmic reticula, Much like in drug discovery, we do not believe we can meaningfully predict all possible off-target effects.
-
-At the risk of spending more time producing underpowered "scientifically useless" results,
+On the other hand, the cellular "structome" also contains countless vesicles and structures of similar nature that might plausibly be damaged; small pockets of lipid in the endoplasmic reticula - nuclear pore complexes, etc.
+This appears to be borne out in Gabriel's data; dense tissues exhibit many .
+It may not be possible to meaningfully predict all possible off-target effects, much like in drug discovery.
 
@@
 
-400x difference, reflected in the numerical steady state.
+The most obvious difference is scale.
+Viruses are minute.
+All other properties of the, the classic Schwan equation implies that the steady-state DC transmembrane voltage is proportional to the size of the particle.
+
+Madiyar's Vaccinia electroporation data aligns with. Assuming that the host porates at 0.05 MV/m, the 250 nm vaccinia might be expected to have a threshold of 4 MV/m.
+
+However, this does not explain
+
+%1/(250e-9 / 20e-6)
+
+400x difference, reflected in the numerical steady state simulations.
 
@@
 [gaussian pulse results, 1/2.7].
-
-The most obvious difference is scale. Viruses are minute. The classic Schwan equation implies that the transmembrane voltage is proportional to
 
@@
 
+Differential
+
 This bears considerable similarity to e.g.
@@
 "Underactuated";
+
+two plant
 

### 2021-04-27 documents/pure_electroporation.tex
Spinning off fdtd into submodule

@@
 
-For PSOPT, a further modification was needed, as the library does not support the derivative of the control; the second derivative was used as the control.
+For PSOPT, a further modification was needed, as the library does not support the derivative of the control; the second derivative was used as the control, and input into a differential-algebraic equation form.
 
@@
 
-First the objective function with an integral power constraint was used, but this did not yield
+First the objective function with a constant integral control power constraint was used, but this did not yield
 

### 2021-04-28 documents/supplemental.tex
Rewording text slightly in case biorxiv is a good idea
1/2 possibly?

@@
 \rule{\linewidth}{0.2pt}
-
-Conductors are represented by zeroing all components of the electric field in those regions.
-
-There are many different possible source geometries, each introducing their own distortions.
-
-There are many ways of linking SPICE and FDTD.
+%
+%Conductors are represented by zeroing all components of the electric field in those regions. 
+%
+%There are many different possible source geometries, each introducing their own distortions.
+%
+%There are many ways of linking SPICE and FDTD.
 
@@
 
-\rule{\linewidth}{0.2pt}
-
-NGSPICE's KSPICE coupled transmission lines require the capacitance and inductance per unit length in Maxwell matrix form, rather than the physical $C_{even}$/$L_{even}$ (each line's capacitance and inductance to ground) and $_{odd}$ (between elements) form provided by tools like wcalc.
+%\rule{\linewidth}{0.2pt}
+%
+%NGSPICE's KSPICE coupled transmission lines require the capacitance and inductance per unit length in Maxwell matrix form, rather than the physical $C_{even}$/$L_{even}$ (each line's capacitance and inductance to ground) and $_{odd}$ (between elements) form provided by tools like wcalc.
 "matrix not positive definite".
 [Schutt-Aine] discusses this; we reproduce here for convienience.
-
-\[ L_{11} = L_{22} = L_{even}  \]
-\[ L_{12} = L_{21} = L_{odd}  \]
-\[ C_{11} = C_{22} = C_{even}+C_{odd}  \]
-\[ C_{12} = C_{21} {\it{(unused)}} = -C_{odd}  \]
-
-\rule{\linewidth}{0.2pt}
-
-In practice, the timestep required to obtain convergence in particularly tight corners of the SPICE simulation can drop to 1e-20, which is far below the Courant limit of the FDTD simulation.
+%
+%\[ L_{11} = L_{22} = L_{even}  \]
+%\[ L_{12} = L_{21} = L_{odd}  \]
+%\[ C_{11} = C_{22} = C_{even}+C_{odd}  \]
+%\[ C_{12} = C_{21} {\it{(unused)}} = -C_{odd}  \]
+%
+%\rule{\linewidth}{0.2pt}
+%
+%In practice, the timestep required to obtain convergence in particularly tight corners of the SPICE simulation can drop to 1e-20, which is far below the Courant limit of the FDTD simulation.
 To eek out a bit more performance, a simple adaptive-timestep technique from [ a ] is used; we simply set the timestep so that the maximum change in voltage per timestep from the SPICE portion is less than
-some threshold.
+%some threshold.
 
@@
 
-\clearpage
-\PRLsep{ Wherein antennas are characterized}
-
-Method-of-moments solvers like NEC-2 are the standard for simulating these sorts of antennas.
+%
+%\clearpage
+%\PRLsep{ Wherein antennas are characterized}
+%
+%Method-of-moments solvers like NEC-2 are the standard for simulating these sorts of antennas.
 However, most commonly-available packages don't seem to handle multiple dielectric constants, such as the air and substrate of a patch antenna.
-
-The impedance of a structure over frequency can be determined in FDTD by:
-
-\begin{itemize}
-  \item Applying a gaussian pulse to a voltage source - in our case, applied to a via connecting the path (or probe)
-  \item Running the simulation until the transients have all died out below some threshold, while logging the source voltage and current at each timestep
-  \item Taking the fourier transform of the (real) excitation voltage and current (producing a complex result, mind you)
-  \item Taking the magnitude of the ratio of the two complex spectra.
-\end{itemize}
-
-This is the computational equivalent of dropping a piano off a balcony to see which key is stuck.
-
-See [Penney 1994], [Luebbers 1992], [Luebbers 1991], [Luk 1997].
-
-Our implementation is in \ghfile{electronics/simple_fdtd/runs/U.py}.
-
-A similar mismatch to the SPICE exists for fourier methods - but in the other direction.
+%
+%The impedance of a structure over frequency can be determined in FDTD by:
+%
+%\begin{itemize}
+%  \item Applying a gaussian pulse to a voltage source - in our case, applied to a via connecting the path (or probe)
+%  \item Running the simulation until the transients have all died out below some threshold, while logging the source voltage and current at each timestep
+%  \item Taking the fourier transform of the (real) excitation voltage and current (producing a complex result, mind you)
+%  \item Taking the magnitude of the ratio of the two complex spectra.
+%\end{itemize}
+%
+%This is the computational equivalent of dropping a piano off a balcony to see which key is stuck.
+%
+%See [Penney 1994], [Luebbers 1992], [Luebbers 1991], [Luk 1997]. 
+%
+%Our implementation is in \ghfile{electronics/simple_fdtd/runs/U.py}.
+%
+%A similar mismatch to the SPICE exists for fourier methods - but in the other direction.
 The courant limit often demands fine timesteps, but since each FFT bin is $ f_{bin} = n_{bin} / (N_{simulation} \ dt) $ , the majority of the FFT bins exist into the hundreds or thousands of GHz, leaving no resolution in the low-frequency domain of interest unless $N_{simulation}$ is extremely large - even if all the transients in the simulation have died down, you still have to keep the sim running to make the FFT happy!
-
-There's more than enough 'information entropy' in 4000 FDTD points for most antennas. But you need some 30,000 points to get 10 bins below 20 GHz!
-
-There are a few methods of changing the FFT bin size artificially, which [Bi 1992] reviews. You can "use a manual fourier integration over the frequency region of interest".
-
-But, in a staggering turn of events which will presumably be familiar to statisticans and preposterous to everyone else, a far simpler method is to {\it discard} 95\% of the data, by down-sampling to 1/10th or so.
-
-An equally simple method that seemed to produce better results in our case is to pad the voltage and current samples to the correct length.
+%
+%There's more than enough 'information entropy' in 4000 FDTD points for most antennas. But you need some 30,000 points to get 10 bins below 20 GHz!
+%
+%There are a few methods of changing the FFT bin size artificially, which [Bi 1992] reviews. You can "use a manual fourier integration over the frequency region of interest".
+%
+%But, in a staggering turn of events which will presumably be familiar to statisticans and preposterous to everyone else, a far simpler method is to {\it discard} 95\% of the data, by down-sampling to 1/10th or so.
+%
+%An equally simple method that seemed to produce better results in our case is to pad the voltage and current samples to the correct length.
 The jump discontinuity introduced by padding with zeros has a negligible effect.
-
-It's so thumpingly unintuitive to me that adding 50,000 zeros to a 5000 value dataset can improve the resolution of a measurement by 300-fold.
-
-It is important to remember to normalize the gaussian pulse, or else numerical noise will be introduced. The magnitude is not important - [Luebbers 1992] use 100v, others use 1v, etc.
-
-Though uneven dt FFTs exist, the time step can be constant at the courant limit for this simulation.
-
-A step impulse (1 first timestep, 0 otherwise) has been used in some works, though in our case performance was quite horrid.
-
-A correction factor due to the staggered magnetic field of the Yee lattice must be introduced; [Fang 1994]. Their $Z_2$ equation (correcting for spatial inaccuracies, but not temporal) was sufficient.
-
-This technique is equivalent to that used in electrochemistry, known as fourier impedance spectroscopy - except they seem to usually use a known impedance source rather than a hard source, presumably because ideal hard sources don't exist in reality.
-
-Allowing the simulation to run for long enough that all transients dissipate is important for accuracy - deceptive dips in the current can cause early termination.
+%
+%It's so thumpingly unintuitive to me that adding 50,000 zeros to a 5000 value dataset can improve the resolution of a measurement by 300-fold.
+%
+%It is important to remember to normalize the gaussian pulse, or else numerical noise will be introduced. The magnitude is not important - [Luebbers 1992] use 100v, others use 1v, etc.
+%
+%Though uneven dt FFTs exist, the time step can be constant at the courant limit for this simulation.
+%
+%A step impulse (1 first timestep, 0 otherwise) has been used in some works, though in our case performance was quite horrid.
+%
+%A correction factor due to the staggered magnetic field of the Yee lattice must be introduced; [Fang 1994].
+Their $Z_2$ equation (correcting for spatial inaccuracies, but not temporal) was sufficient.
+%
+%
+%This technique is equivalent to that used in electrochemistry, known as fourier impedance spectroscopy - except they seem to usually use a known impedance source rather than a hard source, presumably because ideal hard sources don't exist in reality.
+%
+%Allowing the simulation to run for long enough that all transients dissipate is important for accuracy - deceptive dips in the current can cause early termination.
 A surprising amount of detail is contributed by even the smallest current levels.
 Our threshold is 1e-7 amps for 700 iterations.
-
-[Samaras 2004] has a very useful set of experimental and FDTD data for calibration and comparison.
+%
+%[Samaras 2004] has a very useful set of experimental and FDTD data for calibration and comparison.
 Comparing a probe via source in the different positions, we obtained agreement of $\sim 7\%$ in impedance and $\sim 5\%$ in frequency.
-
-The use of a hard source feed-port affects the number of timesteps required by introducing unphysical transients.
+%
+%The use of a hard source feed-port affects the number of timesteps required by introducing unphysical transients.
 Using a port with a virtual 50-ohm resistance reduces the computational requirements by a large factor; see [Luebbers 1996].
-
-Simply monitoring the source current during the simulation is somewhat deceptive. Periodically monitoring the change in the fourier transform seems to be a better convergence metric.
-
-The units of the FFT (unlike those of the continuous FT) remain in volts.
-
-\rule{\linewidth}{0.2pt}
-
-Most equations in papers on the FDTD method are supplied without making the scaling factors explicit; some need multiplying by the Courant number, For use with flaport/fdtd the H-field to current line integral in [] requires scaling by $\mu_0 * (dx/dt)$, where $\mu_0$ is the vacuum magnetic permittivity, dx the cell size, and dt the timestep - despite the equation already possessing a deceptive set of $dx$-es.
-
-FIX THIS IT'S WRONG
-
-Naturally, if one is competent, this discrepancy will be immediately obvious.
+%
+%Simply monitoring the source current during the simulation is somewhat deceptive. Periodically monitoring the change in the fourier transform seems to be a better convergence metric.
+%
+%The units of the FFT (unlike those of the continuous FT) remain in volts.
+%
+%\rule{\linewidth}{0.2pt}
+%
+%Most equations in papers on the FDTD method are supplied without making the scaling factors explicit; some need multiplying by the Courant number, For use with flaport/fdtd the H-field to current line integral in [] requires scaling by $\mu_0 * (dx/dt)$, where $\mu_0$ is the vacuum magnetic permittivity, dx the cell size, and dt the timestep - despite the equation already possessing a deceptive set of $dx$-es.
+%
+%FIX THIS IT'S WRONG
+%
+%Naturally, if one is competent, this discrepancy will be immediately obvious.
 Those not dimensionally-intuitive, such as myself, find it useful to run dimensional analysis using a unit-aware calculator such as {\it sharkdp/insect}.
-
-\rule{\linewidth}{0.2pt}
+%
+%\rule{\linewidth}{0.2pt}
 

### 2021-04-29 documents/pure_electroporation.tex
Unicode math notetaking?!

@@
 \include{preamble}
+
+\usepackage{physics}
+\usepackage{bm}
+\newcommand{\bstar}[1]{ {#1}^{\bm*} }
 
@@
 
-While both mechanisms hinge on time constants, those discussed in the previous paper referred to the time for viscous loss of energy into the surrounding medium and the normal modes of the viral envelope; here the time constants relate to capacitive charging, and Smoluchowski processes.
-The relevant damage quantities were mechanical displacement and membrane stress, whereas here we consider transmembrane voltage and pore diameter.
+While both mechanisms hinge on a set of time constants, those discussed in the previous paper referred to the time for viscous loss of energy into the surrounding medium and the normal modes of the viral envelope; here the time constants relate to capacitive charging, and Smoluchowski processes.
+Previously, the relevant quantities describing damage to the virion were mechanical displacement and membrane stress, whereas here we consider transmembrane voltage and pore diameter.
 
-At the risk of self-plagarism, we will restate some precedent
+At the risk of self-plagarism, we will restate some precedent.
 
@@
 It is, in general, something of a singular outlier in that it is one of very few biological mechanisms relevant at practical electric field intensities.
-Along with thermal treatment, it also performs an operation something like integration, distinct from absolute-value.
+Similar to thermal treatment, it also performs an operation something like integration with a threshold, a process distinct from normal absolute-value.
 It is perhaps this property which provides a small degree of tunability.
@@
 \footnote{It is amusing to draw parallels between electroporation and Bialke et al's reports on spacecraft reaction wheels.
-In both cases, destructive process are charging of the external shell (the spacecraft itself), a highly resistive layer (a layer of grease on the ball bearings), and a }
+In both cases, destructive process involve differential charging of the external shell (the spacecraft itself) against an internal shell (the reaction wheels), producing a potential difference across a highly resistive layer (a layer of grease on the ball bearings)}
 
-Varactor-like parametric, as the bilayer is squished by the potential;
+Varactor-like parametric properties as the bilayer is squished by the potential. hydrodynamic
+
+The same Debye screening effects are also of some relevance.
 
@@
 These regimes of intensity may possibly be accessible via ultrashort optical techniques.
-Similarly, Tsen \cite{Studies2014} report a non-electroporative mechanism, but these results have not been replicated at that intensity\cite{No2011}.
+Similarly, Tsen \cite{Studies2014} report a non-electroporative mechanism, but these results have not been successfully independently replicated at that intensity\cite{No2011}.
 
@@
 
-Electroporation\cite{Electroporation1988}, now a common laboratory procedure, occurs when an enormous electric field causes ions in solution to diffuse across a cell membrane, capacitively charging it, provoking a change in lipid bilayer conformation\cite{Membrane2016}, reversibly rendering the membrane permeable.
+Electroporation\cite{Electroporation1988}, now a common laboratory procedure, occurs when an enormous electric field causes ions in solution to diffuse across a cell membrane, capacitively charging it, provoking a change in lipid bilayer conformation\cite{Membrane2016}, either reversibly rendering the membrane permeable or, if the number and size of pores is considerable, the membrane may be permanently destroyed.
 This is one among many other, more subtle mechanisms; the minutia of poration can become extraordinarily complex in certain circumstances and are beyond the author's current understanding\cite{Theoretical2007}.
@@
 
-\subsection*{Basic scaling laws}
+\section*{Basic scaling laws}
 
@@
 Viruses are minute.
-All other properties of the, the classic Schwan equation implies that the steady-state DC transmembrane voltage is proportional to the size of the particle.
+All other properties of the system being equal, the standard Schwan equation for transmembrane voltage implies that the steady-state DC voltage is proportional to the size of the particle.
+In the case of a 100 nm virus
 
-Madiyar's Vaccinia electroporation data aligns with. Assuming that the host porates at 0.05 MV/m, the 250 nm vaccinia might be expected to have a threshold of 4 MV/m.
+Madiyar's Vaccinia electroporation data aligns with. Assuming that the host porates at 0.05 MV/m, the 250 nm vaccinia might be expected to have a threshold of 4 MV/m. Mutatoyo's data also agree.
 
-However, this does not explain
+This does not agree with the two reports. It does not seem plausible that the
 
@@
 
-Some extremely simplified scaling laws for membrane charging effects due to short (sub Tc) pulses are given by Schoenbach \cite{Bioelectric2007}.
-This is based primarily on an equivalent circuit model, we largely neglect the electrodynamics that apply with short pulses and also the conductivity change due to pore formation.
+Some extremely simplified scaling laws for membrane charging effects due to short (sub-first time constant) pulses are given by Schoenbach \cite{Bioelectric2007}.
+This is based primarily on an equivalent circuit model, we largely neglect the electrodynamics that apply with short pulses and also the conductivity change due to pore formation, modelled by [insert equation from "ADC" paper].
 Electroporation is a highly nonlinear effect\cite{Letter1974}, and this .
@@
 
+Regrettably, despite their diminutive radii, viruses and host cells may well have overlapping time constants due to the other dielectric properties.
+However, even in the case where both time constants are nearly equivalent, a marked discrepancy in the time evolution of short pulses can be seen.
+
+[step response]
+
+And so, despite having similar time constants, a short gaussian pulse [] long
+
 There may be an existing transmembrane potential that must be added - this is neglected in this case.
@@
 
-want to more accurately represent the - most importantly, the core permittivity seems like it should alter the reflection significantly at high frequencies, but isn't usually treated
+Equivalent circuit models want to more accurately represent the - most importantly, the core permittivity intuitively seems like it should alter the reflection significantly at high frequencies, but isn't usually treated
 
@@
 
-Basic dry-weight measurements seem to suggest that influenza contains about 60\% water by weight \cite{lauffer1944biophysical}.
+Dry-weight measurements seem to suggest that influenza contains about 60\% water by weight \cite{lauffer1944biophysical}.
 Has diffusion coefficients and maintains a Donnan ion size equilibrium similar to that of lipid bilayers \cite{Effect2015b}.
@@
 
-\subsection{Electrodynamic considerations}
+\subsection*{Electrodynamic considerations}
 
@@
 
-\subsection{Optimal pulse}
+\subsection*{Optimal pulse}
 
-Differential
+We must apologize once again to the mathematicians for sins of terminology.
 
 This bears considerable similarity to e.g.
-radar waveform design and compressed sensing, and also problems of coherent control in quantum systems.
+radar waveform design and compressed sensing; problems of coherent control of quantum systems.
 In many cases, the optimal control is equal to the transfer function
@@
 
-"Underactuated";
+"Underactuated" robotics
 
@@
 
-\subsection{direct method Pseudospectral solvers}
+\subsection*{direct method Pseudospectral solvers}
 
@@
 
-First the objective function with a constant integral control power constraint was used, but this did not yield
+An objective function with a constant integral control power constraint, $t_{end} = \int_0^t_{end} u(t)^2 dt$ was used, but this did not appear to yield meaningful results.
 
-\subsection{Optimal control solvers}
+\subsection*{Optimal control solvers}
+
+\subsection*{Nondimensionalization}
+
+The coefficients have a very small value; even time has a very small value. This was believed to account for at least some of the
+
+$$\dv[2]{x_V}{t} = 
+\frac{R a_{1V}}{b_{1V}} \dv[2]{u}{t} 
++ \frac{R a_{2V}}{b_{1V}}  \dv{u}{t} 
++ \frac{R a_{3V}}{b_{1V}}  u
+- \frac{b_{2V}}{b_{1V}} \dv{x_V}{t}
+- \frac{b_{3V}}{b_{1V}} x_V $$
+
+$$\dv[2]{x_H}{t} = 
+\frac{R a_{1H}}{b_{1H}} \dv[2]{u}{t} 
++ \frac{R a_{2H}}{b_{1H}}  \dv{u}{t} 
++ \frac{R a_{3H}}{b_{1H}}  u
+- \frac{b_{2H}}{b_{1H}} \dv{x_H}{t}
+- \frac{b_{3H}}{b_{1H}} x_H $$
+
+%x2  = (R*a1*u2 + R*a2*u1 + R*a3*u0 - b2*x1 - b3*x0)/b1
+% https://math.stackexchange.com/questions/3435173/how-to-nondimensionalize-a-second-order-differential-equation
+
+let $x_V^{\bm*} = \frac{x_V}{x_{VK}}$ and $t^{\bm*} = \frac{t}{t_{K}}$ where $_K$ denotes a nondimensionalization constant ($t_0$ is switched to $t_K$ to avoid confusion with x0 used in simulation).
+(the forcing functional u is dependent on t, but this is implied).\\ \\
+
+$$\frac{d^n}{dt^n} = \frac{1}{{t_K}^n}\frac{d^n}{d\bstar{t}^n}$$\\
+
+$$\dv[2]{x_V}{t} = 
+\frac{R a_{1V}}{b_{1V}} \dv[2]{u}{t} 
++ \frac{R a_{2V}}{b_{1V}}  \dv{u}{t} 
++ \frac{R a_{3V}}{b_{1V}}  u
+- \frac{b_{2V}}{b_{1V}} \dv{x_V}{t}
+- \frac{b_{3V}}{b_{1V}} x_V $$
+
+GEKKO's .dt() operator allows u0 to be chosen as the control. 
+Otherwise, the DAE form requires u2 to be used as the control.
+
+denormalize u?
 

### 2021-04-30 documents/eq.tex
further nondimensionalization

\documentclass[11pt]{article}
%Gummi|065|=)
\title{\textbf{Welcome to Gummi 0.6.6}}
\author{Alexander Van der Meij\\
		Wei-Ning Huang\\
		Dion Timmermann}
\date{}

\usepackage{physics}

\usepackage{bm}

\begin{document}

$$\dv[2]{x_V}{t} =
			  \frac{R a_{1V}}{b_{1V}} \dv[2]{u(t)}{t}
			+ \frac{R a_{2V}}{b_{1V}}  \dv{u(t)}{t}
			+ \frac{R a_{3V}}{b_{1V}}  u(t)
			- \frac{b_{2V}}{b_{1V}} \dv{x_V}{t}
			- \frac{b_{3V}}{b_{1V}} x_V $$

$$\dv[2]{x_H}{t} =
			  \frac{R a_{1H}}{b_{1H}} \dv[2]{u(t)}{t}
			+ \frac{R a_{2H}}{b_{1H}}  \dv{u(t)}{t}
			+ \frac{R a_{3H}}{b_{1H}}  u(t)
			- \frac{b_{2H}}{b_{1H}} \dv{x_H}{t}
			- \frac{b_{3H}}{b_{1H}} x_H $$

% x2  = (R*a1*u2 + R*a2*u1 + R*a3*u0 - b2*x1 - b3*x0)/b1
% https://math.stackexchange.com/questions/3435173/how-to-nondimensionalize-a-second-order-differential-equation

let $\bm\tilde x_V = \frac{x_V}{x_{VK}}$ and $\bm\tilde t = \frac{t}{t_{K}}$ where $_K$ denotes a nondimensionalization constant ($t_0$ is switched to $t_K$ to avoid confusion with x0 used in simulation). \\ \\

$$\frac{d^n}{dt^n} = \frac{1}{{t_K}^n}\frac{d^n}{d{\bm\tilde t}^n}$$\\

GEKKO's .dt() operator allows u0 to be chosen as the control.
    Otherwise, the DAE form requires u2 to be used as the control.

\end{document}

### 2021-04-30 documents/pure_electroporation.tex
further nondimensionalization

@@
 \title{Selective electroporation of the viral envelope}
-\author{\footnotesize{Daniel Correia\orcidlink{0000-0002-9353-0216}}\footnote{therobotist@gmail.com, Ontario, Canada.}}
+\author{\footnotesize{Daniel Correia\orcidlink{0000-0002-9353-0216}}\footnote{Ontario, Canada; contact information in the ORCiD.}}
 \date{\small{March 21 2021}}
@@
 
+%mention the github again
 \lettrine{A}{s} an addendum to a crude technical report \cite{notes2021} by the author, presenting some experimental results on an adjacent technique
@@
 
-Lagrange multipliers.
+In the previous paper, an analytic method was shown using variational calculus / lagrange multiplier.
 Unfortunately, while closed-form solutions appear to be readily available for some simplified cases (such as when the membrane is infinitesimally thin or when permittivity is neglected) [schwan paper],
@@
 Kotnik discuss the transmembrane voltage due to several pulse shapes formed from the Laplace Transform of the original differential equation.
-Talele offer their own response due to an arbitrary waveform can be produced by
+
+\subsection{Attempts to solve in s-space; convolution integral}
+
+Talele offer their own response due to an arbitrary waveform using the step response and a convolution integral \cite{Nonlinear2007}.
 
@@
 
-The fourier transform of both the impulse response and the step response exist, are analytic and of manageable size; however, the integral of the cost function is extremely unweildy.
+Via Mathematica, the Fourier transform of both the impulse response and the step response exist, are analytic and of manageable size; however, the integral of the cost function is extremely unwieldy.
+
+Subtracting the frequency domain of the step responses of the two produced an interesting pulse, but not nearly optimal.
 

### 2021-05-04 documents/eq.tex
Returned home

@@
 \usepackage{physics}
-
 \usepackage{bm}
+\usepackage{listings}
+\newcommand{\bstar}[1]{ {#1}^{\bm*} }
 
@@
 
+\{ $a_{1V}$... \} etc have
+
+the a and b coefficients both have units
+
+\[ \{\text{meter}\cdot \text{siemens}^2, \  \text{farad}\cdot \text{meter}\cdot \text{siemens} ,\ \text{farad}^2 \cdot \text{meter}\} \]
+
+in physical units, typical values for as an example, \\
+\verb|Cell(0.3, 80, 0.005, 30, 1e-8, 60, 50e-9, 14e-9, t)| \
+
+$$R = 2.5\times10^{-8}$$
+$$a_1 = 6\times10^{-26}$$
+$$a_2 = 9\times10^{-33}$$
+$$a_3 = 2\times10^{-41}$$
+$$b_1 = 4\times10^{-26}$$
+$$b_2 = 1\times10^{-32}$$
+$$b_3 = 4\times10^{-41}$$
+
+An input control waveform u(t) (volts per meter), and two output waveforms, $x_V(t)$ and $x_H(t)$ in volts.\\
+
+%virus.__dict__
+
+First system of differential equations (named V):\\
+
 $$\dv[2]{x_V}{t} = 
-			  \frac{R a_{1V}}{b_{1V}} \dv[2]{u(t)}{t}
-			+ \frac{R a_{2V}}{b_{1V}}  \dv{u(t)}{t}
-			+ \frac{R a_{3V}}{b_{1V}}  u(t)
+\frac{R_V a_{1V}}{b_{1V}} \dv[2]{u}{t} 
++ \frac{R_V a_{2V}}{b_{1V}}  \dv{u}{t} 
++ \frac{R_V a_{3V}}{b_{1V}}  u
 - \frac{b_{2V}}{b_{1V}} \dv{x_V}{t}
@@
 
+In practice, the solver takes a DAE: the second differential equation is split into an explicit system of eqs:
+
+$$u1 = \dv{}{t} u$$
+$$u2 = \dv{}{t} u1$$
+
+$$x1_V = \dv{}{t} x0_V$$
+$$x2_V = \dv{}{t} x1_V$$
+
+Another system is solved simultaneously (named H), of identical form but different coefficients:
+
 $$\dv[2]{x_H}{t} = 
-			  \frac{R a_{1H}}{b_{1H}} \dv[2]{u(t)}{t}
-			+ \frac{R a_{2H}}{b_{1H}}  \dv{u(t)}{t}
-			+ \frac{R a_{3H}}{b_{1H}}  u(t)
+\frac{R_H a_{1H}}{b_{1H}} \dv[2]{u}{t} 
++ \frac{R_H a_{2H}}{b_{1H}}  \dv{u}{t} 
++ \frac{R_H a_{3H}}{b_{1H}}  u
 - \frac{b_{2H}}{b_{1H}} \dv{x_H}{t}
@@
 
-% x2  = (R*a1*u2 + R*a2*u1 + R*a3*u0 - b2*x1 - b3*x0)/b1
+%x2  = (R*a1*u2 + R*a2*u1 + R*a3*u0 - b2*x1 - b3*x0)/b1
+
+\subsection*{Nondimensionalization}
+
+Let $x_V^{\bm*} = \frac{x_V}{x_{VK}}$ and $t^{\bm*} = \frac{t}{t_{K}}$ where $_K$ denotes a nondimensionalization constant (standard convention of $t_0$ is changed to $t_K$ to avoid confusion with subscript 0s used in simulation).
+(the forcing functional u is dependent on t, but this is implied).\\ \\
+
+$$\frac{d^n}{dt^n} = \frac{1}{{t_K}^n}\frac{d^n}{d{\bstar{t}}^n}$$\\
+
 % https://math.stackexchange.com/questions/3435173/how-to-nondimensionalize-a-second-order-differential-equation
+% http://math.colgate.edu/~wweckesser/math312Spring05/handouts/Nondim.pdf
+% https://faculty.math.illinois.edu/~rdeville/teaching/558/nondimensionalization.pdf
+% http://math.colgate.edu/~wweckesser/math312Spring05/handouts/MoreNondim.pdf
 
-let $\bm\tilde x_V = \frac{x_V}{x_{VK}}$ and $\bm\tilde t = \frac{t}{t_{K}}$ where $_K$ denotes a nondimensionalization constant ($t_0$ is switched to $t_K$ to avoid confusion with x0 used in simulation).
-\\ \\
+% Kronbichler et al suggest an interesting method of nondimensionalizing.
 
-$$\frac{d^n}{dt^n} = \frac{1}{{t_K}^n}\frac{d^n}{d{\bm\tilde t}^n}$$\\
+% https://www.math.colostate.edu/~bangerth/publications/2008-boussinesq.pdf
 

### 2021-05-05 documents/pure_electroporation.tex
A possible analytic method?

@@
 \begin{abstract}
-	\noindent The phenomenon of electroporation occurs when extreme applied electric fields in the MV/m range drive transmembrane potentials, leading to pores in, and perhaps the destruction of, membranes; this is commonly harnessed for transfection into the cell in the laboratory, and has recently been shown to be safe and effective in the clinic for the ablation of tumors.
+	\noindent The phenomenon of electroporation occurs when extreme applied electric fields in the MV/m range drive transmembrane potentials, leading to pores in, and perhaps the destruction of, membranes; this is commonly harnessed for transfection into the cell in the laboratory, and has recently been shown to be safe and effective in the clinic for the in-situ ablation of tumors.
 

### 2021-05-07 documents/pure_electroporation.tex
Kwim's awesome

@@
 \usepackage[left=2cm,right=2cm,
-top=0.5cm,
+top=0.85cm,
 bottom=1.5cm,%
@@
 
-Varactor-like parametric properties as the bilayer is squished by the potential. hydrodynamic
+Varactor-like parametric properties as the bilayer is compressed by forces from the potential difference. hydrodynamic
 
@@
 As in the previous paper, we must stress that meaningful bioelectrics research hinges very strongly on experimental design and methodology, and very few results can be trusted implicitly.
-It appears to be very difficult to unambiguously determine cause and effect on a system as complex as a cell; especially when electrodes are in contact with solution and may release an energy-dependent dose of metal ions.
+It appears to be very difficult to unambiguously determine effects and their cause on a system as complex as a cell, especially when electrodes are in contact with solution and release an energy-dependent dose of metal ions.
 
@@
 
-Note that, despite clear evidence in [nanosecond review], microsecond in vivo and clinical treatment, nanosecond in vivo conduction, and, The NATO review concluded that evidence did not support non-contact, "electrodeless", even above the thresholds that might otherwise be expected to cause electroporation.
+Note that, despite excellent evidence in [nanosecond review], microsecond in vivo and clinical treatment, nanosecond in vivo conduction, and, The NATO review concluded that evidence did not support non-contact, "electrodeless", even above the thresholds that might otherwise be expected to cause electroporation.
 has not yet found any evidence demonstrating electroporation via pulsed RF.
@@
 Viruses have extraordinary mechanical properties\footnote{Why is this?
-What selection pressures drive the selection of this pressure?}, so it seems reasonable that their dielectric properties could differ substantially from that of other structures.
+What selection pressures drive the selection of this pressure?}, so it seems reasonable that their dielectric properties could differ substantially from those of other biological structures.
 
 In the extreme case of the bacteriophage, the genome is packaged so tightly into the protein capsid that the core is often described as a glassy crystal of DNA\cite{Conformation2007}.
-ssRNA viruses like coronaviridae might be expected to be somewhat more sedate, but this does not seem to be borne out in the core conductivity data.
+ssRNA viruses like coronaviridae might be expected to be somewhat more sedate in packing density, but this does not seem to be borne out in the core conductivity data.
 
-On the other hand, the cellular "structome" also contains countless vesicles and structures of similar nature that might plausibly be damaged; small pockets of lipid in the endoplasmic reticula - nuclear pore complexes, etc.
-This appears to be borne out in Gabriel's data; dense tissues exhibit many .
+On the other hand, the eukaryotic "structome" also contains countless vesicles and structures of similar nature that might plausibly be damaged; small pockets of lipid in the endoplasmic reticula - nuclear pore complexes, etc.
+This appears to be seen to some degree in Gabriel's data; dense tissues exhibit many [double check this].
 It may not be possible to meaningfully predict all possible off-target effects, much like in drug discovery.

### 2021-05-07 documents/pure_electroporation.tex
Testing analytic control solution

@@
 \usepackage{bm}
+\usepackage{listings}
 \newcommand{\bstar}[1]{ {#1}^{\bm*} }
@@
 
-The question of optimizing a pulse is not novel, having been discussed by many groups in the past. Retelj use a series of
+The concept of optimizing an electroporation pulse is not novel, having been discussed by many groups in the past; either to prodduce different sterilization effects, tee Retelj use a series of
 
-\subsection*{Optimal pulse}
+\subsection{Attempts to solve for the optimal pulse in the s-space; convolution integral}
 
@@
 Kotnik discuss the transmembrane voltage due to several pulse shapes formed from the Laplace Transform of the original differential equation.
-
-\subsection{Attempts to solve in s-space; convolution integral}
 
@@
 
-An objective function with a constant integral control power constraint, $t_{end} = \int_0^t_{end} u(t)^2 dt$ was used, but this did not appear to yield meaningful results.
+An objective function with a constant integral control power constraint, $t_{end} = \int_0^{t_{end}} u(t)^2 dt$ was used, but this did not appear to yield meaningful results.
 
@@
 
+iLQR. Differential dynamic programming was not evaluated (julia lib).
+
 \subsection*{Nondimensionalization}
 
-The coefficients have a very small value; even time has a very small value. This was believed to account for at least some of the
+The coefficients all have a very small value in standard units. Numerical error was presumed to account for at least some of the difficulty in optimization, so was partially nondimensionalized.
+
+the a and b coefficients both have units
+
+\[ \{\text{meter}\cdot \text{siemens}^2, \  \text{farad}\cdot \text{meter}\cdot \text{siemens} ,\ \text{farad}^2 \cdot \text{meter}\} \]
+
+in physical units, typical values for as an example, \\
+\verb|Cell(0.3, 80, 0.005, 30, 1e-8, 60, 50e-9, 14e-9, t)| \
+
+$$R = 2.5\times10^{-8}$$
+$$a_1 = 6\times10^{-26}$$
+$$a_2 = 9\times10^{-33}$$
+$$a_3 = 2\times10^{-41}$$
+$$b_1 = 4\times10^{-26}$$
+$$b_2 = 1\times10^{-32}$$
+$$b_3 = 4\times10^{-41}$$
+
+An input control waveform u(t) (volts per meter), and two output waveforms, $x_V(t)$ and $x_H(t)$ in volts.\\
+
+%virus.__dict__
+
+First system of differential equations (named V):\\
 
 $$\dv[2]{x_V}{t} = 
-\frac{R a_{1V}}{b_{1V}} \dv[2]{u}{t} 
-+ \frac{R a_{2V}}{b_{1V}}  \dv{u}{t} 
-+ \frac{R a_{3V}}{b_{1V}}  u
+\frac{R_V a_{1V}}{b_{1V}} \dv[2]{u}{t} 
++ \frac{R_V a_{2V}}{b_{1V}}  \dv{u}{t} 
++ \frac{R_V a_{3V}}{b_{1V}}  u
 - \frac{b_{2V}}{b_{1V}} \dv{x_V}{t}
@@
 
+In practice, the solver takes a DAE: the second differential equation is split into an explicit system of eqs:
+
+$$u1 = \dv{}{t} u$$
+$$u2 = \dv{}{t} u1$$
+
+$$x1_V = \dv{}{t} x0_V$$
+$$x2_V = \dv{}{t} x1_V$$
+
+Another system is solved simultaneously (named H), of identical form but different coefficients:
+
 $$\dv[2]{x_H}{t} = 
-\frac{R a_{1H}}{b_{1H}} \dv[2]{u}{t} 
-+ \frac{R a_{2H}}{b_{1H}}  \dv{u}{t} 
-+ \frac{R a_{3H}}{b_{1H}}  u
+\frac{R_H a_{1H}}{b_{1H}} \dv[2]{u}{t} 
++ \frac{R_H a_{2H}}{b_{1H}}  \dv{u}{t} 
++ \frac{R_H a_{3H}}{b_{1H}}  u
 - \frac{b_{2H}}{b_{1H}} \dv{x_H}{t}
@@
 %x2  = (R*a1*u2 + R*a2*u1 + R*a3*u0 - b2*x1 - b3*x0)/b1
-% https://math.stackexchange.com/questions/3435173/how-to-nondimensionalize-a-second-order-differential-equation
 
-let $x_V^{\bm*} = \frac{x_V}{x_{VK}}$ and $t^{\bm*} = \frac{t}{t_{K}}$ where $_K$ denotes a nondimensionalization constant ($t_0$ is switched to $t_K$ to avoid confusion with x0 used in simulation).
+\subsection*{Nondimensionalization}
+
+Let $x_V^{\bm*} = \frac{x_V}{x_{VK}}$ and $t^{\bm*} = \frac{t}{t_{K}}$ where $_K$ denotes a nondimensionalization constant (standard convention of $t_0$ is changed to $t_K$ to avoid confusion with subscript 0s used in simulation).
 (the forcing functional u is dependent on t, but this is implied).\\ \\
 
-$$\frac{d^n}{dt^n} = \frac{1}{{t_K}^n}\frac{d^n}{d\bstar{t}^n}$$\\
+$$\frac{d^n}{dt^n} = \frac{1}{{t_K}^n}\frac{d^n}{d{\bstar{t}}^n}$$\\
 
-$$\dv[2]{x_V}{t} = 
-\frac{R a_{1V}}{b_{1V}} \dv[2]{u}{t} 
-+ \frac{R a_{2V}}{b_{1V}}  \dv{u}{t} 
-+ \frac{R a_{3V}}{b_{1V}}  u
-- \frac{b_{2V}}{b_{1V}} \dv{x_V}{t}
-- \frac{b_{3V}}{b_{1V}} x_V $$
+% https://math.stackexchange.com/questions/3435173/how-to-nondimensionalize-a-second-order-differential-equation
+% http://math.colgate.edu/~wweckesser/math312Spring05/handouts/Nondim.pdf
+% https://faculty.math.illinois.edu/~rdeville/teaching/558/nondimensionalization.pdf
+% http://math.colgate.edu/~wweckesser/math312Spring05/handouts/MoreNondim.pdf
+
+% Kronbichler et al suggest an interesting method of nondimensionalizing.
+
+% https://www.math.colostate.edu/~bangerth/publications/2008-boussinesq.pdf
 
@@
 
-denormalize u?
+\subsection*{}
 
-% Is the effect replicable, or is it simply an electrochemical artifact?
-Will these nanopores be destructive to viruses - will the pores be open for sufficient time for the ssRNA to be released?
-Will the nucleocapsid restrain the genome sufficiently and prevent membrane damage from inactivating the virus?
-Are the apoptosis effects likely to be triggered before these?
-Are there similar structures in tissue?
+However, this overlooks a much simpler method.
 
-% A serious danger would be that if a nuclear or organelle membrane were to be porated, viral ssRNA may be admitted to places it shouldn't be.
-The author does not have the biology experience to evaluate this risk.
+Setting say, the logistic equation, produces an overdetermined system. using the above as a constraint in PSOPT was also ineffective.
 

### 2021-05-17 documents/pure_electroporation.tex
Musings on detection in wastewater

@@
 \usepackage[left=2cm,right=2cm,
-top=0.85cm,
+top=1.25cm,
 bottom=1.5cm,%
@@
 \newcommand{\bstar}[1]{ {#1}^{\bm*} }
+
+ \pagestyle{empty}
 
@@
 \begin{abstract}
-	\noindent The phenomenon of electroporation occurs when extreme applied electric fields in the MV/m range drive transmembrane potentials, leading to pores in, and perhaps the destruction of, membranes; this is commonly harnessed for transfection into the cell in the laboratory, and has recently been shown to be safe and effective in the clinic for the in-situ ablation of tumors.
+	\noindent The phenomenon of electroporation occurs when extreme applied electric fields in the MV/m range drive transmembrane potentials, leading to pores in, and perhaps the destruction of, membranes; this is commonly harnessed for transfection into the cell in the laboratory, and has recently been shown clinically to be safe and effective for the in-situ ablation of tumors.
 
@@
 
+%send to jeff on the discord?
+
 %mention the github again
@@
 
-In a continued effort to make ultracrepidarian physicists such as ourselves feel useful
+In a continued effort to make ultracrepidarian pseudo-physicists such as ourselves feel useful
 
+\begin{tcolorbox}
 While both mechanisms hinge on a set of time constants, those discussed in the previous paper referred to the time for viscous loss of energy into the surrounding medium and the normal modes of the viral envelope; here the time constants relate to capacitive charging, and Smoluchowski processes.
 Previously, the relevant quantities describing damage to the virion were mechanical displacement and membrane stress, whereas here we consider transmembrane voltage and pore diameter.
+\end{tcolorbox}
 
@@
 
-hit "with an electric field strong enough to knock over a horse, and they do enough things to justify international meetings, to fill a sizable book, and to lead one to speak of an entirely new technology for cell manipulation."
+when a strong electric field is applied, they "do enough things to justify international meetings, to fill a sizable book, and to lead one to speak of an entirely new technology for cell manipulation."
 
@@
 These regimes of intensity may possibly be accessible via ultrashort optical techniques.
-Similarly, Tsen \cite{Studies2014} report a non-electroporative mechanism, but these results have not been successfully independently replicated at that intensity\cite{No2011}.
-
-on the other hand, the idea of shocking a virus is so basic that it can scarcely be believed
+Accordingly, Tsen \cite{Studies2014} report a non-electroporative mechanism, but these results have not been successfully independently replicated at that intensity\cite{No2011}.
 
@@
 Of course, unlike localized tumors, viral infections are systemic, affecting many of the most favoured organs.
+
+Also be of some use for testing and detection.
 
@@
 
-The concept of optimizing an electroporation pulse is not novel, having been discussed by many groups in the past; either to prodduce different sterilization effects, tee Retelj use a series of
+The concept of optimizing an electroporation pulse is not novel, having been discussed by many groups in the past; either to prodduce different sterilization effects, tee Retelj use a series of, to
 

### 2021-05-19 documents/pure_electroporation.tex
An obvious discrepancy

@@
 
-\footnote{It is amusing to draw parallels between electroporation and Bialke et al's reports on spacecraft reaction wheels.
+%\footnote{It is amusing to draw parallels between electroporation and Bialke et al's reports on spacecraft reaction wheels.
 In both cases, destructive process involve differential charging of the external shell (the spacecraft itself) against an internal shell (the reaction wheels), producing a potential difference across a highly resistive layer (a layer of grease on the ball bearings)}
@@
 
+software used
+
+Written in texst
+
 \end{document}

### 2021-05-27 documents/pure_electroporation.tex
Swapped terms on virus_optimize.cxx, still no idea why
most promising yet
Introduced a bug somewhere

@@
 
-\title{Selective electroporation of the viral envelope}
+\title{Optimal control for selective electroporation of the viral envelope}
 \author{\footnotesize{Daniel Correia\orcidlink{0000-0002-9353-0216}}\footnote{Ontario, Canada; contact information in the ORCiD.}}
@@
 %mention the github again
+
 \lettrine{A}{s} an addendum to a crude technical report \cite{notes2021} by the author, presenting some experimental results on an adjacent technique
@@
 
+There appears to be an error in; the coefficients are in descending order, whereas they should be in ascending order. See
+
 Talele offer their own response due to an arbitrary waveform using the step response and a convolution integral \cite{Nonlinear2007}.
@@
 Subtracting the frequency domain of the step responses of the two produced an interesting pulse, but not nearly optimal.
+
+%polarization? can we somehow twist the polarization?
 
@@
 
+\subsection*{Limitations and next steps}
+
+Involves careful control of the second derivative of a waveform
+
 \end{document}

### 2021-06-06 documents/pure_electroporation.tex
functioning derivative
symbolic output solution is useless
Trying Differential Evolution

@@
 
-\subsection*{direct method Pseudospectral solvers}
+\subsection*{Pseudospectral solvers}
 
-An excellent overview of solutions http://plato.asu.edu/sub/nlounres.html
+% is this direct or indirect method?
+
+%An excellent overview of solutions http://plato.asu.edu/sub/nlounres.html - nah, not really that good
 
@@
 
-because the problem depends on the second derivative of sub-nanosecond curves, the scaling varies by about 20 orders of magnitude.
+Because the problem depends on the second derivative of sub-nanosecond curves, base variable and coefficient scaling varies by more than 20 orders of magnitude.
+
 PSOPT [] with IPOPT\cite{implementation2006} solver. PSOPT has the advantage of semi-automatic scaling based on supplied bounds.
@@
 \subsection*{Optimal control solvers}
+
+% need to check the required tolerances on the output - how stable is the solution
 
@@
 
-software used
-
 Written in texst
@@
 
+Extremely speculative and
+
 Involves careful control of the second derivative of a waveform
 
+optimal over a distribution
+
+\subsection{Software used and evaluated:}
+
+casADi;
+
+typeset in LaTeX using TeXstudio.
+
+\subsection{Recommended reading}
+
+de Seze;
+
 \end{document}

### 2021-06-10 documents/background.tex
Transmembrane library
Pretty graphs

@@
 
-\begin{fquote}[Professor David Baltimore][\cite{Issues2008}]
+\begin{fquote}[Professor David Baltimore (recently deceased)][\cite{Issues2008}]
 	The scientific literature is a conversation among scientists; we describe to each other what we have done, and we implicitly ask our colleagues to try to build on our results, testing their value and their ability to support a growing edifice.
@@
 
-Vijayalaxmi \cite{Biological2016} \cite{Comprehensive2018} \cite{Funding2019} already offer a number of excellent guidelines on best practices in this field; as do Chou \cite{chou1996radio} and \cite{Effects2016} .
+Vijayalaxmi \cite{Biological2016} \cite{Comprehensive2018} \cite{Funding2019} already offer a number of excellent guidelines on best practices in this field; as do Chou \cite{chou1996radio} and Napotnik \cite{Effects2016} .
 We only offer a few issues which we were particularly concerned about when designing our experiments and searching literature.
@@
 As this is an unpublished negative result, we know nothing about the experimental details that led to this error.
+
+In 1984, O. P. Gandhi \cite{BIOLOGICALa} performed Raman spectroscopy of a variety of viruses in the frequency range 1 to 5e13 Hz.
 

### 2021-06-10 documents/pure_electroporation.tex
Pretty graphs

@@
 
-\title{Optimal control for selective electroporation of the viral envelope}
+\title{Selective electroporation of the viral envelope via optimal control of transmembrane potential}
 \author{\footnotesize{Daniel Correia\orcidlink{0000-0002-9353-0216}}\footnote{Ontario, Canada; contact information in the ORCiD.}}
@@
 \begin{abstract}
-	\noindent The phenomenon of electroporation occurs when extreme applied electric fields in the MV/m range drive transmembrane potentials, leading to pores in, and perhaps the destruction of, membranes; this is commonly harnessed for transfection into the cell in the laboratory, and has recently been shown clinically to be safe and effective for the in-situ ablation of tumors.
+	\noindent The phenomenon of electroporation occurs when extreme applied electric fields in the MV/m range drive transmembrane potentials, leading to pores in (and potentially the destruction of) membranes.
+This is commonly harnessed for transfection into the cell in the laboratory, and has recently been shown clinically to be safe and effective for the in-situ ablation of tumors.
 
-	\noindent As pulse duration is reduced from the microsecond to nanosecond regime, effects targeting smaller intracellular structures are expected and observed, and a degree of tunability arises.
+	\noindent As pulse duration is reduced from the microsecond to sub-nanosecond regime, effects targeting smaller intracellular structures are expected and observed, and a degree of tunability arises.
 Indeed, pulses shorter than 10 ns have been observed to porate the nuclear envelope and organelle membranes while leaving the plasma membrane intact.
@@
 
-when a strong electric field is applied, they "do enough things to justify international meetings, to fill a sizable book, and to lead one to speak of an entirely new technology for cell manipulation."
+when a strong electric field is applied, they "...do enough things to justify international meetings, to fill a sizable book, and to lead one to speak of an entirely new technology for cell manipulation."
 
@@
 
+As in the previous paper, we must stress that meaningful bioelectrics research hinges very strongly on experimental design and methodology, and very few results can be trusted implicitly.
+It appears to be very difficult to unambiguously determine effects and their cause on a system as complex as a cell, especially when electrodes are in contact with solution and release an energy-dependent dose of metal ions.
+
 However, long pulses at $\approx10$ MV/m appear to electroporate large enveloped viruses, similarly to host cells\cite{AC2017}
@@
 
-Despite considering the somewhat harder problem of electroporating while inside the cell, rather than in extracellular fluid, \cite{Electroporation2013} report that 250 nm liposomes should be porated without inducing damage to the host cell, and modelling shows that 100 nm liposomes may be porated by 4 ns pulses never exceeding 20 MV/m.
+Despite considering the presumably harder problem of electroporating small lipid vesicles while inside the cell, rather than in extracellular fluid, \cite{Electroporation2013} report that 250 nm liposomes should be porated without inducing damage to the host cell, and their modelling shows that 100 nm liposomes may be porated by 4 ns pulses never exceeding 20 MV/m.
 
-The same field intensities do not appear to damage phages with protein capsids\cite{Manipulation2013}, in line with our negative results on T4.
+The same field intensities do not appear to damage phages with protein capsids\cite{Manipulation2013}, in line with our previously-reported negative results on T4.
 
-Non-resonant capsid and envelope breakage with 120 pulses, 500 ns each, at 3 MV/m, has been previously observed\cite{Inactivation1990}, but the RNA damage suggests that this is an electrochemical artifact \cite{Formation1996} (c.f.
+Capsid and envelope permeablization with 120 pulses, 500 ns each, at 3 MV/m, has been previously observed\cite{Inactivation1990}, but the RNA damage suggests that this is an electrochemical artifact \cite{Formation1996} (c.f.
 \cite{Microwave1987}).
@@
 The trapping experiments we use were conducted at
-
-As in the previous paper, we must stress that meaningful bioelectrics research hinges very strongly on experimental design and methodology, and very few results can be trusted implicitly.
-It appears to be very difficult to unambiguously determine effects and their cause on a system as complex as a cell, especially when electrodes are in contact with solution and release an energy-dependent dose of metal ions.
 
@@
 
-Viruses have extraordinary mechanical properties\footnote{Why is this?
-What selection pressures drive the selection of this pressure?}, so it seems reasonable that their dielectric properties could differ substantially from those of other biological structures.
+Viruses have extraordinary mechanical properties (why is this?
+What selection pressures drive the selection of this pressure?), so it seems reasonable to speculate that their dielectric properties could differ substantially from those of other biological structures.
 
-In the extreme case of the bacteriophage, the genome is packaged so tightly into the protein capsid that the core is often described as a glassy crystal of DNA\cite{Conformation2007}.
+In the extreme case of coliform bacteriophage, the genome is packaged so tightly into the protein capsid that the core is most accurately described as a glassy crystal of DNA\cite{Conformation2007}.
 ssRNA viruses like coronaviridae might be expected to be somewhat more sedate in packing density, but this does not seem to be borne out in the core conductivity data.
@@
 On the other hand, the eukaryotic "structome" also contains countless vesicles and structures of similar nature that might plausibly be damaged; small pockets of lipid in the endoplasmic reticula - nuclear pore complexes, etc.
-This appears to be seen to some degree in Gabriel's data; dense tissues exhibit many [double check this].
+This appears to be seen to some degree in Gabriel's data; dense tissues exhibit a high cole-cole alpha coefficient [double check this].
 It may not be possible to meaningfully predict all possible off-target effects, much like in drug discovery.
@@
 
-Madiyar's Vaccinia electroporation data aligns with. Assuming that the host porates at 0.05 MV/m, the 250 nm vaccinia might be expected to have a threshold of 4 MV/m. Mutatoyo's data also agree.
+Madiyar's Vaccinia electroporation data aligns with.
+Assuming that the host becomes permeable at 0.05 MV/m, the 250 nm vaccinia might be expected to have a threshold of 4 MV/m.
+Mutatoyo's data also agree.
 
 This does not agree with the two reports. It does not seem plausible that the
+
+A normalized (note that the true value of the virus' transmembrane voltage is, again, a factor of 400 reduced).
+
+\begin{figure}[H]
+	\includegraphics[width=\textwidth]{step_course}
+\end{figure}
+
+Despite the two having similar time constants (host: $\tau_1=444\ \text{ns},\ \tau_2=2.3\ \text{ns}$, virus: $\tau_1=295\ \text{ns},\ \tau_2=3.1\ \text{ns}$), the time course of the transmembrane voltage is clearly distinct.
+(Plot generated via the convolution method, \ghfile{transmembrane_steady_state.py})
+
+Consider the following double gaussian waveform, each with a FWHM of 500 picoseconds, separated by 1 nanosecond.
+In this case, the peak virus transmembrane voltage is no longer 1/400 less than the host cell, but 1/6.5, and the total energy in each curve is also improved to a ratio of 1/37.
+The second, inverted pulse has the effect of quickly zeroing out the host cell's decaying potential to improve the virus' energy ratio.
+
+\begin{figure}[H]
+	\includegraphics[width=\textwidth]{gaussian_pulse}
+\end{figure}
 
@@
 However, not field-time product [analytic, ].
-
-Despite the two having nearly identical time constants, the course of the transmembrane voltage is clearly different.
-[transmembrane plot here]
 
@@
 Kotnik note an important fact: all these permittivity and conductivity values will also depend on frequency, which is not included in their model.
-We have not examined how these factors can be extracted from.
-Also disregarded are the Poisson-boltzmann shielding space-charges that proved all-important in the last study.
+We have not examined whether these factors can be extracted from existing plots.
+Also disregarded are the Poisson-Boltzmann shielding space-charges that proved all-important in the last study.
 
@@
 
-The concept of optimizing an electroporation pulse is not novel, having been discussed by many groups in the past; either to prodduce different sterilization effects, tee Retelj use a series of, to
+The concept of optimizing an electroporation pulse is not novel, having been discussed by many groups in the past; either to produce different sterilization effects, tee Retelj use a series of, to
 

### 2021-06-11 documents/lessons_learned.tex
nondimensionalizing isn't working
Hampath

@@
 \section{Lessons Learned} \
+
+it seems like older papers that establish the base facts of a field, perhaps because of un-searchable full text, or a lack of recent citations directly,means there is some sort of bias towards more recent, but more detail-sparse papers.
+
+PLoS One doesn't allow footnotes. This seemed weird, but trying to rewrite inline actually does seem to make things a lot cleaner, and I'll try to keep this.
+
+I've been muttering a lot about saving the results of the simulations.
+However, perhaps the real solution is to never undergo this trial-and-error technique - to learn enough about the problem, and to have enough testing in place.
+This might not ever be feasible.
+
+\rule{\linewidth}{0.2pt}
 
@@
 
+Memoization is more thoroughly considered in Scaling of Differential Equations with joblib.
+
 Dill

### 2021-06-11 documents/pure_electroporation.tex
Hampath

@@
 
-	fortuitous Dielectric properties apparently due to the
+	Fortuitous dielectric properties ostensibly due to the densely-packed genome core and apparently only affecting some ssRNA viruses
 
@@
 
-At the risk of spending more time producing underpowered "scientifically useless" results,
-
-In a continued effort to make ultracrepidarian pseudo-physicists such as ourselves feel useful
+In a continued effort to make ultracrepidarian physicists such as ourselves feel useful in the wake of a purely biological threat, and at the risk of producing more underpowered and scientifically useless results,
 
@@
 
+The idea of inactivating viruses via electric fields is not new.
+Very recently, Osorio \cite{Receptor2021} have reported on a susceptibility of SARS-CoV-2's spike protein to intense electric fields; however, in general, techniques targeting proteins appear to require truly extreme; fields of up to 2.9 GV/m were used in their computational study.
+Similarly, the dissocation of capsid proteins has been predicted by Man \cite{Picosecond2016b} at 2 GV/m.
+
+These regimes of intensity may possibly be accessible via ultrashort optical techniques.
+Accordingly, Tsen \cite{Studies2014} report a non-electroporative mechanism, but these results have not been successfully independently replicated at that intensity\cite{No2011}.
+
 The field-induced breakdown of lipid membranes has proved to be a particularly useful property of the cell. From initial studies of crude membrane breakdown effects \cite{Reversible1979}
@@
 
-It is, in general, something of a singular outlier in that it is one of very few biological mechanisms relevant at practical electric field intensities.
+It is, in general, something of a singular outlier in that it is one of very few biological mechanisms that manifest at practical electric field intensities.
 Similar to thermal treatment, it also performs an operation something like integration with a threshold, a process distinct from normal absolute-value.
@@
 
-The idea of inactivating viruses via electric fields is not new.
-Very recently, Osorio \cite{Receptor2021} have reported on a susceptibility of SARS-CoV-2's spike protein to intense electric fields; however, in general, techniques targeting proteins appear to require truly extreme; in their study, fields of up to 2.9 GV/m were required.
-Dissocation of capsid proteins has been predicted by Man \cite{Picosecond2016b} at 2 GV/m.
-
-These regimes of intensity may possibly be accessible via ultrashort optical techniques.
-Accordingly, Tsen \cite{Studies2014} report a non-electroporative mechanism, but these results have not been successfully independently replicated at that intensity\cite{No2011}.
-
 Electroporation\cite{Electroporation1988}, now a common laboratory procedure, occurs when an enormous electric field causes ions in solution to diffuse across a cell membrane, capacitively charging it, provoking a change in lipid bilayer conformation\cite{Membrane2016}, either reversibly rendering the membrane permeable or, if the number and size of pores is considerable, the membrane may be permanently destroyed.
@@
 
-There is a single report of the electroporation of HIV in the gray literature.
+%There is a single report of the electroporation of HIV in the gray literature.
 This one of very few reports involving the electroporation of viruses, reporting the ~95\% inactivation of HIV using a standard commercial Bio-Rad electroporation system at 2.3 MV/m.
@@
 The most obvious difference is scale.
-Viruses are minute.
 All other properties of the system being equal, the standard Schwan equation for transmembrane voltage implies that the steady-state DC voltage is proportional to the size of the particle.
-In the case of a 100 nm virus
+In the case of a 100 nm virus, this would 400x difference, which is reflected precisely in the steady state numerical simulations that follow.
 
@@
 Assuming that the host becomes permeable at 0.05 MV/m, the 250 nm vaccinia might be expected to have a threshold of 4 MV/m.
-Mutatoyo's data also agree.
+Mutatoyo's data also agree roughly.
 
-This does not agree with the two reports. It does not seem plausible that the
+This does not agree with Yamada \cite{Electroporation2012}'s data on electroporation of Hepatitis B.
 
@@
 
-Consider the following double gaussian waveform, each with a FWHM of 500 picoseconds, separated by 1 nanosecond.
+Consider the following bipolar gaussian waveform, each with a FWHM of 500 picoseconds, separated by 1 nanosecond.
 In this case, the peak virus transmembrane voltage is no longer 1/400 less than the host cell, but 1/6.5, and the total energy in each curve is also improved to a ratio of 1/37.
@@
 %1/(250e-9 / 20e-6)
-
-400x difference, reflected in the numerical steady state simulations.
 
@@
 
-[step response]
-
-And so, despite having similar time constants, a short gaussian pulse [] long
-
 There may be an existing transmembrane potential that must be added - this is neglected in this case.
 
-The dielectric properties of viruses have been determined by the fascinating technique of electrorotation, dielectrophoresis, and dielectric spectroscopy.
-To prevent fluid heating, these are often conducted in low osmotic strength media.
-Enveloped viruses are permeable to small ions, and so some results may not necessarily representative of conductivities in physiological conditions; \cite{Assessment}.
+\section*{Empirical dielectric properties}
+
+The dielectric properties of viruses have been determined by the fascinating and ingenious techniques involving electrorotation, dielectrophoresis, and dielectric spectroscopy.
+To prevent fluid heating, these are often conducted in low osmotic strength media; as enveloped viruses are permeable to small ions, some results may not necessarily representative of conductivities in physiological conditions or must be \cite{Assessment}.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%55
+\subsection*{Error in Kotnik}
+
+\begin{tcolorbox}
+
+	There appears to be a minor typographical error in equation 8, transfer function, from Kotnik \cite{Time1998}. The equation is given in terms of a and b coefficients,
+
+	\textcolor{red}{$$F(s) = \frac{a_1 s^2 + a_2 s + a_3}{b_1 s^2 + b_2 s + b_3} \text{ (eq. 8)}$$}
+
+	whereas the correct order appears to be:
+
+	\textcolor{blue}{$$F(s) = \frac{a_3 s^2 + a_2 s + a_1}{b_3 s^2 + b_2 s + b_1}$$}
+
+	The rest of the paper appears to obey this coefficient order: for instance, equation A6e in that paper, in the derivation of the step function:
+
+	$$E(s) = \frac{1}{s}$$
+
+	$$F(s) \cdot E(s) = \frac{a_3 s^2 + a_2 s + a_1}{b_3 s^2 + b_2 s + b_1} \frac{1}{s} = \frac{a_3 s^2 + a_2 s + a_1}{b_3 s^3 + b_2 s^2 + b_1 s} \text{ (eq. A6c)}$$ 	%confirmed with mathematica.
+
+	We will continue to use this convention, assuming the subscripts on equations 9a through f are correct.
+
+	This transposition was only detected late in the project, and so some documentation may still contain the incorrect coefficients. Beware.
+
+\end{tcolorbox}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%55
+
 \subsection*{Electrodynamic considerations}
@@
 
-We must apologize once again to the mathematicians for sins of terminology.
+We must apologize once again to the mathematicians for sins of terminology and rigor.
 
@@
 
+Scipy has a convenient LTI class that accepts the terms.
+
 single input, multiple output
 
-"Underactuated" robotics
+underactuated robotics, simultaneous stabilization\cite{results1984}\cite{Simultaneous2005}
 
@@
 
-Kotnik discuss the transmembrane voltage due to several pulse shapes formed from the Laplace Transform of the original differential equation.
+Kotnik discuss the transmembrane voltage due to several pulse shapes constructed simply from the Laplace Transform of the original differential equation.
 
@@
 Via Mathematica, the Fourier transform of both the impulse response and the step response exist, are analytic and of manageable size; however, the integral of the cost function is extremely unwieldy.
+
+Pole placement
+
+\subsection*{Nonlinear model predictive control, quadratic regulators, }
+
+\subsection*{Frequency-domain solution}
 
@@
 
+$$ x_v(t) = A_v \frac{d^2u(t)}{dt^2} + B_v \frac{du(t)}{dt} + C_v u(t) - D_v \frac{dx_v(t)}{dt} - \frac{d^2 x_v(t)}{dt^2} $$
+
+$$ x_h(t) = A_h \frac{d^2u(t)}{dt^2} + B_h \frac{du(t)}{dt} + C_h u(t) - D_h \frac{dx_h(t)}{dt} - \frac{d^2 x_h(t)}{dt^2} $$
+
 % https://math.stackexchange.com/questions/3435173/how-to-nondimensionalize-a-second-order-differential-equation
@@
 
-\subsection*{}
+A system of first-order Differential-Algebraic Equations:
+
+Smooth noise-free combined filter and differentiator.
+
+An advantage of bang-bang or bang-off-bang over is that the values of u0 are not free.
+In this case, it was often found that (perhaps due to poorly-chosen values of the penalty factor rho, a poor initial guess, or some other issue in the problem setup), the gradient descent would decrease the control magnitude to a value below numerical accuracy.
+This necessitated a Lagrange constraint on the total, further increasing the computational complexity and restricting the class of solutions.
+
+\subsection*{Analytic solution}
 
@@
 Setting say, the logistic equation, produces an overdetermined system. using the above as a constraint in PSOPT was also ineffective.
+
+\begin{tcolorbox}
+	First instinct might be to try to solve for the waveform that sets alpha beta gamma to zero. 
+\end{tcolorbox}
 
@@
 
+"Bulk effects", as the concentration increases, can completely alter the. It may not be possible to produce a robust enough scheme
+
 \subsection{Software used and evaluated:}
@@
 
-typeset in LaTeX using TeXstudio.
+typeset in LaTeX on TeXstudio and Gummi.
 
@@
 
+The book Scaling of Differential Equations is an excellent guide to the numerical treatment of DEs.
+
 \end{document}

### 2021-06-11 documents/scan_converter.tex
Oh hey the brilluoin just had a bug
whatever
Rewording text slightly in case biorxiv is a good idea
Pure electroporation
iLQR
Hampath

@@
 \begin{document}
+
+\section{Scan converter}
 
@@
 So called "equivalent-time" or "sampling" oscilloscopes are less expensive; but it was hoped that it would be possible to resolve the breaking of the capsid - a transient, single-shot phenomenon -   A digital oscilloscope capable of real-time sampling such a transient is a tall order, and it did not appear that an undergraduate would be allowed access.
+
+Gating time. Photoconductive gating is a particularly interesting technique for this.
 
@@
 	\centering
-
+	\includegraphics[width=0.6\textwidth]{sensor_damage.jpg}
 	\caption{}
@@
 
+Low vacuum, gas focused tubes are less predictable and more difficult to model.
+XOOPIC; the standard PIC code WARP has undocumented feature of collisional ionization but Tegerup has a guide to use.
+Simulation
+
+PIC-LAS
+
 The distortion due to transit-time phasing is
@@
 
+stray light
+
+old canal ray paper
+
+the old WARP has a module for collisional ionization, though it's got a bug \cite{Simulation}.
+
 \end{document}

### 2021-06-17 documents/pure_electroporation.tex
Hampath math notes

@@
 The most obvious difference is scale.
-All other properties of the system being equal, the standard Schwan equation for transmembrane voltage implies that the steady-state DC voltage is proportional to the size of the particle.
+All other properties of the system being equal, the standard Schwan equation for transmembrane voltage, $\Delta \phi = (3/2) E R \cos(\theta)$ implies that the steady-state DC voltage is proportional to the size of the particle.
 In the case of a 100 nm virus, this would 400x difference, which is reflected precisely in the steady state numerical simulations that follow.
@@
 
-	This transposition was only detected late in the project, and so some documentation may still contain the incorrect coefficients. Beware.
+	This minor transposition was only detected late in the project, and so some documentation may still contain the incorrect coefficients. Beware.
 
@@
 This bears considerable similarity to e.g.
-radar waveform design and compressed sensing; problems of coherent control of quantum systems.
-In many cases, the optimal control is equal to the transfer function
+radar waveform design and compressed sensing; problems of coherent control of quantum systems, single input multiple output underactuated robotics, simultaneous stabilization\cite{results1984}\cite{Simultaneous2005}.
+
+In many cases, the optimal (minimum-energy) control is equal to the transfer function
 
 Scipy has a convenient LTI class that accepts the terms.
-
-single input, multiple output
-
-underactuated robotics, simultaneous stabilization\cite{results1984}\cite{Simultaneous2005}
 
@@
 
-For PSOPT, a further modification was needed, as the library does not support the derivative of the control; the second derivative was used as the control, and input into a differential-algebraic equation form.
+For PSOPT, a further modification was needed, as the library does not appear to natively support the second derivative of the control; the second derivative was used as the control, and input into a differential-algebraic equation form.
 
@@
 A number of linear solvers can be used.
-LANL's Tasseff's integration with the SPRAL solver, reportedly faster on large problems, was
+LANL's Tasseff's integration with the SPRAL solver, reportedly faster on large problems, was .
+HSL libraries ma57 and ma97 were used.
 
@@
 
-\subsection*{Limitations and next steps}
+\section*{Sensitivity analysis}
+
+\section*{Limitations and next steps}
 
@@
 
-\subsection{Software used and evaluated:}
+sensitivity analysis
+
+\subsection*{Software used and evaluated:}
 
@@
 
-\subsection{Recommended reading}
+\subsection*{Recommended reading}
 

### 2021-06-22 documents/pure_electroporation.tex
Gradient bang-bang switching time method, and perhaps Fourier method

@@
 \title{Selective electroporation of the viral envelope via optimal control of transmembrane potential}
-\author{\footnotesize{Daniel Correia\orcidlink{0000-0002-9353-0216}}\footnote{Ontario, Canada; contact information in the ORCiD.}}
+\author{\footnotesize{Daniel Correia\orcidlink{0000-0002-9353-0216} \{dcorreia@whimsysciences.com || therobotist@gmail.com\}
+		 \href{https://0xdbfb7.com/email_pledge.txt}{Please don't hesitate to contact; see here}}\footnote{Ontario, Canada; contact information in the ORCiD.}}
 \date{\small{March 21 2021}}
@@
 
-	This minor transposition was only detected late in the project, and so some documentation may still contain the incorrect coefficients. Beware.
+	This minor transposition was only detected late in the project, so some documentation in the repository may still contain the incorrect coefficients. Beware.
 
@@
 
+a double integrator
+
 In many cases, the optimal (minimum-energy) control is equal to the transfer function
@@
 Scipy has a convenient LTI class that accepts the terms.
+
+There are suprisingly many more quan
 
@@
 \begin{tcolorbox}
-	First instinct might be to try to solve for the waveform that sets alpha beta gamma to zero. 
+	First instinct might be to try to solve for the waveform that sets alpha beta gamma to zero; feeding this though produces a reasonable solution []. 
 \end{tcolorbox}
 
-Written in texst
+Puts much more effort into further analytical rearrangement before resorting to; by more fully using Pontryagin's Maximum Principle, and by formulating a control theoretic Hamiltonian.
+What looks to be a superb code hampath, did not have the experience to implement the hamiltonian at short notice.
+
+\subsection*{Bang-bang control}
+
+A good review of advanced bang-bang control techniques \cite{Computations2004}.
 
@@
 
-\section*{Limitations and next steps}
+\section*{Limitations and recommendations for further study}
 
@@
 
+\section*{Commentary and discussion}
+
+In easily mutable versions of this paper, this section will be
+
+I have been lucky to have been provided the opportunity to conduct this research.
+
 \end{document}

### 2021-06-26 documents/pure_electroporation.tex
Working on Nagurka

@@
 
-An advantage of bang-bang or bang-off-bang over is that the values of u0 are not free.
-In this case, it was often found that (perhaps due to poorly-chosen values of the penalty factor rho, a poor initial guess, or some other issue in the problem setup), the gradient descent would decrease the control magnitude to a value below numerical accuracy.
-This necessitated a Lagrange constraint on the total, further increasing the computational complexity and restricting the class of solutions.
+mayer (endpoint) or Lagrange (integral)
+
+An advantage of bang-bang or bang-singular-bang over is that the values of u0 are not free.
+In PSOPT and , it was often found that (perhaps due to poorly-chosen values of the penalty factor rho, a poor initial guess, or some other issue in the problem setup), the gradient descent would decrease the control magnitude to a value below numerical accuracy.
+This necessitated a Lagrange constraint on the integral, further increasing the computational complexity and restricting the class of solutions.
 
@@
 
+\subsection*{Hampath bang-bang control}
+
+A good review of advanced bang-bang control techniques \cite{Computations2004}.
+
 Puts much more effort into further analytical rearrangement before resorting to; by more fully using Pontryagin's Maximum Principle, and by formulating a control theoretic Hamiltonian.
@@
 
-\subsection*{Bang-bang control}
+\subsection*{Niemann's bang-bang control control}
 
-A good review of advanced bang-bang control techniques \cite{Computations2004}.
+Niemann describes a straightforward bang-bang formulation using gradient methods, using gradient projection to implement the required boundaries \cite{Determinationa}.
+Because the unit step function of the transmembrane voltage is analytic, a bang-bang control can be simulated without integration, by simply summing the (as described by Kotnik).
+This appears to automatically resolve "backwards-integration" and sorting issues presented in chapter 3 of Niemann's thesis.
+
+While
 
@@
 
+As previously mentioned, electroporation is rarely seen in non-contact studies. It is possible that some nuanced
+
 Involves careful control of the second derivative of a waveform
 
-optimal over a distribution
+Viruses vary by \%x . optimal over a distribution of cells and viruses.
 
@@
 sensitivity analysis
+
+must necessarily operate "open loop", without feedback, towards the transmembrane voltage
 
